### 2019-01-18 paper/ms.tex
initial commit

\documentclass[12pt,twocolumn,tighten]{aastex62}
%\pdfoutput=1 %for arXiv submission
\usepackage{amsmath,amstext,amssymb}
\usepackage[T1]{fontenc}
\usepackage{apjfonts}
\usepackage[figure,figure*]{hypcap}
\usepackage{graphics,graphicx}
\usepackage{hyperref}
\usepackage{comment}

\renewcommand*{\sectionautorefname}{Section} %for \autoref
\renewcommand*{\subsectionautorefname}{Section} %for \autoref

%% Reintroduced the \received and \accepted commands from AASTeX v5.2.
%% Add "Submitted to " argument.
\received{\today}
\revised{---}
\accepted{---}
\submitjournal{AAS journals.}

\shortauthors{Bouma et al.}
\shorttitle{Light Curves for Stars in Clusters}

%\NewPageAfterKeywords

\begin{document}

\title{Homogeneous Light Curves for Stars in Clusters from TESS}

\correspondingauthor{L. G. Bouma}
\email{luke@astro.princeton.edu}

\author[0000-0002-0514-5538]{L. G. Bouma}
\affiliation{ Department of Astrophysical Sciences, Princeton
University, 4 Ivy Lane, Princeton, NJ 08540, USA}
%
\author[0000-0002-0628-0088]{W. Bhatti}
\affiliation{ Department of Astrophysical Sciences, Princeton
    University, 4 Ivy Lane, Princeton, NJ 08540, USA}
%
\author[0000-0001-8732-6166]{J. D. Hartman}
\affiliation{ Department of Astrophysical Sciences, Princeton
University, 4 Ivy Lane, Princeton, NJ 08540, USA}
%
\author[0000-0001-7204-6727]{G. \'A. Bakos}
\affiliation{ Department of Astrophysical Sciences, Princeton
University, 4 Ivy Lane, Princeton, NJ 08540, USA}
%
\author[0000-0002-4265-047X]{J. N. Winn}
\affiliation{ Department of Astrophysical Sciences, Princeton
University, 4 Ivy Lane, Princeton, NJ 08540, USA}

\begin{abstract}
  Lorem ipsum.
\end{abstract}

\keywords{
  methods: data analysis ---
  techniques: photometric ---
  %TODO: could be individual, and enumerate each cluster as well.
  (Galaxy:) open clusters and associations: general ---
  planets and satellites: detection 
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:intro}

Lorem ipsum.

In what follows, \S~\ref{sec:method} presents BLAH, and
\S~\ref{sec:results} describes BLAH BLAH.
\S~\ref{sec:discussion} discusses, and \S~\ref{sec:conclusion}
concludes.

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.7\textwidth]{f1_PLACEHOLDER.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{
    {\bf There are many clusters; TESS looks at them.} Placeholder skymap.
		\label{fig:clustermap}
	}
\end{figure*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Method}
\label{sec:method}

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.3\textwidth]{f2.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{
    {\bf Pipeline.} This is what we do.
		\label{fig:pipeline}
	}
\end{figure}

\subsection{Overview}

We reduced the TESS images to lightcurves by performing a sequence of
steps using stand-alone programs.  A conceptual overview of our
``pipeline'' is given in Figure~\ref{fig:pipeline}.  Similar pipelines
have been presented by \citet{Pal_2009},
\citet{soares-furtado_image_2017} and \citet{oelkers_precision_2018}.

We begin with the calibrated full frame images produced by SPOC
(\S~\ref{subsec:observations}).  We then perform a collection of
preparatory steps, including source extraction of bright stars,
astrometry using the resulting positions, and coarse simple aperture
photometry (\S~\ref{subsec:preparation}).  Using the shape values from
the initial astrometry, we select an astrometric reference frame and
transform all of the calibrated images to it.  We construct a
photometric reference by stacking a collection of frames, and then
convolve all the transformed frames to match the photometric reference,
and subtract (\S~\ref{subsec:imagesubtraction}).  We perform aperture
photometry on the subtracted images using positions projected onto the
frame from Gaia DR2.  We detrend the resulting lightcurves
(\S~\ref{subsec:lcdetrending}) in two subsequent steps.  First, we apply
External Parameter Decorrelation (EPD, \citealt{bakos_2010}), and then
we apply a Trend Filtering Algorithm (TFA, \citealt{kovacs_trend_2005}).
Finally, we assess the resulting lightcurves using a variety of
statistics for their white noise and red noise properties
(\S~\ref{sec:results}).

\subsection{Observations}
\label{subsec:observations}

% How did TESS observe?
% What processing steps happened in order to get the calibrated frames?
% Why did we choose to start with them?

The TESS spacecraft began science operations on July 25, 2018.  To
keep its cameras pointed opposite the Sun, the spacecraft advances by
$\approx$$28$ degrees in ecliptic longitude every lunar month.  Data
acquired throughout each ``sector'' is downlinked at spacecraft
perigee through the Deep Space Network.  Verbose descriptions of the
spacecraft's design and operations are given by
\citet{ricker_transiting_2015} and the instrument handbook
\citep{vanderspek_2018}.

For us, the main data product of interest is the calibrated full frame
image (FFI).  Each TESS camera reads out every 2 seconds.  To produce
a manageable telemetric load, the resulting pixel values are summed by
the onboard computer into 30 minute averages. (An on-board cosmic ray
mitigation algorithm is applied.) Once transmitted to the ground, the
raw images are calibrated by the Science Processing Operations Center.
The calibration process includes an overscan, bias, and dark current
correction, and also dividing out a flat field.  The details are given by
\citet{clarke_kepler_2017}, and the resulting science data products are
described by \citet{tess_data_product_description_2018}.

We begin our analysis using the calibrated images, their uncertainty
maps, and their associated headers.  The spacecraft has four cameras,
and each camera has four CCDs.  In the following analysis, all
image-level operations are thus performed on the images for each CCD,
so that at any instant of time there are 16 independent images
undergoing analysis.

\subsection{Preparatory Steps}
\label{subsec:preparation}

Before we can perform any kind of photometry, a few janitorial tasks
are required.

The first is to trim and mask the images.  We convert the calibrated
image from MAST into a \texttt{fitsh}-compatible image by retrieving
the image data (omitting the uncertainty map, for now). We then trim
the image to remove virtual rows and columns (using the
\texttt{SCIROWS}, \texttt{SCIROWE}, \texttt{SCCSA}, \texttt{SCCED},
header values).  We then mask out saturated stars using the `fiign`
program with a fixed saturation level of $2^{16}\,{\rm ADU}$.  As
described by \citet{Pal_2009}, the mask is metadata to the image, and
is not actually applied to the pixel values.  During masking, we also
use the algorithm described by \citet{Pal_2009} to extend masks beyond
purely satured pixels to ``bloomed'' pixels -- pixels horizontally and
vertically adjacent to the saturated pixels.  Finally, for frames with
the \texttt{DQUALITY} bit-flag set to 32~---~corresponding to the
``momentum dumps'' described by \citet{vanderspek_2018}~---~we mask
out the entire frame.  This removes on average a few frames per
sector. Through visual inspection, we see that the stars on these
frames are extremely smeared, and are unlikely to produce useful
science data.

Next, we perform some initial analysis steps to produce metadata
needed during image subtraction.  To obtain an astrometric solution
(independent from the WCS data packaged with the frames), we use
\texttt{fistar} to perform source extraction on bright stars in each
image.  We pass the resulting source lists through
\texttt{astrometry.net} \citep{lang_2010}, which returns an
astrometric solution for each frame packaged in the WCS format
\citep[][Sec.~8]{pence_fits_2010}.  During the initial source
extraction, we also fit elongated gaussians to the bright stars,
yielding the shape parameters (S,D,K), where the flux as a function of
position is assumed to take the form
\begin{align}
  f_{\rm elong}(\vec{x}) &= B + A \exp \{ -0.5 \times ( 
    S(\Delta x^2 + \Delta y^2) + \\
    &D(\Delta x^2 - \Delta y^2) +
    K(2\Delta x \Delta y)
  )  \},
\end{align}
for $\Delta x = x-x_0$, and $\Delta y = y - y_0$.  $S$ is typically
called the ``sharpness''.  For a nearly circular shape profile, ${\rm
FWHM} \approx 2.35\sqrt{S}$ \citep[{\it e.g.},][]{Pal_2009}.  These
shape parameters are later used when selecting an astrometric
reference (\S~\ref{subsec:imagesubtraction})

With the resulting WCS information, we then project a source catalog
from Gaia-DR2 onto the frame, down to a pre-selected magnitude cutoff
\citep{gaia_collaboration_gaia_2018}.  We use these expected positions
to center the apertures in our photometry, rather than attempting to
detect the positions.  Such ``forced-aperture photometry'' is
preferable to performing source extraction because of the large TESS
pixels, and the accurate Gaia positions.  The Gaia-DR2 epoch is
J2015.5, so even the fastest-moving stars with proper motions of
$\sim$$1\,{\rm arcsecond}\,{\rm yr}^{-1}$ are still well within one pixel
of their predicted positions in the TESS images.  The projection and
catalog-indexing is performed using
\texttt{gaia2read}\footnote{\url{github.com/samuelyeewl/gaia2read}}
(CITE Jason Kim junior thesis).

Finally, we perform aperture photometry on the bright stars from the
source list, by summing the counts inside appropriately-weighted
circular apertures centered on the projected positions from Gaia DR2. 
The pixel weights $w_{x,y}$ are equal to the fraction of the pixel
that falls within the aperture.  They are thus unity for pixels
entirely within the aperture, and fractional along the aperture
boundary (e.g., \citealt{Pal_2009} Fig 17). 
The background levels are measured in annuli around each aperture
center.  The raw flux of the object after background removal is then
(\citealt{Pal_2009} Eq 65)
\begin{equation}
  f = \sum_{x,y} w_{x,y} (I_{x,y} - B) = f_{\rm total} - B r_0^2.
  \label{eq:simple_aperture_phot}
\end{equation}
The resulting measurements, for instance of the background level of
each aperture, and the number of ``good'' objects that are detected,
are later used as input for selecting photometric reference frames.

\subsection{Image Subtraction}
\label{subsec:imagesubtraction}

We then select two ``reference frames'' for image subtraction.
The first is the astrometric reference; the second is the photometric
reference.
To choose the astrometric reference, we use the following heuristics:
\begin{enumerate}
  \item The frame must have large and round stars (largest ``S'',
    smallest ``D'' and ``K'' values).
  \item The frame must minimal background noise, as measured in annuli
    around the bright stars selected in \S~\ref{subsec:preparation}.
  \item The frame must have, relative to the other frames being
    considered, a large number of detected sources.
\end{enumerate}
We sort the frames using the above metrics, and then select the
astrometric reference from successive intersections of each sorted
list.
Using the algorithm presented by \citet{pal_astrometry_2006}, we then
calculate a spatial transformation that maps the X and Y coordinates
from each calibrated frame onto the the astrometric reference.

``Registering'' the images onto a common astrometric reference frame
requires some care. In particular, the transformation must preserve
the fluxes of the sources. Since the transformation is affine (a
combination of {\it e.g.}, translation, rotation, dilation, and shear)
standard bilinear or bicubic interpolation would not achieve flux
conservations.  We therefore use the flux-conserving interpolation
scheme described by \citet{Pal_2009} which is based on analytic
integration of the surfaces determined by the pixel values. 
%FIXME: is this interpolation scheme definitely being applied?
The largest component of the transformation is a translation, of order
2 arcseconds, or about 0.1 TESS pixels.

The second reference frame needed for image subtraction is the
photometric reference.
This is a high-SNR median average of frames that is used both to
calculate the convolution kernel during image subtraction, and to
measure the reference flux of each star.
To select viable frames for inclusion in the photometric reference, we
use the results of our initial photometry step
(\S~\ref{subsec:preparation}), and sort frames for each sector by:
\begin{enumerate}
  \item Lowest median scatter in photometry
  \item Lowest median error in photometry
  \item Lowest median background measurement
  \item Lowest median absolute deviation in background measurements
  \item Largest number of stars detected by \texttt{fiphot} with good
    flags.
    % fiphot files used for all of this.
\end{enumerate}
We convolve the 50 best candidate photometric references to the best
photometric reference, and then perform a median combination of the
frames to make the photometric reference.

%FIXME: it seems like it would be smart to produce a photometric
%reference for different intervals of time. 480 frames over 10 days ->
%perhaps split the full 28 day sector entirely by momentum dumps to
%get ~10 photometric references per sector.

%FIXME: LEFT OFF HERE
Some details of, and motivation for, the convolution process are warranted.
The general idea of the image subtraction problem is to...

This has some benefits for crowded regions. Most notably, in enables a
measurement of the background flux level.

Our approach follows from the algorithm presented by
\citet{Alard_Lupton_1998}, and explained in detail by
\citet{miller_optimal_2008}.
The process is: %FIXME: following miller 2008...
\begin{enumerate}
  \item Select a set of isolated stars (``stamps'').
  \item Choose basis vectors $K_n$ for the kernel, $K = \sum_{n=1}^N
    a_n K_n$. Our goal is to determine the best-fitting coefficients
    $a_n$. 
  \item Using these stamps and the least-squares method, ...
\end{enumerate}

%FIXME: when do we actually get the reference fluxes? Where do those
%come from???

Finally, we convolve and subtract all the frames that have been
translated from the photometric reference (\texttt{grcombine}).
We use the same kernel formalism as described by
\citet{soares-furtado_image_2017}.
To compute the convolution kernel, we minimize the difference between
each image and the photometric reference (or something like this),
using the Alard \& Lupton 1998 method (CITE, also CITE Miller's
reference).
The software implementation is that by \citet{Pal_2009}, in the
\texttt{ficonv} program.
The implemented math is as follows.
\begin{equation}
  XXX = XXX. %FIXME: maybe Soares pg 5 main equation?
\end{equation}
We explored a variety of kernel options, including X, Y, and Z.
We wound up including an ``identity'' term (MEANING?), a ``background
term'' (MEANING?) and a delta function term (MEANING? Give math for
all of these).
There are also spatially-varying terms of order XX. (MEANING?)
% I believe this means that we should be able to somehow _visualize_
% the kernel as a function of spatial position in the image. What
% should it look like? Is it like a star's PSF? Or somehow related??

We perform forced-aperture photometry on the subtracted frames,
using the locations from the Gaia projection, to measure the resulting
difference fluxes.
We use circular apertures, with the appropriate weigths along the
boundaries (\texttt{fiphot}; \citet{Pal_2009} Section FIXME).

Note that to measure the fluxes on the differenced images, a
slightly different procedure from Eq.~\ref{eq:simple_aperture_phot} is
relevant.
(Pal 2009 Section 2.9).
Specifically, the subtracted image $S$ is given by $I - B - R\ast K$,
for $I$ the original image, $B$ the background, $R$ the reference
image, and $K$ the convolution kernel.
The flux in the original image is given by
%FIXME: this equation IS PROBABLY WRONG. I_xy? Or S_xy?
\begin{align}
  f &= \sum_{x,y} w_{x,y} I_{x,y} \\
    &= 
       \frac{1}{|| K ||_1^2} \sum_{x,y} S_{x,y} (w \ast K)_{x,y}
       +
       \sum_{x,y} R_{x,y} w_{x,y},
\end{align}
%FIXME: derive this equation. why exactly does this work?

Finally, to convert from a list of sources on each frame to a list of
flux values at any given time, we use the \texttt{grcollect}
transposition tool.

\subsection{Lightcurve Detrending}
\label{subsec:lcdetrending}

The preceding tedium produces lightcurves that include both
instrumental systematics as well as astrophysical variability.
We perform two subsequent detrending steps:
we decorrelate against known external parameters (EPD,
\citealt{bakos_2010}) that we know affect the stellar flux
measurements, and then we filter remaining systematic trends from
unknown parameters (TFA, \citealt{kovacs_trend_2005}).  These
procedures are the standard that have been adopted for the HAT group
(see discussions from {\it e.g.}
\citealt{huang_high-precision_2015,zhang_precision_2016}).
We briefly summarize them here for self-consistency.

In ``external parameter decorrelation'', we fit the magnitude of each star
as a function of parameters that we suspect may systematically affect
the brightness counts.
For instance, intra-pixel quantum efficiency variations can affect
the measured stellar brightness as a function of the fractional
centroid positions, $\{ x \}$ and $\{ y \}$, where $\{ x \} = x -
\lfloor x \rfloor$, for $\lfloor \cdot \rfloor$ the floor function.
Changes in the CCD electronics due to their temperature $T$ might
matter.
The fast focal ratio of the TESS cameras introduces significant
comatic aberrations to the images, which affect the shape of the point
spread function as a function of distance from the center of each
camera's field; this might be at least superficially treated by
allowing the elongated gaussian shape parameters $(S,D,K)$ to be free
parameters.

To chose among these free parameters, we plotted the magnitudes
against each parameter in the vector $\theta' = (S,D,K,S^2,K^2, D^2,
S\cdot D, S\cdot K, D\cdot K, x,y,\{x\},\{y\},T, \sin(2\pi x),
\cos(2\pi x), \sin(2\pi
y),\cos(2\pi y))$.
We used the temperature from the on-chip aluminum-copper sensor
measurements included in the engineering
data\footnote{\url{archive.stsci.edu/missions/tess/engineering/}}.

%FIXME: what did we see? What did we fit for?
We saw significant correlations for parameters X,Y, and Z.

We then fit the following model to the magnitudes $m$:
\begin{equation}
  m = {\rm const.} + \sum_i \theta_i,
\end{equation}
for 
$\theta = (S,D,K,S^2,K^2, D^2, S\cdot D, S\cdot K, D\cdot K,
x,y,\{x\},\{y\},T, \sin(2\pi x), \cos(2\pi x), \sin(2\pi y),\cos(2\pi
y))$.
We optimized via least-squares, and subtracted the maximum-likelihood
model to produce ``EPD'' lightcurves.

In ``trend filtering'', we correlate the flux timeseries of each star
against other stars in the frame (TFA, \citealt{kovacs_trend_2005}).
This requires selecting ``template stars'', which are a subsample of
star that are supposed to represent all the types of systematics
across the dataset. 
%FIXME: clarify this procedure
We select 500 template stars randomly from the stars on-chip with
$G_{\rm R_p}$ magnitudes between 8.5 and 13 (TODO: rather bright?).
We additionally require these stars to not have excessive variability,
by fitting a parabola in the RMS-magnitude plane, and discarding stars
more than $4\sigma$ away from the prediction of this fit.

Once the template stars are selected, we use the secret TFA
implementation from the \texttt{HATpipe} source code, that you and
nobody else is allowed to see.
% It's at /home/lbouma/proj/HATpipe/source/lc/frontends/tfa.c, I
% believe. We could perhaps use the vartools equivalent of this.

To select template stars, we impose a

The details of this selection procedure are

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
\label{sec:results}

RMS vs mag plots.

SNR of retrieved HJs.

Some stellar variability plots (perhaps of known stellar variables).

Some focus on actual cluster fields.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}
\label{sec:discussion}

Lorem ipsum.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}
\label{sec:conclusion}

% \begin{figure}[t]
% 	\begin{center}
% 		\leavevmode
% 		\includegraphics[width=0.49\textwidth]{f6.pdf}
% 	\end{center}
% 	\vspace{-0.5cm}
% 	\caption{
%     {\bf Further observations will be needed to confirm and understand
%     the timing variations of WASP-4b.} Dots are as in
%     Figure~\ref{fig:times}.  Lines are 100 random draws from the
%     posteriors of the apsidal precession model (orange), and the
%     orbital decay model (blue).    
% 		\label{fig:future}
% 	}
% \end{figure}

\acknowledgements
L.G.B.\ gladly acknowledges helpful discussions with
..., and is
grateful to the people who have turned TESS from an idea into reality.
%
J.N.W.\ thanks ...
%
This paper includes data collected by the TESS mission, which are
publicly available from the Mikulski Archive for Space Telescopes
(MAST).
%
Funding for the TESS mission is provided by NASA's Science Mission
directorate.
%
This research has made use of the NASA Exoplanet Archive, which is
operated by the California Institute of Technology, under contract
with the National Aeronautics and Space Administration under the
Exoplanet Exploration Program.
%
This work made use of NASA's Astrophysics Data System Bibliographic
Services.
%
This research has made use of the VizieR catalogue access tool, CDS,
Strasbourg, France. The original description of the VizieR service was
published in A\&AS 143, 23.
%
This work has made use of data from the European Space Agency (ESA)
mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed
by the {\it Gaia} Data Processing and Analysis Consortium (DPAC,
\url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding
for the DPAC has been provided by national institutions, in particular
the institutions participating in the {\it Gaia} Multilateral
Agreement.
%
\newline
%
\facility{
	TESS \citep{ricker_transiting_2015},
	Gaia \citep{gaia_collaboration_gaia_2016,gaia_collaboration_gaia_2018}
}
%
\software{
  \texttt{astrobase} \citep{bhatti_astrobase_2018},
  \texttt{astropy} \citep{the_astropy_collaboration_astropy_2018},
  \texttt{astroquery} \citep{astroquery_2018},
  \texttt{BATMAN} \citep{kreidberg_batman_2015},
  \texttt{corner} \citep{corner_2016},
  \texttt{emcee} \citep{foreman-mackey_emcee_2013},
  \texttt{fitsh} \citep{Pal_2012},
  \texttt{IPython} \citep{perez_2007},
  \texttt{matplotlib} \citep{hunter_matplotlib_2007}, 
  \texttt{numpy} \citep{walt_numpy_2011}, 
  \texttt{pandas} \citep{mckinney-proc-scipy-2010},
  \texttt{scipy} \citep{jones_scipy_2001}.
}

\bibliographystyle{yahapj}                            
\bibliography{bibliography}

% \appendix -- only if needed

\end{document}

### 2019-01-18 src/bspline_fit_xyTmag_BIC_approach.py

@@ -1,0 +1,337 @@
+"""
+scatter plots of magnitudes vs various parameters... to see whether the EPD
+linear fitting approach works.
+"""
+import numpy as np, matplotlib.pyplot as plt, pandas as pd
+from glob import glob
+import os
+
+from astropy.io import fits
+
+from plot_mag_vs_EPD_parameters import get_data as small_get_data
+
+import seaborn as sns
+
+from scipy.interpolate import splprep, splev
+
+from numpy import array as nparr
+
+
+def homog_get_data(lctype='corner'):
+    # lctype = 'corner' or 'center'
+
+    lcdir = '../results/projid1030_lc_fit_check/{}_lcs'.format(lctype)
+    lcfiles = glob(os.path.join(lcdir, '*_llc.fits'))
+
+    datalist = []
+    for lcfile in lcfiles:
+        hdulist = fits.open(lcfile)
+        datalist.append(hdulist[1].data)
+
+    return lcfiles, datalist
+
+
+
+def make_pairplots(lcpaths, lcdatalist, magtype='IRM1', frac_of_lc=0.4,
+                   savdir='../results/bspline_fit_xyTmag/'):
+    # make pairplots of X,Y,T,MAG,S,D,K, and just X,Y,T,MAG
+    # frac_of_lc: for fitting purposes, we want orbit-specific data.
+
+    xcols = ['FSV','FDV','FKV','XIC','YIC','CCDTEMP',magtype]
+    xkeys = ['s','d','k','x','y','T',magtype]
+
+    for lcpath, lc in zip(lcpaths, lcdatalist):
+
+        savname = '{}_frac{:.1f}_pairplot_{}.png'.format(
+            magtype, frac_of_lc, os.path.splitext(os.path.basename(lcpath))[0])
+
+        savpath = os.path.join(savdir, savname)
+
+        if os.path.exists(savpath):
+            print('found {}, continue'.format(savpath))
+            continue
+
+        time = lc['TMID_UTC']
+        timeind = np.argsort(time)
+        d = {}
+        for xcol, k in zip(xcols, xkeys):
+            # pandas/seaborn wants little-endian
+            le_array = lc[xcol].byteswap().newbyteorder()
+            # sort everything by time
+            time_sorted_arr = le_array[timeind]
+            # take the cut so that you deal with orbit-specific data, if
+            # desired
[…]

### 2019-01-18 src/bspline_fit_xyTmag_crossval.py

@@ -1,0 +1,326 @@
+"""
+scatter plots of magnitudes vs various parameters... to see whether the EPD
+linear fitting approach works.
+"""
+import numpy as np, matplotlib.pyplot as plt, pandas as pd
+from glob import glob
+import os
+
+from astropy.io import fits
+
+from plot_mag_vs_EPD_parameters import get_data
+
+import seaborn as sns
+
+from scipy.interpolate import splprep, splev
+
+from numpy import array as nparr
+
+def make_pairplots(lcpaths, lcdatalist, magtype='IRM1', frac_of_lc=0.4):
+    # make pairplots of X,Y,T,MAG,S,D,K, and just X,Y,T,MAG
+    # frac_of_lc: for fitting purposes, we want orbit-specific data.
+
+    xcols = ['FSV','FDV','FKV','XIC','YIC','CCDTEMP',magtype]
+    xkeys = ['s','d','k','x','y','T',magtype]
+
+    for lcpath, lc in zip(lcpaths, lcdatalist):
+
+        savdir = '../results/bspline_fit_xyTmag/'
+        savname = '{}_frac{:.1f}_pairplot_{}.png'.format(
+            magtype, frac_of_lc, os.path.splitext(os.path.basename(lcpath))[0])
+        savpath = os.path.join(savdir, savname)
+
+        if os.path.exists(savpath):
+            print('found {}, continue'.format(savpath))
+            continue
+
+        time = lc['TMID_UTC']
+        timeind = np.argsort(time)
+        d = {}
+        for xcol, k in zip(xcols, xkeys):
+            # pandas/seaborn wants little-endian
+            le_array = lc[xcol].byteswap().newbyteorder()
+            # sort everything by time
+            time_sorted_arr = le_array[timeind]
+            # take the cut so that you deal with orbit-specific data, if
+            # desired
+            d[k] = time_sorted_arr[:int(frac_of_lc*len(time_sorted_arr))]
+
+        df = pd.DataFrame(d)
+
+        if np.all(pd.isnull(df[magtype])):
+            print('mags are all NaN for {}, continue'.format(savname))
+            continue
+
+        # PLOT X,Y,T,MAG,S,D,K
+        plt.close('all')
+
+        g = sns.PairGrid(df)
+        g = g.map_diag(plt.hist)
+        g = g.map_offdiag(plt.scatter, rasterized=True, s=10, alpha=0.8)
+
[…]

### 2019-01-18 src/collect_figures.sh

@@ -1,0 +1,15 @@
+#!/usr/bin/env bash
+
+##########################################
+# USAGE: ./collect_figures.sh
+##########################################
+
+fdir=../paper/figures/
+pdir=../paper/
+
+cp ${fdir}GI_figs/cluster_positions_ecliptic_scicase.pdf \
+   ${pdir}f1_PLACEHOLDER.pdf
+
+cp ${fdir}pipeline_figure.pdf ${pdir}f2.pdf
+
+echo "collected figures -> /paper/f?.pdf"

### 2019-01-18 src/collect_lightcurve_set.py

@@ -1,0 +1,91 @@
+import numpy as np, pandas as pd, matplotlib.pyplot as plt
+from glob import glob
+import os
+from shutil import copyfile
+
+from astropy.io import fits
+
+def collect_lightcurve_set(lcdir = '/home/luke/local/tess-trex/lightcurves'):
+    """
+    make file with x,y,Teff, and lc paths, for selection.
+    """
+
+    lcpaths = glob(os.path.join(lcdir,'*_llc.fits'))
+
+    _paths, _xcc, _ycc, _teff = [], [], [], []
+    for ix, lcpath in enumerate(lcpaths):
+
+        print('{}/{}'.format(ix, len(lcpaths)))
+
+        hdulist = fits.open(lcpath)
+
+        hdr = hdulist[0].header
+
+        _xcc.append(hdr['XCC'])
+        _ycc.append(hdr['YCC'])
+        _paths.append(lcpath)
+        _teff.append(hdr['teff_val'])
+
+    df = pd.DataFrame({'xcc':_xcc, 'ycc':_ycc, 'paths':_paths, 'teff':_teff})
+
+    outpath = '../data/projid1030_cam3_ccd3_lcinfo.csv'
+    df.to_csv(outpath, index=False)
+    print('saved {}'.format(outpath))
+
+
+def copy_lightcurves_mkdirs(lcinfopath):
+
+    df = pd.read_csv(lcinfopath)
+
+    sel_corner = (
+        (df['xcc'] > 250) & (df['xcc'] < 350)
+        &
+        (df['ycc'] > 250) & (df['ycc'] < 350)
+    )
+
+    sel_center = (
+        (df['xcc'] > 1650) & (df['xcc'] < 1750)
+        &
+        (df['ycc'] > 1650) & (df['ycc'] < 1750)
+    )
+
+    f,ax = plt.subplots()
+    ax.scatter(df['xcc'],df['ycc'],rasterized=True,s=3)
+    ax.set_xlabel('xcc')
+    ax.set_ylabel('ycc')
+    figpath = '../results/sanity_checks/lc_positions.png'
+    f.savefig(figpath)
+    print('saved {}'.format(figpath))
+
+    ##########################################
+    print('copying {} lcs from center'.format(len(df[sel_center])))
+    print('copying {} lcs from corner'.format(len(df[sel_corner])))
+
+    for inpath in df.loc[sel_center, 'paths']:
+        indir = os.path.dirname(inpath)
+        inname = os.path.basename(inpath)
[…]

### 2019-01-18 src/interpolate_nd_curve_splrep.py

@@ -1,0 +1,50 @@
+from scipy.interpolate import splprep, splev
+
+import numpy as np
+import matplotlib.pyplot as plt
+
+# make ascending spiral in 3-space
+t= np.linspace(0,1.75*2*np.pi,100)
+
+x = np.sin(t)
+y = np.cos(t)
+z = t
+
+# add noise
+x+= np.random.normal(scale=0.1, size=x.shape)
+y+= np.random.normal(scale=0.1, size=y.shape)
+z+= np.random.normal(scale=0.1, size=z.shape)
+
+# spline parameters
+s=3.0 # smoothness parameter
+k=2 # spline order
+nest=-1 # estimate of number of knots needed (-1 = maximal)
+
+# find the knot points
+tckp,u = splprep([x,y,z],s=s,k=k,nest=-1)
+
+# evaluate spline, including interpolated points
+xnew,ynew,znew = splev(np.linspace(0,1,400),tckp)
+
+plt.subplot(2,2,1)
+data,=plt.plot(x,y,'bo-',label='data')
+fit,=plt.plot(xnew,ynew,'r-',label='fit')
+plt.legend()
+plt.xlabel('x')
+plt.ylabel('y')
+
+plt.subplot(2,2,2)
+data,=plt.plot(x,z,'bo-',label='data')
+fit,=plt.plot(xnew,znew,'r-',label='fit')
+plt.legend()
+plt.xlabel('x')
+plt.ylabel('z')
+
+plt.subplot(2,2,3)
+data,=plt.plot(y,z,'bo-',label='data')
+fit,=plt.plot(ynew,znew,'r-',label='fit')
+plt.legend()
+plt.xlabel('y')
+plt.ylabel('z')
+
+plt.savefig('../results/fitting_experiments/splprep_demo.png')

### 2019-01-18 src/plot_EPD_parameters_vs_time.py

@@ -1,0 +1,180 @@
+"""
+scatter plots of magnitudes vs various parameters... to see whether the EPD
+linear fitting approach works.
+"""
+import numpy as np, matplotlib.pyplot as plt, pandas as pd
+from glob import glob
+import os
+
+from astropy.io import fits
+
+from bspline_fit_xyTmag_BIC_approach import homog_get_data
+
+from mpl_toolkits.axes_grid1 import make_axes_locatable
+
+def plot_flux_vs_EPD_param(lcpaths, lcdatalist, magtype='IRM1',
+                                frac_of_lc=1.0, savdir=None):
+
+    xcols = ['TMID_BJD','XIC','YIC','CCDTEMP','FSV','FDV','FKV','BGV']
+    xkeys = ['tmidbjd','x','y','T','s','d','k','bkgd']
+
+    for lcpath, lc in zip(lcpaths, lcdatalist):
+
+        savname = '{}_vs_EPDparams_frac{:.1f}_{}.png'.format(
+            magtype, frac_of_lc, os.path.splitext(os.path.basename(lcpath))[0])
+
+        savpath = os.path.join(savdir, savname)
+
+        if os.path.exists(savpath):
+            print('found {}, continue'.format(savpath))
+            continue
+
+        time = lc['TMID_UTC']
+
+        flux = lc[magtype]
+        timeind = np.argsort(time)
+        d = {}
+        for xcol, k in zip(xcols, xkeys):
+            # pandas/seaborn wants little-endian
+            le_array = lc[xcol].byteswap().newbyteorder()
+            # sort everything by time
+            time_sorted_arr = le_array[timeind]
+            # take the cut so that you deal with orbit-specific data, if
+            # desired
+            d[k] = time_sorted_arr[:int(frac_of_lc*len(time_sorted_arr))]
+
+        d[magtype] = flux[timeind][:int(frac_of_lc*len(time_sorted_arr))]
+
+        df = pd.DataFrame(d)
+
+        if np.all(pd.isnull(df[magtype])):
+            print('mags are all NaN for {}, continue'.format(savname))
+            continue
+
+        # PLOT flux vs each xcol.
+        plt.close('all')
+
+        fig,axs = plt.subplots(nrows=len(xcols), ncols=1, figsize=(6,6))
+        axs = axs.flatten()
+
+        cm = plt.cm.get_cmap('viridis')
+
+        timeval = np.array(df['tmidbjd'])
[…]

### 2019-01-18 src/plot_mag_vs_EPD_parameters.py

@@ -1,0 +1,130 @@
+"""
+scatter plots of magnitudes vs various parameters... to see whether the EPD
+linear fitting approach works.
+"""
+import numpy as np, matplotlib.pyplot as plt, pandas as pd
+from glob import glob
+import os
+
+from astropy.io import fits
+
+def get_data(n_lcs=10):
+    # return list of length n_lcs, where each element is a FITS_rec table
+    # containing all the needed information.
+
+    lcdir = '../data/lightcurves/'
+    lcfiles = glob(os.path.join(lcdir, '*_llc.fits'))
+
+    if len(lcfiles)>n_lcs:
+        lcfiles = np.random.choice(lcfiles, size=n_lcs, replace=False)
+    else:
+        pass
+
+    datalist = []
+    for lcfile in lcfiles:
+        hdulist = fits.open(lcfile)
+        datalist.append(hdulist[1].data)
+
+    return lcfiles, datalist
+
+
+def make_scatter_plots(lcpaths, lcdatalist, magtype='IRM1'):
+
+    xcols = ['FSV','FDV','FKV','XIC','YIC','CCDTEMP']
+    xkeys = ['s','d','k','x','y','T']
+    desiredx = ['s', 'd', 'k', 'x', 'y', 'T', 'decimal_x', 'decimal_y',
+                'sin(2pi*x)', 'sin(2pi*y)', 'cos(2pi*x)', 'cos(2pi*y)', 's^2',
+                'd^2', 'k^2', 's*d', 'd*k', 's*k']
+
+    for lcpath, lc in zip(lcpaths, lcdatalist):
+
+        d = {}
+        for xcol, k in zip(xcols, xkeys):
+            d[k] = lc[xcol]
+
+        for xstr in desiredx:
+
+            savdir = '../results/epd_parameter_selection/'
+            savname = '{}_vs_{}_{}.png'.format(
+                magtype, xstr, os.path.basename(lcpath))
+            savpath = os.path.join(savdir, savname)
+
+            if os.path.exists(savpath):
+                print('found {}, continue'.format(savpath))
+                continue
+
+            plt.close('all')
+            f,ax = plt.subplots(figsize=(4,3))
+
+            yval = lc[magtype]
+
+            if xstr in ['s','d','k','x','y','T']:
+                xval = d[xstr]
+
+            elif xstr == 'decimal_x':
+                xval = d['x'] - np.floor(d['x'])
+
+            elif xstr == 'decimal_y':
[…]

### 2019-01-18 src/robust_bspline_regression.py

@@ -1,0 +1,94 @@
+#!/usr/bin/env python
+"""
+Robust B-Spline regression with scikit-learn
+"""
+
+import matplotlib.pyplot as plt
+import numpy as np
+import scipy.interpolate as si
+from sklearn.base import TransformerMixin
+from sklearn.pipeline import make_pipeline
+from sklearn.linear_model import LinearRegression, RANSACRegressor,\
+                                 TheilSenRegressor, HuberRegressor
+
+from sklearn.metrics import mean_squared_error
+
+
+class BSplineFeatures(TransformerMixin):
+    def __init__(self, knots, degree=3, periodic=False):
+        self.bsplines = get_bspline_basis(knots, degree, periodic=periodic)
+        self.nsplines = len(self.bsplines)
+
+    def fit(self, X, y=None):
+        return self
+
+    def transform(self, X):
+        nsamples, nfeatures = X.shape
+        features = np.zeros((nsamples, nfeatures * self.nsplines))
+        for ispline, spline in enumerate(self.bsplines):
+            istart = ispline * nfeatures
+            iend = (ispline + 1) * nfeatures
+            features[:, istart:iend] = si.splev(X, spline)
+        return features
+
+
+def main():
+    np.random.seed(42)
+    X = np.random.uniform(low=-10, high=10, size=400)
+    x_predict = np.linspace(-10, 10, 1000)
+    y = np.sin(2 * np.pi * 0.1 * X) + 0.1*np.abs(X) + np.abs(np.arctan(X))
+    X_test = np.random.uniform(low=-30, high=30, size=200)
+    y_test = np.sin(2 * np.pi * 0.1 * X_test)
+
+    y_errors_large = y.copy()
+    y_errors_large[::10] = 6
+
+    # Make sure that X is 2D
+    X = X[:, np.newaxis]
+    X_test = X_test[:, np.newaxis]
+
+    # predict y
+    knots = np.linspace(-30, 30, 20)
+    bspline_features = BSplineFeatures(knots, degree=3, periodic=False)
+    estimators = [('Least-Square', '-', 'C0',
+                   LinearRegression(fit_intercept=False)),
+                  ('Theil-Sen', '-.', 'C1', TheilSenRegressor(random_state=42)),
+                  ('RANSAC', ':', 'C2', RANSACRegressor(random_state=42)),
+                  ('HuberRegressor', '--', 'C3', HuberRegressor())]
+
[…]

### 2019-01-30 src/bspline_fit_xyTmag_BIC_approach.py
bspline: minor changes

@@ -8,8 +8,6 @@ import os
 
 from astropy.io import fits
 
-from plot_mag_vs_EPD_parameters import get_data as small_get_data
-
 import seaborn as sns
 
 from scipy.interpolate import splprep, splev
@@ -17,16 +15,16 @@ from scipy.interpolate import splprep, splev
 from numpy import array as nparr
 
 
-def homog_get_data(lctype='corner'):
+def homog_get_data(lctype='corner', lcdir=None):
     # lctype = 'corner' or 'center'
 
-    lcdir = '../results/projid1030_lc_fit_check/{}_lcs'.format(lctype)
     lcfiles = glob(os.path.join(lcdir, '*_llc.fits'))
 
     datalist = []
     for lcfile in lcfiles:
         hdulist = fits.open(lcfile)
         datalist.append(hdulist[1].data)
+        hdulist.close()
 
     return lcfiles, datalist
 
@@ -140,9 +138,10 @@ def do_bspline_fit_xyTmag(lcpaths, lcdatalist, magtype='IRM1', frac_of_lc=0.4,
             magtype, frac_of_lc, os.path.splitext(os.path.basename(lcpath))[0])
         savpath = os.path.join(savdir, savname)
 
-        if os.path.exists(savpath):
-            print('found {}, continue'.format(savpath))
-            continue
+        #FIXME put in
+        # if os.path.exists(savpath):
+        #     print('found {}, continue'.format(savpath))
+        #     continue
 
         # find the knot points
         x = [nparr(df['x']), nparr(df['y']),
@@ -191,6 +190,7 @@ def do_bspline_fit_xyTmag(lcpaths, lcdatalist, magtype='IRM1', frac_of_lc=0.4,
             # _k: order
             _t,_c,_k = tckp
             coeffs, knots, order = tckp
+            import IPython; IPython.embed() #FIXME
 
             n_dim = 4
             n_data = len(x[0])

### 2019-01-30 src/collect_lightcurve_set.py
collect lightcurves: for projid 1088

@@ -1,3 +1,7 @@
+"""
+collects lightcurves from a given projid into "center" and "corner"
+directories.
+"""
 import numpy as np, pandas as pd, matplotlib.pyplot as plt
 from glob import glob
 import os
@@ -5,7 +9,7 @@ from shutil import copyfile
 
 from astropy.io import fits
 
-def collect_lightcurve_set(lcdir = '/home/luke/local/tess-trex/lightcurves'):
+def collect_lightcurve_set(lcdir=None, projidstr='projid1030_cam3_ccd3'):
     """
     make file with x,y,Teff, and lc paths, for selection.
     """
@@ -28,32 +32,46 @@ def collect_lightcurve_set(lcdir = '/home/luke/local/tess-trex/lightcurves'):
 
     df = pd.DataFrame({'xcc':_xcc, 'ycc':_ycc, 'paths':_paths, 'teff':_teff})
 
-    outpath = '../data/projid1030_cam3_ccd3_lcinfo.csv'
+    outpath = '../data/{}_lcinfo.csv'.format(projidstr)
     df.to_csv(outpath, index=False)
     print('saved {}'.format(outpath))
 
 
-def copy_lightcurves_mkdirs(lcinfopath):
+def copy_lightcurves_mkdirs(lcinfopath, projidstr=None, cam=None, ccd=None):
 
     df = pd.read_csv(lcinfopath)
 
-    sel_corner = (
-        (df['xcc'] > 250) & (df['xcc'] < 350)
-        &
-        (df['ycc'] > 250) & (df['ycc'] < 350)
-    )
+    if cam==3 and ccd==3:
+        sel_corner = (
+            (df['xcc'] > 250) & (df['xcc'] < 350)
+            &
+            (df['ycc'] > 250) & (df['ycc'] < 350)
+        )
 
-    sel_center = (
-        (df['xcc'] > 1650) & (df['xcc'] < 1750)
-        &
-        (df['ycc'] > 1650) & (df['ycc'] < 1750)
-    )
+        sel_center = (
+            (df['xcc'] > 1650) & (df['xcc'] < 1750)
+            &
+            (df['ycc'] > 1650) & (df['ycc'] < 1750)
+        )
+    elif cam==2 and ccd==2:
+        # NOTE: the x,y orientations must have a better description scheme :(
+        sel_corner = (
+            (df['xcc'] > 1650) & (df['xcc'] < 1750)
+            &
+            (df['ycc'] > 250) & (df['ycc'] < 350)
+        )
+
[…]

### 2019-01-30 src/plot_EPD_parameters_vs_time.py
update EPD parameter plots
timeseries, and magnitude correlation

@@ -1,6 +1,5 @@
 """
-scatter plots of magnitudes vs various parameters... to see whether the EPD
-linear fitting approach works.
+(mag, T, x, y, s, d, k, bgd) vs time
 """
 import numpy as np, matplotlib.pyplot as plt, pandas as pd
 from glob import glob
@@ -12,84 +11,10 @@ from bspline_fit_xyTmag_BIC_approach import homog_get_data
 
 from mpl_toolkits.axes_grid1 import make_axes_locatable
 
-def plot_flux_vs_EPD_param(lcpaths, lcdatalist, magtype='IRM1',
-                                frac_of_lc=1.0, savdir=None):
-
-    xcols = ['TMID_BJD','XIC','YIC','CCDTEMP','FSV','FDV','FKV','BGV']
-    xkeys = ['tmidbjd','x','y','T','s','d','k','bkgd']
-
-    for lcpath, lc in zip(lcpaths, lcdatalist):
-
-        savname = '{}_vs_EPDparams_frac{:.1f}_{}.png'.format(
-            magtype, frac_of_lc, os.path.splitext(os.path.basename(lcpath))[0])
-
-        savpath = os.path.join(savdir, savname)
-
-        if os.path.exists(savpath):
-            print('found {}, continue'.format(savpath))
-            continue
-
-        time = lc['TMID_UTC']
-
-        flux = lc[magtype]
-        timeind = np.argsort(time)
-        d = {}
-        for xcol, k in zip(xcols, xkeys):
-            # pandas/seaborn wants little-endian
-            le_array = lc[xcol].byteswap().newbyteorder()
-            # sort everything by time
-            time_sorted_arr = le_array[timeind]
-            # take the cut so that you deal with orbit-specific data, if
-            # desired
-            d[k] = time_sorted_arr[:int(frac_of_lc*len(time_sorted_arr))]
-
-        d[magtype] = flux[timeind][:int(frac_of_lc*len(time_sorted_arr))]
-
-        df = pd.DataFrame(d)
-
-        if np.all(pd.isnull(df[magtype])):
-            print('mags are all NaN for {}, continue'.format(savname))
-            continue
-
-        # PLOT flux vs each xcol.
-        plt.close('all')
-
-        fig,axs = plt.subplots(nrows=len(xcols), ncols=1, figsize=(6,6))
-        axs = axs.flatten()
-
[…]

### 2019-01-30 src/plot_mag_vs_EPD_parameters.py

@@ -1,6 +1,6 @@
 """
-scatter plots of magnitudes vs various parameters... to see whether the EPD
-linear fitting approach works.
+magnitude vs (time, T, x, y, s, d, k, bgd). for: single stars. and 4 chosen
+stars (for paper).
 """
 import numpy as np, matplotlib.pyplot as plt, pandas as pd
 from glob import glob
@@ -8,123 +8,300 @@ import os
 
 from astropy.io import fits
 
-def get_data(n_lcs=10):
-    # return list of length n_lcs, where each element is a FITS_rec table
-    # containing all the needed information.
+from bspline_fit_xyTmag_BIC_approach import homog_get_data
 
-    lcdir = '../data/lightcurves/'
-    lcfiles = glob(os.path.join(lcdir, '*_llc.fits'))
+from astrobase import lcmath
 
-    if len(lcfiles)>n_lcs:
-        lcfiles = np.random.choice(lcfiles, size=n_lcs, replace=False)
-    else:
-        pass
+def plot_mag_vs_EPD_parameters(lcpaths, lcdatalist, magtype='IRM1',
+                               get_norbits=1, expected_norbits=2, savdir=None):
 
-    datalist = []
-    for lcfile in lcfiles:
-        hdulist = fits.open(lcfile)
-        datalist.append(hdulist[1].data)
+    xcols = ['TMID_BJD','CCDTEMP','XIC','YIC','FSV','FDV','FKV']
+    xkeys = ['tmidbjd','T','x','y','s','d','k']
+    # could also include other parameters, like decimal_x, decimal_y,
+    # cross-terms...
+    desiredx = xkeys
 
-    return lcfiles, datalist
-
-
-def make_scatter_plots(lcpaths, lcdatalist, magtype='IRM1'):
-
-    xcols = ['FSV','FDV','FKV','XIC','YIC','CCDTEMP']
-    xkeys = ['s','d','k','x','y','T']
-    desiredx = ['s', 'd', 'k', 'x', 'y', 'T', 'decimal_x', 'decimal_y',
-                'sin(2pi*x)', 'sin(2pi*y)', 'cos(2pi*x)', 'cos(2pi*y)', 's^2',
-                'd^2', 'k^2', 's*d', 'd*k', 's*k']
+    if get_norbits not in [1]:
+        raise AssertionError('you usually only want to get 1 orbit')
 
     for lcpath, lc in zip(lcpaths, lcdatalist):
 
[…]

### 2019-01-30 paper/ms.tex
paper: update detrending procedure

@@
 image from MAST into a \texttt{fitsh}-compatible image by retrieving
-the image data (omitting the uncertainty map, for now). We then trim
-the image to remove virtual rows and columns (using the
-\texttt{SCIROWS}, \texttt{SCIROWE}, \texttt{SCCSA}, \texttt{SCCED},
-header values).  We then mask out saturated stars using the `fiign`
-program with a fixed saturation level of $2^{16}\,{\rm ADU}$.  As
-described by \citet{Pal_2009}, the mask is metadata to the image, and
-is not actually applied to the pixel values.  During masking, we also
-use the algorithm described by \citet{Pal_2009} to extend masks beyond
-purely satured pixels to ``bloomed'' pixels -- pixels horizontally and
-vertically adjacent to the saturated pixels.  Finally, for frames with
-the \texttt{DQUALITY} bit-flag set to 32~---~corresponding to the
+the image data, and omitting the uncertainty map. We then trim the
+image to remove virtual rows and columns using the \texttt{SCIROWS},
+\texttt{SCIROWE}, \texttt{SCCSA}, \texttt{SCCED}, header values.  We
+mask out saturated stars using the `fiign` program with a fixed
+saturation level of $2^{16}\,{\rm ADU}$.  As described by
+\citet{Pal_2009}, the mask is metadata to the image, and is not ever
+actually applied to the pixel values, except during specific image
+processing steps that follow.  During masking, we also use the
+algorithm described by \citet{Pal_2009} to extend masks beyond purely
+saturated pixels to ``bloomed'' pixels horizontally and vertically
+adjacent to the saturated pixels.  Finally, for frames with the
+\texttt{DQUALITY} bit-flag set to 32~---~corresponding to the
 ``momentum dumps'' described by \citet{vanderspek_2018}~---~we mask
@@
 shape parameters are later used when selecting an astrometric
-reference (\S~\ref{subsec:imagesubtraction})
+reference (\S~\ref{subsec:imagesubtraction}).
+We note that the fast focal ratio of the TESS cameras introduces
+significant comatic aberrations to the images, stars closer to the
+center of the field are more round; stars towards the edges are more
+triangular.
 
@@
 The second reference frame needed for image subtraction is the
-photometric reference.
-This is a high-SNR median average of frames that is used both to
-calculate the convolution kernel during image subtraction, and to
-measure the reference flux of each star.
+photometric reference.  Generically, if one were to simply subtract
+two arbitrary frames, the noise level in the resulting difference
+image would be $\sqrt{2}$ times greater than that in the original
+target frame.
+To minimize this effect, we create a high-SNR median average of
+$N$ selected frames, so that the noise level in the resulting
+subtracted images goes as $\sqrt{1+1/N}$.
+This ``photometric reference'' is used both to calculate the
+convolution kernel during image subtraction, and to measure the
+reference flux of each star.
 To select viable frames for inclusion in the photometric reference, we
@@
 
-The preceding tedium produces lightcurves that include both
-instrumental systematics as well as astrophysical variability.
-We perform two subsequent detrending steps:
-we decorrelate against known external parameters (EPD,
-\citealt{bakos_2010}) that we know affect the stellar flux
-measurements, and then we filter remaining systematic trends from
-unknown parameters (TFA, \citealt{kovacs_trend_2005}).  These
-procedures are the standard that have been adopted for the HAT group
-(see discussions from {\it e.g.}
-\citealt{huang_high-precision_2015,zhang_precision_2016}).
-We briefly summarize them here for self-consistency.
+The preceding steps produce lightcurves that include both instrumental
+systematics as well as astrophysical variability.  The detrending
+philosophy adopted by the HAT group typically proceeeds in two
+sequential stages (see discussions from {\it e.g.}
+\citealt{bakos_2010,huang_high-precision_2015,zhang_precision_2016}) .
+The first stage is to decorrelate against external parameters that are
+known to affect the stellar flux measurements (EPD,
+\citealt{bakos_2010}). The second stage is to filter remaining
+systematic trends caused by unknown parameters by decorrelating the
+measured brightnesses of stars against each other (TFA,
+\citealt{kovacs_trend_2005}).
 
-In ``external parameter decorrelation'', we fit the magnitude of each star
-as a function of parameters that we suspect may systematically affect
-the brightness counts.
-For instance, intra-pixel quantum efficiency variations can affect
-the measured stellar brightness as a function of the fractional
-centroid positions, $\{ x \}$ and $\{ y \}$, where $\{ x \} = x -
-\lfloor x \rfloor$, for $\lfloor \cdot \rfloor$ the floor function.
-Changes in the CCD electronics due to their temperature $T$ might
-matter.
-The fast focal ratio of the TESS cameras introduces significant
-comatic aberrations to the images, which affect the shape of the point
-spread function as a function of distance from the center of each
-camera's field; this might be at least superficially treated by
-allowing the elongated gaussian shape parameters $(S,D,K)$ to be free
-parameters.
+In general though, one must adapt detrending procedures to the data at
+hand.  In \S~\ref{sec:flux_vs_external_parameters}, we show that the
+``external parameter'' dependence visible in the TESS data is rather
+complex: ordinary linear model-fitting, as well as an initial attempts
+at non-linear model fitting, are poor descriptions of the data.  We go
+on to show (\S~\ref{sec:tfa_is_good_enough}) that a plausible
+detrending approach for the purpose of transit discovery is to simply
+decorrelate against other nearby stars with standard TFA.
 
-To chose among these free parameters, we plotted the magnitudes
-against each parameter in the vector $\theta' = (S,D,K,S^2,K^2, D^2,
-S\cdot D, S\cdot K, D\cdot K, x,y,\{x\},\{y\},T, \sin(2\pi x),
-\cos(2\pi x), \sin(2\pi
-y),\cos(2\pi y))$.
-We used the temperature from the on-chip aluminum-copper sensor
-measurements included in the engineering
-data\footnote{\url{archive.stsci.edu/missions/tess/engineering/}}.
+\subsubsection{Flux versus external parameters}
+\label{sec:flux_vs_external_parameters}
 
-%FIXME: what did we see? What did we fit for?
-We saw significant correlations for parameters X,Y, and Z.
+\begin{figure*}[t]
+	\begin{center}
+		\leavevmode
+		\includegraphics[width=0.7\textwidth]{f3.png}
+	\end{center}
+	\vspace{-0.5cm}
+	\caption{
+    {\bf Timeseries of ``external parameters'' for a representative
+    star.} {\it Top}: Instrumental raw magnitude (with a particular
+    aperture size), as a function of time.  {\it Second and third from
+    top}: $x$ and $y$ centroid positions as a function of time.
+    Continuing in order are the CCD temperature, the $(s,d,k)$ shape
+    parameters, and the measured background value.
+    Most of the apparent variability is instrumental: see
+    \S~\ref{sec:flux_vs_external_parameters}.
+		\label{fig:external_parameter_timeseries}
+	}
+\end{figure*}
 
-We then fit the following model to the magnitudes $m$:
+\begin{figure*}[t]
+    \begin{center}
+		\includegraphics[height=0.97\textheight]{f4.png}
+    \end{center}
+    \vspace{-0.8cm}
+    \caption{
+      {\bf Flux as a function of ``external parameters'' for four
+      representative stars.} The left two columns are stars at the
+      corner of a camera's field; the right two columns are from the
+      centers.
+      Each row shows a different parameter along the $x$-axis, given
+      in text at the bottom right of each subplot.
+      ``Hooks'' are common features in flux as a function of
+      temperature and centroid position.
+      \S~\ref{sec:flux_vs_external_parameters} gives a verbose
+      description.
+     \label{fig:flux_vs_external_parameters}
+    }
+\end{figure*}
+
+The traditional approach to EPD 
+\citep[][]{Pal_2009,bakos_2010,zhang_precision_2016} is to fit and
+subtract a model of the form
+
 \begin{equation}
-  m = {\rm const.} + \sum_i \theta_i,
+  m = {\rm const.} + \sum_i c_i \theta_i,
+  \label{eq:classical_EPD}
 \end{equation}
-for 
-$\theta = (S,D,K,S^2,K^2, D^2, S\cdot D, S\cdot K, D\cdot K,
-x,y,\{x\},\{y\},T, \sin(2\pi x), \cos(2\pi x), \sin(2\pi y),\cos(2\pi
-y))$.
-We optimized via least-squares, and subtracted the maximum-likelihood
-model to produce ``EPD'' lightcurves.
 
-In ``trend filtering'', we correlate the flux timeseries of each star
+where $\vec{\theta}$ is a vector of parameters such as the shape
+parameters $(s,d,k)$, their products $(s^2, s\cdot d, d^2, \ldots)$,
+the temperature $T$ of the CCDs\footnote{ We used the temperature from
+the on-chip aluminum-copper sensor measurements included in the
+engineering
+data\footnote{\url{archive.stsci.edu/missions/tess/engineering/}}.  },
+the centroid positions $(x,y)$, the fractional part of the
+centroid positions $(\{x\},\{y\})$, and any other parameters that are
+expected\footnote{ The fractional centroid positions might matter
+because intra-pixel quantum efficiency variations could affect the
+measured stellar brightness.  The varying temperature $T$ of the CCD
+electronics might matter.  } to correlate strongly with the observed
+flux.  The coefficients $c_i$ are calculated through linear
+least-squares, and subtracted to produce ``EPD'' lightcurves.
+
+The premise of this model is that the correlations between the
+magnitudes and these external parameters are linear.  For ground-based
+CCD data (e.g., HATNet, HATS, and Nikon DSLRs), \citet{bakos_2010} and
+\citet{zhang_precision_2016} have verified that this model is a
+reasonable fit to the data.
+
+To discern whether such a model describes the TESS data, we examined scatter 
+plots of each
+parameter, as a function of all the other parameters.  We also
+examined plots of each parameter as a function of time.
+A few prominent trends were present.
+
+\begin{enumerate}
+
+\item {\it Flux vs. time}. Most of the lightcurves we examined showed a secular
+    drift with amplitude $0.01\,{\rm mag}$ over the timescale of each
+    orbit.  Sharper trends (``hooks'') at the beginning of each orbit
+    seemed to be less prominent for stars at the corners of the fields
+    than stars at the center.  The periodicity incurred by the
+    2.5$\,{\rm day}$ momentum dumps was also noticeable in more of the
+    lightcurves at the center of the field than at the corners.
+
+\item {\it Flux vs. centroid positions}. The flux as a function of
+  centroid position often showed non-linear ``hooks'' (see Figure
+    \ref{fig:flux_vs_external_parameters}). Most of the data points from a 
+    given orbit reside at a given
+    level, but about 10\% are in a tail. This was seen in lightcurves
+    all across the TESS field of view.
+
+\item {\it Flux vs. temperature} exhibited similar hooks, with most of
+  the flux values residing at a particular level, and perhaps 10\%
+    following a non-linear path (often resembling the Nike ``swoosh'')
+    away from the bulk of points.
+
+\item {\it Flux vs. shape parameters}.  For lightcurves in the corner
+  of the field of view, similar hooks are present in flux {\it vs.}
+    $(s,d,k)$, though the hooks are less sharp.  In the center of the
+    field of view, gaussian ellipses are a better description of the
+    flux {\it vs.} the shape parameters.
+
+\end{enumerate}
+
+Considering the timeseries of parameters other than flux 
+(Figure~\ref{fig:external_parameter_timeseries}):
+
+\begin{enumerate}
+
+\item {\it Centroid positions vs. time}.  The main variability in the
+  centroid positions as a function of time is a secular drift, that is
+    reset every orbit.  The 2.5 day momentum wheel dump is
+    superimposed on this secular drift, and has smaller amplitude than
+    the drift.
+
+\item {\it Temperature vs. time}.  The main variability in temperature
+  {\it vs.} time is a secular drift of the same timescale as that for
+    the centroid positions timeseries.
+
+\item {\it Shape parameters vs. time}.  The main variability in the
+  shape parameters as a function of time is the 2.5 day momentum wheel
+    dump periodicity, with hooks before each momentum dump.
+
+\item {\it Background value vs. time}.  The background is typically stable, 
+except when scattered light from the Earth or Moon enters the frame (visible 
+towards the end of each orbit in 
+Figure~\ref{fig:external_parameter_timeseries}).
+
+\end{enumerate}
+
+Given the characteristics of the variability, a linear model of the
+form given in Equation~\ref{eq:classical_EPD} is not applicable.  To
+fit out the correlations between flux and parameters which most
+commonly exhibited ``hooks'', we explored fitting a parametric open
+curve (an $N$-dimensional B-spline, \citealt{dierckx_curve_1996}) to
+the flux, centroid positions, and temperatures simultaneously.  We
+selected the number of knots through brute-force, by calculating
+$\chi^2$ for the model fit of a grid of knots, and minimizing the
+Bayesian Information Criterion.  Though this approach showed some
+initial promise, even with ``optimal'' knot-selection (in the BIC
+sense) it introduced undesirable residuals in the lightcurves, and
+also distorted transits.
+
+Given these complications, for the time being we omit the step of
+``detrending'' as a function of external parameters. To
+enable further exploration of the issue, we include all the necessary
+vectors of {\it e.g.}, centroid positions, temperatures, and shape
+parameters in our reported lightcurves.
+
+\subsubsection{Trend filtering algorithm}
+\label{sec:tfa_is_good_enough}
+
+Since most of the external parameter dependence is shared between
+stars, we opt to decorrelate the flux timeseries of each star
 against other stars in the frame (TFA, \citealt{kovacs_trend_2005}).
+
+%TODO: write out the procedure, give a model equation!
+
 This requires selecting ``template stars'', which are a subsample of

### 2019-01-30 src/plot_exoplanetarchive_Rp_vs_P_age_cuts.py
add src/plot_exoplanetarchive_Rp_vs_P_age_cuts.py

@@ -1,0 +1,153 @@
+import numpy as np, matplotlib.pyplot as plt, pandas as pd
+from glob import glob
+import os
+
+from numpy import array as nparr
+
+from astroquery.nasa_exoplanet_archive import NasaExoplanetArchive
+
+from datetime import datetime
+
+def plot_exoplanetarchive_Rp_vs_P_age_cuts(whichcut='none'):
+
+    tab = NasaExoplanetArchive.get_confirmed_planets_table(all_columns=True)
+
+    f,ax = plt.subplots(figsize=(6,4))
+
+    xval = nparr(tab['pl_orbper'])
+    yval = nparr(tab['pl_rade'])
+
+    age = nparr(tab['st_age'])
+    age_perr = nparr(tab['st_ageerr1'])
+    age_merr = nparr(tab['st_ageerr2'])
+
+    age_err = np.maximum(age_perr, np.abs(age_merr))
+
+    transits = nparr(tab['pl_tranflag']).astype(bool)
+
+    sel = (
+        np.isfinite(xval) & (xval > 0)
+        &
+        np.isfinite(yval) & (yval > 0)
+        &
+        transits
+    )
+    if whichcut in ['finiteage', 'sigmatau_by_tau_pt5', 'sigmatau_by_tau_pt2',
+                   'age_lt_1Gyr', 'age_gt_10Gyr', 'age_gt_8Gyr',
+                    'age_lt_500Myr', 'age_lt_100Myr']:
+        sel &= np.isfinite(age)
+        sel &= (age>0)
+        sel &= np.isfinite(age_perr)
+        sel &= (age_perr>0)
+        sel &= np.isfinite(age_merr)
+        sel &= (np.abs(age_merr)>0)
+    if whichcut=='sigmatau_by_tau_pt5':
+        sel &= (age_err/age < 0.5)
+    if whichcut=='sigmatau_by_tau_pt2':
+        sel &= (age_err/age < 0.2)
+    if whichcut.endswith('Gyr'):
+        cutval = int(whichcut.split('Gyr')[0].split('_')[-1])
+        if '_gt_' in whichcut:
+            sel &= age > cutval
+        elif '_lt_' in whichcut:
+            sel &= age < cutval
+    if whichcut.endswith('Myr'):
+        cutval_Myr = int(whichcut.split('Myr')[0].split('_')[-1])
+        cutval = (cutval_Myr / 1e3)
[…]

### 2019-01-30 src/collect_figures.sh
update "collect figures" script

@@ -7,9 +7,22 @@
 fdir=../paper/figures/
 pdir=../paper/
 
+# placeholder for positions of clusters
 cp ${fdir}GI_figs/cluster_positions_ecliptic_scicase.pdf \
    ${pdir}f1_PLACEHOLDER.pdf
 
+# placeholder for what our pipeline does
 cp ${fdir}pipeline_figure.pdf ${pdir}f2.pdf
 
-echo "collected figures -> /paper/f?.pdf"
+
+
+lcdir=../results/projid1088_cam2_ccd2_lcs/center_lcs/
+# plot of (mag,x,y,T,s,d,k,bkgd) vs time
+cp ${lcdir}EPDparams_vs_time_frac1.0_4979427719678442752_llc.png ${pdir}f3.png
+
+# plot of mag vs (t,T,x,y,s,d,k) for four stars
+lcdir=../results/projid1088_cam2_ccd2_lcs/
+cp ${lcdir}IRM1_vs_EPD_parameters_fourstars_norbit1.png ${pdir}f4.png
+
+
+echo "collected figures -> /paper/f?.pdf -> /paper/f?.png"

### 2019-02-01 src/optimizing_pipeline_parameters.py
add optimizing_pipeline_parameters.py

@@ -1,0 +1,538 @@
+import numpy as np, pandas as pd, matplotlib.pyplot as plt
+import os, pickle, subprocess, itertools
+from numpy import array as nparr
+from glob import glob
+
+from matplotlib.ticker import MultipleLocator, FormatStrFormatter
+
+def scp_rms_percentile_files(statsdir, outdir):
+
+    if not os.path.exists(outdir):
+        os.mkdir(outdir)
+        print('made {}'.format(outdir))
+
+    p = subprocess.Popen([
+        "scp", "lbouma@phn12:{}/percentiles_RMS_vs_med_mag*.csv".format(statsdir),
+        "{}/.".format(outdir),
+    ])
+    sts = os.waitpid(p.pid, 0)
+
+    return 1
+
+
+def scp_knownplanets(statsdir, outdir):
+
+    if not os.path.exists(outdir):
+        os.mkdir(outdir)
+        print('made {}'.format(outdir))
+
+    p = subprocess.Popen([
+        "scp", "lbouma@phn12:{}/*-0*/*_TFA*_snr_of_fit.csv".format(statsdir),
+        "{}/.".format(outdir),
+    ])
+    sts = os.waitpid(p.pid, 0)
+
+    return 1
+
+
+
+def get_rms_file_dict(projids, camccdstr, ap='TF1'):
+
+    d = {}
+    for projid in projids:
+
+        run_id = "{}-{}".format(camccdstr, projid)
+        indir = (
+            '../results/optimizing_pipeline_parameters/{}_stats'.format(run_id)
+        )
+        inpath = os.path.join(
+            indir, "percentiles_RMS_vs_med_mag_{}.csv".format(ap))
+
+        d[projid] = pd.read_csv(inpath)
+
+    return d
+
+
+def get_knownplanet_file_dict(projids, camccdstr, ap='TFA1'):
+
+    d = {}
+    for projid in projids:
+
+        d[projid] = {}
+
+        run_id = "{}-{}".format(camccdstr, projid)
+        indir = (
+            '../results/optimizing_pipeline_parameters/{}_knownplanets'.format(run_id)
+        )
+
+        inpaths = glob(
+            os.path.join(
+                indir, "*-0*_{}_snr_of_fit.csv".format(ap)
+            )
+        )
+
+        for inpath in inpaths:
+
+            toi_id = str(
+                os.path.basename(inpath).split('_')[0].replace('-','.')
+            )
+
+            d[projid][toi_id] = pd.read_csv(inpath)
+
+    return d
+
+
[…]

### 2019-02-01 src/get_camera_orientations.py
(redundant) tools to clarify camera orientations
it's already in the data release notes

@@ -1,0 +1,64 @@
+from astropy.io import fits
+from astropy.coordinates import SkyCoord
+from astropy import units as u
+
+import numpy as np, pandas as pd
+import os
+from glob import glob
+from parse import search
+from numpy import array as nparr
+
+def main(sectorstr="s0002"):
+
+    ffidir = (
+        '/home/luke/local/tess-trex/fullframeimages/set_single_time_{}'.
+        format(sectorstr)
+    )
+
+    ffipaths = glob(os.path.join(ffidir, 'tess*_ffir.fits'))
+
+    cams,ccds,crval1s,crval2s = [],[],[],[]
+    for ffipath in ffipaths:
+
+        sr = search("{}-s{}-{}-{}-{}.fits", os.path.basename(ffipath))
+        cam = int(sr[2])
+        ccd = int(sr[3])
+
+        hdulist = fits.open(ffipath)
+        hdr = hdulist[1].header
+
+        crval1 = hdr['CRVAL1']
+        crval2 = hdr['CRVAL2']
+
+        hdulist.close()
+
+        cams.append(cam)
+        ccds.append(ccd)
+        crval1s.append(crval1)
+        crval2s.append(crval2)
+
+    ra = nparr(crval1s)
+    dec = nparr(crval2s)
+    c = SkyCoord(ra*u.deg, dec*u.deg, frame='icrs')
+    elon = nparr(c.barycentrictrueecliptic.lon.value)
+    elat = nparr(c.barycentrictrueecliptic.lat.value)
+
+    df = pd.DataFrame(
+        {'cam':nparr(cams), 'ccd':nparr(ccds),
+         'crval_ra':ra, 'crval_dec':dec,
+         'crval_elon':elon, 'crval_elat':elat
+        }
+    )
+
+    outdir = '../results/camera_orientations/'
+    outname = '{}_orientations.csv'.format(sectorstr)
+    outpath = os.path.join(outdir, outname)
+
+    df.to_csv(outpath, index=False)
+    print('made {}'.format(outpath))
+
+if __name__=="__main__":
+
+    sectorstr='s0002'
+
+    main(sectorstr=sectorstr)

### 2019-02-01 src/plot_camera_orientations.py

@@ -1,0 +1,35 @@
+import os
+import numpy as np, pandas as pd
+from tessmaps import tessmaps as tm
+
+from astropy.coordinates import SkyCoord
+from astropy import units as u
+
+def main(sectorstr='s0002'):
+
+    datadir = '../results/camera_orientations/'
+    datapath = os.path.join(datadir,'{}_orientations.csv'.format(sectorstr))
+    df = pd.read_csv(datapath)
+
+    elons, elats = df['crval_elon']*u.deg, df['crval_elat']*u.deg
+    coords = SkyCoord(lon=elons, lat=elats, frame='barycentrictrueecliptic')
+
+    names = np.array(
+        [str(cam)+'-'+str(ccd) for cam, ccd in zip(df['cam'],df['ccd'])]
+    )
+
+    annotate = np.ones_like(names).astype(bool)
+
+    savname = '{}_orientations.png'.format(sectorstr)
+    savdir = '../results/camera_orientations/' # fix this to your preferred directory!
+    title = 'camera ccd orientations'
+    sector_number = 1
+
+    tm.make_rect_map(sector_number, coords, names=names,
+                     annotate_bools=annotate, title=title,
+                     bkgnd_cmap='Blues', savname=savname, savdir=savdir)
+
+    print('if you got here w/out errors, it worked!')
+
+if __name__=="__main__":
+    main()

### 2019-02-01 paper/ms.tex
minor paper improvements

@@
 
-\title{Homogeneous Light Curves for Stars in Clusters from TESS}
+\title{Homogeneous Light Curves for Stars in Clusters from TESS:
+Method \& Sector 1-4 Data Release}
 
@@
 steps using stand-alone programs.  A conceptual overview of our
-``pipeline'' is given in Figure~\ref{fig:pipeline}.  Similar pipelines
-have been presented by \citet{Pal_2009},
-\citet{soares-furtado_image_2017} and \citet{oelkers_precision_2018}.
+``pipeline'' is given in Figure~\ref{fig:pipeline}.  
+Our overall method is in the spirit of the reduction approaches used
+by \citet{Pal_2009}, \citet{soares-furtado_image_2017} and
+\citet{oelkers_precision_2018}.
 
@@
 photometric reference by stacking a collection of frames, and then
-convolve all the transformed frames to match the photometric reference,
+convolve all the transformed frames to the photometric reference,
 and subtract (\S~\ref{subsec:imagesubtraction}).  We perform aperture
@@
 frame from Gaia DR2.  We detrend the resulting lightcurves
-(\S~\ref{subsec:lcdetrending}) in two subsequent steps.  First, we apply
-External Parameter Decorrelation (EPD, \citealt{bakos_2010}), and then
-we apply a Trend Filtering Algorithm (TFA, \citealt{kovacs_trend_2005}).
-Finally, we assess the resulting lightcurves using a variety of
-statistics for their white noise and red noise properties
-(\S~\ref{sec:results}).
+(\S~\ref{subsec:lcdetrending}), and then assess the resulting
+lightcurves using a variety of statistics for their white noise and
+red noise properties (\S~\ref{sec:results}).
 
@@
 image (FFI).  Each TESS camera reads out every 2 seconds.  To produce
-a manageable telemetric load, the resulting pixel values are summed by
-the onboard computer into 30 minute averages. (An on-board cosmic ray
-mitigation algorithm is applied.) Once transmitted to the ground, the
-raw images are calibrated by the Science Processing Operations Center.
-The calibration process includes an overscan, bias, and dark current
-correction, and also dividing out a flat field.  The details are given by
-\citet{clarke_kepler_2017}, and the resulting science data products are
-described by \citet{tess_data_product_description_2018}.
+a manageable telemetric load, the resulting pixel values are averaged
+by the onboard computer into 30 minute exposures. (An on-board cosmic
+ray mitigation algorithm is applied.) Once transmitted to the ground,
+the raw images are calibrated by the Science Processing Operations
+Center.  The calibration process includes an overscan, bias, and dark
+current correction, and also dividing out a flat field.  The details
+are given by \citet{clarke_kepler_2017}, and the resulting science
+data products are described by
+\citet{tess_data_product_description_2018}.
 
@@
 extraction, we also fit elongated gaussians to the bright stars,
-yielding the shape parameters (S,D,K), where the flux as a function of
-position is assumed to take the form
+yielding the shape parameters $(s,d,k)$, where the flux as a function
+of position is assumed to take the form
 \begin{align}
   f_{\rm elong}(\vec{x}) &= B + A \exp \{ -0.5 \times ( 
-    S(\Delta x^2 + \Delta y^2) + \\
-    &D(\Delta x^2 - \Delta y^2) +
-    K(2\Delta x \Delta y)
+    s(\Delta x^2 + \Delta y^2) + \\
+    \nonumber
+    &d(\Delta x^2 - \Delta y^2) +
+    k(2\Delta x \Delta y)
   )  \},
 \end{align}
-for $\Delta x = x-x_0$, and $\Delta y = y - y_0$.  $S$ is typically
-called the ``sharpness''.  For a nearly circular shape profile, ${\rm
-FWHM} \approx 2.35\sqrt{S}$ \citep[{\it e.g.},][]{Pal_2009}.  These
-shape parameters are later used when selecting an astrometric
-reference (\S~\ref{subsec:imagesubtraction}).
-We note that the fast focal ratio of the TESS cameras introduces
-significant comatic aberrations to the images, stars closer to the
-center of the field are more round; stars towards the edges are more
-triangular.
+for $\Delta x = x-x_0$, and $\Delta y = y - y_0$.  For a nearly
+circular shape profile, the sharpness $s$ is related to the FWHM as
+${\rm FWHM} \approx 2.35\sqrt{s}$ \citep[{\it e.g.},][]{Pal_2009}.
+These shape parameters are later used when selecting an astrometric
+reference (\S~\ref{subsec:imagesubtraction}).  We note that the fast
+focal ratio of the TESS cameras introduces significant comatic
+aberrations to the images: stars closer to the center of the field are
+more round, while stars towards the edges are more triangular.
 
@@
 \texttt{gaia2read}\footnote{\url{github.com/samuelyeewl/gaia2read}}
-(CITE Jason Kim junior thesis).
+\citep{kim_2018_gaia2read}.
 
@@
 \label{subsec:imagesubtraction}
+
+The core operation of ``classical'' image subtraction
+attempts to match a photometric reference $R$ and a target image $I$ by 
+computing a convolution kernel.
+The kernel, once applied to the high signal-to noise reference,
+produces a model image, $M_{xy}$,
+\begin{equation}
+    M_{xy} = (R \otimes K)_{xy} + B_{xy},
+\end{equation}
+where $B_{xy}$ is a component of the model image that allows for
+background variations.
+The convolution kernel $K$ is typically decomposed onto a
+basis, $K = \sum_i c_i K_i$, and the coefficients are found
+by minimizing
+\begin{equation}
+    \chi^2 = \sum_{xy} \left( \frac{I_{xy} - M_{xy}}{\sigma_{xy}} \right)^2,
+\end{equation}
+where $\sigma_{xy}$ is the uncertainty in the target image pixel values.
+Photometry is then performed on the difference image $D_{xy}$, where
+$D_{xy} = I_{xy} - M_{xy}$.
+
+% FIXME: describe gaussian kernel (used in e.g., KELT, and maybe other 
+%pipelines?). Perhaps give Eqns for delta kernel.
+The choice of kernel ...
 
@@
     \begin{center}
-		\includegraphics[height=0.97\textheight]{f4.png}
+		\includegraphics[height=0.95\textheight]{f4.png}
     \end{center}
@@
 \citep[][]{Pal_2009,bakos_2010,zhang_precision_2016} is to fit and
-subtract a model of the form
+subtract a model for the magnitudes $m$ of the form
 
@@
 parameters $(s,d,k)$, their products $(s^2, s\cdot d, d^2, \ldots)$,
-the temperature $T$ of the CCDs\footnote{ We used the temperature from
-the on-chip aluminum-copper sensor measurements included in the
-engineering
+the temperature $T$ of the instrument or environment\footnote{ We used
+the temperature from the on-chip aluminum-copper sensor measurements
+included in the engineering
 data\footnote{\url{archive.stsci.edu/missions/tess/engineering/}}.  },
@@
 The premise of this model is that the correlations between the
-magnitudes and these external parameters are linear.  For ground-based
+magnitudes and the external parameters are linear.  For ground-based
 CCD data (e.g., HATNet, HATS, and Nikon DSLRs), \citet{bakos_2010} and
 \citet{zhang_precision_2016} have verified that this model is a
-reasonable fit to the data.
+reasonable description to the data.
 
-To discern whether such a model describes the TESS data, we examined scatter 
-plots of each
-parameter, as a function of all the other parameters.  We also
-examined plots of each parameter as a function of time.
-A few prominent trends were present.
+To discern whether such a model extends to the TESS data, we examined
+scatter plots of each parameter, as a function of all the other
+parameters.  We also examined plots of each parameter as a function of
+time.  A few prominent trends were present.
 
@@
 selected the number of knots through brute-force, by calculating
-$\chi^2$ for the model fit of a grid of knots, and minimizing the
-Bayesian Information Criterion.  Though this approach showed some
-initial promise, even with ``optimal'' knot-selection (in the BIC
-sense) it introduced undesirable residuals in the lightcurves, and
-also distorted transits.
+$\chi^2$ for the model fit over a grid of possible knots, and
+minimizing the Bayesian Information Criterion.  Though this approach
+showed some initial promise, even with ``optimal'' knot-selection (in
+the BIC sense) it introduced undesirable residuals in the lightcurves,
+and also distorted transits.
 

### 2019-02-01 src/plot_exoplanetarchive_Rp_vs_P_age_cuts.py
minor

@@ -131,7 +131,10 @@ def plot_exoplanetarchive_Rp_vs_P_age_cuts(whichcut='none'):
         transform=ax.transAxes
     )
 
-    savpath = '../results/exoplanetarchive_Rp_vs_P_cut{}.png'.format(whichcut)
+    savdir = '../results/exoplanet_archive_age_cut_plots/'
+    savpath = os.path.join(
+        savdir,'exoplanetarchive_Rp_vs_P_cut{}.png'.format(whichcut)
+    )
     f.savefig(savpath, bbox_inches='tight', dpi=400)
     print('made {}'.format(savpath))
 

### 2019-03-03 src/optimizing_pipeline_parameters.py
best snr: made cleaner by adding "bad TOI" list

@@ -93,10 +93,10 @@ def plot_rms_comparison(d, projids, camccdstr, expmtstr, overplot_theory=True,
 
     fig,ax = plt.subplots(figsize=(4,3))
 
-    pctiles = [2,25,50,75,98]
+    pctiles = [25,50,75]
 
     defaultcolors = plt.rcParams['axes.prop_cycle'].by_key()['color']
-    defaultlines = ['-.','-',':','--']
+    defaultlines = ['-.','-',':','--']*2
     if len(projids) > len(defaultcolors):
         raise NotImplementedError('need a new color scheme')
     if len(projids) > len(defaultlines):
@@ -111,7 +111,7 @@ def plot_rms_comparison(d, projids, camccdstr, expmtstr, overplot_theory=True,
 
         run_id = "{}-{}".format(camccdstr, projid)
 
-        for ix, ls in zip([1,2,3], linestyles):
+        for ix, ls in zip([0,1,2], linestyles):
 
             midbins = nparr(d[projid].iloc[ix].index).astype(float)
             rms_vals = nparr(d[projid].iloc[ix])
@@ -220,6 +220,13 @@ def plot_knownplanet_comparison(d, projids, camccdstr, expmtstr, apstr='TFA1',
 
     # some projids have different numbers of TOIs. they will get nans.
     utois = np.sort(np.unique(np.concatenate(temp_tois)))
+
+    # some TOIs are "bad" and need to be filtered. (e.g., if they have
+    # systematics that mess with BLS, and so you dont want them in this
+    # comparison). NOTE: these are manually appended.
+    manual_bad_tois = ['243', '354', '359']
+    utois = [u for u in utois if u.split('.')[0] not in manual_bad_tois]
+
     n_tois = len(utois)
 
     arr = np.zeros((n_projids, n_tois))
@@ -393,11 +400,11 @@ if __name__=="__main__":
     # select your option from the boolean ones below. input your projids and
     # cam/ccd pairs.
 
-    scp_projid_pickle_parameters = 0 # scp the projid pickle descriptions to local
-    scp_rms_files = 0 # scp the RMS percentile csv files to local
-    scp_knownplanet_files = 0
+    scp_projid_pickle_parameters = 1 # scp the projid pickle descriptions to local
[…]

### 2019-03-03 paper/ms.tex
paper updates

@@
 
-\title{Homogeneous Light Curves for Stars in Clusters from TESS:
-Method \& Sector 1-4 Data Release}
+\title{
+  The Cluster Difference Imaging Photometric Survey (CDIPS).
+  I. Methods \& Light Curves from TESS Sectors 1-5
+}
 
@@
 $\approx$$28$ degrees in ecliptic longitude every lunar month.  Data
-acquired throughout each ``sector'' is downlinked at spacecraft
+acquired throughout each ``sector'' are downlinked at spacecraft
 perigee through the Deep Space Network.  Verbose descriptions of the
@@
 a manageable telemetric load, the resulting pixel values are averaged
-by the onboard computer into 30 minute exposures. (An on-board cosmic
-ray mitigation algorithm is applied.) Once transmitted to the ground,
-the raw images are calibrated by the Science Processing Operations
-Center.  The calibration process includes an overscan, bias, and dark
-current correction, and also dividing out a flat field.  The details
-are given by \citet{clarke_kepler_2017}, and the resulting science
-data products are described by
-\citet{tess_data_product_description_2018}.
+by the onboard computer into 30 minute exposures. An on-board cosmic
+ray mitigation algorithm is applied (CITE: BERTA-THOMPSON). Once
+transmitted to the ground, the raw images are calibrated by the
+Science Processing Operations Center.  The calibration process
+includes an overscan, bias, and dark current correction, and also
+divides out a flat field.  The details are given by
+\citet{clarke_kepler_2017}, and the resulting science data products
+are described by \citet{tess_data_product_description_2018}.
 
@@
 
-\subsection{Preparatory Steps}
+\subsection{Image Preparation \& Background Removal}
 \label{subsec:preparation}
@@
 
-The first is to trim and mask the images.  We convert the calibrated
-image from MAST into a \texttt{fitsh}-compatible image by retrieving
-the image data, and omitting the uncertainty map. We then trim the
-image to remove virtual rows and columns using the \texttt{SCIROWS},
-\texttt{SCIROWE}, \texttt{SCCSA}, \texttt{SCCED}, header values.  We
-mask out saturated stars using the `fiign` program with a fixed
-saturation level of $2^{16}\,{\rm ADU}$.  As described by
-\citet{Pal_2009}, the mask is metadata to the image, and is not ever
-actually applied to the pixel values, except during specific image
-processing steps that follow.  During masking, we also use the
-algorithm described by \citet{Pal_2009} to extend masks beyond purely
-saturated pixels to ``bloomed'' pixels horizontally and vertically
-adjacent to the saturated pixels.  Finally, for frames with the
-\texttt{DQUALITY} bit-flag set to 32~---~corresponding to the
-``momentum dumps'' described by \citet{vanderspek_2018}~---~we mask
-out the entire frame.  This removes on average a few frames per
-sector. Through visual inspection, we see that the stars on these
-frames are extremely smeared, and are unlikely to produce useful
-science data.
+First, we trim the images.  We convert the calibrated image from MAST
+into a single-extension FITS image, trimmed to remove virtual rows and
+columns using the \texttt{SCIROWS}, \texttt{SCIROWE}, \texttt{SCCSA},
+and \texttt{SCCED} header values.
+
+Second, we estimate the background of each frame.  We do this by
+temporarily masking out pixels more than $2\sigma$ from the median,
+and then passing a $48\times48$ median box filter over each pixel in
+the image, using reflective boundary conditions. We subtract out this
+smooth background estimate from each image.  This step helps mitigate
+two unwanted image artifacts.  First, it removes a low-level glow
+present in the corners of many images, which remains even after
+flat-fielding \citep[see][\S 7.3.5]{vanderspek_2018}.  Second,
+background subtraction removes scattered light patches from the Earth
+and Moon, which vary in positions around the camera boresight over
+each spacecraft orbit \citep[see][\S 7.3.1--7.3.4]{vanderspek_2018}.
+The typical size of scattered light patches is greater than 32 pixels,
+and their typical amplitude is $\sim 10\times$ the sky background
+level.
+
+% We found this background subtraction step to be particularly important
+% in our subsequent difference imaging analysis. In its absense, the
+% scattered light artifacts could introduce erroneous residuals into the
+% kernel solution used to match reference and target images.  Including
+% this step mitigated such effects, and helped produce clean
+% subtractions.  Even after subtraction, a small fraction of frames also
+% show sharp features (caustics) below our median box filter's size
+% scale.  Such features may affect flux measurements at specific times
+% in a small subset of lightcurves.
+
+After subtracting the background, we mask out saturated stars using a
+fixed saturation level of $8\times10^4\,{\rm ADU}$. This value was
+chosen based on the onset of visible trails of bleeding charge, and is
+slightly greater than the expected saturation level quoted by
+\citet{vanderspek_2018}.  As described by \citet{Pal_2009}, our masks
+are metadata to the image, and are only applied to the
+pixel values during the specific image processing steps ({\it e.g.},
+convolution) in which they are necessary. We also extend the masks
+beyond purely saturated pixels to ``bloomed'' pixels horizontally and
+vertically adjacent to the saturated pixels using the algorithm
+described by \citet{Pal_2009}.
+
+Finally, for frames with the \texttt{DQUALITY} bit-flag set to
+32~---~corresponding to the ``momentum dumps'' described by
+\citet{vanderspek_2018}~---~we mask out the entire frame.  This
+removes on average a few frames per sector. Through visual inspection,
+we see that the stars on these frames are extremely smeared, and are
+unlikely to produce useful science data.
 

### 2019-04-06 paper/ms.tex
update paper w/ star catalog construction

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% BEGIN CUSTOM SHORT-CUT COMMANDS
+
+% BEGIN CLUSTER TABLE
+%FIXME: write code that will write these values
+\newcommand{\cgXVIIInstartot}{}
+\newcommand{\cgXVIIInstarcdipsI}{}
+\newcommand{\gaiaXVIIInstartot}{}
+\newcommand{\gaiaXVIIInstarcdipsI}{}
+
+\newcommand{\kXIIInstartot}{}
+\newcommand{\kXIIInstarcdipsI}{}
+\newcommand{\dXIVnstartot}{}
+\newcommand{\dXIVnstarcdipsI}{}
+\newcommand{\bellXVIInstartot}{}
+\newcommand{\bellXVIInstarcdipsI}{}
+\newcommand{\banyanXIIInstartot}{}
+\newcommand{\banyanXIIInstarcdipsI}{}
+\newcommand{\banyanXIInstartot}{}
+\newcommand{\banyanXIInstarcdipsI}{}
+\newcommand{\banyanXInstartot}{}
+\newcommand{\banyanXInstarcdipsI}{}
+\newcommand{\krausXIVnstartot}{}
+\newcommand{\krausXIVnstarcdipsI}{}
+\newcommand{\ohXVIInstartot}{}
+\newcommand{\ohXVIInstarcdipsI}{}
+\newcommand{\rizzutoXInstartot}{}
+\newcommand{\rizzutoXInstarcdipsI}{}
+\newcommand{\roserXInstartot}{}
+\newcommand{\roserXInstarcdipsI}{}
+
+\newcommand{\cgXVIIInclustertot}{}
+\newcommand{\cgXVIIInclustercdipsI}{}
+\newcommand{\gaiaXVIIInclustertot}{}
+\newcommand{\gaiaXVIIInclustercdipsI}{}
+
+\newcommand{\kXIIInclustertot}{}
+\newcommand{\kXIIInclustercdipsI}{}
+\newcommand{\dXIVnclustertot}{}
+\newcommand{\dXIVnclustercdipsI}{}
+\newcommand{\bellXVIInclustertot}{}
+\newcommand{\bellXVIInclustercdipsI}{}
+\newcommand{\banyanXIIInclustertot}{}
+\newcommand{\banyanXIIInclustercdipsI}{}
+\newcommand{\banyanXIInclustertot}{}
+\newcommand{\banyanXIInclustercdipsI}{}
+\newcommand{\banyanXInclustertot}{}
+\newcommand{\banyanXInclustercdipsI}{}
+\newcommand{\krausXIVnclustertot}{}
+\newcommand{\krausXIVnclustercdipsI}{}
+\newcommand{\ohXVIInclustertot}{}
+\newcommand{\ohXVIInclustercdipsI}{}
+\newcommand{\rizzutoXInclustertot}{}
+\newcommand{\rizzutoXInclustercdipsI}{}
+\newcommand{\roserXInclustertot}{}
+\newcommand{\roserXInclustercdipsI}{}
+% END CLUSTER TABLE
+
+% END CUSTOM SHORT-CUT COMMANDS
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%
+
 %\NewPageAfterKeywords
@@
   The Cluster Difference Imaging Photometric Survey (CDIPS).
-  I. Methods \& Light Curves from TESS Sectors 1-5
+  I. Method \& TESS Light Curves from XXX Clusters
 }
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Method}
+\section{Method: Photometry}
 \label{sec:method}
@@
 frame from Gaia DR2.  We detrend the resulting lightcurves
-(\S~\ref{subsec:lcdetrending}), and then assess the resulting
-lightcurves using a variety of statistics for their white noise and
-red noise properties (\S~\ref{sec:results}).
+(\S~\ref{subsec:lcdetrending}).
+We then select stars that we believe are ``cluster members'',
+roughly X\% of the overall dataset (\S~\ref{sec:starselection}).
+Focusing on the lightcurves of these stars, their white noise and red
+noise properties, and point out a few interesting cases of
+variability (\S~\ref{sec:results}).
 
@@
 
-Second, we estimate the background of each frame.  We do this by
+We then estimate the background of each frame.  We do this by
 temporarily masking out pixels more than $2\sigma$ from the median,
@@
 each spacecraft orbit \citep[see][\S 7.3.1--7.3.4]{vanderspek_2018}.
-The typical size of scattered light patches is greater than 32 pixels,
+The typical size of scattered light patches is greater than 48 pixels,
 and their typical amplitude is $\sim 10\times$ the sky background
@@
 
-Finally, for frames with the \texttt{DQUALITY} bit-flag set to
-32~---~corresponding to the ``momentum dumps'' described by
-\citet{vanderspek_2018}~---~we mask out the entire frame.  This
-removes on average a few frames per sector. Through visual inspection,
-we see that the stars on these frames are extremely smeared, and are
-unlikely to produce useful science data.
+Finally, for frames with the \texttt{DQUALITY} bit-flag corresponding
+to the ``momentum dumps'' and ``coarse pointing modes'' described by
+\citet{vanderspek_2018}, we mask out the entire frame.  This removes
+on average a few frames per sector. Through visual inspection, we see
+that the stars on these frames are extremely smeared, and are unlikely
+to produce useful science data.
+In addition, we use the sector-specific data release
+notes\footnote{\url{ archive.stsci.edu/tess/tess_drn.html}} to
+identify further  times with anomalously poor spacecraft performance,
+which we omit from consideration. For Sectors 1 through 5, these
+include coarse pointing windows from orbits 10, 13, 14, and an
+instrumetal anomaly window in orbit 15.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Method: Star Selection}
+\label{sec:starselection}
+
+A major motivator for the CDIPS project is to increase the number of
+cluster stars for which continuous photometric timeseries are
+available, and thus facilitate studies of exoplanetary and stellar
+processes across different times and stellar environments.
+
+An essential aspect of the project is therefore to define a {\it
+cluster star sample}, consisting of stars that are thought to be
+members of clusters.
+
+Performing a homogeneous membership determination for every known
+cluster is beyond the scope of this work.  Instead, we collect various
+cluster membership catalogs from the literature.  We then use them to
+identify cluster members for which we have already made lightcurves
+from the TESS images.  Our goal in selecting stars is completeness,
+rather than precision.  If there has been a claim in the literature
+that a star should be considered as a cluster member, we aim to
+provide a lightcurve for that star.
+
+Table~N describes the cluster membership catalogs we have used to
+identify candidate cluster members.  Since our photometric reduction
+is based on positions reported in {\it Gaia DR2}, each of our
+lightcurve sources by default is associated with a Gaia identifier.
+Correspondingly, the cluster membership determinations performed by
+\citet{cantat-gaudin_gaia_2018} and \citet{gaia_hr_2018} are the
+easiest case for us to merge against our lightcurve database.
+For the TESS Sectors 1--5 lightcurves produced in this study, this
+yielded X and Y lightcurves respectively.
+
+%FIXME: make table
+
+\subsection{Open clusters (OCs)}
+\label{subsec:oc}
+
+\paragraph{{\it Gaia}-derived OC memberships}
+At the time of writing, two relatively large, homogeneous cluster
+memberships studies had been performed using {\it Gaia}-DR2: those by
+\citet{cantat-gaudin_gaia_2018} and \citet{gaia_hr_2018}.
+
+\citet{cantat-gaudin_gaia_2018} used an unsupervised membership
+assignment algorithm to identify clusters in the three-dimensional
+astrometric space of proper motion and parallax. They used {\it Gaia}
+photometry and radial velocities to then verify the claimed
+membership properties.  From their Table~2, we collect 401{,}448
+cluster members, in 1229 clusters, down to a limiting magnitude of
+$G=18$.
+
+\citet{gaia_hr_2018} reported memberships for stars in a smaller, more
+select group of well-studied open clusters. From their Table~A1, we
+collect 40{,}903 cluster members, in 41 open clusters, mostly within
+$500\,{\rm pc}$. While this work also included memberships for
+globular clusters, we omitted these from consideration.
+
+\paragraph{Pre-{\it Gaia} OC memberships}
+\citet{Kharchenko_et_al_2013} used proper motions calculated in PPMXL
+\citep[][a combination of USNO-B1{.}0 and 2MASS
+astrometry]{roeser_ppmxl_2010} and near-infrared photometry from 2MASS
+\citep{skrutskie_tmass_2006} and reported the existence of 2859 open
+clusters and stellar associations.
+We selected their ``$1\sigma$'' members according to the
+combined photometric, kinematic, and spatial criteria described by
+\citet{kharchenko_global_2012}.  Then, to obtain {\it Gaia}-DR2 source
+identifiers for the members, we performed a crossmatch for {\it
+Gaia}-DR2 sources within 5 arcseconds of the listed positions.  As an
+additional constraint, we used the 2MASS photometry to predict the
+$G$-band magnitudes\footnote{See
+\url{https://gea.esac.esa.int/archive/documentation/GDR2/Data_processing/chap_cu5pho/sec_cu5pho_calibr/ssec_cu5pho_PhotTransf.html},
+online, \texttt{2019-03-29}, or \citet{carrasco_gaia_2016}}, and
+required that the measured $G$-magnitude fall within 2 magnitudes of
+the predicted $G$-magnitude.  If multiple neighbors matched the
+position and magnitude constraints, we took the nearest spatial
+neighbor as the match.  From 373{,}226 stars, this yielded a unique
+best neighbor for 352{,}332 stars (94.4\% of the sample), and a choice
+between two neighbors for 17{,}774 stars.
+
+The second (non-{\it Gaia} derived) open cluster membership catalog we
+used was the \citet{dias_proper_2014} catalog, which was based on
+UCAC4 proper motions.
+From their 1805 reported open clusters, we selected sources with
+quoted membership probability above 50\%.
+To obtain {\it Gaia}-DR2 source identifiers for the members, we
+performed a similar crossmatch as before, looking for sources within 5
+arcseconds of the listed positions, and within $\pm$2 $G$-band
+magnitudes of the prediction.
+From 2{,}034{,}269 stars, this yielded a unique
+best neighbor for 1{,}828{,}630 stars (89.9\% of the sample), and a choice
+between two neighbors for 8.7\% of the remaining sample.
+
+\begin{figure*}[!ht]
+  \gridline{\fig{f5a.png}{0.95\textwidth}{}}
+  \vspace{-0.8cm}
+  \gridline{\fig{f5b.png}{0.95\textwidth}{}}
+  \caption{
+      {\it Top.} Cross-match statistics from \cite{Kharchenko_et_al_2013} {\it 
+      vs.} Gaia-DR2.
+      {\it Bottom.} Ditto, for \cite{dias_proper_2014} {\it vs.} Gaia-DR2.
+  }
+  \label{fig:xmatch_info}
+\end{figure*}
+
+The distributions of various cross-matching statistics are shown in
+Figure~\ref{fig:xmatch_info}.  The distances between matches is
+typically below 1 arcsecond.  The Dias catalog shows somewhat stronger
+crowding effects at the faint end compared to the Kharchenko catalog.
+The Kharchenko catalog also has a more lop-sided distribution of true
+{\it vs.} predicted $G$-band magnitudes.
+
+\subsection{Moving groups and stellar associations}
+\label{subsec:mg}
+
+Stars, moving groups and stellar associations are of interest for
+similar reasons as stars in open clusters.  Though fewer stars
+are known to exist in moving groups, they are of particular interest
+because moving groups are less crowded than open clusters, and are
+often closer to the Sun.
+
+We obtained Gaia DR2 identifiers from the results of the following
+studies:
+\citet{gagne_banyan_XI_2018},
+\citet{gagne_banyan_XII_2018},
+\citet{gagne_banyan_XIII_2018},
+\citet{kraus_tucanahor_2014},
+\citet{roser_deep_2011}, % OC, not MG...
+\citet{bell_32ori_2017},
+\citet{rizzuto_multidimensional_2011},
+and \citet{oh_comoving_2017}, The methods applied in these studies
+vary from kinematic analyses, to astrometric analyses included
+Gaia-DR1 parallaxes, to photometric searches for infrared excesses, to
+spectroscopic studies including RVs, H$\alpha$
+emission, and Li absorption.
+
+For the Gagne et al{.} catalogs, we searched the Gaia-DR2 archive for
+sources within 10 arcseconds of the listed positions.  If Gagne et
+al{.} gave a proper motion, we required that the sign of each the Gaia
+proper motion components match that of the Gagne values (the stated
+proper motion uncertainties seemed to have been underestimated).  We
+also imposed a $G<18$ cut on any putative matches.  Of 3012 moving
+group members collected from the three combined Gagne et al{.}
+catalogs, we found 2702 matches.
+
+The \citet{kraus_tucanahor_2014}, \citet{roser_deep_2011}, and
+\citet{bell_32ori_2017} studies reported members in Tucana-Horologium,
+the Hyades, and 32$\,$Ori respectively.  Applying the same procedure as
+for the Gagne catalogs gave 187, 684, and 119 best-neighbors
+respectively, compared to 205, 724, and 141 initially reported
+members.  Note that \citet{kraus_tucanahor_2014} found that only
+$\sim$70\% of their listed members have spectroscopic indicators
+consistent with their membership in Tucana-Horologium.
+
+\citet{rizzuto_multidimensional_2011} also focused on a single moving
+group: the Sco OB2 association. We used their reported Hipparcos
+identifiers, and matched against the {\it Gaia} archive's
+\texttt{hipparcos2_best_neighbour} table, which gave 319
+nearest-neigbor stars from 436 candidate members.
+
+Finally, \citet{oh_comoving_2017} searched for comoving stars in the
+$\approx$2 million stars that overlapped between Tycho-2 and {\it
+Gaia}-DR1.  They found many wide binaries, and also identified a large
+number of comoving groups.  We chose the 2{,}134 stars that they
+reported were in groups with sizes of at least 3 stars.  Using their
+{\it Gaia}-DR1 source identifiers, we matched against the {\it Gaia}
+archive's \texttt{dr1_neighbourhood} table, which gave 1{,}881
+nearest-neigbor stars in groups of at least three stars
+\citep{marrese_gaia_2019}.
+
+\subsection{Summary of selected stars}
+
+After collecting the results of all the studies described above, we
+merged them into a single table. We queried the
+\texttt{gaiadr2.gaia_source} table to retrieve their photometric $G$,
+$G_{\rm R_p}$, and $G_{\rm B_p}$ magnitudes, as well as their
+five astrometric parameters $(\alpha, \delta, \mu_\alpha, \mu_\delta,
+\pi)$.
+We then imposed that $G_{\rm R_p} < 16$.
+The concatenated results are given in Table~N.
+
+All told, there are 1{,}308{,}706 unique stars, from 12 distinct
+membership catalogs.
+Stars that are reported in multiple catalogs have their reference
+information from each available catalog concatenated.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Results}
@@
 	TESS \citep{ricker_transiting_2015},
-	Gaia \citep{gaia_collaboration_gaia_2016,gaia_collaboration_gaia_2018}
+	Gaia \citep{gaia_collaboration_gaia_2016,gaia_collaboration_gaia_2018},
+	2MASS \citep{skrutskie_tmass_2006}
 }

### 2019-04-06 paper/collect_figures.sh

@@ -1,0 +1,2 @@
+cp ../results/catalog_to_gaia_match_statistics_MWSC.png f5a.png
+cp ../results/catalog_to_gaia_match_statistics_Dias14.png f5b.png

### 2019-04-06 src/homogenize_cluster_lists.py
add tools i used to make OC and MG catalogs

@@ -21,221 +21,434 @@ from astropy.io.votable import from_table, writeto, parse
 from astroquery.gaia import Gaia
 
 from astrobase.timeutils import precess_coordinates
+from datetime import datetime
 
-def GaiaCollaboration2018_clusters_to_csv():
+from open_cluster_xmatch_utils import (
+    GaiaCollaboration2018_clusters_to_csv,
+    Kharchenko2013_position_mag_match_Gaia,
+    Dias2014_nbhr_gaia_to_nearestnbhr
+)
+from moving_group_xmatch_utils import (
+    make_Gagne18_BANYAN_XI_GaiaDR2_crossmatch,
+    make_Gagne18_BANYAN_XII_GaiaDR2_crossmatch,
+    make_Gagne18_BANYAN_XIII_GaiaDR2_crossmatch,
+    make_Kraus14_GaiaDR2_crossmatch,
+    make_Rizzuto11_GaiaDR2_crossmatch,
+    make_Luhman12_GaiaDR2_crossmatch,
+    make_Bell17_GaiaDR2_crossmatch,
+    make_Roser11_GaiaDR2_crossmatch,
+    make_Oh17_GaiaDR2_crossmatch
+)
 
-    inpaths = [
-        '../data/cluster_data/GaiaCollaboration2018_616_A10_tablea1a_within_250pc.vot',
-        '../data/cluster_data/GaiaCollaboration2018_616_A10_tablea1b_beyond_250pc.vot'
-    ]
+def main():
 
-    for inpath in inpaths:
-        tab = parse(inpath)
-
-        t = tab.get_first_table().to_table()
-
-        df = pd.DataFrame({'source':t['Source'], 'cluster':t['Cluster']})
-
-        outpath = inpath.replace('.vot','_cut_only_source_cluster.csv')
-        df.to_csv(outpath, index=False)
-        print('made {}'.format(outpath))
-
-
-def failed_Kharchenko2013_match_Gaia():
-    #
-    # attempt:
-    # use the 2MASS object ID's, given in “pts_key” format from Kharchenko, to
-    # match against the tmass_best_neighbour table (tmass_oid column).
-    #
-    # result:
-    # fails, because I think these are different IDs. not sure if it ALWAYS
-    # fails, but it seems to fail enough of the time that using POSITIONS and
-    # MAGNITUDES directly is probably the safer algorithm.
-
[…]

### 2019-04-06 src/moving_group_xmatch_utils.py

@@ -1,0 +1,925 @@
+# -*- coding: utf-8 -*-
+'''
+functions to download and wrangle catalogs of members that I want to crossmatch
+against TESS objects of interest (alerts)
+
+mostly called from `get_tess_alert_search_list.py`
+'''
+from __future__ import division, print_function
+
+import numpy as np, pandas as pd
+
+from astropy.table import Table
+from astropy import units as u
+from astropy.coordinates import SkyCoord
+from astropy.io import ascii
+from astropy.io.votable import from_table, writeto, parse
+
+from astroquery.gaia import Gaia
+
+from astroquery.vizier import Vizier
+
+import sys, os, re, itertools, subprocess
+from glob import glob
+from numpy import array as arr
+
+def make_Gagne18_BANYAN_XIII_GaiaDR2_crossmatch():
+
+    # Downloaded direct from
+    # http://iopscience.iop.org/0004-637X/862/2/138/suppdata/apjaaca2et2_mrt.txt
+    # God I wish vizier were a thing.
+    tablepath = '../data/cluster_data/moving_groups/Gagne_2018_BANYAN_XIII_apjaaca2et2_mrt.txt'
+
+    make_Gagne18_BANYAN_any_DR2_crossmatch(
+        tablepath, namestr='Gagne_2018_BANYAN_XIII_GaiaDR2_crossmatched',
+        maxsep=10)
+
+
+def make_Gagne18_BANYAN_XII_GaiaDR2_crossmatch():
+
+    # Downloaded direct from
+    # http://iopscience.iop.org/0004-637X/860/1/43/suppdata/apjaac2b8t4_mrt.txt
+    tablepath = '../data/cluster_data/moving_groups/Gagne_2018_BANYAN_XII_apjaac2b8t4_mrt.txt'
+
+    make_Gagne18_BANYAN_any_DR2_crossmatch(
+        tablepath, namestr='Gagne_2018_BANYAN_XII_GaiaDR2_crossmatched',
+        maxsep=10)
+
+
+def make_Gagne18_BANYAN_XI_GaiaDR2_crossmatch():
+
+    # Downloaded direct from
+    # http://iopscience.iop.org/0004-637X/856/1/23/suppdata/apjaaae09t5_mrt.txt
+    tablepath = '../data/cluster_data/moving_groups/Gagne_2018_apjaaae09t5_mrt.txt'
+
[…]

### 2019-04-06 src/open_cluster_xmatch_utils.py

@@ -1,0 +1,449 @@
+# -*- coding: utf-8 -*-
+'''
+functions to download and wrangle catalogs of cluster members that I want to
+crossmatch against Gaia-DR2.
+
+called from `homogenize_cluster_lists.py`
+'''
+import os, pickle, subprocess, itertools
+from glob import glob
+
+from numpy import array as nparr
+
+from astropy.table import Table
+from astropy.io import ascii
+from astropy.coordinates import SkyCoord
+from astropy import units as u, constants as c
+from astropy.io.votable import from_table, writeto, parse
+
+from astroquery.gaia import Gaia
+
+from astrobase.timeutils import precess_coordinates
+from datetime import datetime
+
+def GaiaCollaboration2018_clusters_to_csv():
+
+    inpaths = [
+        '../data/cluster_data/GaiaCollaboration2018_616_A10_tablea1b_beyond_250pc.vot',
+        '../data/cluster_data/GaiaCollaboration2018_616_A10_tablea1a_within_250pc.vot'
+    ]
+
+    for inpath in inpaths:
+        tab = parse(inpath)
+
+        t = tab.get_first_table().to_table()
+
+        df = pd.DataFrame({'source':t['Source'], 'cluster':t['Cluster']})
+
+        cnames = np.array(df['cluster'].str.decode('utf-8'))
+
+        # you don't want the globular clusters from this work!
+        bad_ngcs = [104, 288, 362, 1851, 5272, 5904, 6205, 6218, 6341, 6397,
+                    6656, 6752, 6809, 7099]
+        bad_ngcs = ['NGC{:s}'.format(str(bn).zfill(4)) for bn in bad_ngcs]
+        # however, I manually checked: none of the globular clusters are in the
+        # these source catalogs.
+
+        outpath = inpath.replace('.vot','_cut_only_source_cluster.csv')
+        df.to_csv(outpath, index=False)
+        print('made {}'.format(outpath))
+
+
+def failed_Kharchenko2013_match_Gaia():
+    #
+    # attempt:
+    # use the 2MASS object ID's, given in “pts_key” format from Kharchenko, to
+    # match against the tmass_best_neighbour table (tmass_oid column).
+    #
+    # result:
+    # fails, because I think these are different IDs. not sure if it ALWAYS
[…]

### 2019-04-06 src/plot_star_catalog.py
add src/plot_star_catalog

@@ -1,0 +1,105 @@
+import numpy as np, matplotlib.pyplot as plt, pandas as pd
+import os, subprocess, itertools
+from datetime import datetime
+
+from numpy import array as nparr
+
+import astropy.coordinates as coord
+from astropy import units as u, constants as c
+
+catalogpath = '../data/cluster_data/OC_MG_FINAL_GaiaRp_lt_16.csv'
+
+def main():
+    do_star_catalog_skymap = 0
+    do_star_catalog_mag_histogram = 0
+    do_star_catalog_cmd = 1
+
+    df = pd.read_csv(catalogpath, sep=';')
+
+    if do_star_catalog_skymap:
+        star_catalog_skymap(df)
+    if do_star_catalog_mag_histogram:
+        star_catalog_mag_histogram(df, 'phot_g_mean_mag')
+        star_catalog_mag_histogram(df, 'phot_rp_mean_mag')
+    if do_star_catalog_cmd:
+        star_catalog_cmd(df)
+
+def savefig(fig, figpath):
+    fig.savefig(figpath, dpi=450, bbox_inches='tight')
+    print('{}: made {}'.format(datetime.utcnow().isoformat(), figpath))
+
+def star_catalog_skymap(df):
+
+    ra = coord.Angle(df['ra']*u.deg)
+    ra = ra.wrap_at(180*u.deg)
+    dec = coord.Angle(df['dec']*u.deg)
+
+    f = plt.figure(figsize=(4,3))
+    ax = f.add_subplot(111, projection='mollweide')
+
+    ax.scatter(ra.radian, dec.radian, rasterized=True, s=0.5, alpha=0.5,
+               linewidths=0, zorder=5)
+
+    ax.set_xticklabels(['14h','16h','18h','20h','22h',
+                        '0h','2h','4h','6h','8h','10h'])
+    ax.tick_params(axis='both', which='major', labelsize='x-small')
+    ax.tick_params(axis='both', which='minor', labelsize='x-small')
+    ax.grid(True, linestyle='--', linewidth=0.5, alpha=0.3, zorder=-1)
+
+    f.tight_layout()
+    f.subplots_adjust(left=0.1, right=0.9, top=0.8, bottom=0.2)
+    savefig(f, '../results/star_catalog_skymap.png')
+
+def star_catalog_mag_histogram(df, magstr):
+
+    f,ax = plt.subplots(figsize=(4,3))
+
[…]

### 2019-04-06 src/OLD/parse_MWSC.py
add src/OLD

@@ -1,0 +1,2257 @@
+'''
+DESCRIPTION
+----------
+An assortment of code written for sanity checks on our 2017 TESS GI proposal
+about difference imaging of clusters.
+
+Most of this involving parsing Kharchenko et al (2013)'s table, hence the name
+`parse_MWSC.py`.
+
+The tools here do things like:
+
+* Find how many open clusters we could observe
+
+* Find how many member stars within those we could observe
+
+* Compute TESS mags for everything (mostly via `ticgen`)
+
+* Estimate blending effects, mainly through the dilution (computed just by
+    summing magnitudes appropriately)
+
+* Using K+13's King profile fits, estimate the surface density of member stars.
+    It turns out that this radically underestimates the actual surface density
+    of stars (because of all the background blends). Moreover, for purposes of
+    motivating our difference imaging, "the number of stars in your aperture"
+    is more relevant than "a surface density", and even more relevant than both
+    of those is dilution.
+    So I settled on the dilution calculation.
+
+The plotting scripts here also make the skymap figure of the proposal. (Where
+are the clusters on the sky?)
+
+
+USAGE
+----------
+
+From /src/, select desired functions from __main__ below. Then:
+>>> python parse_MWSC.py > output.log
+
+'''
+
+import matplotlib.pyplot as plt, seaborn as sns
+import pandas as pd, numpy as np
+
+from astropy.table import Table
+from astropy.io import ascii
+from astropy.coordinates import SkyCoord
+import astropy.units as u
+
+from math import pi
+import pickle, os
+
+from scipy.interpolate import interp1d
+
+global COLORS
+COLORS = ['#1f77b4', '#ff7f0e', '#2ca02c', '#d62728', '#9467bd', '#8c564b',
+          '#e377c2', '#7f7f7f', '#bcbd22', '#17becf']
+
+
+# cite:
+# 
+# Jaffe, T. J. & Barclay, T. 2017, ticgen: A tool for calculating a TESS
+# magnitude, and an expected noise level for stars to be observed by TESS.,
[…]

### 2019-04-06 src/plot_catalog_to_gaia_match_statistics.py
update starcatalog to gaia match stats

@@ -47,9 +47,12 @@ def get_mwsc_gaia_xmatch_statistics():
 
     return bigdf
 
-def plot_catalog_to_gaia_match_statistics(bigdf):
+def plot_catalog_to_gaia_match_statistics(bigdf, outpath, isD14=False):
 
-    dist_arcsec = (np.array(bigdf['dist_deg'])*u.deg).to(u.arcsec)
+    if not isD14:
+        dist_arcsec = (np.array(bigdf['dist_deg'])*u.deg).to(u.arcsec)
+    else:
+        dist_arcsec = (np.array(bigdf['dist'])*u.deg).to(u.arcsec)
 
     f,axs = plt.subplots(nrows=1, ncols=3, figsize=(12,4))
 
@@ -57,18 +60,25 @@ def plot_catalog_to_gaia_match_statistics(bigdf):
     axs[0].set_xlabel('distance [arcsec]')
     axs[0].set_yscale('log')
 
-    axs[1].hist(bigdf['gmag_match_minus_estimate'])
+    if isD14:
+        axs[1].hist(bigdf['gaia_gmag']-bigdf['gmag_estimate'])
+    else:
+        axs[1].hist(bigdf['gmag_match_minus_estimate'])
     axs[1].set_xlabel('$\mathrm{G}_{\mathrm{true}}$ -'
-                        '$\mathrm{G}_{\mathrm{pred}}$')
+                      '$\mathrm{G}_{\mathrm{pred}}$')
     axs[1].set_yscale('log')
 
-    axs[2].scatter(bigdf['gmag_match'], bigdf['gmag_match_minus_estimate'],
-                   s=5, alpha=0.1, rasterized=True, linewidths=0)
+    if isD14:
+        axs[2].scatter(bigdf['gaia_gmag'],
+                       bigdf['gaia_gmag']-bigdf['gmag_estimate'], s=5,
+                       alpha=0.1, rasterized=True, linewidths=0)
+    else:
+        axs[2].scatter(bigdf['gmag_match'], bigdf['gmag_match_minus_estimate'],
+                       s=5, alpha=0.1, rasterized=True, linewidths=0)
     axs[2].set_xlabel('$\mathrm{G}_{\mathrm{true}}$')
     axs[2].set_ylabel('$\mathrm{G}_{\mathrm{true}}$ -'
-                        '$\mathrm{G}_{\mathrm{pred}}$')
+                      '$\mathrm{G}_{\mathrm{pred}}$')
 
[…]

### 2019-04-12 src/DEPRECATED/collect_cluster_lightcurves.py
add src/collect_cdips_lightcurves.py

@@ -1,18 +1,23 @@
-"""
-For a given cluster, get the lightcurves that you have made.
-"""
-import numpy as np, matplotlib.pyplot as plt, pandas as pd
-from glob import glob
-import os, pickle, subprocess, itertools
+def make_cg18_cut():
+    """for speed, work with only DR2 source id's and cluster names."""
 
-from numpy import array as nparr
+    datadir = '../data/cluster_data/'
+    tabpath = os.path.join(
+        datadir,'CantatGaudin_2018_table2_membership_info.vot'
+    )
+    vot = parse(tabpath)
+    tab = vot.get_first_table().to_table()
 
-from astropy.table import Table
-from astropy import units as u, constants as c
+    outdf = pd.DataFrame({'source':tab['Source'],'cluster':tab['Cluster']})
 
-from astroquery.gaia import Gaia
+    outpath = (
+        '../data/cluster_data/CantatGaudin_2018_table2_cut_only_source_cluster.csv'
+    )
 
-from astropy.io.votable import from_table, writeto, parse
+    outdf.to_csv(outpath, index=False)
+    print('made {}'.format(outpath))
+
+
 
 def kharchenko13_to_gaiadr2_xmatch(df, cluster_name):
     """
@@ -186,52 +191,8 @@ def write_k13_tab_to_vot(_tab, cluster_name):
     print('wrote {}'.format(outpath))
 
 
-def scp_lightcurves(lcbasenames,
-                    lcdir='/nfs/phtess1/ar1/TESS/FFI/LC/FULL/s0002/ISP_1-2-1163',
-                    outdir='../data/cluster_data/lightcurves/Blanco_1/'):
 
-    if not os.path.exists(outdir):
-        os.mkdir(outdir)
-
-    for lcbasename in lcbasenames:
-
-        fromstr = "lbouma@phn12:{}/{}".format(lcdir, lcbasename)
-        tostr = "{}/.".format(outdir)
-
-        p = subprocess.Popen([
-            "scp",
-            fromstr,
-            tostr,
-        ])
-        sts = os.waitpid(p.pid, 0)
-
-    return 1
-
-
-def make_cg18_cut():
-    """for speed, work with only DR2 source id's and cluster names."""
-
-    datadir = '../data/cluster_data/'
-    tabpath = os.path.join(
-        datadir,'CantatGaudin_2018_table2_membership_info.vot'
-    )
-    vot = parse(tabpath)
[…]

### 2019-04-12 src/collect_cdips_lightcurves.py

@@ -1,0 +1,150 @@
+"""
+Collect lightcurves from phtess[1|2] for the CDIPS project.
+
+How?
+
+* Get lists of lightcurves that were made for each requested projid / sector /
+cam / ccd.
+
+* Crossmatch these lists against the CDIPS star catalog
+(OC_MG_FINAL_GaiaRp_lt_16.csv).
+
+* symlink them to a PROJ directory.
+
+"""
+import numpy as np, matplotlib.pyplot as plt, pandas as pd
+from glob import glob
+import os, pickle, subprocess, itertools
+
+from numpy import array as nparr
+
+from astropy.table import Table
+from astropy import units as u, constants as c
+
+from astroquery.gaia import Gaia
+
+from astropy.io.votable import from_table, writeto, parse
+
+def scp_lightcurves(lcbasenames,
+                    lcdir='/nfs/phtess1/ar1/TESS/FFI/LC/FULL/s0002/ISP_1-2-1163',
+                    outdir='../data/cluster_data/lightcurves/Blanco_1/'):
+
+    if not os.path.exists(outdir):
+        os.mkdir(outdir)
+
+    for lcbasename in lcbasenames:
+
+        fromstr = "lbouma@phn12:{}/{}".format(lcdir, lcbasename)
+        tostr = "{}/.".format(outdir)
+
+        p = subprocess.Popen([
+            "scp",
+            fromstr,
+            tostr,
+        ])
+        sts = os.waitpid(p.pid, 0)
+
+    return 1
+
+def make_local_lc_directories(
+    sectors=range(1,stop=5+1,step=1),
+    cams=range(1,stop=4+1,step=1),
+    ccds=range(1,stop=4+1,step=1),
+    cdipslcdir='/nfs/phtess1/ar1/TESS/PROJ/lbouma/CDIPS_LCS'):
+
+    for sector in sectors:
+        sectordir = os.path.join(cdipslcdir,'sector-{}'.format(sector))
+        if not os.path.exists(sectordir):
+            os.mkdir(sectordir)
+            print('made {}'.format(sectordir))
+    for cam,ccd in zip(cams, ccds):
+        camccddir = os.path.join(cdipslcdir,sector,'cam{}_ccd{}'.format(cam,ccd))
+        if not os.path.exists(camccddir):
+            os.mkdir(camccddir)
+            print('made {}'.format(camccddir))
+
+
[…]

### 2019-04-25 drivers/do_initial_period_finding.py
minor

@@ -132,8 +132,8 @@ def do_initial_period_finding(
     lcpaths = glob(os.path.join(lcdirectory, lcglob))
     np.random.shuffle(lcpaths)
 
-    tasks = [(x) for x in lcpaths[:1000]]
-    N_lcs = len(lcpaths[:1000])
+    tasks = [(x) for x in lcpaths]
+    N_lcs = len(lcpaths)
 
     print('%sZ: %s files to run initial periodograms on' %
           (datetime.utcnow().isoformat(), len(lcpaths)))

### 2019-04-25 drivers/skim_cream.py

@@ -90,8 +90,9 @@ def skim_cream(sectornum=6, tls_sde_cut=15, fap_cut=1e-40):
         source_id = str(int(row['source_id']))
         matching = [l for l in lcpaths if source_id in l]
         if len(matching) != 1:
-            print('expected 1 matching lcpath')
-            import IPython; IPython.embed()
+            print('ERR! expected 1 matching lcpath')
+            continue
+            #import IPython; IPython.embed()
         lcpath = matching[0]
         pfc.do_period_finding_fitslc(lcpath, ap=2, outdir=outdir)
 
@@ -104,7 +105,9 @@ def skim_cream(sectornum=6, tls_sde_cut=15, fap_cut=1e-40):
         source_id = str(int(row['source_id']))
         matching = [l for l in lcpaths if source_id in l]
         if len(matching) != 1:
-            raise AssertionError('expected 1 matching lcpath')
+            print('ERR! expected 1 matching lcpath')
+            continue
+            #raise AssertionError('expected 1 matching lcpath')
         lcpath = matching[0]
         pfc.do_period_finding_fitslc(lcpath, ap=2)
 

### 2019-04-25 paper/ms.tex
minor paper update

@@
   \item Select a set of isolated stars (``stamps'').
+  (For ficonv, the default procedure is: grid up the image. Within
+    each grid... find the brightest nonsaturated region. Use that to
+    fit the kernel!)
   \item Choose basis vectors $K_n$ for the kernel, $K = \sum_{n=1}^N
@@
 
+%FIXME TURGID PROSE
 In general though, one must adapt detrending procedures to the data at
@@
 %FIXME: clarify this procedure
-We select 500 template stars randomly from the stars on-chip with
+We select XXX template stars randomly from the stars on-chip with
 $G_{\rm R_p}$ magnitudes between 8.5 and 13 (TODO: rather bright?).
-We additionally require these stars to not have excessive variability,
-by fitting a parabola in the RMS-magnitude plane, and discarding stars
-more than $4\sigma$ away from the prediction of this fit.
+As an initial variability cut, we fit a parabola in the RMS-magnitude
+plane, and discarding stars more than $2\sigma$ away from the
+prediction of the fit.
+
+We then perform an initial iteration of TFA, on only the candidate
+template stars.
+We inspect the resulting detrended lightcurves for residual
+structure by computing a Lomb-Scargle periodogram.
+If the maximum-power peak has a false alarm probability below 0.1\%, 
+we exclude the star from the list of candidate template stars, on the
+basis of its presumed periodic variability signal.
+
+We then randomly select 200 template stars from the remaining
+non-variable candidates. 
+The choice of number of template stars was discussed by (CITE KOVACS).
+While it can be optimized by constructing and minimizing a BIC-like 
+quantity, a little overfitting is acceptable for our puposes.
 

### 2019-05-13 paper/ms.tex
paper: wrote some words

@@
   The Cluster Difference Imaging Photometric Survey (CDIPS).
-  I. Method \& TESS Light Curves from XXX Clusters
+  I. Method \& TESS Light Curves from Sector 6
 }
@@
 
-Lorem ipsum.
-
+The exoplanet field is evolving.
+At the beginning, Doppler spectroscopy by the Geneva and California groups
+led to the first exoplanet detections (CITE: Mayor 95, Butler, Marcy).
+Some of these planets transited (CITE: Henry, Charbonneau).
+Despite the geometric rarity of transits, photometric monitoring can
+be performed in parallel, while spectroscopy cannot.
+This enabled thousands of planet detections with the Kepler spacecraft
+(CITE: Borucki, Morton).
+The abundance of planets from Kepler taught us about statistics
+(CITE: Howard, Fressin, Petigura).
+By nature of its design, Kepler left open two major avenues for
+improvement: (i) brighter stars, (ii) rare weirdos.
+TESS (CITE: Ricker), by nature of its small, wide-field cameras, and
+nearly all-sky coverage, can capitalize on both.
+TESS observes more stars than Kepler, for on average less time.
+One class of rare weirdo to which TESS is sensitive is stars in
+clusters.  For brevity, we use the term ``cluster'' to refer to open
+clusters, moving groups, associations, and star-forming regions.
+Each of the $\sim$1000 star clusters of the Milky Way is a gift to
+astrophysics, providing a sample of stars that vary widely in mass
+but all have approximately the same age and composition.
+
+Cluster stars have been monitored photometrically from the ground
+(CITE: Joel thesis, Cambridge group).
+A few clusters, NAME1 and NAME2, were observed by Kepler in its prime
+mission (CITE: Meibom).
+And a few more, most notably including X,Y,Z, were observed in K2's
+ecliptic mission (CITE).
+
+TESS holds the promise to deliver the most homogeneous and
+comprehensive cluster photometric survey in history.  Based on the
+cluster membership database of \citet{Kharchenko_et_al_2013} and the
+TESS apparent magnitude calculator of \citet{Jaffe_Barclay_2017}, we
+estimate that $10^5$ cluster members brighter than $T=16$ will be
+observed in the northern ecliptic hemisphere's full-frame images.
+
+Yet, there are formidable obstacles to deriving precise photometry
+from the {\it TESS} images because of the relatively poor angular
+resolution.  Almost all of the clusters are within 10 degrees of the
+Galactic plane (see Figure~1), where the problems with crowding and
+complex backgrounds are so severe that the {\it TESS}\, Science Team
+has neglected that portion of the sky in their planet simulations
+\citep{Sullivan_et_al_2015}. Similarly, the {\it TESS}\, Candidate
+Target List deprioritizes all objects within $15^\circ$ of the
+galactic plane~\citep{stassun_TIC_2018}, which includes 90\% of all
+star clusters.  The large pixel size and the high stellar surface
+density will make aperture photometry unreliable.  Yet, aperture
+photometry is the basis of the official {\it TESS} data reduction
+pipeline and almost all reduction methods that have been applied to
+{\it Kepler} and {\it K2} data.
+
+We have begun to produce photometry from the TESS images.
 In what follows, \S~\ref{sec:method} presents BLAH, and
@@
 identifiers, and matched against the {\it Gaia} archive's
-\texttt{hipparcos2_best_neighbour} table, which gave 319
+\texttt{hipparcos2\_best\_neighbour} table, which gave 319
 nearest-neigbor stars from 436 candidate members.
@@
 {\it Gaia}-DR1 source identifiers, we matched against the {\it Gaia}
-archive's \texttt{dr1_neighbourhood} table, which gave 1{,}881
+archive's \texttt{dr1\_neighbourhood} table, which gave 1{,}881
 nearest-neigbor stars in groups of at least three stars
@@
 merged them into a single table. We queried the
-\texttt{gaiadr2.gaia_source} table to retrieve their photometric $G$,
+\texttt{gaiadr2.gaia\_source} table to retrieve their photometric $G$,
 $G_{\rm R_p}$, and $G_{\rm B_p}$ magnitudes, as well as their
@@
 Some focus on actual cluster fields.
+
+During the period search, we rejected $6\,{\rm hours}$ at the
+beginning and end of each spacecraft orbit, to mitigate the presence
+of correlated red noise in the results.
+This shrinks the data volume by about 5\%, but also lowers the number
+of systematic false positives in subsequent vetting.
 

### 2019-05-20 paper/ms.tex
paper: star selection before phot methods
paper: add magfit discn

@@
 \shortauthors{Bouma et al.}
-\shorttitle{Light Curves for Stars in Clusters}
+\shorttitle{CDIPS I: Method \& Sector 6}
 
@@
 mission (CITE: Meibom).
-And a few more, most notably including X,Y,Z, were observed in K2's
+And a few more, most notably X,Y, and Z, were observed in K2's
 ecliptic mission (CITE).
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Method: Star Selection}
+\label{sec:starselection}
+
+A major motivator for the CDIPS project is to increase the number of
+cluster stars for which continuous photometric timeseries are
+available, and thus facilitate studies of exoplanetary and stellar
+processes across different times and stellar environments.
+
+An essential aspect of the project is therefore to define a {\it
+cluster star sample}, consisting of stars that are thought to be
+members of clusters.
+
+Performing a homogeneous membership determination for every known
+cluster is beyond the scope of this work.  Instead, we collect various
+cluster membership catalogs from the literature.  We then use them to
+identify cluster members for which we have already made lightcurves
+from the TESS images.  Our goal in selecting stars is completeness,
+rather than precision.  If there has been a claim in the literature
+that a star should be considered as a cluster member, we aim to
+provide a lightcurve for that star.
+
+Table~N describes the cluster membership catalogs we have used to
+identify candidate cluster members.  Since our photometric reduction
+is based on positions reported in {\it Gaia DR2}, each of our
+lightcurve sources by default is associated with a Gaia identifier.
+Correspondingly, the cluster membership determinations performed by
+\citet{cantat-gaudin_gaia_2018} and \citet{gaia_hr_2018} are the
+easiest case for us to merge against our lightcurve database.
+For the TESS Sectors 1--5 lightcurves produced in this study, this
+yielded X and Y lightcurves respectively.
+
+%FIXME: make table
+
+\subsection{Open clusters (OCs)}
+\label{subsec:oc}
+
+\paragraph{{\it Gaia}-derived OC memberships}
+At the time of writing, two relatively large, homogeneous cluster
+memberships studies had been performed using {\it Gaia}-DR2: those by
+\citet{cantat-gaudin_gaia_2018} and \citet{gaia_hr_2018}.
+
+\citet{cantat-gaudin_gaia_2018} used an unsupervised membership
+assignment algorithm to identify clusters in the three-dimensional
+astrometric space of proper motion and parallax. They used {\it Gaia}
+photometry and radial velocities to then verify the claimed
+membership properties.  From their Table~2, we collect 401{,}448
+cluster members, in 1229 clusters, down to a limiting magnitude of
+$G=18$.
+
+\citet{gaia_hr_2018} reported memberships for stars in a smaller, more
+select group of well-studied open clusters. From their Table~A1, we
+collect 40{,}903 cluster members, in 41 open clusters, mostly within
+$500\,{\rm pc}$. While this work also included memberships for
+globular clusters, we omitted these from consideration.
+
+\paragraph{Pre-{\it Gaia} OC memberships}
+\citet{Kharchenko_et_al_2013} used proper motions calculated in PPMXL
+\citep[][a combination of USNO-B1{.}0 and 2MASS
+astrometry]{roeser_ppmxl_2010} and near-infrared photometry from 2MASS
+\citep{skrutskie_tmass_2006} and reported the existence of 2859 open
+clusters and stellar associations.
+We selected their ``$1\sigma$'' members according to the
+combined photometric, kinematic, and spatial criteria described by
+\citet{kharchenko_global_2012}.  Then, to obtain {\it Gaia}-DR2 source
+identifiers for the members, we performed a crossmatch for {\it
+Gaia}-DR2 sources within 5 arcseconds of the listed positions.  As an
+additional constraint, we used the 2MASS photometry to predict the
+$G$-band magnitudes\footnote{See
+\url{https://gea.esac.esa.int/archive/documentation/GDR2/Data_processing/chap_cu5pho/sec_cu5pho_calibr/ssec_cu5pho_PhotTransf.html},
+online, \texttt{2019-03-29}, or \citet{carrasco_gaia_2016}}, and
+required that the measured $G$-magnitude fall within 2 magnitudes of
+the predicted $G$-magnitude.  If multiple neighbors matched the
+position and magnitude constraints, we took the nearest spatial
+neighbor as the match.  From 373{,}226 stars, this yielded a unique
+best neighbor for 352{,}332 stars (94.4\% of the sample), and a choice
+between two neighbors for 17{,}774 stars.
+
+The second (non-{\it Gaia} derived) open cluster membership catalog we
+used was the \citet{dias_proper_2014} catalog, which was based on
+UCAC4 proper motions.
+From their 1805 reported open clusters, we selected sources with
+quoted membership probability above 50\%.
+To obtain {\it Gaia}-DR2 source identifiers for the members, we
+performed a similar crossmatch as before, looking for sources within 5
+arcseconds of the listed positions, and within $\pm$2 $G$-band
+magnitudes of the prediction.
+From 2{,}034{,}269 stars, this yielded a unique
+best neighbor for 1{,}828{,}630 stars (89.9\% of the sample), and a choice
+between two neighbors for 8.7\% of the remaining sample.
+
+\begin{figure*}[!ht]
+  \gridline{\fig{f5a.png}{0.95\textwidth}{}}
+  \vspace{-0.8cm}
+  \gridline{\fig{f5b.png}{0.95\textwidth}{}}
+  \caption{
+      {\it Top.} Cross-match statistics from \cite{Kharchenko_et_al_2013} {\it 
+      vs.} Gaia-DR2.
+      {\it Bottom.} Ditto, for \cite{dias_proper_2014} {\it vs.} Gaia-DR2.
+  }
+  \label{fig:xmatch_info}
+\end{figure*}
+
+The distributions of various cross-matching statistics are shown in
+Figure~\ref{fig:xmatch_info}.  The distances between matches is
+typically below 1 arcsecond.  The Dias catalog shows somewhat stronger
+crowding effects at the faint end compared to the Kharchenko catalog.
+The Kharchenko catalog also has a more lop-sided distribution of true
+{\it vs.} predicted $G$-band magnitudes.
+
+\subsection{Moving groups and stellar associations}
+\label{subsec:mg}
+
+Stars, moving groups and stellar associations are of interest for
+similar reasons as stars in open clusters.  Though fewer stars
+are known to exist in moving groups, they are of particular interest
+because moving groups are less crowded than open clusters, and are
+often closer to the Sun.
+
+We obtained Gaia DR2 identifiers from the results of the following
+studies:
+\citet{gagne_banyan_XI_2018},
+\citet{gagne_banyan_XII_2018},
+\citet{gagne_banyan_XIII_2018},
+\citet{kraus_tucanahor_2014},
+\citet{roser_deep_2011}, % OC, not MG...
+\citet{bell_32ori_2017},
+\citet{rizzuto_multidimensional_2011},
+and \citet{oh_comoving_2017}, The methods applied in these studies
+vary from kinematic analyses, to astrometric analyses included
+Gaia-DR1 parallaxes, to photometric searches for infrared excesses, to
+spectroscopic studies including RVs, H$\alpha$
+emission, and Li absorption.
+
+For the Gagne et al{.} catalogs, we searched the Gaia-DR2 archive for
+sources within 10 arcseconds of the listed positions.  If Gagne et
+al{.} gave a proper motion, we required that the sign of each the Gaia
+proper motion components match that of the Gagne values (the stated
+proper motion uncertainties seemed to have been underestimated).  We
+also imposed a $G<18$ cut on any putative matches.  Of 3012 moving
+group members collected from the three combined Gagne et al{.}
+catalogs, we found 2702 matches.
+
+The \citet{kraus_tucanahor_2014}, \citet{roser_deep_2011}, and
+\citet{bell_32ori_2017} studies reported members in Tucana-Horologium,
+the Hyades, and 32$\,$Ori respectively.  Applying the same procedure as
+for the Gagne catalogs gave 187, 684, and 119 best-neighbors
+respectively, compared to 205, 724, and 141 initially reported
+members.  Note that \citet{kraus_tucanahor_2014} found that only
+$\sim$70\% of their listed members have spectroscopic indicators
+consistent with their membership in Tucana-Horologium.
+
+\citet{rizzuto_multidimensional_2011} also focused on a single moving
+group: the Sco OB2 association. We used their reported Hipparcos
+identifiers, and matched against the {\it Gaia} archive's
+\texttt{hipparcos2\_best\_neighbour} table, which gave 319
+nearest-neigbor stars from 436 candidate members.
+
+Finally, \citet{oh_comoving_2017} searched for comoving stars in the
+$\approx$2 million stars that overlapped between Tycho-2 and {\it
+Gaia}-DR1.  They found many wide binaries, and also identified a large
+number of comoving groups.  We chose the 2{,}134 stars that they
+reported were in groups with sizes of at least 3 stars.  Using their
+{\it Gaia}-DR1 source identifiers, we matched against the {\it Gaia}
+archive's \texttt{dr1\_neighbourhood} table, which gave 1{,}881
+nearest-neigbor stars in groups of at least three stars
+\citep{marrese_gaia_2019}.
+
+\subsection{Summary of selected stars}
+
+After collecting the results of all the studies described above, we
+merged them into a single table. We queried the
+\texttt{gaiadr2.gaia\_source} table to retrieve their photometric $G$,
+$G_{\rm R_p}$, and $G_{\rm B_p}$ magnitudes, as well as their
+five astrometric parameters $(\alpha, \delta, \mu_\alpha, \mu_\delta,
+\pi)$.
+We then imposed that $G_{\rm R_p} < 16$.
+The concatenated results are given in Table~N.
+
+All told, there are 1{,}308{,}706 unique stars, from 12 distinct
+membership catalogs.
+Stars that are reported in multiple catalogs have their reference
+information from each available catalog concatenated.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Method: Photometry}
@@
 steps using stand-alone programs.  A conceptual overview of our
-``pipeline'' is given in Figure~\ref{fig:pipeline}.  
+pipeline is given in Figure~\ref{fig:pipeline}.  
 Our overall method is in the spirit of the reduction approaches used
@@
 preparatory steps, including source extraction of bright stars,
-astrometry using the resulting positions, and coarse simple aperture
+astrometric calibration, and coarse simple aperture
 photometry (\S~\ref{subsec:preparation}).  Using the shape values from
-the initial astrometry, we select an astrometric reference frame and
-transform all of the calibrated images to it.  We construct a
+the initial astrometry, we select an astrometric reference frame to
+which we transform all of the calibrated images.  We construct a
 photometric reference by stacking a collection of frames, and then
-convolve all the transformed frames to the photometric reference,
-and subtract (\S~\ref{subsec:imagesubtraction}).  We perform aperture
+convolve all the transformed frames to the photometric reference, and
+subtract (\S~\ref{subsec:imagesubtraction}).  We perform aperture
 photometry on the subtracted images using positions projected onto the
 frame from Gaia DR2.  We detrend the resulting lightcurves
-(\S~\ref{subsec:lcdetrending}).
-We then select stars that we believe are ``cluster members'',
-roughly X\% of the overall dataset (\S~\ref{sec:starselection}).
-Focusing on the lightcurves of these stars, their white noise and red
-noise properties, and point out a few interesting cases of
-variability (\S~\ref{sec:results}).
+(\S~\ref{subsec:lcdetrending}).  We then select stars that we believe
+are ``cluster members'', roughly X\% of the overall dataset
+(\S~\ref{sec:starselection}).  Focusing on the lightcurves of these
+stars, their white noise and red noise properties, and point out a few
+interesting cases of variability (\S~\ref{sec:results}).
 
@@
 systematics as well as astrophysical variability.  The detrending
-philosophy adopted by the HAT group typically proceeeds in two
+approach adopted by the HAT group typically proceeeds in a few
 sequential stages (see discussions from {\it e.g.}
-\citealt{bakos_2010,huang_high-precision_2015,zhang_precision_2016}) .
-The first stage is to decorrelate against external parameters that are
+\citealt{bakos_2010,huang_high-precision_2015,zhang_precision_2016}).
+Given the heritage of our pipeline, we briefly discuss these, and then
+explain why we omit most of the steps described.
+
+The first detrending step commonly performed on ground-based data is
+``magnitude-fitting'': the raw magnitudes measured from the difference
+images are fit by a polynomial that depends on a combination of CCD
+position, sub-pixel position, and optionally catalog magnitude and
+color.
+
+The second step is to decorrelate against external parameters that are
 known to affect the stellar flux measurements (EPD,
-\citealt{bakos_2010}). The second stage is to filter remaining
-systematic trends caused by unknown parameters by decorrelating the
-measured brightnesses of stars against each other (TFA,
-\citealt{kovacs_trend_2005}).
+\citealt{bakos_2010}).  For ground-based data this may include zenith
+angle, or changing PSF parameters.  For TESS data, this might include
+CCD temperature, or perhaps a measure of the scatter in the spacecraft
+pointing (CITE: Vanderburg 2019).
+
+The final step is to then decorrelate the measured brightnesses of
+stars against each other (TFA, \citealt{kovacs_trend_2005}).  
+This accounts for variations due to unknown systematic effects that
+affect many stars.
 
@@
 complex: ordinary linear model-fitting, as well as an initial attempts
-at non-linear model fitting, are poor descriptions of the data.  We go
-on to show (\S~\ref{sec:tfa_is_good_enough}) that a plausible
+at non-linear model fitting, are poor descriptions of the data.  
+In a similar vein ``magnitude-fitting'' is minimally justified, given
+how the TESS magnitudes correlate against these external parameters.
+We go on to show (\S~\ref{sec:tfa_is_good_enough}) that a plausible
 detrending approach for the purpose of transit discovery is to simply
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Method: Star Selection}
-\label{sec:starselection}
-
-A major motivator for the CDIPS project is to increase the number of
-cluster stars for which continuous photometric timeseries are
-available, and thus facilitate studies of exoplanetary and stellar
-processes across different times and stellar environments.
-
-An essential aspect of the project is therefore to define a {\it
-cluster star sample}, consisting of stars that are thought to be
-members of clusters.
-
-Performing a homogeneous membership determination for every known
-cluster is beyond the scope of this work.  Instead, we collect various
-cluster membership catalogs from the literature.  We then use them to
-identify cluster members for which we have already made lightcurves
-from the TESS images.  Our goal in selecting stars is completeness,
-rather than precision.  If there has been a claim in the literature
-that a star should be considered as a cluster member, we aim to
-provide a lightcurve for that star.
-
-Table~N describes the cluster membership catalogs we have used to
-identify candidate cluster members.  Since our photometric reduction
-is based on positions reported in {\it Gaia DR2}, each of our
-lightcurve sources by default is associated with a Gaia identifier.
-Correspondingly, the cluster membership determinations performed by
-\citet{cantat-gaudin_gaia_2018} and \citet{gaia_hr_2018} are the
-easiest case for us to merge against our lightcurve database.
-For the TESS Sectors 1--5 lightcurves produced in this study, this
-yielded X and Y lightcurves respectively.
-
-%FIXME: make table
-
-\subsection{Open clusters (OCs)}
-\label{subsec:oc}
-
-\paragraph{{\it Gaia}-derived OC memberships}
-At the time of writing, two relatively large, homogeneous cluster
-memberships studies had been performed using {\it Gaia}-DR2: those by
-\citet{cantat-gaudin_gaia_2018} and \citet{gaia_hr_2018}.
-
-\citet{cantat-gaudin_gaia_2018} used an unsupervised membership
-assignment algorithm to identify clusters in the three-dimensional
-astrometric space of proper motion and parallax. They used {\it Gaia}
-photometry and radial velocities to then verify the claimed
-membership properties.  From their Table~2, we collect 401{,}448
-cluster members, in 1229 clusters, down to a limiting magnitude of
-$G=18$.
-
-\citet{gaia_hr_2018} reported memberships for stars in a smaller, more
-select group of well-studied open clusters. From their Table~A1, we
-collect 40{,}903 cluster members, in 41 open clusters, mostly within
-$500\,{\rm pc}$. While this work also included memberships for
-globular clusters, we omitted these from consideration.
-
-\paragraph{Pre-{\it Gaia} OC memberships}
-\citet{Kharchenko_et_al_2013} used proper motions calculated in PPMXL
-\citep[][a combination of USNO-B1{.}0 and 2MASS
-astrometry]{roeser_ppmxl_2010} and near-infrared photometry from 2MASS
-\citep{skrutskie_tmass_2006} and reported the existence of 2859 open
-clusters and stellar associations.
-We selected their ``$1\sigma$'' members according to the
-combined photometric, kinematic, and spatial criteria described by
-\citet{kharchenko_global_2012}.  Then, to obtain {\it Gaia}-DR2 source
-identifiers for the members, we performed a crossmatch for {\it
-Gaia}-DR2 sources within 5 arcseconds of the listed positions.  As an
-additional constraint, we used the 2MASS photometry to predict the
-$G$-band magnitudes\footnote{See
-\url{https://gea.esac.esa.int/archive/documentation/GDR2/Data_processing/chap_cu5pho/sec_cu5pho_calibr/ssec_cu5pho_PhotTransf.html},
-online, \texttt{2019-03-29}, or \citet{carrasco_gaia_2016}}, and
-required that the measured $G$-magnitude fall within 2 magnitudes of
-the predicted $G$-magnitude.  If multiple neighbors matched the
-position and magnitude constraints, we took the nearest spatial
-neighbor as the match.  From 373{,}226 stars, this yielded a unique
-best neighbor for 352{,}332 stars (94.4\% of the sample), and a choice
-between two neighbors for 17{,}774 stars.
-
-The second (non-{\it Gaia} derived) open cluster membership catalog we
-used was the \citet{dias_proper_2014} catalog, which was based on
-UCAC4 proper motions.
-From their 1805 reported open clusters, we selected sources with
-quoted membership probability above 50\%.
-To obtain {\it Gaia}-DR2 source identifiers for the members, we
-performed a similar crossmatch as before, looking for sources within 5
-arcseconds of the listed positions, and within $\pm$2 $G$-band
-magnitudes of the prediction.
-From 2{,}034{,}269 stars, this yielded a unique
-best neighbor for 1{,}828{,}630 stars (89.9\% of the sample), and a choice
-between two neighbors for 8.7\% of the remaining sample.
-
-\begin{figure*}[!ht]
-  \gridline{\fig{f5a.png}{0.95\textwidth}{}}
-  \vspace{-0.8cm}
-  \gridline{\fig{f5b.png}{0.95\textwidth}{}}
-  \caption{
-      {\it Top.} Cross-match statistics from \cite{Kharchenko_et_al_2013} {\it 
-      vs.} Gaia-DR2.
-      {\it Bottom.} Ditto, for \cite{dias_proper_2014} {\it vs.} Gaia-DR2.
-  }
-  \label{fig:xmatch_info}
-\end{figure*}
-
-The distributions of various cross-matching statistics are shown in
-Figure~\ref{fig:xmatch_info}.  The distances between matches is
-typically below 1 arcsecond.  The Dias catalog shows somewhat stronger
-crowding effects at the faint end compared to the Kharchenko catalog.
-The Kharchenko catalog also has a more lop-sided distribution of true
-{\it vs.} predicted $G$-band magnitudes.
-
-\subsection{Moving groups and stellar associations}
-\label{subsec:mg}
-
-Stars, moving groups and stellar associations are of interest for
-similar reasons as stars in open clusters.  Though fewer stars
-are known to exist in moving groups, they are of particular interest
-because moving groups are less crowded than open clusters, and are
-often closer to the Sun.
-
-We obtained Gaia DR2 identifiers from the results of the following
-studies:
-\citet{gagne_banyan_XI_2018},
-\citet{gagne_banyan_XII_2018},
-\citet{gagne_banyan_XIII_2018},
-\citet{kraus_tucanahor_2014},
-\citet{roser_deep_2011}, % OC, not MG...
-\citet{bell_32ori_2017},
-\citet{rizzuto_multidimensional_2011},
-and \citet{oh_comoving_2017}, The methods applied in these studies
-vary from kinematic analyses, to astrometric analyses included
-Gaia-DR1 parallaxes, to photometric searches for infrared excesses, to
-spectroscopic studies including RVs, H$\alpha$
-emission, and Li absorption.
-
-For the Gagne et al{.} catalogs, we searched the Gaia-DR2 archive for
-sources within 10 arcseconds of the listed positions.  If Gagne et
-al{.} gave a proper motion, we required that the sign of each the Gaia
-proper motion components match that of the Gagne values (the stated
-proper motion uncertainties seemed to have been underestimated).  We
-also imposed a $G<18$ cut on any putative matches.  Of 3012 moving
-group members collected from the three combined Gagne et al{.}
-catalogs, we found 2702 matches.
-
-The \citet{kraus_tucanahor_2014}, \citet{roser_deep_2011}, and
-\citet{bell_32ori_2017} studies reported members in Tucana-Horologium,
-the Hyades, and 32$\,$Ori respectively.  Applying the same procedure as
-for the Gagne catalogs gave 187, 684, and 119 best-neighbors
-respectively, compared to 205, 724, and 141 initially reported
-members.  Note that \citet{kraus_tucanahor_2014} found that only
-$\sim$70\% of their listed members have spectroscopic indicators
-consistent with their membership in Tucana-Horologium.
-
-\citet{rizzuto_multidimensional_2011} also focused on a single moving
-group: the Sco OB2 association. We used their reported Hipparcos
-identifiers, and matched against the {\it Gaia} archive's
-\texttt{hipparcos2\_best\_neighbour} table, which gave 319
-nearest-neigbor stars from 436 candidate members.
-
-Finally, \citet{oh_comoving_2017} searched for comoving stars in the
-$\approx$2 million stars that overlapped between Tycho-2 and {\it
-Gaia}-DR1.  They found many wide binaries, and also identified a large
-number of comoving groups.  We chose the 2{,}134 stars that they
-reported were in groups with sizes of at least 3 stars.  Using their
-{\it Gaia}-DR1 source identifiers, we matched against the {\it Gaia}
-archive's \texttt{dr1\_neighbourhood} table, which gave 1{,}881
-nearest-neigbor stars in groups of at least three stars
-\citep{marrese_gaia_2019}.
-
-\subsection{Summary of selected stars}
-
-After collecting the results of all the studies described above, we
-merged them into a single table. We queried the
-\texttt{gaiadr2.gaia\_source} table to retrieve their photometric $G$,
-$G_{\rm R_p}$, and $G_{\rm B_p}$ magnitudes, as well as their
-five astrometric parameters $(\alpha, \delta, \mu_\alpha, \mu_\delta,
-\pi)$.
-We then imposed that $G_{\rm R_p} < 16$.
-The concatenated results are given in Table~N.
-
-All told, there are 1{,}308{,}706 unique stars, from 12 distinct
-membership catalogs.
-Stars that are reported in multiple catalogs have their reference
-information from each available catalog concatenated.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Results}

### 2019-05-23 drivers/do_initial_period_finding.py
add drivers/paper_get_CDIPS_star_stats.py
* how many are there total?
* what fraction come from which sources?
* how many are single-source claims?
* how many are multi-source claims?

@@ -55,8 +55,8 @@ def run_periodograms(source_id, tfa_time, tfa_mag, period_min=0.5,
 
     model = transitleastsquares(bls_times, bls_flux)
     results = model.power(use_threads=1, show_progress_bar=False,
-                          R_star_min=0.13, R_star_max=3.5, M_star_min=0.1,
-                          M_star_max=2.0, period_min=period_min,
+                          R_star_min=0.13, R_star_max=10, M_star_min=0.1,
+                          M_star_max=4.0, period_min=period_min,
                           period_max=period_max, n_transits_min=2,
                           transit_template='default', oversampling_factor=4)
 

### 2019-05-23 drivers/paper_get_CDIPS_star_stats.py

@@ -1,0 +1,50 @@
+"""
+analyze stats of cdips stars.
+
+* how many are there total?
+* what fraction come from which sources?
+* how many are single-source claims?
+* how many are multi-source claims?
+
+python paper_get_CDIPS_star_stats.py &> ../logs/paper_get_CDIPS_star_stats.log
+"""
+
+import pandas as pd, numpy as np
+from collections import Counter
+
+cdipspath = '/home/luke/local/cdips/catalogs/OC_MG_FINAL_GaiaRp_lt_16_v0.3.csv'
+
+df = pd.read_csv(cdipspath, sep=';')
+
+n_stars = len(df)
+
+refs = np.array(df['reference'])
+cnt = Counter(refs)
+mostcommon = cnt.most_common(n=10)
+
+ismult = np.array([',' in r for r in refs])
+issing = ~ismult
+
+n_single = len(refs[issing])
+n_mult = len(refs[ismult])
+
+print(
+"""
+From {cdipspath}
+
+Total number of stars with G_Rp < 16: {n_stars}
+
+Most common sources are:
+{mostcommon}
+
+There are {n_single} single-source claims.
+
+There are {n_mult} claims from multiple sources.
+""".format(
+    cdipspath=cdipspath,
+    n_stars=n_stars,
+    mostcommon=repr(mostcommon),
+    n_single=n_single,
+    n_mult=n_mult
+)
+)

### 2019-05-23 paper/ms.tex
paper: wrote some

@@
 \shortauthors{Bouma et al.}
-\shorttitle{CDIPS I: Method \& Sector 6}
+\shorttitle{CDIPS I: Method \& Sectors 6--8}
 
@@
   The Cluster Difference Imaging Photometric Survey (CDIPS).
-  I. Method \& TESS Light Curves from Sector 6
+  I. Method, Light Curves, and Planet Candidates from Sectors 6--8
 }
@@
 Despite the geometric rarity of transits, photometric monitoring can
-be performed in parallel, while spectroscopy cannot.
-This enabled thousands of planet detections with the Kepler spacecraft
-(CITE: Borucki, Morton).
+be performed in parallel; with precise spectroscopy this has not
+yet been achieved.
+Parallel photometric monitoring enabled thousands of planet detections
+with the Kepler spacecraft (CITE: Borucki, Morton).
 The abundance of planets from Kepler taught us about statistics
@@
 nearly all-sky coverage, can capitalize on both.
-TESS observes more stars than Kepler, for on average less time.
+
 One class of rare weirdo to which TESS is sensitive is stars in
@@
 
-Cluster stars have been monitored photometrically from the ground
+Cluster stars have been photometered from the ground for a while
 (CITE: Joel thesis, Cambridge group).
@@
 
-Yet, there are formidable obstacles to deriving precise photometry
+However, there are formidable obstacles to deriving precise photometry
 from the {\it TESS} images because of the relatively poor angular
@@
 We have begun to produce photometry from the TESS images.
+For the time being, we are adopting the difference imaging (or
+optionally, ``image subtraction'') technique, because of its
+benefits in modelling complex backgrouds in crowded regions.
+
 In what follows, \S~\ref{sec:method} presents BLAH, and
@@
 processes across different times and stellar environments.
-
 An essential aspect of the project is therefore to define a {\it
-cluster star sample}, consisting of stars that are thought to be
+cluster star sample}, made of stars that are thought to be
 members of clusters.
@@
 Performing a homogeneous membership determination for every known
-cluster is beyond the scope of this work.  Instead, we collect various
-cluster membership catalogs from the literature.  We then use them to
-identify cluster members for which we have already made lightcurves
-from the TESS images.  Our goal in selecting stars is completeness,
-rather than precision.  If there has been a claim in the literature
-that a star should be considered as a cluster member, we aim to
-provide a lightcurve for that star.
+cluster is beyond the scope of the current work.  Instead, we collect
+various cluster membership catalogs from the literature.  We then use
+them to identify cluster members within the TESS images.  In initially
+selecting stars, we aim for completeness, not accuracy.  If there has
+been a claim in the literature that a star should be considered a
+cluster member, we would like to report a light curve for the star.
+For stars that are photometrically interesting, we can perform post-hoc
+cluster membership quality checks using Gaia DR2 astrometry and photometry.
 
@@
 is based on positions reported in {\it Gaia DR2}, each of our
-lightcurve sources by default is associated with a Gaia identifier.
+light curve sources by default is associated with a Gaia identifier.
 Correspondingly, the cluster membership determinations performed by
 \citet{cantat-gaudin_gaia_2018} and \citet{gaia_hr_2018} are the
-easiest case for us to merge against our lightcurve database.
-For the TESS Sectors 1--5 lightcurves produced in this study, this
-yielded X and Y lightcurves respectively.
+easiest case for us to merge against our light curve database.
+For the TESS Sectors 1--5 light curves produced in this study, this
+yielded X and Y light curves respectively.
 
@@
 
-\subsection{Open clusters (OCs)}
+\subsection{Big catalogs: open clusters}
 \label{subsec:oc}
@@
 photometry and radial velocities to then verify the claimed
-membership properties.  From their Table~2, we collect 401{,}448
-cluster members, in 1229 clusters, down to a limiting magnitude of
+membership properties.  From their Table~2, we collect an initial 401{,}448
+cluster members, in 1229 clusters, down to their limiting magnitude of
 $G=18$.
@@
 astrometry]{roeser_ppmxl_2010} and near-infrared photometry from 2MASS
-\citep{skrutskie_tmass_2006} and reported the existence of 2859 open
+\citep{skrutskie_tmass_2006} to report the existence of 2859 open
 clusters and stellar associations.
@@
 
+%FIXME is this it?
 The second (non-{\it Gaia} derived) open cluster membership catalog we
@@
 
-\subsection{Moving groups and stellar associations}
+\subsection{Smaller catalogs: moving groups and stellar associations}
 \label{subsec:mg}
@@
 \citet{rizzuto_multidimensional_2011},
-and \citet{oh_comoving_2017}, The methods applied in these studies
+\citet{oh_comoving_2017}, and
+\citet{zari_3d_2018}. The methods applied in these studies
 vary from kinematic analyses, to astrometric analyses included
@@
 
-Finally, \citet{oh_comoving_2017} searched for comoving stars in the
+Next, \citet{oh_comoving_2017} searched for comoving stars in the
 $\approx$2 million stars that overlapped between Tycho-2 and {\it
@@
 
+Finally, \citet{zari_3d_2018} constructed a sample of young stars
+within $500\,{\rm pc}$ using data from Gaia-DR2. Two subsamples were
+made: (a) an upper main sequence (MS) sample, with 86{,}102 stars, and
+(b) a pre-MS sample, with 43{,}719 stars.  Each was created from a
+careful combination of distinct astrometric and photometric cuts.
+These stars are the youngest, closest stars, spread across
+star-forming complexes in Sco-Cen, Orion, Vela, Taurus, and other
+regions of the sky.  Though many are not strictly identified with
+moving groups or open clusters, their reported youth and proximity to star
+forming regions justifies their inclusion in our search sample.
+
 \subsection{Summary of selected stars}
 
-After collecting the results of all the studies described above, we
-merged them into a single table. We queried the
+After collecting the aforementioned lists, we
+merged them into a single table. We then queried the
 \texttt{gaiadr2.gaia\_source} table to retrieve their photometric $G$,
-$G_{\rm R_p}$, and $G_{\rm B_p}$ magnitudes, as well as their
-five astrometric parameters $(\alpha, \delta, \mu_\alpha, \mu_\delta,
-\pi)$.
-We then imposed that $G_{\rm R_p} < 16$.
-The concatenated results are given in Table~N.
-
-All told, there are 1{,}308{,}706 unique stars, from 12 distinct
+$G_{\rm Rp}$, and $G_{\rm Bp}$ magnitudes, as well as their
+astrometric measurements $(\alpha, \delta, \mu_\alpha, \mu_\delta,
+\pi)$.  Finally, we required that $G_{\rm Rp} < 16$.
+
+All told, this procedure yielded 1{,}061{,}447 unique stars, from 13 distinct
 membership catalogs.
-Stars that are reported in multiple catalogs have their reference
-information from each available catalog concatenated.
+
+107{,}647 of these stars, or about
+10\% of the collection, have cluster memberships reported by
+multiple authors.  The largest number of stars come from
+\citealt{dias_proper_2014} (44.3\% of stars), \citealt{Kharchenko_et_al_2013}
+(17.3\%), \citealt{cantat-gaudin_gaia_2018} (16.7\%), and \citealt{zari_3d_2018}
+(11.1\%).
+Stars reported in multiple catalogs have all available reference information
+concatenated.  
+The resulting CDIPS target star list is given in Table~N.
 
@@
 	\end{center}
-	\vspace{-0.5cm}
+	\vspace{-0.2cm}
 	\caption{
-    {\bf Pipeline.} This is what we do.
+    {\bf Conceptual overview of photometric reduction pipeline.}
+    Details are given in \S~\ref{sec:method}.
 	\label{fig:pipeline}
@@
 
-We reduced the TESS images to lightcurves by performing a sequence of
-steps using stand-alone programs.  A conceptual overview of our
-pipeline is given in Figure~\ref{fig:pipeline}.  
-Our overall method is in the spirit of the reduction approaches used
+We reduced the TESS images to light curves by performing a sequence of
+steps using stand-alone programs.
+Our overall method is in the spirit of the reduction approaches described
 by \citet{Pal_2009}, \citet{soares-furtado_image_2017} and
-\citet{oelkers_precision_2018}.
-
-We begin with the calibrated full frame images produced by SPOC
-(\S~\ref{subsec:observations}).  We then perform a collection of
+\citet{oelkers_precision_2018}; a conceptual overview is given in
+Figure~\ref{fig:pipeline}.
+
+We begin with the calibrated full frame images produced by the Science
+Processing Operations Center at NASA Ames (\S~\ref{subsec:observations}).
+We then perform a collection of
 preparatory steps, including source extraction of bright stars,
@@
 which we transform all of the calibrated images.  We construct a
-photometric reference by stacking a collection of frames, and then
-convolve all the transformed frames to the photometric reference, and
+photometric reference by stacking a collection of frames,
+convolve the transformed frames to this photometric reference, and
 subtract (\S~\ref{subsec:imagesubtraction}).  We perform aperture
 photometry on the subtracted images using positions projected onto the
-frame from Gaia DR2.  We detrend the resulting lightcurves
-(\S~\ref{subsec:lcdetrending}).  We then select stars that we believe
-are ``cluster members'', roughly X\% of the overall dataset
-(\S~\ref{sec:starselection}).  Focusing on the lightcurves of these
-stars, their white noise and red noise properties, and point out a few
-interesting cases of variability (\S~\ref{sec:results}).
+frame from Gaia DR2.  
+We detrend the resulting light curves
+(\S~\ref{subsec:lcdetrending}).  The resulting white noise and red noise properties
+of the light curves, and a few
+interesting cases of variability, are discussed in \S~\ref{sec:results}.
 
@@
 keep its cameras pointed opposite the Sun, the spacecraft advances by
-$\approx$$28$ degrees in ecliptic longitude every lunar month.  Data
+$\approx$$28$ degrees east in ecliptic longitude every lunar month.  Data
 acquired throughout each ``sector'' are downlinked at spacecraft
@@
 For us, the main data product of interest is the calibrated full frame
-image (FFI).  Each TESS camera reads out every 2 seconds.  To produce
+image (FFI).  Each TESS camera is read out every 2 seconds.  To produce
 a manageable telemetric load, the resulting pixel values are averaged
@@
 includes an overscan, bias, and dark current correction, and also
-divides out a flat field.  The details are given by
+divides out a flat field.  Details are discussed by
 \citet{clarke_kepler_2017}, and the resulting science data products
@@
 
-\subsection{Image Preparation \& Background Removal}
+While we performed numerous initial tests on the first sectors of data,
+by geometric coincidence Sectors 1--5 fell away from the galactic plane.
+Less than 2\% of the CDIPS target star sample
+is therefore observed in the first five TESS sectors.
+Though a few interesting clusters are present ({\it e.g.}, Blanco~1, NGC~2516, NGC~1901),
+for the time being we opted to focus on sectors in which there were stars
+of interest for our intended science.
+These begin in Sector 6 (2018-12-12, spacecraft orbit \#19).
+
+\subsection{Image Preparation, Background Removal, \& Meta-Data Collection}
 \label{subsec:preparation}
@@
 
-We then estimate the background of each frame.  We do this by
-temporarily masking out pixels more than $2\sigma$ from the median,
-and then passing a $48\times48$ median box filter over each pixel in
-the image, using reflective boundary conditions. We subtract out this
-smooth background estimate from each image.  This step helps mitigate
-two unwanted image artifacts.  First, it removes a low-level glow
+In order to pre-emptively address the background
+variations present in some frames due to scattered light from the
+Earth and Moon \citep[see][\S 7.3.1--7.3.4]{vanderspek_2018},
+we then estimate and subtract the large-scale background.
+We do this by
+temporarily masking out pixels more than $2\sigma$ from the image median,
+and then pass a $48\times48$ median box filter over each pixel in
+the image, with reflective boundary conditions. 
+We blur the resulting background estimate with a gaussian kernel,
+which produces a
+smooth background estimate for each image.  These steps also remove
+a low-level vignetting
 present in the corners of many images, which remains even after
-flat-fielding \citep[see][\S 7.3.5]{vanderspek_2018}.  Second,
-background subtraction removes scattered light patches from the Earth
-and Moon, which vary in positions around the camera boresight over
-each spacecraft orbit \citep[see][\S 7.3.1--7.3.4]{vanderspek_2018}.
-The typical size of scattered light patches is greater than 48 pixels,
-and their typical amplitude is $\sim 10\times$ the sky background
-level.
+flat-fielding \citep[see][\S 7.3.5]{vanderspek_2018}.
+With the exception of scattered-light caustics, which remain in small
+areas of less than 10\% of the frames, this ad-hoc procedure removes
+large spatial scale scattered light patches.
 
@@
 % scale.  Such features may affect flux measurements at specific times
-% in a small subset of lightcurves.
+% in a small subset of light curves.
 
@@
 are metadata to the image, and are only applied to the
-pixel values during the specific image processing steps ({\it e.g.},
-convolution) in which they are necessary. We also extend the masks
+pixel values during the specific image processing steps in which they
+are necessary ({\it e.g.}, convolution). We also extend the masks
 beyond purely saturated pixels to ``bloomed'' pixels horizontally and
-vertically adjacent to the saturated pixels using the algorithm
-described by \citet{Pal_2009}.
+vertically adjacent to the saturated pixels (see Figure~6 of \citealt{Pal_2009}).
 
@@
 to the ``momentum dumps'' and ``coarse pointing modes'' described by
-\citet{vanderspek_2018}, we mask out the entire frame.  This removes
+\citet{vanderspek_2018}, we omit the entire frame.  This removes
 on average a few frames per sector. Through visual inspection, we see
@@
 notes\footnote{\url{ archive.stsci.edu/tess/tess_drn.html}} to
-identify further  times with anomalously poor spacecraft performance,
-which we omit from consideration. For Sectors 1 through 5, these
-include coarse pointing windows from orbits 10, 13, 14, and an
-instrumetal anomaly window in orbit 15.
-
-Next, we perform some initial analysis steps to produce metadata
+identify further times with anomalous spacecraft performance,
+which we omit from consideration.
+%For Sectors 1 through 5, these
+%include coarse pointing windows from orbits 10, 13, 14, and an
+%instrumetal anomaly window in orbit 15.
+For Sectors 6 through 8, these include three days at the beginning of
+Sector 6 dedicated to acquiring pixel response function data, and also
+about three days during Sector 8 lost to an instrument anomaly.
+%FIXME for sectors 6 thru 8
+
+Having prepared the images, we perform some initial analysis steps
+to produce metadata
 needed during image subtraction.  To obtain an astrometric solution
-(independent from the WCS data packaged with the frames), we use
+(independent from the solution included with the frames), we use
 \texttt{fistar} to perform source extraction on bright stars in each
@@
 With the resulting WCS information, we then project a source catalog
-from Gaia-DR2 onto the frame, down to a pre-selected magnitude cutoff
-\citep{gaia_collaboration_gaia_2018}.  We use these expected positions
+onto each frame.
+Initially, we intended to photometer all Gaia-DR2 sources in each field
+down to a cutoff of $G_{Rp} < 16$.
+However, we found that for the galactic plane fields this produces an
+excessively large number of sources.
+Our source catalog for each frame is therefore a combination of
+the CDIPS target stars ($G_{Rp} < 16$), and all Gaia-DR2 sources down to
+$G_{Rp} < 13$.
+We use the expected positions of these sources
 to center the apertures in our photometry, rather than attempting to
 detect the positions.  Such ``forced-aperture photometry'' is
-preferable to performing source extraction because of the large TESS
-pixels, and the accurate Gaia positions.  The Gaia-DR2 epoch is
+preferable to performing source extraction simply because the TESS
+pixels are large, and we are operating in crowded fields.
+The Gaia-DR2 epoch is
 J2015.5, so even the fastest-moving stars with proper motions of
 $\sim$$1\,{\rm arcsecond}\,{\rm yr}^{-1}$ are still well within one pixel
-of their predicted positions in the TESS images.  The projection and
-catalog-indexing is performed using
+of their predicted positions in the TESS images.  The projection from
+catalog sky-coordinate positions to pixel coordinates
+is performed using standard WCS transformations, 
+and the source catalog look-up is
+performed using
 \texttt{gaia2read}\footnote{\url{github.com/samuelyeewl/gaia2read}}
@@
 
-Finally, we perform aperture photometry on the bright stars from the
+Finally, we use \texttt{fiphot} to perform aperture photometry on the
+bright stars from the
 source list, by summing the counts inside appropriately-weighted
@@
 entirely within the aperture, and fractional along the aperture
-boundary (e.g., \citealt{Pal_2009} Fig 17). 
+boundary (see \citealt{Pal_2009} Fig 17). 
 The background levels are measured in annuli around each aperture
@@
 background variations.
+We model the background separately, so we set $B_{xy}=0$.
 The convolution kernel $K$ is typically decomposed onto a
@@
     \chi^2 = \sum_{xy} \left( \frac{I_{xy} - M_{xy}}{\sigma_{xy}} \right)^2,
+    \label{eq:chisq_conv}
 \end{equation}
@@
 $D_{xy} = I_{xy} - M_{xy}$.
-
-% FIXME: describe gaussian kernel (used in e.g., KELT, and maybe other 
-%pipelines?). Perhaps give Eqns for delta kernel.
-The choice of kernel ...
-
-We then select two ``reference frames'' for image subtraction.
-The first is the astrometric reference; the second is the photometric
-reference.
-To choose the astrometric reference, we use the following heuristics:
-\begin{enumerate}
-  \item The frame must have large and round stars (largest ``S'',
-    smallest ``D'' and ``K'' values).
-  \item The frame must minimal background noise, as measured in annuli
+For this work, the uncertainty in each target image pixel is
+taken to be a constant.
+
+The procedure described above was first proposed by \citet{Alard_Lupton_1998}.
+It was reviewed and clarified by \citet{miller_optimal_2008}.
+The choice of how to decompose the kernel was further clarified by
+\citet{bramich_new_2008}, who showed that using a delta function
+had a few select advantages compared to a basis of gaussians.
+We perform the convolution using \texttt{ficonv}, and opt for
+the implementation of Bramich's method (see \citealt{Pal_2009} Section 2.8).
+
+For posterity, we note a few implementation details.
+We must select two ``reference frames'' for image subtraction:
+(1) the astrometric reference; (2) the photometric reference.
+
+To choose the astrometric reference, we search for frames with
+the largest and roundest stars (big $s$, small $d$ and $k$ values).
+We also require
+that the frame must minimal background noise, as measured in annuli
 around the bright stars selected in \S~\ref{subsec:preparation}.
-  \item The frame must have, relative to the other frames being
+Finally, the astrometric reference frame must have, relative to the 
+other frames being
 considered, a large number of detected sources.
-\end{enumerate}
-We sort the frames using the above metrics, and then select the
+We sort the frames using these metrics, and then select the
 astrometric reference from successive intersections of each sorted
@@
 Using the algorithm presented by \citet{pal_astrometry_2006}, we then
-calculate a spatial transformation that maps the X and Y coordinates
-from each calibrated frame onto the the astrometric reference.
-
-``Registering'' the images onto a common astrometric reference frame
-requires some care. In particular, the transformation must preserve
-the fluxes of the sources. Since the transformation is affine (a
-combination of {\it e.g.}, translation, rotation, dilation, and shear)
-standard bilinear or bicubic interpolation would not achieve flux
-conservations.  We therefore use the flux-conserving interpolation
-scheme described by \citet{Pal_2009} which is based on analytic
-integration of the surfaces determined by the pixel values. 
-%FIXME: is this interpolation scheme definitely being applied?
-The largest component of the transformation is a translation, of order
-2 arcseconds, or about 0.1 TESS pixels.
-
-The second reference frame needed for image subtraction is the
-photometric reference.  Generically, if one were to simply subtract
-two arbitrary frames, the noise level in the resulting difference
-image would be $\sqrt{2}$ times greater than that in the original
-target frame.
-To minimize this effect, we create a high-SNR median average of
-$N$ selected frames, so that the noise level in the resulting
-subtracted images goes as $\sqrt{1+1/N}$.
-This ``photometric reference'' is used both to calculate the
-convolution kernel during image subtraction, and to measure the
-reference flux of each star.
-To select viable frames for inclusion in the photometric reference, we
-use the results of our initial photometry step
-(\S~\ref{subsec:preparation}), and sort frames for each sector by:
-\begin{enumerate}
-  \item Lowest median scatter in photometry
-  \item Lowest median error in photometry
-  \item Lowest median background measurement
-  \item Lowest median absolute deviation in background measurements
-  \item Largest number of stars detected by \texttt{fiphot} with good
-    flags.
-    % fiphot files used for all of this.
-\end{enumerate}
+use the \texttt{grtrans} tool to
+calculate an affine transformation that maps each calibrated frame
+to the astrometric reference.
+We use the flux-conserving interpolation
+scheme described by \citet{Pal_2009} to minimize photometric errors
+incurred during this step --
+standard bilinear or bicubic interpolation do not achieve flux
+conservation.  
+The largest component of the transformation is typically a translation,
+of order 2 arcseconds, or about 0.1 TESS pixels.
+%FIXME: EXPLAIN THIS BETTER
+
+The second reference frame is the
+photometric reference, which is used both to calculate the
+convolution kernel, and to obtain a
+reference flux for each star.  
+To minimize Poisson errors, our photometric refernce is a median average of
+$N=50$ selected frames.
+The sub-frames are chosen to have low scatter in their photometry,
+and low background measurements, using the metadata collected
+in \S~\ref{subsec:preparation}.
 We convolve the 50 best candidate photometric references to the best
@@
 
-%FIXME: it seems like it would be smart to produce a photometric
-%reference for different intervals of time. 480 frames over 10 days ->
-%perhaps split the full 28 day sector entirely by momentum dumps to
-%get ~10 photometric references per sector.
-
-%FIXME: LEFT OFF HERE
-Some details of, and motivation for, the convolution process are warranted.
-The general idea of the image subtraction problem is to...
-
-This has some benefits for crowded regions. Most notably, in enables a
-measurement of the background flux level.
-
-Our approach follows from the algorithm presented by
-\citet{Alard_Lupton_1998}, and explained in detail by
-\citet{miller_optimal_2008}.
-The process is: %FIXME: following miller 2008...
-\begin{enumerate}
-  \item Select a set of isolated stars (``stamps'').
-  (For ficonv, the default procedure is: grid up the image. Within
-    each grid... find the brightest nonsaturated region. Use that to
-    fit the kernel!)
-  \item Choose basis vectors $K_n$ for the kernel, $K = \sum_{n=1}^N
-    a_n K_n$. Our goal is to determine the best-fitting coefficients
-    $a_n$. 
-  \item Using these stamps and the least-squares method, ...
-\end{enumerate}
-
-%FIXME: when do we actually get the reference fluxes? Where do those
-%come from???
-
-Finally, we convolve and subtract all the frames that have been
-translated from the photometric reference (\texttt{grcombine}).
-We use the same kernel formalism as described by
-\citet{soares-furtado_image_2017}.
-To compute the convolution kernel, we minimize the difference between
-each image and the photometric reference (or something like this),
-using the Alard \& Lupton 1998 method (CITE, also CITE Miller's
-reference).
-The software implementation is that by \citet{Pal_2009}, in the
-\texttt{ficonv} program.
-The implemented math is as follows.
-\begin{equation}
-  XXX = XXX. %FIXME: maybe Soares pg 5 main equation?
-\end{equation}
-We explored a variety of kernel options, including X, Y, and Z.
-We wound up including an ``identity'' term (MEANING?), a ``background
-term'' (MEANING?) and a delta function term (MEANING? Give math for
-all of these).
-There are also spatially-varying terms of order XX. (MEANING?)
-% I believe this means that we should be able to somehow _visualize_
-% the kernel as a function of spatial position in the image. What
-% should it look like? Is it like a star's PSF? Or somehow related??
-
-We perform forced-aperture photometry on the subtracted frames,
-using the locations from the Gaia projection, to measure the resulting
-difference fluxes.
-We use circular apertures, with the appropriate weigths along the
-boundaries (\texttt{fiphot}; \citet{Pal_2009} Section FIXME).
-
-Note that to measure the fluxes on the differenced images, a
-slightly different procedure from Eq.~\ref{eq:simple_aperture_phot} is
-relevant.
-(Pal 2009 Section 2.9).
-Specifically, the subtracted image $S$ is given by $I - B - R\ast K$,
-for $I$ the original image, $B$ the background, $R$ the reference
-image, and $K$ the convolution kernel.
-The flux in the original image is given by
-%FIXME: this equation IS PROBABLY WRONG. I_xy? Or S_xy?
+%\begin{enumerate}
+%  \item Lowest median scatter in photometry
+%  \item Lowest median error in photometry
+%  \item Lowest median background measurement
+%  \item Lowest median absolute deviation in background measurements
+%  \item Largest number of stars detected by \texttt{fiphot} with good
+%    flags.
+    % fiphot files used for all of this.
+%\end{enumerate}
+
+To measure the reference flux for each star, we go a bit further.
+First, we perform forced simple aperture photometry to measure
+the flux for each source.
+The local background is estimated in annuli, with neighboring stars
+masked out during the background measurement.
+If we were to stop here, {\it it would be a bad mistake}.
+The reference flux for faint stars would be overestimated, due to
+crowding.
+The relative amplitude of photometric signals would correspondingly
+be biased small, hindering exoplanet detection.
+Therefore, after performing simple aperture photometry on the 
+reference frame, we fit for an for aperture-size specific zero point
+that relates each star's catalog $T$-band magnitude to the
+measured flux.
+The $T$-band magnitude is calculated according to Equation~1 of 
+Stassun et al (2019, CITE).
+Crowding is minimzed down to Gaia's resolution limit.
+We then use the known catalog magnitude to predict the expected
+photometric reference flux.
+
+The final instrumental flux values we report (for example,
+the \texttt{IFL1} column) are similar to \citealt{Pal_2009} Equation~83:
 \begin{align}
-  f &= \sum_{x,y} w_{x,y} I_{x,y} \\
+f &= f_{\rm subtracted} + f_{\rm reference} \\
 &=
-       \frac{1}{|| K ||_1^2} \sum_{x,y} S_{x,y} (w \ast K)_{x,y}
+\frac{1}{|| K ||_1^2} \sum_{x,y} S_{x,y} (w \otimes K)_{x,y}
 +
-       \sum_{x,y} R_{x,y} w_{x,y},
+g \left(T_{\rm cat} \right),
+\label{eq:ism_flux_measurement}
 \end{align}
+for the subtracted image $S$, which is equal to $I -  R\otimes K$,
+where $I$ is the original image transformed to the astrometric
+reference, $R$ is the photometric reference, and $K$ is the convolution
+kernel.
+The weights $w$ from the circular aperture mask are matched to
+the image convolution.
+The function $g$ takes as input the target star's
+catalog magnitude $T_{\rm cat}$, and returns the reference flux.
+Its coefficients have been fit per the procedure 
+discussed in the preceding paragraph.
 %FIXME: derive this equation. why exactly does this work?
 
-Finally, to convert from a list of sources on each frame to a list of
-flux values at any given time, we use the \texttt{grcollect}
-transposition tool.
-
-\subsection{Lightcurve Detrending}
+A few brief notes on the algorithm to actually solve for the 
+coefficients to the convolution kernel.
+The procedure implemented in \texttt{ficonv} is to grid up
+the image, and within each grid element find the brightest non-saturated
+star. These isolated ``stamp'' stars are then used to solve for the
+coefficients of the kernel, by minimizing
+Equation~\ref{eq:chisq_conv}.
+
+%NOTE : this is kind of incomprehensible
+%CHECK: does the polynomial weighting actually do what you want it to do?
+For the choice of basis, we opt for a delta-function kernel with an additive
+flux scaling term (\citealt{soares-furtado_image_2017} Section 3.3.1
+gives the equations).
+The spatial variations of the PSF are captured by weighting the 
+delta function and the flux scaling terms with varying
+polynomial orders across the image.
+Choosing this kernel introduces three additional
+free parameters:
+(1) the kernel box-size;
+(2) the maximum order of the polynomial weighting the delta function terms;
+(3) the maximum order of the polynomial weighting the flux scaling.
+We performed a grid-search to tune these parameters, in
+which our main metrics for success included the measured RMS as
+a function of magnitude, and also the recovered SNR of transits from
+known TOIs (CITE: Guerrero et al in prep 2019).
+
+Varying the kernel box-size, we found that kernels with box-length smaller than the 
+typical TESS FWHM at field center ($\approx$3 pixels) produced light curves
+with the highest average scatter.
+Increasing the kernel box-size from a $3\times3$ box to a $7\times7$ box led
+to about a 50\% reduction in RMS for bright stars, and no difference for 
+faint stars.
+The largest kernels, of $(11\times11)$ pixels, had on average slightly lower 
+signal-to-noise for recovered transits than for kernels of intermediate size.
+We settled on a kernel box-size of $(7\times7)$ pixels, in part because the 
+FWHM at the camera corners can grow by factors of $\approx$2 relative to the 
+field center.
+
+Varying the polynomial orders, we found that the highest order polynomials 
+retrieved transits with $\approx10\%$ worse SNR compared to lower order
+polynomials.
+Varying the polynomial orders between 1 and 4 did not produce large 
+differences.
+
+Averaging over all TOIs present in the camera we used for these experiments, 
+we found that different choices 
+of kernel parameters produced variations of $\lesssim 12\%$ in the retrieved 
+transit SNR.  
+For computational expediency, we therefore chose a $(7\times 7)$ kernel with 
+second-order spatial polynomial weights in the basis functions.
+However, we caution that within our parameter-tuning experiments, the 
+recovered SNR of perhaps a third of the TOIs varied by up to a factor of two,
+which in a few 
+cases would have lead to non-detections of objects near the noise floor.
+In the longer term, developing an image-subtraction method that marginalizes 
+over uncertainties of how to chose ``optimal'' kernels would be desirable.
+Pixel-level image subtraction methods that omit these 
+parameters entirely 
+are also worth exploring \citep{wang_pixel-level_2017}.
+
+With a kernel selected, and the convolution and subtraction performed, 
+we calculate the instrumental fluxes on each frame per 
+Equation~\ref{eq:ism_flux_measurement}. To finally convert from a list of 
+sources on each frame to a list of flux values at any given time, we use the 
+\texttt{grcollect} transposition tool.
+
+\subsection{Light curve Detrending}
 \label{subsec:lcdetrending}
 
-The preceding steps produce lightcurves that include both instrumental
+The preceding steps produce light curves that include both instrumental
 systematics as well as astrophysical variability.  The detrending
-approach adopted by the HAT group typically proceeeds in a few
+approach adopted by the HAT group typically proceeds in a few
 sequential stages (see discussions from {\it e.g.}
@@
 position, sub-pixel position, and optionally catalog magnitude and
-color.
+color \citep[][Sec.~5.5]{zhang_precision_2016}.
 
@@
 known to affect the stellar flux measurements (EPD,
-\citealt{bakos_2010}).  For ground-based data this may include zenith
+\citealt[][~Appendix]{bakos_2010}).  For ground-based data this may include zenith
 angle, or changing PSF parameters.  For TESS data, this might include
-CCD temperature, or perhaps a measure of the scatter in the spacecraft
+CCD temperature, or perhaps some measure of the scatter in the spacecraft
 pointing (CITE: Vanderburg 2019).
@@
 stars against each other (TFA, \citealt{kovacs_trend_2005}).  
-This accounts for variations due to unknown systematic effects that
-affect many stars.
+This accounts for variations due to unknown systematic
+instrument changes that affect many stars.
 
 %FIXME TURGID PROSE
-In general though, one must adapt detrending procedures to the data at
-hand.  In \S~\ref{sec:flux_vs_external_parameters}, we show that the
+In \S~\ref{sec:flux_vs_external_parameters}, we show that the
 ``external parameter'' dependence visible in the TESS data is rather
@@
 		\leavevmode
-		\includegraphics[width=0.7\textwidth]{f3.png}
+		\includegraphics[width=0.6\textwidth]{f3.png}
 	\end{center}
@@
     \begin{center}
-		\includegraphics[height=0.95\textheight]{f4.png}
+		\includegraphics[height=0.9\textheight]{f4.png}
     \end{center}
-    \vspace{-0.8cm}
+    \vspace{-0.5cm}
     \caption{
@@
 
-The traditional approach to EPD 
-\citep[][]{Pal_2009,bakos_2010,zhang_precision_2016} is to fit and
+The traditional approach to EPD is to fit and
 subtract a model for the magnitudes $m$ of the form
-
 \begin{equation}
@@
 \end{equation}
-
 where $\vec{\theta}$ is a vector of parameters such as the shape
@@
 included in the engineering
-data\footnote{\url{archive.stsci.edu/missions/tess/engineering/}}.  },
+data: \url{archive.stsci.edu/missions/tess/engineering/}.  },
 the centroid positions $(x,y)$, the fractional part of the
@@
 flux.  The coefficients $c_i$ are calculated through linear
-least-squares, and subtracted to produce ``EPD'' lightcurves.
+least-squares, and subtracted to produce ``EPD'' light curves.
 
@@
 \citet{zhang_precision_2016} have verified that this model is a
-reasonable description to the data.
-
+good description to the data.
 To discern whether such a model extends to the TESS data, we examined
@@
 
-\item {\it Flux vs. time}. Most of the lightcurves we examined showed a secular
+\item {\it Flux vs.\ time}. Most of the light curves we examined showed a secular
     drift with amplitude $0.01\,{\rm mag}$ over the timescale of each
@@
     2.5$\,{\rm day}$ momentum dumps was also noticeable in more of the
-    lightcurves at the center of the field than at the corners.
-
-\item {\it Flux vs. centroid positions}. The flux as a function of
+    light curves at the center of the field than at the corners.
+
+\item {\it Flux vs.\ centroid positions}. The flux as a function of
   centroid position often showed non-linear ``hooks'' (see Figure
@@
     given orbit reside at a given
-    level, but about 10\% are in a tail. This was seen in lightcurves
+    level, but about 10\% are in a tail. This was seen in light curves
     all across the TESS field of view.
 
-\item {\it Flux vs. temperature} exhibited similar hooks, with most of
+\item {\it Flux vs.\ temperature} exhibited similar hooks, with most of
   the flux values residing at a particular level, and perhaps 10\%
@@
 
-\item {\it Flux vs. shape parameters}.  For lightcurves in the corner
+\item {\it Flux vs.\ shape parameters}.  For light curves in the corner
   of the field of view, similar hooks are present in flux {\it vs.}
@@
 
-\item {\it Centroid positions vs. time}.  The main variability in the
+\item {\it Centroid positions vs\ time}.  The main variability in the
   centroid positions as a function of time is a secular drift, that is
@@
 
-\item {\it Temperature vs. time}.  The main variability in temperature
+\item {\it Temperature vs.\ time}.  The main variability in temperature
   {\it vs.} time is a secular drift of the same timescale as that for
@@
 
-\item {\it Shape parameters vs. time}.  The main variability in the
+\item {\it Shape parameters vs.\ time}.  The main variability in the
   shape parameters as a function of time is the 2.5 day momentum wheel
@@
 
-\item {\it Background value vs. time}.  The background is typically stable, 
+\item {\it Background value vs.\ time}.  The background is typically stable, 
 except when scattered light from the Earth or Moon enters the frame (visible 
@@
 showed some initial promise, even with ``optimal'' knot-selection (in
-the BIC sense) it introduced undesirable residuals in the lightcurves,
+the BIC sense) it introduced undesirable residuals in the light curves,
 and also distorted transits.
+One thought that we did not try but may explore in future work
+is to use the decorrelate against the scatter of the quartnerion 
+time-series (CITE: Vanderburg, 2019).
 
@@
 vectors of {\it e.g.}, centroid positions, temperatures, and shape
-parameters in our reported lightcurves.
+parameters in our reported light curves.
 
@@
 stars, we opt to decorrelate the flux timeseries of each star
-against other stars in the frame (TFA, \citealt{kovacs_trend_2005}).
-
-%TODO: write out the procedure, give a model equation!
-
-This requires selecting ``template stars'', which are a subsample of
-star that are supposed to represent all the types of systematics
-across the dataset. 
-%FIXME: clarify this procedure
-We select XXX template stars randomly from the stars on-chip with
-$G_{\rm R_p}$ magnitudes between 8.5 and 13 (TODO: rather bright?).
-As an initial variability cut, we fit a parabola in the RMS-magnitude
-plane, and discarding stars more than $2\sigma$ away from the
+against other stars in the frame.
+We use the TFA algorithm proposed by
+\citet{kovacs_trend_2005}, which for self-consistency we reproduce
+here.
+The idea of the method is somewhat simpler than the PDCMAP
+algorithm used in the SPOC pipeline (CITE).
+Suppose we have $M$ ``template stars'', which are a subsample of
+stars that represent all types of systematics across the dataset. 
+Each template star has a light curve with $N$ data points.
+Denote the template time-series $X_j(i)$, where $j={1,\ldots,M}$ and 
+$i={1,\ldots,N}$ is the time index.
+We then want to find periodic signals in a target time-series $Y(i)$.
+This is done by defining a filter function
+\begin{equation}
+F(i) = \sum_{j=1}^{M} c_j X_j(i),
+\end{equation}
+for which the coefficients $c_j$ are found by minimizing
+\begin{equation}
+\mathcal{D} = \sum_{i=1}^{N} \left[ Y(i) - A(i) - F(i) \right]^2.
+\label{eq:tfa_to_minimize}
+\end{equation}
+When trying to find periodic signals, $A(i)$ represents our prior
+knowledge of the light curve's shape.
+This prior is simply that stars on average maintain a constant brightness:
+\begin{equation}
+A(i) = \langle Y \rangle = \frac{1}{N} \sum_{i=1}^{N} Y(i) = {\rm const.}
+\end{equation}
+If a signal is eventually found, for instance using the box-least squares
+method \citep{kovacs_box-fitting_2002},
+this detrending process must then be repeated while accounting for our
+updated knowledge about the light curve's shape.
+
+Some notes on our implementation follow.
+We select template stars in two stages.
+In the first stage, we fit a parabola in the RMS-magnitude
+plane, and discard stars more than $2\sigma$ away from the
 prediction of the fit.
-
+We also require that these initial candidate stars have intermediate
+brightness ($8.5 > T > 13$), and have a relatively large number
+of time-series data points.
 We then perform an initial iteration of TFA, on only the candidate
 template stars.
-We inspect the resulting detrended lightcurves for residual
+We inspect the resulting detrended light curves for residual
 structure by computing a Lomb-Scargle periodogram.
@@
 we exclude the star from the list of candidate template stars, on the
-basis of its presumed periodic variability signal.
-
-We then randomly select 200 template stars from the remaining
+basis of its presumed periodic variability.
+We then randomly select at most 200 template stars from the remaining
 non-variable candidates. 
-The choice of number of template stars was discussed by (CITE KOVACS).
+The choice of number of template stars was discussed by
+\citet{Kovacs_et_al_2005}, and is another free parameter in
+the broad problem of light curve production.
 While it can be optimized by constructing and minimizing a BIC-like 
@@
 
-Once the template stars are selected, we use the secret TFA
-implementation from the \texttt{HATpipe} source code, that you and
-nobody else is allowed to see.
-% It's at /home/lbouma/proj/HATpipe/source/lc/frontends/tfa.c, I
-% believe. We could perhaps use the vartools equivalent of this.
-
-To select template stars, we impose a
-
-The details of this selection procedure are
+Once the template stars are selected, we use the \texttt{VARTOOLS}
+program to perform the detrending \citep{Hartman_Bakos_2016}.
+This process is performed for each photometric aperture
+separately.
 
@@
 
+\subsection{Light Curve Statistics}
+
 RMS vs mag plots.
 
+ACF statistics.
+
 SNR of retrieved HJs.
 
+Maybe movies of subtracted images?
+
 Some stellar variability plots (perhaps of known stellar variables).
 
-Some focus on actual cluster fields.
-
+Some focus on particular clusters.
+
+\subsection{Objects of Interest}
+\label{subsec:ctois}
+
+As an initial search for transiting planets, strong stellar rotators, and 
+eclipsing binaries, we performed a few steps of post-processing. For 
+simplicity,
+we chose a single aperture size~--~``aperture 2''~--~with a radius of 1.5 
+pixels, to perform the period search.
+
+First, to identify periodic transit-like signals, we used 
+\citet{hippke_TLS_2019}'s transit least-squares (TLS) tool.
+The algorithm is the same as the canonical box least-squares
+\citep{kovacs_box-fitting_2002}, except in place of a box template, a transit 
+template is used  for a marginal improvement of the detection efficiency.
+In addition, the search grids in the \texttt{tls} 
+implementation\footnote{\url{https://github.com/hippke/tls}} are slightly more 
+efficient than in most BLS implementations, since it uses the 
+cubic-in-frequency sampling advocated for by \citet{ofir_optimizing_2014}, 
+rather than standard linear-in-frequency sampling.
 During the period search, we rejected $6\,{\rm hours}$ at the
@@
 of systematic false positives in subsequent vetting.
+We also ran a generalized Lomb-Scargle periodogram (CITE), simply to 
+have additional periodicity information.
+
+We then performed a cut on the TLS signal detection efficiency:
+${\rm SDE} > 12$.
+This yielded XXX light curves, and we then
+performed TFA signal reconstruction on these lightcurves using 
+\texttt{vartools}.
+In this process, the model lightcurve $A(i)$ in 
+Equation~\ref{eq:tfa_to_minimize} is set to the phase-binned signal from the 
+most powerful peak in the TLS spectrum, rather than being a constant function. 
+Generally speaking, this helps improve the quality of the resulting light 
+curve.
+
+We then make a multi-page \texttt{.pdf} document with the information 
+necessary to make classifications for vetting.
+These documents are released along with the light curves, as a useful summary
+ for anyone interested in the subset of objects that we have analyzed.
+A full description of each page of the summary \texttt{.pdf} is given in the 
+Appendix.
+
+The classifications we used assess:
+\begin{enumerate}
+    \item {\it The source of photometric variability}. Designations include 
+    tags for planet candidates, eclipsing binaries, instrumental variations, 
+    stellar variations, and ``weirdos''.
+    \item {\it Cluster membership status}. By default, all light curves were 
+    made for stars with at least one literature claim of cluster membership.  
+    We therefore include tags only for non-cluster members, and possible 
+    non-cluster members. Typically the primary source of this information is 
+    the Gaia-DR2 parallax.
+    \item {\it Photometric blends}. Tags are created to highlight whether the 
+    depth of the photometric signal shows a strong dependence on aperture 
+    size, and also whether the in-transit minus the out-of-transit images 
+    reveal that the source of variability is in fact far from the target star.
+\end{enumerate}
+The actual classification process was performed by LGB, JH, and JNW.
+The \texttt{TagSpaces} software was used~--~an extremely helpful tool for the 
+purposes of easily assigning labels to documents.
+
+% FIXME FIXME FIXME
 
@@
 	Gaia \citep{gaia_collaboration_gaia_2016,gaia_collaboration_gaia_2018},
-	2MASS \citep{skrutskie_tmass_2006}
+	2MASS \citep{skrutskie_tmass_2006},
+    DSS (CITE)    
 }
@@
   \texttt{astroquery} \citep{astroquery_2018},
+  \texttt{astroquery.gaia}
+  \texttt{astroquery.simbad}
+  \texttt{astroquery.mast}
+  \texttt{astroquery.nasaexopanetarchive}  
   \texttt{BATMAN} \citep{kreidberg_batman_2015},
@@
   \texttt{pandas} \citep{mckinney-proc-scipy-2010},
-  \texttt{scipy} \citep{jones_scipy_2001}.
+  \texttt{scipy} \citep{jones_scipy_2001},
+  \texttt{TagSpaces} (CITE),
+  \texttt{tesscut} (CITE)
 }
@@
 
-% \appendix -- only if needed
+\appendix
+\section{Time system \& barycentric correction}
+The time-stamps included with the calibrated TESS Full Frame Images
+produced by SPOC include a barycenteric correction at
+a single reference pixel given at the middle of every frame.
+The barycentric correction is at maximum 16 minutes, corresponding to
+points on the sky separated by 180 degrees.
+The angular distance from a TESS camera's center of field to the corners
+is $\approx$17 degrees, so naively one might incur at worst an error of
+$\approx$90 seconds on the time-stamps due to using a barycentric
+correction in a direction that is slightly wrong.
+Perhaps due to the lead author's obsession with getting time-stamps correct 
+\citep{bouma_wasp-4b_2019},
+we perform our own barycentric correction using the appropriate
+sky coordinates for each light curve.
+We advise use of our \texttt{TMID\_BJD} column, which gives the
+mid-time of each exposure in the BJD$_{\rm TDB}$ time system, which
+is the defacto standard in exoplanet and stellar
+astronomy~\citep{eastman_achieving_2010}.
+
+\section{Vetting Document Description}
+
+In \S~\ref{subsec:ctois}, we described the process by which we made 
+\texttt{.pdf} documents suitable for assessing which objects were interesting 
+enough to merit further study.
+
+This section briefly summarizes this document. Updated versions and their 
+\texttt{README} files will live at this web-address: 
+\url{mast.stsci.edu/CDIPS}.
+
+\begin{itemize}
+\item {\it Page 1: period-search summary}. Periodograms from TLS and 
+phase-dispersion minimization 
+\citep{hippke_TLS_2019,stellingwerf_period_1978}, as calculated 
+with \texttt{astrobase.periodbase} are shown. The top three peaks from each 
+method are shown in the second and third rows; the raw light curve is in the 
+top-right. A small finder chart from DSS is shown (CITE).
+
+\item {\it Page 2: light curve diagnostics}.
+\end{itemize}
 

### 2019-05-23 paper/collect_figures.sh

@@ -12,7 +12,7 @@ cp ${fdir}GI_figs/cluster_positions_ecliptic_scicase.pdf \
    ${pdir}f1_PLACEHOLDER.pdf
 
 # placeholder for what our pipeline does
-cp ${fdir}pipeline_figure.pdf ${pdir}f2.pdf
+cp ${fdir}trex_overview.pdf ${pdir}f2.pdf
 
 
 

### 2019-05-29 paper/ms.tex
did astrometry
paper: update figures and text

@@
 		\leavevmode
-		\includegraphics[width=0.7\textwidth]{f1_PLACEHOLDER.pdf}
+		\includegraphics[width=0.7\textwidth]{cluster_positions.pdf}
 	\end{center}
@@
 \begin{figure*}[!ht]
-  \gridline{\fig{f5a.png}{0.95\textwidth}{}}
+  \gridline{\fig{astromresidual_hist.png}{0.5\textwidth}{}}
   \vspace{-0.8cm}
-  \gridline{\fig{f5b.png}{0.95\textwidth}{}}
+  \gridline{\fig{astromresidual_quiver.png}{0.5\textwidth}{}}
+  \vspace{-0.8cm}
+  \gridline{\fig{astromresidual_apertures.png}{0.5\textwidth}{}}
   \caption{
-      {\it Top.} Cross-match statistics from \cite{Kharchenko_et_al_2013} {\it 
-      vs.} Gaia-DR2.
-      {\it Bottom.} Ditto, for \cite{dias_proper_2014} {\it vs.} Gaia-DR2.
+      {\it Top.} Histogram
+      {\it Middle.} Vector
+      {\it Bottom.} Apertures
   }
@@
 		\leavevmode
-		\includegraphics[width=0.3\textwidth]{f2.pdf}
+		\includegraphics[width=0.3\textwidth]{pipelineoverview.pdf}
 	\end{center}
@@
 preparatory steps, including source extraction of bright stars,
-astrometric calibration, and coarse simple aperture
+astrometric verification, and coarse simple aperture
 photometry (\S~\ref{subsec:preparation}).  Using the shape values from
@@
 \label{subsec:preparation}
+
+\begin{figure*}[!ht]
+  \gridline{\fig{mwscmatchstats.png}{0.95\textwidth}{}}
+  \vspace{-0.8cm}
+  \gridline{\fig{dias14matchstats.png}{0.95\textwidth}{}}
+  \caption{
+      {\it Top.} Cross-match statistics from \cite{Kharchenko_et_al_2013} {\it 
+      vs.} Gaia-DR2.
+      {\it Bottom.} Ditto, for \cite{dias_proper_2014} {\it vs.} Gaia-DR2.
+  }
+  \label{fig:xmatch_info}
+\end{figure*}
 
@@
 to produce metadata
-needed during image subtraction.  To obtain an astrometric solution
-(independent from the solution included with the frames), we use
-\texttt{fistar} to perform source extraction on bright stars in each
-image.  We pass the resulting source lists through
-\texttt{astrometry.net} \citep{lang_2010}, which returns an
-astrometric solution for each frame packaged in the WCS format
-\citep[][Sec.~8]{pence_fits_2010}.  During the initial source
+needed during image subtraction.
+
+First, we use \texttt{fistar} to perform source extraction on bright
+stars in each image.
+uring the initial source
 extraction, we also fit elongated gaussians to the bright stars,
@@
 
+For the astrometric solution, we use the WCS and SIP coefficients
+derived by SPOC and included in the FFI headers \citep[][Sec.~8]{pence_fits_2010}.  We
+explored the possibility of using \texttt{astrometry.net}
+\citep{lang_2010} to derive our own astrometric solutions for each
+frame, but found that the astrometric residual (the mean separation
+between projected and measured positions) was consistently a factor of
+1.5-2x higher in our WCS solutions than in those given by SPOC.
+
 With the resulting WCS information, we then project a source catalog
-onto each frame.
-Initially, we intended to photometer all Gaia-DR2 sources in each field
-down to a cutoff of $G_{Rp} < 16$.
-However, we found that for the galactic plane fields this produces an
-excessively large number of sources.
-Our source catalog for each frame is therefore a combination of
-the CDIPS target stars ($G_{Rp} < 16$), and all Gaia-DR2 sources down to
-$G_{Rp} < 13$.
-We use the expected positions of these sources
-to center the apertures in our photometry, rather than attempting to
-detect the positions.  Such ``forced-aperture photometry'' is
-preferable to performing source extraction simply because the TESS
-pixels are large, and we are operating in crowded fields.
-The Gaia-DR2 epoch is
-J2015.5, so even the fastest-moving stars with proper motions of
-$\sim$$1\,{\rm arcsecond}\,{\rm yr}^{-1}$ are still well within one pixel
-of their predicted positions in the TESS images.  The projection from
-catalog sky-coordinate positions to pixel coordinates
-is performed using standard WCS transformations, 
-and the source catalog look-up is
-performed using
+onto each frame.  Initially, we planned to photometer all Gaia-DR2
+sources in each field down to a cutoff of $G_{Rp} < 16$.  However, we
+found that for the galactic plane fields this produces an excessively
+large number of sources.  Our source catalog for each frame is
+therefore a combination of the CDIPS target stars ($G_{Rp} < 16$), and
+all Gaia-DR2 sources down to $G_{Rp} < 13$.  We use the expected
+positions of these sources to center the apertures in our photometry,
+rather than attempting to detect the positions.  Such
+``forced-aperture photometry'' is preferable to performing source
+extraction in the crowded fields that are the focus of this work.  The
+Gaia-DR2 epoch is J2015.5, so even the fastest-moving stars with
+proper motions of $\sim$$1\,{\rm arcsecond}\,{\rm yr}^{-1}$ are still
+well within one pixel of their predicted positions in the TESS images.
+The projection from catalog sky-coordinate positions to pixel
+coordinates is performed using standard WCS transformations, and the
+source catalog look-up is performed using
 \texttt{gaia2read}\footnote{\url{github.com/samuelyeewl/gaia2read}}
 \citep{kim_2018_gaia2read}.
+The astrometric residual is displayed in various forms in
+Figure~\ref{fig:astrometricresidual}.
 
@@
 we calculate the instrumental fluxes on each frame per 
-Equation~\ref{eq:ism_flux_measurement}. To finally convert from a list of 
+Equation~\ref{eq:ism_flux_measurement}. 
+We do this with three different aperture sizes: for this work, circles
+of radii 1 pixel, 1.5 pixels, and 2.25 pixels.
+These sizes were chosen to roughly span the range of optimal aperture
+sizes for stars in our sample, as calcuated in the pre-flight
+\citet{Sullivan_et_al_2015} work.
+To finally convert from a list of 
 sources on each frame to a list of flux values at any given time, we use the 
@@
 
-\subsection{Light curve Detrending}
+\subsection{Light Curve Detrending}
 \label{subsec:lcdetrending}
@@
 		\leavevmode
-		\includegraphics[width=0.6\textwidth]{f3.png}
+		\includegraphics[width=0.6\textwidth]{epdparams_vs_time.png}
 	\end{center}
@@
     \begin{center}
-		\includegraphics[height=0.9\textheight]{f4.png}
+		\includegraphics[height=0.9\textheight]{mag_vs_epdparams.png}
     \end{center}

### 2019-05-29 paper/collect_figures.sh

@@ -7,22 +7,45 @@
 fdir=../paper/figures/
 pdir=../paper/
 
-# placeholder for positions of clusters
+# positions of clusters
 cp ${fdir}GI_figs/cluster_positions_ecliptic_scicase.pdf \
-   ${pdir}f1_PLACEHOLDER.pdf
+   ${pdir}cluster_positions.pdf
 
-# placeholder for what our pipeline does
-cp ${fdir}trex_overview.pdf ${pdir}f2.pdf
+# what our pipeline does
+cp ${fdir}trex_overview.pdf ${pdir}pipelineoverview.pdf
+
+fdir=../results/
+# catalog matching statistics
+cp ${fdir}catalog_to_gaia_match_statistics_MWSC.png \
+   ${pdir}mwscmatchstats.png
+
+cp ${fdir}catalog_to_gaia_match_statistics_Dias14.png \
+   ${pdir}dias14matchstats.png
 
 
+# placeholding wcs
+fdir=../results/astrometric_residual
+cp ${fdir}/proj1510-s0006-cam3-ccd3-combinedphotref-onenight_apertures_on_frame_x_954t1094_y_954t1094.png \
+   ${pdir}astromresidual_apertures.png
+
+cp ${fdir}/proj1500-s0006-cam1-ccd1-combinedphotref-onenight_spocwcs_sep_hist.png \
+   ${pdir}astromresidual_hist.png
+
+cp ${fdir}/proj1500-s0006-cam1-ccd1-combinedphotref-onenight_spocwcs_quiver_meas_proj_sep.png \
+   ${pdir}astromresidual_quiver.png
+
+
+##########################################
 
 lcdir=../results/projid1088_cam2_ccd2_lcs/center_lcs/
 # plot of (mag,x,y,T,s,d,k,bkgd) vs time
-cp ${lcdir}EPDparams_vs_time_frac1.0_4979427719678442752_llc.png ${pdir}f3.png
+cp ${lcdir}EPDparams_vs_time_frac1.0_4979427719678442752_llc.png \
+   ${pdir}epdparams_vs_time.png
 
 # plot of mag vs (t,T,x,y,s,d,k) for four stars
 lcdir=../results/projid1088_cam2_ccd2_lcs/
-cp ${lcdir}IRM1_vs_EPD_parameters_fourstars_norbit1.png ${pdir}f4.png
[…]

### 2019-05-30 paper/ms.tex

@@
 For the astrometric solution, we use the WCS and SIP coefficients
-derived by SPOC and included in the FFI headers \citep[][Sec.~8]{pence_fits_2010}.  We
-explored the possibility of using \texttt{astrometry.net}
-\citep{lang_2010} to derive our own astrometric solutions for each
-frame, but found that the astrometric residual (the mean separation
-between projected and measured positions) was consistently a factor of
-1.5-2x higher in our WCS solutions than in those given by SPOC.
+derived by SPOC and included in the FFI headers
+\citep[][Sec.~8]{pence_fits_2010}.  We explored the possibility of
+using \texttt{astrometry.net} \citep{lang_2010} to derive our own
+astrometric solutions for each frame, but found that the astrometric
+residual (the mean separation between projected and measured
+positions) was consistently a factor of 1.5-2 times higher in our WCS
+solutions than in those given by SPOC (perhaps attributable to the
+algorithm used to select stars and measure their positions).
 
@@
 found that for the galactic plane fields this produces an excessively
-large number of sources.  Our source catalog for each frame is
-therefore a combination of the CDIPS target stars ($G_{Rp} < 16$), and
+large number of sources (millions of stars per
+$12^\circ\times12^\circ$ CCD).  We therefore limited our source
+catalog for each frame to be
+a combination of the CDIPS target stars ($G_{Rp} < 16$), and
 all Gaia-DR2 sources down to $G_{Rp} < 13$.  We use the expected
-positions of these sources to center the apertures in our photometry,
+projected of these sources to center the apertures in our photometry,
 rather than attempting to detect the positions.  Such
 ``forced-aperture photometry'' is preferable to performing source
-extraction in the crowded fields that are the focus of this work.  The
+extraction in the crowded fields that are central in this work.  The
 Gaia-DR2 epoch is J2015.5, so even the fastest-moving stars with
@@
 The projection from catalog sky-coordinate positions to pixel
-coordinates is performed using standard WCS transformations, and the
-source catalog look-up is performed using
+coordinates is performed using an analog of the \texttt{wcs-rd2xy}
+program that performs the standard matrix algebra \citep{lang_2010}.
+The source catalog look-up is performed using
 \texttt{gaia2read}\footnote{\url{github.com/samuelyeewl/gaia2read}}
 \citep{kim_2018_gaia2read}.
-The astrometric residual is displayed in various forms in
+
+The astrometric residual is displayed for one photometric reference
+frame (to be described shortly) in
 Figure~\ref{fig:astrometricresidual}.
+A few salient points can be made.
+First, the typical median precision of the WCS solution is a bit below
+0.1 pixels, and its $90^{\rm th}$ percentile is typically less than
+0.3 pixels\footnote{In fact, in our reduction we automatically impose
+that the median residual and 90th percentile remain below 0.2 and 0.4
+pixels, respectively.}.
+The distribution has a outlier tail of saturated stars which were
+masked, and thus do not have measureable centroid positions.
+The errors are typically largest in the corners of the field of view,
+where the non-linearity of the focal plane is most significant, and
+where the corrections required by the SIP coefficients are largest.
+The final sub-panel of Figure~\ref{fig:astrometricresidual} is a
+sanity check on the location of the projected positions, and also
+gives some context for our chosen aperture radii of 1, 1.5, and 2.25
+pixels.
 
@@
 each aperture, and the number of ``good'' objects that are detected,
-are later used as input for selecting photometric reference frames.
+are later used to select photometric reference frames.
 
@@
 attempts to match a photometric reference $R$ and a target image $I$ by 
-computing a convolution kernel.
+computing and applying a convolution kernel.
+For ground-based data, this ``match'' typically corrects for
+differences in seeing or transparency between the reference and
+target; for space-based data, the match might correct for spacecraft
+jitter, or thermal and corresponding PSF variations.
 The kernel, once applied to the high signal-to noise reference,

### 2019-05-31 cdips/utils/tess_noise_model.py
paper: rms v mag plot now works

@@ -224,6 +224,7 @@ def noise_model(
     # N_pix_sel = N_pix_in_aperture_Jenkins(T_mags)
     # use sullivan's instead
     N_pix_sel = N_pixels_in_aperture_Sullivan(T_mags)
+    N_pix_sel[(N_pix_sel < 3) | (N_pix_sel > 50)] = 3
     # leave N_pix_sel as float, for smooth display at the end
     N_pix_sel = np.round(
             np.maximum(3*np.ones_like(N_pix_sel),N_pix_sel)).astype(int)
@@ -239,6 +240,8 @@ def noise_model(
     e_star_sel_ap = []
     e_sky_sel_ap = []
     for ix, sel_ind in enumerate(sel_inds):
+        if sel_ind > 50 or sel_ind < 2:
+            sel_ind = 2
         e_star_sel_ap.append(e_star_all_ap[ix,sel_ind])
         e_sky_sel_ap.append(e_sky_all_ap[ix,sel_ind])
     e_star_sel_ap = np.array(e_star_sel_ap)

### 2019-05-31 drivers/paper_plot_all_figures.py

@@ -1,3 +1,7 @@
+"""
+execution environment: cdips, + pipe-trex .pth file in
+/home/lbouma/miniconda3/envs/cdips/lib/python3.7/site-packages
+"""
 from glob import glob
 import datetime, os, pickle, shutil
 import numpy as np, pandas as pd
@@ -14,6 +18,8 @@ from astrobase import lcmath
 
 from aperturephot import get_lc_statistics
 
+from cdips.utils import tess_noise_model as tnm
+
 OUTDIR = '/nfs/phtess2/ar0/TESS/PROJ/lbouma/cdips/results/paper_figures/'
 
 def main():
@@ -25,7 +31,12 @@ def main():
     #
     # fig N: RMS vs catalog T mag
     #
-    plot_rms_vs_mag(overwrite=1)
+    plot_rms_vs_mag(overwrite=0)
+
+    #
+    # fig N: ? all-sky map of clusters observed by TESS, over the TESS footprint
+    #
+
 
     #
     # fig N: wcs quality verification
@@ -33,182 +44,6 @@ def main():
     plot_wcs_verification()
 
     pass
-
-
-def get_lc_stats(lcpaths, cdipslcdir, outpath, sectornum, cdipsvnum=1,
-                 N_desired=200):
-
-    if len(lcpaths) > N_desired:
-        selpaths = np.random.choice(lcpaths, size=N_desired, replace=False)
-    else:
-        selpaths = lcpaths
-
-    print('beginning get LC stats on {} LCs'.format(len(selpaths)))
-
-    if os.path.exists(outpath):
-        print('found {}, skip'.format(outpath))
-        return
-
-    hdrkeys = ['Gaia-ID','XCC','YCC','RA[deg]','Dec[deg]',
-               'phot_g_mean_mag','phot_bp_mean_mag','phot_rp_mean_mag',
-               'TESSMAG', 'TMAGPRED', 'TICCONT']
-    skeys = ['stdev_tf1','stdev_tf2','stdev_tf3',
-             'mad_tf1','mad_tf2','mad_tf3',
-             'stdev_sigclip_tf1','stdev_sigclip_tf2','stdev_sigclip_tf3',
-             'mad_sigclip_tf1','mad_sigclip_tf2','mad_sigclip_tf3',
-            ]
-
-    hd = {}
-    for hdrkey in hdrkeys:
-        hd[hdrkey] = []
-    for skey in skeys:
-        hd[skey] = []
-    hd['iscdips'] = []
-
-    for selpath in selpaths:
[…]

### 2019-05-31 paper/ms.tex
paper: incorporate new plots

@@
 	\caption{
-    {\bf There are many clusters; TESS looks at them.} Placeholder skymap.
+    {\bf TESS looks at many clusters.} Placeholder skymap.
 		\label{fig:clustermap}
@@
 \end{figure*}
+
+\begin{figure}[t]
+	\begin{center}
+		\leavevmode
+		\includegraphics[width=0.49\textwidth]{cam1_cluster_field_star_positions.png}
+	\end{center}
+	\vspace{-0.5cm}
+	\caption{
+    {\bf Celestial positions of light curves from Sector 6, Camera 1.}
+		\label{fig:lcradec}
+	}
+\end{figure}
 
@@
 
-RMS vs mag plots.
-
-ACF statistics.
+\begin{figure}[t]
+	\begin{center}
+		\leavevmode
+		\includegraphics[width=0.49\textwidth]{rms_vs_mag.png}
+	\end{center}
+	\vspace{-0.5cm}
+	\caption{
+    {\bf RMS vs mag for CDIPS light curves.}
+		\label{fig:rms_vs_mag}
+	}
+\end{figure}
+
+ACF statistics before and after detrending(?)
 

### 2019-06-01 drivers/do_initial_period_finding.py
update periodfinding grid a bit
26 durations
2450 periods, between 0.6 to 10.6 days

@@ -1,8 +1,8 @@
 """
 given >~10k LCs per galactic field, we want to skim the cream off the top.
 
-run as:
-$ python -u do_initial_period_finding.py &> ../logs/sector6_initial_period_finding.log &
+run as (from phtess2 usually):
+$ python -u do_initial_period_finding.py &> logs/sector6_initial_period_finding.log &
 """
 from astropy.stats import LombScargle
 from transitleastsquares import transitleastsquares
@@ -19,6 +19,15 @@ from astropy.io import fits
 
 from cdips.utils import collect_cdips_lightcurves as ccl
 from cdips.lcproc import mask_orbit_edges as moe
+
+def main():
+
+    do_initial_period_finding(
+        sectornum=6, nworkers=52, maxworkertasks=1000,
+        outdir='/nfs/phtess2/ar0/TESS/PROJ/lbouma/cdips/results/cdips_lc_periodfinding',
+        OC_MG_CAT_ver=0.3
+    )
+
 
 def run_periodograms(source_id, tfa_time, tfa_mag, period_min=0.5,
                      period_max=27, orbitgap=1, expected_norbits=2,
@@ -55,8 +64,8 @@ def run_periodograms(source_id, tfa_time, tfa_mag, period_min=0.5,
 
     model = transitleastsquares(bls_times, bls_flux)
     results = model.power(use_threads=1, show_progress_bar=False,
-                          R_star_min=0.13, R_star_max=10, M_star_min=0.1,
-                          M_star_max=4.0, period_min=period_min,
+                          R_star_min=0.1, R_star_max=10, M_star_min=0.1,
+                          M_star_max=5.0, period_min=period_min,
                           period_max=period_max, n_transits_min=2,
                           transit_template='default', oversampling_factor=4)
 
@@ -233,4 +242,4 @@ def do_initial_period_finding(
 
 
 if __name__ == "__main__":
-    do_initial_period_finding(sectornum=6)
+    main()

### 2019-06-01 paper/ms.tex

@@
 
-\begin{figure*}[!ht]
-  \gridline{\fig{astromresidual_hist.png}{0.5\textwidth}{}}
-  \vspace{-0.8cm}
-  \gridline{\fig{astromresidual_quiver.png}{0.5\textwidth}{}}
-  \vspace{-0.8cm}
-  \gridline{\fig{astromresidual_apertures.png}{0.5\textwidth}{}}
-  \caption{
-      {\it Top.} Histogram
-      {\it Middle.} Vector
-      {\it Bottom.} Apertures
-  }
-  \label{fig:xmatch_info}
-\end{figure*}
-
 The distributions of various cross-matching statistics are shown in
@@
 
+\begin{figure}[t]
+	\begin{center}
+		\leavevmode
+		\includegraphics[width=0.45\textwidth]{star_catalog_mag_histogram_phot_rp_mean_mag.png}
+	\end{center}
+	\vspace{-0.2cm}
+	\caption{
+    {\bf Cumulative counts of candidate cluster member stars a
+    function of Gaia $Rp$-band magnitude.}
+	\label{fig:cdips_targets}
+	}
+\end{figure}
+
+\begin{figure*}[!ht]
+	\gridline{\fig{mwscmatchstats.png}{0.95\textwidth}{}}
+	\vspace{-0.8cm}
+	\gridline{\fig{dias14matchstats.png}{0.95\textwidth}{}}
+	\caption{
+		{\it Top.} Cross-match statistics from \cite{Kharchenko_et_al_2013} {\it 
+			vs.} Gaia-DR2.
+		{\it Bottom.} Ditto, for \cite{dias_proper_2014} {\it vs.} Gaia-DR2.
+	}
+	\label{fig:xmatch_info}
+\end{figure*}
+
 After collecting the aforementioned lists, we
@@
 The resulting CDIPS target star list is given in Table~N.
+The distribution of target star brightnesses is shown in
+Figure~\ref{fig:cdips_targets}.
 
@@
 \begin{figure*}[!ht]
-  \gridline{\fig{mwscmatchstats.png}{0.95\textwidth}{}}
+	\gridline{\fig{astromresidual_hist.png}{0.5\textwidth}{}}
 	\vspace{-0.8cm}
-  \gridline{\fig{dias14matchstats.png}{0.95\textwidth}{}}
+	\gridline{\fig{astromresidual_quiver.png}{0.5\textwidth}{}}
+	\vspace{-0.8cm}
+	\gridline{\fig{astromresidual_apertures.png}{0.5\textwidth}{}}
 	\caption{
-      {\it Top.} Cross-match statistics from \cite{Kharchenko_et_al_2013} {\it 
-      vs.} Gaia-DR2.
-      {\it Bottom.} Ditto, for \cite{dias_proper_2014} {\it vs.} Gaia-DR2.
+		{\it Top.} Histogram
+		{\it Middle.} Vector
+		{\it Bottom.} Apertures
 	}
-  \label{fig:xmatch_info}
+	\label{fig:astromresid}
 \end{figure*}
@@
 	}
+\end{figure}
+
+\begin{figure}[t]
+	\begin{center}
+		\leavevmode
+		\includegraphics[width=0.45\textwidth]{cdf_T_mag.png}
+	\end{center}
+	\vspace{-0.5cm}
+	\caption{
+		{\bf Cumulative distribution of TESS-band magnitudes for CDIPS light curves.}
+		\label{fig:cdf_T_mag}
+	}
+\end{figure}
+
+\begin{figure}[!ht]
+	\gridline{\fig{hrd_scat_all_CDIPS_LCs.png}{0.45\textwidth}{}}
+	\vspace{-0.8cm}
+	\gridline{\fig{hrd_scat_close_subset.png}{0.45\textwidth}{}}
+	\caption{
+		{\it Top.} Stellar properties of CDIPS stars with light curves in this data release.
+		{\it Bottom.} Stellar properties of close CDIPS stars with light curves.
+	}
+	\label{fig:hrd}
 \end{figure}

### 2019-06-02 paper/ms.tex
minor text update

@@
 	\vspace{-0.5cm}
-	\caption{
-    {\bf RMS vs mag for CDIPS light curves.}
+  \caption{ {\bf Standard deviation of light curves vs catalog
+  TESS-band magnitude for CDIPS light curves.}  Faint stars in heavily
+  crowded regions have bright neighbors which drive their light curve
+  scatter below the expected noise limits.
 		\label{fig:rms_vs_mag}
@@
 template is used  for a marginal improvement of the detection efficiency.
-In addition, the search grids in the \texttt{tls} 
-implementation\footnote{\url{https://github.com/hippke/tls}} are slightly more 
-efficient than in most BLS implementations, since it uses the 
-cubic-in-frequency sampling advocated for by \citet{ofir_optimizing_2014}, 
+In addition, the search grids in \texttt{tls} 
+\footnote{\url{https://github.com/hippke/tls}} are slightly more 
+efficient than in most BLS implementations, since \texttt{tls} uses the 
+cubic-in-frequency sampling advocated by \citet{ofir_optimizing_2014}, 
 rather than standard linear-in-frequency sampling.
@@
 of systematic false positives in subsequent vetting.
+Our grids typically consisted of about 25 different durations, and
+about 2500 periods between 0.5 and 11 days.
 We also ran a generalized Lomb-Scargle periodogram (CITE), simply to 

### 2019-06-03 paper/ms.tex
paper: add lc provenance paragraphs

--- 2019-06-01 paper/ms.tex
@@
 Some focus on particular clusters.
+
+\paragraph{Light curve provenance}.
+In Sector 6, about 49{,}000 light curves of candidate cluster stars
+were made. The provenance of the claimed cluster origin of these
+sources is \citet{dias_proper_2014} for 59\% of the sources;
+\citet{zari_3d_2018} for 16\% of sources from their upper
+main-sequence table and 1\% of sources from their PMS table;
+\citet{Kharchenko_et_al_2013} for 8\% of sources,
+\citet{cantat-gaudin_gaia_2018} for 6\% of sources, and more than two
+catalogs for the remaining 10\% of sources.
+
+The clusters with the largest claimed numbers of sources are the
+Platais~6, Platais~5, and Mamajek~3 moving groups, all from
+\citet{dias_proper_2014}, composing about 7000, 7000, and 3500 sources
+respectively. These membership claims should be regarded with some
+skepticism on a source-by-source basis.  For Platais~6,
+\citet{Kharchenko_et_al_2013} claimed only about 400 probable members
+(1$\sigma$) to exist within the angular radius of the cluster.
+Mamajek~3 (32$\,$Ori) has only about 50 confirmed members
+\citep{bell_32ori_2017}.
+
+We remind the reader that our goal in creating this sample was
+completeness, rather than fidelity. The \citet{dias_proper_2014} stars
+in particular were included if they were listed with membership
+probability exceeding 50\%.  To create cleaner sub-samples, we advise
+use of the \texttt{CDEXTCAT} header keyword, which can be
+cross-matched against the original source catalog to obtain the
+membership probabilities claimed by the original catalog.
 

### 2019-06-05 drivers/get_cdips_lc_stats.py
update get lc stats

@@ -17,8 +17,21 @@ from glob import glob
 def get_cdips_lc_stats(
     sectornum=6,
     cdipssource_vnum=0.3,
-    nworkers=32
+    nworkers=32,
+    overwrite=False
 ):
+
+    projdir = '/nfs/phtess2/ar0/TESS/PROJ/lbouma/cdips'
+    statsdir = os.path.join(projdir,
+                            'results',
+                            'cdips_lc_stats',
+                            'sector-{}'.format(sectornum))
+    if not os.path.exists(statsdir):
+        os.mkdir(statsdir)
+    statsfile = os.path.join(statsdir,'cdips_lc_statistics.txt')
+    if os.path.exists(statsfile) and not overwrite:
+        print("found statsfile and not overwrite. skip")
+        return
 
     lcdirectory = (
         '/nfs/phtess2/ar0/TESS/PROJ/lbouma/CDIPS_LCS/sector-{}/'.
@@ -41,15 +54,6 @@ def get_cdips_lc_stats(
         outdf = cdipsdf[['source_id','phot_rp_mean_mag']]
 
         outdf.to_csv(catalogfile, sep=' ', index=False, header=False)
-
-    projdir = '/nfs/phtess2/ar0/TESS/PROJ/lbouma/cdips'
-    statsdir = os.path.join(projdir,
-                            'results',
-                            'cdips_lc_stats',
-                            'sector-{}'.format(sectornum))
-    if not os.path.exists(statsdir):
-        os.mkdir(statsdir)
-    statsfile = os.path.join(statsdir,'cdips_lc_statistics.txt')
 
     ap.parallel_lc_statistics(lcdirectory, lcglob,
                               catalogfile, tfalcrequired=True,

### 2019-06-05 paper/ms.tex

@@
 \end{figure*}
+
+\begin{figure}[t]
+    \begin{center}
+        \leavevmode
+        \includegraphics[width=0.49\textwidth]{sector6_cluster_field_star_positions.png}
+    \end{center}
+    \vspace{-0.5cm}
+    \caption{
+        {\bf Celestial positions of light curves from Sector 6}
+        \label{fig:lcradecsector6}
+    }
+\end{figure}
 
@@
 \subsection{Light Curve Statistics}
+\label{subsec:lcstatistics}
 
@@
 	\vspace{-0.5cm}
-  \caption{ {\bf Standard deviation of light curves vs catalog
-  TESS-band magnitude for CDIPS light curves.}  Faint stars in heavily
-  crowded regions have bright neighbors which drive their light curve
-  scatter below the expected noise limits.
+  \caption{ {\bf Standard deviation vs catalog TESS-band magnitude for
+  trend-filtered CDIPS light curves.} The minimum RMS across all three
+  aperture sizes was selected.  The photon and read noise are
+  calculated using the updated figures from \citet{vanderspek_2018}.
+  The noise from unresolved background stars is expected to be more
+  important than read noise at the faint end, but is omitted from the
+  plot due to model uncertainties (see \S~\ref{subsec:lcstatistics}).
 		\label{fig:rms_vs_mag}
@@
 	\caption{
-		{\bf Cumulative distribution of TESS-band magnitudes for CDIPS light curves.}
+    {\bf Cumulative distribution of TESS-band magnitudes for CDIPS
+    light curves.}
 		\label{fig:cdf_T_mag}
@@
 	\caption{
-		{\it Top.} Stellar properties of CDIPS stars with light curves in this data release.
-		{\it Bottom.} Stellar properties of close CDIPS stars with light curves.
+    {\it Top.} HR diagram of CDIPS stars with light curves in this
+    data release.  {\it Bottom.} HR diagram of close CDIPS stars with
+    light curves. The wedge separating the pre-MS sample from the MS
+    stars was discussed by \citet{zari_3d_2018}, who introduced it in
+    order to avoid contamination by photometric binaries.
 	}
@@
 \end{figure}
+
+\begin{figure}[!ht]
+	\gridline{\fig{pm_scat_all_CDIPS_LCs.png}{0.45\textwidth}{}}
+	\vspace{-0.8cm}
+	\gridline{\fig{pm_scat_close_subset.png}{0.45\textwidth}{}}
+	\caption{
+    {\it Top.} Proper motions of CDIPS stars with light curves in this
+    data release.  {\it Bottom.} Proper motions of close CDIPS stars
+    with light curves. A few additional clusters are visible.
+	}
+	\label{fig:propermotions}
+\end{figure}
+
+The standard deviation of the light curves is plotted as a function of the 
+catalog $T$-band magnitude for CDIPS light curves in 
+Figure~\ref{fig:rms_vs_mag}.
+Ignoring the expected noise contribution from the zodiacal and faint star 
+background, the light curves generally seem to follow the model one would 
+predict.
+The bright end is somewhat noisier than the performance reported by SPOC 
+(CITE), as well as the pipelines of 
+Chelsea (CITE) and Ben (CITE), and maybe Ryan (CITE).
+Simple aperture photometry should out-perform image subtraction techniques in 
+the bright regime, so this is not particularly unexpected.
+
+A few points concerning the noise model predictions are relevant.
+First, the effects of crowding are not apparent in 
+Figure~\ref{fig:rms_vs_mag}. 
+If the reference fluxes were being measured directly from the photometric 
+reference frame, the faint stars would be driven below the expected noise 
+floor, because the reference fluxes would be systematically overestimated.
+Our procedure for determining the reference magnitudes uses our knowledge of 
+the catalog magnitudes to eliminate this effect (REFERENCE).
+
+Second, our plot omits the noise from unresolved background stars.
+If we include it, then our RMS at the faint end is about 0.7x below the model.
+This suggests that the model over-predicts the background, or that we overfit 
+the majority of our light curves. Both are probably a little true.
 
@@
   \texttt{TagSpaces} (CITE),
-  \texttt{tesscut} (CITE)
+  \texttt{tesscut} \citep{brasseur_astrocut_2019}
 }

### 2019-06-10 paper/ms.tex
wrote an abstract

@@
 \shortauthors{Bouma et al.}
-\shorttitle{CDIPS I: Method \& Sectors 6--8}
+\shorttitle{CDIPS I: Method, Sectors 6 \& 7}
 
@@
 % BEGIN CUSTOM SHORT-CUT COMMANDS
+
+% BEGIN NUMBERS
+\newcommand{\numberpcs}{10\ }
+\newcommand{\numberlcs}{42{,}424\ }
+\newcommand{\numberclusters}{424\ }
 
@@
 \title{
-  The Cluster Difference Imaging Photometric Survey (CDIPS).
-  I. Method, Light Curves, and Planet Candidates from Sectors 6--8
+  The Cluster Difference Imaging Photometric Survey (CDIPS).  I.
+  Light Curves \& Planet Candidates in Open Clusters from TESS Sectors 6 \& 7
 }
@@
 \begin{abstract}
-  Lorem ipsum.
+  % Context
+  The Transiting Exoplanet Survey Satellite (TESS) has begun to
+  photometrically monitor almost every nearby star cluster in
+  the Galaxy.
+  % Aims
+  As part of the CDIPS project, we have begun processing the TESS
+  full-frame images to make high-precision light curves for candidate
+  members of stellar associations, moving groups, and open clusters.
+  %
+  Our eventual hope is to discover giant transiting planets, and probe
+  the exoplanet size and separation distributions for planets younger
+  than 1 Gyr.
+  %
+  For this study, we made \numberlcs light curves of candidate young
+  stars in \numberclusters clusters.
+  Each light curve repesents between 20 and 25 days of observations
+  of a star brighter than $G_{Rp}=16$, sampled at 30 minute cadence.
+  % Methods
+  We describe in detail the image subtraction and light curve
+  processing techniques we used to create the light curves, which
+  have noise properties in-line with theoretical expectations.
+  % Results
+  We then highlight the \numberpcs planet candidates identified from
+  an initial search, describe the vetting procedures that they have
+  survived, and emphasize the need for additional
+  spectroscopic and photometric observations.
+  %
+  We also comment on the possible use of the light curve sample for
+  studies of stellar rotation evolution, and binary eccentricity
+  damping.
+  %
+  The data products include both the light curves and also vetting
+  reports, all of which are available at
+  \url{archive.stsci.edu/prepds/cdips}.
 \end{abstract}

### 2019-06-12 paper/ms.tex
update the figs

@@
         \leavevmode
-        \includegraphics[width=0.49\textwidth]{sector6_cluster_field_star_positions.png}
+        \includegraphics[width=0.49\textwidth]{cluster_field_star_positions.png}
     \end{center}
@@
     \caption{
-        {\bf Celestial positions of light curves from Sector 6}
+        {\bf Celestial positions of light curves from Sectors 6 and 7.}
         \label{fig:lcradecsector6}
@@
   aperture sizes was selected.  The photon and read noise are
-  calculated using the updated figures from \citet{vanderspek_2018}.
+  calculated using the effective area from \citet{vanderspek_2018}.
   The noise from unresolved background stars is expected to be more

### 2019-06-12 paper/collect_figures.sh

@@ -45,7 +45,7 @@ cp ${fdir}rms_vs_mag.png ${pdir}rms_vs_mag.png
 cp ${fdir}cam1_cluster_field_star_positions.png ${pdir}cam1_cluster_field_star_positions.png
 
 # positions of lightcurves
-cp ${fdir}sector6_cluster_field_star_positions.png ${pdir}sector6_cluster_field_star_positions.png
+cp ${fdir}cluster_field_star_positions.png ${pdir}cluster_field_star_positions.png
 
 # CDF of T mags of LCs
 cp ${fdir}cdf_T_mag.png ${pdir}cdf_T_mag.png

### 2019-06-12 paper/ms.tex
paper minor update

@@
   % Context
-  The Transiting Exoplanet Survey Satellite (TESS) has begun to
-  photometrically monitor almost every nearby star cluster in
-  the Galaxy.
+  The Transiting Exoplanet Survey Satellite (TESS) has started to
+  photometrically monitor almost every star cluster in
+  the solar neighborhood.
   % Aims
-  As part of the CDIPS project, we have begun processing the TESS
-  full-frame images to make high-precision light curves for candidate
-  members of stellar associations, moving groups, and open clusters.
+  As part of the CDIPS project, we have been processing the TESS
+  full-frame images to make high-precision light curves stars that
+  could be members of stellar associations, moving groups, and open clusters.
   %
@@
   stars in \numberclusters clusters.
-  Each light curve repesents between 20 and 25 days of observations
+  Each light curve represents between 20 and 25 days of observations
   of a star brighter than $G_{Rp}=16$, sampled at 30 minute cadence.
   % Methods
-  We describe in detail the image subtraction and light curve
-  processing techniques we used to create the light curves, which
-  have noise properties in-line with theoretical expectations.
+  We describe in detail the image subtraction and time-series analysis 
+  techniques we used to create the light curves, which
+  have noise properties in agreement with theoretical expectations.
   % Results
-  We then highlight the \numberpcs planet candidates identified from
+  We then highlight the \numberpcs planet candidates we identified in
   an initial search, describe the vetting procedures that they have
-  survived, and emphasize the need for additional
-  spectroscopic and photometric observations.
+  survived, and emphasize the value that additional
+  spectroscopic, photometric, and imaging observations will have in
+  verify that these candidates are in fact planets.
   %
@@
   %
-  The data products include both the light curves and also vetting
-  reports, all of which are available at
+  The light curves and vetting are available at
   \url{archive.stsci.edu/prepds/cdips}.
@@
 
-A major motivator for the CDIPS project is to increase the number of
-cluster stars for which continuous photometric timeseries are
-available, and thus facilitate studies of exoplanetary and stellar
+A major aim of the CDIPS project is to increase the number of
+cluster stars for which photometric time-series are
+available, to facilitate studies of exoplanetary and stellar
 processes across different times and stellar environments.
-An essential aspect of the project is therefore to define a {\it
-cluster star sample}, made of stars that are thought to be
-members of clusters.
-
-Performing a homogeneous membership determination for every known
-cluster is beyond the scope of the current work.  Instead, we collect
-various cluster membership catalogs from the literature.  We then use
-them to identify cluster members within the TESS images.  In initially
-selecting stars, we aim for completeness, not accuracy.  If there has
+An essential step is therefore to define a sample of
+stars that are thought to be young, or members or clusters, or both.
+
+However, a homogeneous membership calculation for every known
+cluster is outside our scope.  So too is a homogeneous search for
+young stars across the galaxy.
+Instead, we opt to collect
+and concatenate appropriate catalogs from across the literature.  
+We then use the resulting meta-catalog to identify our target stars within the 
+TESS images.
+
+In our initial stellar selection our aim is therefore completeness, not 
+accuracy.  If there has
 been a claim in the literature that a star should be considered a
-cluster member, we would like to report a light curve for the star.
+cluster member, or a young star, we would like to report a light curve for the 
+star.
 For stars that are photometrically interesting, we can perform post-hoc
-cluster membership quality checks using Gaia DR2 astrometry and photometry.
-
-Table~N describes the cluster membership catalogs we have used to
-identify candidate cluster members.  Since our photometric reduction
-is based on positions reported in {\it Gaia DR2}, each of our
-light curve sources by default is associated with a Gaia identifier.
-Correspondingly, the cluster membership determinations performed by
-\citet{cantat-gaudin_gaia_2018} and \citet{gaia_hr_2018} are the
-easiest case for us to merge against our light curve database.
-For the TESS Sectors 1--5 light curves produced in this study, this
-yielded X and Y light curves respectively.
+quality checks using Gaia DR2 astrometry and photometry to assess cluster 
+membership and youth.
+
+\S~\ref{subsec:oc} describes the large catalogs we used to 
+identify candidate members of open clusters.
+\S~\ref{subsec:mg} describes the smaller catalogs we used to identify 
+candidate members of moving groups, stellar associations, as well as young 
+stars identified through combined Gaia photometry and astrometry.
+\S~\ref{subsec:ocmgsummary} then reports summary statistics for the entire 
+sample of about one million target stars.
 
@@
 
-\paragraph{{\it Gaia}-derived OC memberships}
 At the time of writing, two relatively large, homogeneous cluster
@@
 \citet{cantat-gaudin_gaia_2018} and \citet{gaia_hr_2018}.
+There were also two large membership studies based on proper motion and 
+photometric catalogs that were of interest: the studies of
+\citet{Kharchenko_et_al_2013} and \citet{dias_proper_2014}.
+
+\paragraph{{\it Gaia}-derived OC memberships}
 
@@
 globular clusters, we omitted these from consideration.
+
+In our photometric reduction,  our default identifier for all sources
+is the Gaia DR2 \texttt{source\_id}.
+The TIC identifiers are found through a spatial cross-match after the light 
+curves have been made
+\citep{stassun_TIC_2018,stassun_TIC8_2019}
+This is because Gaia DR2 is the base-catalog used to project
+sources from celestial coordinates to the imaging plane (\S~\ref{sec:method}).
+It also has the advantage that for any Gaia-derived cluster memberships, 
+we preform cross-matching directly via the source identifiers.
 
@@
 \subsection{Summary of selected stars}
+\label{subsec:ocmgsummary}
 

### 2019-06-12 paper/ms.tex
improved intro

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% The exoplanet field is evolving.
+% At the beginning, Doppler spectroscopy by the Geneva and California groups
+% led to the first exoplanet detections (CITE: Mayor 95, Butler, Marcy).
+% Some of these planets transited (CITE: Henry, Charbonneau).
+% Despite the geometric rarity of transits, photometric monitoring can
+% be performed in parallel; with precise spectroscopy this has not
+% yet been achieved.
+% Parallel photometric monitoring enabled thousands of planet detections
+% with the Kepler spacecraft (CITE: Borucki, Morton).
+% The abundance of planets from Kepler taught us about statistics
+% (CITE: Howard, Fressin, Petigura).
+% By nature of its design, Kepler left open two major avenues for
+% improvement: (i) brighter stars, (ii) rare weirdos.
+% TESS (CITE: Ricker), by nature of its small, wide-field cameras, and
+% nearly all-sky coverage, can capitalize on both.
+
+% One class of rare weirdo to which TESS is sensitive is stars in
+% clusters.  For brevity, we use the term ``cluster'' to refer to open
+% clusters, moving groups, associations, and star-forming regions.
+% Each of the $\sim$1000 star clusters of the Milky Way is a gift to
+% astrophysics, providing a sample of stars that vary widely in mass
+% but all have approximately the same age and composition.
+
 \section{Introduction}
@@
 
-The exoplanet field is evolving.
-At the beginning, Doppler spectroscopy by the Geneva and California groups
-led to the first exoplanet detections (CITE: Mayor 95, Butler, Marcy).
-Some of these planets transited (CITE: Henry, Charbonneau).
-Despite the geometric rarity of transits, photometric monitoring can
-be performed in parallel; with precise spectroscopy this has not
-yet been achieved.
-Parallel photometric monitoring enabled thousands of planet detections
-with the Kepler spacecraft (CITE: Borucki, Morton).
-The abundance of planets from Kepler taught us about statistics
-(CITE: Howard, Fressin, Petigura).
-By nature of its design, Kepler left open two major avenues for
-improvement: (i) brighter stars, (ii) rare weirdos.
-TESS (CITE: Ricker), by nature of its small, wide-field cameras, and
-nearly all-sky coverage, can capitalize on both.
-
-One class of rare weirdo to which TESS is sensitive is stars in
-clusters.  For brevity, we use the term ``cluster'' to refer to open
-clusters, moving groups, associations, and star-forming regions.
-Each of the $\sim$1000 star clusters of the Milky Way is a gift to
-astrophysics, providing a sample of stars that vary widely in mass
-but all have approximately the same age and composition.
-
-Cluster stars have been photometered from the ground for a while
-(CITE: Joel thesis, Cambridge group).
-A few clusters, NAME1 and NAME2, were observed by Kepler in its prime
-mission (CITE: Meibom).
-And a few more, most notably X,Y, and Z, were observed in K2's
-ecliptic mission (CITE).
-
-TESS holds the promise to deliver the most homogeneous and
-comprehensive cluster photometric survey in history.  Based on the
-cluster membership database of \citet{Kharchenko_et_al_2013} and the
-TESS apparent magnitude calculator of \citet{Jaffe_Barclay_2017}, we
-estimate that $10^5$ cluster members brighter than $T=16$ will be
-observed in the northern ecliptic hemisphere's full-frame images.
-
-However, there are formidable obstacles to deriving precise photometry
-from the {\it TESS} images because of the relatively poor angular
-resolution.  Almost all of the clusters are within 10 degrees of the
-Galactic plane (see Figure~1), where the problems with crowding and
-complex backgrounds are so severe that the {\it TESS}\, Science Team
-has neglected that portion of the sky in their planet simulations
+Many evolutionary processes are expected to occur over the lives of
+stars and exoplanets; it would be interesting to statistically observe
+these changes as functions of time.
+However, since dwarf stars do not appreciably change in size or luminosity
+until evolving off the main sequence, creative approaches must be used to
+infer ages \citep{soderblom_ages_2010}.
+In the study of exoplanets, one approach beginning to bear fruit
+is to search for planets in open clusters and moving groups.
+The ages of these stellar ensembles are inferred through isochrone
+analysis, and are typically most constrained by the location of the
+main-sequence turnoff and/or the red giant branch (CITE IF TRUE).
+Once calibrated, gyrochronology can also be used to verify
+the age of a stellar ensemble \citep[{\it
+e.g.},][]{barnes_color-period_2015,meibom_spin-down_2015,curtis_tess_2019}.
+The ages of planets discovered around these cluster stars are then
+assumed to equal those of the star.
+
+The first planet detections in open clusters
+came from radial velocity measurements of evolved stars in the Hyades
+\citep{Sato_et_al_2007}, and in NGC~2423 \citep{lovis_mayor_2007}.
+Subsequent spectroscopic searches in Praesepe led to the detection of the first
+hot Jupiters in a cluster \citep{Quinn_et_al_2012}, and also the first
+multi-planet system \citep{Malavota_et_al_2016}.
+There were also additional detections reported in the Taurus
+star-forming region (CITE V830 Tau b; Donati et al. 2016, and Cl Tau
+b; Johns-Krull et al. 2016, Flagg et al. 2019).
+An additional radial velocity survey was conducted by Brucalassi et al
+(2017, CITE), following 88 stars in M~67 over 7 years.  They
+reported the detections of three hot Jupiters around main sequence
+stars, and one giant planet around an evolved star.
+
+The transit method was slow to catch up, despite deep searches of the
+M~37 open cluster by \citet{hartman_MMT_IV_2009}, as well as
+multi-year searches of nine young clusters in the solar neighborhood
+by the Monitor project
+\citep{aigrain_monitor_2007,irwin_monitordata_2007,miller_monitor_2008}.
+While these studies led to interesting measurements of stellar
+rotation \citep{hartman_rotation_2009,Irwin_NGC2516_2007} as well as
+the discovery of pre-main-sequence (PMS) eclipsing binaries (EBs)
+\citep{irwin_monitor_PMSEB_2007}, no planet in open clusters were
+uncovered.  Transit searches in globular clusters were similarly met
+with null results \citep{gilliland_lack_2000,
+weldrake_searching_2006}.
+
+Kepler \citep{borucki_kepler_2010} was the first machine to observe a
+sufficient number of stars for long enough and with sufficient
+precision to detect transiting planets in open clusters:  Kepler-66b
+and 67b, in the gigayear-old NGC6811 \citep{Meibom_et_al_2013}.
+Though a broken reaction wheel ended the prime Kepler mission, the
+repurposed K2 mission \citep{howell_k2_2014} switched between
+fields along the ecliptic every quarter-year, and was able to observe
+far more clusters and young stars.
+In particular, K2's detections through its surveys of the Pleiades,
+Hyades, Praesepe, and Upper Sco were a major inspiration for the
+present work.
+
+K2-25b, discovered in the Hyades, had a radius ($3.43\,R_\oplus$) that
+was larger than older Kepler planets at similar insolation levels
+\citep{Mann_K2_25_2016}.  This inflated radius is perhaps a hint that
+the planet is contracting, or losing its atmosphere (e.g., CITE).
+The super-Neptune sized K2-33b ($P\approx 5.4\,{\rm d}$), found in
+Upper Sco, showed that at least some close-in planets must form within
+about 10 Myr, excluding long-timescale migration as an explanation for
+its origin \citep{Mann_K2_33b_2016,David_et_al_2017}.
+Further discoveries included six transiting planets in Praesepe (CITE
+Obermeier, Mann 2016 or 2017), a long-period candidate super-Earth in
+the Hyades (CITE Vanderburg 2017), K2-136b in the Hyades (CITE
+Ciardi+2018, Livingston+2018), the transiting multi-planet system
+K2-264bc in Praesepe (CITE Rizzuto+2018, Livingston+2019), as well as
+a Jupiter-sized planet orbiting every 24 days around V1298 Tau (CITE
+David+2019).
+A final related detection was that of three small planets transiting
+K2-233 (CITE David 2018).  Though the star was not in a cluster, its
+age was determined to be $360_{-140}^{+490}\,{\rm Myr}$ based on
+rotation, activity, and kinematic indicators.
+
+Clearly, a significant amount of effort has been and continues to be
+devoted towards the discovery and characterization of planets around
+young stars.
+It would be nice to begin occurrence rate testing, with a machinery
+similar to that described by Rizzuto 2017 (CITE).
+However, due to the geometric rarity of transits, many tens of
+thousands of stars with known ages must be monitored at high precision
+for such studies to be statistically robust.
+
+The TESS mission \citep{ricker_transiting_2015} holds the promise to
+deliver the most homogeneous and comprehensive cluster photometric
+survey in history.  Based on the cluster membership database of
+\citet{Kharchenko_et_al_2013} and the TESS apparent magnitude
+calculator of \citet{Jaffe_Barclay_2017}, we estimated that $\approx
+2\times10^5$ cluster members brighter than $T=16$ will be observed in
+the full-frame images over the first two years of TESS observations.
+The actual number may be even larger, as cluster membership catalogs
+are by no means complete, even at these relatively bright magnitudes
+(CITE recent Gaia discoveries of nearby OCs).
+
+We have begun to produce time-series photometry from the TESS images
+for stars in ``clusters''~--~a collective term we adopt for open
+clusters, moving groups, stellar associations, and star-forming
+regions.
+We are also including some stars that we suspect are young due to
+combined photometric and astrometric indicators (see
+\S~\ref{sec:starselection}).
+Our eventual hope is to discover giant transiting planets, and probe
+the exoplanet size and separation distributions for planets younger
+than 1 Gyr.
+
+%FIXME: this paragraph needs improvement.
+Unfortunately, there are formidable obstacles to deriving precise
+photometry from the {\it TESS} images because of the relatively poor
+angular resolution.  Almost all of the clusters are within 10 degrees
+of the Galactic plane (see FIGURE~1), where the problems with crowding
+and complex backgrounds are so severe that the {\it TESS}\, Science
+Team has neglected that portion of the sky in their planet simulations
 \citep{Sullivan_et_al_2015}. Similarly, the {\it TESS}\, Candidate
-Target List deprioritizes all objects within $15^\circ$ of the
-galactic plane~\citep{stassun_TIC_2018}, which includes 90\% of all
-star clusters.  The large pixel size and the high stellar surface
-density will make aperture photometry unreliable.  Yet, aperture
-photometry is the basis of the official {\it TESS} data reduction
-pipeline and almost all reduction methods that have been applied to
-{\it Kepler} and {\it K2} data.
-
-We have begun to produce photometry from the TESS images.
-For the time being, we are adopting the difference imaging (or
-optionally, ``image subtraction'') technique, because of its
-benefits in modelling complex backgrouds in crowded regions.
+Target List deprioritizes all objects close to the galactic
+plane~\citep{stassun_TIC_2018,stassun_TIC8_2019}, which includes 90\%
+of all star clusters.  The large pixel size and the high stellar
+surface density will make aperture photometry unreliable.  Yet,
+aperture photometry is the basis of the official {\it TESS} data
+reduction pipeline and almost all reduction methods that have been
+applied to {\it Kepler} and {\it K2} data.
+We have therefore adopted the difference imaging technique (also
+dubbed ``image subtraction''), because of its benefits in modelling
+complex backgrouds in crowded regions.
 

### 2019-06-13 paper/ms.tex
update

@@
 \shortauthors{Bouma et al.}
-\shorttitle{CDIPS I: Method, Sectors 6 \& 7}
+\shorttitle{CDIPS I}
 
@@
 % BEGIN NUMBERS
-\newcommand{\numberpcs}{10\ }
-\newcommand{\numberlcs}{42{,}424\ }
-\newcommand{\numberclusters}{424\ }
+\newcommand{\numberpcs}{42\ }
+\newcommand{\numberlcs}{99{,}999\ }
+\newcommand{\numberclusters}{XXX\ }
 
@@
   As part of the CDIPS project, we have been processing the TESS
-  full-frame images to make high-precision light curves stars that
+  full-frame images to make light curves of stars that
   could be members of stellar associations, moving groups, and open clusters.
@@
   %
-  The light curves and vetting are available at
+  The light curves and vetting reports are available at
   \url{archive.stsci.edu/prepds/cdips}.
@@
 these changes as functions of time.
-However, since dwarf stars do not appreciably change in size or luminosity
-until evolving off the main sequence, creative approaches must be used to
-infer ages \citep{soderblom_ages_2010}.
+However, since most dwarf star properties do not appreciably change
+until the stars evolve off the main sequence, creative approaches must
+be used to infer stellar ages \citep{soderblom_ages_2010}.
 In the study of exoplanets, one approach beginning to bear fruit
@@
 The ages of these stellar ensembles are inferred through isochrone
-analysis, and are typically most constrained by the location of the
+analyses, and are typically most constrained by the location of the
 main-sequence turnoff and/or the red giant branch (CITE IF TRUE).
@@
 
-The first planet detections in open clusters
-came from radial velocity measurements of evolved stars in the Hyades
+The first planets in open clusters were detected through radial
+velocity (RV) measurements of evolved stars in the Hyades
 \citep{Sato_et_al_2007}, and in NGC~2423 \citep{lovis_mayor_2007}.
-Subsequent spectroscopic searches in Praesepe led to the detection of the first
-hot Jupiters in a cluster \citep{Quinn_et_al_2012}, and also the first
-multi-planet system \citep{Malavota_et_al_2016}.
-There were also additional detections reported in the Taurus
-star-forming region (CITE V830 Tau b; Donati et al. 2016, and Cl Tau
-b; Johns-Krull et al. 2016, Flagg et al. 2019).
-An additional radial velocity survey was conducted by Brucalassi et al
-(2017, CITE), following 88 stars in M~67 over 7 years.  They
-reported the detections of three hot Jupiters around main sequence
-stars, and one giant planet around an evolved star.
-
-The transit method was slow to catch up, despite deep searches of the
-M~37 open cluster by \citet{hartman_MMT_IV_2009}, as well as
-multi-year searches of nine young clusters in the solar neighborhood
+Subsequent spectroscopic searches in Praesepe led to the detection of
+the first hot Jupiters in a cluster \citep{Quinn_et_al_2012}, and also
+the first multi-planet system \citep{Malavolta_et_al_2016}.
+The youngest RV detections have come from surveys of T Tauri stars in the
+Taurus star-forming region, which showed signals of the hot Jupiter
+\citep[V830~Tau~b][]{donati_hj_2016} and of a giant planet on a 9-day orbit
+\citep[CI~Tau~b][]{johns-krull_candidate_2016,flagg_co_2019}.
+A final RV survey of note was conducted by
+\citet{brucalassi_search_2017}, who followed 88 stars in M~67 over 7
+years.  They reported detections of three hot Jupiters around main
+sequence stars, and of one giant planet around an evolved star.
+
+The transit method was slow to catch up, despite deep searches of
+M~37 by \citet{hartman_MMT_IV_2009}, as well as
+searches of nine young clusters in the solar neighborhood
 by the Monitor project
 \citep{aigrain_monitor_2007,irwin_monitordata_2007,miller_monitor_2008}.
-While these studies led to interesting measurements of stellar
+While these studies led to valuable measurements of stellar
 rotation \citep{hartman_rotation_2009,Irwin_NGC2516_2007} as well as
@@
 
-Kepler \citep{borucki_kepler_2010} was the first machine to observe a
+Kepler \citep{borucki_kepler_2010} was the first project to observe a
 sufficient number of stars for long enough and with sufficient
 precision to detect transiting planets in open clusters:  Kepler-66b
-and 67b, in the gigayear-old NGC6811 \citep{Meibom_et_al_2013}.
+and 67b, in the gigayear-old NGC~6811 \citep{Meibom_et_al_2013}.
 Though a broken reaction wheel ended the prime Kepler mission, the
@@
 
-K2-25b, discovered in the Hyades, had a radius ($3.43\,R_\oplus$) that
-was larger than older Kepler planets at similar insolation levels
-\citep{Mann_K2_25_2016}.  This inflated radius is perhaps a hint that
-the planet is contracting, or losing its atmosphere (e.g., CITE).
-The super-Neptune sized K2-33b ($P\approx 5.4\,{\rm d}$), found in
-Upper Sco, showed that at least some close-in planets must form within
-about 10 Myr, excluding long-timescale migration as an explanation for
-its origin \citep{Mann_K2_33b_2016,David_et_al_2017}.
-Further discoveries included six transiting planets in Praesepe (CITE
-Obermeier, Mann 2016 or 2017), a long-period candidate super-Earth in
-the Hyades (CITE Vanderburg 2017), K2-136b in the Hyades (CITE
-Ciardi+2018, Livingston+2018), the transiting multi-planet system
-K2-264bc in Praesepe (CITE Rizzuto+2018, Livingston+2019), as well as
-a Jupiter-sized planet orbiting every 24 days around V1298 Tau (CITE
-David+2019).
-A final related detection was that of three small planets transiting
-K2-233 (CITE David 2018).  Though the star was not in a cluster, its
-age was determined to be $360_{-140}^{+490}\,{\rm Myr}$ based on
-rotation, activity, and kinematic indicators.
+K2-25b, discovered in the Hyades, had a radius ($3.43\,R_\oplus$) that was
+larger than older Kepler planets at similar insolation levels
+\citep{Mann_K2_25_2016}.  This inflated radius is perhaps a hint that the
+planet is contracting, or losing its atmosphere (e.g., CITE).  The
+super-Neptune sized K2-33b ($P\approx 5.4\,{\rm d}$), found in Upper Sco,
+showed that at least some close-in planets must form within about 10 Myr,
+excluding long-timescale migration as an explanation for its origin
+\citep{Mann_K2_33b_2016,David_et_al_2017}.  Further discoveries included six
+transiting planets in Praesepe \citep{obermeier_k2_2016,Mann_et_al_2017}, a
+long-period candidate super-Earth in the Hyades
+\citep{vanderburg_zeitVII_2018}, the three-planet K2-136 system in the Hyades
+\citep{ciardi_k2-136_2018,livingston_three_2018,mann_ZEITVI_2018}, and also the
+two-planet system K2-264 in Praesepe
+\citep{rizzuto_zeitVIII_2018,livingston_k2-264_2019}.  A final recent
+K2 detection is of a Jupiter-sized planet orbiting every 24 days around V1298
+Tau \citep{david_v1298_2019}.
 
@@
 young stars.
-It would be nice to begin occurrence rate testing, with a machinery
-similar to that described by Rizzuto 2017 (CITE).
-However, due to the geometric rarity of transits, many tens of
-thousands of stars with known ages must be monitored at high precision
-for such studies to be statistically robust.
+Sometimes, cluster membership may not even be necessary, if a star's
+youth can be inferred based on a combination of rotation, activity,
+and kinematic indicators \citep[{e.g.}, K2-233][]{david_k2-233_2018}.
+To investigate demographics in time, the detection sensitivities and
+reliabilities of these searchers need to be calibrated, likely with a
+machinery similar to that outlined by \citet{rizzuto_zeitV_2017}.
+A separate requirement for population studies to be statistically
+robust, imposed by the geometric rarity of transits, is that many tens
+of thousands of stars with known ages must be monitored at high
+precision.
 
@@
 
-We have begun to produce time-series photometry from the TESS images
-for stars in ``clusters''~--~a collective term we adopt for open
-clusters, moving groups, stellar associations, and star-forming
-regions.
+One of the major challenges in deriving precise photometry from the
+TESS images is the relatively poor angular resolution ($\approx
+21''$).  Almost all clusters are within 10 degrees of the Galactic
+plane (see FIGURE~1). The problems with crowding and complex
+backgrounds are so severe near the galactic plane that the {\it
+TESS}\, Candidate Target List has deprioritized all objects at
+galactic latitudes less than $\approx
+15^\circ$~\citep{stassun_TIC_2018,stassun_TIC8_2019}, which includes
+90\% of all star clusters\footnote{TICv8 updates this to $10^\circ$,
+but for the first year of TESS observations, the number used when
+selecting target stars was $15^\circ$.}.
+This is sensible, given that the large pixel size and the high stellar
+surface density will make aperture photometry unreliable.  However, it
+also means that a large number of stars in clusters that could yield
+planet candidates may go unprocessed by the official {\it TESS} data
+reduction pipeline.
+
+We have therefore opted to produce time-series photometry from the
+TESS images for stars in ``clusters''~--~a collective term we adopt
+for open clusters, moving groups, stellar associations, and
+star-forming regions.
 We are also including some stars that we suspect are young due to
-combined photometric and astrometric indicators (see
-\S~\ref{sec:starselection}).
+combined photometric and astrometric indicators.
+We are using the difference imaging technique because of its benefits
+in modelling complex backgrouds in crowded regions.
 Our eventual hope is to discover giant transiting planets, and probe
@@
 
-%FIXME: this paragraph needs improvement.
-Unfortunately, there are formidable obstacles to deriving precise
-photometry from the {\it TESS} images because of the relatively poor
-angular resolution.  Almost all of the clusters are within 10 degrees
-of the Galactic plane (see FIGURE~1), where the problems with crowding
-and complex backgrounds are so severe that the {\it TESS}\, Science
-Team has neglected that portion of the sky in their planet simulations
-\citep{Sullivan_et_al_2015}. Similarly, the {\it TESS}\, Candidate
-Target List deprioritizes all objects close to the galactic
-plane~\citep{stassun_TIC_2018,stassun_TIC8_2019}, which includes 90\%
-of all star clusters.  The large pixel size and the high stellar
-surface density will make aperture photometry unreliable.  Yet,
-aperture photometry is the basis of the official {\it TESS} data
-reduction pipeline and almost all reduction methods that have been
-applied to {\it Kepler} and {\it K2} data.
-We have therefore adopted the difference imaging technique (also
-dubbed ``image subtraction''), because of its benefits in modelling
-complex backgrouds in crowded regions.
-
-In what follows, \S~\ref{sec:method} presents BLAH, and
-\S~\ref{sec:results} describes BLAH BLAH.
+%FIXME improve
+In what follows, \S~\ref{sec:starselection} describes the process of
+selecting stars.  \S~\ref{sec:method} presents the photometric and
+image processing methods, and
+\S~\ref{sec:results} describes results.
 \S~\ref{sec:discussion} discusses, and \S~\ref{sec:conclusion}
@@
 of systematic false positives in subsequent vetting.
-Our grids typically consisted of about 25 different durations, and
-about 2500 periods between 0.5 and 11 days. 
+Our grids typically consisted of about 30 different durations, and
+about 5000 periods between 0.5 and 21 days. 
 We also ran a generalized Lomb-Scargle periodogram (CITE), simply to 

### 2019-06-18 paper/ms.tex
minor

@@
 The actual number may be even larger, as cluster membership catalogs
-are by no means complete, even at these relatively bright magnitudes
-(CITE recent Gaia discoveries of nearby OCs).
+are by no means complete, even at these relatively bright magnitudes.
+For example, using Gaia-DR2 \citet{cantat-gaudin_newOCs_2019}
+discovered a few tens of previously undetected open clusters in
+the direction of Perseus. Earlier, \citet{cantat-gaudin_gaia_2018}
+fortuitously discovered 60 open clusters as well; however a
+homogeneous all-sky search with Gaia data has yet to be performed.
 
@@
 L.G.B.\ gladly acknowledges helpful discussions with
+C Huang, M Soares-Furtado, ...
 ..., and is

### 2019-06-20 cdips/lcproc/reformat_lcs_for_mast.py
protecting requests

@@ -4,7 +4,7 @@ presentable, and apply minor changes to improve their BLS-searchability.
 """
 
 import pandas as pd, numpy as np
-import os
+import os, requests, time
 from astropy.io import fits
 from datetime import datetime
 from astroquery.mast import Catalogs
@@ -210,11 +210,20 @@ def _reformat_header(lcpath, cdips_df, outdir, sectornum, cdipsvnum):
     targetcoord = SkyCoord(ra=ra, dec=dec, unit=(u.degree, u.degree), frame='icrs')
     radius = 1.0*u.arcminute
 
-    stars = Catalogs.query_region(
-        "{} {}".format(float(targetcoord.ra.value), float(targetcoord.dec.value)),
-        catalog="TIC",
-        radius=radius
-    )
+    try:
+        stars = Catalogs.query_region(
+            "{} {}".format(float(targetcoord.ra.value), float(targetcoord.dec.value)),
+            catalog="TIC",
+            radius=radius
+        )
+    except requests.exceptions.ConnectionError:
+        print('ERR! TIC query failed. trying again...')
+        time.sleep(60)
+        stars = Catalogs.query_region(
+            "{} {}".format(float(targetcoord.ra.value), float(targetcoord.dec.value)),
+            catalog="TIC",
+            radius=radius
+        )
 
     Tmag_pred = (primaryhdr['phot_g_mean_mag']
                 - 0.00522555 * (primaryhdr['phot_bp_mean_mag'] - primaryhdr['phot_rp_mean_mag'])**3

### 2019-06-20 paper/ms.tex

@@
 stars and exoplanets; it would be interesting to statistically observe
-these changes as functions of time.
-However, since most dwarf star properties do not appreciably change
-until the stars evolve off the main sequence, creative approaches must
-be used to infer stellar ages \citep{soderblom_ages_2010}.
-In the study of exoplanets, one approach beginning to bear fruit
-is to search for planets in open clusters and moving groups.
-The ages of these stellar ensembles are inferred through isochrone
-analyses, and are typically most constrained by the location of the
-main-sequence turnoff and/or the red giant branch (CITE IF TRUE).
-Once calibrated, gyrochronology can also be used to verify
-the age of a stellar ensemble \citep[{\it
+these changes as functions of time.  However, since most dwarf star
+properties do not appreciably change until the stars evolve off the
+main sequence, creative approaches must be used to infer stellar ages
+\citep{soderblom_ages_2010}.  One approach beginning to bear fruit in
+the study of exoplanets is to search for planets in coeval groups of
+stars, {\it i.e.} in clusters.  This includes the open clusters of
+yore, as well as the moving groups and stellar associations that began
+to be uncovered in the late 1990s \citep{zuckerman_young_2004}.  The
+ages of these stellar ensembles are inferred through isochrone
+analyses on color-magnitude diagrams, using an appropriate combination
+main-sequence turnoff locations, pre-MS turnon locations, and/or MS
+isochrones for the known cluster members \citep[{\it e.g.},][Section
+3.4.3]{kharchenko_global_2012}.  Once calibrated, gyrochronology can
+also be used to verify the age of a stellar ensemble \citep[{\it
 e.g.},][]{barnes_color-period_2015,meibom_spin-down_2015,curtis_tess_2019}.
-The ages of planets discovered around these cluster stars are then
-assumed to equal those of the star.
+The ages of planets discovered in these cluster stars are then
+assumed to equal the age of the larger stellar ensemble.
 
@@
 velocity (RV) measurements of evolved stars in the Hyades
-\citep{Sato_et_al_2007}, and in NGC~2423 \citep{lovis_mayor_2007}.
+and NGC~2423 \citep{Sato_et_al_2007,lovis_mayor_2007}.
 Subsequent spectroscopic searches in Praesepe led to the detection of
-the first hot Jupiters in a cluster \citep{Quinn_et_al_2012}, and also
-the first multi-planet system \citep{Malavolta_et_al_2016}.
+the first hot Jupiter in a cluster \citep{Quinn_et_al_2012}, and also
+the first multi-planet system in a cluster \citep{Malavolta_et_al_2016}.
 The youngest RV detections have come from surveys of T Tauri stars in the
@@
 
-The transit method was slow to catch up, despite deep searches of
-M~37 by \citet{hartman_MMT_IV_2009}, as well as
-searches of nine young clusters in the solar neighborhood
-by the Monitor project
+The transit method was comparatively slow to catch up, despite deep
+searches of M~37 by \citet{hartman_MMT_IV_2009}, as well as searches
+of nine young clusters in the solar neighborhood by the Monitor
+project
 \citep{aigrain_monitor_2007,irwin_monitordata_2007,miller_monitor_2008}.
-While these studies led to valuable measurements of stellar
-rotation \citep{hartman_rotation_2009,Irwin_NGC2516_2007} as well as
+While these studies led to valuable measurements of stellar rotation
+periods \citep{hartman_rotation_2009,Irwin_NGC2516_2007} as well as
 the discovery of pre-main-sequence (PMS) eclipsing binaries (EBs)
-\citep{irwin_monitor_PMSEB_2007}, no planet in open clusters were
-uncovered.  Transit searches in globular clusters were similarly met
-with null results \citep{gilliland_lack_2000,
+\citep{irwin_monitor_PMSEB_2007}, no transiting planets in open
+clusters were found.  Transit searches in globular clusters were
+similarly met with null results \citep{gilliland_lack_2000,
 weldrake_searching_2006}.
 
-Kepler \citep{borucki_kepler_2010} was the first project to observe a
-sufficient number of stars for long enough and with sufficient
-precision to detect transiting planets in open clusters:  Kepler-66b
-and 67b, in the gigayear-old NGC~6811 \citep{Meibom_et_al_2013}.
-Though a broken reaction wheel ended the prime Kepler mission, the
-repurposed K2 mission \citep{howell_k2_2014} switched between
-fields along the ecliptic every quarter-year, and was able to observe
-far more clusters and young stars.
-In particular, K2's detections through its surveys of the Pleiades,
-Hyades, Praesepe, and Upper Sco were a major inspiration for the
-present work.
-
-K2-25b, discovered in the Hyades, had a radius ($3.43\,R_\oplus$) that was
-larger than older Kepler planets at similar insolation levels
-\citep{Mann_K2_25_2016}.  This inflated radius is perhaps a hint that the
-planet is contracting, or losing its atmosphere (e.g., CITE).  The
-super-Neptune sized K2-33b ($P\approx 5.4\,{\rm d}$), found in Upper Sco,
-showed that at least some close-in planets must form within about 10 Myr,
-excluding long-timescale migration as an explanation for its origin
-\citep{Mann_K2_33b_2016,David_et_al_2017}.  Further discoveries included six
-transiting planets in Praesepe \citep{obermeier_k2_2016,Mann_et_al_2017}, a
-long-period candidate super-Earth in the Hyades
-\citep{vanderburg_zeitVII_2018}, the three-planet K2-136 system in the Hyades
-\citep{ciardi_k2-136_2018,livingston_three_2018,mann_ZEITVI_2018}, and also the
-two-planet system K2-264 in Praesepe
-\citep{rizzuto_zeitVIII_2018,livingston_k2-264_2019}.  A final recent
-K2 detection is of a Jupiter-sized planet orbiting every 24 days around V1298
-Tau \citep{david_v1298_2019}.
-
-Clearly, a significant amount of effort has been and continues to be
-devoted towards the discovery and characterization of planets around
-young stars.
+Kepler \citep{borucki_kepler_2010} observed enough stars for long
+enough and with sufficient precision to detect transiting planets in
+open clusters:  Kepler-66b and 67b, in the gigayear-old NGC~6811
+\citep{Meibom_et_al_2013}.  Though a broken reaction wheel ended the
+prime Kepler mission, the repurposed K2 \citep{howell_k2_2014}
+switched between fields along the ecliptic every quarter-year, and was
+able to observe far more clusters and young stars.  The resulting
+discoveries made by K2 through its surveys of the Pleiades, Hyades,
+Praesepe, and Upper Sco were a major inspiration for the present work.
+
+K2-25b, discovered in the Hyades, has a radius ($3.43\,R_\oplus$) that
+is larger than older Kepler planets at similar insolation levels
+\citep{Mann_K2_25_2016}.  This inflated radius is perhaps a hint that
+the planet is contracting, or losing its atmosphere (e.g., CITE).  The
+super-Neptune sized K2-33b ($P\approx 5.4\,{\rm d}$), found in Upper
+Sco, showed that at least some close-in planets must form within about
+10 Myr, excluding long-timescale migration as an explanation for its
+origin \citep{Mann_K2_33b_2016,David_et_al_2017}.  Further discoveries
+included six transiting planets in Praesepe
+\citep{obermeier_k2_2016,Mann_et_al_2017}, a long-period candidate
+super-Earth in the Hyades \citep{vanderburg_zeitVII_2018}, the
+three-planet K2-136 system in the Hyades
+\citep{ciardi_k2-136_2018,livingston_three_2018,mann_ZEITVI_2018}, and
+also the two-planet system K2-264 in Praesepe
+\citep{rizzuto_zeitVIII_2018,livingston_k2-264_2019}.  There has also
+recently been a detection by K2 of a Jupiter-sized planet orbiting
+every 24 days around V1298~Tau \citep{david_v1298_2019}.
+
+A significant amount of effort continues to be devoted towards the
+discovery and characterization of planets around young stars.
 Sometimes, cluster membership may not even be necessary, if a star's
-youth can be inferred based on a combination of rotation, activity,
-and kinematic indicators \citep[{e.g.}, K2-233][]{david_k2-233_2018}.
-To investigate demographics in time, the detection sensitivities and
+youth can be inferred from combined rotation, activity, and kinematic
+indicators \citep[{e.g.}, K2-233;][]{david_k2-233_2018}.  To
+investigate demographics in time, the detection sensitivities and
 reliabilities of these searchers need to be calibrated, likely with a
-machinery similar to that outlined by \citet{rizzuto_zeitV_2017}.
-A separate requirement for population studies to be statistically
+machinery similar to that outlined by \citet{rizzuto_zeitV_2017}.  A
+separate requirement for population studies to be statistically
 robust, imposed by the geometric rarity of transits, is that many tens
@@
 
+%FIXME probably rework the following two paragraphs?
 The TESS mission \citep{ricker_transiting_2015} holds the promise to
 deliver the most homogeneous and comprehensive cluster photometric
-survey in history.  Based on the cluster membership database of
-\citet{Kharchenko_et_al_2013} and the TESS apparent magnitude
-calculator of \citet{Jaffe_Barclay_2017}, we estimated that $\approx
+survey in history.  As an order of magnitude estimate, the 
+\citet{Kharchenko_et_al_2013} combined with the TESS apparent magnitude
+calculator of \citet{Jaffe_Barclay_2017} indicated that $\approx
 2\times10^5$ cluster members brighter than $T=16$ will be observed in
 the full-frame images over the first two years of TESS observations.
-The actual number may be even larger, as cluster membership catalogs
-are by no means complete, even at these relatively bright magnitudes.
-For example, using Gaia-DR2 \citet{cantat-gaudin_newOCs_2019}
-discovered a few tens of previously undetected open clusters in
-the direction of Perseus. Earlier, \citet{cantat-gaudin_gaia_2018}
-fortuitously discovered 60 open clusters as well; however a
-homogeneous all-sky search with Gaia data has yet to be performed.
+The actual number will be larger, as cluster membership catalogs
+are not yet complete, even at these relatively bright magnitudes
+\citep[{\it e.g.},][]{cantat-gaudin_gaia_2018,cantat-gaudin_newOCs_2019}.
+% For example, using Gaia-DR2 \citet{cantat-gaudin_newOCs_2019}
+% discovered a few tens of previously undetected open clusters in
+% the direction of Perseus. Earlier, \citet{cantat-gaudin_gaia_2018}
+% fortuitously discovered 60 open clusters as well; however a
+% homogeneous all-sky search with Gaia data has yet to be performed.
+
+For moving groups and stellar assocations, it is typically a simple thing to do
+aperture photometry.  A number of promising targets from TESS are in various
+stages of follow-up for this, notably DS Tuc Ab (TOI 200,
+\citealt{benatti_dstuc_2019}, Newton+2019), as well as TOI-450 and TOI-451.
+This is good, and these will remain benchmark systems because they are close
+and bright.  However, to do statistics, we need more stars -- we need to
+investigate the full range of cluster properties (densities, ages,
+metallicities).  This motivates the need to go crowded.
 

### 2019-06-20 drivers/get_cdips_lc_stats.py
move allnan cdips LCs to graveyard
they won't be included in the main data release

@@ -1,17 +1,19 @@
 """
-get simple rms vs mag stats for CDIPS LCs. plot them. assess how many all-nan
-LCs there are.
-supplement the statsfile by matching against Gaia DR2 and CDIPS  catalogs.
+* get simple rms vs mag stats for CDIPS LCs
+* plot them.
+* assess how many all-nan LCs there are.
+* move allnan light curves to a graveyard directory to collect dust
+* supplement the statsfile by matching against Gaia DR2 and CDIPS catalogs.
 
 usage:
 
-    $ (trex_37) python -u get_cdips_lc_stats.py |& tee /nfs/phtess2/ar0/TESS/PROJ/lbouma/cdips/results/cdips_lc_stats/sector-6/stats_overview_log.txt
+    $ (cdips) python -u get_cdips_lc_stats.py |& tee logs/s6_stats_overview_log.txt
 
 NOTE: depends on pipe-trex (--> run in environment with aperturephot on path)
 """
 import pandas as pd, numpy as np
 import aperturephot as ap
-import os, subprocess, shlex
+import os, subprocess, shlex, shutil
 from glob import glob
 
 def get_cdips_lc_stats(
@@ -200,12 +202,95 @@ def print_metadata_stats(sector=6):
           format(len(stats[stats['stdev_tf1'] > 0])))
 
 
+def move_allnan_lcs(sector=None, cdipsvnum=None):
+
+    statsfile = os.path.join(
+        '/nfs/phtess2/ar0/TESS/PROJ/lbouma/cdips/results/cdips_lc_stats',
+        'sector-{}'.format(sector),
+        'cdips_lc_statistics.txt'
+    )
+
+    stats = ap.read_stats_file(statsfile, fovcathasgaiaids=True)
+    N_lcs = len(stats)
+
+    print('CDIPS LIGHTCURVES STATS FOR SECTOR {}'.format(sector))
+    print(42*'-')
+    print('total N_lcs: {}'.format(N_lcs))
+
+    for apn in [1,2,3]:
+        N_nan = len(stats[stats['ndet_tf{}'.format(apn)]==0])
+        print('for ap {}, {} ({:.1f}%) are all nan, leaving {} ok lcs'.
+              format(apn, N_nan, N_nan/N_lcs*100, N_lcs-N_nan))
+
+    print(42*'-')
+    print('BEGINNING MOVE OF ALLNAN LIGHT CURVES')
+
+    sel = (
[…]

### 2019-06-20 paper/ms.tex
paper words

@@
 \newcommand{\numberpcs}{42\ }
-\newcommand{\numberlcs}{99{,}999\ }
+\newcommand{\sVInumberlcs}{67{,}601\ }  % 2019/06/20 not allnan
+\newcommand{\sVIInumberlcs}{91{,}736\ }  % 2019/06/20 not allnan
+\newcommand{\numberlcs}{159{,}337\ } % 2019/06/20 sum
 \newcommand{\numberclusters}{XXX\ }
-
-% BEGIN CLUSTER TABLE
-%FIXME: write code that will write these values
-\newcommand{\cgXVIIInstartot}{}
-\newcommand{\cgXVIIInstarcdipsI}{}
-\newcommand{\gaiaXVIIInstartot}{}
-\newcommand{\gaiaXVIIInstarcdipsI}{}
-
-\newcommand{\kXIIInstartot}{}
-\newcommand{\kXIIInstarcdipsI}{}
-\newcommand{\dXIVnstartot}{}
-\newcommand{\dXIVnstarcdipsI}{}
-\newcommand{\bellXVIInstartot}{}
-\newcommand{\bellXVIInstarcdipsI}{}
-\newcommand{\banyanXIIInstartot}{}
-\newcommand{\banyanXIIInstarcdipsI}{}
-\newcommand{\banyanXIInstartot}{}
-\newcommand{\banyanXIInstarcdipsI}{}
-\newcommand{\banyanXInstartot}{}
-\newcommand{\banyanXInstarcdipsI}{}
-\newcommand{\krausXIVnstartot}{}
-\newcommand{\krausXIVnstarcdipsI}{}
-\newcommand{\ohXVIInstartot}{}
-\newcommand{\ohXVIInstarcdipsI}{}
-\newcommand{\rizzutoXInstartot}{}
-\newcommand{\rizzutoXInstarcdipsI}{}
-\newcommand{\roserXInstartot}{}
-\newcommand{\roserXInstarcdipsI}{}
-
-\newcommand{\cgXVIIInclustertot}{}
-\newcommand{\cgXVIIInclustercdipsI}{}
-\newcommand{\gaiaXVIIInclustertot}{}
-\newcommand{\gaiaXVIIInclustercdipsI}{}
-
-\newcommand{\kXIIInclustertot}{}
-\newcommand{\kXIIInclustercdipsI}{}
-\newcommand{\dXIVnclustertot}{}
-\newcommand{\dXIVnclustercdipsI}{}
-\newcommand{\bellXVIInclustertot}{}
-\newcommand{\bellXVIInclustercdipsI}{}
-\newcommand{\banyanXIIInclustertot}{}
-\newcommand{\banyanXIIInclustercdipsI}{}
-\newcommand{\banyanXIInclustertot}{}
-\newcommand{\banyanXIInclustercdipsI}{}
-\newcommand{\banyanXInclustertot}{}
-\newcommand{\banyanXInclustercdipsI}{}
-\newcommand{\krausXIVnclustertot}{}
-\newcommand{\krausXIVnclustercdipsI}{}
-\newcommand{\ohXVIInclustertot}{}
-\newcommand{\ohXVIInclustercdipsI}{}
-\newcommand{\rizzutoXInclustertot}{}
-\newcommand{\rizzutoXInclustercdipsI}{}
-\newcommand{\roserXInclustertot}{}
-\newcommand{\roserXInclustercdipsI}{}
-% END CLUSTER TABLE
 
@@
   % Context
-  The Transiting Exoplanet Survey Satellite (TESS) has started to
+  The Transiting Exoplanet Survey Satellite (TESS) has begun to
   photometrically monitor almost every star cluster in
@@
   % Aims
-  As part of the CDIPS project, we have been processing the TESS
-  full-frame images to make light curves of stars that
-  could be members of stellar associations, moving groups, and open clusters.
+  The CDIPS project is processing the TESS
+  full-frame images and making light curves of stars that could be
+  members of stellar associations, moving groups, or open clusters.
   %
-  Our eventual hope is to discover giant transiting planets, and probe
-  the exoplanet size and separation distributions for planets younger
-  than 1 Gyr.
+  Our eventual hope is to discover giant transiting planets with known
+  ages, and probe the exoplanet size and separation distributions for
+  planets younger than 1 Gyr.
   %
-  For this study, we made \numberlcs light curves of candidate young
+  In this study, we made \numberlcs light curves of candidate young
   stars in \numberclusters clusters.
@@
   an initial search, describe the vetting procedures that they have
-  survived, and emphasize the value that additional
-  spectroscopic, photometric, and imaging observations will have in
-  verify that these candidates are in fact planets.
+  survived, and emphasize the additional spectroscopic, photometric,
+  and imaging observations that are needed to verify that these
+  candidates are in fact planets.
   %
@@
 \keywords{
+  planets and satellites: detection  --
   methods: data analysis ---
   techniques: photometric ---
-  %TODO: could be individual, and enumerate each cluster as well.
   (Galaxy:) open clusters and associations: general ---
-  planets and satellites: detection 
 }
@@
 \citep{soderblom_ages_2010}.  One approach beginning to bear fruit in
-the study of exoplanets is to search for planets in coeval groups of
-stars, {\it i.e.} in clusters.  This includes the open clusters of
-yore, as well as the moving groups and stellar associations that began
-to be uncovered in the late 1990s \citep{zuckerman_young_2004}.  The
-ages of these stellar ensembles are inferred through isochrone
-analyses on color-magnitude diagrams, using an appropriate combination
-main-sequence turnoff locations, pre-MS turnon locations, and/or MS
-isochrones for the known cluster members \citep[{\it e.g.},][Section
-3.4.3]{kharchenko_global_2012}.  Once calibrated, gyrochronology can
-also be used to verify the age of a stellar ensemble \citep[{\it
+exoplanet studies is to search for planets in coeval groups of stars,
+hereafter ``clusters''.  This includes the open clusters of yore, as
+well as the moving groups and stellar associations that began to be
+uncovered in the late 1990s \citep{zuckerman_young_2004}.  The ages of
+these stellar ensembles are inferred through isochrone analyses of
+color-magnitude diagrams, using an appropriate combination of
+main-sequence turnoff locations, pre-main-sequence turnon locations,
+and possibly averaged MS isochronal ages across known cluster members
+\citep[{\it e.g.},][Section 3.4.3]{kharchenko_global_2012}.  Once
+calibrated, gyrochronology can also be used to verify the age of a
+stellar ensemble \citep[{\it
 e.g.},][]{barnes_color-period_2015,meibom_spin-down_2015,curtis_tess_2019}.
-The ages of planets discovered in these cluster stars are then
-assumed to equal the age of the larger stellar ensemble.
+The ages of planets discovered in these cluster stars are then assumed
+to equal the age of the larger stellar ensemble.
 
@@
 
-%FIXME probably rework the following two paragraphs?
-The TESS mission \citep{ricker_transiting_2015} holds the promise to
-deliver the most homogeneous and comprehensive cluster photometric
-survey in history.  As an order of magnitude estimate, the 
-\citet{Kharchenko_et_al_2013} combined with the TESS apparent magnitude
-calculator of \citet{Jaffe_Barclay_2017} indicated that $\approx
-2\times10^5$ cluster members brighter than $T=16$ will be observed in
-the full-frame images over the first two years of TESS observations.
-The actual number will be larger, as cluster membership catalogs
-are not yet complete, even at these relatively bright magnitudes
-\citep[{\it e.g.},][]{cantat-gaudin_gaia_2018,cantat-gaudin_newOCs_2019}.
-% For example, using Gaia-DR2 \citet{cantat-gaudin_newOCs_2019}
-% discovered a few tens of previously undetected open clusters in
-% the direction of Perseus. Earlier, \citet{cantat-gaudin_gaia_2018}
-% fortuitously discovered 60 open clusters as well; however a
-% homogeneous all-sky search with Gaia data has yet to be performed.
-
-For moving groups and stellar assocations, it is typically a simple thing to do
-aperture photometry.  A number of promising targets from TESS are in various
-stages of follow-up for this, notably DS Tuc Ab (TOI 200,
-\citealt{benatti_dstuc_2019}, Newton+2019), as well as TOI-450 and TOI-451.
-This is good, and these will remain benchmark systems because they are close
-and bright.  However, to do statistics, we need more stars -- we need to
-investigate the full range of cluster properties (densities, ages,
-metallicities).  This motivates the need to go crowded.
+The TESS mission \citep{ricker_transiting_2015}, though designed for
+other purposes, holds the promise to deliver the most homogeneous and
+comprehensive cluster photometric survey in history.  More
+quantitatively, the \citet{Kharchenko_et_al_2013} cluster member
+database indicates that $\approx 2\times10^5$ open cluster members
+brighter than $T=16$ will be observed in the full-frame images over
+the first two years of TESS observations.  The actual number will be
+larger, as cluster membership catalogs are not yet complete, even at
+these relatively bright magnitudes \citep[{\it
+e.g.},][]{cantat-gaudin_gaia_2018,cantat-gaudin_newOCs_2019}.
+% Our target list currently sits at $\approx 1.0\times10^6$ candidate
+% young stars, perhaps one-third of which are bonafide cluster members
+% (see \S~\ref{sec:starselection}).
 
 One of the major challenges in deriving precise photometry from the
-TESS images is the relatively poor angular resolution ($\approx
-21''$).  Almost all clusters are within 10 degrees of the Galactic
-plane (see FIGURE~1). The problems with crowding and complex
-backgrounds are so severe near the galactic plane that the {\it
-TESS}\, Candidate Target List has deprioritized all objects at
-galactic latitudes less than $\approx
+TESS images is the relatively poor angular resolution ($\approx 21''$
+per pixel).  Almost all clusters are within 10 degrees of the Galactic
+plane. The problems with crowding and complex backgrounds are so
+severe near the galactic plane that the TESS Candidate Target List has
+deprioritized all objects at galactic latitudes less than $\approx
 15^\circ$~\citep{stassun_TIC_2018,stassun_TIC8_2019}, which includes
-90\% of all star clusters\footnote{TICv8 updates this to $10^\circ$,
+90\% of all star clusters\footnote{TICv8 has updated this to $10^\circ$,
 but for the first year of TESS observations, the number used when
-selecting target stars was $15^\circ$.}.
-This is sensible, given that the large pixel size and the high stellar
-surface density will make aperture photometry unreliable.  However, it
-also means that a large number of stars in clusters that could yield
-planet candidates may go unprocessed by the official {\it TESS} data
-reduction pipeline.
+selecting target stars was $15^\circ$.}.  This is sensible, given that
+the large pixel size and the high stellar surface density will make
+aperture photometry unreliable.  However, it also means that a large
+number of stars in clusters that could yield planet candidates may go
+unprocessed by the official {\it TESS} data reduction pipeline.
+
+If one's concern is to discover and characterize benchmark systems
+with known ages,
+hunting for transiting planets in nearby stellar assocations is a path
+that seems to be working.  A number of promising targets from TESS are
+in various stages of follow-up from this approach, notably DS Tuc Ab
+(TOI 200, \citealt{benatti_dstuc_2019}, Newton+2019), as well as
+TOI-450 and TOI-451.  This is good, and these will remain benchmark
+systems because they are close and bright.  However, to do statistics,
+we need more stars -- we might also benefit from investigating the full range of cluster
+properties (densities, ages, metallicities).  This motivates the need
+to go crowded, and fainter.
 
 We have therefore opted to produce time-series photometry from the
-TESS images for stars in ``clusters''~--~a collective term we adopt
-for open clusters, moving groups, stellar associations, and
-star-forming regions.
-We are also including some stars that we suspect are young due to
-combined photometric and astrometric indicators.
-We are using the difference imaging technique because of its benefits
-in modelling complex backgrouds in crowded regions.
-Our eventual hope is to discover giant transiting planets, and probe
-the exoplanet size and separation distributions for planets younger
-than 1 Gyr.
-
-%FIXME improve
-In what follows, \S~\ref{sec:starselection} describes the process of
-selecting stars.  \S~\ref{sec:method} presents the photometric and
-image processing methods, and
-\S~\ref{sec:results} describes results.
+TESS images of any star that could be a member of a coeval group.  We
+are also including some stars that we suspect are young due to
+combined photometric and astrometric indicators.  We are using the
+difference imaging technique because of its benefits in modelling
+complex backgrouds in crowded regions.  While we hope to
+discover at least a few giant transiting planets, a separate hope
+is that the dataset might be useful to those wishing to study the
+time evolution of stellar processes.
+
+In the following, \S~\ref{sec:starselection} describes the process of
+selecting target stars.  \S~\ref{sec:method} presents the photometric and
+image processing methods, and \S~\ref{sec:results} describes results.
 \S~\ref{sec:discussion} discusses, and \S~\ref{sec:conclusion}
@@
 
-\begin{figure*}[t]
-	\begin{center}
-		\leavevmode
-		\includegraphics[width=0.7\textwidth]{cluster_positions.pdf}
-	\end{center}
+%\begin{figure*}[t]
+%	\begin{center}
+%		\leavevmode
+%		\includegraphics[width=0.7\textwidth]{cluster_positions.pdf}
+%	\end{center}
+%	\vspace{-0.5cm}
+%	\caption{
+%    {\bf TESS looks at many clusters.} Placeholder skymap.
+%		\label{fig:clustermap}
+%	}
+%\end{figure*}
+
+\begin{figure*}[!ht]
+    \gridline{
+      \fig{cluster_field_star_positions.png}{0.49\textwidth}{}
+      \fig{cam1_cluster_field_star_positions.png}{0.49\textwidth}{}
+    }
+    %\begin{center}
+    %    \leavevmode
+    %    \includegraphics[width=0.49\textwidth]{cluster_field_star_positions.png}
+    %\end{center}
     \vspace{-0.5cm}
     \caption{
-    {\bf TESS looks at many clusters.} Placeholder skymap.
-		\label{fig:clustermap}
+        {\it Left}. Celestial positions of light curves from Sectors 6 and 7.
+        {\it Right}. Celestial positions of light curves from Sector 6, Camera 1.
+        \label{fig:lcradecsector6}
     }
@@
 
-\begin{figure}[t]
-    \begin{center}
-        \leavevmode
-        \includegraphics[width=0.49\textwidth]{cluster_field_star_positions.png}
-    \end{center}
-    \vspace{-0.5cm}
-    \caption{
-        {\bf Celestial positions of light curves from Sectors 6 and 7.}
-        \label{fig:lcradecsector6}
-    }
-\end{figure}
-
-\begin{figure}[t]
-	\begin{center}
-		\leavevmode
-		\includegraphics[width=0.49\textwidth]{cam1_cluster_field_star_positions.png}
-	\end{center}
-	\vspace{-0.5cm}
-	\caption{
-    {\bf Celestial positions of light curves from Sector 6, Camera 1.}
-		\label{fig:lcradec}
-	}
-\end{figure}
+% \begin{figure}[t]
+% 	\begin{center}
+% 		\leavevmode
+% 		\includegraphics[width=0.49\textwidth]{cam1_cluster_field_star_positions.png}
+% 	\end{center}
+% 	\vspace{-0.5cm}
+% 	\caption{
+%     {\bf Celestial positions of light curves from Sector 6, Camera 1.}
+% 		\label{fig:lcradec}
+% 	}
+% \end{figure}
 
@@
 Our overall method is in the spirit of the reduction approaches described
-by \citet{Pal_2009}, \citet{soares-furtado_image_2017} and
+by \citet{Pal_2009}, \citet{huang_high-precision_2015}, \citet{soares-furtado_image_2017} and
 \citet{oelkers_precision_2018}; a conceptual overview is given in
@@
 While we performed numerous initial tests on the first sectors of data,
-by geometric coincidence Sectors 1--5 fell away from the galactic plane.
+by geometric coincidence Sectors 1--5 were pointed away from the galactic plane.
 Less than 2\% of the CDIPS target star sample
-is therefore observed in the first five TESS sectors.
+was therefore observed in the first five TESS sectors.
 Though a few interesting clusters are present ({\it e.g.}, Blanco~1, NGC~2516, NGC~1901),
@@
 These begin in Sector 6 (2018-12-12, spacecraft orbit \#19).
+For this run of processing, they conclude at the end of Sector 7
+(2019-02-01, spacecraft orbit \#22).
 
@@
 reference flux for each star.  
-To minimize Poisson errors, our photometric refernce is a median average of
+To minimize Poisson errors, our photometric reference is a median average of
 $N=50$ selected frames.
@@
 
-\begin{figure}[t]
-	\begin{center}
-		\leavevmode
-		\includegraphics[width=0.49\textwidth]{rms_vs_mag.png}
-	\end{center}
-	\vspace{-0.5cm}
-  \caption{ {\bf Standard deviation vs catalog TESS-band magnitude for
-  trend-filtered CDIPS light curves.} The minimum RMS across all three
-  aperture sizes was selected.  The photon and read noise are
-  calculated using the effective area from \citet{vanderspek_2018}.
-  The noise from unresolved background stars is expected to be more
-  important than read noise at the faint end, but is omitted from the
-  plot due to model uncertainties (see \S~\ref{subsec:lcstatistics}).
-		\label{fig:rms_vs_mag}
-	}
-\end{figure}
+\subsubsection{Stellar properties}
 
@@
 
-The standard deviation of the light curves is plotted as a function of the 
-catalog $T$-band magnitude for CDIPS light curves in 
-Figure~\ref{fig:rms_vs_mag}.
-Ignoring the expected noise contribution from the zodiacal and faint star 
-background, the light curves generally seem to follow the model one would 
-predict.
-The bright end is somewhat noisier than the performance reported by SPOC 
-(CITE), as well as the pipelines of 
-Chelsea (CITE) and Ben (CITE), and maybe Ryan (CITE).
-Simple aperture photometry should out-perform image subtraction techniques in 
-the bright regime, so this is not particularly unexpected.
-
-A few points concerning the noise model predictions are relevant.
-First, the effects of crowding are not apparent in 
-Figure~\ref{fig:rms_vs_mag}. 
-If the reference fluxes were being measured directly from the photometric 
-reference frame, the faint stars would be driven below the expected noise 
-floor, because the reference fluxes would be systematically overestimated.
-Our procedure for determining the reference magnitudes uses our knowledge of 
-the catalog magnitudes to eliminate this effect (REFERENCE).
-
-Second, our plot omits the noise from unresolved background stars.
-If we include it, then our RMS at the faint end is about 0.7x below the model.
-This suggests that the model over-predicts the background, or that we overfit 
-the majority of our light curves. Both are probably a little true.
-
-ACF statistics before and after detrending(?)
-
-SNR of retrieved HJs.
-
-Maybe movies of subtracted images?
-
-Some stellar variability plots (perhaps of known stellar variables).
-
-Some focus on particular clusters.
-
-\paragraph{Light curve provenance}.
-In Sector 6, about 49{,}000 light curves of candidate cluster stars
+Describe
+Figure~\ref{fig:cdf_T_mag}
+Figure~\ref{fig:hrd}
+Figure~\ref{fig:propermotions}
+
+\subsubsection{Cluster membership provenance}.
+
+\paragraph{Sector 6}
+In Sector 6, \sVInumberlcs light curves of candidate cluster stars
 were made. The provenance of the claimed cluster origin of these
@@
 
+\paragraph{Sector 7}
+In Sector 7, \sVIInumberlcs light curves of candidate cluster stars
+were made. The provenance of the claimed cluster origin of these
+sources is  ...
+
+The clusters with the largest claimed numbers of sources are ...
+
+\subsubsection{Light curve noise properties}
+
+\begin{figure}[t]
+	\begin{center}
+		\leavevmode
+		\includegraphics[width=0.49\textwidth]{rms_vs_mag.png}
+	\end{center}
+	\vspace{-0.5cm}
+  \caption{ {\bf Standard deviation vs catalog TESS-band magnitude for
+  trend-filtered CDIPS light curves.} 
+  The minimum RMS across all three
+  aperture sizes was selected.  The photon and read noise are
+  calculated using the effective area from \citet{vanderspek_2018}.
+  The noise from unresolved background stars is a function of
+  galactic latitude, and dominates over zodiacal light and read noise
+  for faint stars near the galactic plane; the dotted line assumes a
+  sight-line towards the center of Sector 6, Camera 1 (further details
+  are in \S~\ref{subsec:lcstatistics}).
+		\label{fig:rms_vs_mag}
+	}
+\end{figure}
+
+\paragraph{Observed RMS vs magnitude.}
+The standard deviation of the TFA-detrended light curves is plotted as
+a function of the catalog $T$-band magnitude for CDIPS light curves in
+Figure~\ref{fig:rms_vs_mag}.
+For the $y$-axis of this plot, we have taken
+\begin{equation}
+  {\rm RMS} = \left[
+    \frac{1}{N-M-1}
+    \sum_{i=1}^{N} (f_i - \bar{f})^2
+  \right]^{1/2},
+\end{equation}
+where $f_i$ is the value of the flux at the $i^{\rm th}$ point in the
+time-series, $\bar{f}$ is the mean flux, $N$ is the
+number of points in the time-series, and $M$ is the number
+of template light curves used during TFA detrending.
+The correction in the denominator penalizes the natural degree of
+overfitting inherent to the TFA algorithm.
+
+The observed RMS (black points) follows the expected shape,
+with photon noise dominating from $T=9$ to $T=12$, beyond which the
+onset of the ``sky'' background changes the overall slope of the
+curve to a slightly steeper scaling.
+For the brightest stars ($T\lesssim 9$), a ``systematic floor'' was an
+expected part of the mission's error budget \citep{ricker_transiting_2015}, 
+but 
+has not been observed in early
+reports of the photometric performance of various aperture photometry
+pipelines ({\it e.g.,} the SPOC pipeline \citealt{jenkins_spoc_2010},
+the MIT-QLP \citealt{huang_tess_2018}, and \texttt{eleanor}
+\citealt{feinstein_eleanor_2019}).
+The fact that our light curves for the brightests stars are above this
+purported ``floor'', rather than below it, suggests that our
+image subtraction techniques could be introducing some small degree of
+noise to the light curves of the brightest stars.
+It is also true however that our largest aperture contains only about
+16 pixels, which is sub-optimal for stars brighter than $T\approx9$
+\citep[see][Figure~14]{Sullivan_et_al_2015}.
+Since the brightest stars are not the focus of the present work, we
+leave this as a point to improve in future work.
+
+Importantly, the faint stars do not noticeably exhibit
+the typical effects of crowding at the faint end 
+\citep[{\it e.g.},][Figure~5]{feinstein_eleanor_2019}.
+In aperture photometry pipelines, star in very crowded regions typically 
+have their flux overestimated relative to what would be predicted from their
+catalog magnitudes.
+This leads to systematic underestimates of the uncertainty in the relative 
+fluxes, as well as ``flux contamination'' (the reduction in amplitude of say, 
+transit signals, due to diluting flux).
+Our method to work around this problem -- using the catalog magnitudes to 
+predict the reference flux values, and measuring deviations from these 
+reference fluxes on the subtracted images -- seems to be performing as we had 
+hoped.
+
+\paragraph{Expected RMS vs magnitude.}
+
+The noise model shown in Figure~\ref{fig:rms_vs_mag} is quite similar
+to that of \citet{Sullivan_et_al_2015}, save for two changes.
+The first change is minor: the effective area of the telescope is
+updated to be $86.6\,{\rm cm}^2$, per the measurements of
+\citet{vanderspek_2018}.
+
+The second point is more important: we explicitly include the
+estimated noise contribution from unresolved faint stars.  The
+brightness of the diffuse sky is dominated by different sources at
+different wavelengths.  For instance, the CMB is most important in
+the microwave, and thermal radiation from dust grains in the solar
+system (zodiacal light) is dominant in the far infra-red
+\citep{leinert_1997_1998}.  In the TESS-band, both zodiacal light and
+faint stars can play a role, depending on the line of sight under
+consideration. The zodiacal light is brightest near the ecliptic
+plane, and the faint star background is brightest near the galactic
+plane (and towards the galactic center).  \citet{winn_background_2013}
+estimated the photon-counts from each component that would be observed 
+by TESS.
+His zodiacal light model was presented by \citet{Sullivan_et_al_2015},
+but the faint star model was not emphasized since the Sullivan
+simulations were performed away from the galactic plane.
+
+A few words are therefore pertinent about the diffuse sky model we
+have used for Figure~\ref{fig:rms_vs_mag}, which is adopted explicitly
+because most of our target stars are near the galactic plane.
+Stars are judged to be ``unresolved'' and part of the background if
+their surface density exceeds the angular resolution of the telescope.
+TESS has an angular resolution of $\Delta \theta \sim 1'$, set by a
+combination of the pixel size as well as the typical stellar FWHM.
+Sources with sky surface density exceeding $\Delta \theta^{-2}$
+therefore contribute to the background.
+
+The relevant quantity needed to calculate the integrated 
+photon counts from faint sources
+is  $N(<m,l,b)$ --- the number of stars per square arcsecond
+brighter than magnitude $m$, along a line of sight with galactic
+longitude and latitude $(l,b)$.
+\citet{winn_background_2013} queried the Besan\c con model 
+\citep{robin_synthetic_2003}  along a grid of galactic sight-lines, and 
+converted the resulting $N(<m,l,b)$ surface densities into $I$-band surface 
+brightnesses.
+Fitting a smooth function to the results, \citet{winn_background_2013} found
+\begin{equation}
+I\ {\rm mag\ arcsec}^{-2} =
+    a_0 + a_1 \left(\frac{|b|}{40^\circ}\right)
+    + a_2 \left(\frac{|l|}{180^\circ}\right)^{a_3},
+\end{equation}
+where the galactic longitude $l$ is measured from $-180^\circ$ to 
+$180^\circ$, and the empirical coefficients were found to be $a_0 = 18.9733$, 
+$a_1=8.833$, $a_2=4.007$, and $a_3=0.805$.
+This fit was cautioned to be {\it very approximate}.
+It is sensitive to the threshold used to select ``unresolved'' stars, and 
+likely no more accurate than 0.5 mag on average.
+In regions with exceptionally high extinction ({\it e.g.}, star forming 
+regions) it is expected to systematic underestimate the background brightness 
+by an even larger degree.
+
+\paragraph{ACF statistics}
+ACF statistics before and after detrending(?)
+
+SNR of retrieved HJs.
+
+Maybe movies of subtracted images?
+
+Some stellar variability plots (perhaps of known stellar variables).
+
+Some focus on particular clusters.
+
 \subsection{Objects of Interest}
@@
 
-As an initial search for transiting planets, strong stellar rotators, and 
-eclipsing binaries, we performed a few steps of post-processing. For 
-simplicity,
-we chose a single aperture size~--~``aperture 2''~--~with a radius of 1.5 
-pixels, to perform the period search.
-
-First, to identify periodic transit-like signals, we used 
+To identify an initial set of transiting planets, strong stellar rotators, and 
+eclipsing binaries, we performed a few steps of post-processing on the light 
+curve described in the preceding sections. 
+This processing was entirely independent of the data release, since it was 
+quite specific to our own scientific interests.
+
+For simplicity,
+we first chose a single aperture size~--~``aperture 2''~--~with a radius of 
+1.5  pixels.
+Then, to identify periodic transit-like signals, we used 
 \citet{hippke_TLS_2019}'s transit least-squares (TLS) tool.
@@
 rather than standard linear-in-frequency sampling.
-During the period search, we rejected $6\,{\rm hours}$ at the
+Our grids typically consisted of about 30 different durations, and
+about 5000 periods between 0.5 and 21 days.
+
+Before performing the period search, we rejected $6\,{\rm hours}$ at the
 beginning and end of each spacecraft orbit, to mitigate the presence
 of correlated red noise in the results.
-This shrinks the data volume by about 5\%, but also lowers the number
+This shrank the data volume by about 5\%, but also lowered the number
 of systematic false positives in subsequent vetting.
-Our grids typically consisted of about 30 different durations, and
-about 5000 periods between 0.5 and 21 days. 
-We also ran a generalized Lomb-Scargle periodogram (CITE), simply to 
-have additional periodicity information.
-
-We then performed a cut on the TLS signal detection efficiency:
-${\rm SDE} > 12$.
-This yielded XXX light curves, and we then
-performed TFA signal reconstruction on these lightcurves using 
+We then performed an asymmetric sigma-clipping of $(50\sigma,5\sigma)$ to 
+preserve transits while omitting flares and other positive flux excursions.
+
+A number of the light curves show residual variability, often of stellar 
+origin.
+This expected for a sample of young stars; the issue of finding transits in 
+the face of large stellar rotation signals 
+has been explored by both \citet{rizzuto_zeitV_2017} and also 
+\citet{hippke_wotan_2019}.
+The former adopted an approach that we have yet to explore, which is to 
+pass a sliding window over the light curve that, within each step, performs a 
+Bayesian model comparison between a spline and a spline-plus-notch model.  If 
+the spline-plus-notch model is favored, the transits are preserved for 
+subsequent discovery.
+\citet{hippke_wotan_2019}, conversely, described a large number of possible 
+detrending methods, and found that many performed more or less the same at 
+recovering planetary transits for a sample of young stars with strong rotation 
+signals.
+
+Our approach in this work is essentially identical to one of the methods 
+described by \citet{hippke_wotan_2019}.
+First, we run a generalized Lomb-Scargle periodogram (CITE) on each TFA light 
+curve.
+If a peak is found with false alarm probability below $10^{-5}$, we consider 
+the star ``variable'', and opt to 
+detrend the light curve with robust penalized B-splines, which are splines 
+with knot-length automatically determined via cross-validation 
+\citep{eilers_flexible_1996}. The idea behind the cross-validation is that a 
+larger  number of knots leads to smaller residuals on training data, but 
+larger errors 
+when tested on the entire dataset.
+We used the \texttt{wotan} implementation, which is a wrapper to the 
+\texttt{pyGAM} spline fitter, with $2\sigma$ clipping of outliers from the fit 
+residuals at each iteration 
+\citep{serven_pygam_2018_1476122,hippke_wotan_2019}.
+The maximum number of spline knots is set to 50, which for each TESS sector 
+($\approx 25\,{\rm days}$) is commensurate with a $\approx0.5\,{\rm day}$ 
+window.
+
+\begin{figure}[!ht]
+    \gridline{\fig{tlsresult_sector6.png}{0.45\textwidth}{}}
+    \vspace{-0.8cm}
+    \gridline{\fig{tlsresult_sector7.png}{0.45\textwidth}{}}
+    \caption{
+        Significance thresholds empirically defined for the transiting planet 
+        search described in \S~\ref{subsec:ctois}. Each point represents the 
+        TLS periodogram peak signal detection efficiency from one light curve.
+        {\it Top.} Sector 6.  {\it Bottom.} Sector 7.
+    }
+    \label{fig:tlsresults}
+\end{figure}
+
+After (optionally) detrending, we run the TLS search. To select 
+``significant'' signals for visual inspection, we 
+performed a cut on the TLS signal detection efficiency defined piecewise over 
+the signal periods.
+The overall lower limit is ${\rm SDE} > 12$, with higher limits imposed in 
+regions with heavy contamination from systematic signals.
+The signals for sectors 6 and 7 are shown in the space of SDE vs period in 
+Figure~\ref{fig:tlsresults}.
+
+This yielded a few thousand light curves.  About two-thirds already had been 
+detrended with splines, and were not processed further.
+For the remaining third we
+performed TFA signal reconstruction using 
 \texttt{vartools}.
@@
 most powerful peak in the TLS spectrum, rather than being a constant function. 
-Generally speaking, this helps improve the quality of the resulting light 
-curve.
-
-We then make a multi-page \texttt{.pdf} document with the information 
+This helps improve lower the scatter of the light curve at frequencies near 
+the TLS peak.
+
+We then make a multi-page \texttt{.pdf} document report with the information 
 necessary to make classifications for vetting.
-These documents are released along with the light curves, as a useful summary
- for anyone interested in the subset of objects that we have analyzed.
+These documents are released along with the light curves, and are a useful 
+summary for anyone interested in the subset of objects that we have analyzed.
 A full description of each page of the summary \texttt{.pdf} is given in the 
@@
   \texttt{astroquery} \citep{astroquery_2018},
-  \texttt{astroquery.gaia}
-  \texttt{astroquery.simbad}
-  \texttt{astroquery.mast}
-  \texttt{astroquery.nasaexopanetarchive}  
+  \texttt{astroquery.gaia} CITE,
+  \texttt{astroquery.simbad} CITE,
+  \texttt{astroquery.mast} CITE,
+  \texttt{astroquery.nasaexopanetarchive} CITE,
   \texttt{BATMAN} \citep{kreidberg_batman_2015},
@@
   \texttt{pandas} \citep{mckinney-proc-scipy-2010},
+  \texttt{pyGAM} \citep{serven_pygam_2018_1476122}
   \texttt{scipy} \citep{jones_scipy_2001},
   \texttt{TagSpaces} (CITE),
-  \texttt{tesscut} \citep{brasseur_astrocut_2019}
+  \texttt{tesscut} \citep{brasseur_astrocut_2019},
+  \texttt{wotan} \citep{hippke_wotan_2019}
 }

### 2019-06-20 drivers/paper_plot_all_figures.py
minor figure updates

@@ -30,20 +30,20 @@ def main():
     # fig N: RMS vs catalog T mag
     plot_rms_vs_mag(sectors, overwrite=1)
 
-    # # fig N: histogram (or CDF) of stellar magnitude (T mag)
-    # plot_cdf_T_mag(sectors, overwrite=0)
+    # fig N: histogram (or CDF) of stellar magnitude (T mag)
+    plot_cdf_T_mag(sectors, overwrite=1)
 
-    # # fig N: histogram (or CDF) of TICCONT. unfortunately this is only
-    # # calculated for CTL stars, so by definition it has limited use
-    # plot_cdf_cont(sectors, overwrite=0)
+    # fig N: histogram (or CDF) of TICCONT. unfortunately this is only
+    # calculated for CTL stars, so by definition it has limited use
+    plot_cdf_cont(sectors, overwrite=1)
 
-    # # fig N: HRD for CDIPS stars.
-    # plot_hrd_scat(sectors, overwrite=0, close_subset=1)
-    # plot_hrd_scat(sectors, overwrite=0, close_subset=0)
+    # fig N: HRD for CDIPS stars.
+    plot_hrd_scat(sectors, overwrite=1, close_subset=1)
+    plot_hrd_scat(sectors, overwrite=1, close_subset=0)
 
-    # # fig N: pmRA and pmDEC scatter for CDIPS stars.
-    # plot_pm_scat(sectors, overwrite=0, close_subset=1)
-    # plot_pm_scat(sectors, overwrite=0, close_subset=0)
+    # fig N: pmRA and pmDEC scatter for CDIPS stars.
+    plot_pm_scat(sectors, overwrite=1, close_subset=1)
+    plot_pm_scat(sectors, overwrite=1, close_subset=0)
 
     # # fig N: positions of field and cluster stars (currently all cams)
     # plot_cluster_and_field_star_scatter(sectors, overwrite=1)
@@ -99,7 +99,8 @@ def plot_cdf_T_mag(sectors, overwrite=0):
     bins = np.arange(np.floor(np.min(df[magstr])),
                      np.ceil(np.max(df[magstr]))+1,
                      1)
-    ax.hist(df[magstr], bins=bins, cumulative=True)
+    ax.hist(df[magstr], bins=bins, cumulative=True, color='black', fill=False,
+            linewidth=0.5)
 
     ax.yaxis.set_ticks_position('both')
     ax.xaxis.set_ticks_position('both')
[…]

### 2019-06-20 paper/ms.tex
update

@@
 \subsubsection{Light curve noise properties}
+\label{subsubsec:rmsvsmag}
 
@@
 		\leavevmode
-		\includegraphics[width=0.49\textwidth]{rms_vs_mag.png}
+		\includegraphics[width=0.47\textwidth]{rms_vs_mag.png}
 	\end{center}
@@
   trend-filtered CDIPS light curves.} 
-  The minimum RMS across all three
-  aperture sizes was selected.  The photon and read noise are
-  calculated using the effective area from \citet{vanderspek_2018}.
-  The noise from unresolved background stars is a function of
-  galactic latitude, and dominates over zodiacal light and read noise
-  for faint stars near the galactic plane; the dotted line assumes a
+  Black points correspond to the minimum RMS across the available three
+  aperture sizes.  
+  The model (orange and gray lines) uses the optimal aperture sizes reported 
+  by \citet{Sullivan_et_al_2015}, and the effective area from 
+  \citet{vanderspek_2018}.
+  The noise from unresolved background stars (dotted gray line) is a function 
+  of galactic latitude, and dominates over zodiacal light and read noise
+  for faint stars near the galactic plane; the line shown assumes a
   sight-line towards the center of Sector 6, Camera 1 (further details
-  are in \S~\ref{subsec:lcstatistics}).
+  are in \S~\ref{subsubsec:rmsvsmag}).
 		\label{fig:rms_vs_mag}

### 2019-06-23 cdips/plotting/plot_catalog_to_gaia_match_statistics.py
update plots

@@ -93,6 +93,12 @@ def plot_catalog_to_gaia_match_statistics(bigdf, outpath, isD14=False):
     axs[2].set_xlim([4,18])
     axs[2].set_ylim([-2.1,2.1])
 
+    for ax in axs:
+        ax.yaxis.set_ticks_position('both')
+        ax.xaxis.set_ticks_position('both')
+        ax.get_yaxis().set_tick_params(which='both', direction='in')
+        ax.get_xaxis().set_tick_params(which='both', direction='in')
+
     f.tight_layout()
     f.savefig(outpath, dpi=450, bbox_inches='tight')
     print('saved {}'.format(outpath))

### 2019-06-23 drivers/paper_plot_all_figures.py

@@ -31,7 +31,6 @@ CLUSTERDATADIR = '/home/lbouma/proj/cdips/data/cluster_data'
 
 def main():
 
-    assert 0
     # fig N: wcs quality verification
     plot_wcs_verification()
 
@@ -41,31 +40,33 @@ def main():
     sectors = [6,7]
 
     # fig N: cumulative counts of CDIPS target stars.
-    plot_target_star_cumulative_counts(OC_MG_CAT_ver=0.3, overwrite=1)
+    plot_target_star_cumulative_counts(OC_MG_CAT_ver=0.3, overwrite=0)
 
     # fig N: catalog_to_gaia_match_statistics
-    plot_catalog_to_gaia_match_statistics(overwrite=1)
+    plot_catalog_to_gaia_match_statistics(overwrite=0)
 
     # fig N: RMS vs catalog T mag
-    plot_rms_vs_mag(sectors, overwrite=1)
+    plot_rms_vs_mag(sectors, overwrite=0)
 
     # fig N: histogram (or CDF) of stellar magnitude (T mag)
-    plot_cdf_T_mag(sectors, overwrite=1)
+    plot_cdf_T_mag(sectors, overwrite=0)
 
     # fig N: histogram (or CDF) of TICCONT. unfortunately this is only
     # calculated for CTL stars, so by definition it has limited use
-    plot_cdf_cont(sectors, overwrite=1)
+    # plot_cdf_cont(sectors, overwrite=1)
 
     # fig N: HRD for CDIPS stars.
-    plot_hrd_scat(sectors, overwrite=1, close_subset=1)
-    plot_hrd_scat(sectors, overwrite=1, close_subset=0)
+    plot_hrd_scat(sectors, overwrite=0, close_subset=1)
+    plot_hrd_scat(sectors, overwrite=0, close_subset=0)
 
     # fig N: pmRA and pmDEC scatter for CDIPS stars.
-    plot_pm_scat(sectors, overwrite=1, close_subset=1)
-    plot_pm_scat(sectors, overwrite=1, close_subset=0)
+    plot_pm_scat(sectors, overwrite=0, close_subset=1)
+    plot_pm_scat(sectors, overwrite=0, close_subset=0)
 
     # fig N: positions of field and cluster stars (currently all cams)
-    plot_cluster_and_field_star_scatter(sectors, overwrite=0)
+    plot_cluster_and_field_star_scatter(sectors=sectors, overwrite=1)
[…]

### 2019-06-23 paper/ms.tex

@@
 \citep{skrutskie_tmass_2006} to report the existence of 2859 open
-clusters and stellar associations.
-We selected their ``$1\sigma$'' members according to the
+clusters and stellar associations (globular clusters were
+omitted by excluding any entry of type \texttt{'g'}).
+We selected ``$1\sigma$'' members according to the
 combined photometric, kinematic, and spatial criteria described by
@@
 		\leavevmode
-		\includegraphics[width=0.45\textwidth]{star_catalog_mag_histogram_phot_rp_mean_mag.png}
+		\includegraphics[width=0.45\textwidth]{target_star_cumulative_counts.png}
 	\end{center}
@@
 	\caption{
-    {\bf Cumulative counts of candidate cluster member stars a
-    function of Gaia $Rp$-band magnitude.}
+    {\bf Cumulative number of target stars as
+    a function of Gaia $Rp$-band magnitude.}  The selected stars are eiher candidate
+    members of clusters, or else have other youth indicators. We only consider stars
+    with $G_{\rm Rp} < 16$.
 	\label{fig:cdips_targets}

### 2019-06-23 paper/ms.tex
update paper

@@
 \newcommand{\numberclusters}{XXX\ }
+
+\newcommand{\stscilink} {\url{archive.stsci.edu/prepds/cdips}}
 
@@
   The light curves and vetting reports are available at
-  \url{archive.stsci.edu/prepds/cdips}.
+  \stscilink.
 \end{abstract}
@@
 
-%\begin{figure*}[t]
-%	\begin{center}
-%		\leavevmode
-%		\includegraphics[width=0.7\textwidth]{cluster_positions.pdf}
-%	\end{center}
-%	\vspace{-0.5cm}
-%	\caption{
-%    {\bf TESS looks at many clusters.} Placeholder skymap.
-%		\label{fig:clustermap}
-%	}
-%\end{figure*}
-
-\begin{figure*}[!ht]
-    \gridline{
-      \fig{cluster_field_star_positions.png}{0.49\textwidth}{}
-      \fig{cam1_cluster_field_star_positions.png}{0.49\textwidth}{}
-    }
-    %\begin{center}
-    %    \leavevmode
-    %    \includegraphics[width=0.49\textwidth]{cluster_field_star_positions.png}
-    %\end{center}
-    \vspace{-0.5cm}
-    \caption{
-        {\it Left}. Celestial positions of light curves from Sectors 6 and 7.
-        {\it Right}. Celestial positions of light curves from Sector 6, Camera 1.
-        \label{fig:lcradecsector6}
-    }
-\end{figure*}
-
-% \begin{figure}[t]
-% 	\begin{center}
-% 		\leavevmode
-% 		\includegraphics[width=0.49\textwidth]{cam1_cluster_field_star_positions.png}
-% 	\end{center}
-% 	\vspace{-0.5cm}
-% 	\caption{
-%     {\bf Celestial positions of light curves from Sector 6, Camera 1.}
-% 		\label{fig:lcradec}
-% 	}
-% \end{figure}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-However, a homogeneous membership calculation for every known
+How
+ever, a homogeneous membership calculation for every known
 cluster is outside our scope.  So too is a homogeneous search for
@@
     {\bf Cumulative number of target stars as
-    a function of Gaia $Rp$-band magnitude.}  The selected stars are eiher candidate
-    members of clusters, or else have other youth indicators. We only consider stars
-    with $G_{\rm Rp} < 16$.
+    a function of Gaia $Rp$-band magnitude.}  The selected stars are
+    either candidate members of clusters, or else have other youth
+    indicators (see \S~\ref{sec:starselection}). We only consider
+    stars with $G_{\rm Rp} < 16$.
 	\label{fig:cdips_targets}
@@
 	\caption{
-		{\it Top.} Cross-match statistics from \cite{Kharchenko_et_al_2013} {\it 
-			vs.} Gaia-DR2.
-		{\it Bottom.} Ditto, for \cite{dias_proper_2014} {\it vs.} Gaia-DR2.
+    {\it Top.} Cross-match statistics from
+    \cite{Kharchenko_et_al_2013} cluster members to Gaia-DR2. A
+    histogram of the distances between matched stars is on the left; a
+    histogram of the difference between the true $G$-band magnitude
+    and that predicted from 2MASS photometry in the middle; a scatter
+    plot of the same magnitude difference as a function of $G$-band
+    magnitude is on the right.
+    {\it Bottom.} Same, but cross-matching \cite{dias_proper_2014}
+    cluster members to Gaia-DR2.
 	}
@@
 
-\begin{figure}[t]
+\begin{figure}[!t]
+	%\gridline{
+	%  \fig{cluster_field_star_positions.png}{0.49\textwidth}{}
+	%  \fig{sector6_cam[1]_ccd[1-2-3-4]cluster_field_star_positions.png}{0.49\textwidth}{}
+	%}
+	\begin{center}
+		\leavevmode
+		\includegraphics[width=0.47\textwidth]{cluster_field_star_positions.png}
+	\end{center}
+	\vspace{-0.5cm}
+	\caption{
+		{\bf Celestial positions of light curves from Sectors 6
+			and 7.}  Black: $G_{\rm Rp}<13$ field stars.  Blue: $G_{\rm
+			Rp}<16$ target stars.
+		\label{fig:lcradec}
+	}
+\end{figure}
+
+\begin{figure}[!t]
+	\begin{center}
+		\leavevmode
+		\includegraphics[width=0.47\textwidth]{sector6_cam[1]_ccd[1-2-3-4]cluster_field_star_positions.png}
+	\end{center}
+	\vspace{-0.5cm}
+	\caption{
+		{\bf  Zoom of Sector 6, Camera 1 from Figure~\ref{fig:lcradec}.}
+		\label{fig:lcradeczoom}
+	}
+\end{figure}
+
+\begin{figure}[!t]
 	\begin{center}
@@
 	\caption{
-    {\bf Cumulative distribution of TESS-band magnitudes for CDIPS
-    light curves.}
+    {\bf Cumulative number of CDIPS light curves a function of TESS
+    $T$-band magnitude.}  Light curves were made for the subset of
+    stars shown in Figure~\ref{fig:cdips_targets} that were observed
+    in Sectors 6 or 7.
 		\label{fig:cdf_T_mag}
@@
 	\gridline{\fig{hrd_scat_close_subset.png}{0.45\textwidth}{}}
+	\vspace{-0.8cm}
 	\caption{
-    {\it Top.} HR diagram of CDIPS stars with light curves in this
-    data release.  {\it Bottom.} HR diagram of close CDIPS stars with
-    light curves. The wedge separating the pre-MS sample from the MS
+    {\it Top.} HR diagram of CDIPS stars on silicon in this
+    data release.  {\it Bottom.} HR diagram of close CDIPS stars on
+    silicon. The wedge separating the pre-MS sample from the MS
     stars was discussed by \citet{zari_3d_2018}, who introduced it in
@@
 
-\begin{figure}[!ht]
+\begin{figure}[!t]
 	\gridline{\fig{pm_scat_all_CDIPS_LCs.png}{0.45\textwidth}{}}
@@
 	\gridline{\fig{pm_scat_close_subset.png}{0.45\textwidth}{}}
+	\vspace{-0.8cm}
 	\caption{
-    {\it Top.} Proper motions of CDIPS stars with light curves in this
-    data release.  {\it Bottom.} Proper motions of close CDIPS stars
-    with light curves. A few additional clusters are visible.
+    {\it Top.} Proper motions of CDIPS stars on silicon in this
+    data release.  Many of the stars in the central ``blob'' are possible
+    field-contaminants.
+    {\it Bottom.} Proper motions of close CDIPS stars
+    on silicon.
 	}
@@
 
-Describe
-Figure~\ref{fig:cdf_T_mag}
-Figure~\ref{fig:hrd}
-Figure~\ref{fig:propermotions}
+The on-sky locations of the light curves from Sectors 6 and 7
+are shown in Figure~\ref{fig:lcradec}.
+Black stars are the field stars for which we performed photometry,
+but only to calibrate the cluster star sample.
+The blue stars are the \numberlcs stars with light curves available
+from \stscilink.
+Most of the target stars are quite close to the galactic plane.
+Gaps between CCD chips are also visible.
+
+A zoom-in of Figure~\ref{fig:lcradec} is shown in Figure~\ref{fig:lcradeczoom}
+for the Camera 1, Sector 6 field. The effects of galactic-latitude
+dependent extinction are visible through the decreasing density of black
+points towards the right of the image.
+The highly clumped nature of the target stars is also apparent.
+
+Figure~\ref{fig:cdf_T_mag} shows the cumulative distribution of
+TESS $T$-band magnitudes for the target stars.
+Though most of the targets are faint, $\approx3\times10^4$ are
+brighter than $T=13$, and so are more promising targets for any
+detailed follow-up observtions.
+
+An HR diagram for the entire sample of stars on silicon
+is shown in Figure~\ref{fig:hrd} (top).
+The sub-sample of stars with
+measured positive parallaxes and naive distances less than
+$1\,{\rm kpc}$ is also shown (bottom).
+About one-third of the stars are in this latter sample.
+The close stars are predominantly on the main-sequence, or the pre-main-sequence.
+A relatively large fraction of these come from \citet{zari_3d_2018},
+and are either on the PMS or upper main-sequence.
+The latter set of OBA dwarf stars, while ``younger'' than the typical
+field dwarf, are likely the least interesting subset of our target sample
+from the perspective of age analyses.
+In the entire sample (Figure~\ref{fig:hrd} top), a much larger fraction of stars are sub-giants,
+red giants, and helium-burning red-clump stars.
+We failed to obtain light curves for roughly $5\%$ of the stars on silicon, 
+primarily due to our masking of saturated stars and their nearby pixels.
+
+Finally, 
+Figure~\ref{fig:propermotions} shows the proper motions
+of the entire and close samples of stars on silicon.
+Each clump signifies a different star cluster. The central
+blob in the top figure is in fact two separate blobs,
+due to the different directions in the Galaxy being observed
+in Sectors 6 and 7.
 
@@
   aperture sizes.  
-  The model (orange and gray lines) uses the optimal aperture sizes reported 
+  The model (orange and gray lines) assumes aperture sizes reported 
   by \citet{Sullivan_et_al_2015}, and the effective area from 
@@
   The noise from unresolved background stars (dotted gray line) is a function 
-  of galactic latitude, and dominates over zodiacal light and read noise
+  of galactic latitude, and dominates over zodiacal light
   for faint stars near the galactic plane; the line shown assumes a
@@
 
-\begin{figure}[!ht]
+\begin{figure}[!t]
     \gridline{\fig{tlsresult_sector6.png}{0.45\textwidth}{}}

### 2019-06-23 paper/collect_figures.sh

@@ -7,9 +7,9 @@
 fdir=../paper/figures/
 pdir=../paper/
 
-# positions of clusters
-cp ${fdir}GI_figs/cluster_positions_ecliptic_scicase.pdf \
-   ${pdir}cluster_positions.pdf
+# # positions of clusters
+# cp ${fdir}GI_figs/cluster_positions_ecliptic_scicase.pdf \
+#    ${pdir}cluster_positions.pdf
 
 # what our pipeline does
 cp ${fdir}trex_overview.pdf ${pdir}pipelineoverview.pdf
@@ -30,7 +30,8 @@ fdir=../results/paper_figures/
 cp ${fdir}rms_vs_mag.png ${pdir}rms_vs_mag.png
 
 # positions of lightcurves
-cp ${fdir}cam1_cluster_field_star_positions.png ${pdir}cam1_cluster_field_star_positions.png
+cp ${fdir}sector6_cam[1]_ccd[1-2-3-4]cluster_field_star_positions.png \
+   ${pdir}sector6_cam[1]_ccd[1-2-3-4]cluster_field_star_positions.png
 
 # positions of lightcurves
 cp ${fdir}cluster_field_star_positions.png ${pdir}cluster_field_star_positions.png

### 2019-06-23 paper/ms.tex
add vetting report to appendix

@@
 		{\bf  Zoom of Sector 6, Camera 1 from Figure~\ref{fig:lcradec}.}
+		The most populated cluster is XXX, primarily due to candidate
+		members proposed by \citet{dias_proper_2014}.
 		\label{fig:lcradeczoom}
@@
     {\bf Cumulative number of CDIPS light curves a function of TESS
-    $T$-band magnitude.}  Light curves were made for the subset of
-    stars shown in Figure~\ref{fig:cdips_targets} that were observed
+    $T$-band magnitude.}  Light curves were made for the
+    target stars (Figure~\ref{fig:cdips_targets}) that were observed
     in Sectors 6 or 7.
@@
 origin.
-This expected for a sample of young stars; the issue of finding transits in 
+This is expected for a sample of young stars; the problem of finding transits in 
 the face of large stellar rotation signals 
@@
 subsequent discovery.
-\citet{hippke_wotan_2019}, conversely, described a large number of possible 
-detrending methods, and found that many performed more or less the same at 
+\citet{hippke_wotan_2019}, conversely, described a number of different
+detrending methods, and found that most performed more or less the same at 
 recovering planetary transits for a sample of young stars with strong rotation 
@@
 described by \citet{hippke_wotan_2019}.
-First, we run a generalized Lomb-Scargle periodogram (CITE) on each TFA light 
-curve.
+First, we run a generalized Lomb-Scargle periodogram on each TFA light 
+curve \citep{lomb_1976,scargle_studies_1982,vanderplas_periodograms_2015}.
 If a peak is found with false alarm probability below $10^{-5}$, we consider 
@@
 
+We verified by injecting and recovering a 2.5 mmag central-transit planet
+with variable period that this detrending approach marginally improved
+the recovery probability, compared to not doing anything.
+The main cases for which it helps are those with large residual stellar
+variability in the TFA light curve.
+
 \begin{figure}[!t]
@@
 most powerful peak in the TLS spectrum, rather than being a constant function. 
-This helps improve lower the scatter of the light curve at frequencies near 
+This helps lower the scatter of the light curve at frequencies away from
 the TLS peak.
@@
 
-The classifications we used assess:
+The classifications we used assessed:
 \begin{enumerate}
-    \item {\it The source of photometric variability}. Designations include 
+    \item {\it Photometric variability classification}. Designations include 
     tags for planet candidates, eclipsing binaries, instrumental variations, 
     stellar variations, and ``weirdos''.
+    %
     \item {\it Cluster membership status}. By default, all light curves were 
     made for stars with at least one literature claim of cluster membership.  
-    We therefore include tags only for non-cluster members, and possible 
-    non-cluster members. Typically the primary source of this information is 
-    the Gaia-DR2 parallax.
+    However, some of these claims pre-dated the availability of Gaia-DR2
+    parallaxes or proper motions.
+    We therefore re-assess the membership status on a case-by-case basis 
+    through inspection of the available astrometry and photometry.
+    Known asterisms are also omitted at this point
+    \citep[{\it e.g.},][]{sulentic_revised_1973,kos_galah_2018}.
+    %
     \item {\it Photometric blends}. Tags are created to highlight whether the 
@@
 In \S~\ref{subsec:ctois}, we described the process by which we made 
-\texttt{.pdf} documents suitable for assessing which objects were interesting 
+vetting reports suitable for assessing which objects were interesting 
 enough to merit further study.
 
-This section briefly summarizes this document. Updated versions and their 
+Figures~\ref{fig:pg1} to~\ref{fig:pg6} of this
+section summarize this document. Updated versions and their 
 \texttt{README} files will live at this web-address: 
 \url{mast.stsci.edu/CDIPS}.
-
-\begin{itemize}
-\item {\it Page 1: period-search summary}. Periodograms from TLS and 
-phase-dispersion minimization 
-\citep{hippke_TLS_2019,stellingwerf_period_1978}, as calculated 
-with \texttt{astrobase.periodbase} are shown. The top three peaks from each 
+The planet candidate chosen for these figures
+(Gaia DR2 \texttt{5541111035713815552} = TIC \texttt{134528212}) was
+chosen for the demonstration in part because it passes all
+the tests.
+
+\begin{figure*}[!h]
+	\begin{center}
+		\leavevmode
+		\includegraphics[width=0.98\textwidth]{gaiatwo0005541111035713815552-0007_page01.pdf}
+	\end{center}
+	\vspace{-0.5cm}
+	\caption{
+		{\bf Page 1: period-search summary.} Periodograms from TLS and 
+		phase-dispersion minimization, as calculated 
+		with \texttt{astrobase.periodbase}, are shown in the top left and top center 
+		\citep{bhatti_astrobase_2018,hippke_TLS_2019,stellingwerf_period_1978}.
+		The top three peaks from each 
 		method are shown in the second and third rows; the raw light curve is in the 
-top-right. A small finder chart from DSS is shown (CITE).
-
-\item {\it Page 2: light curve diagnostics}.
-\end{itemize}
+		top-right. A small finder chart from DSS is inset to the top left, with
+		the 1.5-pixel radius aperture used to extract the light curve in orange (CITE).
+		\label{fig:pg1}
+	}
+\end{figure*}
+
+\begin{figure*}[!h]
+	\begin{center}
+		\leavevmode
+		\includegraphics[width=0.98\textwidth]{gaiatwo0005541111035713815552-0007_page02.pdf}
+	\end{center}
+	\vspace{-0.5cm}
+	\caption{
+		{\bf Page 2: light curve diagnostics.} 
+		Time-series of raw flux (\texttt{IRM2}),  TFA-detrended flux (\texttt{TF2}), stellar-variability
+		detrended flux, and the background are shown as a function of
+		barycentric Julian date.
+		The overplotted dashed vertical lines are the ephemeris of the highest-power
+		TLS peak from Figure~\ref{fig:pg1}.
+		An important check is whether the flux dips are correlated with changes in the 
+		background level -- in this case, they are not.
+		The standard deviation and TESS magnitude are quoted in the upper right.
+		The red line in the second from the top plot is the windowed 
+		spline described in Section~\ref{subsec:ctois} -- in this case it is near its maximal
+		frequency.
+		\label{fig:pg2}
+	}
+\end{figure*}
+
+\begin{figure*}[!h]
+	\begin{center}
+		\leavevmode
+		\includegraphics[width=0.98\textwidth]{gaiatwo0005541111035713815552-0007_page03.pdf}
+	\end{center}
+	\vspace{-0.5cm}
+	\caption{
+		{\bf Page 3: Transit diagnostics.} The plots show the maximally-detrended
+		light curve (top); the phase-folded light curve centered on the primary transit
+		(middle left); the phase-folded light curve centered on the secondary eclipse
+		(middle right); the odd-numbered transits (lower left); and the
+		even-numbered transits (lower right).
+		The stellar parameters ($T_{\rm eff}, R_\star$) are taken from Gaia-DR2 
+		when available.
+		The first eight lines of text are parameters determined 
+		from the best-fitting TLS model.
+		The one exception is the planet radius, which uses the stellar radius
+		as noted above.
+		The ``flux contamination'' (\texttt{TICCONT}) from neighboring stars
+		is {\it never} taken into account, because transit depth dilution does
+		not affect image subtraction analyses in the same manner as 
+		aperture-photometry reductions.
+		To estimate the transit to occulation
+		depth ratio,
+		the phase-folded light curve is also coarsely fit via maximum likelihood
+		by a sum of two gaussians.
+		``AstExc'' refers to the Gaia-DR2 astrometric excess, which can indicate
+		hints of astrometric binarity in the system.
+		``$R_\star + M_\star \rightarrow T_{b0}$'' gives the duration of a 
+		zero-eccentricity central transit based on the Gaia-DR2 stellar radius,
+		and a stellar mass interpolated from the \citet{pecaut_intrinsic_2013} table,
+		under the assumption that the star is a dwarf.%\footnote{\url{http://www.pas.rochester.edu/~emamajek/EEM_dwarf_UBVIJHK_colors_Teff.txt}}.
+		\label{fig:pg3}
+	}
+\end{figure*}
+
+\begin{figure*}[!h]
+	\begin{center}
+		\leavevmode
+		\includegraphics[width=0.98\textwidth]{gaiatwo0005541111035713815552-0007_page04.pdf}
+	\end{center}
+	\vspace{-0.5cm}
+	\caption{
+		{\bf Page 4: Light curves for increasing aperture sizes.} 
+		Apertures of radius 1, 1.5, and 2.25 pixels are shown from top to bottom.
+		The blue line is the reference transit depth from the best-fitting TLS model.
+		Any changes in depth with aperture size might indicate the need for a 
+		detailed pixel-level analysis.
+		\label{fig:pg4}
+	}
+\end{figure*}
+
+\begin{figure*}[!h]
+	\begin{center}
+		\leavevmode
+		\includegraphics[width=0.98\textwidth]{gaiatwo0005541111035713815552-0007_page05.pdf}
+	\end{center}
+	\vspace{-0.5cm}
+	\caption{
+		{\bf Page 5: Cluster membership assessment diagnostics.}
+		The star was considered a candidate cluster member by the source(s) listed under
+		``Reference'', in this case \citet{dias_proper_2014}.
+		The name used in the Dias catalog in this case was \texttt{264-025831}, a
+		UCAC-4 identifier, which can be back-referenced to find that \citet{dias_proper_2014}
+		assigned this star a
+		membership probability in NGC 2546 of 98\%.
+		The base catalog for the plots is chiefly that of \citet{Kharchenko_et_al_2013},
+		due to its homogeneous parameter determination procedure (particularly for age).
+		If a match to the \citet{Kharchenko_et_al_2013} catalog is found, then the remaining
+		plots are populated.
+		Top-left shows the parallax, with orange points sampled from the Gaia-DR2
+		posterior, black points the other cluster members in the Kharchenko catalog,
+		and the blue line the claimed Kharchenko parallax for the cluster.
+		A large number of field contaminants are visible in this case.
+		Top-right are the Gaia proper motions, where against black points are cluster
+		members from Kharchenko, and the orange is the target star.
+		Bottom-left is the HR diagram, and bottom-right are the on-sky positions.
+		In the text,
+		\texttt{N1sr2} is the number of $1\sigma$ cluster members claimed
+		by \citet{Kharchenko_et_al_2013} within the cluster angular radius;
+		$\log t$ is the base-10 logarithm of the age in years;
+		\texttt{type} matches the type codes provided by \citet{Kharchenko_et_al_2013}.
+		\label{fig:pg5}
+	}
+\end{figure*}
+
+\begin{figure*}[!h]
+	\begin{center}
+		\leavevmode
+		\includegraphics[width=0.98\textwidth]{gaiatwo0005541111035713815552-0007_page06.pdf}
+	\end{center}
+	\vspace{-0.5cm}
+	\caption{
+		{\bf Page 6: Imaging variability diagnostics.} 
+		This page is intended to help diagnose which stars are producing the observed
+		variability.
+		Top-left and top-center are the mean out-of-transit (OOT) and mean in-transit 
+		calibrated images (separate from any of our image-subtraction analysis).
+		The OOT images are based on the same number of exposures as the in-transit images
+		and split evenly before and after each transit \citep[following][]{bryson_identification_2013,kostov_l9859_2019}.
+		The yellow star is the target; cyan dots are the flux-weighted centroid of the entire
+		image for each transit event; small red crosses are WCS-projected locations of neighbor stars.
+		Middle-left is the most important sub-panel: the difference between
+		the OOT and in-transit mean images.
+		If the variability shown in background map (units: ADU) is off-target, the
+		transit is typically not from the target star.
+		Middle-center is the same, normalized by the uncertainty map.
+		Lower left and lower center show the DSS field in linear and log scales
+		at roughly the same pixel scale as the TESS image,
+		with the 1, 1.5, and 2.25 pixel-radius apertures in blue, orange, and green respectively.
+		The brightness of neighborhood stars is given on the far right.
+		Note the slight rotation difference between DSS and TESS images;
+		DSS images are aligned north-up, east-left; TESS images are oriented as closely as
+		possible to this system without actually performing the rotation.
+		\label{fig:pg6}
+	}
+\end{figure*}
 

### 2019-06-23 paper/collect_figures.sh

@@ -58,6 +58,9 @@ cp ${fdir}catalog_to_gaia_match_statistics_MWSC.png \
 cp ${fdir}catalog_to_gaia_match_statistics_Dias14.png \
    ${pdir}dias14matchstats.png
 
+# pdftk burst the chosen vetting pdf
+pdftk vet_hlsp_cdips_tess_ffi_gaiatwo0005541111035713815552-0007_tess_v01_llc.pdf burst output gaiatwo0005541111035713815552-0007_page%02d.pdf
+
 
 
 ##########################################

### 2019-06-23 paper/ms.tex
update

@@
 
-\subsection{Objects of Interest}
+\subsection{Identifying Objects of Interest}
 \label{subsec:ctois}
@@
 \end{enumerate}
-The actual classification process was performed by LGB, JH, and JNW.
-The \texttt{TagSpaces} software was used~--~an extremely helpful tool for the 
-purposes of easily assigning labels to documents.
-
-% FIXME FIXME FIXME
+The actual classifications were performed by LGB, JH, and JNW.
+The \texttt{TagSpaces} software was used~--~an extremely helpful tool
+for the purposes of easily assigning labels to documents.
+An example of a full vetting report is described in
+Appendix~\ref{appendix:vetreport}.
+
+\subsection{Objects of Interest}
+The objects that all vetters identified as planet candidates were then
+fit with the usual \citet{mandel_analytic_2002} model. (CITE BATMAN).
+The resulting fits are shown in Figure XXX.
+The parameters of the planet candidates are given in Table YYY, and
+are also available as cTOIs NNN.01 - MMM.01 on exofop-TESS (LINK).
+
+Different types of observations and analyses are needed to confirm 
+(i) the planetary nature of these signals, and
+(ii) whether the host stars are bonafide cluster members.
+For (i), follow-up photometry, high-resolution imaging, and in some
+cases spectroscopic mass measurement are needed.
+For (ii), one or two radial velocity measurements might kinematically
+exclude cluster membership in a number of cases.
+A full assessment of the target star's age indiciators, including
+photometric rotation signatures, spectroscopic Li and H$\alpha$
+measurements, and even an isochronal analysis, would be helpful.
+
+%tODO: add plots and descriptions of other nice objects too
 
@@
 \section{Time system \& barycentric correction}
+\label{appendix:time}
+
 The time-stamps included with the calibrated TESS Full Frame Images
@@
 \section{Vetting Document Description}
+\label{appendix:vetreport}
 
@@
 the tests.
+It is one of a number of the giant planet candidates that we note may
+be in open clusters.
 

### 2019-06-24 paper/ms.tex
update plots

@@
 
-How
-ever, a homogeneous membership calculation for every known
+However, a homogeneous membership calculation for every known
 cluster is outside our scope.  So too is a homogeneous search for
@@
 
-\begin{figure*}[!ht]
+\begin{figure}[!t]
 	\gridline{\fig{astromresidual_hist.png}{0.5\textwidth}{}}
@@
 	\gridline{\fig{astromresidual_quiver.png}{0.5\textwidth}{}}
+  %\vspace{-0.8cm}
+	%\gridline{\fig{astromresidual_apertures.png}{0.5\textwidth}{}}
 	\vspace{-0.8cm}
-	\gridline{\fig{astromresidual_apertures.png}{0.5\textwidth}{}}
     \caption{
-		{\it Top.} Histogram
-		{\it Middle.} Vector
-		{\it Bottom.} Apertures
+		{\it Top.} {\bf Histogram of astrometric residual.} The $x$-axis shows 
+		the distance between the measured centroid positions of stars, 
+		compared to the predicted positions from the WCS solution.
+		{\it Bottom.} {\bf Vector plot of astrometric residual.} Each arrow is 
+		the vector from the measured to the projected star position. 
+		Directions are correct, but lengths are 50 times their true size for 
+		visualization purposes.
+        The systematic error in the top-right corner is a typical problem in 
+        wide-field astrometry.
+        The frame chosen for this plot is the photometric reference frame used 
+        for Sector 6, Camera 1, CCD 1; we automatically 
+        impose cutoffs on the median and $90^{\rm th}$ percentile of the 
+        astrometric residual in order to ensure similar levels of astrometric 
+        precision are maintained throughout the reduction.
 	}
 	\label{fig:astromresid}
-\end{figure*}
+\end{figure}
 
@@
 frame (to be described shortly) in
-Figure~\ref{fig:astrometricresidual}.
+Figure~\ref{fig:astromresid}.
 A few salient points can be made.

### 2019-06-24 paper/collect_figures.sh

@@ -14,17 +14,6 @@ pdir=../paper/
 # what our pipeline does
 cp ${fdir}trex_overview.pdf ${pdir}pipelineoverview.pdf
 
-# placeholding wcs
-fdir=../results/astrometric_residual/
-cp ${fdir}proj1510-s0006-cam3-ccd3-combinedphotref-onenight_apertures_on_frame_x_954t1094_y_954t1094.png \
-   ${pdir}astromresidual_apertures.png
-
-cp ${fdir}proj1500-s0006-cam1-ccd1-combinedphotref-onenight_spocwcs_sep_hist.png \
-   ${pdir}astromresidual_hist.png
-
-cp ${fdir}proj1500-s0006-cam1-ccd1-combinedphotref-onenight_spocwcs_quiver_meas_proj_sep.png \
-   ${pdir}astromresidual_quiver.png
-
 # rms vs mag 
 fdir=../results/paper_figures/
 cp ${fdir}rms_vs_mag.png ${pdir}rms_vs_mag.png
@@ -58,12 +47,22 @@ cp ${fdir}catalog_to_gaia_match_statistics_MWSC.png \
 cp ${fdir}catalog_to_gaia_match_statistics_Dias14.png \
    ${pdir}dias14matchstats.png
 
+# wcs
+cp ${fdir}proj1500-s0006-cam1-ccd1-combinedphotref-onenight_spocwcs_sep_hist.png \
+   ${pdir}astromresidual_hist.png
+
+cp ${fdir}proj1500-s0006-cam1-ccd1-combinedphotref-onenight_spocwcs_quiver_meas_proj_sep.png \
+   ${pdir}astromresidual_quiver.png
+
 # pdftk burst the chosen vetting pdf
 pdftk vet_hlsp_cdips_tess_ffi_gaiatwo0005541111035713815552-0007_tess_v01_llc.pdf burst output gaiatwo0005541111035713815552-0007_page%02d.pdf
 
-
-
 ##########################################
+
+# outdated, probably won't be in paper
+fdir=../results/astrometric_residual/
+cp ${fdir}proj1510-s0006-cam3-ccd3-combinedphotref-onenight_apertures_on_frame_x_954t1094_y_954t1094.png \
+   ${pdir}astromresidual_apertures.png
 
 lcdir=../results/projid1088_cam2_ccd2_lcs/center_lcs/
[…]

### 2019-06-28 paper/ms.tex
improve intro

@@
 % BEGIN NUMBERS
-\newcommand{\numberpcs}{42\ }
+\newcommand{\numberpcs}{29\ }  % 2019/06/28 unanimous gold
 \newcommand{\sVInumberlcs}{67{,}601\ }  % 2019/06/20 not allnan
@@
 stars and exoplanets; it would be interesting to statistically observe
-these changes as functions of time.  However, since most dwarf star
-properties do not appreciably change until the stars evolve off the
+these changes as functions of time.  However, since most dwarf stars
+do not appreciably change until evolving off the
 main sequence, creative approaches must be used to infer stellar ages
@@
 
-The first planets in open clusters were detected through radial
-velocity (RV) measurements of evolved stars in the Hyades
-and NGC~2423 \citep{Sato_et_al_2007,lovis_mayor_2007}.
+The first planets to be detected in open clusters were found through
+radial velocity (RV) measurements of evolved stars in the Hyades and
+NGC~2423 \citep{Sato_et_al_2007,lovis_mayor_2007}.
 Subsequent spectroscopic searches in Praesepe led to the detection of
@@
 \citep{aigrain_monitor_2007,irwin_monitordata_2007,miller_monitor_2008}.
-While these studies led to valuable measurements of stellar rotation
+While these studies led to measurements of stellar rotation
 periods \citep{hartman_rotation_2009,Irwin_NGC2516_2007} as well as
@@
 \citep{Mann_K2_25_2016}.  This inflated radius is perhaps a hint that
-the planet is contracting, or losing its atmosphere (e.g., CITE).  The
+the planet is contracting, or losing its atmosphere \citep[{\it
+e.g.},][]{Fortney_et_al_2007,Owen_Wu_2013,Fulton_et_al_2017}.  The
 super-Neptune sized K2-33b ($P\approx 5.4\,{\rm d}$), found in Upper
@@
 \citep{ciardi_k2-136_2018,livingston_three_2018,mann_ZEITVI_2018}, and
-also the two-planet system K2-264 in Praesepe
+later the two-planet system K2-264 in Praesepe
 \citep{rizzuto_zeitVIII_2018,livingston_k2-264_2019}.  There has also
@@
 brighter than $T=16$ will be observed in the full-frame images over
-the first two years of TESS observations.  The actual number will be
+the first two years of TESS observations.  The actual number may be
 larger, as cluster membership catalogs are not yet complete, even at
@@
 
-One of the major challenges in deriving precise photometry from the
+One of the major barriers to deriving precise photometry from the
 TESS images is the relatively poor angular resolution ($\approx 21''$
@@
 15^\circ$~\citep{stassun_TIC_2018,stassun_TIC8_2019}, which includes
-90\% of all star clusters\footnote{TICv8 has updated this to $10^\circ$,
+almost all star clusters\footnote{TICv8 has updated this to $10^\circ$,
 but for the first year of TESS observations, the number used when
 selecting target stars was $15^\circ$.}.  This is sensible, given that
-the large pixel size and the high stellar surface density will make
+the large pixel size and the high stellar surface density make
 aperture photometry unreliable.  However, it also means that a large
-number of stars in clusters that could yield planet candidates may go
-unprocessed by the official {\it TESS} data reduction pipeline.
-
-If one's concern is to discover and characterize benchmark systems
-with known ages,
-hunting for transiting planets in nearby stellar assocations is a path
-that seems to be working.  A number of promising targets from TESS are
-in various stages of follow-up from this approach, notably DS Tuc Ab
-(TOI 200, \citealt{benatti_dstuc_2019}, Newton+2019), as well as
-TOI-450 and TOI-451.  This is good, and these will remain benchmark
-systems because they are close and bright.  However, to do statistics,
-we need more stars -- we might also benefit from investigating the full range of cluster
-properties (densities, ages, metallicities).  This motivates the need
-to go crowded, and fainter.
+number of stars in clusters that could yield transiting planets will
+go unprocessed by the official {\it TESS} data reduction pipeline.
+
+Of course, not all young stars are in crowded fields.  TESS
+observations of a few nearby non-crowded stellar assocations have
+already begun bearing fruit, notably DS Tuc Ab (TOI 200;
+\citealt{benatti_dstuc_2019,newton_dstuc_2019}), and perhaps the
+planet candidates TOI-450 and 451.  These objects are close and
+bright, and will be benchmark systems because they are relatively easy
+to characterize.  However, statistical studies of how stellar and
+planetary properties are affected by ages require tens of thousands of
+target stars.  This motivates us to also search the more crowded, and
+fainter fields.
 
@@
 difference imaging technique because of its benefits in modelling
-complex backgrouds in crowded regions.  While we hope to
-discover at least a few giant transiting planets, a separate hope
-is that the dataset might be useful to those wishing to study the
-time evolution of stellar processes.
-
-In the following, \S~\ref{sec:starselection} describes the process of
-selecting target stars.  \S~\ref{sec:method} presents the photometric and
-image processing methods, and \S~\ref{sec:results} describes results.
-\S~\ref{sec:discussion} discusses, and \S~\ref{sec:conclusion}
-concludes.
+complex backgrouds in crowded regions.  While we hope to discover at
+least a few giant transiting planets, a separate hope is that the
+dataset might be useful to those wishing to study the time evolution
+of stellar processes.
+
+In the following, \S~\ref{sec:starselection} describes how we selected
+target stars. \S~\ref{sec:method} presents the photometric and image
+processing methods we used to produce light curves for these stars.
+The statistical properties of the \numberlcs light curves from TESS Sectors
+6 and 7 are then summarized (\S~\ref{subsec:lcstatistics}).  The
+procedure we used to identify and vet transiting planets is
+described in \S~\ref{subsec:identifying_ctois}, and the candidate
+planets are presented in \S~\ref{subsec:ctois}.
+\S~\ref{sec:discussion} discusses the additional work that is required
+to confirm or reject the planetary nature of these objects, and
+\S~\ref{sec:conclusion} summarizes our findings.
 
@@
 
-A major aim of the CDIPS project is to increase the number of
-cluster stars for which photometric time-series are
-available, to facilitate studies of exoplanetary and stellar
-processes across different times and stellar environments.
-An essential step is therefore to define a sample of
-stars that are thought to be young, or members or clusters, or both.
-
-However, a homogeneous membership calculation for every known
-cluster is outside our scope.  So too is a homogeneous search for
-young stars across the galaxy.
-Instead, we opt to collect
-and concatenate appropriate catalogs from across the literature.  
-We then use the resulting meta-catalog to identify our target stars within the 
-TESS images.
-
-In our initial stellar selection our aim is therefore completeness, not 
-accuracy.  If there has
-been a claim in the literature that a star should be considered a
-cluster member, or a young star, we would like to report a light curve for the 
-star.
-For stars that are photometrically interesting, we can perform post-hoc
-quality checks using Gaia DR2 astrometry and photometry to assess cluster 
-membership and youth.
-
-\S~\ref{subsec:oc} describes the large catalogs we used to 
-identify candidate members of open clusters.
-\S~\ref{subsec:mg} describes the smaller catalogs we used to identify 
-candidate members of moving groups, stellar associations, as well as young 
-stars identified through combined Gaia photometry and astrometry.
-\S~\ref{subsec:ocmgsummary} then reports summary statistics for the entire 
-sample of about one million target stars.
+The main aim of the CDIPS project is to increase the number of cluster
+stars for which photometric time-series are available, and thereby
+facilitate studies of exoplanetary and stellar processes across
+different times and stellar environments.  An essential step is
+therefore to define a sample of stars that are thought to be young, or
+members or clusters, or both.
+
+A homogeneous membership calculation for every known cluster is a
+rather large undertaking, and currently falls outside our scope.  So
+too is a homogeneous search for young stars across the galaxy.
+Instead, we have opted to collect and concatenate appropriate catalogs
+from across the literature.  We then use the resulting meta-catalog to
+identify our target stars within the TESS images.
+
+In our initial stellar selection our aim is completeness, not
+accuracy.  If there has been a claim in the literature that a star
+should be considered a cluster member, or a young star, we would like
+to report a light curve for the star.  For stars that are
+photometrically interesting, we can perform post-hoc quality checks
+using Gaia DR2 astrometry and photometry to assess cluster membership
+and youth.
+
+\S~\ref{subsec:oc} describes the catalogs we used to identify
+candidate members of open clusters.  \S~\ref{subsec:mg} describes the
+catalogs we used to identify candidate members of moving groups,
+stellar associations, as well as young stars identified through
+combined Gaia photometry and astrometry.  \S~\ref{subsec:ocmgsummary}
+then reports summary statistics for the entire sample of about one
+million target stars.
 
@@
 \subsection{Identifying Objects of Interest}
-\label{subsec:ctois}
+\label{subsec:identifying_ctois}
 
@@
 for the purposes of easily assigning labels to documents.
-An example of a full vetting report is described in
+An example vetting report for a planet candidate is described in
 Appendix~\ref{appendix:vetreport}.
@@
 \subsection{Objects of Interest}
+\label{subsec:ctois}
 The objects that all vetters identified as planet candidates were then
@@
 
-Lorem ipsum.
+Additional observations are needed for two major goals:
+a) cluster membership confirmation
+(age indicators, across the board);
+b) verify the planetary nature of the signals
+(seeing-limited photometry, RV mass measurement).
 
@@
 
-% \begin{figure}[t]
-% 	\begin{center}
-% 		\leavevmode
-% 		\includegraphics[width=0.49\textwidth]{f6.pdf}
-% 	\end{center}
-% 	\vspace{-0.5cm}
-% 	\caption{
-%     {\bf Further observations will be needed to confirm and understand
-%     the timing variations of WASP-4b.} Dots are as in
-%     Figure~\ref{fig:times}.  Lines are 100 random draws from the
-%     posteriors of the apsidal precession model (orange), and the
-%     orbital decay model (blue).    
-% 		\label{fig:future}
-% 	}
-% \end{figure}
+Lorem ipsum.
 

### 2019-06-28 paper/ms.tex
add words describing transit model fitting

@@
         Significance thresholds empirically defined for the transiting planet 
-        search described in \S~\ref{subsec:ctois}. Each point represents the 
+        search described in \S~\ref{subsec:identifying_ctois}. Each point represents the 
         TLS periodogram peak signal detection efficiency from one light curve.
@@
 \label{subsec:ctois}
-The objects that all vetters identified as planet candidates were then
-fit with the usual \citet{mandel_analytic_2002} model. (CITE BATMAN).
-The resulting fits are shown in Figure XXX.
-The parameters of the planet candidates are given in Table YYY, and
-are also available as cTOIs NNN.01 - MMM.01 on exofop-TESS (LINK).
+
+\begin{figure*}[t]
+	\begin{center}
+		\leavevmode
+		\includegraphics[width=0.9\textwidth]{ctoi_quilt.png}
+	\end{center}
+	\vspace{-0.2cm}
+	\caption{
+    {\bf 12 of the \numberpcs candidate transiting planets identified
+    in this work.} 
+    Models are fit as described in \S~\ref{subsec:ctois}.
+    The full set of model parameters are in Table~XXX and on
+    exofop-TESS.
+	\label{fig:ctoi_quilt}
+	}
+\end{figure*}
+
+If all vetters identified an object as a planet candidate, we then
+proceeded to fit a transit model to the data.  The procedure closely
+mirrors that used by \citet{bouma_wasp-4b_2019} to create a
+phase-folded light curve for WASP-4.
+
+First, we selected points within 5 transit durations of each transit
+midpoint, using the orbital period, transit duration, and reference
+epoch found from applying TLS to the detrended light curve.  We then
+fitted a line to the out-of-transit flux measurements around each
+transit window, and divided it out.  We then fitted a standard transit
+model using the formulae given by \citet{mandel_analytic_2002} and
+implemented by \citet[][\texttt{BATMAN}]{kreidberg_batman_2015}.  The
+free parameters were the orbital period, the reference epoch, the
+planet to star radius ratio $R_{\rm p}/R_\star$, the orbital distance
+to stellar radius ratio $a/R_\star$, and the inclination $i$.  We
+assumed circular orbits.  To fix the quadratic limb-darkening
+parameters, we collected $T_{\rm eff}$ and $\log g$ from the TIC, and
+then interpolated against the \citet{claret_limb_2017} tables.  For
+stars hotter than the maximal effective temperature of these tables
+($12,000\,{\rm K}$), we simply used the coefficients of the hottest
+star.
+
+We then sampled the posterior probability distribution using the
+\citet{goodman_ensemble_2010} algorithm, as implemented by
+\citet[][\texttt{emcee}]{foreman-mackey_emcee_2013}.  Our main goal in
+this procedure was to provide an accurate ephemeris.  To ensure that
+the reported uncertainties are valid, after performing the initial fit
+using the photometric uncertainties reported in our light curves, we
+rescaled the the uncertainty in each photometric data point to equal
+the root-mean-square deviation of each transit-model subtracted light
+curve. We then refitted each light curve.
+
+The resulting parameters are given in Table YYY, and are also
+available as cTOIs NNN.01 - MMM.01 on exofop-TESS (LINK).
+Figure~\ref{fig:ctoi_quilt} shows the phase-folded lightcurves and
+their best-fitting moels.
+
+The physical parameters quoted in Table YYY, and on exofop-TESS,
+should be considered preliminary, and could be substantially improved
+with an object-by-object analysis.  A few additional assumptions were
+required to report some of the values.  For the stellar radii, we
+assumed the $R_\star$ values and uncertainties reported in the TIC.
+There were a few cases with null uncertainties in the stellar radii --
+for these, we simply invented a relative uncertainty of 30\%, and note
+in the comments that this was done.  The uncertainties in e.g., the
+planetary radii and impact parameters were found using linear error
+propagation theory, under the idealized assumption that the covariance
+between all stellar and planetary parameters was zero.
+
+Finally, the determine the names of the objects -- that is whether
+they were already TOIs, or cTOIs -- we cross-referenced based on a
+combination of the TIC identifier, spatial position, and the ephemeris
+of each object.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Discussion}
+\label{sec:discussion}
+
+Additional observations are needed for two major goals:
+a) cluster membership confirmation
+(age indicators, across the board);
+b) verify the planetary nature of the signals
+(seeing-limited photometry, RV mass measurement).
 
@@
 measurements, and even an isochronal analysis, would be helpful.
-
-%tODO: add plots and descriptions of other nice objects too
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Discussion}
-\label{sec:discussion}
-
-Additional observations are needed for two major goals:
-a) cluster membership confirmation
-(age indicators, across the board);
-b) verify the planetary nature of the signals
-(seeing-limited photometry, RV mass measurement).
 

### 2019-06-28 drivers/fit_models_to_gold.py
fit transit: edge case of nan TIC

@@ -25,6 +25,8 @@ from astroquery.mast import Catalogs
 from astroquery.vizier import Vizier
 
 from numpy.polynomial.legendre import Legendre
+from scipy import optimize
+from scipy.interpolate import interp1d
 
 from astropy import units as u
 from astropy.coordinates import SkyCoord
@@ -276,6 +278,39 @@ def _fit_given_cdips_lcpath(tfa_sr_path, lcpath, outpath, mdf, sourceid,
         logg_err = seltab['e_logg']
         rstar = seltab['rad']
         rstar_err = seltab['e_rad']
+
+        if type(teff)==np.ma.core.MaskedConstant:
+            print('WRN! TIC teff nan. why? trying gaia value')
+            teff = hdr['teff_val']
+            teff_err = 100
+
+        if type(rstar)==np.ma.core.MaskedConstant:
+            print('WRN! TIC rstar nan. why? trying gaia value')
+            rstar = hdr['radius_val']
+            rstar_err = 0.3*rstar
+            # get mass given rstar, so that you can get logg
+            mamadf = pd.read_csv('../data/Mamajek_Rstar_Mstar_Teff_SpT.txt',
+                                 delim_whitespace=True)
+            if rstar != 'NaN':
+                mamarstar, mamamstar = nparr(mamadf['Rsun'])[::-1], nparr(mamadf['Msun'])[::-1]
+                isbad = np.insert(np.diff(mamamstar) <= 0, False, 0)
+                fn_mass_to_rstar = interp1d(mamamstar[~isbad], mamarstar[~isbad],
+                                            kind='quadratic', bounds_error=False,
+                                            fill_value='extrapolate')
+                radiusval = rstar
+                fn = lambda mass: fn_mass_to_rstar(mass) - radiusval
+                mass_guess = mamamstar[np.argmin(np.abs(mamarstar - radiusval))]
+                try:
+                    mass_val = optimize.newton(fn, mass_guess)
+                except RuntimeError:
+                    mass_val = mass_guess
+                mstar = mass_val
+            else:
+                raise NotImplementedError('need rstar somehow')
+            _Mstar = mstar*u.Msun
+            _Rstar = rstar*u.Rsun
+            logg = np.log10((const.G * _Mstar / _Rstar**2).cgs.value)
+            logg_err = 0.3*logg
 
         ticid = int(hdr['TICID'])
 

### 2019-06-28 paper/ms.tex
update text for above

@@
 for these, we simply invented a relative uncertainty of 30\%, and note
-in the comments that this was done.  The uncertainties in e.g., the
-planetary radii and impact parameters were found using linear error
-propagation theory, under the idealized assumption that the covariance
-between all stellar and planetary parameters was zero.
-
-Finally, the determine the names of the objects -- that is whether
-they were already TOIs, or cTOIs -- we cross-referenced based on a
-combination of the TIC identifier, spatial position, and the ephemeris
-of each object.
+in the comments that this was done.  There were also a few cases for
+which the TIC stellar temperatures and/or radii were not available,
+but the Gaia values were.  In these cases, we used the Gaia $T_{\rm
+eff}$ and $R_\star$ values, and used the stellar mass interpolated
+from the \citet{pecaut_intrinsic_2013} table (assuming the star is a
+dwarf) to estimate $\log g$.  The uncertainties in e.g., the planetary
+radii and impact parameters were found using linear error propagation
+theory, under the idealized assumption that the covariance between all
+stellar and planetary parameters was zero.
+
+Finally, the determine the names of the objects -- and whether they
+had already been identified as TOIs or cTOIs -- we cross-referenced
+based on a combination of the TIC identifier, spatial position, and
+the ephemeris of each object.
 

### 2019-07-01 cdips/catalogbuild/construct_unique_cluster_name_column.py
unique cluster name column now working

@@ -2,8 +2,6 @@
 we need some idea of the cluster names.
 """
 
-#TODO write ... and generalize to match between pg 5 and this function...
-
 from glob import glob
 import os, textwrap, re, requests, time
 import numpy as np, pandas as pd, matplotlib.pyplot as plt
@@ -23,11 +21,10 @@ from astropy.io.votable import from_table, writeto, parse
 
 clusterdir = "/home/lbouma/proj/cdips/data/cluster_data"
 
-DEBUG = False
-
 def main(cdips_cat_vnum=0.3):
 
-    # cluster;dec;dist;ext_catalog_name;parallax;phot_bp_mean_mag;phot_g_mean_mag;phot_rp_mean_mag;pmdec;pmra;ra;reference;source_id
+    # cluster;dec;dist;ext_catalog_name;parallax;phot_bp_mean_mag;
+    # phot_g_mean_mag;phot_rp_mean_mag;pmdec;pmra;ra;reference;source_id
     cdips_df = ccl.get_cdips_catalog(ver=cdips_cat_vnum)
 
     # Name,Type,MWSC,ra,dec, etc.
@@ -39,20 +36,19 @@ def main(cdips_cat_vnum=0.3):
     decs = nparr(cdips_df['dec'])
     referencearr = nparr(cdips_df['reference'])
 
-    if DEBUG:
-        # test on all unique non-nan cluster names.
-        inds = ~pd.isnull(clusterarr)
-        sourceid = sourceid[inds]
-        clusterarr = clusterarr[inds]
-        ras = ras[inds]
-        decs = decs[inds]
-        referencearr = referencearr[inds]
-        uarr, inds = np.unique(clusterarr, return_index=True)
-        sourceid = sourceid[inds]
-        clusterarr = clusterarr[inds]
-        ras = ras[inds]
-        decs = decs[inds]
-        referencearr = referencearr[inds]
+    # first, generate names for all unique non-nan cluster names.
+    inds = ~pd.isnull(clusterarr)
+    sourceid = sourceid[inds]
+    clusterarr = clusterarr[inds]
+    ras = ras[inds]
+    decs = decs[inds]
+    referencearr = referencearr[inds]
+    uarr, inds = np.unique(clusterarr, return_index=True)
+    sourceid = sourceid[inds]
+    clusterarr = clusterarr[inds]
+    ras = ras[inds]
+    decs = decs[inds]
[…]

### 2019-07-01 paper/ms.tex
paper: add description of name conventions

@@
 these relatively bright magnitudes \citep[{\it
-e.g.},][]{cantat-gaudin_gaia_2018,cantat-gaudin_newOCs_2019}.
+e.g.},][]{roser_nine_RSG_2016,cantat-gaudin_gaia_2018,cantat-gaudin_newOCs_2019}.
 % Our target list currently sits at $\approx 1.0\times10^6$ candidate
@@
 (17.3\%), \citealt{cantat-gaudin_gaia_2018} (16.7\%), and \citealt{zari_3d_2018}
-(11.1\%).
+(11.1\%). %FIXME how many in PMS vs UMS?
 Stars reported in multiple catalogs have all available reference information
 concatenated.
+
+To assign unique cluster names, we adopted the name matched against
+\citet{Kharchenko_et_al_2013} whenever possible, following the
+procedure described in Appendix~\ref{appendix:uniquenames}.  For
+moving groups not identified in \citet{Kharchenko_et_al_2013}, we
+adopted the constellation-based naming convention from
+\citet{gagne_banyan_XI_2018}.  Otherwise, we used the name reported by
+the original catalog.  This process reduced 16,425 name permutations
+down to 3,216 unique cluster names.  Though we have made every effort
+to avoid duplicates, a small number may remain in this column, so we
+advise inspection of the \texttt{cluster} and \texttt{reference}
+columns rather than the \texttt{unique_cluster_name} column when
+analyzing individual objects of interest.  Nonetheless, 87.7\% of the
+$\sim$million unique target stars are matched to clusters within
+\citet{Kharchenko_et_al_2013}, and 88.8\% are assigned a cluster name.
+The remainder are mostly the young stars from \citet{zari_3d_2018}.
+
 The resulting CDIPS target star list is given in Table~N.
@@
     Known asterisms are also omitted at this point
-    \citep[{\it e.g.},][]{sulentic_revised_1973,kos_galah_2018}.
+    \citep[{\it e.g.},][]{sulentic_revised_1973,baumgardt_asterisms_1998,kos_galah_2018}.
     %
@@
 
+\section{Assigning unique names to each cluster}
+\label{appendix:uniquenames}
+
+In assigning a single unique cluster name to each star, we matched
+against the \citet{Kharchenko_et_al_2013} name whenever possible,
+since this was the largest available catalog, and it also included
+homogeneous age determinations for many of the clusters.
+To find the matching name, in order of precedence we
+\begin{enumerate}[(i)]
+  \item checked for direct string matches from
+    \citet{Kharchenko_et_al_2013} clusters with determined parameters;
+  \item checked whether the SIMBAD online name resolving service had
+    any direct string matches against \citet{Kharchenko_et_al_2013}
+    clusters with determined parameters;
+  \item checked for string matches in the full
+    \citet{Kharchenko_et_al_2013} index (including clusters without
+    determined parameters);
+  \item searched for spatial matches between each star and cluster
+    centers from \citet{Kharchenko_et_al_2013} within 10 arcminutes.
+    In cases with multiple cluster matches, we ignored candidate
+    matches to avoid assigning incorrect names;
+  \item checked the WEBDA double name
+    list\footnote{\url{https://webda.physics.muni.cz/double_names.html}},
+    and repeated (i)-(iv).
+\end{enumerate}
+
+A few edge-cases, including for instance sub-clusters within larger
+star-forming complexes like in Sco-Cen or Collinder~33, were 
+manually resolved to the extent feasible \citep[][give
+detailed pictures of the complex morphologies that frequently arise in
+very young star-forming
+regions]{rizzuto_multidimensional_2011,saurin_isolating_2015}.
+
+The procedure described above failed to yield matches for a few of the
+infrared clusters identified by \citet{majaess_discovering_2013} and
+included in the \citet{dias_proper_2014} catalog.
+For these cases, we used the name given by \citet{dias_proper_2014}.
+
+The Hyades and a number of other nearby moving groups were also
+missed, since they were not in the \citet{Kharchenko_et_al_2013}
+catalog.  For moving groups not identified in
+\citet{Kharchenko_et_al_2013}, we adopted the constellation-based
+naming convention from \citet{gagne_banyan_XI_2018}.
+
+Finally, the procedure enumerated above did not yield matches for
+recently discovered clusters, such as the ``RSG'' clusters found by
+\citet{roser_nine_RSG_2016} and the ``Gulliver'' clusters from
+\citet{cantat-gaudin_gaia_2018}.  In these cases, we used the names
+given by the original authors.
+
 \section{Vetting Document Description}

### 2019-07-01 paper/ms.tex
update paper

@@
 procedure described in Appendix~\ref{appendix:uniquenames}.  For
-moving groups not identified in \citet{Kharchenko_et_al_2013}, we
-adopted the constellation-based naming convention from
+moving groups not identified in \citet{Kharchenko_et_al_2013}, we used
+the constellation-based naming convention from
 \citet{gagne_banyan_XI_2018}.  Otherwise, we used the name reported by
-the original catalog.  This process reduced 16,425 name permutations
-down to 3,216 unique cluster names.  Though we have made every effort
-to avoid duplicates, a small number may remain in this column, so we
-advise inspection of the \texttt{cluster} and \texttt{reference}
-columns rather than the \texttt{unique_cluster_name} column when
-analyzing individual objects of interest.  Nonetheless, 87.7\% of the
-$\sim$million unique target stars are matched to clusters within
-\citet{Kharchenko_et_al_2013}, and 88.8\% are assigned a cluster name.
-The remainder are mostly the young stars from \citet{zari_3d_2018}.
+the original catalog claiming membership.  This process reduced 16,425
+name permutations down to 3,216 unique cluster names.  Though we have
+made every effort to avoid duplicates, a small number may remain, so we
+advise inspection of the \texttt{cluster} column
+as well as the references given in the
+\texttt{reference} column rather than using the
+\texttt{unique\_cluster\_name} column to analyze individual objects
+of interest.  Nonetheless, 87.7\% of the $\sim$million unique target
+stars are matched to clusters within \citet{Kharchenko_et_al_2013},
+and 88.8\% are assigned a cluster name.  The remainder are mostly the
+young stars from \citet{zari_3d_2018}.
 
@@
 		\leavevmode
-		\includegraphics[width=0.9\textwidth]{ctoi_quilt.png}
+		\includegraphics[width=0.9\textwidth]{tlsresult_sector6.png}%{ctoi_quilt.png}
 	\end{center}
@@
 To find the matching name, in order of precedence we
-\begin{enumerate}[(i)]
-  \item checked for direct string matches from
+\begin{enumerate}
+  \item Checked for direct string matches from
     \citet{Kharchenko_et_al_2013} clusters with determined parameters;
-  \item checked whether the SIMBAD online name resolving service had
+  \item Checked whether the SIMBAD online name resolving service \citep{wenger_simbad_2000} had
     any direct string matches against \citet{Kharchenko_et_al_2013}
     clusters with determined parameters;
-  \item checked for string matches in the full
+  \item Checked for string matches in the full
     \citet{Kharchenko_et_al_2013} index (including clusters without
     determined parameters);
-  \item searched for spatial matches between each star and cluster
+  \item Searched for spatial matches between each star and cluster
     centers from \citet{Kharchenko_et_al_2013} within 10 arcminutes.
@@
     matches to avoid assigning incorrect names;
-  \item checked the WEBDA double name
+  \item Checked the WEBDA double name
     list\footnote{\url{https://webda.physics.muni.cz/double_names.html}},
-    and repeated (i)-(iv).
+    and repeated Steps 1-4 with any matches.
 \end{enumerate}
 
-A few edge-cases, including for instance sub-clusters within larger
+A few edge-cases, including for instance sub-clusters  larger
 star-forming complexes like in Sco-Cen or Collinder~33, were 
-manually resolved to the extent feasible \citep[][give
+manually resolved to the extent feasible (\citealt{rizzuto_multidimensional_2011}
+and \citealt{saurin_isolating_2015} give
 detailed pictures of the complex morphologies that frequently arise in
-very young star-forming
-regions]{rizzuto_multidimensional_2011,saurin_isolating_2015}.
+young star-forming regions).
 

### 2019-07-01 paper/ms.tex
add age figure to paper

@@
 		\leavevmode
-		\includegraphics[width=0.45\textwidth]{target_star_cumulative_counts.png}
+    %\includegraphics[width=0.45\textwidth]{target_star_cumulative_counts.png}
+    \gridline{\fig{target_star_cumulative_counts.png}{0.45\textwidth}{}}
+    \vspace{-0.8cm}
+    \gridline{\fig{target_star_hist_logt.png}{0.45\textwidth}{}}
 	\end{center}
-	\vspace{-0.2cm}
+	\vspace{-0.8cm}
 	\caption{
-    {\bf Cumulative number of target stars as
-    a function of Gaia $Rp$-band magnitude.}  The selected stars are
+    {\it Top.} Cumulative number of target stars as
+    a function of Gaia $Rp$-band magnitude.  The selected stars are
     either candidate members of clusters, or else have other youth
@@
     stars with $G_{\rm Rp} < 16$.
+    {\it Bottom.} Histogram of target star ages, for the subset of
+    stars with ages matched against \citet{Kharchenko_et_al_2013}.
 	\label{fig:cdips_targets}
@@
 young stars from \citet{zari_3d_2018}.
+Ages and their uncertainties are then merged against the 
+parameters reported by \citet{Kharchenko_et_al_2013}.
 
 The resulting CDIPS target star list is given in Table~N.
-The distribution of target star brightnesses is shown in
-Figure~\ref{fig:cdips_targets}.
+The cumulative distribution of target star brightnesses, as well as a
+histogram of the ages, is shown in Figure~\ref{fig:cdips_targets}.
+Relative to field stars, our target star sample is young, with a
+typical age of 100$\,$Myr.
 

### 2019-07-01 paper/collect_figures.sh

@@ -40,6 +40,9 @@ cp ${fdir}pm_scat_close_subset.png ${pdir}pm_scat_close_subset.png
 cp ${fdir}target_star_cumulative_counts.png \
    ${pdir}target_star_cumulative_counts.png
 
+cp ${fdir}target_star_hist_logt.png \
+   ${pdir}target_star_hist_logt.png
+
 # catalog matching statistics
 cp ${fdir}catalog_to_gaia_match_statistics_MWSC.png \
    ${pdir}mwscmatchstats.png

### 2019-07-01 drivers/paper_plot_all_figures.py
update figs

@@ -35,9 +35,8 @@ def main():
 
     sectors = [6,7]
 
-    # fig N: histogram of CDIPS target star age.
-    plot_target_star_hist_logt(OC_MG_CAT_ver=0.3, overwrite=1)
-    assert 0
+    # fig N: histogram of ages of LC stars 
+    plot_hist_logt(sectors, overwrite=1)
 
     # fig N: wcs quality verification
     plot_wcs_verification(overwrite=1)
@@ -48,26 +47,26 @@ def main():
     # fig N: catalog_to_gaia_match_statistics
     plot_catalog_to_gaia_match_statistics(overwrite=0)
 
+    # fig N: histogram of CDIPS target star age.
+    plot_target_star_hist_logt(OC_MG_CAT_ver=0.3, overwrite=1)
+
     # fig N: RMS vs catalog T mag
     plot_rms_vs_mag(sectors, overwrite=0)
 
     # fig N: histogram (or CDF) of stellar magnitude (T mag)
-    plot_cdf_T_mag(sectors, overwrite=0)
-
-    # fig N: histogram of ages of LC stars 
-    plot_hist_logt(sectors, overwrite=1)
+    plot_cdf_T_mag(sectors, overwrite=1)
 
     # fig N: HRD for CDIPS stars.
-    plot_hrd_scat(sectors, overwrite=0, close_subset=1)
-    plot_hrd_scat(sectors, overwrite=0, close_subset=0)
+    plot_hrd_scat(sectors, overwrite=1, close_subset=1)
+    plot_hrd_scat(sectors, overwrite=1, close_subset=0)
 
     # fig N: pmRA and pmDEC scatter for CDIPS stars.
-    plot_pm_scat(sectors, overwrite=0, close_subset=1)
-    plot_pm_scat(sectors, overwrite=0, close_subset=0)
+    plot_pm_scat(sectors, overwrite=1, close_subset=1)
+    plot_pm_scat(sectors, overwrite=1, close_subset=0)
 
     # fig N: positions of field and cluster stars (currently all cams)
-    plot_cluster_and_field_star_scatter(sectors=sectors, overwrite=1)
-    plot_cluster_and_field_star_scatter(sectors=[6], overwrite=1, cams=[1],
+    plot_cluster_and_field_star_scatter(sectors=sectors, overwrite=0)
[…]

### 2019-07-01 paper/ms.tex
update paper

@@
 \newcommand{\numberlcs}{159{,}337\ } % 2019/06/20 sum
-\newcommand{\numberclusters}{XXX\ }
+\newcommand{\numberclusters}{596\ } % 2019/07/01 paper_plot_all_figures.py
 
@@
 \title{
-  The Cluster Difference Imaging Photometric Survey (CDIPS).  I.
   Light Curves \& Planet Candidates in Open Clusters from TESS Sectors 6 \& 7
@@
   % Aims
-  The CDIPS project is processing the TESS
-  full-frame images and making light curves of stars that could be
-  members of stellar associations, moving groups, or open clusters.
+  As part of the Cluster Difference Imaging Photometric Survey
+  (CDIPS), we have been processing the TESS full-frame images and
+  making light curves of stars that could be members of stellar
+  associations, moving groups, or open clusters.
   %
@@
   techniques we used to create the light curves, which
-  have noise properties in agreement with theoretical expectations.
+  have noise properties that agree with theoretical expectations.
   % Results
@@
   survived, and emphasize the additional spectroscopic, photometric,
-  and imaging observations that are needed to verify that these
-  candidates are in fact planets.
+  and imaging observations that are needed to verify (i) that these
+  candidates are planets and (ii) that the host stars are cluster members.
   %
@@
 The Kharchenko catalog also has a more lop-sided distribution of true
-{\it vs.} predicted $G$-band magnitudes.
+{\it vs.}$\,$predicted $G$-band magnitudes.
 
@@
 
-For the Gagne et al{.} catalogs, we searched the Gaia-DR2 archive for
-sources within 10 arcseconds of the listed positions.  If Gagne et
+For the Gagn\'e et al{.} catalogs, we searched the Gaia-DR2 archive for
+sources within 10 arcseconds of the listed positions.  If Gagn\'e et
 al{.} gave a proper motion, we required that the sign of each the Gaia
-proper motion components match that of the Gagne values (the stated
+proper motion components match that of the Gagn\'e values (the stated
 proper motion uncertainties seemed to have been underestimated).  We
 also imposed a $G<18$ cut on any putative matches.  Of 3012 moving
-group members collected from the three combined Gagne et al{.}
+group members collected from the three combined Gagn\'e et al{.}
 catalogs, we found 2702 matches.
@@
 the Hyades, and 32$\,$Ori respectively.  Applying the same procedure as
-for the Gagne catalogs gave 187, 684, and 119 best-neighbors
+for the Gagn\'e catalogs gave 187, 684, and 119 best-neighbors
 respectively, compared to 205, 724, and 141 initially reported
@@
 To assign unique cluster names, we adopted the name matched against
-\citet{Kharchenko_et_al_2013} whenever possible, following the
-procedure described in Appendix~\ref{appendix:uniquenames}.  For
-moving groups not identified in \citet{Kharchenko_et_al_2013}, we used
+\citet{Kharchenko_et_al_2013} whenever possible.
+Appendix~\ref{appendix:uniquenames} describes  how this was done in detail.
+For moving groups not identified in \citet{Kharchenko_et_al_2013}, we used
 the constellation-based naming convention from
@@
 steps using stand-alone programs.
-Our overall method is in the spirit of the reduction approaches described
+Our overall method is in the spirit of the reduction approaches developed
 by \citet{Pal_2009}, \citet{huang_high-precision_2015}, \citet{soares-furtado_image_2017} and
@@
 astrometric verification, and coarse simple aperture
-photometry (\S~\ref{subsec:preparation}).  Using the shape values from
-the initial astrometry, we select an astrometric reference frame to
+photometry of bright stars (\S~\ref{subsec:preparation}).  Using the metadata
+collected from these initial steps, we select an astrometric reference frame to
 which we transform all of the calibrated images.  We construct a
-photometric reference by stacking a collection of frames,
-convolve the transformed frames to this photometric reference, and
-subtract (\S~\ref{subsec:imagesubtraction}).  We perform aperture
+photometric reference by stacking a subset of these transformed frames, after
+having convolved the frames to match the stellar profiles of an intermediate
+reference frame. Finally, we
+subtract each target frame from the photometric reference (\S~\ref{subsec:imagesubtraction}).
+We perform aperture
 photometry on the subtracted images using positions projected onto the
-frame from Gaia DR2.  
+frame from the Gaia DR2 source catalog.  
 We detrend the resulting light curves
@@
 where the corrections required by the SIP coefficients are largest.
-The final sub-panel of Figure~\ref{fig:astrometricresidual} is a
-sanity check on the location of the projected positions, and also
-gives some context for our chosen aperture radii of 1, 1.5, and 2.25
-pixels.
+%The final sub-panel of Figure~\ref{fig:astrometricresidual} is a
+%sanity check on the location of the projected positions, and also
+%gives some context for our chosen aperture radii of 1, 1.5, and 2.25
+%pixels.
 

### 2019-07-02 paper/ms.tex
update paper

@@
 \newcommand{\numberclusters}{596\ } % 2019/07/01 paper_plot_all_figures.py
+\newcommand{\pctoflcswithage}{77} %  2019/07/02 from hist_logt.png
 
@@
   In this study, we made \numberlcs light curves of candidate young
-  stars in \numberclusters clusters.
+  stars, across \numberclusters distinct clusters.
   Each light curve represents between 20 and 25 days of observations
@@
   survived, and emphasize the additional spectroscopic, photometric,
-  and imaging observations that are needed to verify (i) that these
-  candidates are planets and (ii) that the host stars are cluster members.
+  and imaging observations that are needed to verify (i) whether these
+  candidates are planets and (ii) whether the host stars are cluster members.
   %
-  We also comment on the possible use of the light curve sample for
+  We also comment on the possible utility of the light curve sample for
   studies of stellar rotation evolution, and binary eccentricity
@@
     \gridline{\fig{tlsresult_sector7.png}{0.45\textwidth}{}}
+    \vspace{-0.8cm}
     \caption{
@@
 		\leavevmode
-		\includegraphics[width=0.9\textwidth]{tlsresult_sector6.png}%{ctoi_quilt.png}
+		\includegraphics[width=0.9\textwidth]{quilt_PCs.png}
 	\end{center}
@@
 	\caption{
-    {\bf 12 of the \numberpcs candidate transiting planets identified
-    in this work.} 
-    Models are fit as described in \S~\ref{subsec:ctois}.
-    The full set of model parameters are in Table~XXX and on
-    exofop-TESS.
+    {\bf 6 of the \numberpcs candidate transiting planets identified
+    in this studies.}
+	Black points are detrended flux measurements, phased to the
+	best-fit orbital period, indicated in the lower right of each panel.
+	Best-fit models are fit as described in \S~\ref{subsec:ctois}, and
+	shown with blue lines.
+	For display purpses, $\pm 4$ transit durations of the
+	light curves are displayed.
+	The vetting reports for these objects are available at XXX.	%FIXME
+	The Gaia source identifiers are
+	a): 5605128927705695232, 
+	b): 3125263468681400320, 
+	c): 5510676828723793920, 
+	d): 3007171311355035136, 
+	e): 5617126180115568256, 
+	f): 3220266049321724416.   
 	\label{fig:ctoi_quilt}
@@
 
-Finally, the determine the names of the objects -- and whether they
+Finally, to determine the names of the objects -- and whether they
 had already been identified as TOIs or cTOIs -- we cross-referenced
@@
 	\caption{
-		{\bf Page 3: Transit diagnostics.} The plots show the maximally-detrended
-		light curve (top); the phase-folded light curve centered on the primary transit
-		(middle left); the phase-folded light curve centered on the secondary eclipse
-		(middle right); the odd-numbered transits (lower left); and the
-		even-numbered transits (lower right).
-		The stellar parameters ($T_{\rm eff}, R_\star$) are taken from Gaia-DR2 
-		when available.
-		The first eight lines of text are parameters determined 
-		from the best-fitting TLS model.
-		The one exception is the planet radius, which uses the stellar radius
-		as noted above.
-		The ``flux contamination'' (\texttt{TICCONT}) from neighboring stars
-		is {\it never} taken into account, because transit depth dilution does
-		not affect image subtraction analyses in the same manner as 
-		aperture-photometry reductions.
-		To estimate the transit to occulation
-		depth ratio,
-		the phase-folded light curve is also coarsely fit via maximum likelihood
-		by a sum of two gaussians.
-		``AstExc'' refers to the Gaia-DR2 astrometric excess, which can indicate
-		hints of astrometric binarity in the system.
+    {\bf Page 3: Transit diagnostics.} The plots show the
+    maximally-detrended light curve (top); the phase-folded light
+    curve centered over $\pm3$ transit durations of the primary
+    transit (middle left); the secondary eclipse (middle right); the
+    odd-numbered transits (lower left); and the even-numbered transits
+    (lower right).
+    The stellar parameters ($T_{\rm eff}, R_\star$) are taken from
+    Gaia-DR2 Apsis pipeline results when available
+    \citep{andrae_apsis_2018}.
+    The first eight lines of text are parameters determined from the
+    best-fitting TLS model.
+    The one exception is the planet radius, which uses the stellar
+    radius as noted above.
+    The ``flux contamination'' (\texttt{TICCONT}) from neighboring
+    stars is {\it never} taken into account, because transit depth
+    dilution does not affect image subtraction analyses in the same
+    manner as aperture-photometry reductions.
+    To estimate the transit to occulation depth ratio, the
+    phase-folded light curve is also coarsely fit via maximum
+    likelihood by a sum of two gaussians.
+    ``AstExc'' refers to the Gaia-DR2 astrometric excess, which can
+    indicate hints of astrometric binarity in the system.
     ``$R_\star + M_\star \rightarrow T_{b0}$'' gives the duration of a
-		zero-eccentricity central transit based on the Gaia-DR2 stellar radius,
-		and a stellar mass interpolated from the \citet{pecaut_intrinsic_2013} table,
-		under the assumption that the star is a dwarf.%\footnote{\url{http://www.pas.rochester.edu/~emamajek/EEM_dwarf_UBVIJHK_colors_Teff.txt}}.
+    zero-eccentricity central transit based on the Gaia-DR2 stellar
+    radius, and a stellar mass interpolated from the
+    \citet{pecaut_intrinsic_2013} table, under the assumption that the
+    star is a dwarf.
+    %\footnote{\url{http://www.pas.rochester.edu/~emamajek/EEM_dwarf_UBVIJHK_colors_Teff.txt}}.
 		\label{fig:pg3}

### 2019-07-02 paper/collect_figures.sh

@@ -18,6 +18,9 @@ cp ${fdir}trex_overview.pdf ${pdir}pipelineoverview.pdf
 fdir=../results/paper_figures/
 cp ${fdir}rms_vs_mag.png ${pdir}rms_vs_mag.png
 
+# quilt of PCs
+cp ${fdir}quilt_PCs.png ${pdir}quilt_PCs.png
+
 # positions of lightcurves
 cp ${fdir}sector6_cam[1]_ccd[1-2-3-4]cluster_field_star_positions.png \
    ${pdir}sector6_cam[1]_ccd[1-2-3-4]cluster_field_star_positions.png

### 2019-07-02 drivers/paper_plot_all_figures.py
position plot: add galactic coords

@@ -36,10 +36,6 @@ def main():
 
     sectors = [6,7]
 
-    plot_quilt_PCs(overwrite=1)
-    assert 0
-
-
     # fig N: T magnitue CDF for all CDIPS target stars.
     plot_target_star_cumulative_counts(OC_MG_CAT_ver=0.3, overwrite=0)
 
@@ -69,7 +65,12 @@ def main():
     plot_pm_scat(sectors, overwrite=1, close_subset=1)
     plot_pm_scat(sectors, overwrite=1, close_subset=0)
 
+    # fig N: 3x2 quilty of phased PC
+    plot_quilt_PCs(overwrite=1)
+
     # fig N: positions of field and cluster LC stars (currently all cams)
+    plot_cluster_and_field_star_scatter(sectors=sectors, overwrite=0,
+                                        galacticcoords=True)
     plot_cluster_and_field_star_scatter(sectors=sectors, overwrite=0)
     plot_cluster_and_field_star_scatter(sectors=[6], overwrite=0, cams=[1],
                                         ccds=[1,2,3,4])
@@ -107,7 +108,7 @@ def plot_quilt_PCs(overwrite=1):
 
     np.random.seed(42)
     spaths = np.random.choice(fpaths, size=3*2, replace=False)
-    ylims = [
+    ylims = [ # for seed 42
         (0.957, 1.015),
         (0.97, 1.017),
         (0.995, 1.003),
@@ -682,7 +683,8 @@ def plot_pm_scat(sectors, overwrite=0, close_subset=0):
 
 
 def plot_cluster_and_field_star_scatter(sectors=None, overwrite=0,
-                                        cams=[1,2,3,4], ccds=[1,2,3,4]):
+                                        cams=[1,2,3,4], ccds=[1,2,3,4],
+                                        galacticcoords=False):
     """
     note: being kept separate from other stats collection step b/c here you
     need all LCs + CDIPS LCs, rather than only CDIPS LCs
@@ -692,6 +694,8 @@ def plot_cluster_and_field_star_scatter(sectors=None, overwrite=0,
     N_max = 100000
 
     prestr = 'sector{}_'.format(sectors[0]) if len(sectors)==1 else ''
+    if galacticcoords:
+        prestr = prestr + 'galacticcoords_'
 
     if cams==[1,2,3,4] and ccds==[1,2,3,4]:
[…]

### 2019-07-02 paper/ms.tex
update paper

@@
 
-\begin{figure}[!t]
+\begin{figure*}[!t]
 	%\gridline{
@@
 		\leavevmode
-		\includegraphics[width=0.47\textwidth]{cluster_field_star_positions.png}
+		\includegraphics[width=0.97\textwidth]{galacticcoords_cluster_field_star_positions.png}
 	\end{center}
@@
 	\caption{
-		{\bf Celestial positions of light curves from Sectors 6
-			and 7.}  Black: $G_{\rm Rp}<13$ field stars.  Blue: $G_{\rm
-			Rp}<16$ target stars.
-		\label{fig:lcradec}
-	}
-\end{figure}
+		{\bf Positions of light curves from Sectors 6
+			and 7 in galactic coordinates.}
+		    Black: $G_{\rm Rp}<13$ field stars.  Blue: $G_{\rm Rp}<16$ target stars.
+		\label{fig:lcgalactic}
+	}
+\end{figure*}
 
@@
 	\caption{
-		{\bf  Zoom of Sector 6, Camera 1 from Figure~\ref{fig:lcradec}.}
+		{\bf  Zoom and coordinate transformation
+			of Sector 6, Camera 1 from Figure~\ref{fig:lcgalactic}.}
 		The most populated cluster is XXX, primarily due to candidate
@@
 The on-sky locations of the light curves from Sectors 6 and 7
-are shown in Figure~\ref{fig:lcradec}.
+are shown in Figure~\ref{fig:lcgalactic}.
 Black stars are the field stars for which we performed photometry,
@@
 
-A zoom-in of Figure~\ref{fig:lcradec} is shown in Figure~\ref{fig:lcradeczoom}
+A zoom-in of Figure~\ref{fig:lcgalactic} is shown in Figure~\ref{fig:lcradeczoom}
 for the Camera 1, Sector 6 field. The effects of galactic-latitude
@@
 	\caption{
-    {\bf 6 of the \numberpcs candidate transiting planets identified
-    in this studies.}
+    {\bf Six of the \numberpcs candidate transiting planets identified
+    from this work.}
     Black points are detrended flux measurements, phased to the
@@
     shown with blue lines.
-	For display purpses, $\pm 4$ transit durations of the
-	light curves are displayed.
+    For display purpses, a window of $\pm 4$ transit durations from the
+    mid-point is displayed.
     The vetting reports for these objects are available at XXX.	%FIXME
+    % TODO: include age? T mag?
     The Gaia source identifiers are
@@
 but the Gaia values were.  In these cases, we used the Gaia $T_{\rm
-eff}$ and $R_\star$ values, and used the stellar mass interpolated
-from the \citet{pecaut_intrinsic_2013} table (assuming the star is a
-dwarf) to estimate $\log g$.  The uncertainties in e.g., the planetary
-radii and impact parameters were found using linear error propagation
-theory, under the idealized assumption that the covariance between all
-stellar and planetary parameters was zero.
-
-Finally, to determine the names of the objects -- and whether they
-had already been identified as TOIs or cTOIs -- we cross-referenced
-based on a combination of the TIC identifier, spatial position, and
-the ephemeris of each object.
+eff}$ and $R_\star$ values \citep{andrae_apsis_2018}, and a stellar
+mass interpolated from the \citet{pecaut_intrinsic_2013} table
+(assuming the star is a dwarf) to estimate $\log g$.  The
+uncertainties in e.g., the planetary radii and impact parameters were
+found using linear error propagation theory, under the idealized
+assumption that the covariance between all stellar and planetary
+parameters was zero.
+
+Finally, to assign the names of the planet candidates -- and determine
+whether they had already been identified as TOIs or cTOIs -- we used
+lists downloaded from the \url{tev.mit.edu} alert site for TOIs, and
+from \url{exofop.ipac.caltech.edu/tess} for cTOIs.  We
+cross-referenced based on a combination of the TIC identifier, spatial
+position, and the ephemeris of each object.
 

### 2019-07-02 paper/collect_figures.sh

@@ -26,7 +26,12 @@ cp ${fdir}sector6_cam[1]_ccd[1-2-3-4]cluster_field_star_positions.png \
    ${pdir}sector6_cam[1]_ccd[1-2-3-4]cluster_field_star_positions.png
 
 # positions of lightcurves
-cp ${fdir}cluster_field_star_positions.png ${pdir}cluster_field_star_positions.png
+cp ${fdir}cluster_field_star_positions.png \
+   ${pdir}cluster_field_star_positions.png
+
+# positions of lightcurves
+cp ${fdir}galacticcoords_cluster_field_star_positions.png \
+   ${pdir}galacticcoords_cluster_field_star_positions.png
 
 # CDF of T mags of LCs
 cp ${fdir}cdf_T_mag.png ${pdir}cdf_T_mag.png

### 2019-07-02 paper/ms.tex
update paper

@@
 	\gridline{\fig{dias14matchstats.png}{0.95\textwidth}{}}
+	\vspace{-0.8cm}
 	\caption{
@@
     histogram of the difference between the true $G$-band magnitude
-    and that predicted from 2MASS photometry in the middle; a scatter
+    and that predicted from 2MASS photometry is in the middle; a scatter
     plot of the same magnitude difference as a function of $G$-band
@@
 		visualization purposes.
-        The systematic error in the top-right corner is a typical problem in 
-        wide-field astrometry.
+    The systematic error in the top-right corner is a typical
+    problem generic to wide-field astrometry.
     The frame chosen for this plot is the photometric reference frame used 
@@
 
-\begin{figure*}[t]
-    \begin{center}
-		\includegraphics[height=0.9\textheight]{mag_vs_epdparams.png}
-    \end{center}
-    \vspace{-0.5cm}
-    \caption{
-      {\bf Flux as a function of ``external parameters'' for four
-      representative stars.} The left two columns are stars at the
-      corner of a camera's field; the right two columns are from the
-      centers.
-      Each row shows a different parameter along the $x$-axis, given
-      in text at the bottom right of each subplot.
-      ``Hooks'' are common features in flux as a function of
-      temperature and centroid position.
-      \S~\ref{sec:flux_vs_external_parameters} gives a verbose
-      description.
-     \label{fig:flux_vs_external_parameters}
-    }
-\end{figure*}
+% \begin{figure*}[t]
+%     \begin{center}
+% 		\includegraphics[height=0.9\textheight]{mag_vs_epdparams.png}
+%     \end{center}
+%     \vspace{-0.5cm}
+%     \caption{
+%       {\bf Flux as a function of ``external parameters'' for four
+%       representative stars.} The left two columns are stars at the
+%       corner of a camera's field; the right two columns are from the
+%       centers.
+%       Each row shows a different parameter along the $x$-axis, given
+%       in text at the bottom right of each subplot.
+%       ``Hooks'' are common features in flux as a function of
+%       temperature and centroid position.
+%       \S~\ref{sec:flux_vs_external_parameters} gives a verbose
+%       description.
+%      \label{fig:flux_vs_external_parameters}
+%     }
+% \end{figure*}
 
@@
 \item {\it Flux vs.\ centroid positions}. The flux as a function of
-  centroid position often showed non-linear ``hooks'' (see Figure
-    \ref{fig:flux_vs_external_parameters}). Most of the data points from a 
-    given orbit reside at a given
+  centroid position often showed non-linear ``hooks''
+    %(see Figure \ref{fig:flux_vs_external_parameters}).
+    Most of the data points from a given orbit reside at a given
     level, but about 10\% are in a tail. This was seen in light curves
@@
 	\caption{
-		{\bf Positions of light curves from Sectors 6
+		{\bf Positions of light curves from TESS Sectors 6
 			and 7 in galactic coordinates.}
-		    Black: $G_{\rm Rp}<13$ field stars.  Blue: $G_{\rm Rp}<16$ target stars.
+        Black: $G_{\rm Rp}<13$ field stars.  Blue: $G_{\rm Rp}<16$
+        target stars.  The target stars are mostly near the galactic
+        plane.
 		\label{fig:lcgalactic}
@@
 	\caption{
-    {\bf Six of the \numberpcs candidate transiting planets identified
-    from this work.}
+    {\bf Phased light curves for six of the \numberpcs candidate
+    transiting planets identified in this work.}
     Black points are detrended flux measurements, phased to the
-    best-fit orbital period, indicated in the lower right of each panel.
+    best-fit orbital period indicated in the lower right of each
+    panel.
     Best-fit models are fit as described in \S~\ref{subsec:ctois}, and
-    shown with blue lines.
-    For display purpses, a window of $\pm 4$ transit durations from the
-    mid-point is displayed.
+    plotted with blue lines.
+    For display purpses, a window of $\pm 4$ transit durations
+    centered on the transit mid-point is displayed.
     The vetting reports for these objects are available at XXX.	%FIXME

### 2019-07-02 paper/collect_figures.sh
minor

@@ -21,6 +21,9 @@ cp ${fdir}rms_vs_mag.png ${pdir}rms_vs_mag.png
 # quilt of PCs
 cp ${fdir}quilt_PCs.png ${pdir}quilt_PCs.png
 
+# time evolution of LS peak period
+cp ${fdir}LS_period_vs_color_and_age.png ${pdir}LS_period_vs_color_and_age.png
+
 # positions of lightcurves
 cp ${fdir}sector6_cam[1]_ccd[1-2-3-4]cluster_field_star_positions.png \
    ${pdir}sector6_cam[1]_ccd[1-2-3-4]cluster_field_star_positions.png

### 2019-07-02 paper/ms.tex
paper update

@@
 
-\subsection{Identifying Objects of Interest}
+\subsection{Identifying Planet Candidates}
 \label{subsec:identifying_ctois}
@@
 
-\subsection{Objects of Interest}
+\subsection{Candidate TESS Objects of Interest}
 \label{subsec:ctois}
@@
 position, and the ephemeris of each object.
+
+\subsection{Eclipsing binaries, stellar rotation}
+
+\begin{figure}[t]
+	\begin{center}
+		\leavevmode
+		\includegraphics[width=0.47\textwidth]{LS_period_vs_color_and_age.png}
+	\end{center}
+	\vspace{-0.2cm}
+	\caption{
+    {\bf Time evolution of Lomb-Scargle periodogram peak period versus
+    Gaia color.}
+    Red stars are on the right, blue stars are on the left.
+    Each point on this diagram is a star for which the false alarm
+    probability of the most powerful Lomb-Scargle peak is below
+    $10^{-15}$.
+    Additionally, we required (a) that the membership claim originate
+    from \citet{cantat-gaudin_gaia_2018},
+    \citet{Kharchenko_et_al_2013}, or \citet{gaia_hr_2018}; and (b)
+    that the claimed cluster had an age reported by
+    \citet{Kharchenko_et_al_2013}.
+	\label{fig:ls_peak_vs_time}
+	}
+\end{figure}
+
+TODO: describe how this was made.
+Figure~\ref{fig:ls_peak_vs_time}.
 

### 2019-07-02 drivers/do_initial_period_finding.py
add figure for LS peak evoln in time

@@ -232,7 +232,8 @@ def do_initial_period_finding(
         df['source_id'] = df['source_id'].astype(np.int64)
         mdf = df.merge(cd, how='left', on='source_id')
 
-        mdf.to_csv(outpath, index=False)
+        # ";" sep needed b/c reference is ","-separated
+        mdf.to_csv(outpath, index=False, sep=';')
         print('made {}'.format(outpath))
     else:
         mdf = pd.read_csv(outpath)

### 2019-07-02 drivers/paper_plot_all_figures.py

@@ -29,12 +29,18 @@ from cdips.plotting import plot_catalog_to_gaia_match_statistics as xms
 from cdips.plotting import plot_wcsqa as wcsqa
 from cdips.utils import collect_cdips_lightcurves as ccl
 
+from collections import Counter
+
 OUTDIR = '/nfs/phtess2/ar0/TESS/PROJ/lbouma/cdips/results/paper_figures/'
 CLUSTERDATADIR = '/home/lbouma/proj/cdips/data/cluster_data'
 
 def main():
 
     sectors = [6,7]
+
+    plot_LS_period_vs_color_and_age(sectors, overwrite=1, OC_MG_CAT_ver=0.3)
+    assert 0
+
 
     # fig N: T magnitue CDF for all CDIPS target stars.
     plot_target_star_cumulative_counts(OC_MG_CAT_ver=0.3, overwrite=0)
@@ -83,6 +89,144 @@ def main():
 def savefig(fig, figpath):
     fig.savefig(figpath, dpi=450, bbox_inches='tight')
     print('{}: made {}'.format(datetime.utcnow().isoformat(), figpath))
+
+
+def plot_LS_period_vs_color_and_age(sectors, overwrite=0, OC_MG_CAT_ver=0.3):
+    """
+    * plot lomb-scargle periodogram peak period vs Gaia-G magnitude.
+      (or vs Bp-Rp).
+      should show : there's a lot of science to do here.
+
+      * cut on FAP < 1e-20, or something.
+
+      * selected by e.g., only "good member lists" -- Kharchenko, and
+        Cantat-Gaudin. never Dias.
+
+      * focus on any cluster larger than 100 Myr...
+    """
+
+    outpath = os.path.join(OUTDIR, 'LS_period_vs_color_and_age.png')
+    if os.path.exists(outpath) and not overwrite:
+        print('found {} and not overwrite; return'.format(outpath))
+        return
+
+    pfdir = '/nfs/phtess2/ar0/TESS/PROJ/lbouma/cdips/results/cdips_lc_periodfinding'
+    pfpaths = []
+    for sector in sectors:
+        thisdir = os.path.join(pfdir, 'sector-{}'.format(sector))
+        pfpath = os.path.join(thisdir, 'initial_period_finding_results.csv')
+        pfpaths.append(pfpath)
+
+    pfdf = pd.concat((pd.read_csv(f) for f in pfpaths))
[…]

### 2019-07-02 paper/ms.tex
update paper

@@
     $10^{-15}$.
-    Additionally, we required (a) that the membership claim originate
+    Additionally, we required (1) that the membership claim originate
     from \citet{cantat-gaudin_gaia_2018},
-    \citet{Kharchenko_et_al_2013}, or \citet{gaia_hr_2018}; and (b)
-    that the claimed cluster had an age reported by
+    \citet{Kharchenko_et_al_2013}, or \citet{gaia_hr_2018}; and (2)
+    that the cluster with claimed membership had an age reported by
     \citet{Kharchenko_et_al_2013}.

### 2019-07-03 drivers/paper_plot_all_figures.py
add pie chart for membership provenance

@@ -41,6 +41,9 @@ def main():
     # fig N: LS period vs color evolution in time
     plot_LS_period_vs_color_and_age(sectors, overwrite=1, OC_MG_CAT_ver=0.3)
 
+    # fig N: target star provenance
+    plot_target_star_reference_pie_chart(OC_MG_CAT_ver=0.3, overwrite=1)
+
     # fig N: T magnitude CDF for all CDIPS target stars.
     plot_target_star_cumulative_counts(OC_MG_CAT_ver=0.3, overwrite=0)
 
@@ -200,7 +203,7 @@ def plot_LS_period_vs_color_and_age(sectors, overwrite=0, OC_MG_CAT_ver=0.3):
         xval = sdf[allsel]['phot_bp_mean_mag'] - sdf[allsel]['phot_rp_mean_mag']
         yval = sdf[allsel]['ls_period']
         ax.scatter(xval, yval, rasterized=True, s=5, alpha=0.9, linewidths=0,
-                   zorder=2, c='gray')
+                   zorder=2, c='lightgray')
 
     for ax in axs:
         ax.yaxis.set_ticks_position('both')
@@ -525,6 +528,67 @@ def plot_target_star_hist_logt(OC_MG_CAT_ver=0.3, overwrite=1):
     ax.set_yscale('log')
     ax.set_xlim([5.5, 10.5])
     ax.set_ylim([3e3, 3e5])
+
+    f.tight_layout(pad=0.2)
+    savefig(f, outpath)
+
+
+def plot_target_star_reference_pie_chart(OC_MG_CAT_ver=0.3, overwrite=1):
+
+    cdips_df = ccl.get_cdips_catalog(ver=OC_MG_CAT_ver)
+
+    outpath = os.path.join(OUTDIR, 'target_star_reference_pie_chart.png')
+    if os.path.exists(outpath) and not overwrite:
+        print('found {} and not overwrite; return'.format(outpath))
+        return
+
+    #
+    # Collect the info:
+    # ('Dias2014', 470313), ('Kharchenko2013', 183992), ('CantatGaudin_2018',
+    # 177913), ('Zari_2018_UMS', 82875), ('Zari_2018_PMS', 35488)
+    #
+    cnt = Counter(nparr(cdips_df['reference']))
+    atleast2 = 0
+    for k in cnt.keys():
+        if ',' in k:
+            atleast2 += cnt[k]
+
+    mostcommon = cnt.most_common(n=5)
+    mostcommon.append(('>2', atleast2))
+
[…]

### 2019-07-03 paper/ms.tex

@@
 
-The preceding steps produce light curves that include both instrumental
-systematics as well as astrophysical variability.  The detrending
-approach adopted by the HAT group typically proceeds in a few
-sequential stages (see discussions from {\it e.g.}
-\citealt{bakos_2010,huang_high-precision_2015,zhang_precision_2016}).
-Given the heritage of our pipeline, we briefly discuss these, and then
-explain why we omit most of the steps described.
-
-The first detrending step commonly performed on ground-based data is
-``magnitude-fitting'': the raw magnitudes measured from the difference
-images are fit by a polynomial that depends on a combination of CCD
-position, sub-pixel position, and optionally catalog magnitude and
-color \citep[][Sec.~5.5]{zhang_precision_2016}.
-
-The second step is to decorrelate against external parameters that are
-known to affect the stellar flux measurements (EPD,
-\citealt[][~Appendix]{bakos_2010}).  For ground-based data this may include zenith
-angle, or changing PSF parameters.  For TESS data, this might include
-CCD temperature, or perhaps some measure of the scatter in the spacecraft
-pointing (CITE: Vanderburg 2019).
-
-The final step is to then decorrelate the measured brightnesses of
-stars against each other (TFA, \citealt{kovacs_trend_2005}).  
-This accounts for variations due to unknown systematic
-instrument changes that affect many stars.
-
-%FIXME TURGID PROSE
-In \S~\ref{sec:flux_vs_external_parameters}, we show that the
-``external parameter'' dependence visible in the TESS data is rather
-complex: ordinary linear model-fitting, as well as an initial attempts
-at non-linear model fitting, are poor descriptions of the data.  
-In a similar vein ``magnitude-fitting'' is minimally justified, given
-how the TESS magnitudes correlate against these external parameters.
-We go on to show (\S~\ref{sec:tfa_is_good_enough}) that a plausible
-detrending approach for the purpose of transit discovery is to simply
-decorrelate against other nearby stars with standard TFA.
-
-\subsubsection{Flux versus external parameters}
-\label{sec:flux_vs_external_parameters}
-
 \begin{figure*}[t]
@@
 \end{figure*}
+
+The preceding steps produce light curves that include both instrumental
+systematics as well as astrophysical variability.  The detrending
+approach adopted by the HAT group typically proceeds in a few
+sequential stages (see discussions from {\it e.g.}
+\citealt{bakos_2010,huang_high-precision_2015,zhang_precision_2016}).
+Given the heritage of our pipeline, we briefly discuss these, and then
+explain why we omit most of the steps described.
+
+The first detrending step commonly performed on ground-based data is
+``magnitude-fitting'': the raw magnitudes measured from the difference
+images are fit by a polynomial that depends on a combination of CCD
+position, sub-pixel position, and optionally catalog magnitude and
+color \citep[][Sec.~5.5]{zhang_precision_2016}.
+
+The second step is to decorrelate against external parameters that are
+known to affect the stellar flux measurements (EPD,
+\citealt[][~Appendix]{bakos_2010}).  For ground-based data this may include zenith
+angle, or changing PSF parameters.  For TESS data, this might include
+CCD temperature, or perhaps some measure of the scatter in the spacecraft
+pointing (CITE: Vanderburg 2019).
+
+The final step is to then decorrelate the measured brightnesses of
+stars against each other (TFA, \citealt{kovacs_trend_2005}).  
+This accounts for variations due to unknown systematic
+instrument changes that affect many stars.
+
+%FIXME TURGID PROSE
+In \S~\ref{sec:flux_vs_external_parameters}, we show that the
+``external parameter'' dependence visible in the TESS data is rather
+complex: ordinary linear model-fitting, as well as an initial attempts
+at non-linear model fitting, are poor descriptions of the data.  
+In a similar vein ``magnitude-fitting'' is minimally justified, given
+how the TESS magnitudes correlate against these external parameters.
+We go on to show (\S~\ref{sec:tfa_is_good_enough}) that a plausible
+detrending approach for the purpose of transit discovery is to simply
+decorrelate against other nearby stars with standard TFA.
+
+\subsubsection{Flux versus external parameters}
+\label{sec:flux_vs_external_parameters}
 
@@
 
-\subsection{Light Curve Statistics}
-\label{subsec:lcstatistics}
-
-\subsubsection{Stellar properties}
-
 \begin{figure*}[!t]
-	%\gridline{
-	%  \fig{cluster_field_star_positions.png}{0.49\textwidth}{}
-	%  \fig{sector6_cam[1]_ccd[1-2-3-4]cluster_field_star_positions.png}{0.49\textwidth}{}
-	%}
 	\begin{center}
@@
 
-\begin{figure}[!t]
-	\begin{center}
-		\leavevmode
-		\includegraphics[width=0.47\textwidth]{sector6_cam[1]_ccd[1-2-3-4]cluster_field_star_positions.png}
-	\end{center}
-	\vspace{-0.5cm}
-	\caption{
-		{\bf  Zoom and coordinate transformation
-			of Sector 6, Camera 1 from Figure~\ref{fig:lcgalactic}.}
-		The most populated cluster is XXX, primarily due to candidate
-		members proposed by \citet{dias_proper_2014}.
-		\label{fig:lcradeczoom}
-	}
-\end{figure}
+%\begin{figure}[!t]
+%	\begin{center}
+%		\leavevmode
+%		\includegraphics[width=0.47\textwidth]{sector6_cam[1]_ccd[1-2-3-4]cluster_field_star_positions.png}
+%	\end{center}
+%	\vspace{-0.5cm}
+%	\caption{
+%		{\bf  Zoom and coordinate transformation
+%			of Sector 6, Camera 1 from Figure~\ref{fig:lcgalactic}.}
+%		The most populated cluster is XXX, primarily due to candidate
+%		members proposed by \citet{dias_proper_2014}.
+%		\label{fig:lcradeczoom}
+%	}
+%\end{figure}
 
@@
 \end{figure}
-
-The on-sky locations of the light curves from Sectors 6 and 7
-are shown in Figure~\ref{fig:lcgalactic}.
-Black stars are the field stars for which we performed photometry,
-but only to calibrate the cluster star sample.
-The blue stars are the \numberlcs stars with light curves available
-from \stscilink.
-Most of the target stars are quite close to the galactic plane.
-Gaps between CCD chips are also visible.
-
-A zoom-in of Figure~\ref{fig:lcgalactic} is shown in Figure~\ref{fig:lcradeczoom}
-for the Camera 1, Sector 6 field. The effects of galactic-latitude
-dependent extinction are visible through the decreasing density of black
-points towards the right of the image.
-The highly clumped nature of the target stars is also apparent.
-
-Figure~\ref{fig:cdf_T_mag} shows the cumulative distribution of
-TESS $T$-band magnitudes for the target stars.
-Though most of the targets are faint, $\approx3\times10^4$ are
-brighter than $T=13$, and so are more promising targets for any
-detailed follow-up observtions.
-
-An HR diagram for the entire sample of stars on silicon
-is shown in Figure~\ref{fig:hrd} (top).
-The sub-sample of stars with
-measured positive parallaxes and naive distances less than
-$1\,{\rm kpc}$ is also shown (bottom).
-About one-third of the stars are in this latter sample.
-The close stars are predominantly on the main-sequence, or the pre-main-sequence.
-A relatively large fraction of these come from \citet{zari_3d_2018},
-and are either on the PMS or upper main-sequence.
-The latter set of OBA dwarf stars, while ``younger'' than the typical
-field dwarf, are likely the least interesting subset of our target sample
-from the perspective of age analyses.
-In the entire sample (Figure~\ref{fig:hrd} top), a much larger fraction of stars are sub-giants,
-red giants, and helium-burning red-clump stars.
-We failed to obtain light curves for roughly $5\%$ of the stars on silicon, 
-primarily due to our masking of saturated stars and their nearby pixels.
-
-Finally, 
-Figure~\ref{fig:propermotions} shows the proper motions
-of the entire and close samples of stars on silicon.
-Each clump signifies a different star cluster. The central
-blob in the top figure is in fact two separate blobs,
-due to the different directions in the Galaxy being observed
-in Sectors 6 and 7.
-
-\subsubsection{Cluster membership provenance}.
-
-\paragraph{Sector 6}
-In Sector 6, \sVInumberlcs light curves of candidate cluster stars
-were made. The provenance of the claimed cluster origin of these
-sources is \citet{dias_proper_2014} for 59\% of the sources;
-\citet{zari_3d_2018} for 16\% of sources from their upper
-main-sequence table and 1\% of sources from their PMS table;
-\citet{Kharchenko_et_al_2013} for 8\% of sources,
-\citet{cantat-gaudin_gaia_2018} for 6\% of sources, and more than two
-catalogs for the remaining 10\% of sources.
-
-The clusters with the largest claimed numbers of sources are the
-Platais~6, Platais~5, and Mamajek~3 moving groups, all from
-\citet{dias_proper_2014}, composing about 7000, 7000, and 3500 sources
-respectively. These membership claims should be regarded with some
-skepticism on a source-by-source basis.  For Platais~6,
-\citet{Kharchenko_et_al_2013} claimed only about 400 probable members
-(1$\sigma$) to exist within the angular radius of the cluster.
-Mamajek~3 (32$\,$Ori) has only about 50 confirmed members
-\citep{bell_32ori_2017}.
-
-We remind the reader that our goal in creating this sample was
-completeness, rather than fidelity. The \citet{dias_proper_2014} stars
-in particular were included if they were listed with membership
-probability exceeding 50\%.  To create cleaner sub-samples, we advise
-use of the \texttt{CDEXTCAT} header keyword, which can be
-cross-matched against the original source catalog to obtain the
-membership probabilities claimed by the original catalog.
-
-\paragraph{Sector 7}
-In Sector 7, \sVIInumberlcs light curves of candidate cluster stars
-were made. The provenance of the claimed cluster origin of these
-sources is  ...
-
-The clusters with the largest claimed numbers of sources are ...
-
-\subsubsection{Light curve noise properties}
-\label{subsubsec:rmsvsmag}
 
@@
 \end{figure}
+
+\subsection{Light Curve Statistics}
+\label{subsec:lcstatistics}
+
+\subsubsection{Stellar properties}
+
+The on-sky locations of the light curves from Sectors 6 and 7
+are shown in Figure~\ref{fig:lcgalactic}.
+Black stars are the field stars for which we performed photometry,
+but only to calibrate the cluster star sample.
+The blue stars are the \numberlcs stars with light curves available
+from \stscilink.
+Most of the target stars are quite close to the galactic plane.
+Gaps between CCD chips are also visible.
+The highly clumped nature of the target stars is also apparent.
+
+%A zoom-in of Figure~\ref{fig:lcgalactic} is shown in Figure~\ref{fig:lcradeczoom}
+%for the Camera 1, Sector 6 field. The effects of galactic-latitude
+%dependent extinction are visible through the decreasing density of black
+%points towards the right of the image.
+
+Figure~\ref{fig:cdf_T_mag} shows the cumulative distribution of
+TESS $T$-band magnitudes for the target stars.
+Though most of the targets are faint, $\approx3\times10^4$ are
+brighter than $T=13$. These targets are more promising for any
+detailed follow-up observtions.
+
+An HR diagram for the entire sample of stars on silicon
+is shown in Figure~\ref{fig:hrd} (top).
+The sub-sample of stars with
+measured positive parallaxes and naive distances less than
+$1\,{\rm kpc}$ is also shown (bottom).
+About one-third of the stars are in this latter sample.
+The close stars are predominantly on the main-sequence, or the pre-main-sequence.
+A relatively large fraction of these come from \citet{zari_3d_2018},
+and are either on the PMS or upper main-sequence.
+The latter set of OBA dwarf stars, while ``younger'' than the typical
+field dwarf, are likely the least interesting subset of our target sample
+from the perspective of age analyses.
+In the entire sample (Figure~\ref{fig:hrd} top), a much larger fraction of stars are sub-giants,
+red giants, and helium-burning red-clump stars.
+We failed to obtain light curves for roughly $5\%$ of the stars on silicon, 
+primarily due to our masking of saturated stars and their nearby pixels.
+
+Finally, 
+Figure~\ref{fig:propermotions} shows the proper motions
+of the entire and close samples of stars on silicon.
+Each clump signifies a different star cluster. The central
+blob in the top figure is in fact two separate blobs,
+due to the different directions in the Galaxy being observed
+in Sectors 6 and 7.
+
+\subsubsection{Cluster membership provenance}.
+
+\paragraph{Sector 6}
+In Sector 6, \sVInumberlcs light curves of candidate cluster stars
+were made. The provenance of the claimed cluster origin of these
+sources is \citet{dias_proper_2014} for 59\% of the sources;
+\citet{zari_3d_2018} for 16\% of sources from their upper
+main-sequence table and 1\% of sources from their PMS table;
+\citet{Kharchenko_et_al_2013} for 8\% of sources,
+\citet{cantat-gaudin_gaia_2018} for 6\% of sources, and more than two
+catalogs for the remaining 10\% of sources.
+
+The clusters with the largest claimed numbers of sources are the
+Platais~6, Platais~5, and Mamajek~3 moving groups, all from
+\citet{dias_proper_2014}, composing about 7000, 7000, and 3500 sources
+respectively. These membership claims should be regarded with some
+skepticism on a source-by-source basis.  For Platais~6,
+\citet{Kharchenko_et_al_2013} claimed only about 400 probable members
+(1$\sigma$) to exist within the angular radius of the cluster.
+Mamajek~3 (32$\,$Ori) has only about 50 confirmed members
+\citep{bell_32ori_2017}.
+
+We remind the reader that our goal in creating this sample was
+completeness, rather than fidelity. The \citet{dias_proper_2014} stars
+in particular were included if they were listed with membership
+probability exceeding 50\%.  To create cleaner sub-samples, we advise
+use of the \texttt{CDEXTCAT} header keyword, which can be
+cross-matched against the original source catalog to obtain the
+membership probabilities claimed by the original catalog.
+
+\paragraph{Sector 7}
+In Sector 7, \sVIInumberlcs light curves of candidate cluster stars
+were made. The provenance of the claimed cluster origin of these
+sources is  ...
+
+The clusters with the largest claimed numbers of sources are ...
+
+\subsubsection{Light curve noise properties}
+\label{subsubsec:rmsvsmag}
 
@@
 
-To identify an initial set of transiting planets, strong stellar rotators, and 
-eclipsing binaries, we performed a few steps of post-processing on the light 
-curve described in the preceding sections. 
-This processing was entirely independent of the data release, since it was 
-quite specific to our own scientific interests.
-
-For simplicity,
-we first chose a single aperture size~--~``aperture 2''~--~with a radius of 
-1.5  pixels.
-Then, to identify periodic transit-like signals, we used 
-\citet{hippke_TLS_2019}'s transit least-squares (TLS) tool.
-The algorithm is the same as the canonical box least-squares
-\citep{kovacs_box-fitting_2002}, except in place of a box template, a transit 
-template is used  for a marginal improvement of the detection efficiency.
-In addition, the search grids in \texttt{tls} 
-\footnote{\url{https://github.com/hippke/tls}} are slightly more 
-efficient than in most BLS implementations, since \texttt{tls} uses the 
-cubic-in-frequency sampling advocated by \citet{ofir_optimizing_2014}, 
-rather than standard linear-in-frequency sampling.
-Our grids typically consisted of about 30 different durations, and
-about 5000 periods between 0.5 and 21 days.
-
-Before performing the period search, we rejected $6\,{\rm hours}$ at the
-beginning and end of each spacecraft orbit, to mitigate the presence
-of correlated red noise in the results.
-This shrank the data volume by about 5\%, but also lowered the number
-of systematic false positives in subsequent vetting.
-We then performed an asymmetric sigma-clipping of $(50\sigma,5\sigma)$ to 
-preserve transits while omitting flares and other positive flux excursions.
-
-A number of the light curves show residual variability, often of stellar 
-origin.
-This is expected for a sample of young stars; the problem of finding transits in 
-the face of large stellar rotation signals 
-has been explored by both \citet{rizzuto_zeitV_2017} and also 
-\citet{hippke_wotan_2019}.
-The former adopted an approach that we have yet to explore, which is to 
-pass a sliding window over the light curve that, within each step, performs a 
-Bayesian model comparison between a spline and a spline-plus-notch model.  If 
-the spline-plus-notch model is favored, the transits are preserved for 
-subsequent discovery.
-\citet{hippke_wotan_2019}, conversely, described a number of different
-detrending methods, and found that most performed more or less the same at 
-recovering planetary transits for a sample of young stars with strong rotation 
-signals.
-
-Our approach in this work is essentially identical to one of the methods 
-described by \citet{hippke_wotan_2019}.
-First, we run a generalized Lomb-Scargle periodogram on each TFA light 
-curve \citep{lomb_1976,scargle_studies_1982,vanderplas_periodograms_2015}.
-If a peak is found with false alarm probability below $10^{-5}$, we consider 
-the star ``variable'', and opt to 
-detrend the light curve with robust penalized B-splines, which are splines 
-with knot-length automatically determined via cross-validation 
-\citep{eilers_flexible_1996}. The idea behind the cross-validation is that a 
-larger  number of knots leads to smaller residuals on training data, but 
-larger errors 
-when tested on the entire dataset.
-We used the \texttt{wotan} implementation, which is a wrapper to the 
-\texttt{pyGAM} spline fitter, with $2\sigma$ clipping of outliers from the fit 
-residuals at each iteration 
-\citep{serven_pygam_2018_1476122,hippke_wotan_2019}.
-The maximum number of spline knots is set to 50, which for each TESS sector 
-($\approx 25\,{\rm days}$) is commensurate with a $\approx0.5\,{\rm day}$ 
-window.
-
-We verified by injecting and recovering a 2.5 mmag central-transit planet
-with variable period that this detrending approach marginally improved
-the recovery probability, compared to not doing anything.
-The main cases for which it helps are those with large residual stellar
-variability in the TFA light curve.
-
 \begin{figure}[!t]
@@
 	\caption{
-        Significance thresholds empirically defined for the transiting planet 
-        search described in \S~\ref{subsec:identifying_ctois}. Each point represents the 
-        TLS periodogram peak signal detection efficiency from one light curve.
-        {\it Top.} Sector 6.  {\it Bottom.} Sector 7.
+		Significance thresholds empirically defined for the transiting
+		planet search described in \S~\ref{subsec:identifying_ctois}.
+		Each point represents the TLS periodogram peak signal
+		detection efficiency from one light curve.  {\it Top.} Sector
+		6.  {\it Bottom.} Sector 7.
 	}
@@
 
+To identify an initial set of transiting planets, strong stellar
+rotators, and eclipsing binaries, we performed a few steps of
+post-processing on the light curve described in the preceding
+sections.  This processing was entirely independent of the data
+release, since it was quite specific to our own scientific interests.
+
+For simplicity, we first chose a single aperture size~--~``aperture
+2''~--~with a radius of 1.5  pixels.  Then, to identify periodic
+transit-like signals, we used \citet{hippke_TLS_2019}'s transit
+least-squares (TLS) tool.  The algorithm is the same as the canonical
+box least-squares \citep{kovacs_box-fitting_2002}, except in place of
+a box template, a transit template is used  for a marginal improvement
+of the detection efficiency.  In addition, the search grids in
+\texttt{tls} \footnote{\url{https://github.com/hippke/tls}} are
+slightly more efficient than in most BLS implementations, since
+\texttt{tls} uses the cubic-in-frequency sampling advocated by
+\citet{ofir_optimizing_2014}, rather than standard linear-in-frequency
+sampling.  Our grids typically consisted of about 30 different
+durations, and about 5000 periods between 0.5 and 21 days.
+
+Before performing the period search, we rejected $6\,{\rm hours}$ at
+the beginning and end of each spacecraft orbit, to mitigate the
+presence of correlated red noise in the results.  This shrank the data
+volume by about 5\%, but also lowered the number of systematic false
+positives in subsequent vetting.  We then performed an asymmetric
+sigma-clipping of $(50\sigma,5\sigma)$ to preserve transits while
+omitting flares and other positive flux excursions.
+
+A number of the light curves show residual variability, often of
+stellar origin.  This is expected for a sample of young stars; the
+problem of finding transits in the face of large stellar rotation
+signals has been explored by both \citet{rizzuto_zeitV_2017} and also
+\citet{hippke_wotan_2019}.  The former adopted an approach that we
+have yet to explore, which is to pass a sliding window over the light
+curve that, within each step, performs a Bayesian model comparison
+between a spline and a spline-plus-notch model.  If the
+spline-plus-notch model is favored, the transits are preserved for
+subsequent discovery.  \citet{hippke_wotan_2019}, conversely,
+described a number of different detrending methods, and found that
+most performed more or less the same at recovering planetary transits
+for a sample of young stars with strong rotation signals.
+
+Our approach in this work is essentially identical to one of the
+methods described by \citet{hippke_wotan_2019}.  First, before
+sigma-clipping or omitting points near the edges of orbits we run a
+generalized Lomb-Scargle periodogram on each TFA light curve
+\citep{lomb_1976,scargle_studies_1982,vanderplas_periodograms_2015}.
+If a peak is found with false alarm probability below $10^{-5}$, we
+consider the star ``variable'', and opt to detrend the light curve
+with robust penalized B-splines, which are splines with knot-length
+automatically determined via cross-validation
+\citep{eilers_flexible_1996}. The idea behind the cross-validation is
+that more knots leads to smaller residuals on training data, but
+larger errors when tested on the entire dataset.  We used the
+\texttt{wotan} implementation, which is a wrapper to the
+\texttt{pyGAM} spline fitter, with $2\sigma$ clipping of outliers from
+the fit residuals at each iteration
+\citep{serven_pygam_2018_1476122,hippke_wotan_2019}.  The maximum
+number of spline knots is set to 50, which for each TESS sector
+($\approx 25\,{\rm days}$) is commensurate with a $\approx0.5\,{\rm
+day}$ window.
+
+We verified by injecting and recovering a 2.5 mmag central-transit
+planet with variable period that this detrending approach marginally
+improved the recovery probability, compared to not doing anything.
+The main cases for which it helps are those with large residual
+stellar variability in the TFA light curve.
+
 After (optionally) detrending, we run the TLS search. To select
-``significant'' signals for visual inspection, we 
-performed a cut on the TLS signal detection efficiency defined piecewise over 
-the signal periods.
-The overall lower limit is ${\rm SDE} > 12$, with higher limits imposed in 
-regions with heavy contamination from systematic signals.
-The signals for sectors 6 and 7 are shown in the space of SDE vs period in 
-Figure~\ref{fig:tlsresults}.
-
-This yielded a few thousand light curves.  About two-thirds already had been 
-detrended with splines, and were not processed further.
-For the remaining third we
-performed TFA signal reconstruction using 
-\texttt{vartools}.
-In this process, the model lightcurve $A(i)$ in 
-Equation~\ref{eq:tfa_to_minimize} is set to the phase-binned signal from the 
-most powerful peak in the TLS spectrum, rather than being a constant function. 
-This helps lower the scatter of the light curve at frequencies away from
-the TLS peak.
-
-We then make a multi-page \texttt{.pdf} document report with the information 
-necessary to make classifications for vetting.
-These documents are released along with the light curves, and are a useful 
-summary for anyone interested in the subset of objects that we have analyzed.
-A full description of each page of the summary \texttt{.pdf} is given in the 
-Appendix.
+``significant'' signals for visual inspection, we performed a cut on
+the TLS signal detection efficiency defined piecewise over the signal
+periods.  The overall lower limit is ${\rm SDE} > 12$, with higher
+limits imposed in regions with heavy contamination from systematic
+signals.  The signals for sectors 6 and 7 are shown in the space of
+SDE vs period in Figure~\ref{fig:tlsresults}.
+
+This yielded a few thousand light curves.  About two-thirds already
+had been detrended with splines, and were not processed further.  For
+the remaining third we performed TFA signal reconstruction using
+\texttt{vartools}.  In this process, the model lightcurve $A(i)$ in
+Equation~\ref{eq:tfa_to_minimize} is set to the phase-binned signal
+from the most powerful peak in the TLS spectrum, rather than being a
+constant function.  This helps lower the scatter of the light curve at
+frequencies away from the TLS peak.
+
+We then make a multi-page \texttt{.pdf}-format document report with
+the information necessary to make classifications for vetting.  These
+vetting reports are released along with the light curves, and are a
+useful summary for anyone interested in the subset of objects that we
+have analyzed.  A full description of each page of the report is given
+in Appendix~\ref{appendix:vetreport}.
 
@@
 \begin{enumerate}
-    \item {\it Photometric variability classification}. Designations include 
-    tags for planet candidates, eclipsing binaries, instrumental variations, 
-    stellar variations, and ``weirdos''.
+    \item {\it Photometric variability classification}. Designations
+      include tags for planet candidates, eclipsing binaries,
+      instrumental variations, stellar variations, and ``weirdos''.
     %
-    \item {\it Cluster membership status}. By default, all light curves were 
-    made for stars with at least one literature claim of cluster membership.  
-    However, some of these claims pre-dated the availability of Gaia-DR2
-    parallaxes or proper motions.
-    We therefore re-assess the membership status on a case-by-case basis 
-    through inspection of the available astrometry and photometry.
-    Known asterisms are also omitted at this point
-    \citep[{\it e.g.},][]{sulentic_revised_1973,baumgardt_asterisms_1998,kos_galah_2018}.
+    \item {\it Cluster membership status}. By default, all light
+      curves were made for stars with at least one literature claim of
+      cluster membership.  However, some of these claims pre-dated the
+      availability of Gaia-DR2 parallaxes or proper motions.  We
+      therefore re-assess the membership status on a case-by-case
+      basis through inspection of the available astrometry and
+      photometry.  Known asterisms are also omitted at this point
+      \citep[{\it
+      e.g.},][]{sulentic_revised_1973,baumgardt_asterisms_1998,kos_galah_2018}.
     %
-    \item {\it Photometric blends}. Tags are created to highlight whether the 
-    depth of the photometric signal shows a strong dependence on aperture 
-    size, and also whether the in-transit minus the out-of-transit images 
-    reveal that the source of variability is in fact far from the target star.
+    \item {\it Photometric blends}. Tags are created to highlight
+      whether the depth of the photometric signal shows a strong
+      dependence on aperture size, and also whether the in-transit
+      minus the out-of-transit images reveal that the source of
+      variability is in fact far from the target star.
 \end{enumerate}
-The actual classifications were performed by LGB, JH, and JNW.
-The \texttt{TagSpaces} software was used~--~an extremely helpful tool
-for the purposes of easily assigning labels to documents.
-An example vetting report for a planet candidate is described in
-Appendix~\ref{appendix:vetreport}.
+The initial classifications were performed by LGB, with subsequent
+checking by JH and JNW.  The \texttt{TagSpaces} software was
+used~--~an extremely helpful tool for the purposes of easily assigning
+labels to documents.
 
@@
 
-\begin{figure*}[t]
+\begin{figure*}[!t]
 	\begin{center}
@@
 
+\begin{figure}[!t]
+	\begin{center}
+		\leavevmode
+		\includegraphics[width=0.45\textwidth]{LS_period_vs_color_and_age.png}
+	\end{center}
+	\vspace{-0.2cm}
+	\caption{
+		{\bf Time evolution of Lomb-Scargle periodogram peak period versus
+			Gaia color.}
+		Red stars are on the right, blue stars are on the left.
+		Each point on this diagram is a star for which the false alarm
+		probability of the most powerful Lomb-Scargle peak is below
+		$10^{-15}$.
+		Additionally, we required (1) that the membership claim originate
+		from \citet{cantat-gaudin_gaia_2018},
+		\citet{Kharchenko_et_al_2013}, or \citet{gaia_hr_2018}; and (2)
+		that the cluster with claimed membership had an age reported by
+		\citet{Kharchenko_et_al_2013}.
+		Our approach for avoiding photometric blends is described in
+		\S~\ref{subsec:notplanets}.
+		\label{fig:ls_peak_vs_time}
+	}
+\end{figure}
+
 If all vetters identified an object as a planet candidate, we then
@@
 \subsection{Eclipsing binaries, stellar rotation}
-
-\begin{figure}[t]
-	\begin{center}
-		\leavevmode
-		\includegraphics[width=0.47\textwidth]{LS_period_vs_color_and_age.png}
-	\end{center}
-	\vspace{-0.2cm}
-	\caption{
-    {\bf Time evolution of Lomb-Scargle periodogram peak period versus
-    Gaia color.}
-    Red stars are on the right, blue stars are on the left.
-    Each point on this diagram is a star for which the false alarm
-    probability of the most powerful Lomb-Scargle peak is below
-    $10^{-15}$.
-    Additionally, we required (1) that the membership claim originate
-    from \citet{cantat-gaudin_gaia_2018},
-    \citet{Kharchenko_et_al_2013}, or \citet{gaia_hr_2018}; and (2)
-    that the cluster with claimed membership had an age reported by
+\label{subsec:notplanets}
+
+To assess the prospects for studying forms of stellar variability
+other than that caused by transiting planets, we performed a brief
+additional exploration.
+Using the Lomb-Scargle periodogram results from
+\S~\ref{subsec:identifying_ctois}, we selected light curves 
+for which the periodogram peak power had a corresponding false alarm
+probability below $10^{-15}$.
+We chose this cutoff to be small enough to give us a reasonable number
+of objects, but large enough so that there would be no question that
+the signal being detected was astrophysical.
+
+Further, we then restricted our focus to stars with a cluster
+membership claim in \citet{cantat-gaudin_gaia_2018},
+\citet{Kharchenko_et_al_2013}, or \citet{gaia_hr_2018}, since from our
+experience these works have a relatively low false positive
+probability.
+We then further restricted our sample of stars to be those for which
+the claimed cluster also had an age reported by
 \citet{Kharchenko_et_al_2013}.
-	\label{fig:ls_peak_vs_time}
-	}
-\end{figure}
-
-TODO: describe how this was made.
-Figure~\ref{fig:ls_peak_vs_time}.
+
+To remove obvious photometrically-blended duplicates, for any signal,
+if any nearby stars had matching periods, we kept only the signal with
+the lowest false alarm probabilty.
+While this does not ensure that the detected signals originate from
+the target star, it removed a large number of the duplicate signals,
+and suits our exploratory purposes.
+
+All told, this yielded 4057 stars between the ages of about 25 Myr and
+1 Gyr.
+In Figure~\ref{fig:ls_peak_vs_time}, we plot the Lomb-Scargle peak period
+versus $G_{\rm Bp} - G_{\rm Rp}$ color over four different bins of
+time.
+The bins were chosen to match the sub-sample sizes within reasonable
+proximity.
+
+The youngest sample of stars is the reddest, as might be expected
+given that many of these stars have not yet reached the main sequence,
+and may exist along lines of sight with heavy extinction.
+
+%FIXME
+The weird part is that the oldest stars seem to have relatively more
+sub-day peak periods.
 
@@
 
+\subsection{The planet candidates require more observations}
 Additional observations are needed for two major goals:
@@
 
+\subsection{Eclipsing binary and stellar variability analyses may also
+be feasible}
+
+Lorem ipsum
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-Lorem ipsum.
+%FIXME: paraphrase / improve all the below
+In this study, we made \numberlcs light curves of candidate young
+stars, across \numberclusters distinct clusters.
+Each light curve represents between 20 and 25 days of observations
+of a star brighter than $G_{Rp}=16$, sampled at 30 minute cadence.
+
+In the process of making the light curves, we learned X, Y, and Z.
+One point in particular was that image subtraction analyses seem to
+do fine at detecting variability in the galactic plane.
+
+In analyzing the noise properties of our light curves, we found that
+at the faint end, contamination from unresolved background stars
+dominated over other noise sources.
+
+From a cursory transiting planet search, we identified \numberpcs
+planet candidates, which need additional spectroscopic, photometric,
+and imaging observations to verify (i) whether these candidates are
+planets and (ii) whether the host stars are cluster members.
+The vetting reports are available at \stscilink, and the planet
+candidate parameters are on exoFOP-TESS.
+
+We also briefly explored the age-evolution of extremely high-SNR
+variability in the space of dominant period versus color
+(Figure~\ref{fig:ls_peak_vs_time}).
+This seems to show X, and Y.
+
+The overall takeaway is that the sample of light curves and vetting
+reports we have made should prove useful for doing some astrophysics.
+%  We also comment on the possible utility of the light curve sample for
+%  studies of stellar rotation evolution, and binary eccentricity
+%  damping.
 
@@
 
+\clearpage
+\newpage
+
 \bibliographystyle{yahapj}                            

### 2019-07-03 paper/ms.tex
update paper

@@
     %\includegraphics[width=0.45\textwidth]{target_star_cumulative_counts.png}
-    \gridline{\fig{target_star_cumulative_counts.png}{0.45\textwidth}{}}
+    \gridline{\fig{target_star_cumulative_counts.png}{0.4\textwidth}{}}
     \vspace{-0.8cm}
-    \gridline{\fig{target_star_hist_logt.png}{0.45\textwidth}{}}
+    \gridline{\fig{target_star_hist_logt.png}{0.4\textwidth}{}}
+    \vspace{-0.8cm}
+    \gridline{\fig{target_star_reference_pie_chart.png}{0.4\textwidth}{}}
 	\end{center}
@@
 	\caption{
-    {\it Top.} Cumulative number of target stars as
-    a function of Gaia $Rp$-band magnitude.  The selected stars are
+    {\it Top.} Cumulative counts of target stars as
+    a function of Gaia $Rp$-band magnitude.  The stars are
     either candidate members of clusters, or else have other youth
@@
     stars with $G_{\rm Rp} < 16$.
-    {\it Bottom.} Histogram of target star ages, for the subset of
+    {\it Middle.} Histogram of target star ages, for the subset of
     stars with ages matched against \citet{Kharchenko_et_al_2013}.
+    {\it Bottom.} Provenance of cluster membership.  Percentages are
+    relative to $N_{\rm total}=1061446$ target stars. Symbols
+    are as follows.
+    D14 is \citet{dias_proper_2014}.
+    K13 is \citet{Kharchenko_et_al_2013}.
+    CG18 is \citet{cantat-gaudin_gaia_2018}.
+    Z18 is \citet{zari_3d_2018}, with upper main sequence and
+    pre-main-sequence samples sub-divided.
+    ``$\geq 2$'' indicates at least two authors reported a star as a
+    candidate cluster member.
+    %``Other'' refers to sources enumerated in \S~\ref{sec:starselection}.
 	\label{fig:cdips_targets}
@@
 	\caption{
-    {\it Top.} Cross-match statistics from
-    \cite{Kharchenko_et_al_2013} cluster members to Gaia-DR2. A
+    {\it Top.} Quality diagnostics from cross-matching
+    \cite{Kharchenko_et_al_2013} cluster members against Gaia-DR2.
     histogram of the distances between matched stars is on the left; a
@@
 	\caption{
-		Significance thresholds empirically defined for the transiting
-		planet search described in \S~\ref{subsec:identifying_ctois}.
-		Each point represents the TLS periodogram peak signal
-		detection efficiency from one light curve.  {\it Top.} Sector
-		6.  {\it Bottom.} Sector 7.
+    (IN PROGRESS) Significance thresholds empirically defined for the
+    transiting planet search described in
+    \S~\ref{subsec:identifying_ctois}.  Each point represents the TLS
+    periodogram peak signal detection efficiency from one light curve.
+    {\it Top.} Sector 6.  {\it Bottom.} Sector 7.
 	}
@@
 		panel.
-		Best-fit models are fit as described in \S~\ref{subsec:ctois}, and
-		plotted with blue lines.
-		For display purpses, a window of $\pm 4$ transit durations
+    Transit models are fitted as described in \S~\ref{subsec:ctois},
+    and plotted with blue lines.
+		For display purposes, a window of $\pm 4$ transit durations
 		centered on the transit mid-point is displayed.

### 2019-07-03 paper/collect_figures.sh

@@ -54,6 +54,10 @@ cp ${fdir}target_star_cumulative_counts.png \
 cp ${fdir}target_star_hist_logt.png \
    ${pdir}target_star_hist_logt.png
 
+cp ${fdir}target_star_reference_pie_chart.png \
+   ${pdir}target_star_reference_pie_chart.png
+
+
 # catalog matching statistics
 cp ${fdir}catalog_to_gaia_match_statistics_MWSC.png \
    ${pdir}mwscmatchstats.png

### 2019-07-03 paper/ms.tex
update paper

@@
 
-\author[0000-0002-0514-5538]{L. G. Bouma}
+\author[0000-0002-0514-5538]{L. G. Bouma (ORDER TBD)}
+\affiliation{ Department of Astrophysical Sciences, Princeton
+University, 4 Ivy Lane, Princeton, NJ 08540, USA}
+%
+\author[0000-0001-8732-6166]{J. D. Hartman}
 \affiliation{ Department of Astrophysical Sciences, Princeton
@@
 %
-\author[0000-0001-8732-6166]{J. D. Hartman}
+\author[0000-0002-4265-047X]{J. N. Winn}
 \affiliation{ Department of Astrophysical Sciences, Princeton
@@
 \author[0000-0001-7204-6727]{G. \'A. Bakos}
-\affiliation{ Department of Astrophysical Sciences, Princeton
-University, 4 Ivy Lane, Princeton, NJ 08540, USA}
-%
-\author[0000-0002-4265-047X]{J. N. Winn}
 \affiliation{ Department of Astrophysical Sciences, Princeton
@@
 photometrically interesting, we can perform post-hoc quality checks
-using Gaia DR2 astrometry and photometry to assess cluster membership
+using Gaia-DR2 astrometry and photometry to assess cluster membership
 and youth.
@@
 In our photometric reduction,  our default identifier for all sources
-is the Gaia DR2 \texttt{source\_id}.
+is the Gaia-DR2 \texttt{source\_id}.
 The TIC identifiers are found through a spatial cross-match after the light 
@@
 \citep{stassun_TIC_2018,stassun_TIC8_2019}
-This is because Gaia DR2 is the base-catalog used to project
+This is because Gaia-DR2 is the base-catalog used to project
 sources from celestial coordinates to the imaging plane (\S~\ref{sec:method}).
@@
 
-We obtained Gaia DR2 identifiers from the results of the following
+We obtained Gaia-DR2 identifiers from the results of the following
 studies:
@@
 
-We reduced the TESS images to light curves by performing a sequence of
-steps using stand-alone programs.
-Our overall method is in the spirit of the reduction approaches developed
-by \citet{Pal_2009}, \citet{huang_high-precision_2015}, \citet{soares-furtado_image_2017} and
-\citet{oelkers_precision_2018}; a conceptual overview is given in
-Figure~\ref{fig:pipeline}.
-
-We begin with the calibrated full frame images produced by the Science
-Processing Operations Center at NASA Ames (\S~\ref{subsec:observations}).
-We then perform a collection of
+We reduced the TESS images to light curves using an image subtraction
+approach.  The overall method is in the spirit of the reduction
+pipelines developed by \citet{Pal_2009},
+\citet{huang_high-precision_2015}, \citet{soares-furtado_image_2017}
+and \citet{oelkers_precision_2018}; a conceptual overview is given in
+Figure~\ref{fig:pipeline}.  Most sub-modules of our pipeline have been
+developed over the past decade to process HAT data \citep[{\it
+e.g.},][]{bakos_hat_review_2018}.  The specific high-level framework
+used for this reduction was adapted from a pipeline called
+\texttt{pipe-trex}, under development primarily for the HATPI project
+(\url{hatpi.org}).  This code is available
+online\footnote{\url{github.com/waqasbhatti/pipe-trex}, commit
+\texttt{cd9f9bb}.}.
+
+We begin our processing with the calibrated full frame images produced
+by the Science Processing Operations Center at NASA Ames
+(\S~\ref{subsec:observations}).  We then perform a collection of
 preparatory steps, including source extraction of bright stars,
-astrometric verification, and coarse simple aperture
-photometry of bright stars (\S~\ref{subsec:preparation}).  Using the metadata
-collected from these initial steps, we select an astrometric reference frame to
-which we transform all of the calibrated images.  We construct a
-photometric reference by stacking a subset of these transformed frames, after
-having convolved the frames to match the stellar profiles of an intermediate
-reference frame. Finally, we
-subtract each target frame from the photometric reference (\S~\ref{subsec:imagesubtraction}).
-We perform aperture
-photometry on the subtracted images using positions projected onto the
-frame from the Gaia DR2 source catalog.  
-We detrend the resulting light curves
-(\S~\ref{subsec:lcdetrending}).  The resulting white noise and red noise properties
-of the light curves, and a few
-interesting cases of variability, are discussed in \S~\ref{sec:results}.
+astrometric verification, and coarse simple aperture photometry of
+bright stars (\S~\ref{subsec:preparation}).  Using the metadata
+collected from these initial steps, we select an astrometric reference
+frame to which we transform all of the calibrated images.  We
+construct a photometric reference by stacking a subset of these
+transformed frames, after having convolved the frames to have
+identical stellar profiles. Finally, we subtract each target frame
+from the photometric reference (\S~\ref{subsec:imagesubtraction}).  We
+perform aperture photometry on the subtracted images using positions
+projected onto the frame from the Gaia-DR2 source catalog.  We detrend
+the resulting light curves (\S~\ref{subsec:lcdetrending}).  The
+resulting white noise and red noise properties of the light curves,
+and a few interesting cases of variability, are discussed in
+\S~\ref{sec:results}.
 
@@
 keep its cameras pointed opposite the Sun, the spacecraft advances by
-$\approx$$28$ degrees east in ecliptic longitude every lunar month.  Data
-acquired throughout each ``sector'' are downlinked at spacecraft
+$\approx$$28$ degrees east in ecliptic longitude every lunar month.
+Data acquired throughout each ``sector'' are downlinked at spacecraft
 perigee through the Deep Space Network.  Verbose descriptions of the
@@
 For us, the main data product of interest is the calibrated full frame
-image (FFI).  Each TESS camera is read out every 2 seconds.  To produce
-a manageable telemetric load, the resulting pixel values are averaged
-by the onboard computer into 30 minute exposures. An on-board cosmic
-ray mitigation algorithm is applied (CITE: BERTA-THOMPSON). Once
-transmitted to the ground, the raw images are calibrated by the
-Science Processing Operations Center.  The calibration process
-includes an overscan, bias, and dark current correction, and also
-divides out a flat field.  Details are discussed by
-\citet{clarke_kepler_2017}, and the resulting science data products
+image (FFI).  Each TESS camera is read out every 2 seconds.  To
+produce a manageable telemetric load, the resulting pixel values are
+averaged by the onboard computer into 30 minute exposures. An on-board
+cosmic ray mitigation algorithm is applied \citep[][\S
+5.1]{vanderspek_2018}. Once transmitted to the ground, the raw images
+are calibrated by the Science Processing Operations Center.  The
+calibration process includes an overscan, bias, and dark current
+correction, and also divides out a flat field.  Details are discussed
+by \citet{clarke_kepler_2017}, and the resulting science data products
 are described by \citet{tess_data_product_description_2018}.
 
-We begin our analysis using the calibrated images, their uncertainty
-maps, and their associated headers.  The spacecraft has four cameras,
-and each camera has four CCDs.  In the following analysis, all
-image-level operations are thus performed on the images for each CCD,
-so that at any instant of time there are 16 independent images
-undergoing analysis.
-
-While we performed numerous initial tests on the first sectors of data,
-by geometric coincidence Sectors 1--5 were pointed away from the galactic plane.
-Less than 2\% of the CDIPS target star sample
-was therefore observed in the first five TESS sectors.
-Though a few interesting clusters are present ({\it e.g.}, Blanco~1, NGC~2516, NGC~1901),
-for the time being we opted to focus on sectors in which there were stars
-of interest for our intended science.
-These begin in Sector 6 (2018-12-12, spacecraft orbit \#19).
+We perform our processing using the calibrated images, their
+uncertainty maps, and their associated headers.  The spacecraft has
+four cameras, and each camera has four CCDs.  In the following
+analysis, all image-level operations are thus performed on the images
+for each CCD, so that at any instant of time there are 16 independent
+images that require analysis.
+
+While we performed numerous initial tests on the first sectors of
+data, by geometric coincidence Sectors 1--5 were pointed away from the
+galactic plane.  Consequently, less than 2\% of the CDIPS target star
+sample was observed in the first five TESS sectors.  Though a few
+interesting clusters are present in these observations ({\it e.g.},
+Blanco~1, NGC~2516, NGC~1901), for the present work we opted to focus
+on sectors in which there were more stars of interest for our intended
+science.  These begin in Sector 6 (2018-12-12, spacecraft orbit \#19).
 For this run of processing, they conclude at the end of Sector 7
@@
 
-\subsection{Image Preparation, Background Removal, \& Meta-Data Collection}
+\subsection{Image Preparation \& Background Removal}
 \label{subsec:preparation}
+
+Before we can perform any kind of photometry, a few janitorial tasks
+are required.
+First, we convert the calibrated image from MAST into a
+single-extension FITS image, and trim to remove virtual rows and
+columns using the \texttt{SCIROWS}, \texttt{SCIROWE}, \texttt{SCCSA},
+and \texttt{SCCED} header values.
+
+In order to pre-emptively address the background variations present in
+some frames due to scattered light from the Earth and Moon
+\citep[see][\S 7.3.1--7.3.4]{vanderspek_2018}, we then estimate and
+subtract the large-scale background.  We do this by temporarily
+masking out pixels more than $2\sigma$ from the image median, and then
+pass a $48\times48$ median box filter over each pixel in the image,
+with reflective boundary conditions.  We blur the resulting background
+estimate with a gaussian kernel, which produces a smooth background
+estimate for each image.  These steps also remove a low-level
+vignetting present in the corners of many images, which remains even
+after flat-fielding \citep[see][\S 7.3.5]{vanderspek_2018}.  With the
+exception of scattered-light caustics, which remain over small areas
+of less than 10\% of the frames, our ad-hoc procedure seems to
+adequately remove large spatial scale scattered light patches.
+
+% We found this background subtraction step to be particularly important
+% in our subsequent difference imaging analysis. In its absense, the
+% scattered light artifacts could introduce erroneous residuals into the
+% kernel solution used to match reference and target images.  Including
+% this step mitigated such effects, and helped produce clean
+% subtractions.  Even after subtraction, a small fraction of frames also
+% show sharp features (caustics) below our median box filter's size
+% scale.  Such features may affect flux measurements at specific times
+% in a small subset of light curves.
+
+After subtracting the background, we mask out saturated stars using a
+fixed saturation level of $8\times10^4\,{\rm ADU}$. This value was
+chosen based on the onset of bleeding charge trails in the images, and
+is slightly greater than the expected saturation level quoted by
+\citet{vanderspek_2018}.  As described by \citet{Pal_2009}, our masks
+are metadata to the image, and are only applied to the pixel values
+during the specific image processing steps in which they are necessary
+({\it e.g.}, convolution). We also extend the masks beyond purely
+saturated pixels to ``bloomed'' pixels horizontally and vertically
+adjacent to the saturated pixels (see Figure~6 of \citealt{Pal_2009}).
+
+Finally, for frames with the \texttt{DQUALITY} bit-flag corresponding
+to the ``momentum dumps'' and ``coarse pointing modes'' described by
+\citet{vanderspek_2018}, we omit the entire frame.  This removes on
+average a few frames per sector. Through visual inspection, we see
+that the stars on these frames are extremely smeared, and are unlikely
+to produce useful science data.  In addition, we use the
+sector-specific data release notes\footnote{\url{
+  archive.stsci.edu/tess/tess_drn.html}} to identify further times
+with anomalous spacecraft performance, which we omit from
+consideration.
+For Sectors 6 and 7, this included three days at the beginning of
+Sector 6 dedicated to acquiring pixel response function data, and no
+additional gaps in Sector 7.
+%For Sectors 1 through 5, these
+%include coarse pointing windows from orbits 10, 13, 14, and an
+%instrumetal anomaly window in orbit 15.
+% For Sectors 6 through 8, these include three days at the beginning of
+% Sector 6 dedicated to acquiring pixel response function data, and also
+% about three days during Sector 8 lost to an instrument anomaly.
+
+\subsection{Meta-Data Collection \& WCS verification}
+\label{subsec:metadatacollection}
 
@@
 
-Before we can perform any kind of photometry, a few janitorial tasks
-are required.
-
-First, we trim the images.  We convert the calibrated image from MAST
-into a single-extension FITS image, trimmed to remove virtual rows and
-columns using the \texttt{SCIROWS}, \texttt{SCIROWE}, \texttt{SCCSA},
-and \texttt{SCCED} header values.
-
-In order to pre-emptively address the background
-variations present in some frames due to scattered light from the
-Earth and Moon \citep[see][\S 7.3.1--7.3.4]{vanderspek_2018},
-we then estimate and subtract the large-scale background.
-We do this by
-temporarily masking out pixels more than $2\sigma$ from the image median,
-and then pass a $48\times48$ median box filter over each pixel in
-the image, with reflective boundary conditions. 
-We blur the resulting background estimate with a gaussian kernel,
-which produces a
-smooth background estimate for each image.  These steps also remove
-a low-level vignetting
-present in the corners of many images, which remains even after
-flat-fielding \citep[see][\S 7.3.5]{vanderspek_2018}.
-With the exception of scattered-light caustics, which remain in small
-areas of less than 10\% of the frames, this ad-hoc procedure removes
-large spatial scale scattered light patches.
-
-% We found this background subtraction step to be particularly important
-% in our subsequent difference imaging analysis. In its absense, the
-% scattered light artifacts could introduce erroneous residuals into the
-% kernel solution used to match reference and target images.  Including
-% this step mitigated such effects, and helped produce clean
-% subtractions.  Even after subtraction, a small fraction of frames also
-% show sharp features (caustics) below our median box filter's size
-% scale.  Such features may affect flux measurements at specific times
-% in a small subset of light curves.
-
-After subtracting the background, we mask out saturated stars using a
-fixed saturation level of $8\times10^4\,{\rm ADU}$. This value was
-chosen based on the onset of visible trails of bleeding charge, and is
-slightly greater than the expected saturation level quoted by
-\citet{vanderspek_2018}.  As described by \citet{Pal_2009}, our masks
-are metadata to the image, and are only applied to the
-pixel values during the specific image processing steps in which they
-are necessary ({\it e.g.}, convolution). We also extend the masks
-beyond purely saturated pixels to ``bloomed'' pixels horizontally and
-vertically adjacent to the saturated pixels (see Figure~6 of \citealt{Pal_2009}).
-
-Finally, for frames with the \texttt{DQUALITY} bit-flag corresponding
-to the ``momentum dumps'' and ``coarse pointing modes'' described by
-\citet{vanderspek_2018}, we omit the entire frame.  This removes
-on average a few frames per sector. Through visual inspection, we see
-that the stars on these frames are extremely smeared, and are unlikely
-to produce useful science data.
-In addition, we use the sector-specific data release
-notes\footnote{\url{ archive.stsci.edu/tess/tess_drn.html}} to
-identify further times with anomalous spacecraft performance,
-which we omit from consideration.
-%For Sectors 1 through 5, these
-%include coarse pointing windows from orbits 10, 13, 14, and an
-%instrumetal anomaly window in orbit 15.
-For Sectors 6 through 8, these include three days at the beginning of
-Sector 6 dedicated to acquiring pixel response function data, and also
-about three days during Sector 8 lost to an instrument anomaly.
-%FIXME for sectors 6 thru 8
-
-Having prepared the images, we perform some initial analysis steps
-to produce metadata
-needed during image subtraction.
+Having prepared the images, we perform some initial analysis steps to
+produce metadata needed during image subtraction.
 
 First, we use \texttt{fistar} to perform source extraction on bright
-stars in each image.
-uring the initial source
-extraction, we also fit elongated gaussians to the bright stars,
-yielding the shape parameters $(s,d,k)$, where the flux as a function
-of position is assumed to take the form
+stars in each image.  During the initial source extraction, we also
+fit elongated gaussians to the bright stars, yielding the shape
+parameters $(s,d,k)$, where the flux $f$ as a function of position
+$(x,y)$ in the CCD image plane is assumed to take the form
 \begin{align}
-  f_{\rm elong}(\vec{x}) &= B + A \exp \{ -0.5 \times ( 
+  f(x,y) &= B + A \exp \{ -0.5 \times [
     s(\Delta x^2 + \Delta y^2) + \\
@@
     k(2\Delta x \Delta y)
-  )  \},
+  ]  \},
 \end{align}
-for $\Delta x = x-x_0$, and $\Delta y = y - y_0$.  For a nearly
-circular shape profile, the sharpness $s$ is related to the FWHM as
-${\rm FWHM} \approx 2.35\sqrt{s}$ \citep[{\it e.g.},][]{Pal_2009}.
-These shape parameters are later used when selecting an astrometric
-reference (\S~\ref{subsec:imagesubtraction}).  We note that the fast
-focal ratio of the TESS cameras introduces significant comatic
-aberrations to the images: stars closer to the center of the field are
-more round, while stars towards the edges are more triangular.
+for $(x_0,y_0)$ arbitrary reference positions,
+$\Delta x = x-x_0$, $\Delta y = y - y_0$, and $A$ and $B$ arbitrary
+flux-scaling constants.
+For a nearly circular shape profile, the sharpness $s$ is related to
+the FWHM as ${\rm FWHM} \approx 2.35\sqrt{s}$ \citep[{\it
+e.g.},][]{Pal_2009}.  These shape parameters are later used when
+selecting an astrometric reference frame
+(\S~\ref{subsec:imagesubtraction}).  
+In agreement with what is obvious upon visual inspection, this 
+fitting process shows that stars closer to the
+center of each camera's field are round, while
+stars near the field edges are more triangular.
 
@@
 positions) was consistently a factor of 1.5-2 times higher in our WCS
-solutions than in those given by SPOC (perhaps attributable to the
-algorithm used to select stars and measure their positions).
+solutions than in those given by SPOC.  This was perhaps because
+we did not invest major amounts of time developing a robust
+algorith to select non-blended stars of intermediate brightness before
+measuring their positions.
 
@@
 a combination of the CDIPS target stars ($G_{Rp} < 16$), and
-all Gaia-DR2 sources down to $G_{Rp} < 13$.  We use the expected
-projected of these sources to center the apertures in our photometry,
+all Gaia-DR2 sources down to $G_{Rp} < 13$.  We use the
+projected positions of these sources to center the apertures in our
+photometry,
 rather than attempting to detect the positions.  Such
-``forced-aperture photometry'' is preferable to performing source
-extraction in the crowded fields that are central in this work.  The
+``forced-aperture photometry'' is preferable to source
+extraction in the crowded fields that are central to this work.  The
 Gaia-DR2 epoch is J2015.5, so even the fastest-moving stars with
@@
 The astrometric residual is displayed for one photometric reference
-frame (to be described shortly) in
-Figure~\ref{fig:astromresid}.
-A few salient points can be made.
+frame in Figure~\ref{fig:astromresid}.
+The construction of this frame will be described shortly, however
+a few salient points can first be made.
 First, the typical median precision of the WCS solution is a bit below
@@
 pixels, respectively.}.
-The distribution has a outlier tail of saturated stars which were
-masked, and thus do not have measureable centroid positions.
+%The distribution has a outlier tail of saturated stars which were
+%masked, and thus do not have measureable centroid positions.
 The errors are typically largest in the corners of the field of view,
@@
 
-Finally, we use \texttt{fiphot} to perform aperture photometry on the
+As a final step of metadata collection, we use \texttt{fiphot}
+to perform aperture photometry on the
 bright stars from the
 source list, by summing the counts inside appropriately-weighted
-circular apertures centered on the projected positions from Gaia DR2. 
-The pixel weights $w_{x,y}$ are equal to the fraction of the pixel
+circular apertures centered on the projected positions. 
+The pixel weights are equal to the fraction of the pixel
 that falls within the aperture.  They are thus unity for pixels
 entirely within the aperture, and fractional along the aperture
-boundary (see \citealt{Pal_2009} Fig 17). 
+boundary. % (see \citealt{Pal_2009} Fig 17). 
 The background levels are measured in annuli around each aperture
-center.  The raw flux of the object after background removal is then
-(\citealt{Pal_2009} Eq 65)
-\begin{equation}
-  f = \sum_{x,y} w_{x,y} (I_{x,y} - B) = f_{\rm total} - B r_0^2.
-  \label{eq:simple_aperture_phot}
-\end{equation}
+center. 
+%The raw flux of the object after background removal is then
+%(\citealt{Pal_2009} Eq 65)
+%\begin{equation}
+%  f = \sum_{x,y} w_{x,y} (I_{x,y} - B) = f_{\rm total} - B r_0^2.
+%  \label{eq:simple_aperture_phot}
+%\end{equation}
 The resulting measurements, for instance of the background level of
-each aperture, and the number of ``good'' objects that are detected,
+each aperture, and the number of stars with ``good'' photometry,
 are later used to select photometric reference frames.
@@
 
+\subsubsection{History of image subtraction method}
 The core operation of ``classical'' image subtraction
@@
 target; for space-based data, the match might correct for spacecraft
-jitter, or thermal and corresponding PSF variations.
+jitter, or thermal and corresponding point-spread function (PSF)
+variations.
 The kernel, once applied to the high signal-to noise reference,
@@
     M_{xy} = (R \otimes K)_{xy} + B_{xy},
+    \label{eq:imagemodel}
 \end{equation}
@@
 background variations.
-We model the background separately, so we set $B_{xy}=0$.
+Since we modeled the background separately (\S~\ref{subsec:preparation}),
+we set $B_{xy}=0$.
 The convolution kernel $K$ is typically decomposed onto a
@@
 $D_{xy} = I_{xy} - M_{xy}$.
-For this work, the uncertainty in each target image pixel is
+For the present reduction, the uncertainty in each target image pixel was
 taken to be a constant.
@@
 It was reviewed and clarified by \citet{miller_optimal_2008}.
-The choice of how to decompose the kernel was further clarified by
+The choice of how to decompose the kernel was further explored by
 \citet{bramich_new_2008}, who showed that using a delta function
@@
 We perform the convolution using \texttt{ficonv}, and opt for
-the implementation of Bramich's method (see \citealt{Pal_2009} Section 2.8).
-
-For posterity, we note a few implementation details.
-We must select two ``reference frames'' for image subtraction:
-(1) the astrometric reference; (2) the photometric reference.
-
-To choose the astrometric reference, we search for frames with
-the largest and roundest stars (big $s$, small $d$ and $k$ values).
-We also require
-that the frame must minimal background noise, as measured in annuli
+the implementation of Bramich's method (see \citealt{Pal_2009} \S~2.8).
+
+\subsubsection{Astrometric registration}
+We now describe a few implementation details we used to make the
+above high-level picture work.
+First, we needed to select two ``reference frames'' for image subtraction:
+(1) the astrometric reference; and (2) the photometric reference.
+
+To choose the astrometric reference, we searched for frames with
+large, round stars (big $s$, small $d$ and $k$ values).
+We also required
+that the frame have minimal background noise, as measured in annuli
 around the bright stars selected in \S~\ref{subsec:preparation}.
-Finally, the astrometric reference frame must have, relative to the 
+Finally, the astrometric reference frame needed to have, relative to the 
 other frames being
 considered, a large number of detected sources.
-We sort the frames using these metrics, and then select the
+We sorted the frames using these metrics, and then selected the
 astrometric reference from successive intersections of each sorted
 list.
-Using the algorithm presented by \citet{pal_astrometry_2006}, we then
-use the \texttt{grtrans} tool to
-calculate an affine transformation that maps each calibrated frame
-to the astrometric reference.
-We use the flux-conserving interpolation
-scheme described by \citet{Pal_2009} to minimize photometric errors
-incurred during this step --
-standard bilinear or bicubic interpolation do not achieve flux
-conservation.  
-The largest component of the transformation is typically a translation,
-of order 2 arcseconds, or about 0.1 TESS pixels.
-%FIXME: EXPLAIN THIS BETTER
-
-The second reference frame is the
+
+We then
+used the \texttt{grmatch} and \texttt{grtrans} tools to
+compute and apply a spatial transformation of each calibrated frame
+to match the astrometric reference frame.
+The transformation is calculated using the measured source positions
+found in ~\S~\ref{subsec:metadatacollection},
+and the symmetric triangle point-matching scheme described
+by \citet[][~\S~2.5.2]{Pal_2009}.
+The transformation~--~a combination of rotation, dilation, and
+translation~--~typically moves stars by less than a pixel, since
+the TESS spacecraft is quite stable.
+The precision of the transformation is guaranteed by forcing 
+its unitarity $\Lambda$ to always be below 0.01, where 
+$\Lambda$ is defined by \citet[][~Eq.~54]{Pal_2009}.
+We reduced the photometric errors
+incurred during this step by using
+the flux-conserving interpolation
+scheme described by \citet{Pal_2009},
+which was necessary because polynomial interpolation schemes
+do not conserve stellar flux.
+
+\subsubsection{Photometric reference frame construction \& reference flux measurement}
+
+The second required reference frame is the
 photometric reference, which is used both to calculate the
@@
 reference flux for each star.  
-To minimize Poisson errors, our photometric reference is a median average of
-$N=50$ selected frames.
-The sub-frames are chosen to have low scatter in their photometry,
-and low background measurements, using the metadata collected
+To make it, we first chose 50
+sub-frames with low scatter in their photometry
+and low background measurements, according to the metadata collected
 in \S~\ref{subsec:preparation}.
-We convolve the 50 best candidate photometric references to the best
-photometric reference, and then perform a median combination of the
-frames to make the photometric reference.
+We then convolved these candidate photometric reference frame to the best
+frame, and performed a median average over the entire stack
+to make the photometric reference.
 
@@
 
-To measure the reference flux for each star, we go a bit further.
+Measuring the reference flux for each star is a slightly non-trivial
+operation.
 First, we perform forced simple aperture photometry to measure
@@
 masked out during the background measurement.
-If we were to stop here, {\it it would be a bad mistake}.
-The reference flux for faint stars would be overestimated, due to
+However if we were to stop here, {\it it would be a bad mistake}.
+The reference fluxes for faint stars would be overestimated, due to
 crowding.
@@
 be biased small, hindering exoplanet detection.
+
 Therefore, after performing simple aperture photometry on the 
-reference frame, we fit for an for aperture-size specific zero point
-that relates each star's catalog $T$-band magnitude to the
+reference frame, we fitted an aperture-size specific zero point
+between the catalog $T$-band magnitude of each star, and its
 measured flux.
-The $T$-band magnitude is calculated according to Equation~1 of 
-Stassun et al (2019, CITE).
-Crowding is minimzed down to Gaia's resolution limit.
+The $T$-band magnitude was calculated according to Equation~1 of 
+\citet{stassun_TIC8_2019}.
 We then use the known catalog magnitude to predict the expected
-photometric reference flux.
-
-The final instrumental flux values we report (for example,
-the \texttt{IFL1} column) are similar to \citealt{Pal_2009} Equation~83:
+reference flux for each star.
+In effect, this minimizes crowding down to Gaia's resolution limit of
+$\approx$1$''$, rather than the TESS limit of $\approx$20$''$.
+
+Following \citet{Pal_2009}~Equation~83,
+the final instrumental flux values $f$ we report\footnote{For example,
+the \texttt{IFL1} column} are then equal to
 \begin{align}
-f &= f_{\rm subtracted} + f_{\rm reference} \\
+f &=  f_{\rm reference} + f_{\rm subtracted} \\
 &=
-\frac{1}{|| K ||_1^2} \sum_{x,y} S_{x,y} (w \otimes K)_{x,y}
+g \left(T_{\rm cat} \right)
 +
-g \left(T_{\rm cat} \right),
+\frac{1}{|| K ||_1^2} \sum_{x,y} D_{x,y} (w \otimes K)_{x,y}.
 \label{eq:ism_flux_measurement}
 \end{align}
-for the subtracted image $S$, which is equal to $I -  R\otimes K$,
-where $I$ is the original image transformed to the astrometric
+The function $g$ takes as input the target star's
+catalog magnitude $T_{\rm cat}$, and returns the reference flux.
+Its coefficients have been fit per the procedure  just discussed.
+The difference image $D$ is equal to $I -  R\otimes K$,
+where as in Equation~\ref{eq:imagemodel}, $I$ is the target image 
+transformed to the astrometric
 reference, $R$ is the photometric reference, and $K$ is the convolution
 kernel.
-The weights $w$ from the circular aperture mask are matched to
-the image convolution.
-The function $g$ takes as input the target star's
-catalog magnitude $T_{\rm cat}$, and returns the reference flux.
-Its coefficients have been fit per the procedure 
-discussed in the preceding paragraph.
-%FIXME: derive this equation. why exactly does this work?
-
+The weights $w$ from the circular aperture mask are included in
+the convolution.
+The norm $|| K ||_1$ is defined by \citet{Pal_2009}~Equation~81.
+
+\subsection{Choice of convolution kernel}
 A few brief notes on the algorithm to actually solve for the 
 coefficients to the convolution kernel.
-The procedure implemented in \texttt{ficonv} is to grid up
+The procedure implemented in \texttt{ficonv} is to grid
 the image, and within each grid element find the brightest non-saturated
@@
 coefficients of the kernel, by minimizing
-Equation~\ref{eq:chisq_conv}.
+Equation~\ref{eq:chisq_conv} over the sum of all stamps.
 
@@
 We performed a grid-search to tune these parameters, in
-which our main metrics for success included the measured RMS as
+which our metrics for success included the measured RMS as
 a function of magnitude, and also the recovered SNR of transits from
-known TOIs (CITE: Guerrero et al in prep 2019).
+the catalog of known TOIs (TESS Objects of Interest; N.~Guerrero, in prep).
 
@@
 transit SNR.  
-For computational expediency, we therefore chose a $(7\times 7)$ kernel with 
-second-order spatial polynomial weights in the basis functions.
+For computational expediency, we therefore chose a single
+$(7\times 7)$ kernel with 
+second-order spatial polynomial weights in the basis functions for the
+remainder of our reduction.
 However, we caution that within our parameter-tuning experiments, the 
@@
 which in a few 
-cases would have lead to non-detections of objects near the noise floor.
+cases led to non-detections of transit signals near the noise floor.
 In the longer term, developing an image-subtraction method that marginalizes 
@@
 With a kernel selected, and the convolution and subtraction performed, 
-we calculate the instrumental fluxes on each frame per 
+we calculate the instrumental fluxes for each frame per 
 Equation~\ref{eq:ism_flux_measurement}. 
-We do this with three different aperture sizes: for this work, circles
+We did this with three different aperture sizes: for this work, circles
 of radii 1 pixel, 1.5 pixels, and 2.25 pixels.
 These sizes were chosen to roughly span the range of optimal aperture
-sizes for stars in our sample, as calcuated in the pre-flight
-\citet{Sullivan_et_al_2015} work.
-To finally convert from a list of 
-sources on each frame to a list of flux values at any given time, we use the 
+sizes for stars in our sample, as calcuated from the pre-flight
+\citet{Sullivan_et_al_2015} noise model.
+Finally, to convert from a list of 
+flux measurements for each source on a frame to a list of flux values
+at any given time, we used the 
 \texttt{grcollect} transposition tool.
@@
 approach adopted by the HAT group typically proceeds in a few
-sequential stages (see discussions from {\it e.g.}
+sequential stages (previously discussed by {\it e.g.}
 \citealt{bakos_2010,huang_high-precision_2015,zhang_precision_2016}).
-Given the heritage of our pipeline, we briefly discuss these, and then
-explain why we omit most of the steps described.
+Given the heritage of our pipeline, we briefly note which of these concepts
+were used in this reduction.
 
@@
 CCD temperature, or perhaps some measure of the scatter in the spacecraft
-pointing (CITE: Vanderburg 2019).
+pointing \citep{vanderburg_hr858_2019}.
 
@@
 
+%TODO TODO TODO FIXME LEFT OFF EDITS HERE
 %FIXME TURGID PROSE
@@
 		Black: $G_{\rm Rp}<13$ field stars.  Blue: $G_{\rm Rp}<16$
-		target stars.  The target stars are mostly near the galactic
-		plane.
+		target stars.  Target stars are mostly near the galactic
+		plane. The data for Sectors 6 and 7 cover about one-sixth of
+		the galactic plane.
 		\label{fig:lcgalactic}
@@
 
-We remind the reader that our goal in creating this sample was
+We remind the reader that our goal in creating our target catalog was
 completeness, rather than fidelity. The \citet{dias_proper_2014} stars
@@
 probability exceeding 50\%.  To create cleaner sub-samples, we advise
-use of the \texttt{CDEXTCAT} header keyword, which can be
-cross-matched against the original source catalog to obtain the
+use of the \texttt{CDEXTCAT} header keyword, which can be used
+to merge against the original source catalog to obtain the
 membership probabilities claimed by the original catalog.
@@
 The planet candidate chosen for these figures
-(Gaia DR2 \texttt{5541111035713815552} = TIC \texttt{134528212}) was
+(Gaia-DR2 \texttt{5541111035713815552} = TIC \texttt{134528212}) was
 chosen for the demonstration in part because it passes all

### 2019-07-04 drivers/paper_plot_all_figures.py
add plot_avg_acf

@@ -5,7 +5,7 @@ execution environment: cdips, + pipe-trex .pth file in
 python -u paper_plot_all_figures.py &> logs/paper_plot_all.log &
 """
 from glob import glob
-import datetime, os, pickle, shutil
+import datetime, os, pickle, shutil, subprocess
 import numpy as np, pandas as pd
 import matplotlib.pyplot as plt
 
@@ -21,6 +21,7 @@ from astrobase import lcmath
 from astrobase.lcmath import phase_magseries
 
 from aperturephot import get_lc_statistics
+import lcstatistics as lcs
 
 from cdips.utils import tess_noise_model as tnm
 
@@ -33,10 +34,14 @@ from collections import Counter
 
 OUTDIR = '/nfs/phtess2/ar0/TESS/PROJ/lbouma/cdips/results/paper_figures/'
 CLUSTERDATADIR = '/home/lbouma/proj/cdips/data/cluster_data'
+LCDIR = '/nfs/phtess2/ar0/TESS/PROJ/lbouma/CDIPS_LCS/'
 
 def main():
 
     sectors = [6,7]
+
+    # fig N: average autocorrelation fn of LCs
+    plot_avg_acf(sectors, overwrite=1, cleanprevacf=True)
 
     # fig N: 3x2 quilty of phased PC
     plot_quilt_PCs(overwrite=1)
@@ -91,6 +96,141 @@ def main():
 def savefig(fig, figpath):
     fig.savefig(figpath, dpi=450, bbox_inches='tight')
     print('{}: made {}'.format(datetime.utcnow().isoformat(), figpath))
+
+
+def plot_avg_acf(sectors, size=10000, overwrite=0, percentiles=[25,50,75],
+                 cleanprevacf=True):
+
+    outpath = os.path.join(OUTDIR, 'avg_acf.png')
+    if os.path.exists(outpath) and not overwrite:
+        print('found {} and not overwrite; return'.format(outpath))
+        return
+
+    #
+    # collect acfs for however many random LCs passed
+    #
+    np.random.seed(42)
+    lcpaths = []
+    for sector in sectors:
+        lcpaths.append(
+            np.random.choice(
+                glob(os.path.join(LCDIR, 'sector-{}'.format(sector),
+                                  'cam?_ccd?', 'hlsp_*llc.fits')),
+                size=size,
+                replace=False
+            )
+        )
+    lcpaths = nparr(lcpaths).flatten()
+
[…]

### 2019-07-04 paper/ms.tex

@@
 
-\subsection{Summary of selected stars}
+\subsection{Summary of target stars}
 \label{subsec:ocmgsummary}
@@
     Details are given in \S~\ref{sec:method}.
+    %TODO: add latex section numbers!
+    %TODO: do FORCED aperture photomery on differenced images
+    %TODO: improve text generally
 	\label{fig:pipeline}
@@
 
-We reduced the TESS images to light curves using an image subtraction
-approach.  The overall method is in the spirit of the reduction
-pipelines developed by \citet{Pal_2009},
+To reduce the TESS images to light curves, we adopted an image
+subtraction approach.  The overall method is in the spirit of the
+reduction pipelines developed by \citet{Pal_2009},
 \citet{huang_high-precision_2015}, \citet{soares-furtado_image_2017}
@@
 \texttt{pipe-trex}, under development primarily for the HATPI project
-(\url{hatpi.org}).  This code is available
+(\url{hatpi.org}).  The code is available
 online\footnote{\url{github.com/waqasbhatti/pipe-trex}, commit
@@
 
-\subsection{Image Preparation \& Background Removal}
+\subsection{Image preparation \& background removal}
 \label{subsec:preparation}
@@
 
-\subsection{Meta-Data Collection \& WCS verification}
+\subsection{Metadata collection \& WCS verification}
 \label{subsec:metadatacollection}
@@
 
-\subsection{Image Subtraction}
+\subsection{Image subtraction}
 \label{subsec:imagesubtraction}
@@
 the final instrumental flux values $f$ we report\footnote{For example,
-the \texttt{IFL1} column} are then equal to
+the \texttt{IFL1} column.} are then equal to
 \begin{align}
@@
 
-\subsection{Light Curve Detrending}
+\subsection{Light curve detrending}
 \label{subsec:lcdetrending}
 
-\begin{figure*}[t]
+\begin{figure}[!t]
 	\begin{center}
 		\leavevmode
-		\includegraphics[width=0.6\textwidth]{epdparams_vs_time.png}
+		\includegraphics[width=0.47\textwidth]{epdparams_vs_time.png}
 	\end{center}
@@
 		parameters, and the measured background value.
-		Most of the apparent variability is instrumental: see
-		\S~\ref{sec:flux_vs_external_parameters}.
+		Most of the apparent variability is instrumental.
 		\label{fig:external_parameter_timeseries}
 	}
-\end{figure*}
-
-The preceding steps produce light curves that include both instrumental
-systematics as well as astrophysical variability.  The detrending
-approach adopted by the HAT group typically proceeds in a few
-sequential stages (previously discussed by {\it e.g.}
-\citealt{bakos_2010,huang_high-precision_2015,zhang_precision_2016}).
-Given the heritage of our pipeline, we briefly note which of these concepts
-were used in this reduction.
+\end{figure}
+
+The preceding steps produce light curves that include both
+instrumental systematics as well as astrophysical variability.  The
+detrending approach adopted by the HAT group to remove systematic
+variability typically proceeds in a few sequential stages, as
+discussed by {\it e.g.} \citet{bakos_2010}, \citet{huang_high-precision_2015},
+and \citet{zhang_precision_2016}.
 
@@
 position, sub-pixel position, and optionally catalog magnitude and
-color \citep[][Sec.~5.5]{zhang_precision_2016}.
+color \citep[][\S~5.5]{zhang_precision_2016}.
 
@@
 known to affect the stellar flux measurements (EPD,
-\citealt[][~Appendix]{bakos_2010}).  For ground-based data this may include zenith
-angle, or changing PSF parameters.  For TESS data, this might include
-CCD temperature, or perhaps some measure of the scatter in the spacecraft
-pointing \citep{vanderburg_hr858_2019}.
+\citealt[][]{bakos_2010}).  For ground-based data this may
+include zenith angle, or changing PSF parameters.  For TESS data, this
+might include CCD temperature, or the angles of the Moon and Earth
+relative to each camera's boresight.
+Some example ``external'' parameters that we
+include with our light curves are shown as functions of time in
+Figure~\ref{fig:external_parameter_timeseries}.
 
 The final step is to then decorrelate the measured brightnesses of
-stars against each other (TFA, \citealt{kovacs_trend_2005}).  
-This accounts for variations due to unknown systematic
-instrument changes that affect many stars.
-
-%TODO TODO TODO FIXME LEFT OFF EDITS HERE
-%FIXME TURGID PROSE
-In \S~\ref{sec:flux_vs_external_parameters}, we show that the
-``external parameter'' dependence visible in the TESS data is rather
-complex: ordinary linear model-fitting, as well as an initial attempts
-at non-linear model fitting, are poor descriptions of the data.  
-In a similar vein ``magnitude-fitting'' is minimally justified, given
-how the TESS magnitudes correlate against these external parameters.
-We go on to show (\S~\ref{sec:tfa_is_good_enough}) that a plausible
-detrending approach for the purpose of transit discovery is to simply
-decorrelate against other nearby stars with standard TFA.
-
-\subsubsection{Flux versus external parameters}
-\label{sec:flux_vs_external_parameters}
-
-% \begin{figure*}[t]
-%     \begin{center}
-% 		\includegraphics[height=0.9\textheight]{mag_vs_epdparams.png}
-%     \end{center}
-%     \vspace{-0.5cm}
-%     \caption{
-%       {\bf Flux as a function of ``external parameters'' for four
-%       representative stars.} The left two columns are stars at the
-%       corner of a camera's field; the right two columns are from the
-%       centers.
-%       Each row shows a different parameter along the $x$-axis, given
-%       in text at the bottom right of each subplot.
-%       ``Hooks'' are common features in flux as a function of
-%       temperature and centroid position.
-%       \S~\ref{sec:flux_vs_external_parameters} gives a verbose
-%       description.
-%      \label{fig:flux_vs_external_parameters}
-%     }
-% \end{figure*}
-
-The traditional approach to EPD is to fit and
-subtract a model for the magnitudes $m$ of the form
-\begin{equation}
-  m = {\rm const.} + \sum_i c_i \theta_i,
-  \label{eq:classical_EPD}
-\end{equation}
-where $\vec{\theta}$ is a vector of parameters such as the shape
-parameters $(s,d,k)$, their products $(s^2, s\cdot d, d^2, \ldots)$,
-the temperature $T$ of the instrument or environment\footnote{ We used
-the temperature from the on-chip aluminum-copper sensor measurements
-included in the engineering
-data: \url{archive.stsci.edu/missions/tess/engineering/}.  },
-the centroid positions $(x,y)$, the fractional part of the
-centroid positions $(\{x\},\{y\})$, and any other parameters that are
-expected\footnote{ The fractional centroid positions might matter
-because intra-pixel quantum efficiency variations could affect the
-measured stellar brightness.  The varying temperature $T$ of the CCD
-electronics might matter.  } to correlate strongly with the observed
-flux.  The coefficients $c_i$ are calculated through linear
-least-squares, and subtracted to produce ``EPD'' light curves.
-
-The premise of this model is that the correlations between the
-magnitudes and the external parameters are linear.  For ground-based
-CCD data (e.g., HATNet, HATS, and Nikon DSLRs), \citet{bakos_2010} and
-\citet{zhang_precision_2016} have verified that this model is a
-good description to the data.
-To discern whether such a model extends to the TESS data, we examined
-scatter plots of each parameter, as a function of all the other
-parameters.  We also examined plots of each parameter as a function of
-time.  A few prominent trends were present.
-
-\begin{enumerate}
-
-\item {\it Flux vs.\ time}. Most of the light curves we examined showed a secular
-    drift with amplitude $0.01\,{\rm mag}$ over the timescale of each
-    orbit.  Sharper trends (``hooks'') at the beginning of each orbit
-    seemed to be less prominent for stars at the corners of the fields
-    than stars at the center.  The periodicity incurred by the
-    2.5$\,{\rm day}$ momentum dumps was also noticeable in more of the
-    light curves at the center of the field than at the corners.
-
-\item {\it Flux vs.\ centroid positions}. The flux as a function of
-  centroid position often showed non-linear ``hooks''
-    %(see Figure \ref{fig:flux_vs_external_parameters}).
-    Most of the data points from a given orbit reside at a given
-    level, but about 10\% are in a tail. This was seen in light curves
-    all across the TESS field of view.
-
-\item {\it Flux vs.\ temperature} exhibited similar hooks, with most of
-  the flux values residing at a particular level, and perhaps 10\%
-    following a non-linear path (often resembling the Nike ``swoosh'')
-    away from the bulk of points.
-
-\item {\it Flux vs.\ shape parameters}.  For light curves in the corner
-  of the field of view, similar hooks are present in flux {\it vs.}
-    $(s,d,k)$, though the hooks are less sharp.  In the center of the
-    field of view, gaussian ellipses are a better description of the
-    flux {\it vs.} the shape parameters.
-
-\end{enumerate}
-
-Considering the timeseries of parameters other than flux 
-(Figure~\ref{fig:external_parameter_timeseries}):
-
-\begin{enumerate}
-
-\item {\it Centroid positions vs\ time}.  The main variability in the
-  centroid positions as a function of time is a secular drift, that is
-    reset every orbit.  The 2.5 day momentum wheel dump is
-    superimposed on this secular drift, and has smaller amplitude than
-    the drift.
-
-\item {\it Temperature vs.\ time}.  The main variability in temperature
-  {\it vs.} time is a secular drift of the same timescale as that for
-    the centroid positions timeseries.
-
-\item {\it Shape parameters vs.\ time}.  The main variability in the
-  shape parameters as a function of time is the 2.5 day momentum wheel
-    dump periodicity, with hooks before each momentum dump.
-
-\item {\it Background value vs.\ time}.  The background is typically stable, 
-except when scattered light from the Earth or Moon enters the frame (visible 
-towards the end of each orbit in 
-Figure~\ref{fig:external_parameter_timeseries}).
-
-\end{enumerate}
-
-Given the characteristics of the variability, a linear model of the
-form given in Equation~\ref{eq:classical_EPD} is not applicable.  To
-fit out the correlations between flux and parameters which most
-commonly exhibited ``hooks'', we explored fitting a parametric open
-curve (an $N$-dimensional B-spline, \citealt{dierckx_curve_1996}) to
-the flux, centroid positions, and temperatures simultaneously.  We
-selected the number of knots through brute-force, by calculating
-$\chi^2$ for the model fit over a grid of possible knots, and
-minimizing the Bayesian Information Criterion.  Though this approach
-showed some initial promise, even with ``optimal'' knot-selection (in
-the BIC sense) it introduced undesirable residuals in the light curves,
-and also distorted transits.
-One thought that we did not try but may explore in future work
-is to use the decorrelate against the scatter of the quartnerion 
-time-series (CITE: Vanderburg, 2019).
+stars against each other (TFA, \citealt{kovacs_trend_2005}).  This
+accounts for variations due to unknown systematic instrument changes
+that affect many stars.  This latter step is effectively a principle
+component analysis of all the light curves, in which the components
+are chosen as a subset of the light curves.
+In this sense TFA is similar to the PDC-MAP and ARC2 methods
+\citep{smith_pdc_2012,aigrain_robust_2017} except that these latter
+two methods are much more careful in their choice of basis vectors.
+
+We explored the possibility of fitting linear models of flux as
+functions of {\it e.g.,} temperature, shape parameters, centroid
+positions, and stellar colors.  We also briefly explored non-linear
+model fitting using $N$-dimensional B-splines to fit the flux,
+centroid positions, and temperatures simultaneously
+\citep{dierckx_curve_1996}.  The linear models typically underfit the
+light curves, particularly during the large shifts that happen as the
+spacecraft nears perigee.  The non-linear models showed some promise,
+but often seemed to overfit stellar variability signals.  One thought
+that we did not try but may explore in future work is to decorrelate
+against the scatter of the spacecraft quartnerion time-series
+\citep{vanderburg_hr858_2019}.
 
 Given these complications, for the time being we omit the step of
-``detrending'' as a function of external parameters. To
-enable further exploration of the issue, we include all the necessary
-vectors of {\it e.g.}, centroid positions, temperatures, and shape
-parameters in our reported light curves.
-
-\subsubsection{Trend filtering algorithm}
-\label{sec:tfa_is_good_enough}
+``detrending'' as a function of external parameters. To enable further
+exploration of the issue, we include all the necessary vectors of {\it
+e.g.}, centroid positions, temperatures, and shape parameters in our
+reported light curves.
+
+% In \S~\ref{sec:flux_vs_external_parameters}, we describe the
+% ``external parameter'' dependence visible in our reduction of
+% the TESS data.
+% Ordinary linear model-fitting, as well as an initial attempts
+% at non-linear model fitting, are poor descriptions of the data.  
+% In a similar vein ``magnitude-fitting'' is minimally justified, given
+% how the TESS magnitudes correlate against these external parameters.
+% We go on to show (\S~\ref{sec:tfa_is_good_enough}) that a plausible
+% detrending approach for the purpose of transit discovery is to simply
+% decorrelate against other nearby stars with standard TFA.
+%
+
+% \subsubsection{Flux versus external parameters}
+% \label{sec:flux_vs_external_parameters}
+% 
+% 
+% % \begin{figure*}[t]
+% %     \begin{center}
+% % 		\includegraphics[height=0.9\textheight]{mag_vs_epdparams.png}
+% %     \end{center}
+% %     \vspace{-0.5cm}
+% %     \caption{
+% %       {\bf Flux as a function of ``external parameters'' for four
+% %       representative stars.} The left two columns are stars at the
+% %       corner of a camera's field; the right two columns are from the
+% %       centers.
+% %       Each row shows a different parameter along the $x$-axis, given
+% %       in text at the bottom right of each subplot.
+% %       ``Hooks'' are common features in flux as a function of
+% %       temperature and centroid position.
+% %       \S~\ref{sec:flux_vs_external_parameters} gives a verbose
+% %       description.
+% %      \label{fig:flux_vs_external_parameters}
+% %     }
+% % \end{figure*}
+% 
+% The traditional approach to EPD is to fit and
+% subtract a model for the magnitudes $m$ of the form
+% \begin{equation}
+%   m = {\rm const.} + \sum_i c_i \theta_i,
+%   \label{eq:classical_EPD}
+% \end{equation}
+% where $\vec{\theta}$ is a vector of parameters such as the shape
+% parameters $(s,d,k)$, their products $(s^2, s\cdot d, d^2, \ldots)$,
+% the temperature $T$ of the instrument or environment\footnote{ We used
+% the temperature from the on-chip aluminum-copper sensor measurements
+% included in the engineering
+% data: \url{archive.stsci.edu/missions/tess/engineering/}.  },
+% the centroid positions $(x,y)$, the fractional part of the
+% centroid positions $(\{x\},\{y\})$, and any other parameters that are
+% expected\footnote{ The fractional centroid positions might matter
+% because intra-pixel quantum efficiency variations could affect the
+% measured stellar brightness.  The varying temperature $T$ of the CCD
+% electronics might matter.  } to correlate strongly with the observed
+% flux.  The coefficients $c_i$ are calculated through linear
+% least-squares, and subtracted to produce ``EPD'' light curves.
+% 
+% The premise of this model is that the correlations between the
+% magnitudes and the external parameters are linear.  For ground-based
+% CCD data (e.g., HATNet, HATS, and Nikon DSLRs), \citet{bakos_2010} and
+% \citet{zhang_precision_2016} have verified that this model is a
+% good description to the data.
+% To discern whether such a model extends to the TESS data, we examined
+% scatter plots of each parameter, as a function of all the other
+% parameters.  We also examined plots of each parameter as a function of
+% time.  A few prominent trends were present.
+% 
+% \begin{enumerate}
+% 
+% \item {\it Flux vs.\ time}. Most of the light curves we examined showed a secular
+%     drift with amplitude $0.01\,{\rm mag}$ over the timescale of each
+%     orbit.  Sharper trends (``hooks'') at the beginning of each orbit
+%     seemed to be less prominent for stars at the corners of the fields
+%     than stars at the center.  The periodicity incurred by the
+%     2.5$\,{\rm day}$ momentum dumps was also noticeable in more of the
+%     light curves at the center of the field than at the corners.
+% 
+% \item {\it Flux vs.\ centroid positions}. The flux as a function of
+%   centroid position often showed non-linear ``hooks''
+%     %(see Figure \ref{fig:flux_vs_external_parameters}).
+%     Most of the data points from a given orbit reside at a given
+%     level, but about 10\% are in a tail. This was seen in light curves
+%     all across the TESS field of view.
+% 
+% \item {\it Flux vs.\ temperature} exhibited similar hooks, with most of
+%   the flux values residing at a particular level, and perhaps 10\%
+%     following a non-linear path (often resembling the Nike ``swoosh'')
+%     away from the bulk of points.
+% 
+% \item {\it Flux vs.\ shape parameters}.  For light curves in the corner
+%   of the field of view, similar hooks are present in flux {\it vs.}
+%     $(s,d,k)$, though the hooks are less sharp.  In the center of the
+%     field of view, gaussian ellipses are a better description of the
+%     flux {\it vs.} the shape parameters.
+%     
+% \end{enumerate}
+% 
+% Considering the timeseries of parameters other than flux 
+% (Figure~\ref{fig:external_parameter_timeseries}):
+% 
+% \begin{enumerate}
+% 
+% \item {\it Centroid positions vs\ time}.  The main variability in the
+%   centroid positions as a function of time is a secular drift, that is
+%     reset every orbit.  The 2.5 day momentum wheel dump is
+%     superimposed on this secular drift, and has smaller amplitude than
+%     the drift.
+% 
+% \item {\it Temperature vs.\ time}.  The main variability in temperature
+%   {\it vs.} time is a secular drift of the same timescale as that for
+%     the centroid positions timeseries.
+% 
+% \item {\it Shape parameters vs.\ time}.  The main variability in the
+%   shape parameters as a function of time is the 2.5 day momentum wheel
+%     dump periodicity, with hooks before each momentum dump.
+% 
+% \item {\it Background value vs.\ time}.  The background is typically stable, 
+% except when scattered light from the Earth or Moon enters the frame (visible 
+% towards the end of each orbit in 
+% Figure~\ref{fig:external_parameter_timeseries}).
+% 
+% \end{enumerate}
+% 
+% Given the characteristics of the variability, a linear model of the
+% form given in Equation~\ref{eq:classical_EPD} is not applicable.  To
+% fit out the correlations between flux and parameters which most
+% commonly exhibited ``hooks'', we explored fitting a parametric open
+% curve (an $N$-dimensional B-spline, \citealt{dierckx_curve_1996}) to
+% the flux, centroid positions, and temperatures simultaneously.  We
+% selected the number of knots through brute-force, by calculating
+% $\chi^2$ for the model fit over a grid of possible knots, and
+% minimizing the Bayesian Information Criterion.  Though this approach
+% showed some initial promise, even with ``optimal'' knot-selection (in
+% the BIC sense) it introduced undesirable residuals in the light curves,
+% and also distorted transits.
+% One thought that we did not try but may explore in future work
+% is to use the decorrelate against the scatter of the quartnerion 
+% time-series \citep{vanderburg_hr858_2019}.
+% 
+% Given these complications, for the time being we omit the step of
+% ``detrending'' as a function of external parameters. To
+% enable further exploration of the issue, we include all the necessary
+% vectors of {\it e.g.}, centroid positions, temperatures, and shape
+% parameters in our reported light curves.
 
 Since most of the external parameter dependence is shared between
-stars, we opt to decorrelate the flux timeseries of each star
-against other stars in the frame.
-We use the TFA algorithm proposed by
-\citet{kovacs_trend_2005}, which for self-consistency we reproduce
+stars, we opt instead to decorrelate the flux timeseries of each star
+against other stars in the frame.  We use the TFA algorithm proposed
+by \citet{kovacs_trend_2005}, which for self-consistency we describe
 here.
-The idea of the method is somewhat simpler than the PDCMAP
-algorithm used in the SPOC pipeline (CITE).
+
+The idea of the method is as follows.
 Suppose we have $M$ ``template stars'', which are a subsample of
@@
 The choice of number of template stars was discussed by
-\citet{Kovacs_et_al_2005}, and is another free parameter in
+\citet{kovacs_trend_2005}, and is another free parameter in
 the broad problem of light curve production.
-While it can be optimized by constructing and minimizing a BIC-like 
-quantity, a little overfitting is acceptable for our puposes.
+This choice is analogous to the issue of how many cotrending basis
+vectors to choose in PDC-MAP or ARC2 \citep{aigrain_robust_2017}.
+While the number of template stars can be optimized by constructing
+and minimizing a BIC-like quantity, a little overfitting is acceptable
+for our pupose of finding planetary transits.
 
@@
 
-\begin{figure*}[!t]
+\begin{figure}[!t]
 	\begin{center}
 		\leavevmode
-		\includegraphics[width=0.97\textwidth]{galacticcoords_cluster_field_star_positions.png}
+		\includegraphics[width=0.47\textwidth]{galacticcoords_cluster_field_star_positions.png}
 	\end{center}
@@
 	}
-\end{figure*}
+\end{figure}
 
@@
 Black stars are the field stars for which we performed photometry,
-but only to calibrate the cluster star sample.
+and of which a subset were used as template stars during TFA.
 The blue stars are the \numberlcs stars with light curves available
@@
 
-\subsubsection{Cluster membership provenance}.
+\subsubsection{Cluster membership provenance}
 
@@
 (1$\sigma$) to exist within the angular radius of the cluster.
-Mamajek~3 (32$\,$Ori) has only about 50 confirmed members
+Mamajek~3 (= 32$\,$Ori) has only about 50 confirmed members
 \citep{bell_32ori_2017}.
@@
 \paragraph{ACF statistics}
+TODO:
 ACF statistics before and after detrending(?)
 
-SNR of retrieved HJs.
+SNR of retrieved HJs?
 
@@
 
-Some stellar variability plots (perhaps of known stellar variables).
-
-Some focus on particular clusters.
+Some stellar variability plots (perhaps of known stellar variables)?
+
+Some focus on particular clusters?
 
@@
 rotators, and eclipsing binaries, we performed a few steps of
-post-processing on the light curve described in the preceding
-sections.  This processing was entirely independent of the data
-release, since it was quite specific to our own scientific interests.
+post-processing on the light curves.  This processing was done
+independently of the data release, since it was quite specific to our
+own scientific interests.  The code used to do this additional
+processing is also available
+online\footnote{\url{github.com/lgbouma/cdips}, commit
+\texttt{348eea7}.}.
 
@@
 If a peak is found with false alarm probability below $10^{-5}$, we
-consider the star ``variable'', and opt to detrend the light curve
+consider the star ``variable'', and opt to detrend the flux timeseries
 with robust penalized B-splines, which are splines with knot-length
@@
 in Appendix~\ref{appendix:vetreport}.
-
-The classifications we used assessed:
+When classifying these reports, we assessed:
 \begin{enumerate}
-    \item {\it Photometric variability classification}. Designations
+    \item {\it Morphology of photometric variability}. Designations
       include tags for planet candidates, eclipsing binaries,
@@
 \end{enumerate}
-The initial classifications were performed by LGB, with subsequent
-checking by JH and JNW.  The \texttt{TagSpaces} software was
-used~--~an extremely helpful tool for the purposes of easily assigning
-labels to documents.
+The initial classifications were performed by LGB, with possible
+planet candidates inspected by JH and JNW.  The \texttt{TagSpaces}
+software was used to easily assign labels to the documents.
 
@@
 
+Maybe JH or JNW could contribute these subsections?
+
 \subsection{The planet candidates require more observations}
@@
 be feasible}
-
-Lorem ipsum
 

### 2019-07-04 paper/ms.tex
update paper

@@
 
-\begin{figure}[t]
+\begin{figure}[!t]
 	\begin{center}
@@
 		\label{fig:rms_vs_mag}
+	}
+\end{figure}
+
+\begin{figure}[!t]
+	\begin{center}
+		\leavevmode
+		\includegraphics[width=0.47\textwidth]{avg_acf.png}
+	\end{center}
+	\vspace{-0.5cm}
+  \caption{
+    {\bf Percentiles of the average autocorrelation of
+    $10^4$ randomly selected light curves from each sector.} The
+    25$^{\rm th}$, 50$^{\rm th}$, and 75$^{\rm th}$ percentiles at
+    time lags spaced by one hour are
+    shown by dashed, solid, and dotted lines respectively.  The raw
+    light curves (column name \texttt{IRM}) are shown in gray, and the
+    TFA-detrended light curves are in black.
+  \label{fig:avg_acf}
 	}
@@
 \paragraph{ACF statistics}
-TODO:
-ACF statistics before and after detrending(?)
-
-SNR of retrieved HJs?
-
-Maybe movies of subtracted images?
-
-Some stellar variability plots (perhaps of known stellar variables)?
-
-Some focus on particular clusters?
+
+The preceding discussion is only relevant to the white noise
+properties of the light curves. 
+In Figure~\ref{fig:avg_acf} we show the average autocorrelation of the
+raw and TFA-filtered light curves.
+The raw light curves have substantial systematic red noise; 
+their average autocorrelation, evaluated at various time lags, is
+positive.
+The TFA-filtered light curves are much closer to gaussian~--~the
+average autocorrelation between any two points in these light curves
+is close to zero.
+However, the average TFA-filtered light curve is not {\it exactly}
+gaussian.
+At time lags of a few hours or less, there is some excess power.
+This suggests that additional detrending may be
+necessary to maximize the effectiveness of planet searches (or the discovery of
+any other signals via matched-filter techniques).
 

### 2019-07-04 paper/collect_figures.sh

@@ -16,7 +16,9 @@ cp ${fdir}trex_overview.pdf ${pdir}pipelineoverview.pdf
 
 # rms vs mag 
 fdir=../results/paper_figures/
+
 cp ${fdir}rms_vs_mag.png ${pdir}rms_vs_mag.png
+cp ${fdir}avg_acf.png ${pdir}avg_acf.png
 
 # quilt of PCs
 cp ${fdir}quilt_PCs.png ${pdir}quilt_PCs.png

### 2019-07-04 drivers/paper_plot_all_figures.py
add tls_sde_vs_period_scatter_sector6.png

@@ -10,10 +10,10 @@ import numpy as np, pandas as pd
 import matplotlib.pyplot as plt
 
 from numpy import array as nparr
-from astropy.io import fits
-from astropy.io.votable import from_table, writeto, parse
 from datetime import datetime
 
+from astropy.io import fits
+from astropy.io.votable import from_table, writeto, parse
 from astropy.coordinates import SkyCoord
 from astropy import units as u
 
@@ -24,11 +24,12 @@ from aperturephot import get_lc_statistics
 import lcstatistics as lcs
 
 from cdips.utils import tess_noise_model as tnm
-
 from cdips.plotting import plot_star_catalog as psc
 from cdips.plotting import plot_catalog_to_gaia_match_statistics as xms
 from cdips.plotting import plot_wcsqa as wcsqa
 from cdips.utils import collect_cdips_lightcurves as ccl
+
+from skim_cream import plot_initial_period_finding_results
 
 from collections import Counter
 
@@ -39,6 +40,9 @@ LCDIR = '/nfs/phtess2/ar0/TESS/PROJ/lbouma/CDIPS_LCS/'
 def main():
 
     sectors = [6,7]
+
+    # fig N: tls_sde_vs_period_scatter
+    plot_tls_sde_vs_period_scatter(sectors, overwrite=1)
 
     # fig N: average autocorrelation fn of LCs
     plot_avg_acf(sectors, overwrite=1, cleanprevacf=True)
@@ -96,6 +100,60 @@ def main():
 def savefig(fig, figpath):
     fig.savefig(figpath, dpi=450, bbox_inches='tight')
     print('{}: made {}'.format(datetime.utcnow().isoformat(), figpath))
+
+
+def plot_tls_sde_vs_period_scatter(sectors, overwrite=1):
+
+    outpath = os.path.join(
+        OUTDIR, 'tls_sde_vs_period_scatter.png')
+    if os.path.exists(outpath) and not overwrite:
+        print('found {} and not overwrite; return'.format(outpath))
+        return
+
+    if len(sectors) != 2:
+        raise AssertionError
+
+    f,axs = plt.subplots(nrows=2, sharex=True, figsize=(4,6))
+
+    for sector, ax in zip(sectors, axs):
+
+        pfdir = ('/nfs/phtess2/ar0/TESS/PROJ/lbouma/cdips/'
+                 'results/cdips_lc_periodfinding/sector-{}'.format(sector))
[…]

### 2019-07-04 paper/ms.tex
update paper

@@
 \begin{figure}[!t]
-	\gridline{\fig{tlsresult_sector6.png}{0.45\textwidth}{}}
-	\vspace{-0.8cm}
-	\gridline{\fig{tlsresult_sector7.png}{0.45\textwidth}{}}
+	\gridline{\fig{tls_sde_vs_period_scatter.png}{0.45\textwidth}{}}
 	\vspace{-0.8cm}
 	\caption{
-    (IN PROGRESS) Significance thresholds empirically defined for the
-    transiting planet search described in
-    \S~\ref{subsec:identifying_ctois}.  Each point represents the TLS
-    periodogram peak signal detection efficiency from one light curve.
+    {\bf Transiting planet search periodogram summary.}
+    Each point represents the TLS periodogram peak signal detection
+    efficiency (SDE) and corresponding period from one light curve.
+    Significance thresholds (orange lines) are empirically defined for
+    the transiting planet search described in
+    \S~\ref{subsec:identifying_ctois}.  
     {\it Top.} Sector 6.  {\it Bottom.} Sector 7.

### 2019-07-04 paper/collect_figures.sh

@@ -20,6 +20,9 @@ fdir=../results/paper_figures/
 cp ${fdir}rms_vs_mag.png ${pdir}rms_vs_mag.png
 cp ${fdir}avg_acf.png ${pdir}avg_acf.png
 
+cp ${fdir}tls_sde_vs_period_scatter.png \
+   ${pdir}tls_sde_vs_period_scatter.png
+
 # quilt of PCs
 cp ${fdir}quilt_PCs.png ${pdir}quilt_PCs.png
 
@@ -58,7 +61,6 @@ cp ${fdir}target_star_hist_logt.png \
 
 cp ${fdir}target_star_reference_pie_chart.png \
    ${pdir}target_star_reference_pie_chart.png
-
 
 # catalog matching statistics
 cp ${fdir}catalog_to_gaia_match_statistics_MWSC.png \

### 2019-07-04 paper/ms.tex
update paper

@@
     %\includegraphics[width=0.45\textwidth]{target_star_cumulative_counts.png}
-    \gridline{\fig{target_star_cumulative_counts.png}{0.4\textwidth}{}}
+    \gridline{\fig{target_star_cumulative_counts.png}{0.41\textwidth}{}}
     \vspace{-0.8cm}
-    \gridline{\fig{target_star_hist_logt.png}{0.4\textwidth}{}}
+    \gridline{\fig{target_star_hist_logt.png}{0.41\textwidth}{}}
     \vspace{-0.8cm}
-    \gridline{\fig{target_star_reference_pie_chart.png}{0.4\textwidth}{}}
+    \gridline{\fig{target_star_reference_pie_chart.png}{0.41\textwidth}{}}
 	\end{center}
@@
 	\caption{
-    {\it Top.} Cumulative counts of target stars as
-    a function of Gaia $Rp$-band magnitude.  The stars are
-    either candidate members of clusters, or else have other youth
-    indicators (see \S~\ref{sec:starselection}). We only consider
-    stars with $G_{\rm Rp} < 16$.
+    Target star statistics.
+    {\it Top.} Cumulative counts as a function of Gaia $Rp$-band
+    magnitude.  The stars are either candidate members of clusters, or
+    else have other youth indicators (see \S~\ref{sec:starselection}).
     {\it Middle.} Histogram of target star ages, for the subset of
@@
 	\caption{
-    {\bf Conceptual overview of photometric reduction pipeline.}
+    Conceptual overview of photometric reduction pipeline.
     Details are given in \S~\ref{sec:method}.
@@
     \caption{
-		{\it Top.} {\bf Histogram of astrometric residual.} The $x$-axis shows 
+		{\it Top.} Histogram of astrometric residual. The $x$-axis shows 
 		the distance between the measured centroid positions of stars, 
 		compared to the predicted positions from the WCS solution.
-		{\it Bottom.} {\bf Vector plot of astrometric residual.} Each arrow is 
+		{\it Bottom.} Vector plot of astrometric residual. Each arrow is 
 		the vector from the measured to the projected star position. 
@@
 	\caption{
-		{\bf Timeseries of ``external parameters'' for a representative
-			star.} {\it Top}: Instrumental raw magnitude (with a particular
+		Timeseries of ``external parameters'' for a representative
+			star. {\it Top}: Instrumental raw magnitude (with a particular
 		aperture size), as a function of time.  {\it Second and third from
@@
 	\caption{
-		{\bf Positions of light curves from TESS Sectors 6
-			and 7 in galactic coordinates.}
+		Positions of light curves from TESS Sectors 6
+			and 7 in galactic coordinates.
 		Black: $G_{\rm Rp}<13$ field stars.  Blue: $G_{\rm Rp}<16$
@@
 	\caption{
-		{\bf Cumulative number of CDIPS light curves a function of TESS
-			$T$-band magnitude.}  Light curves were made for the
+		Cumulative number of CDIPS light curves a function of TESS
+			$T$-band magnitude.  Light curves were made for the
 		target stars (Figure~\ref{fig:cdips_targets}) that were observed
@@
 	\vspace{-0.5cm}
-	\caption{ {\bf Standard deviation vs catalog TESS-band magnitude for
-			trend-filtered CDIPS light curves.} 
-		Black points correspond to the minimum RMS across the available three
-		aperture sizes.  
-		The model (orange and gray lines) assumes aperture sizes reported 
-		by \citet{Sullivan_et_al_2015}, and the effective area from 
-		\citet{vanderspek_2018}.
-		The noise from unresolved background stars (dotted gray line) is a function 
-		of galactic latitude, and dominates over zodiacal light
-		for faint stars near the galactic plane; the line shown assumes a
-		sight-line towards the center of Sector 6, Camera 1 (further details
-		are in \S~\ref{subsubsec:rmsvsmag}).
+	\caption{
+    Standard deviation of trend-filtered CDIPS light curves as a
+    function of catalog TESS-band magnitude.  Black points correspond
+    to the minimum RMS across the available three aperture sizes.  The
+    model (orange and gray lines) assumes aperture sizes reported by
+    \citet{Sullivan_et_al_2015}, and the effective area from
+    \citet{vanderspek_2018}.  The noise from unresolved background
+    stars (dotted gray line) is a function of galactic latitude, and
+    dominates over zodiacal light for faint stars near the galactic
+    plane; the line shown assumes a sight-line towards the center of
+    Sector 6, Camera 1 (further details are in
+    \S~\ref{subsubsec:rmsvsmag}).
 		\label{fig:rms_vs_mag}
@@
   \caption{
-    {\bf Percentiles of the average autocorrelation of
-    $10^4$ randomly selected light curves from each sector.} The
-    25$^{\rm th}$, 50$^{\rm th}$, and 75$^{\rm th}$ percentiles at
-    time lags spaced by one hour are
-    shown by dashed, solid, and dotted lines respectively.  The raw
-    light curves (column name \texttt{IRM}) are shown in gray, and the
+    Average autocorrelations of $10^4$ randomly selected light curves
+    from each sector. The 25$^{\rm th}$, 50$^{\rm th}$, and 75$^{\rm
+    th}$ percentiles at time lags spaced by one hour are shown by
+    dashed, solid, and dotted lines respectively.  The raw light
+    curves (column name \texttt{IRM}) are shown in gray, and the
     TFA-detrended light curves are in black.
@@
 
-The observed RMS (black points) follows the expected shape,
+The observed RMS (black points) follows the usual shape,
 with photon noise dominating from $T=9$ to $T=12$, beyond which the
 onset of the ``sky'' background changes the overall slope of the
-curve to a slightly steeper scaling.
+curve to be more steep.
 For the brightest stars ($T\lesssim 9$), a ``systematic floor'' was an
@@
 Since the brightest stars are not the focus of the present work, we
-leave this as a point to improve in future work.
+leave this issue unaddressed for the time being.
 
@@
 \citep[{\it e.g.},][Figure~5]{feinstein_eleanor_2019}.
-In aperture photometry pipelines, star in very crowded regions typically 
-have their flux overestimated relative to what would be predicted from their
-catalog magnitudes.
+In aperture photometry pipelines, stars in very crowded regions typically 
+have their flux overestimated relative to the actual number of photons
+that fall on silicon.
 This leads to systematic underestimates of the uncertainty in the relative 
 fluxes, as well as ``flux contamination'' (the reduction in amplitude of say, 
-transit signals, due to diluting flux).
+transit signals, due to diluting flux from neighbor stars).
 Our method to work around this problem -- using the catalog magnitudes to 
 predict the reference flux values, and measuring deviations from these 
-reference fluxes on the subtracted images -- seems to be performing as we had 
-hoped.
+reference fluxes on the subtracted images -- seems to be performing well.
 
@@
 to that of \citet{Sullivan_et_al_2015}, save for two changes.
-The first change is minor: the effective area of the telescope is
-updated to be $86.6\,{\rm cm}^2$, per the measurements of
+The first change is that the effective area of the telescope is
+updated to be $86.6\,{\rm cm}^2$, per the measurements by
 \citet{vanderspek_2018}.
 
-The second point is more important: we explicitly include the
+The second change is that we have explicitly included the
 estimated noise contribution from unresolved faint stars.  The
@@
 plane, and the faint star background is brightest near the galactic
-plane (and towards the galactic center).  \citet{winn_background_2013}
-estimated the photon-counts from each component that would be observed 
-by TESS.
+plane (and towards the galactic center).  
+When performing pre-launch noise estimates,
+\citet{winn_background_2013}
+estimated the photon-counts from each component.
 His zodiacal light model was presented by \citet{Sullivan_et_al_2015},
-but the faint star model was not emphasized since the Sullivan
+but the faint star component was not emphasized since the Sullivan
 simulations were performed away from the galactic plane.
 
-A few words are therefore pertinent about the diffuse sky model we
-have used for Figure~\ref{fig:rms_vs_mag}, which is adopted explicitly
-because most of our target stars are near the galactic plane.
+The diffuse sky model we have used for Figure~\ref{fig:rms_vs_mag} is
+adopted explicitly because most of our target stars are near the
+galactic plane.
 Stars are judged to be ``unresolved'' and part of the background if
@@
 longitude and latitude $(l,b)$.
-\citet{winn_background_2013} queried the Besan\c con model 
-\citep{robin_synthetic_2003}  along a grid of galactic sight-lines, and 
-converted the resulting $N(<m,l,b)$ surface densities into $I$-band surface 
-brightnesses.
-Fitting a smooth function to the results, \citet{winn_background_2013} found
+To calculate this surface density, \citet{winn_background_2013}
+queried the Besan\c con model
+\citep{robin_synthetic_2003}  along a grid of galactic sight-lines,
+and then converted to $I$-band surface brightnesses.
+Fitting a smooth function to the results, \citet{winn_background_2013}
+found
 \begin{equation}
@@
 where the galactic longitude $l$ is measured from $-180^\circ$ to
-$180^\circ$, and the empirical coefficients were found to be $a_0 = 18.9733$, 
-$a_1=8.833$, $a_2=4.007$, and $a_3=0.805$.
-This fit was cautioned to be {\it very approximate}.
-It is sensitive to the threshold used to select ``unresolved'' stars, and 
-likely no more accurate than 0.5 mag on average.
-In regions with exceptionally high extinction ({\it e.g.}, star forming 
-regions) it is expected to systematic underestimate the background brightness 
-by an even larger degree.
+$180^\circ$, and the empirical coefficients were found to be $a_0 =
+18.9733$, $a_1=8.833$, $a_2=4.007$, and $a_3=0.805$.  This fit was
+cautioned to be {\it very approximate}.  It is sensitive to the
+threshold used to select ``unresolved'' stars, and likely no more
+accurate than 0.5 mag on average.  In regions with exceptionally high
+extinction ({\it e.g.}, star forming regions) it is expected to
+systematic underestimate the background brightness by an even larger
+degree.
+Nonetheless, this model for the diffuse sky background seems
+to agree reasonably well with the observed trend of standard deviation
+versus stellar magnitude.
 
@@
 
-The preceding discussion is only relevant to the white noise
-properties of the light curves. 
+Beyond the white noise properties of the light curves, the red noise
+properties are also important. 
 In Figure~\ref{fig:avg_acf} we show the average autocorrelation of the
@@
 	\caption{
-    {\bf Transiting planet search periodogram summary.}
+    Transiting planet search periodogram summary.
     Each point represents the TLS periodogram peak signal detection
@@
 the remaining third we performed TFA signal reconstruction using
-\texttt{vartools}.  In this process, the model lightcurve $A(i)$ in
+\texttt{VARTOOLS}.  In this process, the model lightcurve $A(i)$ in
 Equation~\ref{eq:tfa_to_minimize} is set to the phase-binned signal
@@
 \end{enumerate}
-The initial classifications were performed by LGB, with possible
-planet candidates inspected by JH and JNW.  The \texttt{TagSpaces}
+The initial classifications were performed by LGB, and possible
+planet candidates were then vetted by JH and JNW.
+The \texttt{TagSpaces}
 software was used to easily assign labels to the documents.
@@
 	\caption{
-		{\bf Phased light curves for six of the \numberpcs candidate
-			transiting planets identified in this work.}
+		Phased light curves for six of the \numberpcs candidate
+			transiting planets identified in this work.
 		Black points are detrended flux measurements, phased to the
@@
 	\caption{
-		{\bf Time evolution of Lomb-Scargle periodogram peak period versus
-			Gaia color.}
+    Time evolution of Lomb-Scargle periodogram peak period versus Gaia
+    color.
 		Red stars are on the right, blue stars are on the left.
@@
 %
+The Digitized Sky Surveys were produced at the Space Telescope Science Institute under U.S.
+Government grant NAG W-2166.
+The images of these surveys are based on photographic data obtained using the Oschin Schmidt Telescope on Palomar Mountain and the UK Schmidt Telescope.
+The plates were processed into the present compressed digital form with the permission of these institutions.
+%
 \newline
@@
 \facility{
+	2MASS \citep{skrutskie_tmass_2006},
+	Gaia \citep{gaia_collaboration_gaia_2016,gaia_collaboration_gaia_2018},
 	TESS \citep{ricker_transiting_2015},
-	Gaia \citep{gaia_collaboration_gaia_2016,gaia_collaboration_gaia_2018},
-	2MASS \citep{skrutskie_tmass_2006},
-    DSS (CITE)    
+	UCAC4 \citep{zacharias_fourth_2013}
+    %DSS (CITE)    
 }
@@
   \texttt{astroquery} \citep{astroquery_2018},
-  \texttt{astroquery.gaia} CITE,
-  \texttt{astroquery.simbad} CITE,
-  \texttt{astroquery.mast} CITE,
-  \texttt{astroquery.nasaexopanetarchive} CITE,
+  %\texttt{astroquery.gaia} CITE,
+  %\texttt{astroquery.simbad} CITE,
+  %\texttt{astroquery.mast} CITE,
+  %\texttt{astroquery.nasaexopanetarchive} CITE,
   \texttt{BATMAN} \citep{kreidberg_batman_2015},
@@
   \texttt{pyGAM} \citep{serven_pygam_2018_1476122}
+  \texttt{psycopg2} (\url{initd.org/psycopg})
   \texttt{scipy} \citep{jones_scipy_2001},
-  \texttt{TagSpaces} (CITE),
+  \texttt{TagSpaces} (\url{tagspaces.org}),
   \texttt{tesscut} \citep{brasseur_astrocut_2019},
-  \texttt{wotan} \citep{hippke_wotan_2019}
+  \texttt{VARTOOLS} \citep{Hartman_Bakos_2016}
+  \texttt{wotan} \citep{hippke_wotan_2019},
 }

### 2019-07-05 paper/ms.tex
update paper

@@
 % BEGIN NUMBERS
-\newcommand{\numberpcs}{29\ }  % 2019/06/28 unanimous gold
+\newcommand{\numberpcs}{39\ }  % 2019/06/28 unanimous gold
+\newcommand{\numberzaripcs}{10\ }  % 2019/06/28 unanimous gold
+\newcommand{\numberclusterpcs}{29\ }  % 2019/06/28 unanimous gold
 \newcommand{\sVInumberlcs}{67{,}601\ }  % 2019/06/20 not allnan
@@
 
-\newcommand{\stscilink} {\url{archive.stsci.edu/prepds/cdips}}
+\newcommand{\stscilink}{\url{archive.stsci.edu/prepds/cdips}}
+\newcommand{\stscivetlink}{\url{archive.stsci.edu/prepds/cdips/vetting}}
 
@@
   % Aims
-  As part of the Cluster Difference Imaging Photometric Survey
-  (CDIPS), we have been processing the TESS full-frame images and
-  making light curves of stars that could be members of stellar
-  associations, moving groups, or open clusters.
-  %
-  Our eventual hope is to discover giant transiting planets with known
-  ages, and probe the exoplanet size and separation distributions for
-  planets younger than 1 Gyr.
+  To make light curves of stars that could be members of stellar
+  associations, moving groups, or open clusters, we have begun a
+  Cluster Difference Imaging Photometric Survey (CDIPS).
+  %
+  Our aim is to discover giant transiting planets with known
+  ages, and to probe the exoplanet size and separation distributions for
+  planets younger than one gigayear.
   %
@@
   We then highlight the \numberpcs planet candidates we identified in
-  an initial search, describe the vetting procedures that they have
-  survived, and emphasize the additional spectroscopic, photometric,
-  and imaging observations that are needed to verify (i) whether these
-  candidates are planets and (ii) whether the host stars are cluster members.
+  an initial search.
+  \numberclusterpcs of these planet candidates are candidate cluter
+  members, and the remaining \numberzaripcs have indications of youth
+  relative to field stars.
+  We describe the vetting procedures that these objects have survived,
+  and emphasize the additional spectroscopic, photometric, and imaging
+  observations that are needed to determine (i) whether these candidates
+  are planets and (ii) for which cases the host stars are cluster members.
   %
@@
 
-The main aim of the CDIPS project is to increase the number of cluster
-stars for which photometric time-series are available, and thereby
-facilitate studies of exoplanetary and stellar processes across
-different times and stellar environments.  An essential step is
-therefore to define a sample of stars that are thought to be young, or
-members or clusters, or both.
-
-A homogeneous membership calculation for every known cluster is a
-rather large undertaking, and currently falls outside our scope.  So
-too is a homogeneous search for young stars across the galaxy.
-Instead, we have opted to collect and concatenate appropriate catalogs
-from across the literature.  We then use the resulting meta-catalog to
-identify our target stars within the TESS images.
-
-In our initial stellar selection our aim is completeness, not
-accuracy.  If there has been a claim in the literature that a star
-should be considered a cluster member, or a young star, we would like
-to report a light curve for the star.  For stars that are
-photometrically interesting, we can perform post-hoc quality checks
-using Gaia-DR2 astrometry and photometry to assess cluster membership
-and youth.
-
-\S~\ref{subsec:oc} describes the catalogs we used to identify
-candidate members of open clusters.  \S~\ref{subsec:mg} describes the
-catalogs we used to identify candidate members of moving groups,
-stellar associations, as well as young stars identified through
-combined Gaia photometry and astrometry.  \S~\ref{subsec:ocmgsummary}
-then reports summary statistics for the entire sample of about one
-million target stars.
-
-%FIXME: make table
-
-\subsection{Big catalogs: open clusters}
-\label{subsec:oc}
-
-At the time of writing, two relatively large, homogeneous cluster
-memberships studies had been performed using {\it Gaia}-DR2: those by
-\citet{cantat-gaudin_gaia_2018} and \citet{gaia_hr_2018}.
-There were also two large membership studies based on proper motion and 
-photometric catalogs that were of interest: the studies of
-\citet{Kharchenko_et_al_2013} and \citet{dias_proper_2014}.
-
-\paragraph{{\it Gaia}-derived OC memberships}
-
-\citet{cantat-gaudin_gaia_2018} used an unsupervised membership
-assignment algorithm to identify clusters in the three-dimensional
-astrometric space of proper motion and parallax. They used {\it Gaia}
-photometry and radial velocities to then verify the claimed
-membership properties.  From their Table~2, we collect an initial 401{,}448
-cluster members, in 1229 clusters, down to their limiting magnitude of
-$G=18$.
-
-\citet{gaia_hr_2018} reported memberships for stars in a smaller, more
-select group of well-studied open clusters. From their Table~A1, we
-collect 40{,}903 cluster members, in 41 open clusters, mostly within
-$500\,{\rm pc}$. While this work also included memberships for
-globular clusters, we omitted these from consideration.
-
-In our photometric reduction,  our default identifier for all sources
-is the Gaia-DR2 \texttt{source\_id}.
-The TIC identifiers are found through a spatial cross-match after the light 
-curves have been made
-\citep{stassun_TIC_2018,stassun_TIC8_2019}
-This is because Gaia-DR2 is the base-catalog used to project
-sources from celestial coordinates to the imaging plane (\S~\ref{sec:method}).
-It also has the advantage that for any Gaia-derived cluster memberships, 
-we preform cross-matching directly via the source identifiers.
-
-\paragraph{Pre-{\it Gaia} OC memberships}
-\citet{Kharchenko_et_al_2013} used proper motions calculated in PPMXL
-\citep[][a combination of USNO-B1{.}0 and 2MASS
-astrometry]{roeser_ppmxl_2010} and near-infrared photometry from 2MASS
-\citep{skrutskie_tmass_2006} to report the existence of 2859 open
-clusters and stellar associations (globular clusters were
-omitted by excluding any entry of type \texttt{'g'}).
-We selected ``$1\sigma$'' members according to the
-combined photometric, kinematic, and spatial criteria described by
-\citet{kharchenko_global_2012}.  Then, to obtain {\it Gaia}-DR2 source
-identifiers for the members, we performed a crossmatch for {\it
-Gaia}-DR2 sources within 5 arcseconds of the listed positions.  As an
-additional constraint, we used the 2MASS photometry to predict the
-$G$-band magnitudes\footnote{See
-\url{https://gea.esac.esa.int/archive/documentation/GDR2/Data_processing/chap_cu5pho/sec_cu5pho_calibr/ssec_cu5pho_PhotTransf.html},
-online, \texttt{2019-03-29}, or \citet{carrasco_gaia_2016}}, and
-required that the measured $G$-magnitude fall within 2 magnitudes of
-the predicted $G$-magnitude.  If multiple neighbors matched the
-position and magnitude constraints, we took the nearest spatial
-neighbor as the match.  From 373{,}226 stars, this yielded a unique
-best neighbor for 352{,}332 stars (94.4\% of the sample), and a choice
-between two neighbors for 17{,}774 stars.
-
-%FIXME is this it?
-The second (non-{\it Gaia} derived) open cluster membership catalog we
-used was the \citet{dias_proper_2014} catalog, which was based on
-UCAC4 proper motions.
-From their 1805 reported open clusters, we selected sources with
-quoted membership probability above 50\%.
-To obtain {\it Gaia}-DR2 source identifiers for the members, we
-performed a similar crossmatch as before, looking for sources within 5
-arcseconds of the listed positions, and within $\pm$2 $G$-band
-magnitudes of the prediction.
-From 2{,}034{,}269 stars, this yielded a unique
-best neighbor for 1{,}828{,}630 stars (89.9\% of the sample), and a choice
-between two neighbors for 8.7\% of the remaining sample.
-
-The distributions of various cross-matching statistics are shown in
-Figure~\ref{fig:xmatch_info}.  The distances between matches is
-typically below 1 arcsecond.  The Dias catalog shows somewhat stronger
-crowding effects at the faint end compared to the Kharchenko catalog.
-The Kharchenko catalog also has a more lop-sided distribution of true
-{\it vs.}$\,$predicted $G$-band magnitudes.
-
-\subsection{Smaller catalogs: moving groups and stellar associations}
-\label{subsec:mg}
-
-Stars, moving groups and stellar associations are of interest for
-similar reasons as stars in open clusters.  Though fewer stars
-are known to exist in moving groups, they are of particular interest
-because moving groups are less crowded than open clusters, and are
-often closer to the Sun.
-
-We obtained Gaia-DR2 identifiers from the results of the following
-studies:
-\citet{gagne_banyan_XI_2018},
-\citet{gagne_banyan_XII_2018},
-\citet{gagne_banyan_XIII_2018},
-\citet{kraus_tucanahor_2014},
-\citet{roser_deep_2011}, % OC, not MG...
-\citet{bell_32ori_2017},
-\citet{rizzuto_multidimensional_2011},
-\citet{oh_comoving_2017}, and
-\citet{zari_3d_2018}. The methods applied in these studies
-vary from kinematic analyses, to astrometric analyses included
-Gaia-DR1 parallaxes, to photometric searches for infrared excesses, to
-spectroscopic studies including RVs, H$\alpha$
-emission, and Li absorption.
-
-For the Gagn\'e et al{.} catalogs, we searched the Gaia-DR2 archive for
-sources within 10 arcseconds of the listed positions.  If Gagn\'e et
-al{.} gave a proper motion, we required that the sign of each the Gaia
-proper motion components match that of the Gagn\'e values (the stated
-proper motion uncertainties seemed to have been underestimated).  We
-also imposed a $G<18$ cut on any putative matches.  Of 3012 moving
-group members collected from the three combined Gagn\'e et al{.}
-catalogs, we found 2702 matches.
-
-The \citet{kraus_tucanahor_2014}, \citet{roser_deep_2011}, and
-\citet{bell_32ori_2017} studies reported members in Tucana-Horologium,
-the Hyades, and 32$\,$Ori respectively.  Applying the same procedure as
-for the Gagn\'e catalogs gave 187, 684, and 119 best-neighbors
-respectively, compared to 205, 724, and 141 initially reported
-members.  Note that \citet{kraus_tucanahor_2014} found that only
-$\sim$70\% of their listed members have spectroscopic indicators
-consistent with their membership in Tucana-Horologium.
-
-\citet{rizzuto_multidimensional_2011} also focused on a single moving
-group: the Sco OB2 association. We used their reported Hipparcos
-identifiers, and matched against the {\it Gaia} archive's
-\texttt{hipparcos2\_best\_neighbour} table, which gave 319
-nearest-neigbor stars from 436 candidate members.
-
-Next, \citet{oh_comoving_2017} searched for comoving stars in the
-$\approx$2 million stars that overlapped between Tycho-2 and {\it
-Gaia}-DR1.  They found many wide binaries, and also identified a large
-number of comoving groups.  We chose the 2{,}134 stars that they
-reported were in groups with sizes of at least 3 stars.  Using their
-{\it Gaia}-DR1 source identifiers, we matched against the {\it Gaia}
-archive's \texttt{dr1\_neighbourhood} table, which gave 1{,}881
-nearest-neigbor stars in groups of at least three stars
-\citep{marrese_gaia_2019}.
-
-Finally, \citet{zari_3d_2018} constructed a sample of young stars
-within $500\,{\rm pc}$ using data from Gaia-DR2. Two subsamples were
-made: (a) an upper main sequence (MS) sample, with 86{,}102 stars, and
-(b) a pre-MS sample, with 43{,}719 stars.  Each was created from a
-careful combination of distinct astrometric and photometric cuts.
-These stars are the youngest, closest stars, spread across
-star-forming complexes in Sco-Cen, Orion, Vela, Taurus, and other
-regions of the sky.  Though many are not strictly identified with
-moving groups or open clusters, their reported youth and proximity to star
-forming regions justifies their inclusion in our search sample.
-
-\subsection{Summary of target stars}
-\label{subsec:ocmgsummary}
-
-\begin{figure}[t]
+\begin{figure}[!t]
 	\begin{center}
@@
 
-\begin{figure*}[!ht]
+\begin{figure*}[!t]
 	\gridline{\fig{mwscmatchstats.png}{0.95\textwidth}{}}
@@
 \end{figure*}
+
+The main aim of the CDIPS project is to increase the number of cluster
+stars for which photometric time-series are available, and thereby
+facilitate studies of exoplanetary and stellar processes across
+different times and stellar environments.  An essential step is
+therefore to define a sample of stars that are thought to be young, or
+members or clusters, or both.
+
+A homogeneous membership calculation for every known cluster is a
+rather large undertaking, and currently falls outside our scope.  So
+too is a homogeneous search for young stars across the galaxy.
+Instead, we have opted to collect and concatenate appropriate catalogs
+from across the literature.  We then use the resulting meta-catalog to
+identify our target stars within the TESS images.
+
+In our initial stellar selection our aim is completeness, not
+accuracy.  If there has been a claim in the literature that a star
+should be considered a cluster member, or a young star, we would like
+to report a light curve for the star.  For stars that are
+photometrically interesting, we can perform post-hoc quality checks
+using Gaia-DR2 astrometry and photometry to assess cluster membership
+and youth.
+
+\S~\ref{subsec:oc} describes the catalogs we used to identify
+candidate members of open clusters.  \S~\ref{subsec:mg} describes the
+catalogs we used to identify candidate members of moving groups,
+stellar associations, as well as young stars identified through
+combined Gaia photometry and astrometry.  \S~\ref{subsec:ocmgsummary}
+then reports summary statistics for the entire sample of about one
+million target stars.
+
+%FIXME: make table
+
+\subsection{Big catalogs: open clusters}
+\label{subsec:oc}
+
+At the time of writing, two relatively large, homogeneous cluster
+memberships studies had been performed using {\it Gaia}-DR2: those by
+\citet{cantat-gaudin_gaia_2018} and \citet{gaia_hr_2018}.
+There were also two large membership studies based on proper motion and 
+photometric catalogs that were of interest: the studies of
+\citet{Kharchenko_et_al_2013} and \citet{dias_proper_2014}.
+
+\paragraph{{\it Gaia}-derived OC memberships}
+
+\citet{cantat-gaudin_gaia_2018} used an unsupervised membership
+assignment algorithm to identify clusters in the three-dimensional
+astrometric space of proper motion and parallax. They used {\it Gaia}
+photometry and radial velocities to then verify the claimed
+membership properties.  From their Table~2, we collect an initial 401{,}448
+cluster members, in 1229 clusters, down to their limiting magnitude of
+$G=18$.
+
+\citet{gaia_hr_2018} reported memberships for stars in a smaller, more
+select group of well-studied open clusters. From their Table~A1, we
+collect 40{,}903 cluster members, in 41 open clusters, mostly within
+$500\,{\rm pc}$. While this work also included memberships for
+globular clusters, we omitted these from consideration.
+
+In our photometric reduction,  our default identifier for all sources
+is the Gaia-DR2 \texttt{source\_id}.
+The TIC identifiers are found through a spatial cross-match after the light 
+curves have been made
+\citep{stassun_TIC_2018,stassun_TIC8_2019}
+This is because Gaia-DR2 is the base-catalog used to project
+sources from celestial coordinates to the imaging plane (\S~\ref{sec:method}).
+It also has the advantage that for any Gaia-derived cluster memberships, 
+we preform cross-matching directly via the source identifiers.
+
+\paragraph{Pre-{\it Gaia} OC memberships}
+\citet{Kharchenko_et_al_2013} used proper motions calculated in PPMXL
+\citep[][a combination of USNO-B1{.}0 and 2MASS
+astrometry]{roeser_ppmxl_2010} and near-infrared photometry from 2MASS
+\citep{skrutskie_tmass_2006} to report the existence of 2859 open
+clusters and stellar associations (globular clusters were
+omitted by excluding any entry of type \texttt{'g'}).
+We selected ``$1\sigma$'' members according to the
+combined photometric, kinematic, and spatial criteria described by
+\citet{kharchenko_global_2012}.  Then, to obtain {\it Gaia}-DR2 source
+identifiers for the members, we performed a crossmatch for {\it
+Gaia}-DR2 sources within 5 arcseconds of the listed positions.  As an
+additional constraint, we used the 2MASS photometry to predict the
+$G$-band magnitudes\footnote{See
+\url{https://gea.esac.esa.int/archive/documentation/GDR2/Data_processing/chap_cu5pho/sec_cu5pho_calibr/ssec_cu5pho_PhotTransf.html},
+online, \texttt{2019-03-29}, or \citet{carrasco_gaia_2016}}, and
+required that the measured $G$-magnitude fall within 2 magnitudes of
+the predicted $G$-magnitude.  If multiple neighbors matched the
+position and magnitude constraints, we took the nearest spatial
+neighbor as the match.  From 373{,}226 stars, this yielded a unique
+best neighbor for 352{,}332 stars (94.4\% of the sample), and a choice
+between two neighbors for 17{,}774 stars.
+
+%FIXME is this it?
+The second (non-{\it Gaia} derived) open cluster membership catalog we
+used was the \citet{dias_proper_2014} catalog, which was based on
+UCAC4 proper motions.
+From their 1805 reported open clusters, we selected sources with
+quoted membership probability above 50\%.
+To obtain {\it Gaia}-DR2 source identifiers for the members, we
+performed a similar crossmatch as before, looking for sources within 5
+arcseconds of the listed positions, and within $\pm$2 $G$-band
+magnitudes of the prediction.
+From 2{,}034{,}269 stars, this yielded a unique
+best neighbor for 1{,}828{,}630 stars (89.9\% of the sample), and a choice
+between two neighbors for 8.7\% of the remaining sample.
+
+The distributions of various cross-matching statistics are shown in
+Figure~\ref{fig:xmatch_info}.  The distances between matches is
+typically below 1 arcsecond.  The Dias catalog shows somewhat stronger
+crowding effects at the faint end compared to the Kharchenko catalog.
+The Kharchenko catalog also has a more lop-sided distribution of true
+{\it vs.}$\,$predicted $G$-band magnitudes.
+
+\subsection{Smaller catalogs: moving groups and stellar associations}
+\label{subsec:mg}
+
+Stars, moving groups and stellar associations are of interest for
+similar reasons as stars in open clusters.  Though fewer stars
+are known to exist in moving groups, they are of particular interest
+because moving groups are less crowded than open clusters, and are
+often closer to the Sun.
+
+We obtained Gaia-DR2 identifiers from the results of the following
+studies:
+\citet{gagne_banyan_XI_2018},
+\citet{gagne_banyan_XII_2018},
+\citet{gagne_banyan_XIII_2018},
+\citet{kraus_tucanahor_2014},
+\citet{roser_deep_2011}, % OC, not MG...
+\citet{bell_32ori_2017},
+\citet{rizzuto_multidimensional_2011},
+\citet{oh_comoving_2017}, and
+\citet{zari_3d_2018}. The methods applied in these studies
+vary from kinematic analyses, to astrometric analyses included
+Gaia-DR1 parallaxes, to photometric searches for infrared excesses, to
+spectroscopic studies including RVs, H$\alpha$
+emission, and Li absorption.
+
+For the Gagn\'e et al{.} catalogs, we searched the Gaia-DR2 archive for
+sources within 10 arcseconds of the listed positions.  If Gagn\'e et
+al{.} gave a proper motion, we required that the sign of each the Gaia
+proper motion components match that of the Gagn\'e values (the stated
+proper motion uncertainties seemed to have been underestimated).  We
+also imposed a $G<18$ cut on any putative matches.  Of 3012 moving
+group members collected from the three combined Gagn\'e et al{.}
+catalogs, we found 2702 matches.
+
+The \citet{kraus_tucanahor_2014}, \citet{roser_deep_2011}, and
+\citet{bell_32ori_2017} studies reported members in Tucana-Horologium,
+the Hyades, and 32$\,$Ori respectively.  Applying the same procedure as
+for the Gagn\'e catalogs gave 187, 684, and 119 best-neighbors
+respectively, compared to 205, 724, and 141 initially reported
+members.  Note that \citet{kraus_tucanahor_2014} found that only
+$\sim$70\% of their listed members have spectroscopic indicators
+consistent with their membership in Tucana-Horologium.
+
+\citet{rizzuto_multidimensional_2011} also focused on a single moving
+group: the Sco OB2 association. We used their reported Hipparcos
+identifiers, and matched against the {\it Gaia} archive's
+\texttt{hipparcos2\_best\_neighbour} table, which gave 319
+nearest-neigbor stars from 436 candidate members.
+
+Next, \citet{oh_comoving_2017} searched for comoving stars in the
+$\approx$2 million stars that overlapped between Tycho-2 and {\it
+Gaia}-DR1.  They found many wide binaries, and also identified a large
+number of comoving groups.  We chose the 2{,}134 stars that they
+reported were in groups with sizes of at least 3 stars.  Using their
+{\it Gaia}-DR1 source identifiers, we matched against the {\it Gaia}
+archive's \texttt{dr1\_neighbourhood} table, which gave 1{,}881
+nearest-neigbor stars in groups of at least three stars
+\citep{marrese_gaia_2019}.
+
+Finally, \citet{zari_3d_2018} constructed a sample of young stars
+within $500\,{\rm pc}$ using data from Gaia-DR2. Two subsamples were
+made: (a) an upper main sequence (MS) sample, with 86{,}102 stars, and
+(b) a pre-MS sample, with 43{,}719 stars.  Each was created from a
+careful combination of distinct astrometric and photometric cuts.
+These stars are the youngest, closest stars, spread across
+star-forming complexes in Sco-Cen, Orion, Vela, Taurus, and other
+regions of the sky.  Though many are not strictly identified with
+moving groups or open clusters, their reported youth and proximity to star
+forming regions justifies their inclusion in our search sample.
+
+\subsection{Summary of target stars}
+\label{subsec:ocmgsummary}
 
@@
 for $(x_0,y_0)$ arbitrary reference positions,
-$\Delta x = x-x_0$, $\Delta y = y - y_0$, and $A$ and $B$ arbitrary
-flux-scaling constants.
+$\Delta x = x-x_0$, $\Delta y = y - y_0$, $B$ is the background
+level, and $A$ is an arbitrary
+flux-scaling constant.
 For a nearly circular shape profile, the sharpness $s$ is related to
@@
 where $B_{xy}$ is a component of the model image that allows for
-background variations.
+background variations, and $\otimes$ denotes convolution.
 Since we modeled the background separately (\S~\ref{subsec:preparation}),
@@
 		Timeseries of ``external parameters'' for a representative
-			star. {\it Top}: Instrumental raw magnitude (with a particular
+			star over one sector.
+			{\it Top}: Instrumental raw magnitude (with a particular
 		aperture size), as a function of time.  {\it Second and third from
@@
 
-Some notes on our implementation follow.
-We select template stars in two stages.
-In the first stage, we fit a parabola in the RMS-magnitude
-plane, and discard stars more than $2\sigma$ away from the
+Some implementation notes follow.
+We selected template stars in two stages.
+In the first stage, we fitted a parabola in the RMS-magnitude
+plane, and discarded stars more than $2\sigma$ away from the
 prediction of the fit.
-We also require that these initial candidate stars have intermediate
+We also required that these initial candidate stars have intermediate
 brightness ($8.5 > T > 13$), and have a relatively large number
 of time-series data points.
-We then perform an initial iteration of TFA, on only the candidate
+We then performed an initial iteration of TFA, on only the candidate
 template stars.
-We inspect the resulting detrended light curves for residual
+We inspected the resulting detrended light curves for residual
 structure by computing a Lomb-Scargle periodogram.
-If the maximum-power peak has a false alarm probability below 0.1\%, 
-we exclude the star from the list of candidate template stars, on the
+If the maximum-power peak had a false alarm probability below 0.1\%, 
+we excluded the star from the list of candidate template stars, on the
 basis of its presumed periodic variability.
-We then randomly select at most 200 template stars from the remaining
+We then randomly selected at most 200 template stars from the remaining
 non-variable candidates. 
@@
 
-Once the template stars are selected, we use the \texttt{VARTOOLS}
+Once the template stars were selected, we use the \texttt{VARTOOLS}
 program to perform the detrending \citep{Hartman_Bakos_2016}.
-This process is performed for each photometric aperture
+This process was performed for each photometric aperture
 separately.
@@
 were made. The provenance of the claimed cluster origin of these
-sources is  ...
+sources is  ... LGBTODO
 
 The clusters with the largest claimed numbers of sources are ...
+LGBTODO
 
@@
 and may exist along lines of sight with heavy extinction.
-
-%FIXME
-The weird part is that the oldest stars seem to have relatively more
-sub-day peak periods.
+Stars younger than about 200 Myr (the first two age bins) also tend
+to be bluer.
+The oldest stars, between about 450 Myr and 1 Gyr, show a hint in
+the detected periods of being ``bottom-heavy'', {\it i.e.}, there are
+relatively more short-period objects in this sample.
+The reason why is unclear~--~the effect could be due to systematic
+differences in the stellar samples, rather than being astrophysical.
+More investigation will be required.
 
@@
 
-Maybe JH or JNW could contribute these subsections?
+Maybe JH or JNW could work on these subsections?
 
@@
 
+JH?
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %FIXME: paraphrase / improve all the below
-In this study, we made \numberlcs light curves of candidate young
-stars, across \numberclusters distinct clusters.
-Each light curve represents between 20 and 25 days of observations
-of a star brighter than $G_{Rp}=16$, sampled at 30 minute cadence.
-
-In the process of making the light curves, we learned X, Y, and Z.
-One point in particular was that image subtraction analyses seem to
-do fine at detecting variability in the galactic plane.
-
-In analyzing the noise properties of our light curves, we found that
-at the faint end, contamination from unresolved background stars
-dominated over other noise sources.
-
-From a cursory transiting planet search, we identified \numberpcs
-planet candidates, which need additional spectroscopic, photometric,
-and imaging observations to verify (i) whether these candidates are
-planets and (ii) whether the host stars are cluster members.
-The vetting reports are available at \stscilink, and the planet
-candidate parameters are on exoFOP-TESS.
-
-We also briefly explored the age-evolution of extremely high-SNR
-variability in the space of dominant period versus color
-(Figure~\ref{fig:ls_peak_vs_time}).
-This seems to show X, and Y.
-
-The overall takeaway is that the sample of light curves and vetting
-reports we have made should prove useful for doing some astrophysics.
-%  We also comment on the possible utility of the light curve sample for
-%  studies of stellar rotation evolution, and binary eccentricity
-%  damping.
+In this study, we first collected an all-sky sample of about one million
+candidate young stars brighter than $G_{\rm Rp}$ of 16.
+82\% of the target star sample resides in a ``cluster'', a generic
+term we adopted for open clusters, stellar associations, and moving
+groups.
+The remaining stars have photometric or astrometric indications of
+their youth, and either reside on the pre-main-sequence or upper
+main sequence.
+
+We then reduced TESS full frame images taken over the course of about
+two months (Sectors 6 and 7; the first fields very close to the galactic
+plane).
+We performed difference imaging in order to minimize the complications
+of the crowded background.
+Using forced aperture photometry, we made light curves for all stars
+brighter than $G_{\rm Rp}$ of 13, and went three magnitudes deeper for
+our target star sample.
+This yielded \numberlcs light curves of candidate young stars across
+\numberclusters distinct clusters.
+
+The light curves seem to be limited in precision by photon noise at
+the bright end, and by unresolved background stars at the faint end.
+Though the raw light curves show significant red noise, decorrelating
+against a set of template stars led to an ensemble of light curves
+with very nearly gaussian noise properties.
+
+An initial search for transiting planets, along with subsequent
+vetting to remove obvious non-cluster members and photometric blends,
+has revealed \numberpcs planet candidates.
+\numberclusterpcs of these candidates are candidate cluter members,
+and the remaining \numberzaripcs have indications of youth, relative
+to field stars.
+The latter sub-sample is the less interesting one for this work, but
+may be of interest for other studies.
+Substantial follow-up efforts on these objects are needed to determine
+(i) whether the candidates are planets and (ii) whether the host stars
+are truly cluster members.
+We suspect that a sizeable fraction of our planet candidates may
+be eclipsing binaries, however it likely also includes real planets.
+The vetting reports are available at \stscivetlink, and also documented
+in Appendix~\ref{appendix:vetreport}.
+The planet candidate parameters are on exoFOP-TESS.
+
+We also briefly explored other forms of photometric variability in the
+dataset.
+The age-evolution of extremely high-SNR variability seems to show some
+evolution in the space of LS peak-period versus color
+(Figure~\ref{fig:ls_peak_vs_time}), but interpreting this result will
+require a more careful exploration.
+In searching for transiting planets, we found many eclipsing binaries,
+as well as stellar rotation and pulsation signals.
+Those who wish to explore the time-evolution in these and any other
+systems are invited to explore the data at \stscilink.
 

### 2019-07-08 cdips/plotting/vetting_pdf.py
vetting report: label sizes

@@ -1208,6 +1208,14 @@ def centroid_plots(c_obj, cd, hdr, _pfdf, toidf, figsize=(30,20),
 
     ##########################################
 
+    import matplotlib as mpl
+    mpl.rcParams['axes.titlesize'] = 'xx-large'
+    mpl.rcParams['axes.labelsize'] = 'xx-large'
+    mpl.rcParams['xtick.direction'] = 'in'
+    mpl.rcParams['ytick.direction'] = 'in'
+    mpl.rcParams['xtick.labelsize'] = 'xx-large'
+    mpl.rcParams['ytick.labelsize'] = 'xx-large'
+
     plt.close('all')
     fig = plt.figure(figsize=figsize)
 
@@ -1519,13 +1527,7 @@ def centroid_plots(c_obj, cd, hdr, _pfdf, toidf, figsize=(30,20),
 
 
     ##########################################
-    for ax in [ax0,ax1,ax2,ax3,ax4,ax5,ax6,ax7]:
-        ax.get_yaxis().set_tick_params(which='both', direction='in',
-                                       labelsize='xx-large')
-        ax.get_xaxis().set_tick_params(which='both', direction='in',
-                                       labelsize='xx-large')
-
-    fig.tight_layout(pad=2, h_pad=1.7)
+    fig.tight_layout(pad=3.0, h_pad=1.7)
 
     ax5.text(txt_x, txt_y, outstr, ha='left', va='top',
              fontsize=22, zorder=2, transform=ax5.transAxes)

### 2019-07-08 paper/ms.tex
minor

@@
 		members from Kharchenko, and the orange is the target star.
-		Bottom-left is the HR diagram, and bottom-right are the on-sky positions.
-		In the text,
-		\texttt{N1sr2} is the number of $1\sigma$ cluster members claimed
+    Bottom-left is the color-magnitude diagram, and bottom-right are
+    the on-sky positions.  In the text,
+		\texttt{N1sr2} is the number of $1\sigma$ cluster members reported
 		by \citet{Kharchenko_et_al_2013} within the cluster angular radius;
 		$\log t$ is the base-10 logarithm of the age in years;
-		\texttt{type} matches the type codes provided by \citet{Kharchenko_et_al_2013}.
+		\texttt{type} matches the type codes provided by
+    \citet{Kharchenko_et_al_2013};
+    \texttt{K13Note} gives the description of the cluster from
+    \citet{Kharchenko_et_al_2013}, if available.
 		\label{fig:pg5}

### 2019-07-10 drivers/remove_select_reports.py
add drivers/remove_select_reports.py

@@ -1,0 +1,35 @@
+import os
+from glob import glob
+import pandas as pd, numpy as np
+
+sector=6
+
+if sector==6:
+    date = '20190616'
+elif sector==7:
+    date = '20190618'
+
+csvpath = (
+    '/home/luke/Dropbox/proj/cdips/results/vetting_classifications/'
+    '{}_LGB_sector{}_classifications_PC_cut.csv'.format(date,sector)
+)
+
+df = pd.read_csv(csvpath)
+
+for n in np.array(df['Name']):
+
+    pdfname = n+'.pdf'
+
+    pdfdir = '/home/luke/local/cdips/vetting/sector-{}/pdfs/'.format(sector)
+
+    pdfpath = os.path.join(pdfdir, pdfname)
+
+    if os.path.exists(pdfpath):
+
+        os.remove(pdfpath)
+
+        print('removed {}'.format(pdfpath))
+
+    else:
+
+        print('didnt find & skipped {}'.format(pdfpath))

### 2019-07-10 drivers/remove_select_reports.py
minor

@@ -2,7 +2,7 @@ import os
 from glob import glob
 import pandas as pd, numpy as np
 
-sector=6
+sector=7
 
 if sector==6:
     date = '20190616'
@@ -18,7 +18,7 @@ df = pd.read_csv(csvpath)
 
 for n in np.array(df['Name']):
 
-    pdfname = n+'.pdf'
+    pdfname = 'vet_'+n+'_llc.pdf'
 
     pdfdir = '/home/luke/local/cdips/vetting/sector-{}/pdfs/'.format(sector)
 

### 2019-07-10 paper/ms.tex
minor paper update

@@
 astrometric space of proper motion and parallax. They used {\it Gaia}
-photometry and radial velocities to then verify the claimed
-membership properties.  From their Table~2, we collect an initial 401{,}448
+photometry and radial velocities to then verify the claimed membership
+properties.  From their Table~2, we collect an initial 401{,}448
 cluster members, in 1229 clusters, down to their limiting magnitude of
@@
 In our photometric reduction,  our default identifier for all sources
-is the Gaia-DR2 \texttt{source\_id}.
-The TIC identifiers are found through a spatial cross-match after the light 
-curves have been made
-\citep{stassun_TIC_2018,stassun_TIC8_2019}
-This is because Gaia-DR2 is the base-catalog used to project
-sources from celestial coordinates to the imaging plane (\S~\ref{sec:method}).
-It also has the advantage that for any Gaia-derived cluster memberships, 
-we preform cross-matching directly via the source identifiers.
+is the Gaia-DR2 \texttt{source\_id}.  The TIC identifiers are found
+through a spatial cross-match after the light curves have been made,
+subject to the requirement that the Gaia-DR2 source identifiers match
+\citep{stassun_TIC_2018,stassun_TIC8_2019}.  We take this approach
+because Gaia-DR2 is the base-catalog used to project sources from
+celestial coordinates to the imaging plane (\S~\ref{sec:method}).  It
+also has the advantage that for any Gaia-derived cluster memberships,
+we can cross-match directly against source identifiers.
 
@@
 	\caption{
-		{\bf Page 1: period-search summary.} Periodograms from TLS and 
+		{\bf Transit search summary.} Periodograms from TLS and 
 		phase-dispersion minimization, as calculated 
@@
 		top-right. A small finder chart from DSS is inset to the top left, with
-		the 1.5-pixel radius aperture used to extract the light curve in orange (CITE).
+		the 1.5-pixel radius aperture used to extract the light curve in orange.
 		\label{fig:pg1}
@@
 	\caption{
-		{\bf Page 2: light curve diagnostics.} 
+		{\bf Light curve diagnostics.} 
 		Time-series of raw flux (\texttt{IRM2}),  TFA-detrended flux (\texttt{TF2}), stellar-variability
@@
 	\caption{
-    {\bf Page 3: Transit diagnostics.} The plots show the
+    {\bf Transit diagnostics.} The plots show the
     maximally-detrended light curve (top); the phase-folded light
@@
     (lower right).
-    The stellar parameters ($T_{\rm eff}, R_\star$) are taken from
-    Gaia-DR2 Apsis pipeline results when available
-    \citep{andrae_apsis_2018}.
+    The stellar parameters ($T_{\rm eff}, R_\star, M_\star$) are taken from
+    TICv8 when available \citep{stassun_TIC8_2019}.
+    %Gaia-DR2 Apsis pipeline results when available
+    %\citep{andrae_apsis_2018}.
     The first eight lines of text are parameters determined from the
@@
     indicate hints of astrometric binarity in the system.
+    ``$d_{\rm geom}$'' is the geometric distance from
+    \citet{bailer-jones_distances_2018}.
     ``$R_\star + M_\star \rightarrow T_{b0}$'' gives the duration of a
-    zero-eccentricity central transit based on the Gaia-DR2 stellar
-    radius, and a stellar mass interpolated from the
+    zero-eccentricity central transit based on the TICv8 stellar
+    radius and mass if available. If the mass is not available, a
+    stellar mass is interpolated from the
     \citet{pecaut_intrinsic_2013} table, under the assumption that the
@@
 	\caption{
-		{\bf Page 4: Light curves for increasing aperture sizes.} 
+		{\bf Light curves for increasing aperture sizes.} 
 		Apertures of radius 1, 1.5, and 2.25 pixels are shown from top to bottom.
@@
 	\caption{
-		{\bf Page 5: Cluster membership assessment diagnostics.}
+		{\bf Cluster membership assessment diagnostics.}
 		The star was considered a candidate cluster member by the source(s) listed under
@@
 	\caption{
-		{\bf Page 6: Imaging variability diagnostics.} 
+		{\bf Imaging variability diagnostics.} 
 		This page is intended to help diagnose which stars are producing the observed

### 2019-07-10 paper/ms.tex
most png figures to pdfs

@@
 		%\includegraphics[width=0.45\textwidth]{target_star_cumulative_counts.png}
-		\gridline{\fig{target_star_cumulative_counts.png}{0.41\textwidth}{}}
+		\gridline{\fig{target_star_cumulative_counts.pdf}{0.41\textwidth}{}}
 		\vspace{-0.8cm}
-		\gridline{\fig{target_star_hist_logt.png}{0.41\textwidth}{}}
+		\gridline{\fig{target_star_hist_logt.pdf}{0.41\textwidth}{}}
 		\vspace{-0.8cm}
-		\gridline{\fig{target_star_reference_pie_chart.png}{0.41\textwidth}{}}
+		\gridline{\fig{target_star_reference_pie_chart.pdf}{0.41\textwidth}{}}
 	\end{center}
@@
 \begin{figure*}[!t]
-	\gridline{\fig{mwscmatchstats.png}{0.95\textwidth}{}}
+	\gridline{\fig{mwscmatchstats.pdf}{0.95\textwidth}{}}
 	\vspace{-0.8cm}
-	\gridline{\fig{dias14matchstats.png}{0.95\textwidth}{}}
+	\gridline{\fig{dias14matchstats.pdf}{0.95\textwidth}{}}
 	\vspace{-0.8cm}
@@
 \begin{figure}[!t]
-	\gridline{\fig{astromresidual_hist.png}{0.5\textwidth}{}}
+	\gridline{\fig{astromresidual_hist.pdf}{0.5\textwidth}{}}
 	\vspace{-0.8cm}
-	\gridline{\fig{astromresidual_quiver.png}{0.5\textwidth}{}}
+	\gridline{\fig{astromresidual_quiver.pdf}{0.5\textwidth}{}}
   %\vspace{-0.8cm}
-	%\gridline{\fig{astromresidual_apertures.png}{0.5\textwidth}{}}
+	%\gridline{\fig{astromresidual_apertures.pdf}{0.5\textwidth}{}}
 	\vspace{-0.8cm}
@@
 		\leavevmode
-		\includegraphics[width=0.47\textwidth]{galacticcoords_cluster_field_star_positions.png}
+		\includegraphics[width=0.47\textwidth]{galacticcoords_cluster_field_star_positions.pdf}
 	\end{center}
@@
 		\leavevmode
-		\includegraphics[width=0.45\textwidth]{cdf_T_mag.png}
+		\includegraphics[width=0.45\textwidth]{cdf_T_mag.pdf}
 	\end{center}
@@
 \begin{figure}[!ht]
-	\gridline{\fig{hrd_scat_all_CDIPS_LCs.png}{0.45\textwidth}{}}
+	\gridline{\fig{hrd_scat_all_CDIPS_LCs.pdf}{0.45\textwidth}{}}
 	\vspace{-0.8cm}
-	\gridline{\fig{hrd_scat_close_subset.png}{0.45\textwidth}{}}
+	\gridline{\fig{hrd_scat_close_subset.pdf}{0.45\textwidth}{}}
 	\vspace{-0.8cm}
@@
 \begin{figure}[!t]
-	\gridline{\fig{pm_scat_all_CDIPS_LCs.png}{0.45\textwidth}{}}
+	\gridline{\fig{pm_scat_all_CDIPS_LCs.pdf}{0.45\textwidth}{}}
 	\vspace{-0.8cm}
-	\gridline{\fig{pm_scat_close_subset.png}{0.45\textwidth}{}}
+	\gridline{\fig{pm_scat_close_subset.pdf}{0.45\textwidth}{}}
 	\vspace{-0.8cm}
@@
 		\leavevmode
-		\includegraphics[width=0.47\textwidth]{rms_vs_mag.png}
+		\includegraphics[width=0.47\textwidth]{rms_vs_mag.pdf}
 	\end{center}
@@
 		\leavevmode
-		\includegraphics[width=0.47\textwidth]{avg_acf.png}
+		\includegraphics[width=0.47\textwidth]{avg_acf.pdf}
 	\end{center}
@@
 \begin{figure}[!t]
-	\gridline{\fig{tls_sde_vs_period_scatter.png}{0.45\textwidth}{}}
+	\gridline{\fig{tls_sde_vs_period_scatter.pdf}{0.45\textwidth}{}}
 	\vspace{-0.8cm}
@@
 		\leavevmode
-		\includegraphics[width=0.9\textwidth]{quilt_PCs.png}
+		\includegraphics[width=0.9\textwidth]{quilt_PCs.pdf}
 	\end{center}
@@
 		\leavevmode
-		\includegraphics[width=0.45\textwidth]{LS_period_vs_color_and_age.png}
+		\includegraphics[width=0.45\textwidth]{LS_period_vs_color_and_age.pdf}
 	\end{center}

### 2019-07-10 paper/collect_figures.sh

@@ -17,17 +17,17 @@ cp ${fdir}trex_overview.pdf ${pdir}pipelineoverview.pdf
 # rms vs mag 
 fdir=../results/paper_figures/
 
-cp ${fdir}rms_vs_mag.png ${pdir}rms_vs_mag.png
-cp ${fdir}avg_acf.png ${pdir}avg_acf.png
+cp ${fdir}rms_vs_mag.pdf ${pdir}rms_vs_mag.pdf
+cp ${fdir}avg_acf.pdf ${pdir}avg_acf.pdf
 
-cp ${fdir}tls_sde_vs_period_scatter.png \
-   ${pdir}tls_sde_vs_period_scatter.png
+cp ${fdir}tls_sde_vs_period_scatter.pdf \
+   ${pdir}tls_sde_vs_period_scatter.pdf
 
 # quilt of PCs
-cp ${fdir}quilt_PCs.png ${pdir}quilt_PCs.png
+cp ${fdir}quilt_PCs.pdf ${pdir}quilt_PCs.pdf
 
 # time evolution of LS peak period
-cp ${fdir}LS_period_vs_color_and_age.png ${pdir}LS_period_vs_color_and_age.png
+cp ${fdir}LS_period_vs_color_and_age.pdf ${pdir}LS_period_vs_color_and_age.pdf
 
 # positions of lightcurves
 cp ${fdir}sector6_cam[1]_ccd[1-2-3-4]cluster_field_star_positions.png \
@@ -38,43 +38,43 @@ cp ${fdir}cluster_field_star_positions.png \
    ${pdir}cluster_field_star_positions.png
 
 # positions of lightcurves
-cp ${fdir}galacticcoords_cluster_field_star_positions.png \
-   ${pdir}galacticcoords_cluster_field_star_positions.png
+cp ${fdir}galacticcoords_cluster_field_star_positions.pdf \
+   ${pdir}galacticcoords_cluster_field_star_positions.pdf
 
 # CDF of T mags of LCs
-cp ${fdir}cdf_T_mag.png ${pdir}cdf_T_mag.png
+cp ${fdir}cdf_T_mag.pdf ${pdir}cdf_T_mag.pdf
 
 # HRDs of close and entire LC subsets
-cp ${fdir}hrd_scat_all_CDIPS_LCs.png ${pdir}hrd_scat_all_CDIPS_LCs.png
-cp ${fdir}hrd_scat_close_subset.png ${pdir}hrd_scat_close_subset.png
[…]

### 2019-07-11 paper/ms.tex

@@
   an initial search.
-  \numberclusterpcs of these planet candidates are candidate cluter
+  \numberclusterpcs of these planet candidates are candidate cluster
   members, and the remaining \numberzaripcs have indications of youth
@@
 main-sequence turnoff locations, pre-main-sequence turnon locations,
-and possibly averaged MS isochronal ages across known cluster members
+and averaged MS isochronal ages across known cluster members
 \citep[{\it e.g.},][Section 3.4.3]{kharchenko_global_2012}.  Once
@@
 The first planets to be detected in open clusters were found through
-radial velocity (RV) measurements of evolved stars in the Hyades and
+radial velocity (RV) measurements of red giants in the Hyades and
 NGC~2423 \citep{Sato_et_al_2007,lovis_mayor_2007}.
@@
 
-The transit method was comparatively slow to catch up, despite deep
-searches of M~37 by \citet{hartman_MMT_IV_2009}, as well as searches
-of nine young clusters in the solar neighborhood by the Monitor
-project
+The transit method was comparatively slow to catch up.  Deep transit
+searches typically comprising days to weeks of observations were
+performed for NGC~2158, 6791, and 1245, among other clusters
+\citep{mochejska_planets_2005,mochejska_planets_2006,burke_survey_2006}.
+Related projects include a search of M~37 by
+\citet{hartman_MMT_IV_2009}, of Praesepe by
+\citet{pepper_photometric_2008}, and of nine young clusters in the
+solar neighborhood by the Monitor team
 \citep{aigrain_monitor_2007,irwin_monitordata_2007,miller_monitor_2008}.
-While these studies led to measurements of stellar rotation
-periods \citep{hartman_rotation_2009,Irwin_NGC2516_2007} as well as
-the discovery of pre-main-sequence (PMS) eclipsing binaries (EBs)
-\citep{irwin_monitor_PMSEB_2007}, no transiting planets in open
-clusters were found.  Transit searches in globular clusters were
+Though these studies led to measurements of stellar rotation periods
+\citep{hartman_rotation_2009,Irwin_NGC2516_2007} as well as the
+discovery of pre-main-sequence (PMS) eclipsing binaries (EBs)
+\citep{irwin_monitor_PMSEB_2007}, no definitive transiting planets in
+open clusters were found.  Transit searches in globular clusters were
 similarly met with null results \citep{gilliland_lack_2000,
-weldrake_searching_2006}.
+weldrake_searching_2006}.  These searches were typically sensitive to
+planets larger than Jupiter, on $\lesssim 3$ day orbital periods.  Hot
+Jupiter occurrence rate limits were derived at the $\lesssim 5\%$
+level \citep[{\it e.g.},][]{burke_survey_2006, hartman_MMT_IV_2009}.
+The modern 0.5-1\% occurrence rate suggests that these early transit
+surveys needed a greater data volume, at higher precision for
+detection to be possible
+\citep{mayor_harps_2011,wright_frequency_2012,howard_planet_2012,petigura_metallicity_2018}.
 
@@
 Sco, showed that at least some close-in planets must form within about
-10 Myr, excluding long-timescale migration as an explanation for its
-origin \citep{Mann_K2_33b_2016,David_et_al_2017}.  Further discoveries
+10 Myr \citep{Mann_K2_33b_2016,David_et_al_2017}.  Further discoveries
 included six transiting planets in Praesepe
@@
 
-One of the major barriers to deriving precise photometry from the
-TESS images is the relatively poor angular resolution ($\approx 21''$
-per pixel).  Almost all clusters are within 10 degrees of the Galactic
+One of the major barriers to deriving precise photometry from the TESS
+images is the relatively poor angular resolution ($\approx 21''$ per
+pixel).  Almost all clusters are within 10 degrees of the Galactic
 plane. The problems with crowding and complex backgrounds are so
 severe near the galactic plane that the TESS Candidate Target List has
-deprioritized all objects at galactic latitudes less than $\approx
-15^\circ$~\citep{stassun_TIC_2018,stassun_TIC8_2019}, which includes
-almost all star clusters\footnote{TICv8 has updated this to $10^\circ$,
-but for the first year of TESS observations, the number used when
-selecting target stars was $15^\circ$.}.  This is sensible, given that
-the large pixel size and the high stellar surface density make
-aperture photometry unreliable.  However, it also means that a large
-number of stars in clusters that could yield transiting planets will
-go unprocessed by the official {\it TESS} data reduction pipeline.
+deprioritized 2-minute targets at galactic latitudes less than
+$\approx 15^\circ$~\citep{stassun_TIC_2018,stassun_TIC8_2019}, which
+includes almost all star clusters\footnote{TICv8 has updated this to
+$10^\circ$, but for the first year of TESS observations, the number
+used when selecting target stars was $15^\circ$.}.  This is sensible,
+since the large pixel size and the high stellar surface density
+make aperture photometry unreliable.  However, it also means that a
+large number of stars in clusters that could yield transiting planets
+will go unprocessed by the official {\it TESS} data reduction
+pipeline.
 
@@
 difference imaging technique because of its benefits in modelling
-complex backgrouds in crowded regions.  While we hope to discover at
+complex backgrounds in crowded regions.  While we hope to discover at
 least a few giant transiting planets, a separate hope is that the
@@
 combined Gaia photometry and astrometry.  \S~\ref{subsec:ocmgsummary}
-then reports summary statistics for the entire sample of about one
-million target stars.
+and Figure~\ref{fig:cdips_targets} describe summary statistics for the
+entire sample of about one million target stars.
 
@@
 
-\citet{cantat-gaudin_gaia_2018} used an unsupervised membership
-assignment algorithm to identify clusters in the three-dimensional
-astrometric space of proper motion and parallax. They used {\it Gaia}
-photometry and radial velocities to then verify the claimed membership
-properties.  From their Table~2, we collect an initial 401{,}448
-cluster members, in 1229 clusters, down to their limiting magnitude of
-$G=18$.
+\citet{cantat-gaudin_gaia_2018} used the UPMASK unsupervised membership
+assignment algorithm \citep{krone-martins_upmask_2014} to identify cluster
+members using Gaia-DR2 positions, proper motions, and parallaxes.
+They used {\it Gaia} photometry and radial velocities to then verify the
+claimed membership properties.  From their Table~2, we collect an initial
+401{,}448 cluster members, in 1229 clusters, down to their limiting magnitude
+of $G=18$.
 
@@
 
-In our photometric reduction,  our default identifier for all sources
-is the Gaia-DR2 \texttt{source\_id}.  The TIC identifiers are found
-through a spatial cross-match after the light curves have been made,
-subject to the requirement that the Gaia-DR2 source identifiers match
-\citep{stassun_TIC_2018,stassun_TIC8_2019}.  We take this approach
-because Gaia-DR2 is the base-catalog used to project sources from
-celestial coordinates to the imaging plane (\S~\ref{sec:method}).  It
-also has the advantage that for any Gaia-derived cluster memberships,
-we can cross-match directly against source identifiers.
+Given the unprecedented quality of Gaia-DR2 astrometry, these two
+membership sources are our most reliable sources of membership
+information.  In our photometric reduction,  our default identifier
+for all sources is correspondingly the Gaia-DR2 \texttt{source\_id}.
+The TIC identifiers are found through a spatial cross-match after the
+light curves have been made, subject to the requirement that the
+Gaia-DR2 source identifiers match
+\citep{stassun_TIC_2018,stassun_TIC8_2019}.
+
+% We take this approach
+% because Gaia-DR2 is the base-catalog used to project sources from
+% celestial coordinates to the imaging plane (\S~\ref{sec:method}).  It
+% also has the advantage that for any Gaia-derived cluster memberships,
+% we can cross-match directly against source identifiers.
 
@@
 \citep{skrutskie_tmass_2006} to report the existence of 2859 open
-clusters and stellar associations (globular clusters were
-omitted by excluding any entry of type \texttt{'g'}).
-We selected ``$1\sigma$'' members according to the
-combined photometric, kinematic, and spatial criteria described by
-\citet{kharchenko_global_2012}.  Then, to obtain {\it Gaia}-DR2 source
-identifiers for the members, we performed a crossmatch for {\it
-Gaia}-DR2 sources within 5 arcseconds of the listed positions.  As an
-additional constraint, we used the 2MASS photometry to predict the
-$G$-band magnitudes\footnote{See
+clusters and stellar associations (globular clusters were omitted by
+excluding any entry of type \texttt{'g'}).  We selected the most
+probable cluster members (``$1\sigma$ members'') using the combined
+photometric, kinematic, and spatial criteria described by
+\citet[][Section~3.3]{kharchenko_global_2012}.  Then, to obtain {\it
+Gaia}-DR2 source identifiers for the members, we performed a
+crossmatch for {\it Gaia}-DR2 sources within 5 arcseconds of the
+listed positions.  To improve the quality of the cross-match, we
+additionally used the 2MASS photometry to predict the $G$-band
+magnitudes\footnote{See
 \url{https://gea.esac.esa.int/archive/documentation/GDR2/Data_processing/chap_cu5pho/sec_cu5pho_calibr/ssec_cu5pho_PhotTransf.html},
@@
 used was the \citet{dias_proper_2014} catalog, which was based on
-UCAC4 proper motions.
+UCAC4 proper motions acquired by the US Naval Observatory
+\citep{zacharias_fourth_2013}.
 From their 1805 reported open clusters, we selected sources with
@@
 astrometric verification, and coarse simple aperture photometry of
-bright stars (\S~\ref{subsec:preparation}).  Using the metadata
+bright stars (\S~\ref{subsec:preparation}).  Using the information
 collected from these initial steps, we select an astrometric reference
@@
 Data acquired throughout each ``sector'' are downlinked at spacecraft
-perigee through the Deep Space Network.  Verbose descriptions of the
+perigee through the Deep Space Network.  Descriptions of the
 spacecraft's design and operations are given by
@@
 5.1]{vanderspek_2018}. Once transmitted to the ground, the raw images
-are calibrated by the Science Processing Operations Center.  The
+are calibrated by the Science Processing Operations Center (SPOC).  The
 calibration process includes an overscan, bias, and dark current
@@
 pass a $48\times48$ median box filter over each pixel in the image,
-with reflective boundary conditions.  We blur the resulting background
-estimate with a gaussian kernel, which produces a smooth background
-estimate for each image.  These steps also remove a low-level
-vignetting present in the corners of many images, which remains even
-after flat-fielding \citep[see][\S 7.3.5]{vanderspek_2018}.  With the
-exception of scattered-light caustics, which remain over small areas
-of less than 10\% of the frames, our ad-hoc procedure seems to
-adequately remove large spatial scale scattered light patches.
+with reflective boundary conditions.  The resulting background
+estimate has low-amplitude structure over spatial scales of a few
+pixels, so we then blur it with a gaussian kernel to produce a smooth
+background estimate for each image.  These steps also remove a
+low-level vignetting present in the corners of many images, which
+remains even after flat-fielding \citep[see][\S
+7.3.5]{vanderspek_2018}.  With the exception of scattered-light
+caustics, which remain over small areas of less than 10\% of the
+frames, our ad-hoc procedure seems to adequately remove large spatial
+scale scattered light patches.
 
@@
 
-After subtracting the background, we mask out saturated stars using a
+After subtracting the background, we mask out saturated pixels using a
 fixed saturation level of $8\times10^4\,{\rm ADU}$. This value was
 chosen based on the onset of bleeding charge trails in the images, and
-is slightly greater than the expected saturation level quoted by
-\citet{vanderspek_2018}.  As described by \citet{Pal_2009}, our masks
-are metadata to the image, and are only applied to the pixel values
-during the specific image processing steps in which they are necessary
-({\it e.g.}, convolution). We also extend the masks beyond purely
-saturated pixels to ``bloomed'' pixels horizontally and vertically
-adjacent to the saturated pixels (see Figure~6 of \citealt{Pal_2009}).
+is slightly greater than the saturation level of $2\times10^5$
+electrons, or about $4\times10^4\,{\rm ADU}$, quoted by
+\citet{vanderspek_2018}. 
+We correspondingly do not analyze stars brighter than $T\approx 6.5$.
+As described by \citet{Pal_2009}, the pixel masks are metadata to the
+image, and are only applied to the pixel values during the specific
+image processing steps in which they are necessary ({\it e.g.},
+convolution). We also extend the masks beyond purely saturated pixels
+to ``bloomed'' pixels horizontally and vertically adjacent to the
+saturated pixels (see Figure~6 of \citealt{Pal_2009}).
 
@@
 \citet{vanderspek_2018}, we omit the entire frame.  This removes on
-average a few frames per sector. Through visual inspection, we see
-that the stars on these frames are extremely smeared, and are unlikely
-to produce useful science data.  In addition, we use the
-sector-specific data release notes\footnote{\url{
+average a few frames per sector, out of about one thousand. Through
+visual inspection, we see that the stars on these frames are extremely
+smeared, and are unlikely to produce useful science data.  In
+addition, we use the sector-specific data release notes\footnote{\url{
   archive.stsci.edu/tess/tess_drn.html}} to identify further times
 with anomalous spacecraft performance, which we omit from
-consideration.
-For Sectors 6 and 7, this included three days at the beginning of
-Sector 6 dedicated to acquiring pixel response function data, and no
-additional gaps in Sector 7.
+consideration.  For Sectors 6 and 7, this included three days at the
+beginning of Sector 6 dedicated to acquiring pixel response function
+data, and no additional gaps in Sector 7.
 %For Sectors 1 through 5, these
@@
 
-First, we use \texttt{fistar} to perform source extraction on bright
-stars in each image.  During the initial source extraction, we also
-fit elongated gaussians to the bright stars, yielding the shape
+First, we use \texttt{fistar} to perform source extraction on the
+thousand or so brightest, non-saturated stars in each image.  The
+source extraction derives centroid positions for these stars, and also
+fits elongated gaussians to their profiles, yielding the shape
 parameters $(s,d,k)$, where the flux $f$ as a function of position
@@
 
-For the astrometric solution, we use the WCS and SIP coefficients
+For the astrometric solution, we use the World Coordinate System (WCS)
+and fourth-order Simple Imaging Polynomial (SIP) coefficients
 derived by SPOC and included in the FFI headers
@@
 we did not invest major amounts of time developing a robust
-algorith to select non-blended stars of intermediate brightness before
+algorithm to select non-blended stars of intermediate brightness before
 measuring their positions.
@@
 
-The astrometric residual is displayed for one photometric reference
-frame in Figure~\ref{fig:astromresid}.
+The residual between the measured and projected stellar centroid
+positions is displayed for one photometric reference frame in
+Figure~\ref{fig:astromresid}.
 The construction of this frame will be described shortly, however
@@
 
-As a final step of metadata collection, we use \texttt{fiphot}
-to perform aperture photometry on the
-bright stars from the
-source list, by summing the counts inside appropriately-weighted
-circular apertures centered on the projected positions. 
+As a final step of metadata collection, we perform aperture photometry on the
+bright stars by summing the counts inside appropriately-weighted
+circular apertures centered on the projected positions. This task is
+performed using \texttt{fiphot}.
 The pixel weights are equal to the fraction of the pixel
@@
 The choice of how to decompose the kernel was further explored by
-\citet{bramich_new_2008}, who showed that using a delta function
-had a few select advantages compared to a basis of gaussians.
-We perform the convolution using \texttt{ficonv}, and opt for
-the implementation of Bramich's method (see \citealt{Pal_2009} \S~2.8).
+\citet{bramich_new_2008}, who showed that using a linear combination
+of delta functions had advantages compared to a basis of gaussians.
+We perform the convolution using \texttt{ficonv}, and opt for the
+implementation of Bramich's method (see \citealt{Pal_2009} \S~2.8).
 
@@
 A few brief notes on the algorithm to actually solve for the
-coefficients to the convolution kernel.
-The procedure implemented in \texttt{ficonv} is to grid
-the image, and within each grid element find the brightest non-saturated
-star. These isolated ``stamp'' stars are then used to solve for the
-coefficients of the kernel, by minimizing
-Equation~\ref{eq:chisq_conv} over the sum of all stamps.
+coefficients to the convolution kernel.  The procedure implemented in
+\texttt{ficonv} is to subdivide the image, and within each grid
+element find the brightest non-saturated star. These isolated
+``stamp'' stars are then used to solve for the coefficients of the
+kernel, by minimizing Equation~\ref{eq:chisq_conv} over the sum of all
+stamps.
 
@@
 accounts for variations due to unknown systematic instrument changes
-that affect many stars.  This latter step is effectively a principle
+that affect many stars.  This latter step is effectively a principal
 component analysis of all the light curves, in which the components
@@
 that we did not try but may explore in future work is to decorrelate
-against the scatter of the spacecraft quartnerion time-series
+against the standard deviation of the spacecraft quartnerion time-series
 \citep{vanderburg_hr858_2019}.
@@
 
-The observed RMS (black points) follows the usual shape,
-with photon noise dominating from $T=9$ to $T=12$, beyond which the
-onset of the ``sky'' background changes the overall slope of the
-curve to be more steep.
-For the brightest stars ($T\lesssim 9$), a ``systematic floor'' was an
-expected part of the mission's error budget \citep{ricker_transiting_2015}, 
-but 
-has not been observed in early
+The observed RMS (black points) follows the usual shape, with photon
+noise dominating from $T=9$ to $T=12$, beyond which the onset of the
+``sky'' background changes the overall slope of the curve to be more
+steep.  For the brightest stars ($T\lesssim 9$), a ``systematic
+floor'' was part of the mission's error budget
+\citep{ricker_transiting_2015}, but has not been observed in early
 reports of the photometric performance of various aperture photometry
@@
 the MIT-QLP \citealt{huang_tess_2018}, and \texttt{eleanor}
-\citealt{feinstein_eleanor_2019}).
-The fact that our light curves for the brightests stars are above this
-purported ``floor'', rather than below it, suggests that our
-image subtraction techniques could be introducing some small degree of
-noise to the light curves of the brightest stars.
-It is also true however that our largest aperture contains only about
-16 pixels, which is sub-optimal for stars brighter than $T\approx9$
-\citep[see][Figure~14]{Sullivan_et_al_2015}.
-Since the brightest stars are not the focus of the present work, we
-leave this issue unaddressed for the time being.
+\citealt{feinstein_eleanor_2019}).  The fact that our light curves for
+the brightest stars are above this purported ``floor'', rather than
+below it, suggests that our image subtraction techniques could be
+introducing some small degree of noise to the light curves of the
+brightest stars.  It is also true however that our largest aperture
+contains only about 16 pixels, which is sub-optimal for stars brighter
+than $T\approx9$ \citep[see][Figure~14]{Sullivan_et_al_2015}.  Since
+the brightest stars are not the focus of the present work, we leave
+this issue unaddressed for the time being.
 
@@
 positives in subsequent vetting.  We then performed an asymmetric
-sigma-clipping of $(50\sigma,5\sigma)$ to preserve transits while
-omitting flares and other positive flux excursions.
+sigma-clipping of $(50\sigma,5\sigma)$ about the median to preserve
+transits while omitting flares and other positive flux excursions.
 
@@
 
-We verified by injecting and recovering a 2.5 mmag central-transit
+We verified by injecting and recovering a 2.5 mmag, zero impact
+parameter 
 planet with variable period that this detrending approach marginally
@@
 has revealed \numberpcs planet candidates.
-\numberclusterpcs of these candidates are candidate cluter members,
+\numberclusterpcs of these candidates are candidate cluster members,
 and the remaining \numberzaripcs have indications of youth, relative

### 2019-07-11 paper/ms.tex
compile figure updates per JNW suggestions
Co-authored-by: joshwinn <jwinn@astro.princeton.edu>

@@
 catalog magnitude $T_{\rm cat}$, and returns the reference flux.
-Its coefficients have been fit per the procedure  just discussed.
+Its coefficients have been fit per the procedure just discussed,
+independently for each aperture.
 The difference image $D$ is equal to $I -  R\otimes K$,
@@
 for our pupose of finding planetary transits.
+For other applications, {\it e.g.,} stellar rotation period searches,
+it is almost certainly preferable to adopt a less forceful
+detrending approach.
 
@@
 
-\begin{figure}[!t]
+\begin{figure*}[!t]
 	\begin{center}
 		\leavevmode
-		\includegraphics[width=0.47\textwidth]{galacticcoords_cluster_field_star_positions.pdf}
+		\includegraphics[width=0.9\textwidth]{galacticcoords_cluster_field_star_positions.pdf}
 	\end{center}
@@
 	}
-\end{figure}
+\end{figure*}
 
@@
     Average autocorrelations of $10^4$ randomly selected light curves
-    from each sector. The 25$^{\rm th}$, 50$^{\rm th}$, and 75$^{\rm
-    th}$ percentiles at time lags spaced by one hour are shown by
-    dashed, solid, and dotted lines respectively.  The raw light
-    curves (column name \texttt{IRM}) are shown in gray, and the
-    TFA-detrended light curves are in black.
+    from each sector.
+    The medians at time lags spaced by one hour are shown for 
+    raw light
+    curves (column name \texttt{IRM}) in gray, and for
+    TFA-detrended light curves in black.
+    The gray bands display the 25$^{\rm th}$ to 75$^{\rm th}$ percentile
+    range for each type of light curve.
   \label{fig:avg_acf}
@@
 
-An HR diagram for the entire sample of stars on silicon
+An HR diagram for the entire sample of CDIPS stars on silicon
 is shown in Figure~\ref{fig:hrd} (top).
@@
 
-Finally, 
-Figure~\ref{fig:propermotions} shows the proper motions
-of the entire and close samples of stars on silicon.
-Each clump signifies a different star cluster. The central
-blob in the top figure is in fact two separate blobs,
-due to the different directions in the Galaxy being observed
-in Sectors 6 and 7.
+Finally, Figure~\ref{fig:propermotions} shows the proper motions of
+the entire and close samples of stars on silicon.  Each clump
+signifies a different star cluster. The largest overdensity in the top
+figure is composed mainly of field star contaminants. It has two
+subcomponents, due to the two different directions in the Galaxy being
+observed in Sectors 6 and 7.
 
@@
 mass interpolated from the \citet{pecaut_intrinsic_2013} table
-(assuming the star is a dwarf) to estimate $\log g$.  The
-uncertainties in e.g., the planetary radii and impact parameters were
-found using linear error propagation theory, under the idealized
-assumption that the covariance between all stellar and planetary
-parameters was zero.
+(assuming the star is a dwarf) to estimate $\log g$ for the
+limb-darkening.  The uncertainties in e.g., the planetary radii and
+impact parameters were found using linear error propagation theory,
+under the idealized assumption that the covariance between all stellar
+and planetary parameters was zero.
 

### 2019-07-13 drivers/paper_plot_all_figures.py
add figure of raw LCs (showcases systematics)

@@ -42,6 +42,11 @@ def main():
 
     sectors = [6,7]
 
+    plot_raw_light_curve_systematics(sector=7, cam=2, ccd=4, overwrite=1,
+                                     seed=42)
+    plot_raw_light_curve_systematics(sector=6, cam=1, ccd=2, overwrite=1,
+                                     seed=43)
+
     # fig N: average autocorrelation fn of LCs
     plot_avg_acf(sectors, overwrite=1, cleanprevacf=False)
 
@@ -96,6 +101,115 @@ def main():
     # fig N: histogram (or CDF) of TICCONT. unfortunately this is only
     # calculated for CTL stars, so by definition it has limited use
     plot_cdf_cont(sectors, overwrite=0)
+
+
+def get_Tmag(fitspath):
+    with fits.open(fitspath) as hdulist:
+        mag = hdulist[0].header['TESSMAG']
+    return mag
+
+def get_mag(fitspath, ap='IRM2'):
+    with fits.open(fitspath) as hdulist:
+        mag = hdulist[1].data[ap]
+    return mag
+
+def plot_raw_light_curve_systematics(sector=None, cam=None, ccd=None,
+                                     overwrite=False, N_to_plot=20, seed=42):
+
+    """
+    get a random sample of IRM2 light curves from the same camera & ccd. plot
+    them all together to show how we are systematics dominated.
+    """
+
+    outpath = os.path.join(
+        OUTDIR,
+        'raw_light_curve_systematics_sec{}cam{}ccd{}.png'.
+        format(sector, cam, ccd)
+    )
+    if os.path.exists(outpath) and not overwrite:
+        print('found {} and not overwrite; return'.format(outpath))
+        return
+
+    dfpath = os.path.join(
+        OUTDIR,
+        'raw_light_curve_systematics_sec{}cam{}ccd{}.csv'.
+        format(sector, cam, ccd)
+    )
+    if not os.path.exists(dfpath):
+        lcdir = (
+            '/nfs/phtess2/ar0/TESS/PROJ/lbouma/CDIPS_LCS/sector-{}/cam{}_ccd{}'.
+            format(sector, cam, ccd)
+        )
+        lcpaths = glob(os.path.join(lcdir, '*_llc.fits'))
+        Tmags = np.array([get_Tmag(l) for l in lcpaths])
+
[…]

### 2019-07-13 paper/ms.tex

@@
 
+\begin{figure*}[!t]
+	\begin{center}
+		\leavevmode
+		\includegraphics[width=0.9\textwidth]{target_star_positions.png}
+		%\gridline{\fig{target_star_cumulative_counts.pdf}{0.41\textwidth}{}}
+	\end{center}
+	\vspace{-0.8cm}
+	\caption{
+    Target star positions (blue) and predicted TESS
+    observing footprint (gray).
+    Target stars are either candidate members of clusters, or
+    else have other youth indicators (see \S~\ref{sec:starselection}).
+    Most will be observed for one or two lunar months over the course
+    of the TESS Prime Mission.
+    \label{fig:cdips_targets_positions}
+	}
+\end{figure*}
+
 \begin{figure}[!t]
@@
 		{\it Top.} Cumulative counts as a function of Gaia $Rp$-band
-		magnitude.  The stars are either candidate members of clusters, or
-		else have other youth indicators (see \S~\ref{sec:starselection}).
+		magnitude.  
 		{\it Middle.} Histogram of target star ages, for the subset of

### 2019-07-15 paper/ms.tex
minor paper update

@@
 
-\author[0000-0002-0514-5538]{L. G. Bouma (ORDER TBD)}
+\author[0000-0002-0514-5538]{L. G. Bouma}
 \affiliation{ Department of Astrophysical Sciences, Princeton
@@
 
+\begin{figure*}[!t]
+	\gridline{
+    \fig{raw_light_curve_systematics_sec6cam1ccd2.pdf}{0.48\textwidth}{}
+    \fig{raw_light_curve_systematics_sec7cam2ccd4.pdf}{0.48\textwidth}{}
+  }
+	\vspace{-0.5cm}
+	\caption{
+	Twenty randomly selected raw image-subtracted light curves drawn
+	from the same sector, camera,
+	and CCD, for stars with $T$-band magnitudes between 13 and 14.
+	A number of systematic trends are shared across the light curves.
+	The sector, camera, and CCD numbers are 6, 1, 2 (left) and 7, 2, 4 (right).
+	\label{fig:lc_systematics}
+	}
+\end{figure*}
+
 \begin{figure}[!t]
@@
 \end{figure}
-
 The preceding steps produce light curves that include both
@@
 accounts for variations due to unknown systematic instrument changes
-that affect many stars.  This latter step is effectively a principal
+that affect many stars.  This latter step is similar to a principal
 component analysis of all the light curves, in which the components
 are chosen as a subset of the light curves.
-In this sense TFA is similar to the PDC-MAP and ARC2 methods
-\citep{smith_pdc_2012,aigrain_robust_2017} except that these latter
-two methods are much more careful in their choice of basis vectors.
+In this sense TFA is similar to the Sys-Rem, PDC, and ARC2 methods
+\citep{tamuz_correcting_2005,smith_pdc_2012,aigrain_robust_2017}
+except that these latter methods make different choices for the basis
+vectors, and apply different procedures for determining the
+best-fitting coefficients of the linear model.
 
@@
 For these cases, we used the name given by \citet{dias_proper_2014}.
+The larger set of ``FSR'' infrared clusters from
+\citet{froebrich_FSR_2007} was incorporated to
+\citet{Kharchenko_et_al_2013}, and so did not present any
+complications.
 

### 2019-07-15 paper/collect_figures.sh

@@ -23,6 +23,11 @@ cp ${fdir}primary_mission_galacticmap_forproposal_cdipsoverplot.png \
 cp ${fdir}rms_vs_mag.pdf ${pdir}rms_vs_mag.pdf
 cp ${fdir}avg_acf.pdf ${pdir}avg_acf.pdf
 
+cp ${fdir}raw_light_curve_systematics_sec7cam2ccd4.pdf \
+   ${pdir}raw_light_curve_systematics_sec7cam2ccd4.pdf
+cp ${fdir}raw_light_curve_systematics_sec6cam1ccd2.pdf \
+   ${pdir}raw_light_curve_systematics_sec6cam1ccd2.pdf
+
 cp ${fdir}tls_sde_vs_period_scatter.pdf \
    ${pdir}tls_sde_vs_period_scatter.pdf
 

### 2019-07-18 drivers/merge_for_exofoptess.py
add observer info for PCs

@@ -3,6 +3,8 @@ from glob import glob
 import numpy as np, pandas as pd
 from cdips.utils import today_YYYYMMDD
 
+import imageutils as iu
+
 def main():
 
     paramglob = ("/home/lbouma/proj/cdips/results/fit_gold"
@@ -13,6 +15,41 @@ def main():
 
     outpath = ("/home/lbouma/proj/cdips/results/fit_gold/"
                "{}_sector6_and_sector7_gold_mergedfitparams.csv".
+               format(today_YYYYMMDD()))
+    df.to_csv(outpath, index=False, sep='|')
+    print('made {}'.format(outpath))
+
+    #
+    # above is the format exofop-TESS wants. however it's not particularly
+    # useful for followup. for that, we want: gaia IDs, magnitudes, ra, dec.
+    #
+    gaiaids = list(map(
+        lambda x: int(
+            os.path.basename(x).split('gaiatwo')[1].split('-')[0].lstrip('0')
+        ), parampaths
+    ))
+
+    lcnames = list(map(
+        lambda x: os.path.basename(x).replace('_fitparameters.csv','.fits'),
+        parampaths
+    ))
+
+    lcdir = '/nfs/phtess2/ar0/TESS/PROJ/lbouma/CDIPS_LCS/sector-?/cam?_ccd?/'
+    lcpaths = [ glob(os.path.join(lcdir,lcn))[0] for lcn in lcnames ]
+
+    # now get the header values
+    kwlist = ['RA_OBJ','DEC_OBJ','CDIPSREF','phot_g_mean_mag',
+              'phot_bp_mean_mag','phot_rp_mean_mag','TICID',
+              'TESSMAG','Gaia-ID']
+
+    for k in kwlist:
+        thislist = []
+        for l in lcpaths:
+            thislist.append(iu.get_header_keyword(l, k, ext=0))
+        df[k] = np.array(thislist)
+
+    outpath = ("/home/lbouma/proj/cdips/results/fit_gold/"
+               "{}_sector6_and_sector7_gold_fitparams_plus_observer_info.csv".
                format(today_YYYYMMDD()))
     df.to_csv(outpath, index=False, sep='|')
     print('made {}'.format(outpath))

### 2019-07-18 paper/ms.tex

@@
 K2-25b, discovered in the Hyades, has a radius ($3.43\,R_\oplus$) that
-is larger than older Kepler planets at similar insolation levels
+is larger than older Kepler planets around M dwarfs at similar insolation levels
 \citep{Mann_K2_25_2016}.  This inflated radius is perhaps a hint that
@@
 brighter than $T=16$ will be observed in the full-frame images over
-the first two years of TESS observations.  The actual number may be
-larger, as cluster membership catalogs are not yet complete, even at
-these relatively bright magnitudes \citep[{\it
+the first two years of TESS observations.  This count includes the
+``most probable'' members within each cluster's radius, which by the
+\citet[][]{kharchenko_global_2012} definition requires the independent
+kinematic, photometric, and spatial membership probabilities to each
+exceed 61\%.  The actual number of stars in clusters may be larger, as
+the membership catalogs are not yet complete, even at these relatively
+bright magnitudes \citep[{\it
 e.g.},][]{roser_nine_RSG_2016,cantat-gaudin_gaia_2018,cantat-gaudin_newOCs_2019}.
@@
 since the large pixel size and the high stellar surface density
-make aperture photometry unreliable.  However, it also means that a
+make aperture photometry unreliable.  
+However, it also means that a
 large number of stars in clusters that could yield transiting planets
@@
 pipeline.
+
+One way to quantify the blending problem is to ask what fraction of
+the total flux in a photometric aperture is contributed by a
+particular target star. Aperture photometry is reliable if this
+fraction is close to unity.  Based on the
+\citet{Kharchenko_et_al_2013} cluster membership data, and the density
+of background stars, we find that the median dilution fraction of
+stars with $T< 16$ is 0.13 for an aperture radius of 2 pixels.
+
+By combining difference imaging with forced-aperture photometry, we
+can avoid the primary effects of blending.  This is because in
+forced-aperture photometry the reference flux is determined from a
+calibrated catalog magnitude-to-flux relation.  The deviation from the
+reference is measured on the difference image.  Assuming that only a
+single source is causing the variability, blended neighbor stars only
+act to increase the poisson noise, and down not ``dilute'' transit
+signals, down to the angular resoution of the source catalog being
+used to determine the reference flux.  This is one of the main
+benefits of performing image subtraction in crowded fields.
 
@@
 
-In our initial stellar selection our aim is completeness, not
-accuracy.  If there has been a claim in the literature that a star
-should be considered a cluster member, or a young star, we would like
-to report a light curve for the star.  For stars that are
-photometrically interesting, we can perform post-hoc quality checks
-using Gaia-DR2 astrometry and photometry to assess cluster membership
-and youth.
+The probabilistic criteria for inclusion in our target star list is
+necessarily heterogeneous across different catalogs.  However, in our
+initial stellar selection our aim is completeness, not accuracy.  If
+there has been a claim in the literature that a star should be
+considered a cluster member, or a young star, we would like to err on
+the side of reporting a light curve for the star.  For stars that are
+photometrically interesting, we can then perform post-hoc quality
+checks using Gaia-DR2 astrometry and photometry to assess cluster
+membership and youth.
 
@@
 typically below 1 arcsecond.  The Dias catalog shows somewhat stronger
-crowding effects at the faint end compared to the Kharchenko catalog.
-The Kharchenko catalog also has a more lop-sided distribution of true
-{\it vs.}$\,$predicted $G$-band magnitudes.
+crowding effects at the faint end compared to the Kharchenko catalog,
+and likely has a larger number of false matches.
+At their faint ends, both catalogs show a tendency for true $G$-band
+magnitudes being somewhat larger than predicted $G$-band magnitudes,
+due to dust reddening.
 
@@
 
-After collecting the aforementioned lists, we
-merged them into a single table. We then queried the
-\texttt{gaiadr2.gaia\_source} table to retrieve their photometric $G$,
-$G_{\rm Rp}$, and $G_{\rm Bp}$ magnitudes, as well as their
-astrometric measurements $(\alpha, \delta, \mu_\alpha, \mu_\delta,
-\pi)$.  Finally, we required that $G_{\rm Rp} < 16$.
-
-All told, this procedure yielded 1{,}061{,}447 unique stars, from 13 distinct
-membership catalogs.
-
-107{,}647 of these stars, or about
-10\% of the collection, have cluster memberships reported by
-multiple authors.  The largest number of stars come from
-\citealt{dias_proper_2014} (44.3\% of stars), \citealt{Kharchenko_et_al_2013}
-(17.3\%), \citealt{cantat-gaudin_gaia_2018} (16.7\%), and \citealt{zari_3d_2018}
-(11.1\%). %FIXME how many in PMS vs UMS?
+After collecting the aforementioned lists, we merged them into a
+single table. We queried the \texttt{gaiadr2.gaia\_source} table to
+retrieve their photometric $G$, $G_{\rm Rp}$, and $G_{\rm Bp}$
+magnitudes, as well as their astrometric measurements $(\alpha,
+\delta, \mu_\alpha, \mu_\delta, \pi)$.  Finally, we required that
+$G_{\rm Rp} < 16$, which is roughly where the 1-hour photometric
+precision of TESS is predicted to reach 1\%
+\citep{ricker_transiting_2015}.
+
+All told, this procedure yielded 1{,}061{,}447 unique stars, from 13
+distinct membership catalogs.
+
+The relative fractions of stars from each catalog are shown in
+Figure~\ref{fig:cdips_targets}.
+The largest number of stars come from \citealt{dias_proper_2014}
+(44.3\% of stars), \citealt{Kharchenko_et_al_2013} (17.3\%),
+\citealt{cantat-gaudin_gaia_2018} (16.7\%), and \citealt{zari_3d_2018}
+(11.1\%, of which 7.8\% are OBA stars, and 3.3\% are pre-MS stars).
+107{,}647 of the stars, or about 10\%
+of the collection, have cluster memberships reported by multiple
+authors.  Since the membership probability calculations often use
+independent data and methods, agreement between multiple investigators
+on a given star's cluster membership is a helpful indication of it
+being a bonafide member.
 Stars reported in multiple catalogs have all available reference information
 concatenated.
+
+The fraction of target stars from each catalog which are bonafide
+cluster members should be understood to be heterogeneous.  For the
+\citet{dias_proper_2014} catalog, their membership calculation
+included only spatial and kinematic information, and we used a
+relatively low probability threshold when including their stars (based
+on the criteria \citealt{dias_proper_2014} used for their star
+counts).  The \citet{Kharchenko_et_al_2013} catalog combined spatial,
+kinematic, and photometric information to derive their membership
+probabilities.  We also used a somewhat more restrictive membership
+probability cut (again, following the criteria they used for their
+star counts), and so this sub-sample is likely less contaminated
+with field interlopers.
+\citet{cantat-gaudin_gaia_2018} used spatial, kinematic, and
+astrometric information from Gaia-DR2. Despite the lack of
+photometric information, the quality of the Gaia data suggest that the
+field contamination rate will be lowest for the
+\citet{cantat-gaudin_gaia_2018} sample.
 
@@
 We perform our processing using the calibrated images, their
-uncertainty maps, and their associated headers.  The spacecraft has
-four cameras, and each camera has four CCDs.  In the following
-analysis, all image-level operations are thus performed on the images
-for each CCD, so that at any instant of time there are 16 independent
-images that require analysis.
+corresponding uncertainty images, and the associated headers.  The
+spacecraft has four cameras, and each camera has four CCDs.  In the
+following analysis, all image-level operations are thus performed on
+the images for each CCD, so that at any instant of time there are 16
+independent images that require analysis.
 
@@
 (2019-02-01, spacecraft orbit \#22).
+Sectors 6 and 7 cover galactic longitudes from roughly 200$^\circ$ to 280$^\circ$, 
+with fair coverage within $\pm 20^\circ$ of the galactic plane
+(Figure~\ref{fig:cdips_targets_positions}).
 
@@
 are required.
-First, we convert the calibrated image from MAST into a
-single-extension FITS image, and trim to remove virtual rows and
-columns using the \texttt{SCIROWS}, \texttt{SCIROWE}, \texttt{SCCSA},
-and \texttt{SCCED} header values.
+First, we convert the multi-extension calibrated FITS image from MAST
+into a single-extension FITS image, and trim to remove virtual rows
+and columns using the \texttt{SCIROWS}, \texttt{SCIROWE},
+\texttt{SCCSA}, and \texttt{SCCED} header values.
 
@@
 remains even after flat-fielding \citep[see][\S
-7.3.5]{vanderspek_2018}.  With the exception of scattered-light
-caustics, which remain over small areas of less than 10\% of the
+7.3.5]{vanderspek_2018}.  With the exception of scattered light
+patches, which remain over small areas of less than 10\% of the
 frames, our ad-hoc procedure seems to adequately remove large spatial

### 2019-07-19 paper/ms.tex
add image processing figure

@@
 \end{figure}
+
+\begin{figure*}[!t]
+    \begin{center}
+        \leavevmode
+        \includegraphics[width=0.95\textwidth]{stages_of_image_processing_good.png}
+    \end{center}
+    \vspace{-0.6cm}
+    \caption{
+        Stages of image processing for an image taken during the middle
+        of an orbit.
+        {\it Top right}. Calibrated image.
+        {\it Top left}. Smooth background estimate.
+        {\it Middle right}. Calibrated image minus its median pixel value.
+        {\it Middle left}. Calibrated image minus smooth background.
+        {\it Bottom left}. Registered difference image.
+        {\it Bottom right}. Zoom of difference image.
+        Each image is $(2048\times2048)$ pixels, except for the bottom-right 
+        image, which is $(500\times500)$.
+        All images except the top-right have the same color map.
+        The sector, camera, and CCD are (6, 1, 2).
+        \label{fig:stages_good}
+    }
+\end{figure*}
+
+\begin{figure*}[!t]
+    \begin{center}
+        \leavevmode
+        \includegraphics[width=0.95\textwidth]{stages_of_image_processing_bad.png}
+    \end{center}
+    \vspace{-0.6cm}
+    \caption{
+        Same sector, camera and CCD as Figure~\ref{fig:stages_good}, but for an image taken during
+        perigee passage, when scattered light from the Earth is
+        prominent.
+        A number of systematic artifacts are present,
+        including vertical ``straps'' and small-scale structure in scattered light
+        patches.
+        The quality of astrometric registration in the difference image is also
+        worse, leading to larger residuals in the lower-right panel.
+        \label{fig:stages_bad}
+    }
+\end{figure*}
 
@@
 
-In order to pre-emptively address the background variations present in
+In order to preemptively address the background variations present in
 some frames due to scattered light from the Earth and Moon
@@
 remains even after flat-fielding \citep[see][\S
-7.3.5]{vanderspek_2018}.  With the exception of scattered light
-patches, which remain over small areas of less than 10\% of the
-frames, our ad-hoc procedure seems to adequately remove large spatial
-scale scattered light patches.
+7.3.5]{vanderspek_2018}.  
+The results are shown in the upper four panels of Figures~\ref{fig:stages_good}
+and~\ref{fig:stages_bad}.
+Features with spatial scales smaller than $\approx$48 pixel remain, 
+and large spatial scale scattered light patches are removed.
 
@@
 
-The procedure described above was first proposed by \citet{Alard_Lupton_1998}.
+The general procedure described above was first proposed by \citet{Alard_Lupton_1998}.
 It was reviewed and clarified by \citet{miller_optimal_2008}.
@@
 implementation of Bramich's method (see \citealt{Pal_2009} \S~2.8).
+The lower panels of
+Figure~\ref{fig:stages_good} show the procedure
+working well, and producing a ``clean'' difference image.
+Figure~\ref{fig:stages_bad} shows what happens for an
+image taken when scattered light from the Earth causes the
+model image $M_{xy}$ to be a poor fit to the target image $I_{xy}$, 
+leading to a number of systematic artificats.
 
 \subsubsection{Astrometric registration}
-We now describe a few implementation details we used to make the
+We now describe some implementation details we used to make the
 above high-level picture work.
@@
   \texttt{scipy} \citep{jones_scipy_2001},
+  \texttt{scikit-learn} \citep{sklearn_2011},
   \texttt{TagSpaces} (\url{tagspaces.org}),

### 2019-07-19 paper/collect_figures.sh

@@ -17,6 +17,12 @@ cp ${fdir}trex_overview.pdf ${pdir}pipelineoverview.pdf
 # rms vs mag 
 fdir=../results/paper_figures/
 
+cp ${fdir}stages_of_image_processing_good.png \
+   ${pdir}stages_of_image_processing_good.png
+
+cp ${fdir}stages_of_image_processing_bad.png \
+   ${pdir}stages_of_image_processing_bad.png
+
 cp ${fdir}primary_mission_galacticmap_forproposal_cdipsoverplot.png \
    ${pdir}target_star_positions.png
 

### 2019-07-21 cdips/lcproc/detrend.py
bugfix

@@ -2,6 +2,8 @@ from wotan import flatten
 import os, shutil
 from glob import glob
 
+import matplotlib
+matplotlib.use("AGG")
 import numpy as np, pandas as pd, matplotlib.pyplot as plt
 from astropy.io import fits
 

### 2019-07-21 paper/ms.tex
paper improvements

@@
 \end{figure}
+
 The preceding steps produce light curves that include both
-instrumental systematics as well as astrophysical variability.  The
-detrending approach adopted by the HAT group to remove systematic
-variability typically proceeds in a few sequential stages, as
-discussed by {\it e.g.} \citet{bakos_2010}, \citet{huang_high-precision_2015},
-and \citet{zhang_precision_2016}.
-
-The first detrending step commonly performed on ground-based data is
-``magnitude-fitting'': the raw magnitudes measured from the difference
-images are fit by a polynomial that depends on a combination of CCD
-position, sub-pixel position, and optionally catalog magnitude and
-color \citep[][\S~5.5]{zhang_precision_2016}.
-
-The second step is to decorrelate against external parameters that are
-known to affect the stellar flux measurements (EPD,
-\citealt[][]{bakos_2010}).  For ground-based data this may
-include zenith angle, or changing PSF parameters.  For TESS data, this
-might include CCD temperature, or the angles of the Moon and Earth
-relative to each camera's boresight.
-Some example ``external'' parameters that we
-include with our light curves are shown as functions of time in
+instrumental systematics as well as astrophysical variability.
+Figure~\ref{fig:lc_systematics} shows twenty stars of
+comparable brightness randomly selected from two CCDs.  Stars that are
+far apart on the same CCD share similar changes in flux.
+In other words, the instrumental systematics seem to dominate.
+This problem is generic to most wide-field photometric datasets, including
+those from {\it e.g.}, the WASP, HAT, and Kepler surveys.
+To remove the systematic variability, we adopted two different
+approaches: {\it (i)} the trend-filtering algorithm (TFA,
+\citealt{kovacs_trend_2005}), and {\it (ii)} a principal component analysis
+(PCA).
+
+However, a number of other approaches to the problem
+were possible. To encourage
+future improvements, we describe the
+possibility of decorrelating against external parameters
+(\S~\ref{subsubsec:external}), and also describe different approaches
+to ensemble detrending (\S~\ref{subsubsec:ensemble}), before
+explaining our implementation.
+
+\subsubsection{Decorrelating against external parameters}
+\label{subsubsec:external}
+
+Often, ensemble trends of stellar magnitude with CCD position,
+sub-pixel position, catalog magnitude, and color are present in
+datasets.  One detrending step that can be valuable is to fit and
+subtract a linear combination of these trends as they appear across
+many light curves \citep[{\it
+e.g.},][\S~5.5]{zhang_precision_2016}.
+
+A separate step for each light curve can then be to fit out linear
+correlations of stellar magnitude with ``external parameters'' (EPD,
+\citealt[][]{bakos_2010,huang_high-precision_2015}).  For ground-based
+data these parameters might include zenith angle, or changing PSF shape.  For
+TESS data, they might include CCD temperature, or the angles of the
+Moon and Earth relative to each camera's boresight.  
+They might also include the standard deviation of the spacecraft
+quartnerion time-series \citep{vanderburg_hr858_2019}.
+Some example ``external'' parameters that we include with our light
+curves are shown as functions of time in
 Figure~\ref{fig:external_parameter_timeseries}.
 
-The final step is to then decorrelate the measured brightnesses of
-stars against each other (TFA, \citealt{kovacs_trend_2005}).  This
-accounts for variations due to unknown systematic instrument changes
-that affect many stars.  This latter step is similar to a principal
-component analysis of all the light curves, in which the components
-are chosen as a subset of the light curves.
-In this sense TFA is similar to the Sys-Rem, PDC, and ARC2 methods
-\citep{tamuz_correcting_2005,smith_pdc_2012,aigrain_robust_2017}
-except that these latter methods make different choices for the basis
-vectors, and apply different procedures for determining the
-best-fitting coefficients of the linear model.
-
 We explored the possibility of fitting linear models of flux as
-functions of {\it e.g.,} temperature, shape parameters, centroid
-positions, and stellar colors.  We also briefly explored non-linear
+functions of {\it e.g.,} temperature, shape parameters, and centroid
+positions to each light curve.  We also briefly explored non-linear
 model fitting using $N$-dimensional B-splines to fit the flux,
@@
 spacecraft nears perigee.  The non-linear models showed some promise,
-but often seemed to overfit stellar variability signals.  One thought
-that we did not try but may explore in future work is to decorrelate
-against the standard deviation of the spacecraft quartnerion time-series
-\citep{vanderburg_hr858_2019}.
-
-Given these complications, for the time being we omit the step of
-``detrending'' as a function of external parameters. To enable further
-exploration of the issue, we include all the necessary vectors of {\it
-e.g.}, centroid positions, temperatures, and shape parameters in our
-reported light curves.
+but often seemed to overfit stellar variability signals.  Given these
+complications, for the time being we omitted the step of ``detrending''
+as a function of external parameters. To enable further exploration of
+the issue, we included all the necessary vectors of {\it e.g.},
+centroid positions, temperatures, and shape parameters in our reported
+light curves.
+
+\subsubsection{Ensemble detrending}
+\label{subsubsec:ensemble}
+
+The parameters that capture systematic trends are often poorly known.
+In such cases, an effective model of the systematics comes from
+constructing a set of vectors that empirically captures trends common
+to many stars.  Each target light curve is then assumed to be a linear
+combination of the trend vectors.
+
+The well-known algorithms, TFA, Sys-Rem, PDC-MAP, and ARC2, all take
+slightly different approaches to constructing this set of basis
+vectors, as well as to solving for the weights to assign each linear
+component
+\citep{kovacs_trend_2005,tamuz_correcting_2005,smith_pdc_2012,aigrain_robust_2017}.
+TFA selects individual ``template stars'' as basis vectors, and
+equally weights each template when solving for the coefficients via
+linear least squares.  PDC-MAP computes ``co-trending basis vectors''
+(CBVs) by applying singular value decomposition to the light curves
+that show the strongest mutual correlation.  It solves for the
+coefficients through a two-step procedure.  The first step is to
+calculate the coefficients through linear least squares.  The
+least-squares coefficients are then used to construct a prior over
+plausible coefficient values, which is then used to recompute the
+maximum likelihood coefficients for each star.  This latter step
+reduces overfitting for stars with variability not present in the set
+of CBVs.
+
+We opted to use two different detrending approaches, each aimed
+at a different use case.  For transit-search related science,
+we used TFA, as implemented by \texttt{VARTOOLS}
+\citep{kovacs_trend_2005,Hartman_Bakos_2016}.  For stellar
+astrophysics related work, we used a simple variant of PCA, as
+implemented in \texttt{scikit-learn} \citep{sklearn_2011}.  For
+self-consistency, we describe each method and its implementation in
+the following paragraphs.
+
+\paragraph{TFA detrending}
+
+The idea of TFA is as follows.  Suppose we have $M$ ``template
+stars'', which are a subsample of stars that represent all types of
+systematics across the dataset.  Each template star has a light curve
+with $N$ data points.  Denote the template time-series $X_j(i)$, where
+$j={1,\ldots,M}$ and $i={1,\ldots,N}$ is the time index.  We then want
+to find periodic signals in a target time-series $Y(i)$.  This is done
+by defining a filter function
+\begin{equation}
+  F(i) = \sum_{j=1}^{M} c_j X_j(i),
+\end{equation}
+for which the coefficients $c_j$ are found by minimizing
+\begin{equation}
+  \mathcal{D} = \sum_{i=1}^{N} \left[ Y(i) - A(i) - F(i) \right]^2.
+  \label{eq:tfa_to_minimize}
+\end{equation}
+When trying to find periodic signals, $A(i)$ represents our prior
+knowledge of the light curve's shape.  This prior is simply that stars
+on average maintain a constant brightness:
+\begin{equation}
+  A(i) = \langle Y \rangle = \frac{1}{N} \sum_{i=1}^{N} Y(i) = {\rm const.}
+\end{equation}
+If a signal is eventually found, for instance using the box-least
+squares method \citep{kovacs_box-fitting_2002}, this detrending
+process must then be repeated while accounting for our updated
+knowledge about the light curve's shape.
+
+Some implementation notes follow.  We selected template stars in two
+stages.  In the first stage, we fitted a parabola in the RMS-magnitude
+plane, and discarded stars more than $2\sigma$ away from the
+prediction of the fit.  We also required that these initial candidate
+stars have intermediate brightness ($8.5 > T > 13$), and have a
+relatively large number of time-series data points.  We then performed
+an initial iteration of TFA, on only the candidate template stars.  We
+inspected the resulting detrended light curves for residual structure
+by computing a Lomb-Scargle periodogram.  If the maximum-power peak
+had a false alarm probability below 0.1\%, we excluded the star from
+the list of candidate template stars, on the basis of its presumed
+periodic variability.  We then randomly selected at most 200 template
+stars from the remaining non-variable candidates.  The choice of
+number of template stars was discussed by \citet{kovacs_trend_2005},
+and is another free parameter in the broad problem of light curve
+production.  This choice is analogous to the issue of how many
+cotrending basis vectors to choose in PDC-MAP or ARC2
+\citep{aigrain_robust_2017}.  While the number of template stars can
+be optimized by constructing and minimizing a BIC-like quantity, a
+little overfitting is acceptable for our pupose of finding planetary
+transits.  For other applications, {\it e.g.,} stellar rotation period
+searches, it is almost certainly preferable to adopt a less forceful
+detrending approach.
+
+\paragraph{PCA detrending}
+
+To remove the largest systematic trends with minimal overfitting of
+{\it e.g.}, stellar rotation signals, we adopted a simple variant of PCA
+(see {\it e.g.}, \citealt{ivezic_statistics_2014} for a review).  A similar
+approach was taken by \citet{feinstein_eleanor_2019} in
+\texttt{eleanor}.  We derived the principal components for each CCD
+using the 200 template stars previously selected for TFA.
+We then modelled each target light curve as a linear combination of a
+subset of these principal components, with weights determined by
+linear least squares.
+
+To determine the ``optimal'' number of principal components to use, we
+performed a cross-validation analysis on the template stars using the
+components derived both from PCA, as well as a separate factor
+analysis.  As is typically the case when the noise variance is
+different for each ``feature'' (each point in time), we found that
+$k$-folding cross-validation using PCA failed to recover a plausible
+number of components\footnote{See for example
+\url{https://scikit-learn.org/stable/auto_examples/decomposition/plot_pca_vs_fa_model_selection.html}}.
+However, the factor analysis typically maximized the cross-validation
+score with anywhere from $10$ to $15$ components, which agreed with a
+visual analysis of the number of PCA components past which overfitting
+began.  We therefore used the maximum cross-validation score 
+from thefactor analysis
+as the number of principal components to use in each light curve.
+This number is
+documented in the \texttt{FITS} headers of each light curve.
 
@@
 % parameters in our reported light curves.
-
-Since most of the external parameter dependence is shared between
-stars, we opt instead to decorrelate the flux timeseries of each star
-against other stars in the frame.  We use the TFA algorithm proposed
-by \citet{kovacs_trend_2005}, which for self-consistency we describe
-here.
-
-The idea of the method is as follows.
-Suppose we have $M$ ``template stars'', which are a subsample of
-stars that represent all types of systematics across the dataset. 
-Each template star has a light curve with $N$ data points.
-Denote the template time-series $X_j(i)$, where $j={1,\ldots,M}$ and 
-$i={1,\ldots,N}$ is the time index.
-We then want to find periodic signals in a target time-series $Y(i)$.
-This is done by defining a filter function
-\begin{equation}
-F(i) = \sum_{j=1}^{M} c_j X_j(i),
-\end{equation}
-for which the coefficients $c_j$ are found by minimizing
-\begin{equation}
-\mathcal{D} = \sum_{i=1}^{N} \left[ Y(i) - A(i) - F(i) \right]^2.
-\label{eq:tfa_to_minimize}
-\end{equation}
-When trying to find periodic signals, $A(i)$ represents our prior
-knowledge of the light curve's shape.
-This prior is simply that stars on average maintain a constant brightness:
-\begin{equation}
-A(i) = \langle Y \rangle = \frac{1}{N} \sum_{i=1}^{N} Y(i) = {\rm const.}
-\end{equation}
-If a signal is eventually found, for instance using the box-least squares
-method \citep{kovacs_box-fitting_2002},
-this detrending process must then be repeated while accounting for our
-updated knowledge about the light curve's shape.
-
-Some implementation notes follow.
-We selected template stars in two stages.
-In the first stage, we fitted a parabola in the RMS-magnitude
-plane, and discarded stars more than $2\sigma$ away from the
-prediction of the fit.
-We also required that these initial candidate stars have intermediate
-brightness ($8.5 > T > 13$), and have a relatively large number
-of time-series data points.
-We then performed an initial iteration of TFA, on only the candidate
-template stars.
-We inspected the resulting detrended light curves for residual
-structure by computing a Lomb-Scargle periodogram.
-If the maximum-power peak had a false alarm probability below 0.1\%, 
-we excluded the star from the list of candidate template stars, on the
-basis of its presumed periodic variability.
-We then randomly selected at most 200 template stars from the remaining
-non-variable candidates. 
-The choice of number of template stars was discussed by
-\citet{kovacs_trend_2005}, and is another free parameter in
-the broad problem of light curve production.
-This choice is analogous to the issue of how many cotrending basis
-vectors to choose in PDC-MAP or ARC2 \citep{aigrain_robust_2017}.
-While the number of template stars can be optimized by constructing
-and minimizing a BIC-like quantity, a little overfitting is acceptable
-for our pupose of finding planetary transits.
-For other applications, {\it e.g.,} stellar rotation period searches,
-it is almost certainly preferable to adopt a less forceful
-detrending approach.
-
-Once the template stars were selected, we use the \texttt{VARTOOLS}
-program to perform the detrending \citep{Hartman_Bakos_2016}.
-This process was performed for each photometric aperture
-separately.
 
@@
 The planet candidate chosen for these figures
-(Gaia-DR2 \texttt{5541111035713815552} = TIC \texttt{134528212}) was
+(Gaia-DR2 \texttt{5541111035713815552} = TIC \texttt{110718787}) was
 chosen for the demonstration in part because it passes all
@@
 		\leavevmode
-		\includegraphics[width=0.98\textwidth]{gaiatwo0005541111035713815552-0007_page01.pdf}
+		\includegraphics[width=0.98\textwidth]{gaiatwo0005599752663752776192-0007_page01.pdf}
 	\end{center}
@@
 	\caption{
-		{\bf Transit search summary.} Periodograms from TLS and 
-		phase-dispersion minimization, as calculated 
-		with \texttt{astrobase.periodbase}, are shown in the top left and top center 
+		{\bf Transit search summary.}
+    Periodograms from TLS and phase-dispersion minimization, as
+    calculated with \texttt{astrobase.periodbase}, are shown in the
+    top left and top center
     \citep{bhatti_astrobase_2018,hippke_TLS_2019,stellingwerf_period_1978}.
-		The top three peaks from each 
-		method are shown in the second and third rows; the raw light curve is in the 
-		top-right. A small finder chart from DSS is inset to the top left, with
-		the 1.5-pixel radius aperture used to extract the light curve in orange.
+    The top three peaks from each method are shown in the second and
+    third rows; the raw light curve is in the top-right. A small
+    finder chart from DSS is inset to the top left, with the 1.5-pixel
+    radius aperture used to extract the light curve in orange.
 		\label{fig:pg1}
@@
 		\leavevmode
-		\includegraphics[width=0.98\textwidth]{gaiatwo0005541111035713815552-0007_page02.pdf}
+		\includegraphics[width=0.98\textwidth]{gaiatwo0005599752663752776192-0007_page02.pdf}
 	\end{center}
@@
 		{\bf Light curve diagnostics.} 
-		Time-series of raw flux (\texttt{IRM2}),  TFA-detrended flux (\texttt{TF2}), stellar-variability
-		detrended flux, and the background are shown as a function of
-		barycentric Julian date.
-		The overplotted dashed vertical lines are the ephemeris of the highest-power
-		TLS peak from Figure~\ref{fig:pg1}.
-		An important check is whether the flux dips are correlated with changes in the 
-		background level -- in this case, they are not.
-		The standard deviation and TESS magnitude are quoted in the upper right.
-		The red line in the second from the top plot is the windowed 
-		spline described in Section~\ref{subsec:ctois} -- in this case it is near its maximal
-		frequency.
+    Time-series of raw flux (\texttt{IRM2}),  TFA-detrended flux
+    (\texttt{TF2}), stellar-variability detrended flux, and the
+    background are shown as a function of barycentric Julian date.
+    The overplotted dashed vertical lines are the ephemeris of the
+    highest-power TLS peak from Figure~\ref{fig:pg1}.
+    An important check is whether the flux dips are correlated with
+    changes in the background level -- in this case, they are not.
+    The standard deviation and TESS magnitude are quoted in the upper
+    right.  The red line in the second from the top plot is the
+    windowed spline described in Section~\ref{subsec:ctois}, in this
+    case an essential step for finding the eclipse signal.
 		\label{fig:pg2}
@@
 		\leavevmode
-		\includegraphics[width=0.98\textwidth]{gaiatwo0005541111035713815552-0007_page03.pdf}
+		\includegraphics[width=0.98\textwidth]{gaiatwo0005599752663752776192-0007_page03.pdf}
 	\end{center}
@@
 	\caption{
-    {\bf Transit diagnostics.} The plots show the
-    maximally-detrended light curve (top); the phase-folded light
-    curve centered over $\pm3$ transit durations of the primary
-    transit (middle left); the secondary eclipse (middle right); the
-    odd-numbered transits (lower left); and the even-numbered transits
-    (lower right).
-    The stellar parameters ($T_{\rm eff}, R_\star, M_\star$) are taken from
-    TICv8 when available \citep{stassun_TIC8_2019}.
+    {\bf Transit diagnostics.}
+    The plots show the maximally-detrended light curve (top); the
+    phase-folded light curve centered over $\pm3$ transit durations of
+    the primary transit (middle left); the secondary eclipse (middle
+    right); the odd-numbered transits (lower left); and the
+    even-numbered transits (lower right).
+    The stellar parameters ($T_{\rm eff}, R_\star, M_\star$) are taken
+    from TICv8 when available \citep{stassun_TIC8_2019}.
     %Gaia-DR2 Apsis pipeline results when available
@@
     The first eight lines of text are parameters determined from the
-    best-fitting TLS model.
-    The one exception is the planet radius, which uses the stellar
-    radius as noted above.
+    best-fitting TLS model.  The one exception is the planet radius,
+    which uses the stellar radius as noted above.
     The ``flux contamination'' (\texttt{TICCONT}) from neighboring
@@
     manner as aperture-photometry reductions.
-    To estimate the transit to occulation depth ratio, the
-    phase-folded light curve is also coarsely fit via maximum
-    likelihood by a sum of two gaussians.
+    The significance of the odd-to-even asymmetry is quoted,
+    but given the strong rotational variability in this object (Figure~\ref{fig:pg2}),
+   	the apparent odd-even asymmetry could have been caused by the detrending process.
+    To estimate the transit to occulation depth ratio $\delta_{\rm tra}/\delta_{\rm occ}$,
+    the phase-folded light curve is also fit by a sum of two
+    gaussians (in this case, the fit failed).
     ``AstExc'' refers to the Gaia-DR2 astrometric excess, which can
@@
 		\leavevmode
-		\includegraphics[width=0.98\textwidth]{gaiatwo0005541111035713815552-0007_page04.pdf}
+		\includegraphics[width=0.98\textwidth]{gaiatwo0005599752663752776192-0007_page04.pdf}
 	\end{center}
@@
 		{\bf Light curves for increasing aperture sizes.} 
-		Apertures of radius 1, 1.5, and 2.25 pixels are shown from top to bottom.
-		The blue line is the reference transit depth from the best-fitting TLS model.
-		Any changes in depth with aperture size might indicate the need for a 
-		detailed pixel-level analysis.
+    Apertures of radius 1, 1.5, and 2.25 pixels are shown from top to
+    bottom.  The blue line is the reference transit depth from the
+    best-fitting TLS model.  Changes in depth with increasing aperture size
+    can indicate that the source of variability is off-center from the 
+    aperture, suggesting a photometric blend.
 		\label{fig:pg4}
@@
 		\leavevmode
-		\includegraphics[width=0.98\textwidth]{gaiatwo0005541111035713815552-0007_page05.pdf}
+		\includegraphics[width=0.98\textwidth]{gaiatwo0005599752663752776192-0007_page05.pdf}
 	\end{center}
@@
 		{\bf Cluster membership assessment diagnostics.}
-		The star was considered a candidate cluster member by the source(s) listed under
-		``Reference'', in this case \citet{dias_proper_2014}.
-		The name used in the Dias catalog in this case was \texttt{264-025831}, a
-		UCAC-4 identifier, which can be back-referenced to find that \citet{dias_proper_2014}
-		assigned this star a
-		membership probability in NGC 2546 of 98\%.
-		The base catalog for the plots is chiefly that of \citet{Kharchenko_et_al_2013},
-		due to its homogeneous parameter determination procedure (particularly for age).
-		If a match to the \citet{Kharchenko_et_al_2013} catalog is found, then the remaining
-		plots are populated.
-		Top-left shows the parallax, with orange points sampled from the Gaia-DR2
-		posterior, black points the other cluster members in the Kharchenko catalog,
-		and the blue line the claimed Kharchenko parallax for the cluster.
-		A large number of field contaminants are visible in this case.
-		Top-right are the Gaia proper motions, where against black points are cluster
-		members from Kharchenko, and the orange is the target star.
-    Bottom-left is the color-magnitude diagram, and bottom-right are
-    the on-sky positions.  In the text,
+    The star was considered a candidate cluster member by the
+    source(s) listed under ``Reference'', in this case
+    \citet{cantat-gaudin_gaia_2018}.  The name used in their catalog
+    in this case was \texttt{5599752663752776192}, a Gaia-DR2
+    identifier, which can be back-referenced to find that
+    \citet{cantat-gaudin_gaia_2018} assigned this star a membership
+    probability in Haffner 13 of just 10\%.
+    The base catalog for the plots is chiefly that of
+    \citet{Kharchenko_et_al_2013}, due to its homogeneous parameter
+    determination procedure (particularly for age).  If a match to the
+    \citet{Kharchenko_et_al_2013} catalog is found, then the remaining
+    plots are populated.  Top-left shows the parallax, with orange
+    points sampled from the Gaia-DR2 posterior, black points the other
+    cluster members in the Kharchenko catalog, and the blue line the
+    claimed Kharchenko parallax for the cluster.  A number of
+    field contaminants in the Kharchenko catalog are visible in this
+    case.  Top-right are the Gaia proper motions, where against black
+    points are cluster members from Kharchenko, and the orange is the
+    target star.  Bottom-left is the color-magnitude diagram, and
+    bottom-right are the on-sky positions.  In the text,
     \texttt{N1sr2} is the number of $1\sigma$ cluster members reported
-		by \citet{Kharchenko_et_al_2013} within the cluster angular radius;
-		$\log t$ is the base-10 logarithm of the age in years;
+    by \citet{Kharchenko_et_al_2013} within the cluster angular
+    radius; $\log t$ is the base-10 logarithm of the age in years;
     \texttt{type} matches the type codes provided by
-    \citet{Kharchenko_et_al_2013};
-    \texttt{K13Note} gives the description of the cluster from
-    \citet{Kharchenko_et_al_2013}, if available.
+    \citet{Kharchenko_et_al_2013}; \texttt{K13Note} gives the
+    description of the cluster from \citet{Kharchenko_et_al_2013}, if
+    available.
+    Extra caution must be taken when interpreting this set of plots,
+    since they can only show disagreement between the observed star's
+    properties and those of the listed Kharchenko members (and the
+    latter may be biased).
 		\label{fig:pg5}
@@
 		\leavevmode
-		\includegraphics[width=0.98\textwidth]{gaiatwo0005541111035713815552-0007_page06.pdf}
+		\includegraphics[width=0.98\textwidth]{gaiatwo0005599752663752776192-0007_page06.pdf}
 	\end{center}
@@
 		{\bf Imaging variability diagnostics.} 
-		This page is intended to help diagnose which stars are producing the observed
-		variability.
-		Top-left and top-center are the mean out-of-transit (OOT) and mean in-transit 
-		calibrated images (separate from any of our image-subtraction analysis).
-		The OOT images are based on the same number of exposures as the in-transit images
-		and split evenly before and after each transit \citep[following][]{bryson_identification_2013,kostov_l9859_2019}.
-		The yellow star is the target; cyan dots are the flux-weighted centroid of the entire
-		image for each transit event; small red crosses are WCS-projected locations of neighbor stars.
-		Middle-left is the most important sub-panel: the difference between
-		the OOT and in-transit mean images.
-		If the variability shown in background map (units: ADU) is off-target, the
-		transit is typically not from the target star.
-		Middle-center is the same, normalized by the uncertainty map.
-		Lower left and lower center show the DSS field in linear and log scales
-		at roughly the same pixel scale as the TESS image,
-		with the 1, 1.5, and 2.25 pixel-radius apertures in blue, orange, and green respectively.
+    This page is intended to help diagnose which stars are producing
+    the observed variability.  Top-left and top-center are the mean
+    out-of-transit (OOT) and mean in-transit calibrated images
+    (separate from any of our image-subtraction analysis).  The OOT
+    images are based on the same number of exposures as the in-transit
+    images and split evenly before and after each transit
+    \citep[following][]{bryson_identification_2013,kostov_l9859_2019}.
+    The yellow star is the target; cyan dots are the flux-weighted
+    centroid of the entire image for each transit event; small red
+    crosses are WCS-projected locations of neighbor stars.
+    Middle-left is the most important sub-panel: the difference
+    between the OOT and in-transit mean images.  If the variability
+    shown in background map (units: ADU) is off-target, the transit is
+    typically not from the target star.  Middle-center is the same,
+    normalized by the uncertainty map.  Lower left and lower center
+    show the DSS field in linear and log scales at roughly the same
+    pixel scale as the TESS image, with the 1, 1.5, and 2.25
+    pixel-radius apertures in blue, orange, and green respectively.
     The brightness of neighborhood stars is given on the far right.
-		Note the slight rotation difference between DSS and TESS images;
-		DSS images are aligned north-up, east-left; TESS images are oriented as closely as
-		possible to this system without actually performing the rotation.
+    Note the slight coordinate rotation difference between DSS and TESS images;
+    DSS images are aligned north-up, east-left; TESS images are
+    oriented as closely as possible to this system without actually
+    performing the rotation.
 		\label{fig:pg6}
@@
 
+% \begin{figure*}[!h]
+% 	\begin{center}
+% 		\leavevmode
+% 		\includegraphics[width=0.98\textwidth]{gaiatwo0005541111035713815552-0007_page01.pdf}
+% 	\end{center}
+% 	\vspace{-0.5cm}
+% 	\caption{
+% 		{\bf Transit search summary.} Periodograms from TLS and 
+% 		phase-dispersion minimization, as calculated 
+% 		with \texttt{astrobase.periodbase}, are shown in the top left and top center 
+% 		\citep{bhatti_astrobase_2018,hippke_TLS_2019,stellingwerf_period_1978}.
+% 		The top three peaks from each 
+% 		method are shown in the second and third rows; the raw light curve is in the 
+% 		top-right. A small finder chart from DSS is inset to the top left, with
+% 		the 1.5-pixel radius aperture used to extract the light curve in orange.
+% 		\label{fig:pg1}
+% 	}
+% \end{figure*}
+% 
+% \begin{figure*}[!h]
+% 	\begin{center}
+% 		\leavevmode
+% 		\includegraphics[width=0.98\textwidth]{gaiatwo0005541111035713815552-0007_page02.pdf}
+% 	\end{center}
+% 	\vspace{-0.5cm}
+% 	\caption{
+% 		{\bf Light curve diagnostics.} 
+% 		Time-series of raw flux (\texttt{IRM2}),  TFA-detrended flux (\texttt{TF2}), stellar-variability
+% 		detrended flux, and the background are shown as a function of
+% 		barycentric Julian date.
+% 		The overplotted dashed vertical lines are the ephemeris of the highest-power
+% 		TLS peak from Figure~\ref{fig:pg1}.
+% 		An important check is whether the flux dips are correlated with changes in the 
+% 		background level -- in this case, they are not.
+% 		The standard deviation and TESS magnitude are quoted in the upper right.
+% 		The red line in the second from the top plot is the windowed 
+% 		spline described in Section~\ref{subsec:ctois} -- in this case it is near its maximal
+% 		frequency.
+% 		\label{fig:pg2}
+% 	}
+% \end{figure*}
+% 
+% \begin{figure*}[!h]
+% 	\begin{center}
+% 		\leavevmode
+% 		\includegraphics[width=0.98\textwidth]{gaiatwo0005541111035713815552-0007_page03.pdf}
+% 	\end{center}
+% 	\vspace{-0.5cm}
+% 	\caption{
+%     {\bf Transit diagnostics.} The plots show the
+%     maximally-detrended light curve (top); the phase-folded light
+%     curve centered over $\pm3$ transit durations of the primary
+%     transit (middle left); the secondary eclipse (middle right); the
+%     odd-numbered transits (lower left); and the even-numbered transits
+%     (lower right).
+%     The stellar parameters ($T_{\rm eff}, R_\star, M_\star$) are taken from
+%     TICv8 when available \citep{stassun_TIC8_2019}.
+%     %Gaia-DR2 Apsis pipeline results when available
+%     %\citep{andrae_apsis_2018}.
+%     The first eight lines of text are parameters determined from the
+%     best-fitting TLS model.
+%     The one exception is the planet radius, which uses the stellar
+%     radius as noted above.
+%     The ``flux contamination'' (\texttt{TICCONT}) from neighboring
+%     stars is {\it never} taken into account, because transit depth
+%     dilution does not affect image subtraction analyses in the same
+%     manner as aperture-photometry reductions.
+%     To estimate the transit to occulation depth ratio, the
+%     phase-folded light curve is also coarsely fit via maximum
+%     likelihood by a sum of two gaussians.
+%     ``AstExc'' refers to the Gaia-DR2 astrometric excess, which can
+%     indicate hints of astrometric binarity in the system.
+%     ``$d_{\rm geom}$'' is the geometric distance from
+%     \citet{bailer-jones_distances_2018}.
+%     ``$R_\star + M_\star \rightarrow T_{b0}$'' gives the duration of a
+%     zero-eccentricity central transit based on the TICv8 stellar
+%     radius and mass if available. If the mass is not available, a
+%     stellar mass is interpolated from the
+%     \citet{pecaut_intrinsic_2013} table, under the assumption that the
+%     star is a dwarf.
+%     %\footnote{\url{http://www.pas.rochester.edu/~emamajek/EEM_dwarf_UBVIJHK_colors_Teff.txt}}.
+% 		\label{fig:pg3}
+% 	}
+% \end{figure*}
+% 
+% \begin{figure*}[!h]
+% 	\begin{center}
+% 		\leavevmode
+% 		\includegraphics[width=0.98\textwidth]{gaiatwo0005541111035713815552-0007_page04.pdf}
+% 	\end{center}
+% 	\vspace{-0.5cm}
+% 	\caption{
+% 		{\bf Light curves for increasing aperture sizes.} 
+% 		Apertures of radius 1, 1.5, and 2.25 pixels are shown from top to bottom.
+% 		The blue line is the reference transit depth from the best-fitting TLS model.
+% 		Any changes in depth with aperture size might indicate the need for a 
+% 		detailed pixel-level analysis.
+% 		\label{fig:pg4}
+% 	}
+% \end{figure*}
+% 
+% \begin{figure*}[!h]
+% 	\begin{center}
+% 		\leavevmode
+% 		\includegraphics[width=0.98\textwidth]{gaiatwo0005541111035713815552-0007_page05.pdf}
+% 	\end{center}
+% 	\vspace{-0.5cm}
+% 	\caption{
+% 		{\bf Cluster membership assessment diagnostics.}
+% 		The star was considered a candidate cluster member by the source(s) listed under
+% 		``Reference'', in this case \citet{dias_proper_2014}.
+% 		The name used in the Dias catalog in this case was \texttt{264-025831}, a
+% 		UCAC-4 identifier, which can be back-referenced to find that \citet{dias_proper_2014}
+% 		assigned this star a
+% 		membership probability in NGC 2546 of 98\%.
+% 		The base catalog for the plots is chiefly that of \citet{Kharchenko_et_al_2013},
+% 		due to its homogeneous parameter determination procedure (particularly for age).
+% 		If a match to the \citet{Kharchenko_et_al_2013} catalog is found, then the remaining
+% 		plots are populated.
+% 		Top-left shows the parallax, with orange points sampled from the Gaia-DR2
+% 		posterior, black points the other cluster members in the Kharchenko catalog,
+% 		and the blue line the claimed Kharchenko parallax for the cluster.
+% 		A large number of field contaminants are visible in this case.
+% 		Top-right are the Gaia proper motions, where against black points are cluster
+% 		members from Kharchenko, and the orange is the target star.
+%     Bottom-left is the color-magnitude diagram, and bottom-right are
+%     the on-sky positions.  In the text,
+% 		\texttt{N1sr2} is the number of $1\sigma$ cluster members reported
+% 		by \citet{Kharchenko_et_al_2013} within the cluster angular radius;
+% 		$\log t$ is the base-10 logarithm of the age in years;
+% 		\texttt{type} matches the type codes provided by
+%     \citet{Kharchenko_et_al_2013};
+%     \texttt{K13Note} gives the description of the cluster from
+%     \citet{Kharchenko_et_al_2013}, if available.
+% 		\label{fig:pg5}
+% 	}
+% \end{figure*}
+% 
+% \begin{figure*}[!h]
+% 	\begin{center}
+% 		\leavevmode
+% 		\includegraphics[width=0.98\textwidth]{gaiatwo0005541111035713815552-0007_page06.pdf}
+% 	\end{center}
+% 	\vspace{-0.5cm}
+% 	\caption{
+% 		{\bf Imaging variability diagnostics.} 
+% 		This page is intended to help diagnose which stars are producing the observed
+% 		variability.
+% 		Top-left and top-center are the mean out-of-transit (OOT) and mean in-transit 
+% 		calibrated images (separate from any of our image-subtraction analysis).
+% 		The OOT images are based on the same number of exposures as the in-transit images
+% 		and split evenly before and after each transit \citep[following][]{bryson_identification_2013,kostov_l9859_2019}.
+% 		The yellow star is the target; cyan dots are the flux-weighted centroid of the entire
+% 		image for each transit event; small red crosses are WCS-projected locations of neighbor stars.
+% 		Middle-left is the most important sub-panel: the difference between
+% 		the OOT and in-transit mean images.
+% 		If the variability shown in background map (units: ADU) is off-target, the
+% 		transit is typically not from the target star.
+% 		Middle-center is the same, normalized by the uncertainty map.
+% 		Lower left and lower center show the DSS field in linear and log scales
+% 		at roughly the same pixel scale as the TESS image,
+% 		with the 1, 1.5, and 2.25 pixel-radius apertures in blue, orange, and green respectively.
+% 		The brightness of neighborhood stars is given on the far right.
+% 		Note the slight rotation difference between DSS and TESS images;
+% 		DSS images are aligned north-up, east-left; TESS images are oriented as closely as
+% 		possible to this system without actually performing the rotation.
+% 		\label{fig:pg6}
+% 	}
+% \end{figure*}
+
 \end{document}

### 2019-07-21 paper/collect_figures.sh

@@ -91,7 +91,9 @@ cp ${fdir}proj1500-s0006-cam1-ccd1-combinedphotref-onenight_spocwcs_quiver_meas_
    ${pdir}astromresidual_quiver.pdf
 
 # pdftk burst the chosen vetting pdf
-pdftk vet_hlsp_cdips_tess_ffi_gaiatwo0005541111035713815552-0007_tess_v01_llc.pdf burst output gaiatwo0005541111035713815552-0007_page%02d.pdf
+pdftk \
+  vet_hlsp_cdips_tess_ffi_gaiatwo0005599752663752776192-0007_tess_v01_llc.pdf \
+  burst output gaiatwo0005599752663752776192-0007_page%02d.pdf
 
 ##########################################
 

### 2019-07-22 paper/ms.tex
add plot_external_parameters_vs_time

@@
 		\leavevmode
-		\includegraphics[width=0.47\textwidth]{epdparams_vs_time.png}
+		\includegraphics[width=0.47\textwidth]{external_parameters_vs_time_sec6cam1ccd1.pdf}
 	\end{center}
@@
 	\caption{
-		Timeseries of ``external parameters'' for a representative
-			star over one sector.
-			{\it Top}: Instrumental raw magnitude (with a particular
-		aperture size), as a function of time.  {\it Second and third from
-			top}: $x$ and $y$ centroid positions as a function of time.
-		Continuing in order are the CCD temperature, the $(s,d,k)$ shape
-		parameters, and the measured background value.
-		Most of the apparent variability is instrumental.
+    Timeseries of ``external parameters'' for a representative star
+    over one sector.  {\it Top}: Instrumental raw magnitude (with a
+    particular aperture size), as a function of time.  {\it Second and
+    third from top}: $x$ and $y$ centroid positions as a function of
+    time.  Continuing in order are the $(s,d,k)$ PSF shape parameters,
+    the CCD temperature,  and the measured background value.  Most of
+    the apparent variability is instrumental.  Momentum dumps are
+    marked with vertical dashed lines.
 		\label{fig:external_parameter_timeseries}

### 2019-07-22 drivers/paper_plot_all_figures.py

@@ -46,11 +46,15 @@ LCDIR = '/nfs/phtess2/ar0/TESS/PROJ/lbouma/CDIPS_LCS/'
 
 def main():
 
+    #FIXME NEED TO VERIFY THIS WORKS
     plot_detrended_light_curves(sector=6, cam=1, ccd=2, overwrite=1, seed=43)
 
     assert 0
 
     sectors = [6,7]
+
+    plot_external_parameters_vs_time(sector=6, cam=1, ccd=1, overwrite=1,
+                                     seed=43)
 
     # fig N: RMS vs catalog T mag for LC stars, with TFA LCs
     plot_rms_vs_mag(sectors, overwrite=1)
@@ -128,6 +132,140 @@ def get_mag(fitspath, ap='IRM2'):
     with fits.open(fitspath) as hdulist:
         mag = hdulist[1].data[ap]
     return mag
+
+
+def plot_external_parameters_vs_time(sector=6, cam=1, ccd=2, overwrite=1,
+                                     seed=42):
+
+    outpath = os.path.join(
+        OUTDIR,
+        'external_parameters_vs_time_sec{}cam{}ccd{}.png'.
+        format(sector, cam, ccd)
+    )
+    if os.path.exists(outpath) and not overwrite:
+        print('found {} and not overwrite; return'.format(outpath))
+        return
+
+    #
+    # data dir with what lcs exist, and what their T mags are.
+    #
+    dfpath = os.path.join(
+        OUTDIR,
+        'detrended_light_curves_sec{}cam{}ccd{}.csv'.
+        format(sector, cam, ccd)
+    )
+    if not os.path.exists(dfpath):
+        lcdir = (
+            '/nfs/phtess2/ar0/TESS/PROJ/lbouma/CDIPS_LCS/sector-{}/cam{}_ccd{}'.
+            format(sector, cam, ccd)
+        )
+        lcpaths = glob(os.path.join(lcdir, '*_llc.fits'))
+        Tmags = np.array([get_Tmag(l) for l in lcpaths])
+
+        df = pd.DataFrame({'lcpaths':lcpaths,'Tmags':Tmags})
+        df.to_csv(dfpath, index=False, sep=',')
+    else:
+        df = pd.read_csv(dfpath, sep=',')
+
+    sel = (df['Tmags'] > 13) & (df['Tmags'] < 14)
+
+    lcpaths = nparr(df['lcpaths'][sel])
+
+    np.random.seed(seed)
[…]

### 2019-07-22 paper/collect_figures.sh

@@ -17,6 +17,9 @@ cp ${fdir}trex_overview.pdf ${pdir}pipelineoverview.pdf
 # rms vs mag 
 fdir=../results/paper_figures/
 
+cp ${fdir}external_parameters_vs_time_sec6cam1ccd1.pdf \
+   ${pdir}external_parameters_vs_time_sec6cam1ccd1.pdf
+
 cp ${fdir}stages_of_image_processing_good.png \
    ${pdir}stages_of_image_processing_good.png
 

### 2019-07-22 paper/ms.tex
update paper

--- 2019-07-21 paper/ms.tex
@@
 		\leavevmode
-		\includegraphics[width=0.47\textwidth]{epdparams_vs_time.png}
+		\includegraphics[width=0.44\textwidth]{external_parameters_vs_time_sec6cam1ccd1.pdf}
 	\end{center}
@@
 	\caption{
-		Timeseries of ``external parameters'' for a representative
-			star over one sector.
-			{\it Top}: Instrumental raw magnitude (with a particular
-		aperture size), as a function of time.  {\it Second and third from
-			top}: $x$ and $y$ centroid positions as a function of time.
-		Continuing in order are the CCD temperature, the $(s,d,k)$ shape
-		parameters, and the measured background value.
-		Most of the apparent variability is instrumental.
+    The variability in flux is sometimes correlated with variability in
+	``external'' parameters, shown here for a representative star
+    over two orbits.  {\it Top}: Instrumental raw magnitude (with a
+    particular aperture size), as a function of time.  
+    Continuing in order are $x$ and $y$ centroid positions as a functions of
+    time, the $(s,d,k)$ PSF shape parameters,
+    the CCD temperature,  and the measured background value.
+    Differential aberration affect the centroid position over the span of each orbit.
+    Momentum dumps are
+    marked with vertical dashed lines, and affect the measured shapes of stars.
 		\label{fig:external_parameter_timeseries}

### 2019-07-22 paper/ms.tex
paper: add detrended lc plot

@@
 	\caption{
-    The variability in flux is sometimes correlated with variability in
-	``external'' parameters, shown here for a representative star
+    The variability in flux is sometimes correlated with variability
+    in ``external'' parameters, shown here for a representative star
     over two orbits.  {\it Top}: Instrumental raw magnitude (with a
-    particular aperture size), as a function of time.  
-    Continuing in order are $x$ and $y$ centroid positions as a functions of
-    time, the $(s,d,k)$ PSF shape parameters,
-    the CCD temperature,  and the measured background value.
-    Differential aberration affect the centroid position over the span of each orbit.
-    Momentum dumps are
-    marked with vertical dashed lines, and affect the measured shapes of stars.
+    particular aperture size), as a function of time.  Continuing in
+    order are $x$ and $y$ centroid positions as a functions of time,
+    the $(s,d,k)$ PSF shape parameters, the CCD temperature,  and the
+    measured background value.  Differential aberration affect the
+    centroid position over the span of each orbit.  Momentum dumps are
+    marked with vertical dashed lines, and affect the measured shapes
+    of stars.
 		\label{fig:external_parameter_timeseries}
+	}
+\end{figure}
+
+\begin{figure}[!t]
+	\begin{center}
+		\leavevmode
+		\includegraphics[width=0.47\textwidth]{detrended_light_curves_sec6cam1ccd1.pdf}
+	\end{center}
+	\vspace{-0.5cm}
+	\caption{
+    Twenty randomly selected light curves drawn
+    from the same sector, camera,
+    and CCD, for stars with $T$-band magnitudes between 13 and 14.
+    Each light curve is shown from top to bottom in raw, PCA-detrended, and
+    TFA-detrended forms.
+    Stellar rotation signals are usually preserved in the PCA light curves,
+    while TFA tends to either filter them out, or to distort them.
+		\label{fig:detrended}
 	}

### 2019-07-23 paper_I/ms.tex
add paper I
we're splitting it.

paper I: before there were no light curves. now there are some.

paper I: before there were no PCs. now there are some.

--- 2019-07-22 paper/ms.tex
@@
 \title{
-  Light Curves \& Planet Candidates in Open Clusters from TESS Sectors 6 \& 7
+  CDIPS. I. Light Curves in Open Clusters from TESS Sectors 6 \& 7
 }
@@
   The Transiting Exoplanet Survey Satellite (TESS) has begun to
-  photometrically monitor almost every star cluster in
-  the solar neighborhood.
+  photometrically monitor almost every star cluster in the solar
+  neighborhood.
   % Aims
-  To make light curves of stars that could be members of stellar
-  associations, moving groups, or open clusters, we have begun a
-  Cluster Difference Imaging Photometric Survey (CDIPS).
-  %
-  Our aim is to discover giant transiting planets with known
-  ages, and to probe the exoplanet size and separation distributions for
-  planets younger than one gigayear.
-  %
-  In this study, we made \numberlcs light curves of candidate young
-  stars, across \numberclusters distinct clusters.
-  Each light curve represents between 20 and 25 days of observations
-  of a star brighter than $G_{Rp}=16$, sampled at 30 minute cadence.
+  Using the TESS images, we have begun a Cluster Difference Imaging
+  Photometric Survey (CDIPS), in which we are focusing on stars that
+  are candidate cluster members, or else show other indications of
+  youth relative to field stars.
+  %
+  Our aims are to discover giant transiting planets with known
+  ages, and also to provide a light curve sample fit for studies in
+  stellar astrophysics.
+  %
+  For this work, we made \numberlcs light curves of candidate young
+  stars, across \numberclusters distinct clusters.  Each light curve
+  represents between 20 and 25 days of observations of a star brighter
+  than $G_{Rp}=16$, sampled at 30 minute cadence.
   % Methods
-  We describe in detail the image subtraction and time-series analysis 
-  techniques we used to create the light curves, which
-  have noise properties that agree with theoretical expectations.
-  % Results
-  We then highlight the \numberpcs planet candidates we identified in
-  an initial search.
-  \numberclusterpcs of these planet candidates are candidate cluster
-  members, and the remaining \numberzaripcs have indications of youth
-  relative to field stars.
-  We describe the vetting procedures that these objects have survived,
-  and emphasize the additional spectroscopic, photometric, and imaging
-  observations that are needed to determine (i) whether these candidates
-  are planets and (ii) for which cases the host stars are cluster members.
+  We describe the image subtraction and time-series analysis
+  techniques we used to create the light curves, which have noise
+  properties that agree with theoretical expectations.
   %
@@
   %
-  The light curves and vetting reports are available at
-  \stscilink.
+  The light curves are available at \stscilink.
 \end{abstract}
@@
 
-Many evolutionary processes are expected to occur over the lives of
-stars and exoplanets; it would be interesting to statistically observe
-these changes as functions of time.  However, since most dwarf stars
-do not appreciably change until evolving off the
-main sequence, creative approaches must be used to infer stellar ages
-\citep{soderblom_ages_2010}.  One approach beginning to bear fruit in
-exoplanet studies is to search for planets in coeval groups of stars,
-hereafter ``clusters''.  This includes the open clusters of yore, as
-well as the moving groups and stellar associations that began to be
-uncovered in the late 1990s \citep{zuckerman_young_2004}.  The ages of
-these stellar ensembles are inferred through isochrone analyses of
-color-magnitude diagrams, using an appropriate combination of
-main-sequence turnoff locations, pre-main-sequence turnon locations,
-and averaged MS isochronal ages across known cluster members
-\citep[{\it e.g.},][Section 3.4.3]{kharchenko_global_2012}.  Once
-calibrated, gyrochronology can also be used to verify the age of a
-stellar ensemble \citep[{\it
-e.g.},][]{barnes_color-period_2015,meibom_spin-down_2015,curtis_tess_2019}.
-The ages of planets discovered in these cluster stars are then assumed
-to equal the age of the larger stellar ensemble.
-
-The first planets to be detected in open clusters were found through
-radial velocity (RV) measurements of red giants in the Hyades and
-NGC~2423 \citep{Sato_et_al_2007,lovis_mayor_2007}.
-Subsequent spectroscopic searches in Praesepe led to the detection of
-the first hot Jupiter in a cluster \citep{Quinn_et_al_2012}, and also
-the first multi-planet system in a cluster \citep{Malavolta_et_al_2016}.
-The youngest RV detections have come from surveys of T Tauri stars in the
-Taurus star-forming region, which showed signals of the hot Jupiter
-\citep[V830~Tau~b][]{donati_hj_2016} and of a giant planet on a 9-day orbit
-\citep[CI~Tau~b][]{johns-krull_candidate_2016,flagg_co_2019}.
-A final RV survey of note was conducted by
-\citet{brucalassi_search_2017}, who followed 88 stars in M~67 over 7
-years.  They reported detections of three hot Jupiters around main
-sequence stars, and of one giant planet around an evolved star.
-
-The transit method was comparatively slow to catch up.  Deep transit
-searches typically comprising days to weeks of observations were
-performed for NGC~2158, 6791, and 1245, among other clusters
-\citep{mochejska_planets_2005,mochejska_planets_2006,burke_survey_2006}.
-Related projects include a search of M~37 by
-\citet{hartman_MMT_IV_2009}, of Praesepe by
-\citet{pepper_photometric_2008}, and of nine young clusters in the
-solar neighborhood by the Monitor team
-\citep{aigrain_monitor_2007,irwin_monitordata_2007,miller_monitor_2008}.
-Though these studies led to measurements of stellar rotation periods
-\citep{hartman_rotation_2009,Irwin_NGC2516_2007} as well as the
-discovery of pre-main-sequence (PMS) eclipsing binaries (EBs)
-\citep{irwin_monitor_PMSEB_2007}, no definitive transiting planets in
-open clusters were found.  Transit searches in globular clusters were
-similarly met with null results \citep{gilliland_lack_2000,
-weldrake_searching_2006}.  These searches were typically sensitive to
-planets larger than Jupiter, on $\lesssim 3$ day orbital periods.  Hot
-Jupiter occurrence rate limits were derived at the $\lesssim 5\%$
-level \citep[{\it e.g.},][]{burke_survey_2006, hartman_MMT_IV_2009}.
-The modern 0.5-1\% occurrence rate suggests that these early transit
-surveys needed a greater data volume, at higher precision for
-detection to be possible
-\citep{mayor_harps_2011,wright_frequency_2012,howard_planet_2012,petigura_metallicity_2018}.
-
-Kepler \citep{borucki_kepler_2010} observed enough stars for long
-enough and with sufficient precision to detect transiting planets in
-open clusters:  Kepler-66b and 67b, in the gigayear-old NGC~6811
-\citep{Meibom_et_al_2013}.  Though a broken reaction wheel ended the
-prime Kepler mission, the repurposed K2 \citep{howell_k2_2014}
-switched between fields along the ecliptic every quarter-year, and was
-able to observe far more clusters and young stars.  The resulting
-discoveries made by K2 through its surveys of the Pleiades, Hyades,
-Praesepe, and Upper Sco were a major inspiration for the present work.
-
-K2-25b, discovered in the Hyades, has a radius ($3.43\,R_\oplus$) that
-is larger than older Kepler planets around M dwarfs at similar insolation levels
-\citep{Mann_K2_25_2016}.  This inflated radius is perhaps a hint that
-the planet is contracting, or losing its atmosphere \citep[{\it
-e.g.},][]{Fortney_et_al_2007,Owen_Wu_2013,Fulton_et_al_2017}.  The
-super-Neptune sized K2-33b ($P\approx 5.4\,{\rm d}$), found in Upper
-Sco, showed that at least some close-in planets must form within about
-10 Myr \citep{Mann_K2_33b_2016,David_et_al_2017}.  Further discoveries
-included six transiting planets in Praesepe
-\citep{obermeier_k2_2016,Mann_et_al_2017}, a long-period candidate
-super-Earth in the Hyades \citep{vanderburg_zeitVII_2018}, the
-three-planet K2-136 system in the Hyades
-\citep{ciardi_k2-136_2018,livingston_three_2018,mann_ZEITVI_2018}, and
-later the two-planet system K2-264 in Praesepe
-\citep{rizzuto_zeitVIII_2018,livingston_k2-264_2019}.  There has also
-recently been a detection by K2 of a Jupiter-sized planet orbiting
-every 24 days around V1298~Tau \citep{david_v1298_2019}.
-
-A significant amount of effort continues to be devoted towards the
-discovery and characterization of planets around young stars.
-Sometimes, cluster membership may not even be necessary, if a star's
-youth can be inferred from combined rotation, activity, and kinematic
-indicators \citep[{e.g.}, K2-233;][]{david_k2-233_2018}.  To
-investigate demographics in time, the detection sensitivities and
-reliabilities of these searchers need to be calibrated, likely with a
-machinery similar to that outlined by \citet{rizzuto_zeitV_2017}.  A
-separate requirement for population studies to be statistically
-robust, imposed by the geometric rarity of transits, is that many tens
-of thousands of stars with known ages must be monitored at high
-precision.
+Each of the $\sim$3000 known star clusters of the Milky Way is a gift
+to astrophysics, providing a sample of stars that vary widely in mass
+but all have approximately the same age and composition.  Time-series
+photometry of clusters has many applications. By measuring rotation
+periods over a range of ages, we can study the angular momentum
+evolution of stars and improve our ability
+to determine stellar ages through gyrochronology \citep[{\it
+e.g.},][]{skumanich_time_1972,barnes_color-period_2015,meibom_spin-down_2015,curtis_tess_2019}.
+By measuring eccenticities as a function age, we can study the tidal
+evolution of binaries (CITE). The detection of eclipsing binaries can
+also lead to the precise determination of the absolute dimensions of
+the stars and stringent tests of stellar-evolutionary models (CITE).
+Finally, transiting exoplanets discovered in clusters can shed light
+on the timescales for processes in planet formation, evolution, and
+migration \citep[{\it
+e.g.},][]{Fortney_et_al_2007,Mann_K2_33b_2016,David_et_al_2017}, as
+well as on the effects of metallicity \citep[{\it
+e.g.},][]{fischer_planet-metallicity_2005,petigura_metallicity_2018}.
 
@@
 kinematic, photometric, and spatial membership probabilities to each
-exceed 61\%.  The actual number of stars in clusters may be larger, as
-the membership catalogs are not yet complete, even at these relatively
-bright magnitudes \citep[{\it
+exceed 61\%.  The actual number of stars in clusters is larger, as the
+membership catalogs are not yet complete, even down to these
+relatively bright magnitudes \citep[{\it
 e.g.},][]{roser_nine_RSG_2016,cantat-gaudin_gaia_2018,cantat-gaudin_newOCs_2019}.
-% Our target list currently sits at $\approx 1.0\times10^6$ candidate
-% young stars, perhaps one-third of which are bonafide cluster members
-% (see \S~\ref{sec:starselection}).
 
@@
 severe near the galactic plane that the TESS Candidate Target List has
-deprioritized 2-minute targets at galactic latitudes less than
-$\approx 15^\circ$~\citep{stassun_TIC_2018,stassun_TIC8_2019}, which
-includes almost all star clusters\footnote{TICv8 has updated this to
+deprioritizes 2-minute targets at galactic latitudes less than
+$\approx 15^\circ$~\citep{stassun_TIC_2018,stassun_TIC8_2019}. This
+includes almost all star clusters\footnote{TICv8 has updated the cutoff to
 $10^\circ$, but for the first year of TESS observations, the number
@@
 
-By combining difference imaging with forced-aperture photometry, we
-can avoid the primary effects of blending.  This is because in
-forced-aperture photometry the reference flux is determined from a
+By combining difference imaging \citep{Alard_Lupton_1998,miller_optimal_2008} 
+with forced-aperture photometry, we
+can avoid the primary effects of blending.  
+In this procedure, the positions of stars are predicted from an 
+astrometric solution, while the reference fluxes are determined from a
 calibrated catalog magnitude-to-flux relation.  The deviation from the
 reference is measured on the difference image.  Assuming that only a
-single source is causing the variability, blended neighbor stars only
-act to increase the poisson noise, and down not ``dilute'' transit
-signals, down to the angular resoution of the source catalog being
+single source is causes the variability, blended neighbor stars only
+act to increase Poisson noise, and do not ``dilute'' transit
+signals, down to the angular resolution of the source catalog being
 used to determine the reference flux.  This is one of the main
 benefits of performing image subtraction in crowded fields.
-
-Of course, not all young stars are in crowded fields.  TESS
-observations of a few nearby non-crowded stellar assocations have
-already begun bearing fruit, notably DS Tuc Ab (TOI 200;
-\citealt{benatti_dstuc_2019,newton_dstuc_2019}), and perhaps the
-planet candidates TOI-450 and 451.  These objects are close and
-bright, and will be benchmark systems because they are relatively easy
-to characterize.  However, statistical studies of how stellar and
-planetary properties are affected by ages require tens of thousands of
-target stars.  This motivates us to also search the more crowded, and
-fainter fields.
 
@@
 difference imaging technique because of its benefits in modelling
-complex backgrounds in crowded regions.  While we hope to discover at
-least a few giant transiting planets, a separate hope is that the
-dataset might be useful to those wishing to study the time evolution
-of stellar processes.
-
-In the following, \S~\ref{sec:starselection} describes how we selected
-target stars. \S~\ref{sec:method} presents the photometric and image
-processing methods we used to produce light curves for these stars.
-The statistical properties of the \numberlcs light curves from TESS Sectors
-6 and 7 are then summarized (\S~\ref{subsec:lcstatistics}).  The
-procedure we used to identify and vet transiting planets is
-described in \S~\ref{subsec:identifying_ctois}, and the candidate
-planets are presented in \S~\ref{subsec:ctois}.
-\S~\ref{sec:discussion} discusses the additional work that is required
-to confirm or reject the planetary nature of these objects, and
-\S~\ref{sec:conclusion} summarizes our findings.
+complex backgrounds in crowded regions.  While we hope to
+discover at least a few giant transiting planets, the focus of the
+present study is to produce a more general-purpose dataset,
+applicable for studies both in exoplanetary as well as stellar
+astrophysics.
+
+For the remainder of this work, we adopt the term ``star cluster'', or
+simply cluster, to refer to a coeval group of stars.  This includes
+the open clusters of yore, as well as the moving groups and stellar
+associations that have been discovered since the late
+1990s \citep{zuckerman_young_2004}.
+
+The plan of action is as follows. In \S~\ref{sec:starselection}, we
+describe how target stars were selected. \S~\ref{sec:method} presents
+the photometric and image processing methods we used to produce light
+curves for these stars.  The statistical properties of the \numberlcs
+light curves from TESS Sectors 6 and 7 are then summarized
+(\S~\ref{subsec:lcstatistics}).  
+An example of how we might use the data to identify pulsating
+stars, eclipsing binaries, and transiting planets is then
+given
+(\S~\ref{subsec:identifying_variability}). 
+\S~\ref{sec:conclusion}
+summarizes our findings, and discusses them with an eye towards
+the studies we hope this and subsequent rounds of data processing
+will enable.
 
@@
 	\caption{
-    Target star positions (blue) and predicted TESS
-    observing footprint (gray).
-    Target stars are either candidate members of clusters, or
-    else have other youth indicators (see \S~\ref{sec:starselection}).
-    Most will be observed for one or two lunar months over the course
-    of the TESS Prime Mission.
+    Target star positions (blue) and predicted TESS observing
+    footprint (gray).  Target stars are either candidate members of
+    clusters, or else have other youth indicators (see
+    \S~\ref{sec:starselection}).  Most will be observed for one or two
+    lunar months over the course of the TESS Prime Mission.
     \label{fig:cdips_targets_positions}
@@
 		\cite{Kharchenko_et_al_2013} cluster members against Gaia-DR2.
-		histogram of the distances between matched stars is on the left; a
+		A histogram of the distances between matched stars is on the left; a
 		histogram of the difference between the true $G$-band magnitude
@@
 facilitate studies of exoplanetary and stellar processes across
-different times and stellar environments.  An essential step is
+different times and stellar environments.  A key step is
 therefore to define a sample of stars that are thought to be young, or
-members or clusters, or both.
+members of clusters, or both.
 
@@
 necessarily heterogeneous across different catalogs.  However, in our
-initial stellar selection our aim is completeness, not accuracy.  If
+initial stellar selection we aim for completeness, not accuracy.  If
 there has been a claim in the literature that a star should be
@@
 least-squares coefficients are then used to construct a prior over
-plausible coefficient values, which is then used to recompute the
+plausible coefficient values, which is subsequently used to recompute the
 maximum likelihood coefficients for each star.  This latter step
@@
 at a different use case.  For transit-search related science,
-we used TFA, as implemented by \texttt{VARTOOLS}
+we used TFA, as implemented in \texttt{VARTOOLS}
 \citep{kovacs_trend_2005,Hartman_Bakos_2016}.  For stellar
@@
 	\caption{
-    Standard deviation of trend-filtered CDIPS light curves as a
+    Standard deviation of TFA-detrended CDIPS light curves as a
     function of catalog TESS-band magnitude.  Black points correspond
@@
 
-\subsection{Identifying Planet Candidates}
-\label{subsec:identifying_ctois}
+\subsection{A Few Objects of Interest}
+\label{subsec:identifying_variability}
 
@@
     the transiting planet search described in
-    \S~\ref{subsec:identifying_ctois}.  
+    \S~\ref{subsec:identifying_variability}.  
     {\it Top.} Sector 6.  {\it Bottom.} Sector 7.
@@
 
-To identify an initial set of transiting planets, strong stellar
-rotators, and eclipsing binaries, we performed a few steps of
+We will discuss our search for transiting planets in an upcoming
+report.  To identify an initial set of transiting planets, strong
+stellar rotators, and eclipsing binaries, we performed a few steps of
 post-processing on the light curves.  This processing was done
@@
 
-For simplicity, we first chose a single aperture size~--~``aperture
-2''~--~with a radius of 1.5  pixels.  Then, to identify periodic
-transit-like signals, we used \citet{hippke_TLS_2019}'s transit
-least-squares (TLS) tool.  The algorithm is the same as the canonical
-box least-squares \citep{kovacs_box-fitting_2002}, except in place of
-a box template, a transit template is used  for a marginal improvement
-of the detection efficiency.  In addition, the search grids in
-\texttt{tls} \footnote{\url{https://github.com/hippke/tls}} are
-slightly more efficient than in most BLS implementations, since
-\texttt{tls} uses the cubic-in-frequency sampling advocated by
-\citet{ofir_optimizing_2014}, rather than standard linear-in-frequency
-sampling.  Our grids typically consisted of about 30 different
-durations, and about 5000 periods between 0.5 and 21 days.
-
-Before performing the period search, we rejected $6\,{\rm hours}$ at
-the beginning and end of each spacecraft orbit, to mitigate the
-presence of correlated red noise in the results.  This shrank the data
-volume by about 5\%, but also lowered the number of systematic false
-positives in subsequent vetting.  We then performed an asymmetric
-sigma-clipping of $(50\sigma,5\sigma)$ about the median to preserve
-transits while omitting flares and other positive flux excursions.
-
-A number of the light curves show residual variability, often of
-stellar origin.  This is expected for a sample of young stars; the
-problem of finding transits in the face of large stellar rotation
-signals has been explored by both \citet{rizzuto_zeitV_2017} and also
-\citet{hippke_wotan_2019}.  The former adopted an approach that we
-have yet to explore, which is to pass a sliding window over the light
-curve that, within each step, performs a Bayesian model comparison
-between a spline and a spline-plus-notch model.  If the
-spline-plus-notch model is favored, the transits are preserved for
-subsequent discovery.  \citet{hippke_wotan_2019}, conversely,
-described a number of different detrending methods, and found that
-most performed more or less the same at recovering planetary transits
-for a sample of young stars with strong rotation signals.
-
-Our approach in this work is essentially identical to one of the
-methods described by \citet{hippke_wotan_2019}.  First, before
-sigma-clipping or omitting points near the edges of orbits we run a
-generalized Lomb-Scargle periodogram on each TFA light curve
-\citep{lomb_1976,scargle_studies_1982,vanderplas_periodograms_2015}.
-If a peak is found with false alarm probability below $10^{-5}$, we
-consider the star ``variable'', and opt to detrend the flux timeseries
-with robust penalized B-splines, which are splines with knot-length
-automatically determined via cross-validation
-\citep{eilers_flexible_1996}. The idea behind the cross-validation is
-that more knots leads to smaller residuals on training data, but
-larger errors when tested on the entire dataset.  We used the
-\texttt{wotan} implementation, which is a wrapper to the
-\texttt{pyGAM} spline fitter, with $2\sigma$ clipping of outliers from
-the fit residuals at each iteration
-\citep{serven_pygam_2018_1476122,hippke_wotan_2019}.  The maximum
-number of spline knots is set to 50, which for each TESS sector
-($\approx 25\,{\rm days}$) is commensurate with a $\approx0.5\,{\rm
-day}$ window.
-
-We verified by injecting and recovering a 2.5 mmag, zero impact
-parameter 
-planet with variable period that this detrending approach marginally
-improved the recovery probability, compared to not doing anything.
-The main cases for which it helps are those with large residual
-stellar variability in the TFA light curve.
-
-After (optionally) detrending, we run the TLS search. To select
-``significant'' signals for visual inspection, we performed a cut on
-the TLS signal detection efficiency defined piecewise over the signal
-periods.  The overall lower limit is ${\rm SDE} > 12$, with higher
-limits imposed in regions with heavy contamination from systematic
-signals.  The signals for sectors 6 and 7 are shown in the space of
-SDE vs period in Figure~\ref{fig:tlsresults}.
-
-This yielded a few thousand light curves.  About two-thirds already
-had been detrended with splines, and were not processed further.  For
-the remaining third we performed TFA signal reconstruction using
-\texttt{VARTOOLS}.  In this process, the model lightcurve $A(i)$ in
-Equation~\ref{eq:tfa_to_minimize} is set to the phase-binned signal
-from the most powerful peak in the TLS spectrum, rather than being a
-constant function.  This helps lower the scatter of the light curve at
-frequencies away from the TLS peak.
-
-We then make a multi-page \texttt{.pdf}-format document report with
-the information necessary to make classifications for vetting.  These
-vetting reports are released along with the light curves, and are a
-useful summary for anyone interested in the subset of objects that we
-have analyzed.  A full description of each page of the report is given
-in Appendix~\ref{appendix:vetreport}.
-When classifying these reports, we assessed:
-\begin{enumerate}
-    \item {\it Morphology of photometric variability}. Designations
-      include tags for planet candidates, eclipsing binaries,
-      instrumental variations, stellar variations, and ``weirdos''.
-    %
-    \item {\it Cluster membership status}. By default, all light
-      curves were made for stars with at least one literature claim of
-      cluster membership.  However, some of these claims pre-dated the
-      availability of Gaia-DR2 parallaxes or proper motions.  We
-      therefore re-assess the membership status on a case-by-case
-      basis through inspection of the available astrometry and
-      photometry.  Known asterisms are also omitted at this point
-      \citep[{\it
-      e.g.},][]{sulentic_revised_1973,baumgardt_asterisms_1998,kos_galah_2018}.
-    %
-    \item {\it Photometric blends}. Tags are created to highlight
-      whether the depth of the photometric signal shows a strong
-      dependence on aperture size, and also whether the in-transit
-      minus the out-of-transit images reveal that the source of
-      variability is in fact far from the target star.
-\end{enumerate}
-The initial classifications were performed by LGB, and possible
-planet candidates were then vetted by JH and JNW.
-The \texttt{TagSpaces}
-software was used to easily assign labels to the documents.
-
-\subsection{Candidate TESS Objects of Interest}
-\label{subsec:ctois}
-
-\begin{figure*}[!t]
-	\begin{center}
-		\leavevmode
-		\includegraphics[width=0.9\textwidth]{quilt_PCs.pdf}
-	\end{center}
-	\vspace{-0.2cm}
-	\caption{
-		Phased light curves for six of the \numberpcs candidate
-			transiting planets identified in this work.
-		Black points are detrended flux measurements, phased to the
-		best-fit orbital period indicated in the lower right of each
-		panel.
-    Transit models are fitted as described in \S~\ref{subsec:ctois},
-    and plotted with blue lines.
-		For display purposes, a window of $\pm 4$ transit durations
-		centered on the transit mid-point is displayed.
-		The vetting reports for these objects are available at XXX.	%FIXME
-		% TODO: include age? T mag?
-		The Gaia source identifiers are
-		a): 5605128927705695232, 
-		b): 3125263468681400320, 
-		c): 5510676828723793920, 
-		d): 3007171311355035136, 
-		e): 5617126180115568256, 
-		f): 3220266049321724416.   
-		\label{fig:ctoi_quilt}
-	}
-\end{figure*}
-
-\begin{figure}[!t]
-	\begin{center}
-		\leavevmode
-		\includegraphics[width=0.45\textwidth]{LS_period_vs_color_and_age.pdf}
-	\end{center}
-	\vspace{-0.2cm}
-	\caption{
-    Time evolution of Lomb-Scargle periodogram peak period versus Gaia
-    color.
-		Red stars are on the right, blue stars are on the left.
-		Each point on this diagram is a star for which the false alarm
-		probability of the most powerful Lomb-Scargle peak is below
-		$10^{-15}$.
-		Additionally, we required (1) that the membership claim originate
-		from \citet{cantat-gaudin_gaia_2018},
-		\citet{Kharchenko_et_al_2013}, or \citet{gaia_hr_2018}; and (2)
-		that the cluster with claimed membership had an age reported by
-		\citet{Kharchenko_et_al_2013}.
-		Our approach for avoiding photometric blends is described in
-		\S~\ref{subsec:notplanets}.
-		\label{fig:ls_peak_vs_time}
-	}
-\end{figure}
-
-If all vetters identified an object as a planet candidate, we then
-proceeded to fit a transit model to the data.  The procedure closely
-mirrors that used by \citet{bouma_wasp-4b_2019} to create a
-phase-folded light curve for WASP-4.
-
-First, we selected points within 5 transit durations of each transit
-midpoint, using the orbital period, transit duration, and reference
-epoch found from applying TLS to the detrended light curve.  We then
-fitted a line to the out-of-transit flux measurements around each
-transit window, and divided it out.  We then fitted a standard transit
-model using the formulae given by \citet{mandel_analytic_2002} and
-implemented by \citet[][\texttt{BATMAN}]{kreidberg_batman_2015}.  The
-free parameters were the orbital period, the reference epoch, the
-planet to star radius ratio $R_{\rm p}/R_\star$, the orbital distance
-to stellar radius ratio $a/R_\star$, and the inclination $i$.  We
-assumed circular orbits.  To fix the quadratic limb-darkening
-parameters, we collected $T_{\rm eff}$ and $\log g$ from the TIC, and
-then interpolated against the \citet{claret_limb_2017} tables.  For
-stars hotter than the maximal effective temperature of these tables
-($12,000\,{\rm K}$), we simply used the coefficients of the hottest
-star.
-
-We then sampled the posterior probability distribution using the
-\citet{goodman_ensemble_2010} algorithm, as implemented by
-\citet[][\texttt{emcee}]{foreman-mackey_emcee_2013}.  Our main goal in
-this procedure was to provide an accurate ephemeris.  To ensure that
-the reported uncertainties are valid, after performing the initial fit
-using the photometric uncertainties reported in our light curves, we
-rescaled the the uncertainty in each photometric data point to equal
-the root-mean-square deviation of each transit-model subtracted light
-curve. We then refitted each light curve.
-
-The resulting parameters are given in Table YYY, and are also
-available as cTOIs NNN.01 - MMM.01 on exofop-TESS (LINK).
-Figure~\ref{fig:ctoi_quilt} shows the phase-folded lightcurves and
-their best-fitting moels.
-
-The physical parameters quoted in Table YYY, and on exofop-TESS,
-should be considered preliminary, and could be substantially improved
-with an object-by-object analysis.  A few additional assumptions were
-required to report some of the values.  For the stellar radii, we
-assumed the $R_\star$ values and uncertainties reported in the TIC.
-There were a few cases with null uncertainties in the stellar radii --
-for these, we simply invented a relative uncertainty of 30\%, and note
-in the comments that this was done.  There were also a few cases for
-which the TIC stellar temperatures and/or radii were not available,
-but the Gaia values were.  In these cases, we used the Gaia $T_{\rm
-eff}$ and $R_\star$ values \citep{andrae_apsis_2018}, and a stellar
-mass interpolated from the \citet{pecaut_intrinsic_2013} table
-(assuming the star is a dwarf) to estimate $\log g$ for the
-limb-darkening.  The uncertainties in e.g., the planetary radii and
-impact parameters were found using linear error propagation theory,
-under the idealized assumption that the covariance between all stellar
-and planetary parameters was zero.
-
-Finally, to assign the names of the planet candidates -- and determine
-whether they had already been identified as TOIs or cTOIs -- we used
-lists downloaded from the \url{tev.mit.edu} alert site for TOIs, and
-from \url{exofop.ipac.caltech.edu/tess} for cTOIs.  We
-cross-referenced based on a combination of the TIC identifier, spatial
-position, and the ephemeris of each object.
-
-\subsection{Eclipsing binaries, stellar rotation}
-\label{subsec:notplanets}
-
-To assess the prospects for studying forms of stellar variability
-other than that caused by transiting planets, we performed a brief
-additional exploration.
-Using the Lomb-Scargle periodogram results from
-\S~\ref{subsec:identifying_ctois}, we selected light curves 
-for which the periodogram peak power had a corresponding false alarm
-probability below $10^{-15}$.
-We chose this cutoff to be small enough to give us a reasonable number
-of objects, but large enough so that there would be no question that
-the signal being detected was astrophysical.
-
-Further, we then restricted our focus to stars with a cluster
-membership claim in \citet{cantat-gaudin_gaia_2018},
-\citet{Kharchenko_et_al_2013}, or \citet{gaia_hr_2018}, since from our
-experience these works have a relatively low false positive
-probability.
-We then further restricted our sample of stars to be those for which
-the claimed cluster also had an age reported by
-\citet{Kharchenko_et_al_2013}.
-
-To remove obvious photometrically-blended duplicates, for any signal,
-if any nearby stars had matching periods, we kept only the signal with
-the lowest false alarm probabilty.
-While this does not ensure that the detected signals originate from
-the target star, it removed a large number of the duplicate signals,
-and suits our exploratory purposes.
-
-All told, this yielded 4057 stars between the ages of about 25 Myr and
-1 Gyr.
-In Figure~\ref{fig:ls_peak_vs_time}, we plot the Lomb-Scargle peak period
-versus $G_{\rm Bp} - G_{\rm Rp}$ color over four different bins of
-time.
-The bins were chosen to match the sub-sample sizes within reasonable
-proximity.
-
-The youngest sample of stars is the reddest, as might be expected
-given that many of these stars have not yet reached the main sequence,
-and may exist along lines of sight with heavy extinction.
-Stars younger than about 200 Myr (the first two age bins) also tend
-to be bluer.
-The oldest stars, between about 450 Myr and 1 Gyr, show a hint in
-the detected periods of being ``bottom-heavy'', {\it i.e.}, there are
-relatively more short-period objects in this sample.
-The reason why is unclear~--~the effect could be due to systematic
-differences in the stellar samples, rather than being astrophysical.
-More investigation will be required.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Discussion}
-\label{sec:discussion}
-
-Maybe JH or JNW could work on these subsections?
-
-\subsection{The planet candidates require more observations}
-Additional observations are needed for two major goals:
-a) cluster membership confirmation
-(age indicators, across the board);
-b) verify the planetary nature of the signals
-(seeing-limited photometry, RV mass measurement).
-
-Different types of observations and analyses are needed to confirm 
-(i) the planetary nature of these signals, and
-(ii) whether the host stars are bonafide cluster members.
-For (i), follow-up photometry, high-resolution imaging, and in some
-cases spectroscopic mass measurement are needed.
-For (ii), one or two radial velocity measurements might kinematically
-exclude cluster membership in a number of cases.
-A full assessment of the target star's age indiciators, including
-photometric rotation signatures, spectroscopic Li and H$\alpha$
-measurements, and even an isochronal analysis, would be helpful.
-
-\subsection{Eclipsing binary and stellar variability analyses may also
-be feasible}
-
-JH?
+%FIXME
+%FIXME
+%FIXME
+%FIXME
 
@@
 
-An initial search for transiting planets, along with subsequent
-vetting to remove obvious non-cluster members and photometric blends,
-has revealed \numberpcs planet candidates.
-\numberclusterpcs of these candidates are candidate cluster members,
-and the remaining \numberzaripcs have indications of youth, relative
-to field stars.
-The latter sub-sample is the less interesting one for this work, but
-may be of interest for other studies.
-Substantial follow-up efforts on these objects are needed to determine
-(i) whether the candidates are planets and (ii) whether the host stars
-are truly cluster members.
-We suspect that a sizeable fraction of our planet candidates may
-be eclipsing binaries, however it likely also includes real planets.
-The vetting reports are available at \stscivetlink, and also documented
-in Appendix~\ref{appendix:vetreport}.
-The planet candidate parameters are on exoFOP-TESS.
-
-We also briefly explored other forms of photometric variability in the
-dataset.
-The age-evolution of extremely high-SNR variability seems to show some
-evolution in the space of LS peak-period versus color
-(Figure~\ref{fig:ls_peak_vs_time}), but interpreting this result will
-require a more careful exploration.
-In searching for transiting planets, we found many eclipsing binaries,
-as well as stellar rotation and pulsation signals.
-Those who wish to explore the time-evolution in these and any other
-systems are invited to explore the data at \stscilink.
+An initial search for objects that were photometrically variable
+returned pulsating stars, eclipsing binaries, and planet candidates.
+A detailed planet search is the subject of ongoing work.
+An of the stars in the sample must be understood to be {\it candidate}
+cluster stars, and the possibility of photometric blends 
+is important to rule out in subsequent vetting efforts of any variable
+object.
+
+As a brief exploration of the photometric variability in the dataset,
+we looked at the age-evolution of extremely high-SNR variability,
+which seems to show some evolution in the space of LS peak-period
+versus color (Figure~\ref{fig:ls_peak_vs_time}), but interpreting this
+result will require a more careful exploration.  In searching for
+transiting planets, we found many eclipsing binaries, as well as
+stellar rotation and pulsation signals.
+
+Those who wish to explore the
+time-evolution in these and any other systems are invited to explore
+the data at \stscilink.
 
@@
 %
-The Digitized Sky Surveys were produced at the Space Telescope Science Institute under U.S.
-Government grant NAG W-2166.
-The images of these surveys are based on photographic data obtained using the Oschin Schmidt Telescope on Palomar Mountain and the UK Schmidt Telescope.
-The plates were processed into the present compressed digital form with the permission of these institutions.
+The Digitized Sky Surveys were produced at the Space Telescope Science
+Institute under U.S. Government grant NAG W-2166. The images of these
+surveys are based on photographic data obtained using the Oschin
+Schmidt Telescope on Palomar Mountain and the UK Schmidt Telescope.
+The plates were processed into the present compressed digital form
+with the permission of these institutions.
 %
@@
 
-\section{Vetting Document Description}
-\label{appendix:vetreport}
-
-In \S~\ref{subsec:ctois}, we described the process by which we made 
-vetting reports suitable for assessing which objects were interesting 
-enough to merit further study.
-
-Figures~\ref{fig:pg1} to~\ref{fig:pg6} of this
-section summarize this document. Updated versions and their 
-\texttt{README} files will live at this web-address: 
-\url{mast.stsci.edu/CDIPS}.
-The planet candidate chosen for these figures
-(Gaia-DR2 \texttt{5541111035713815552} = TIC \texttt{110718787}) was
-chosen for the demonstration in part because it passes all
-the tests.
-It is one of a number of the giant planet candidates that we note may
-be in open clusters.
-
-\begin{figure*}[!h]
-	\begin{center}
-		\leavevmode
-		\includegraphics[width=0.98\textwidth]{gaiatwo0005599752663752776192-0007_page01.pdf}
-	\end{center}
-	\vspace{-0.5cm}
-	\caption{
-		{\bf Transit search summary.}
-    Periodograms from TLS and phase-dispersion minimization, as
-    calculated with \texttt{astrobase.periodbase}, are shown in the
-    top left and top center
-    \citep{bhatti_astrobase_2018,hippke_TLS_2019,stellingwerf_period_1978}.
-    The top three peaks from each method are shown in the second and
-    third rows; the raw light curve is in the top-right. A small
-    finder chart from DSS is inset to the top left, with the 1.5-pixel
-    radius aperture used to extract the light curve in orange.
-		\label{fig:pg1}
-	}
-\end{figure*}
-
-\begin{figure*}[!h]
-	\begin{center}
-		\leavevmode
-		\includegraphics[width=0.98\textwidth]{gaiatwo0005599752663752776192-0007_page02.pdf}
-	\end{center}
-	\vspace{-0.5cm}
-	\caption{
-		{\bf Light curve diagnostics.} 
-    Time-series of raw flux (\texttt{IRM2}),  TFA-detrended flux
-    (\texttt{TF2}), stellar-variability detrended flux, and the
-    background are shown as a function of barycentric Julian date.
-    The overplotted dashed vertical lines are the ephemeris of the
-    highest-power TLS peak from Figure~\ref{fig:pg1}.
-    An important check is whether the flux dips are correlated with
-    changes in the background level -- in this case, they are not.
-    The standard deviation and TESS magnitude are quoted in the upper
-    right.  The red line in the second from the top plot is the
-    windowed spline described in Section~\ref{subsec:ctois}, in this
-    case an essential step for finding the eclipse signal.
-		\label{fig:pg2}
-	}
-\end{figure*}
-
-\begin{figure*}[!h]
-	\begin{center}
-		\leavevmode
-		\includegraphics[width=0.98\textwidth]{gaiatwo0005599752663752776192-0007_page03.pdf}
-	\end{center}
-	\vspace{-0.5cm}
-	\caption{
-    {\bf Transit diagnostics.}
-    The plots show the maximally-detrended light curve (top); the
-    phase-folded light curve centered over $\pm3$ transit durations of
-    the primary transit (middle left); the secondary eclipse (middle
-    right); the odd-numbered transits (lower left); and the
-    even-numbered transits (lower right).
-    The stellar parameters ($T_{\rm eff}, R_\star, M_\star$) are taken
-    from TICv8 when available \citep{stassun_TIC8_2019}.
-    %Gaia-DR2 Apsis pipeline results when available
-    %\citep{andrae_apsis_2018}.
-    The first eight lines of text are parameters determined from the
-    best-fitting TLS model.  The one exception is the planet radius,
-    which uses the stellar radius as noted above.
-    The ``flux contamination'' (\texttt{TICCONT}) from neighboring
-    stars is {\it never} taken into account, because transit depth
-    dilution does not affect image subtraction analyses in the same
-    manner as aperture-photometry reductions.
-    The significance of the odd-to-even asymmetry is quoted,
-    but given the strong rotational variability in this object (Figure~\ref{fig:pg2}),
-   	the apparent odd-even asymmetry could have been caused by the detrending process.
-    To estimate the transit to occulation depth ratio $\delta_{\rm tra}/\delta_{\rm occ}$,
-    the phase-folded light curve is also fit by a sum of two
-    gaussians (in this case, the fit failed).
-    ``AstExc'' refers to the Gaia-DR2 astrometric excess, which can
-    indicate hints of astrometric binarity in the system.
-    ``$d_{\rm geom}$'' is the geometric distance from
-    \citet{bailer-jones_distances_2018}.
-    ``$R_\star + M_\star \rightarrow T_{b0}$'' gives the duration of a
-    zero-eccentricity central transit based on the TICv8 stellar
-    radius and mass if available. If the mass is not available, a
-    stellar mass is interpolated from the
-    \citet{pecaut_intrinsic_2013} table, under the assumption that the
-    star is a dwarf.
-    %\footnote{\url{http://www.pas.rochester.edu/~emamajek/EEM_dwarf_UBVIJHK_colors_Teff.txt}}.
-		\label{fig:pg3}
-	}
-\end{figure*}
-
-\begin{figure*}[!h]
-	\begin{center}
-		\leavevmode
-		\includegraphics[width=0.98\textwidth]{gaiatwo0005599752663752776192-0007_page04.pdf}
-	\end{center}
-	\vspace{-0.5cm}
-	\caption{
-		{\bf Light curves for increasing aperture sizes.} 
-    Apertures of radius 1, 1.5, and 2.25 pixels are shown from top to
-    bottom.  The blue line is the reference transit depth from the
-    best-fitting TLS model.  Changes in depth with increasing aperture size
-    can indicate that the source of variability is off-center from the 
-    aperture, suggesting a photometric blend.
-		\label{fig:pg4}
-	}
-\end{figure*}
-
-\begin{figure*}[!h]
-	\begin{center}
-		\leavevmode
-		\includegraphics[width=0.98\textwidth]{gaiatwo0005599752663752776192-0007_page05.pdf}
-	\end{center}
-	\vspace{-0.5cm}
-	\caption{
-		{\bf Cluster membership assessment diagnostics.}
-    The star was considered a candidate cluster member by the
-    source(s) listed under ``Reference'', in this case
-    \citet{cantat-gaudin_gaia_2018}.  The name used in their catalog
-    in this case was \texttt{5599752663752776192}, a Gaia-DR2
-    identifier, which can be back-referenced to find that
-    \citet{cantat-gaudin_gaia_2018} assigned this star a membership
-    probability in Haffner 13 of just 10\%.
-    The base catalog for the plots is chiefly that of
-    \citet{Kharchenko_et_al_2013}, due to its homogeneous parameter
-    determination procedure (particularly for age).  If a match to the
-    \citet{Kharchenko_et_al_2013} catalog is found, then the remaining
-    plots are populated.  Top-left shows the parallax, with orange
-    points sampled from the Gaia-DR2 posterior, black points the other
-    cluster members in the Kharchenko catalog, and the blue line the
-    claimed Kharchenko parallax for the cluster.  A number of
-    field contaminants in the Kharchenko catalog are visible in this
-    case.  Top-right are the Gaia proper motions, where against black
-    points are cluster members from Kharchenko, and the orange is the
-    target star.  Bottom-left is the color-magnitude diagram, and
-    bottom-right are the on-sky positions.  In the text,
-    \texttt{N1sr2} is the number of $1\sigma$ cluster members reported
-    by \citet{Kharchenko_et_al_2013} within the cluster angular
-    radius; $\log t$ is the base-10 logarithm of the age in years;
-    \texttt{type} matches the type codes provided by
-    \citet{Kharchenko_et_al_2013}; \texttt{K13Note} gives the
-    description of the cluster from \citet{Kharchenko_et_al_2013}, if
-    available.
-    Extra caution must be taken when interpreting this set of plots,
-    since they can only show disagreement between the observed star's
-    properties and those of the listed Kharchenko members (and the
-    latter may be biased).
-		\label{fig:pg5}
-	}
-\end{figure*}
-
-\begin{figure*}[!h]
-	\begin{center}
-		\leavevmode
-		\includegraphics[width=0.98\textwidth]{gaiatwo0005599752663752776192-0007_page06.pdf}
-	\end{center}
-	\vspace{-0.5cm}
-	\caption{
-		{\bf Imaging variability diagnostics.} 
-    This page is intended to help diagnose which stars are producing
-    the observed variability.  Top-left and top-center are the mean
-    out-of-transit (OOT) and mean in-transit calibrated images
-    (separate from any of our image-subtraction analysis).  The OOT
-    images are based on the same number of exposures as the in-transit
-    images and split evenly before and after each transit
-    \citep[following][]{bryson_identification_2013,kostov_l9859_2019}.
-    The yellow star is the target; cyan dots are the flux-weighted
-    centroid of the entire image for each transit event; small red
-    crosses are WCS-projected locations of neighbor stars.
-    Middle-left is the most important sub-panel: the difference
-    between the OOT and in-transit mean images.  If the variability
-    shown in background map (units: ADU) is off-target, the transit is
-    typically not from the target star.  Middle-center is the same,
-    normalized by the uncertainty map.  Lower left and lower center
-    show the DSS field in linear and log scales at roughly the same
-    pixel scale as the TESS image, with the 1, 1.5, and 2.25
-    pixel-radius apertures in blue, orange, and green respectively.
-    The brightness of neighborhood stars is given on the far right.
-    Note the slight coordinate rotation difference between DSS and TESS images;
-    DSS images are aligned north-up, east-left; TESS images are
-    oriented as closely as possible to this system without actually
-    performing the rotation.
-		\label{fig:pg6}
-	}
-\end{figure*}
-
-% \begin{figure*}[!h]
-% 	\begin{center}
-% 		\leavevmode
-% 		\includegraphics[width=0.98\textwidth]{gaiatwo0005541111035713815552-0007_page01.pdf}
-% 	\end{center}
-% 	\vspace{-0.5cm}
-% 	\caption{
-% 		{\bf Transit search summary.} Periodograms from TLS and 
-% 		phase-dispersion minimization, as calculated 
-% 		with \texttt{astrobase.periodbase}, are shown in the top left and top center 
-% 		\citep{bhatti_astrobase_2018,hippke_TLS_2019,stellingwerf_period_1978}.
-% 		The top three peaks from each 
-% 		method are shown in the second and third rows; the raw light curve is in the 
-% 		top-right. A small finder chart from DSS is inset to the top left, with
-% 		the 1.5-pixel radius aperture used to extract the light curve in orange.
-% 		\label{fig:pg1}
-% 	}
-% \end{figure*}
-% 
-% \begin{figure*}[!h]
-% 	\begin{center}
-% 		\leavevmode
-% 		\includegraphics[width=0.98\textwidth]{gaiatwo0005541111035713815552-0007_page02.pdf}
-% 	\end{center}
-% 	\vspace{-0.5cm}
-% 	\caption{
-% 		{\bf Light curve diagnostics.} 
-% 		Time-series of raw flux (\texttt{IRM2}),  TFA-detrended flux (\texttt{TF2}), stellar-variability
-% 		detrended flux, and the background are shown as a function of
-% 		barycentric Julian date.
-% 		The overplotted dashed vertical lines are the ephemeris of the highest-power
-% 		TLS peak from Figure~\ref{fig:pg1}.
-% 		An important check is whether the flux dips are correlated with changes in the 
-% 		background level -- in this case, they are not.
-% 		The standard deviation and TESS magnitude are quoted in the upper right.
-% 		The red line in the second from the top plot is the windowed 
-% 		spline described in Section~\ref{subsec:ctois} -- in this case it is near its maximal
-% 		frequency.
-% 		\label{fig:pg2}
-% 	}
-% \end{figure*}
-% 
-% \begin{figure*}[!h]
-% 	\begin{center}
-% 		\leavevmode
-% 		\includegraphics[width=0.98\textwidth]{gaiatwo0005541111035713815552-0007_page03.pdf}
-% 	\end{center}
-% 	\vspace{-0.5cm}
-% 	\caption{
-%     {\bf Transit diagnostics.} The plots show the
-%     maximally-detrended light curve (top); the phase-folded light
-%     curve centered over $\pm3$ transit durations of the primary
-%     transit (middle left); the secondary eclipse (middle right); the
-%     odd-numbered transits (lower left); and the even-numbered transits
-%     (lower right).
-%     The stellar parameters ($T_{\rm eff}, R_\star, M_\star$) are taken from
-%     TICv8 when available \citep{stassun_TIC8_2019}.
-%     %Gaia-DR2 Apsis pipeline results when available
-%     %\citep{andrae_apsis_2018}.
-%     The first eight lines of text are parameters determined from the
-%     best-fitting TLS model.
-%     The one exception is the planet radius, which uses the stellar
-%     radius as noted above.
-%     The ``flux contamination'' (\texttt{TICCONT}) from neighboring
-%     stars is {\it never} taken into account, because transit depth
-%     dilution does not affect image subtraction analyses in the same
-%     manner as aperture-photometry reductions.
-%     To estimate the transit to occulation depth ratio, the
-%     phase-folded light curve is also coarsely fit via maximum
-%     likelihood by a sum of two gaussians.
-%     ``AstExc'' refers to the Gaia-DR2 astrometric excess, which can
-%     indicate hints of astrometric binarity in the system.
-%     ``$d_{\rm geom}$'' is the geometric distance from
-%     \citet{bailer-jones_distances_2018}.
-%     ``$R_\star + M_\star \rightarrow T_{b0}$'' gives the duration of a
-%     zero-eccentricity central transit based on the TICv8 stellar
-%     radius and mass if available. If the mass is not available, a
-%     stellar mass is interpolated from the
-%     \citet{pecaut_intrinsic_2013} table, under the assumption that the
-%     star is a dwarf.
-%     %\footnote{\url{http://www.pas.rochester.edu/~emamajek/EEM_dwarf_UBVIJHK_colors_Teff.txt}}.
-% 		\label{fig:pg3}
-% 	}
-% \end{figure*}
-% 
-% \begin{figure*}[!h]
-% 	\begin{center}
-% 		\leavevmode
-% 		\includegraphics[width=0.98\textwidth]{gaiatwo0005541111035713815552-0007_page04.pdf}
-% 	\end{center}
-% 	\vspace{-0.5cm}
-% 	\caption{
-% 		{\bf Light curves for increasing aperture sizes.} 
-% 		Apertures of radius 1, 1.5, and 2.25 pixels are shown from top to bottom.
-% 		The blue line is the reference transit depth from the best-fitting TLS model.
-% 		Any changes in depth with aperture size might indicate the need for a 
-% 		detailed pixel-level analysis.
-% 		\label{fig:pg4}
-% 	}
-% \end{figure*}
-% 
-% \begin{figure*}[!h]
-% 	\begin{center}
-% 		\leavevmode
-% 		\includegraphics[width=0.98\textwidth]{gaiatwo0005541111035713815552-0007_page05.pdf}
-% 	\end{center}
-% 	\vspace{-0.5cm}
-% 	\caption{
-% 		{\bf Cluster membership assessment diagnostics.}
-% 		The star was considered a candidate cluster member by the source(s) listed under
-% 		``Reference'', in this case \citet{dias_proper_2014}.
-% 		The name used in the Dias catalog in this case was \texttt{264-025831}, a
-% 		UCAC-4 identifier, which can be back-referenced to find that \citet{dias_proper_2014}
-% 		assigned this star a
-% 		membership probability in NGC 2546 of 98\%.
-% 		The base catalog for the plots is chiefly that of \citet{Kharchenko_et_al_2013},
-% 		due to its homogeneous parameter determination procedure (particularly for age).
-% 		If a match to the \citet{Kharchenko_et_al_2013} catalog is found, then the remaining
-% 		plots are populated.
-% 		Top-left shows the parallax, with orange points sampled from the Gaia-DR2
-% 		posterior, black points the other cluster members in the Kharchenko catalog,
-% 		and the blue line the claimed Kharchenko parallax for the cluster.
-% 		A large number of field contaminants are visible in this case.
-% 		Top-right are the Gaia proper motions, where against black points are cluster
-% 		members from Kharchenko, and the orange is the target star.
-%     Bottom-left is the color-magnitude diagram, and bottom-right are
-%     the on-sky positions.  In the text,
-% 		\texttt{N1sr2} is the number of $1\sigma$ cluster members reported
-% 		by \citet{Kharchenko_et_al_2013} within the cluster angular radius;
-% 		$\log t$ is the base-10 logarithm of the age in years;
-% 		\texttt{type} matches the type codes provided by
-%     \citet{Kharchenko_et_al_2013};
-%     \texttt{K13Note} gives the description of the cluster from
-%     \citet{Kharchenko_et_al_2013}, if available.
-% 		\label{fig:pg5}
-% 	}
-% \end{figure*}
-% 
-% \begin{figure*}[!h]
-% 	\begin{center}
-% 		\leavevmode
-% 		\includegraphics[width=0.98\textwidth]{gaiatwo0005541111035713815552-0007_page06.pdf}
-% 	\end{center}
-% 	\vspace{-0.5cm}
-% 	\caption{
-% 		{\bf Imaging variability diagnostics.} 
-% 		This page is intended to help diagnose which stars are producing the observed
-% 		variability.
-% 		Top-left and top-center are the mean out-of-transit (OOT) and mean in-transit 
-% 		calibrated images (separate from any of our image-subtraction analysis).
-% 		The OOT images are based on the same number of exposures as the in-transit images
-% 		and split evenly before and after each transit \citep[following][]{bryson_identification_2013,kostov_l9859_2019}.
-% 		The yellow star is the target; cyan dots are the flux-weighted centroid of the entire
-% 		image for each transit event; small red crosses are WCS-projected locations of neighbor stars.
-% 		Middle-left is the most important sub-panel: the difference between
-% 		the OOT and in-transit mean images.
-% 		If the variability shown in background map (units: ADU) is off-target, the
-% 		transit is typically not from the target star.
-% 		Middle-center is the same, normalized by the uncertainty map.
-% 		Lower left and lower center show the DSS field in linear and log scales
-% 		at roughly the same pixel scale as the TESS image,
-% 		with the 1, 1.5, and 2.25 pixel-radius apertures in blue, orange, and green respectively.
-% 		The brightness of neighborhood stars is given on the far right.
-% 		Note the slight rotation difference between DSS and TESS images;
-% 		DSS images are aligned north-up, east-left; TESS images are oriented as closely as
-% 		possible to this system without actually performing the rotation.
-% 		\label{fig:pg6}
-% 	}
-% \end{figure*}
-
 \end{document}

### 2019-07-23 paper_I/collect_figures.sh

@@ -1,0 +1,118 @@
+#!/usr/bin/env bash
+
+##########################################
+# USAGE: ./collect_figures.sh
+##########################################
+
+fdir=../paper_I/figures/
+pdir=../paper_I/
+
+# # positions of clusters
+# cp ${fdir}GI_figs/cluster_positions_ecliptic_scicase.pdf \
+#    ${pdir}cluster_positions.pdf
+
+# what our pipeline does
+cp ${fdir}trex_overview.pdf ${pdir}pipelineoverview.pdf
+
+# rms vs mag 
+fdir=../results/paper_figures/
+
+cp ${fdir}detrended_light_curves_sec6cam1ccd1.pdf \
+   ${pdir}detrended_light_curves_sec6cam1ccd1.pdf
+
+cp ${fdir}external_parameters_vs_time_sec6cam1ccd1.pdf \
+   ${pdir}external_parameters_vs_time_sec6cam1ccd1.pdf
+
+cp ${fdir}stages_of_image_processing_good.png \
+   ${pdir}stages_of_image_processing_good.png
+
+cp ${fdir}stages_of_image_processing_bad.png \
+   ${pdir}stages_of_image_processing_bad.png
+
+cp ${fdir}primary_mission_galacticmap_forproposal_cdipsoverplot.png \
+   ${pdir}target_star_positions.png
+
+cp ${fdir}rms_vs_mag.pdf ${pdir}rms_vs_mag.pdf
+cp ${fdir}avg_acf.pdf ${pdir}avg_acf.pdf
+
+cp ${fdir}raw_light_curve_systematics_sec7cam2ccd4.pdf \
+   ${pdir}raw_light_curve_systematics_sec7cam2ccd4.pdf
+cp ${fdir}raw_light_curve_systematics_sec6cam1ccd2.pdf \
+   ${pdir}raw_light_curve_systematics_sec6cam1ccd2.pdf
+
+cp ${fdir}tls_sde_vs_period_scatter.pdf \
+   ${pdir}tls_sde_vs_period_scatter.pdf
+
+# quilt of PCs
+cp ${fdir}quilt_PCs.pdf ${pdir}quilt_PCs.pdf
+
+# time evolution of LS peak period
+cp ${fdir}LS_period_vs_color_and_age.pdf ${pdir}LS_period_vs_color_and_age.pdf
+
+# positions of lightcurves
[…]

### 2019-07-24 paper/ms.tex
intro + methods basically good

@@
 	\caption{
-	Twenty randomly selected raw image-subtracted light curves drawn
+	Twenty randomly selected stars drawn
 	from the same sector, camera,
 	and CCD, for stars with $T$-band magnitudes between 13 and 14.
+
+  %#FIXME CAPTIOIN
+raw image-subtracted light curves
+
 	A number of systematic trends are shared across the light curves.
 	The sector, camera, and CCD numbers are 6, 1, 2 (left) and 7, 2, 4 (right).
-	\label{fig:lc_systematics}
+	\label{fig:lc_systematics_detrended}
 	}
 \end{figure*}
+
+\begin{figure}[!t]
+	\begin{center}
+		\leavevmode
+		\includegraphics[width=0.47\textwidth]{detrended_light_curves_sec6cam1ccd1.pdf}
+	\end{center}
+	\vspace{-0.5cm}
+	\caption{
+    Twenty randomly selected light curves drawn
+    from the same sector, camera,
+    and CCD, for stars with $T$-band magnitudes between 13 and 14.
+    Each light curve is shown from top to bottom in raw, PCA-detrended, and
+    TFA-detrended forms.
+    Stellar rotation signals are usually preserved in the PCA light curves,
+    while TFA tends to either filter them out, or to distort them.
+		\label{fig:detrended}
+	}
+\end{figure}
 
@@
 
-\begin{figure}[!t]
-	\begin{center}
-		\leavevmode
-		\includegraphics[width=0.47\textwidth]{detrended_light_curves_sec6cam1ccd1.pdf}
-	\end{center}
-	\vspace{-0.5cm}
-	\caption{
-    Twenty randomly selected light curves drawn
-    from the same sector, camera,
-    and CCD, for stars with $T$-band magnitudes between 13 and 14.
-    Each light curve is shown from top to bottom in raw, PCA-detrended, and
-    TFA-detrended forms.
-    Stellar rotation signals are usually preserved in the PCA light curves,
-    while TFA tends to either filter them out, or to distort them.
-		\label{fig:detrended}
-	}
-\end{figure}
-
 The preceding steps produce light curves that include both
 instrumental systematics as well as astrophysical variability.
-Figure~\ref{fig:lc_systematics} shows twenty stars of
+Figure~\ref{fig:lc_systematics_detrended} shows twenty stars of
 comparable brightness randomly selected from two CCDs.  Stars that are

### 2019-07-24 paper_I/ms.tex
intro + methods basically good

@@
 
-% The exoplanet field is evolving.
-% At the beginning, Doppler spectroscopy by the Geneva and California groups
-% led to the first exoplanet detections (CITE: Mayor 95, Butler, Marcy).
-% Some of these planets transited (CITE: Henry, Charbonneau).
-% Despite the geometric rarity of transits, photometric monitoring can
-% be performed in parallel; with precise spectroscopy this has not
-% yet been achieved.
-% Parallel photometric monitoring enabled thousands of planet detections
-% with the Kepler spacecraft (CITE: Borucki, Morton).
-% The abundance of planets from Kepler taught us about statistics
-% (CITE: Howard, Fressin, Petigura).
-% By nature of its design, Kepler left open two major avenues for
-% improvement: (i) brighter stars, (ii) rare weirdos.
-% TESS (CITE: Ricker), by nature of its small, wide-field cameras, and
-% nearly all-sky coverage, can capitalize on both.
-
-% One class of rare weirdo to which TESS is sensitive is stars in
-% clusters.  For brevity, we use the term ``cluster'' to refer to open
-% clusters, moving groups, associations, and star-forming regions.
-% Each of the $\sim$1000 star clusters of the Milky Way is a gift to
-% astrophysics, providing a sample of stars that vary widely in mass
-% but all have approximately the same age and composition.
-
 \section{Introduction}
@@
 periods over a range of ages, we can study the angular momentum
-evolution of stars and improve our ability
-to determine stellar ages through gyrochronology \citep[{\it
+evolution of stars and improve our ability to determine stellar ages
+through gyrochronology \citep[{\it
 e.g.},][]{skumanich_time_1972,barnes_color-period_2015,meibom_spin-down_2015,curtis_tess_2019}.
 By measuring eccenticities as a function age, we can study the tidal
-evolution of binaries (CITE). The detection of eclipsing binaries can
-also lead to the precise determination of the absolute dimensions of
-the stars and stringent tests of stellar-evolutionary models (CITE).
+circularization of binaries
+\citep{meibom_robust_2005,milliman_wiyn_2014,price-whelan_binary_2018}.
+The detection of eclipsing binaries can also lead to the precise
+determination of the absolute dimensions of the stars and stringent
+tests of stellar-evolutionary models
+\citep{luhman_formation_2012,stassun_review_2014,kraus_mass-radius_2015}.
 Finally, transiting exoplanets discovered in clusters can shed light
 on the timescales for processes in planet formation, evolution, and
-migration \citep[{\it
-e.g.},][]{Fortney_et_al_2007,Mann_K2_33b_2016,David_et_al_2017}, as
-well as on the effects of metallicity \citep[{\it
-e.g.},][]{fischer_planet-metallicity_2005,petigura_metallicity_2018}.
+migration
+\citep[][]{Fortney_et_al_2007,Mann_K2_33b_2016,David_et_al_2017}, as
+well as on the effects of metallicity
+\citep[][]{fischer_planet-metallicity_2005,petigura_metallicity_2018}.
 
@@
 ``most probable'' members within each cluster's radius, which by the
-\citet[][]{kharchenko_global_2012} definition requires the independent
+\citet{kharchenko_global_2012} definition requires the independent
 kinematic, photometric, and spatial membership probabilities to each
 exceed 61\%.  The actual number of stars in clusters is larger, as the
-membership catalogs are not yet complete, even down to these
+membership catalogs are not yet complete, even at these
 relatively bright magnitudes \citep[{\it
@@
 
-One of the major barriers to deriving precise photometry from the TESS
-images is the relatively poor angular resolution ($\approx 21''$ per
-pixel).  Almost all clusters are within 10 degrees of the Galactic
-plane. The problems with crowding and complex backgrounds are so
-severe near the galactic plane that the TESS Candidate Target List has
-deprioritizes 2-minute targets at galactic latitudes less than
-$\approx 15^\circ$~\citep{stassun_TIC_2018,stassun_TIC8_2019}. This
-includes almost all star clusters\footnote{TICv8 has updated the cutoff to
-$10^\circ$, but for the first year of TESS observations, the number
-used when selecting target stars was $15^\circ$.}.  This is sensible,
-since the large pixel size and the high stellar surface density
-make aperture photometry unreliable.  
-However, it also means that a
-large number of stars in clusters that could yield transiting planets
+A major barrier to deriving precise photometry from the TESS images is
+the relatively poor angular resolution ($\approx 21''$ per pixel).
+Almost all clusters are within 10 degrees of the Galactic plane. The
+problems with crowding and complex backgrounds become so severe
+that the TESS Candidate Target List deprioritizes
+2-minute targets at galactic latitudes less than $\approx
+15^\circ$~\citep{stassun_TIC_2018,stassun_TIC8_2019}. This includes
+almost all star clusters\footnote{TICv8 updated the cutoff to
+$10^\circ$. During the first year of TESS observations, the number
+used when selecting 2-minute target stars was $15^\circ$.}.  This decision
+was made because
+the large pixel size and the high stellar surface density make
+aperture photometry unreliable.  However, it means that most
+stars in clusters, though capable of yielding a cornucopia of science,
 will go unprocessed by the official {\it TESS} data reduction
@@
 
-One way to quantify the blending problem is to ask what fraction of
+One way to quantify the blending problem is to determine what fraction of
 the total flux in a photometric aperture is contributed by a
-particular target star. Aperture photometry is reliable if this
-fraction is close to unity.  Based on the
+particular target star. Aperture photometry is reliable when this
+fraction is close to unity.  
+Difference imaging \citep{Alard_Lupton_1998,miller_optimal_2008}, in
+our group's experience, can be viable down to crowding fractions
+of perhaps 1 part in 10.
+Based on the
 \citet{Kharchenko_et_al_2013} cluster membership data, and the density
-of background stars, we find that the median dilution fraction of
-stars with $T< 16$ is 0.13 for an aperture radius of 2 pixels.
-
-By combining difference imaging \citep{Alard_Lupton_1998,miller_optimal_2008} 
-with forced-aperture photometry, we
-can avoid the primary effects of blending.  
-In this procedure, the positions of stars are predicted from an 
-astrometric solution, while the reference fluxes are determined from a
-calibrated catalog magnitude-to-flux relation.  The deviation from the
-reference is measured on the difference image.  Assuming that only a
-single source is causes the variability, blended neighbor stars only
-act to increase Poisson noise, and do not ``dilute'' transit
-signals, down to the angular resolution of the source catalog being
-used to determine the reference flux.  This is one of the main
-benefits of performing image subtraction in crowded fields.
-
-We have therefore opted to produce time-series photometry from the
-TESS images of any star that could be a member of a coeval group.  We
+of background stars, we calculated that the median dilution fraction of
+cluster stars with $T< 16$ is 0.13, for an aperture radius of 2 pixels.
+For at least $\sim$$10^5$ cluster stars then, it seems that difference
+imaging may be worthwhile.
+
+Difference imaging avoids the primary effects of blending through
+forced-aperture photometry.  In this method,
+the positions of stars are predicted from an astrometric
+solution, and the reference fluxes are determined from a calibrated
+catalog magnitude-to-flux relation.  The deviation from the reference
+flux is measured on the difference image.  Assuming that only a single
+source causes the variability, blended neighbor stars only act to
+increase Poisson noise, and do not ``dilute'' transit signals, down to
+the angular resolution of the source catalog used to determine the
+reference flux.  This is a major benefit of performing image
+subtraction in crowded fields.
+
+We have therefore begun to apply difference imaging to the
+TESS images, with a focus on any star that could be a member
+of a coeval group.  We
 are also including some stars that we suspect are young due to
-combined photometric and astrometric indicators.  We are using the
-difference imaging technique because of its benefits in modelling
-complex backgrounds in crowded regions.  While we hope to
-discover at least a few giant transiting planets, the focus of the
-present study is to produce a more general-purpose dataset,
-applicable for studies both in exoplanetary as well as stellar
-astrophysics.
+combined photometric and astrometric indicators.
+A major motivation for
+this effort is to discover giant transiting planets with known ages.
+The focus of the present study however is to describe our
+methods, and to produce a general-purpose
+dataset applicable for studies both in exoplanetary and also
+stellar astrophysics.
 
@@
 light curves from TESS Sectors 6 and 7 are then summarized
-(\S~\ref{subsec:lcstatistics}).  
-An example of how we might use the data to identify pulsating
-stars, eclipsing binaries, and transiting planets is then
-given
-(\S~\ref{subsec:identifying_variability}). 
-\S~\ref{sec:conclusion}
-summarizes our findings, and discusses them with an eye towards
-the studies we hope this and subsequent rounds of data processing
-will enable.
+(\S~\ref{subsec:lcstatistics}).  An example of how we might use the
+data to identify pulsating stars, eclipsing binaries, and transiting
+planets is then given (\S~\ref{subsec:identifying_variability}).
+\S~\ref{sec:conclusion} summarizes our findings, and discusses them
+with an eye towards the studies we hope this and subsequent rounds of
+data processing will enable.
 
@@
 
-\begin{figure*}[!t]
+\begin{figure}[!t]
 	\begin{center}
 		\leavevmode
-		\includegraphics[width=0.9\textwidth]{target_star_positions.png}
+		\includegraphics[width=0.48\textwidth]{target_star_positions.png}
 		%\gridline{\fig{target_star_cumulative_counts.pdf}{0.41\textwidth}{}}
 	\end{center}
-	\vspace{-0.8cm}
+	\vspace{-0.5cm}
 	\caption{
@@
     \S~\ref{sec:starselection}).  Most will be observed for one or two
-    lunar months over the course of the TESS Prime Mission.
+    lunar months over the TESS Prime Mission.
     \label{fig:cdips_targets_positions}
 	}
-\end{figure*}
+\end{figure}
 
@@
 \begin{figure*}[!t]
-	\gridline{\fig{mwscmatchstats.pdf}{0.95\textwidth}{}}
+	\gridline{\fig{mwscmatchstats.pdf}{0.75\textwidth}{}}
 	\vspace{-0.8cm}
-	\gridline{\fig{dias14matchstats.pdf}{0.95\textwidth}{}}
+	\gridline{\fig{dias14matchstats.pdf}{0.75\textwidth}{}}
 	\vspace{-0.8cm}
@@
 magnitudes being somewhat larger than predicted $G$-band magnitudes,
-due to dust reddening.
+presumably due to dust reddening.
 
@@
 
-For the Gagn\'e et al{.} catalogs, we searched the Gaia-DR2 archive for
-sources within 10 arcseconds of the listed positions.  If Gagn\'e et
-al{.} gave a proper motion, we required that the sign of each the Gaia
-proper motion components match that of the Gagn\'e values (the stated
-proper motion uncertainties seemed to have been underestimated).  We
-also imposed a $G<18$ cut on any putative matches.  Of 3012 moving
-group members collected from the three combined Gagn\'e et al{.}
-catalogs, we found 2702 matches.
+For the Gagn\'e et al{.} catalogs, a large
+number of the stars have high proper motions.
+However, a number of the stars do not have proper motions quoted.
+To perform the cross-match,
+we searched the Gaia-DR2 archive for
+sources within 10 arcseconds of the listed positions (propagated to the
+Gaia-DR2 J2015.5 epoch, if the proper motions were available, otherwise
+simply using the listed J2000 positions).
+We also imposed a $G<18$ cut on any putative matches. 
+We then chose the nearest neighbor by spatial separation.
+Of 3012 moving group members collected from the
+three combined Gagn\'e et al{.}
+catalogs, this procedure yielded 2702 matches.
 
@@
 
-\citet{rizzuto_multidimensional_2011} also focused on a single moving
+\citet{rizzuto_multidimensional_2011} focused on a single moving
 group: the Sco OB2 association. We used their reported Hipparcos
@@
 \texttt{hipparcos2\_best\_neighbour} table, which gave 319
-nearest-neigbor stars from 436 candidate members.
+nearest-neighbor stars from 436 candidate members.
 
@@
 star-forming complexes in Sco-Cen, Orion, Vela, Taurus, and other
-regions of the sky.  Though many are not strictly identified with
-moving groups or open clusters, their reported youth and proximity to star
+regions of the sky.  Though most of these stars are not directly
+identified with moving groups or open clusters, their reported
+youth and proximity to star
 forming regions justifies their inclusion in our search sample.
@@
 
-To reduce the TESS images to light curves, we adopted an image
-subtraction approach.  The overall method is in the spirit of the
+To reduce the TESS images to light curves, we adopted a
+difference imaging approach.  The overall method is in the spirit of the
 reduction pipelines developed by \citet{Pal_2009},
@@
 and~\ref{fig:stages_bad}.
-Features with spatial scales smaller than $\approx$48 pixel remain, 
-and large spatial scale scattered light patches are removed.
+Features with spatial scales smaller than $\approx$48 pixels remain, 
+but large scale scattered light patches are removed.
 
@@
 
-First, we use \texttt{fistar} to perform source extraction on the
-thousand or so brightest, non-saturated stars in each image.  The
-source extraction derives centroid positions for these stars, and also
-fits elongated gaussians to their profiles, yielding the shape
+First, we perform source extraction on the
+thousand or so brightest, non-saturated stars in each image.  
+This is done using a \texttt{fitsh} tool, \texttt{fistar}.
+We derive centroid positions for the stars, and
+simultaneously
+fit elongated gaussians to their profiles, yielding the shape
 parameters $(s,d,k)$, where the flux $f$ as a function of position
@@
 \end{align}
-for $(x_0,y_0)$ arbitrary reference positions,
-$\Delta x = x-x_0$, $\Delta y = y - y_0$, $B$ is the background
-level, and $A$ is an arbitrary
+for $(x_0,y_0)$ the central coordinates of the star,
+$\Delta x = x-x_0$, $\Delta y = y - y_0$, $B$ the background
+level, and $A$ an arbitrary
 flux-scaling constant.
@@
 solutions than in those given by SPOC.  This was perhaps because
-we did not invest major amounts of time developing a robust
+we did not develop a robust
 algorithm to select non-blended stars of intermediate brightness before
 measuring their positions.
+Nonetheless, we did find that extending the astrometric correction
+to sixth order (compared to the fourth-order polynomial coefficients
+in the SPOC solution) did not improve the quality of the fit.
 
 With the resulting WCS information, we then project a source catalog
-onto each frame.  Initially, we planned to photometer all Gaia-DR2
-sources in each field down to a cutoff of $G_{Rp} < 16$.  However, we
-found that for the galactic plane fields this produces an excessively
-large number of sources (millions of stars per
-$12^\circ\times12^\circ$ CCD).  We therefore limited our source
-catalog for each frame to be
-a combination of the CDIPS target stars ($G_{Rp} < 16$), and
-all Gaia-DR2 sources down to $G_{Rp} < 13$.  We use the
-projected positions of these sources to center the apertures in our
+onto each frame. 
+We use the
+projected positions of the sources to center the apertures in our
 photometry,
@@
 \citep{kim_2018_gaia2read}.
+
+For the source catalog itself, we initially planned to photometer all Gaia-DR2
+sources in each field down to a cutoff of $G_{Rp} < 16$.  However,
+for the galactic plane fields this produced an excessively
+large number of sources (millions of stars per
+$12^\circ\times12^\circ$ CCD).  We therefore limited our source
+catalog for each frame to be
+a combination of the CDIPS target stars ($G_{Rp} < 16$), and
+all Gaia-DR2 sources down to $G_{Rp} < 13$.  
+The latter set of stars are used for image processing and
+light curve detrending.
 
@@
 where the non-linearity of the focal plane is most significant, and
-where the corrections required by the SIP coefficients are largest.
+the corrections required by the SIP coefficients are largest.
 %The final sub-panel of Figure~\ref{fig:astrometricresidual} is a
@@
 
-As a final step of metadata collection, we perform aperture photometry on the
-bright stars by summing the counts inside appropriately-weighted
-circular apertures centered on the projected positions. This task is
-performed using \texttt{fiphot}.
+Finally, to collect the metadata needed
+to select photometric reference frames,
+we perform
+aperture photometry on the
+bright stars.
+This task is
+performed by using \texttt{fiphot} to
+sum the counts inside 
+circular apertures centered on the projected stellar positions.
 The pixel weights are equal to the fraction of the pixel
-that falls within the aperture.  They are thus unity for pixels
+that falls within the aperture.  They are unity for pixels
 entirely within the aperture, and fractional along the aperture
@@
 each aperture, and the number of stars with ``good'' photometry,
-are later used to select photometric reference frames.
+can then be used to assess the photometric quality of each frame.
 
@@
 \subsubsection{History of image subtraction method}
-The core operation of ``classical'' image subtraction
-attempts to match a photometric reference $R$ and a target image $I$ by 
-computing and applying a convolution kernel.
-For ground-based data, this ``match'' typically corrects for
-differences in seeing or transparency between the reference and
-target; for space-based data, the match might correct for spacecraft
-jitter, or thermal and corresponding point-spread function (PSF)
-variations.
-The kernel, once applied to the high signal-to noise reference,
-produces a model image, $M_{xy}$,
+
+The core operation of ``classical'' image subtraction attempts to
+match a photometric reference $R$ and a target image $I$ by computing
+and applying a convolution kernel.  For ground-based data, this
+``match'' typically corrects for differences in seeing or transparency
+between the reference and target; for space-based data, the match
+might correct for spacecraft jitter, or thermal and corresponding
+point-spread function (PSF) variations.  The kernel, once applied to
+the high signal-to noise reference, produces a model image, $M_{xy}$,
 \begin{equation}
@@
 where $B_{xy}$ is a component of the model image that allows for
-background variations, and $\otimes$ denotes convolution.
-Since we modeled the background separately (\S~\ref{subsec:preparation}),
-we set $B_{xy}=0$.
-The convolution kernel $K$ is typically decomposed onto a
-basis, $K = \sum_i c_i K_i$, and the coefficients are found
-by minimizing
+background variations, and $\otimes$ denotes convolution.  Since we
+modeled the background separately (\S~\ref{subsec:preparation}), we
+set $B_{xy}=0$.  The convolution kernel $K$ is typically decomposed
+onto a basis, $K = \sum_i c_i K_i$, and the coefficients are found by
+minimizing
 \begin{equation}
@@
 \end{equation}
-where $\sigma_{xy}$ is the uncertainty in the target image pixel values.
-Photometry is then performed on the difference image $D_{xy}$, where
-$D_{xy} = I_{xy} - M_{xy}$.
-For the present reduction, the uncertainty in each target image pixel was
-taken to be a constant.
-
-The general procedure described above was first proposed by \citet{Alard_Lupton_1998}.
-It was reviewed and clarified by \citet{miller_optimal_2008}.
-The choice of how to decompose the kernel was further explored by
-\citet{bramich_new_2008}, who showed that using a linear combination
-of delta functions had advantages compared to a basis of gaussians.
-We perform the convolution using \texttt{ficonv}, and opt for the
-implementation of Bramich's method (see \citealt{Pal_2009} \S~2.8).
-The lower panels of
-Figure~\ref{fig:stages_good} show the procedure
-working well, and producing a ``clean'' difference image.
-Figure~\ref{fig:stages_bad} shows what happens for an
-image taken when scattered light from the Earth causes the
-model image $M_{xy}$ to be a poor fit to the target image $I_{xy}$, 
-leading to a number of systematic artificats.
+where $\sigma_{xy}$ is the uncertainty in the target image pixel
+values.  Photometry is then performed on the difference image
+$D_{xy}$, where $D_{xy} = I_{xy} - M_{xy}$.  For the present
+reduction, the uncertainty in each target image pixel was taken to be
+a constant.
+
+The general procedure described above was first proposed by
+\citet{Alard_Lupton_1998}.  It was reviewed and clarified by
+\citet{miller_optimal_2008}.  The choice of how to decompose the
+kernel was further explored by \citet{bramich_new_2008}, who showed
+that using a linear combination of delta functions (also called
+a ``discrete kernel'') had advantages
+compared to a basis of gaussians.  We perform the convolution using
+\texttt{ficonv}, and opt for the implementation of Bramich's method
+(see \citealt{Pal_2009} \S~2.8).  The lower panels of
+Figure~\ref{fig:stages_good} show the procedure working well, and
+producing a ``clean'' difference image.  Figure~\ref{fig:stages_bad}
+shows what happens for an image taken when scattered light from the
+Earth causes the model image to be a poor fit to the target
+image.
 
 \subsubsection{Astrometric registration}
-We now describe some implementation details we used to make the
-above high-level picture work.
-First, we needed to select two ``reference frames'' for image subtraction:
+
+To make the above high-level picture work, we need to select
+two ``reference frames'':
 (1) the astrometric reference; and (2) the photometric reference.
 
-To choose the astrometric reference, we searched for frames with
-large, round stars (big $s$, small $d$ and $k$ values).
-We also required
-that the frame have minimal background noise, as measured in annuli
-around the bright stars selected in \S~\ref{subsec:preparation}.
-Finally, the astrometric reference frame needed to have, relative to the 
-other frames being
-considered, a large number of detected sources.
-We sorted the frames using these metrics, and then selected the
-astrometric reference from successive intersections of each sorted
-list.
-
-We then
-used the \texttt{grmatch} and \texttt{grtrans} tools to
-compute and apply a spatial transformation of each calibrated frame
-to match the astrometric reference frame.
-The transformation is calculated using the measured source positions
-found in ~\S~\ref{subsec:metadatacollection},
-and the symmetric triangle point-matching scheme described
-by \citet[][~\S~2.5.2]{Pal_2009}.
-The transformation~--~a combination of rotation, dilation, and
-translation~--~typically moves stars by less than a pixel, since
-the TESS spacecraft is quite stable.
-The precision of the transformation is guaranteed by forcing 
-its unitarity $\Lambda$ to always be below 0.01, where 
-$\Lambda$ is defined by \citet[][~Eq.~54]{Pal_2009}.
-We reduced the photometric errors
-incurred during this step by using
-the flux-conserving interpolation
-scheme described by \citet{Pal_2009},
-which was necessary because polynomial interpolation schemes
-do not conserve stellar flux.
+To choose the astrometric reference, we search for frames with
+large, round stars (big $s$, small $d$ and $k$ values).  We also
+require that the frame have minimal background noise, as measured in
+annuli around the bright stars selected in
+\S~\ref{subsec:preparation}.  Finally, the astrometric reference
+needs to have, relative to the other frames being considered, a large
+number of detected sources (though the variance between frames was rather 
+small).  We sort the frames
+using these metrics, and then select the astrometric reference from
+successive intersections of each sorted list.
+
+We then compute and apply a spatial transformation of each calibrated
+frame to match the astrometric reference frame.  This
+transformation~--~a combination of rotation, dilation, and
+translation~--~typically moves stars by less than a pixel, since the
+TESS spacecraft pointing is quite stable.  We calculate the transformation
+using the measured source positions found in
+~\S~\ref{subsec:metadatacollection}, and the symmetric triangle
+point-matching scheme described by \citet[][~\S~2.5.2]{Pal_2009}.
+This step is achieved using the \texttt{fitsh} tools \texttt{grmatch} and
+\texttt{grtrans}.  To help ensure the precision of the transformation,
+we require the ``unitarity'' $\Lambda$
+\citep[][~Eq.~54]{Pal_2009}, which characterizes the degree of
+distortion in the transformation matrix, to be below 0.01.  To
+mitigate possible photometric errors incurred during this step, we
+also use the flux-conserving interpolation scheme described by
+\citet{Pal_2009}, which is necessary because polynomial interpolation
+schemes do not conserve stellar flux.
 
@@
 
-The second required reference frame is the
-photometric reference, which is used both to calculate the
-convolution kernel, and to obtain a
-reference flux for each star.  
-To make it, we first chose 50
-sub-frames with low scatter in their photometry
-and low background measurements, according to the metadata collected
-in \S~\ref{subsec:preparation}.
-We then convolved these candidate photometric reference frame to the best
-frame, and performed a median average over the entire stack
-to make the photometric reference.
-
-%\begin{enumerate}
-%  \item Lowest median scatter in photometry
-%  \item Lowest median error in photometry
-%  \item Lowest median background measurement
-%  \item Lowest median absolute deviation in background measurements
-%  \item Largest number of stars detected by \texttt{fiphot} with good
-%    flags.
-    % fiphot files used for all of this.
-%\end{enumerate}
-
-Measuring the reference flux for each star is a slightly non-trivial
-operation.
-First, we perform forced simple aperture photometry to measure
-the flux for each source.
-The local background is estimated in annuli, with neighboring stars
-masked out during the background measurement.
-However if we were to stop here, {\it it would be a bad mistake}.
-The reference fluxes for faint stars would be overestimated, due to
-crowding.
-The relative amplitude of photometric signals would correspondingly
-be biased small, hindering exoplanet detection.
-
-Therefore, after performing simple aperture photometry on the 
-reference frame, we fitted an aperture-size specific zero point
-between the catalog $T$-band magnitude of each star, and its
-measured flux.
-The $T$-band magnitude was calculated according to Equation~1 of 
-\citet{stassun_TIC8_2019}.
+The second required reference frame is the photometric reference,
+which is used both to calculate the convolution kernel, and to obtain
+a reference flux for each star.  To make it, we first choose 50 images
+with low background measurements (measured for each frame from the
+annuli around bright stars), and only consider frames with a
+relatively large number of detected bright objects.  We then convolve
+these candidate photometric reference frames to the frame with the
+lowest background measurement, and construct the photometric
+reference as the median image across the 50 frame stack.
+
+Measuring the reference flux for each star is a non-trivial
+operation.  First, we perform forced simple aperture photometry on the
+photometric reference frame to measure the flux for each source.  The
+local background is estimated in annuli, with neighboring stars masked
+out during the background measurement.  If we were to stop
+here, {\it it would be a bad mistake}.  The reference fluxes for faint
+stars would be overestimated, due to crowding.  The relative amplitude
+of photometric signals for faint stars would correspondingly be biased
+small, which would hinder exoplanet detection, among other
+applications.
+
+To avoid this problem, after performing simple aperture photometry on
+the reference frame, we fitted a line between the catalog $T$-band
+magnitude of each star, and its measured flux.  The $T$-band magnitude
+was calculated according to Equation~1 of \citet{stassun_TIC8_2019}.
 We then use the known catalog magnitude to predict the expected
-reference flux for each star.
-In effect, this minimizes crowding down to Gaia's resolution limit of
-$\approx$1$''$, rather than the TESS limit of $\approx$20$''$.
-
-Following \citet{Pal_2009}~Equation~83,
-the final instrumental flux values $f$ we report\footnote{For example,
-the \texttt{IFL1} column.} are then equal to
+reference flux for each star.  This minimizes crowding down to Gaia's
+resolution limit of $\approx$1$''$, rather than the TESS limit of
+$\approx$20$''$.
+
+The final instrumental flux
+values $f$ we report are given by \citep[][Equation~83]{Pal_2009} 
 \begin{align}
@@
 \end{align}
-The function $g$ takes as input the target star's
-catalog magnitude $T_{\rm cat}$, and returns the reference flux.
-Its coefficients have been fit per the procedure just discussed,
-independently for each aperture.
-The difference image $D$ is equal to $I -  R\otimes K$,
+The function $g$ takes as input the target star's catalog magnitude
+$T_{\rm cat}$, and returns the reference flux.  Its coefficients have
+been fit per the procedure just discussed, independently for each
+aperture.  The difference image $D$ is equal to $I -  R\otimes K$,
 where as in Equation~\ref{eq:imagemodel}, $I$ is the target image
-transformed to the astrometric
-reference, $R$ is the photometric reference, and $K$ is the convolution
-kernel.
-The weights $w$ from the circular aperture mask are included in
-the convolution.
-The norm $|| K ||_1$ is defined by \citet{Pal_2009}~Equation~81.
+transformed to the astrometric reference, $R$ is the photometric
+reference, and $K$ is the convolution kernel.  The weights $w$ from
+the circular aperture mask are included in the convolution.  The norm
+$|| K ||_1$ is defined by \citet{Pal_2009}~Equation~81.
 
 \subsection{Choice of convolution kernel}
-A few brief notes on the algorithm to actually solve for the
-coefficients to the convolution kernel.  The procedure implemented in
+
+To solve for the coefficients to the convolution kernel, a
+few further assumptions are necessary.  The procedure implemented in
 \texttt{ficonv} is to subdivide the image, and within each grid
@@
 kernel, by minimizing Equation~\ref{eq:chisq_conv} over the sum of all
-stamps.
+stamps.  For the kernel basis, we use a linear combination of
+delta functions with a flux scaling term
+(\citealt{soares-furtado_image_2017} Section 3.3.1 gives the
+equations).  In this model, spatial variations of the PSF across the
+image are captured by weighting each basis component with spatial
+polynomials up to a cut-off order.
 
@@
 %CHECK: does the polynomial weighting actually do what you want it to do?
-For the choice of basis, we opt for a delta-function kernel with an additive
-flux scaling term (\citealt{soares-furtado_image_2017} Section 3.3.1
-gives the equations).
-The spatial variations of the PSF are captured by weighting the 
-delta function and the flux scaling terms with varying
-polynomial orders across the image.
-Choosing this kernel introduces three additional
-free parameters:
-(1) the kernel box-size;
-(2) the maximum order of the polynomial weighting the delta function terms;
-(3) the maximum order of the polynomial weighting the flux scaling.
-We performed a grid-search to tune these parameters, in
-which our metrics for success included the measured RMS as
-a function of magnitude, and also the recovered SNR of transits from
-the catalog of known TOIs (TESS Objects of Interest; N.~Guerrero, in prep).
-
-Varying the kernel box-size, we found that kernels with box-length smaller than the 
-typical TESS FWHM at field center ($\approx$3 pixels) produced light curves
-with the highest average scatter.
-Increasing the kernel box-size from a $3\times3$ box to a $7\times7$ box led
-to about a 50\% reduction in RMS for bright stars, and no difference for 
-faint stars.
-The largest kernels, of $(11\times11)$ pixels, had on average slightly lower 
-signal-to-noise for recovered transits than for kernels of intermediate size.
-We settled on a kernel box-size of $(7\times7)$ pixels, in part because the 
-FWHM at the camera corners can grow by factors of $\approx$2 relative to the 
-field center.
-
-Varying the polynomial orders, we found that the highest order polynomials 
-retrieved transits with $\approx10\%$ worse SNR compared to lower order
-polynomials.
-Varying the polynomial orders between 1 and 4 did not produce large 
-differences.
-
-Averaging over all TOIs present in the camera we used for these experiments, 
-we found that different choices 
-of kernel parameters produced variations of $\lesssim 12\%$ in the retrieved 
-transit SNR.  
-For computational expediency, we therefore chose a single
-$(7\times 7)$ kernel with 
-second-order spatial polynomial weights in the basis functions for the
-remainder of our reduction.
-However, we caution that within our parameter-tuning experiments, the 
-recovered SNR of perhaps a third of the TOIs varied by up to a factor of two,
-which in a few 
-cases led to non-detections of transit signals near the noise floor.
-In the longer term, developing an image-subtraction method that marginalizes 
-over uncertainties of how to chose ``optimal'' kernels would be desirable.
-Pixel-level image subtraction methods that omit these 
-parameters entirely 
-are also worth exploring \citep{wang_pixel-level_2017}.
+
+This kernel model has three free parameters: (1) the box-size; 
+(2) the maximum order of the polynomial weighting the delta
+function terms; (3) the maximum order of the polynomial weighting the
+flux scaling.  We performed a grid-search to tune these parameters, in
+which our ``loss functions'' were the measured RMS as a function
+of magnitude, and the recovered SNR of transits from the catalog
+of known TOIs (TESS Objects of Interest; N.~Guerrero, in prep).
+
+In the first dimension, we varied the kernel size between a box of
+$3\times3$ pixels and $11\times11$ pixels.  Increasing the kernel
+box-size from a $3\times3$ box to a $7\times7$ box led to about a 50\%
+lower light curve RMS for bright stars, and no difference for faint
+stars.  The largest kernels, of $(11\times11)$ pixels, returned
+slightly lower signal-to-noise for recovered transits than kernels
+of intermediate size.  We settled on a kernel box-size of $(7\times7)$
+pixels, which is $\approx$2 times larger than the typical TESS FWHM
+at field center.
+
+In the other two dimensions, we varied the spatial polynomial orders
+weighting the kernel's individual pixels between first and fifth
+order.  We did the same for the polynomial weights of the ``identity''
+pixel.  Varying the polynomial orders between 1 and 4 did not produce
+large differences.  The fifth order polynomials retrieved transits
+with $\approx10\%$ worse SNR compared to lower order polynomials.  We
+therefore adopted a second order polynomial weight in both terms.
+
+Averaging over all TOIs present in the camera we used for these
+experiments, we found that different choices of kernel parameters
+produced variations of $\lesssim 12\%$ in the retrieved transit SNR.  
+For computational expediency, we therefore chose a single $(7\times
+7)$ kernel with second-order spatial polynomial weights in the basis
+functions for the remainder of our reduction.
+
+However, we caution that within these fine-tuning experiments, we
+found that transit signals near the noise floor could fall under the
+noise floor for different cases of tuned parameters.  In the longer
+term, developing an image-subtraction method that marginalizes over
+uncertainties of how to chose ``optimal'' kernels would be desirable.
+Pixel-level image subtraction methods that omit these parameters
+entirely are similarly worth exploring \citep{wang_pixel-level_2017}.
 
@@
 we calculate the instrumental fluxes for each frame per
-Equation~\ref{eq:ism_flux_measurement}. 
-We did this with three different aperture sizes: for this work, circles
-of radii 1 pixel, 1.5 pixels, and 2.25 pixels.
-These sizes were chosen to roughly span the range of optimal aperture
-sizes for stars in our sample, as calcuated from the pre-flight
-\citet{Sullivan_et_al_2015} noise model.
-Finally, to convert from a list of 
-flux measurements for each source on a frame to a list of flux values
-at any given time, we used the 
-\texttt{grcollect} transposition tool.
+Equation~\ref{eq:ism_flux_measurement}.  We did this with three
+different aperture sizes: for this work, circles of radii 1 pixel, 1.5
+pixels, and 2.25 pixels.  These sizes were chosen to roughly span the
+range of optimal aperture sizes for stars in our sample, as calcuated
+from the pre-flight \citet{Sullivan_et_al_2015} noise model.  Finally,
+to convert from a list of flux measurements for each source on a frame
+to a list of flux values at any given time, we used the
+\texttt{fitsh} transposition tool \texttt{grcollect}.
 
@@
 	\gridline{
-    \fig{raw_light_curve_systematics_sec6cam1ccd2.pdf}{0.48\textwidth}{}
-    \fig{raw_light_curve_systematics_sec7cam2ccd4.pdf}{0.48\textwidth}{}
+    \fig{detrended_light_curves_sec6cam1ccd4.pdf}{0.5\textwidth}{}
+    \fig{detrended_light_curves_sec7cam3ccd2.pdf}{0.5\textwidth}{}
   }
@@
 	\caption{
-	Twenty randomly selected raw image-subtracted light curves drawn
-	from the same sector, camera,
-	and CCD, for stars with $T$-band magnitudes between 13 and 14.
-	A number of systematic trends are shared across the light curves.
-	The sector, camera, and CCD numbers are 6, 1, 2 (left) and 7, 2, 4 (right).
-	\label{fig:lc_systematics}
+    Twenty randomly selected light curves drawn from the same sector,
+    camera, and CCD, for CDIPS target stars with $T$-band magnitudes
+    between 13 and 14.  For each star, we show the raw light curve
+    (top), PCA-detrended light curve (middle), and TFA-detrended light
+    curve (bottom).  The sector, camera, and CCD numbers are 6, 1, 4
+    (left) and 7, 3, 2 (right).  A number of systematic trends are
+    shared across raw light curves ({\it e.g.}, the periodic $\sim$3 day
+    ``chopping'' seen in the left plot).  In the PCA light curves,
+    stellar rotation signals are usually preserved, but not always ({\it
+    e.g.}, left panel, seventh from the top).  TFA filters out almost
+    all long-term trends, or else heavily distorts them ({\it e.g.},
+    right panel, fourth from the bottom)
+	\label{fig:lc_systematics_dtr}
 	}
@@
 
-\begin{figure}[!t]
-	\begin{center}
-		\leavevmode
-		\includegraphics[width=0.47\textwidth]{detrended_light_curves_sec6cam1ccd1.pdf}
-	\end{center}
-	\vspace{-0.5cm}
-	\caption{
-    Twenty randomly selected light curves drawn
-    from the same sector, camera,
-    and CCD, for stars with $T$-band magnitudes between 13 and 14.
-    Each light curve is shown from top to bottom in raw, PCA-detrended, and
-    TFA-detrended forms.
-    Stellar rotation signals are usually preserved in the PCA light curves,
-    while TFA tends to either filter them out, or to distort them.
-		\label{fig:detrended}
-	}
-\end{figure}
-
 The preceding steps produce light curves that include both
 instrumental systematics as well as astrophysical variability.
-Figure~\ref{fig:lc_systematics} shows twenty stars of
-comparable brightness randomly selected from two CCDs.  Stars that are
-far apart on the same CCD share similar changes in flux.
-In other words, the instrumental systematics seem to dominate.
-This problem is generic to most wide-field photometric datasets, including
-those from {\it e.g.}, the WASP, HAT, and Kepler surveys.
-To remove the systematic variability, we adopted two different
+Figure~\ref{fig:lc_systematics_dtr} shows twenty stars of comparable
+brightness randomly selected from two CCDs.  Stars that are far apart
+on the same CCD often share similar changes in flux.  In other words,
+the instrumental systematics seem to dominate.  This problem is
+generic to most wide-field photometric datasets, including the WASP,
+Kepler, and HAT surveys
+\cite{Pollacco_2006,borucki_kepler_2010,bakos_hat_review_2018}.  To
+remove the systematic variability, we adopted two different
 approaches: {\it (i)} the trend-filtering algorithm (TFA,
-\citealt{kovacs_trend_2005}), and {\it (ii)} a principal component analysis
-(PCA).
-
-However, a number of other approaches to the problem
-were possible. To encourage
-future improvements, we describe the
-possibility of decorrelating against external parameters
-(\S~\ref{subsubsec:external}), and also describe different approaches
+\citealt{kovacs_trend_2005}), and {\it (ii)} a principal component
+analysis (PCA).
+
+However, a number of other approaches to the problem were possible. To
+encourage future improvements, we describe the possibility of
+decorrelating against external parameters
+(\S~\ref{subsubsec:external}), and also different available approaches
 to ensemble detrending (\S~\ref{subsubsec:ensemble}), before
-explaining our implementation.
+explaining our adopted implementation.
 
@@
 subtract a linear combination of these trends as they appear across
-many light curves \citep[{\it
-e.g.},][\S~5.5]{zhang_precision_2016}.
+many light curves \citep[{\it e.g.},][\S~5.5]{zhang_precision_2016}.
 
@@
 \citealt[][]{bakos_2010,huang_high-precision_2015}).  For ground-based
-data these parameters might include zenith angle, or changing PSF shape.  For
-TESS data, they might include CCD temperature, or the angles of the
-Moon and Earth relative to each camera's boresight.  
+data these parameters might include zenith angle, or changing PSF
+shape.  For TESS data, they might include CCD temperature, or the
+angles of the Moon and Earth relative to each camera's boresight.
 They might also include the standard deviation of the spacecraft
-quartnerion time-series \citep{vanderburg_hr858_2019}.
-Some example ``external'' parameters that we include with our light
-curves are shown as functions of time in
+quartnerion time-series \citep{vanderburg_hr858_2019}.  Some example
+``external'' parameters that we include with our light curves are
+shown as functions of time in
 Figure~\ref{fig:external_parameter_timeseries}.
@@
 but often seemed to overfit stellar variability signals.  Given these
-complications, for the time being we omitted the step of ``detrending''
-as a function of external parameters. To enable further exploration of
-the issue, we included all the necessary vectors of {\it e.g.},
-centroid positions, temperatures, and shape parameters in our reported
-light curves.
+complications, for the time being we omitted the step of
+``detrending'' as a function of external parameters. To enable further
+exploration of the issue, we included all the necessary vectors of
+{\it e.g.}, centroid positions, temperatures, and shape parameters in
+our reported light curves.
 
@@
 least-squares coefficients are then used to construct a prior over
-plausible coefficient values, which is subsequently used to recompute the
-maximum likelihood coefficients for each star.  This latter step
+plausible coefficient values, which is subsequently used to recompute
+the maximum likelihood coefficients for each star.  This latter step
 reduces overfitting for stars with variability not present in the set
@@
 To remove the largest systematic trends with minimal overfitting of
-{\it e.g.}, stellar rotation signals, we adopted a simple variant of PCA
-(see {\it e.g.}, \citealt{ivezic_statistics_2014} for a review).  A similar
-approach was taken by \citet{feinstein_eleanor_2019} in
+{\it e.g.}, stellar rotation signals, we adopted a simple variant of
+PCA (see {\it e.g.}, \citealt{ivezic_statistics_2014} for a review).
+A similar approach was taken by \citet{feinstein_eleanor_2019} in
 \texttt{eleanor}.  We derived the principal components for each CCD
-using the 200 template stars previously selected for TFA.
-We then modelled each target light curve as a linear combination of a
-subset of these principal components, with weights determined by
-linear least squares.
+using the 200 template stars previously selected for TFA.  We then
+modelled each target light curve as a linear combination of a subset
+of these principal components, with weights determined by linear least
+squares.
 
@@
 visual analysis of the number of PCA components past which overfitting
-began.  We therefore used the maximum cross-validation score 
-from thefactor analysis
-as the number of principal components to use in each light curve.
-This number is
-documented in the \texttt{FITS} headers of each light curve.
+began.  We therefore used the maximum cross-validation score from
+thefactor analysis as the number of principal components to use in
+each light curve.  This number is documented in the \texttt{FITS}
+header of each light curve.
 
@@
 	\caption{
-		Positions of light curves from TESS Sectors 6
-			and 7 in galactic coordinates.
-		Black: $G_{\rm Rp}<13$ field stars.  Blue: $G_{\rm Rp}<16$
-		target stars.  Target stars are mostly near the galactic
-		plane. The data for Sectors 6 and 7 cover about one-sixth of
-		the galactic plane.
+    Positions of light curves from TESS Sectors 6 and 7 in galactic
+    coordinates.  Black: $G_{\rm Rp}<13$ field stars.  Blue: $G_{\rm
+    Rp}<16$ target stars.  Target stars are mostly near the galactic
+    plane. The data for Sectors 6 and 7 cover about one-sixth of the
+    galactic plane.
 		\label{fig:lcgalactic}
@@
     Cumulative number of CDIPS light curves a function of TESS
-			$T$-band magnitude.  Light curves were made for the
-		target stars (Figure~\ref{fig:cdips_targets}) that were observed
-		in Sectors 6 or 7.
+    $T$-band magnitude.  Light curves were made for the target stars
+    (Figure~\ref{fig:cdips_targets}) that were observed in Sectors 6
+    or 7.
 		\label{fig:cdf_T_mag}
@@
 	\caption{
-		{\it Top.} HR diagram of CDIPS stars on silicon in this
-		data release.  {\it Bottom.} HR diagram of close CDIPS stars on
-		silicon. The wedge separating the pre-MS sample from the MS
-		stars was discussed by \citet{zari_3d_2018}, who introduced it in
-		order to avoid contamination by photometric binaries.
+    {\it Top.} HR diagram of CDIPS stars on silicon in this data
+    release.  {\it Bottom.} HR diagram of close CDIPS stars on
+    silicon. The wedge separating the pre-MS sample from the MS stars
+    was discussed by \citet{zari_3d_2018}, who introduced it in order
+    to avoid contamination by photometric binaries.
 	}
@@
     Average autocorrelations of $10^4$ randomly selected light curves
-    from each sector.
-    The medians at time lags spaced by one hour are shown for 
-    raw light
-    curves (column name \texttt{IRM}) in gray, and for
-    TFA-detrended light curves in black.
-    The gray bands display the 25$^{\rm th}$ to 75$^{\rm th}$ percentile
-    range for each type of light curve.
+    from each sector.  The medians at time lags spaced by one hour are
+    shown for raw light curves (column name \texttt{IRM}) in gray, and
+    for TFA-detrended light curves in black.  The gray bands display
+    the 25$^{\rm th}$ to 75$^{\rm th}$ percentile range for each type
+    of light curve.
   \label{fig:avg_acf}
@@
 
-The on-sky locations of the light curves from Sectors 6 and 7
-are shown in Figure~\ref{fig:lcgalactic}.
-Black stars are the field stars for which we performed photometry,
-and of which a subset were used as template stars during TFA.
-The blue stars are the \numberlcs stars with light curves available
-from \stscilink.
-Most of the target stars are quite close to the galactic plane.
-Gaps between CCD chips are also visible.
-The highly clumped nature of the target stars is also apparent.
+The on-sky locations of the light curves from Sectors 6 and 7 are
+shown in Figure~\ref{fig:lcgalactic}.  Black stars are the field stars
+for which we performed photometry, and of which a subset were used as
+template stars during TFA.  The blue stars are the \numberlcs stars
+with light curves available from \stscilink.  Most of the target stars
+are quite close to the galactic plane.  Gaps between CCD chips are
+also visible.  The highly clumped nature of the target stars is also
+apparent.
 
@@
 
-Figure~\ref{fig:cdf_T_mag} shows the cumulative distribution of
-TESS $T$-band magnitudes for the target stars.
-Though most of the targets are faint, $\approx3\times10^4$ are
-brighter than $T=13$. These targets are more promising for any
-detailed follow-up observtions.
-
-An HR diagram for the entire sample of CDIPS stars on silicon
-is shown in Figure~\ref{fig:hrd} (top).
-The sub-sample of stars with
-measured positive parallaxes and naive distances less than
-$1\,{\rm kpc}$ is also shown (bottom).
-About one-third of the stars are in this latter sample.
-The close stars are predominantly on the main-sequence, or the pre-main-sequence.
-A relatively large fraction of these come from \citet{zari_3d_2018},
-and are either on the PMS or upper main-sequence.
-The latter set of OBA dwarf stars, while ``younger'' than the typical
-field dwarf, are likely the least interesting subset of our target sample
-from the perspective of age analyses.
-In the entire sample (Figure~\ref{fig:hrd} top), a much larger fraction of stars are sub-giants,
-red giants, and helium-burning red-clump stars.
-We failed to obtain light curves for roughly $5\%$ of the stars on silicon, 
-primarily due to our masking of saturated stars and their nearby pixels.
+Figure~\ref{fig:cdf_T_mag} shows the cumulative distribution of TESS
+$T$-band magnitudes for the target stars.  Though most of the targets
+are faint, $\approx3\times10^4$ are brighter than $T=13$. These
+targets are more promising for any detailed follow-up observtions.
+
+An HR diagram for the entire sample of CDIPS stars on silicon is shown
+in Figure~\ref{fig:hrd} (top).  The sub-sample of stars with measured
+positive parallaxes and naive distances less than $1\,{\rm kpc}$ is
+also shown (bottom).  About one-third of the stars are in this latter
+sample.  The close stars are predominantly on the main-sequence, or
+the pre-main-sequence.  A relatively large fraction of these come from
+\citet{zari_3d_2018}, and are either on the PMS or upper
+main-sequence.  The latter set of OBA dwarf stars, while ``younger''
+than the typical field dwarf, are likely the least interesting subset
+of our target sample from the perspective of age analyses.  In the
+entire sample (Figure~\ref{fig:hrd} top), a much larger fraction of
+stars are sub-giants, red giants, and helium-burning red-clump stars.
+We failed to obtain light curves for roughly $5\%$ of the stars on
+silicon, primarily due to our masking of saturated stars and their
+nearby pixels.
 
@@
 probability exceeding 50\%.  To create cleaner sub-samples, we advise
-use of the \texttt{CDEXTCAT} header keyword, which can be used
-to merge against the original source catalog to obtain the
-membership probabilities claimed by the original catalog.
+use of the \texttt{CDEXTCAT} header keyword, which can be used to
+merge against the original source catalog to obtain the membership
+probabilities claimed by the original catalog.
 

### 2019-07-24 paper_I/collect_figures.sh

@@ -17,8 +17,11 @@ cp ${fdir}trex_overview.pdf ${pdir}pipelineoverview.pdf
 # rms vs mag 
 fdir=../results/paper_figures/
 
-cp ${fdir}detrended_light_curves_sec6cam1ccd1.pdf \
-   ${pdir}detrended_light_curves_sec6cam1ccd1.pdf
+cp ${fdir}detrended_light_curves_sec7cam3ccd2.pdf \
+   ${pdir}detrended_light_curves_sec7cam3ccd2.pdf
+
+cp ${fdir}detrended_light_curves_sec6cam1ccd4.pdf \
+   ${pdir}detrended_light_curves_sec6cam1ccd4.pdf
 
 cp ${fdir}external_parameters_vs_time_sec6cam1ccd1.pdf \
    ${pdir}external_parameters_vs_time_sec6cam1ccd1.pdf

### 2019-07-25 paper_I/ms_ttrex_sketch.tex

%% LaTeX template for the science justification & technical
%% feasibility to be submitted as part of a TESS Guest Investigator
%% Program proposal. This template is based on the proposal template
%% used by the NuSTAR mission.
%%
%% TESS Guest Investigator Proposal Cycle 1 template
%% V1.0
%% 2017-08-04

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% DOCUMENT FORMAT %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% The default font was chosen to be easily readable while allowing
%% sufficient material to be included.

%% Please note that the proposal will be printed on US Letter size paper,
%% 8.5 in x 11 in, and that formatting the text for other sizes will
%% generally cause layout problems and may result in text being cut
%% off near the edges. PLEASE DO NOT CHANGE THE 'LETTERPAPER' OPTION
%% IN THE DOCUMENTCLASS COMMAND.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% Default format: 11pt single column %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% NOTE: NASA ROSES requires body font size to be no smaller than 15 
%% characters per inch (equivalent to Times Roman 12 point).
%%
%% Minimum margin size is 1 inch from top, bottom, and sides.

\documentclass[letterpaper,11pt]{article}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% HOW TO INCLUDE FIGURES %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% Please see the ``Included packages'' section below.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% Included packages %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{graphics,graphicx}
\usepackage{hyperref}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{comment}
\usepackage{amssymb}
\usepackage{setspace}
\renewcommand{\baselinestretch}{1.0}

%\usepackage[colorlinks]{hyperref}
%\hypersetup{urlcolor=blue}
%\usepackage{cleveref}

\usepackage{natbib}
\usepackage{bibentry} %needed for "nobibliography" option
% abbrvnat, modded to fix length of references, and to not show title
\bibliographystyle{abbrvnat86}
\setcitestyle{authoryear,open={(},close={)}}
\setlength{\bibsep}{0pt plus 0.2ex} % set bibliography line separation small
\renewcommand{\bibsection}{} % get rid of "References" heading

%% Feel free to modify the included packages list to use your
%% favorite packages.

%% In the graphics and graphicx packages, Postscript and eps figures
%% can be included using the \includegraphics command. The graphics
%% package is part of standard LaTeX2e and provides a basic way of including a
%% figure. The graphicx package is not standard, but extends the
%% \includegraphics command to make it more user-friendly. If graphicx
%% is not available on your system please remove it from the list of
%% included packages above.

%% Syntax:
%% In the graphics package:
%%
%% \begin{figure}
%% \includegraphics[llx,lly][urx,ury]{file}
%% \end{figure}
%%
%% where ll denotes 'lower left' and ur 'upper right' and the x and y
%% values are the coordinates of the PostScript bounding box in
%% points. There are 72 points in an inch.
%%
%% In the graphicx package:
%% 
%% \begin{figure}
%% \includegraphics[key=val,key=val,...]{file}
%% \end{figure}
%%
%% where some of the useful keys are: angle, width, height,
%% keepaspectratio (='true' or 'false') and scale. Bounding box values
%% can be given as [bb=llx lly urx ury].
%%
%% In either case you have to use LaTeX figure placement commands to
%% position the figure on the page; \includegraphics will not do
%% that. Both these commands also have other options that are listed
%% in the LaTeX manual (for the graphics package) and in 'The LaTeX
%% Graphics Companion' (for the graphicx package).

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% Page dimensions %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setlength{\textwidth}{6.5in} 
\setlength{\textheight}{9in}
\setlength{\topmargin}{-0.0625in} 
\setlength{\oddsidemargin}{0in}
\setlength{\evensidemargin}{0in} 
\setlength{\headheight}{0in}
\setlength{\headsep}{0in} 
\setlength{\hoffset}{0in}
\setlength{\voffset}{0in}
\setlength{\skip\footins}{2ex}

% remove excess white space
\setlength\belowcaptionskip{-3ex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% Section heading format %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\makeatletter
\renewcommand\section{\@startsection%
{section}{1}{0mm}{-0.5\baselineskip}%
{0.5\baselineskip}{\normalfont\normalsize\bfseries}}%
\makeatother

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% Some Useful Abbreviations %%%%% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\tess}{{\it TESS}}
\newcommand{\jwst}{{\it JWST}}
\newcommand{\kepler}{{\it Kepler}}
\newcommand{\ktwo}{{\it K2}}
\newcommand{\hst}{{\it HST}}
\newcommand{\msun}{$M_{\odot}$}
\newcommand{\rsun}{$R_{\odot}$}
\newcommand{\lsun}{$L_{\odot}$}
\newcommand{\re}{$R_{\oplus}$}
\newcommand{\me}{$M_{\oplus}$}
\newcommand{\rj}{$R_{\textrm{\scriptsize Jup}}$}
\newcommand{\mj}{$M_{\textrm{\scriptsize Jup}}$}
\newcommand{\ms}{m~s$^{-1}$}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% Start of document %%%%% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
%\nobibliography{bibliography}{}
\pagestyle{plain}
\pagenumbering{arabic}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% Title of proposal %%%%% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{center} 
\bfseries\uppercase{
  Difference Imaging Makes A Difference: Probing Exoplanet Age Evolution With 
All-Sky Cluster Surveys  
}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% Body of science justification %%%%%
%%%%% and technical feasibility     %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vspace{-4mm}

\section{Scientific Motivation}

\vspace{-0.3mm}
Each of the $\sim$1000 star clusters of the Milky Way is a gift to
astrophysics, providing a sample of stars that vary widely in mass
but all have approximately the same age and composition.  Time-series
photometry of clusters\footnote{For brevity, we use this term to refer
  to open clusters, moving groups, associations, and star-forming
  regions.} has numerous applications.  By measuring rotation periods
over a range of ages, we can study the angular momentum evolution of
stars and improve our ability to determine stellar ages through
``gyrochronology.'' By measuring eccentricities as a function age, we
can study the tidal evolution of binaries. The detection of eclipsing
binaries can lead to the precise determination of the absolute
dimensions of the stars and stringent tests of stellar-evolutionary
models.  Circumstellar material can also be studied by finding the
rare cases in which the material produces eclipses.

The detection of transiting planets --- our main motivation for the
proposed work --- will shed light on the timescales for processes in
planet formation, evolution, and migration, and on the effects of
cluster density. With a larger sample of transiting planets in clusters of
varying ages, we could see the evolution of the radius distribution of
giant planets as they contract \citep{Fortney_et_al_2007}, and watch
as the closest-in planets lose mass to photo-evaporation
\citep{Owen_Wu_2017, Fulton_et_al_2017}.  The Hyades planet K2-25b
\citep{Mann_K2_25_2016}, for example, appears to be oversized compared
to mature planets of the same mass and irradiation.  By searching for
hot Jupiters in clusters we can determine when these misplaced planes
begin to appear,
thereby constraining theories for their formation. The discovery of
K2-33b has already showed that in at least one case a hot Neptune was
able to form in fewer than 10~Myr \citep{David_et_al_2017,Mann_K2_33b_2016}.
Detecting planets in dense clusters ($\gtrsim$1000\,pc$^{-3}$) may
also reveal how the stellar encounters affect planetary
system architecture \citep{Meibom_et_al_2013}.  Yet most of this work
remains for the future: only about 10 of the currently known
transiting planets are in clusters.

In mid-2018, the Transiting Exoplanet Survey Satellite (\tess) will
begin searching for exoplanets.  The mission's main
goal is to detect small transiting planets around bright stars, and to
measure their masses using ground-based Doppler spectroscopy.  Within a
few months of data acquisition, the {\it TESS} team will release light curves
with 2-minute sampling for a few hundred thousand pre-selected target
stars.  These target stars will be chosen based on planet
detectability~\citep{Stassun_et_al_2017}.  In addition, the mission will
release full-frame images with 30-minute sampling, which are a ``bonus''
that were not part of the original mission goals.

Through its full-frame images, \tess\ holds the promise to
deliver the most homogeneous and comprehensive photometric cluster
survey in history.  Based on the cluster membership database of
\citet{Kharchenko_et_al_2013} and the $\!$\tess\ apparent magnitude
calculator of~\citet{Jaffe_Barclay_2017}, we estimate that $10^5$
cluster members brighter than $T=16$ will be observed in each
ecliptic hemisphere's full-frame images.

There will be formidable obstacles to deriving precise
photometry from {\it TESS} images of cluster fields because
of the relatively poor angular resolution ($\approx 20''/{\rm px}$).
Almost all clusters are within 10 degrees of the Galactic
plane (see Figure~\ref{fig:cluster_positions_dilution}),
where the problems with crowding and complex backgrounds are so severe that 
the {\it TESS}\,
Science Team has neglected that portion of the sky in their planet
simulations \citep{Sullivan_et_al_2015}. 
Similarly, the {\it TESS}\, target star list deprioritizes all objects 
within $15^\circ$ of the galactic plane~\citep{Stassun_et_al_2017}, which 
includes 90\% of
all star clusters.  The large pixel size and the high stellar surface
density will make aperture photometry unreliable.  Yet,
aperture photometry is the basis of the official {\it TESS} data
reduction pipeline and almost all reduction methods that have been
applied to {\it Kepler} and {\it K2} data.

These challenges are substantial --- and surmountable, with the tools
that have been used to analyze ground-based images with very similar 
characteristics to those of {\it TESS} images.  {\bf We
  propose to produce light curves of star cluster members by applying
  difference-imaging methods to the {\it TESS} full-frame images.}
Our own motivation is to search for transiting giant planets, but we will 
deliver these light curves promptly to the MAST public archive
for the entire community to perform a wide range of scientific
investigations.

\begin{figure}[!tb]
    \begin{subfigure}{.6\textwidth}
        \centering
        \includegraphics[width=1.02\textwidth]{figures/cluster_positions_ecliptic_scicase.pdf}
        %\caption{A subfigure}
        %\label{fig:sub2}
    \end{subfigure}
    \begin{subfigure}{.4\textwidth}
        \centering
        \includegraphics[width=.95\textwidth]{figures/dil_Tmaglt16_dlt2kpc_members.pdf}
        %\caption{A subfigure}
        %\label{fig:sub3}
    \end{subfigure}
    \caption{ {\it Left:\,} Clusters are at low galactic latitudes. Each
      ecliptic hemisphere has about $10^5$ cluster stars with
      $T<16$ and $d < 2\,{\rm kpc}$. Blue circles show 885
      documented clusters \citep{Kharchenko_et_al_2013}. Orange stars are the
      clusters that have been closely monitored by ground-based telescopes. 
      Orange squares are clusters that were surveyed by \kepler\ and \ktwo.
      {\it TESS} will provide homogeneous and continuous data for most of 
      these clusters (shaded background).  
    \newline{\it Right:} The dilution problem. Within a standard
    aperture, a single cluster star usually contributes only a small
    fraction of the total flux. Shown here is the histogram of this
    flux fraction for cluster stars with $T<16$ and $d<2\,{\rm
      kpc}$. Almost none are well suited to aperture photometry. About
    half have flux fractions $>0.1$ and will be amenable to difference
    imaging. 
    \label{fig:cluster_positions_dilution}
    }
\end{figure}

\vspace{-0.3mm}
\section{Team \& Context}
\vspace{-0.3mm}

Ph.D. student Luke Bouma will hold primary responsibility for the project.
Mr.$\ $Bouma will process the \tess\ full-frame images, produce light curves, 
and deliver them to the MAST archive. He will search the light curves for 
transiting exoplanets, oversee follow-up observations of candidates, and lead 
the subsequent analysis effort.
This will be accomplished under the supervision of Prof.$\ $Joshua Winn (PI), 
and collaborating with Prof.$\ $G\'asp\'ar Bakos, Dr.$\ $Joel Hartman, and 
Dr.$\ $Waqas Bhatti.

Our group has extensive experience with precise time-series
photometry, including difference imaging and cluster photometry,
through our leadership of the HATNet and HATSouth transiting planet
surveys as well as deep surveys of crowded fields in M\,37 and 
M\,33~\citep{hartman_deep_2006,hartman_deep_2009}.  We are commissioning a new
multi-telescope observatory called HATPI, at Las Campanas Observatory,
employing 63 wide-field 10~cm lenses that have a pixel scale similar
to the {\it TESS} cameras. 
The combined HATPI, HATSouth, and HATNet datasets will compliment
\tess, and will help in discovering large planets with only a few transits in 
the $28\,{\rm days}$ of \tess\ photometry.

\vspace{-0.3mm}
\section{Data Reduction Plan}
\vspace{-0.3mm}

The concept of difference imaging (also called image subtraction) is
to isolate variable sources from within blends and complex
backgrounds, by subtracting each image from an appropriate convolution
of a master image \citep{Alard_Lupton_1998}.

We have an existing software pipeline for difference imaging, photometry, and 
detrending. Our implementation is a descendant of the \texttt{fitsh} code, 
described by~\citet{Pal_2012}. Our light curve processing tools are based on
\texttt{VARTOOLS}~\citep{Hartman_Bakos_2016} and 
\texttt{astrobase}~\citep{bhatti_astrobase_2018}.
We also have modules for filtering instrumental systematics from 
the light curves, leaving only astrophysical 
signals~~\citep{Kovacs_et_al_2005,Bakos_et_al_2010}.
Our tools for identification and vetting of candidate transit signals are 
well-tested: they have been honed over 15 years and more than 100 planet 
discoveries.
We also successfully applied our pipeline to {\it K2} data.
In a project led by a Princeton Ph.D. student,
\citet{Soares-Furtado_et_al_2017} performed difference imaging on a
\ktwo\ ``superstamp'' covering the open clusters M\,35 and NGC\,2158,
leading to the most precise time-series photometry that is currently
available for those fields.

Figure~\ref{fig:hatpi_feasibile} shows that our image subtraction
pipeline can successfully reduce HATPI images, which will be very
similar to \tess\ full-frame images.  
Mr.$\ $Bouma will reduce and analyze three years of 
similar data from the HATPI prototype instrument before the initial \tess\ 
data release, which will provide an opportunity for further software testing.

\begin{figure}[!t]
    \centering
    \includegraphics[width=.85\textwidth]{figures/FieldComparison.png}
    \caption{The problem of crowding. Each field is a real 13$^\circ$ image
      from HATPI, which has nearly the same pixel scale as {\it TESS}. On the 
      left
      is a typical field, for which aperture photometry will be adequate.
      On the right is a typical {\it cluster} field, for which aperture 
      photometry
      cannot be relied upon. Difference imaging is required to isolate
      sources of photometric variability.
      \label{fig:FieldComparison}}
\end{figure}

\vspace{-0.3mm}
\section{Necessity and Feasibility}
\label{sec:technical_feasibility}
\vspace{-0.3mm}

For almost all the clusters {\it TESS} will observe, image subtraction
is necessary to produce reliable light curves.  One way to quantify
the blending problem is to ask what fraction of the total flux in a
photometric aperture is contributed by a particular target star.
Aperture photometry is reliable when this fraction is close to unity.
Difference imaging, in our experience, can produce reliable photometry
even when this fraction is as low as 0.1.  Based on the cluster
membership data of \citet{Kharchenko_et_al_2013}, and the density of
background stars, we find that the median dilution fraction of stars
with $T<16$ is 0.13 for an aperture radius of 2 pixels. Difference
imaging is therefore essential, and feasible.

As noted above, the scope of scientific investigations that will be
possible with cluster light curves is very broad.  Since our own
interest is in transiting planets, we have assessed the prospects for
planet detection in the following manner.  We used the {\it TESS}
noise model of \citet{Sullivan_et_al_2015}, as implemented in the code
of \citet{Jaffe_Barclay_2017}, to predict the achievable noise
level for all $T<16$ cluster members in the southern ecliptic
hemisphere.  Using the catalog values of the color and age of each
star, we estimated the mass and radius with reference to the
stellar-evolutionary models of \citet{Siess_et_al_2000}. We then
calculated the number of stars for which a planet with a 10-day period
could be detected with a signal-to-noise ratio exceeding 10, even in
the face of the estimated flux dilution.

During \tess\ Cycle 1 ($\sim$June 2018-2019) we find that 20,000 cluster stars 
can be searched for Jupiter-sized planets, and 3,200 stars can be searched for
Neptune-sized planets.  Taking into account the transit probability,
and a typical occurrence of 0.5\%, this would result in about 15 hot
Jupiters and 5 hot Neptunes.  To put this into perspective, there are
currently only 13 transiting cluster planets known, and only one transiting hot
Jupiter \citep{David_et_al_2017,Mann_et_al_2017}.
\tess\ will observe a comparable number of cluster stars in Cycle 2 
($\sim$June 2019-2020), which will double the yields, giving a total of 30 hot 
Jupiters and 10 hot Neptunes by the end of \tess\ Cycle~2.

We will follow up planet candidates through our participation in the {\it TESS}
Follow-up Observing Program and the international KESPRINT consortium.
We also have 100\% of the observing time on the newly deployed CHAT
0.7$\,$m automated photometric telescope at Las Campanas Observatory,
Chile. Dedicated observations with CHAT will allow us to obtain images with 
better photometric precision and higher spatial resolution ($\approx 
0.7''/{\rm px}$) than {\it TESS}. This will be essential in helping us
determine which star is responsible for transits in heavily blended regions of 
clusters.
The HATNet and HATSouth teams have many years of experience vetting transit 
candidates, and have confirmed over 100 transiting planets from their combined 
surveys.

\vspace{-0.3mm}
\section{Expected Impact}
\label{sec:impact}

\vspace{-0.3mm}
\begin{figure}[!t]
    \centering
    \begin{subfigure}{.333\textwidth}
        \centering
        \includegraphics[width=.99\textwidth]{figures/M25_crop.png}
        %\caption{A subfigure}
        %\label{fig:sub1}
    \end{subfigure}%
    \begin{subfigure}{.333\textwidth}
        \centering
        \includegraphics[width=.99\textwidth]{figures/M25_sub_crop.png}
        %\caption{A subfigure}
        %\label{fig:sub2}
    \end{subfigure}
    \begin{subfigure}{.30\textwidth}
        \centering
        \includegraphics[width=1.05\textwidth]{figures/norefnoise_rms_vs_mag_binned30min_TESScomparison.pdf}
        %\caption{A subfigure}
        %\label{fig:sub3}
    \end{subfigure}
    \caption{Application of difference imaging to the field shown in the right 
    panel of Figure~\ref{fig:FieldComparison}.
    {\it Left}: The 2.2$^\circ$ region surrounding the cluster M\,25.
    {\it Middle:} Typical difference image. Variable stars are black 
    or white; saturated stars are masked; other artifacts are PSF residuals.
    {\it Right:} Variability (median absolute deviation) of HATPI light 
    curves, at 30 minute cadence, for thousands of stars in this crowded 
    field. The solid curve is \tess's expected performance, ignoring signal 
    dilution by blended stars~\citep{Sullivan_et_al_2015}. The dashed curve 
    accounts for dilution by a factor of 10.
    HATPI's light-collecting area is similar to that of \tess,
    and HATPI achieves a precision comparable to that expected from \tess.
    }
    \label{fig:hatpi_feasibile}
\end{figure}

\vspace{-0.3mm}
The \tess\ full-frame images of star clusters are a gold mine for
stellar astrophysics and exoplanetary science.  However the gold will
remain in the ground without a dedicated effort to solve the problem
of achieving high photometric precision in crowded images.  With
funding from the NESSF we will adapt our codes for difference
imaging to the {\it TESS} full-frame images.  We will make the light
curves available through MAST, and we will make the source code for
image subtraction, photometry, and detrending available on github. We
will also search the light curves of suitable stars for transiting
planets, which we intend to validate and follow up.  Through this
effort we can expect to quadruple the number of known transiting planets in
clusters, and provide a glimpse of the evolving physical and dynamical
properties of giant planets.

\vspace{-0.3mm}
\section{Relevance to NASA's Astrophysics \& Planetary Science Goals}
\vspace{-0.3mm}
Our proposal aims to discover and study planets around other stars, 
which is a goal of NASA's Astrophysics 
subdivision~\citep[][Ch.~4.4]{NASA_strategic_2014}. 
The analysis will be primarily enabled by \tess, an Astrophysics Explorer 
mission.
The effort will enhance \tess's science return because
\begin{itemize}
\item[A)] we will use a different reduction method from the mission's 
science team (difference imaging vs.~aperture photometry),
which will increase our photometric precision in crowded fields;
\vspace{-0.4mm}
%
\item[B)] we will focus our analysis and follow-up efforts near the 
galactic plane, which will be neglected by the mission's prioritization 
metrics~\citep{Stassun_et_al_2017}. 
%
\item[C)] we will perform high resolution ground-based photometric follow-up 
with the CHAT 0.7m to validate candidate transiting planets;
%
\item[D)] we will deliver our light curves to the MAST public archive, 
which will facilitate a wide range of other investigations. The \tess\ team 
has only committed to producing lightcurves for 200,000 stars amenable to 
transiting exoplanet detection, most of which will be far from the galactic 
plane~\citep{Stassun_et_al_2017}. 
\vspace{-0.4mm}
%
\
\end{itemize}

Our proposal also addresses topics solicited by the Planetary Science 
subdivision: one way to improve understanding of how exoplanet systems form 
and evolve is to observe them at known ages. 
By studying the sizes of transiting planets as a function of age, 
we could indirectly observe processes including photoevaporation and giant 
planet contraction.
By discovering hot Jupiters around young hosts, we could also
help distinguish between hot Jupiter formation scenarios, since the timescales 
for some variants of high-eccentricity migration are longer than those for 
disk migration~\citep[\textit{e.g.},][]{dawson_origins_2018}.
Another way to help distinguish between hot Jupiter formation channels would 
be measuring exoplanet (occurrence, period, age) or (occurrence, eccentricity, 
age) relations. For such analysis efforts to be convincing, we must first 
expand the sample of giant planets with known ages.

\vspace{-0.3mm}
\section{Timeline \& Expected Publications}
\vspace{-0.3mm}
\begin{figure}[!h]
    \centering
    \includegraphics[width=\textwidth]{figures/work_plan_crop.pdf}
    \caption{
    Project timeline. Colors correspond to the planned times of each task.
    Team members~---~LB: Luke Bouma, JW: Joshua Winn, GB: G\'asp\'ar 
    Bakos, JH: Joel Hartman, WB: Waqas Bhatti.
    \label{fig:work_plan}}
\end{figure}

A timeline listing our major expected milestones, as well as those of the 
\tess\ project, is shown in Figure~\ref{fig:work_plan}.
Once our \tess\ data reduction pipeline has been heavily automated, we will 
begin a second component of the project: jointly analyzing the HAT and \tess\ 
lightcurves in the southern sky.
Extending the observing baseline for these targets beyond the expected 
$\approx\!28\,{\rm days}$ of \tess\ photometry will improve our sensitivity 
to longer period planets.

At least four publications are expected from the three-year effort.
Their respective topics will be:
1) \tess\ Cycle~1 planet discovery paper;
2) combined southern-sky HAT and \tess\ planet discovery paper;
3) \tess\ Cycle~2 planet discovery paper;
4) injection-recovery analysis of cluster survey from Cycles~1~\&~2, with 
occurrence rate estimate over as many ages as possible.

\vspace{-0.3mm}
\section{Robustness of Research Plan to Anticipated Setbacks}
\vspace{-0.3mm}

If the \tess\ mission performs as expected, the technical challenges of this 
project are surmountable: we showed in 
Figures~\ref{fig:FieldComparison}~\&~\ref{fig:hatpi_feasibile} that we
can reduce images analogous to the \tess\ full-frames images, in crowded 
fields with heavy blending.
Beyond applying photometric and centroid tests to \tess\ data, we will 
vet for astrophysical false positives by performing higher resolution 
follow-up photometry with the CHAT 0.7m ($\approx 0.7''/{\rm px}$ over a 
$0.4^\circ\times 0.4^\circ$ 
field of view). This will be especially important for determining which stars 
are the planet-hosts in crowded regions.

If \tess' photometric precision is worse than expected, our project 
will still have a high impact; our planet yield estimates are not strongly 
dependent on low-SNR detections, and so we can afford a somewhat lower
photometric precision.
Relatedly, young stars are more variable than old stars, and so their light 
curves will be noisier over transit timescales than assumed
by~\citet{Sullivan_et_al_2015}.
For young stars in clusters, simultaneously fitting for dips and a 
quadratic continuum during the transit search can help recover any losses in 
detection efficiency~\citep{rizzuto_zodiacal_2017}.

Finally, there is a community-oriented question: the \tess\ team, and other 
teams interested in cluster planets, will detect some planets in clusters 
before us.
This will at most marginally affect our work's impact: our publicly-released 
light curves will still be useful for broad community science, and they will 
still achieve higher photometric precision than simple aperture photometry.
Our approach will help maximize the overall number of detected planets in 
clusters, and so no matter what will be valuable for systematically studying 
planet occurrence as a function of age.

\vspace{.3cm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

% References {\it are included} when considering the proposal 4 page limit.
%\begingroup
%    \setlength{\bibsep}{10pt}
%    \linespread{1}\selectfont
%    \nobibliography{bibliography}{}
%\endgroup
%\newpage
%\newpage
\noindent
{ \tiny
\bibliography{bibliography}{}
}
%\bibliographystyle{aasjournal}

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% End of document %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}

### 2019-07-25 paper_I/ms.tex
paper updtaes

@@
   %
-  The light curves are available at \stscilink.
+  The light curves, which cover about one sixth of the galactic plane,
+  are available at \stscilink.
 \end{abstract}
@@
 
-\begin{figure}[!t]
+\begin{figure*}[!t]
 	\begin{center}
 		\leavevmode
-		\includegraphics[width=0.47\textwidth]{rms_vs_mag.pdf}
+		\includegraphics[width=0.97\textwidth]{IRM-PCA-TFA_rms_vs_mag.pdf}
 	\end{center}
@@
 	\caption{
-    Standard deviation of TFA-detrended CDIPS light curves as a
-    function of catalog TESS-band magnitude.  Black points correspond
-    to the minimum RMS across the available three aperture sizes.  The
-    model (orange and gray lines) assumes aperture sizes reported by
+    Standard deviation of CDIPS light curves as a function of catalog
+    TESS-band magnitude.  Left-to-right are raw, PCA-detrended, and
+    TFA-detrended light curves. Black points correspond to the minimum
+    RMS across the available three aperture sizes.  The model (orange
+    and gray lines) assumes aperture sizes reported by
     \citet{Sullivan_et_al_2015}, and the effective area from
@@
 
-We will discuss our search for transiting planets in an upcoming
-report.  To identify an initial set of transiting planets, strong
+Below, we provide a few examples of how one might go about identifying
+pulsating stars, strong stellar rotators, eclipsing binaries, and
+transiting planets in the light curves.
+
+\paragraph{Sinusoidal signals}
+For pulsating stars and strong stellar rotators, the Lomb-Scargle
+periodogram (CITE) is a tried-and-true discovery method.
+
+We measured rotation periods for stars in X, Y clean cluster.
+
+A figure is given here.
+
+To identify an initial set of transiting planets, strong
 stellar rotators, and eclipsing binaries, we performed a few steps of

### 2019-07-25 paper_I/collect_figures.sh

@@ -35,7 +35,7 @@ cp ${fdir}stages_of_image_processing_bad.png \
 cp ${fdir}primary_mission_galacticmap_forproposal_cdipsoverplot.png \
    ${pdir}target_star_positions.png
 
-cp ${fdir}rms_vs_mag.pdf ${pdir}rms_vs_mag.pdf
+cp ${fdir}IRM-PCA-TFA_rms_vs_mag.pdf ${pdir}IRM-PCA-TFA_rms_vs_mag.pdf
 cp ${fdir}avg_acf.pdf ${pdir}avg_acf.pdf
 
 cp ${fdir}raw_light_curve_systematics_sec7cam2ccd4.pdf \

### 2019-07-25 tests/kernel_checks.py
add kernel visualization test

@@ -1,0 +1,129 @@
+import os
+import numpy as np, pandas as pd, matplotlib.pyplot as plt
+
+from mpl_toolkits.axes_grid1 import make_axes_locatable
+import matplotlib.colors as colors
+from matplotlib import cm
+
+from datetime import datetime
+
+kerneldir ='../data/kernels/'
+testkernel = os.path.join(kerneldir,
+                          'rsub-d2f9343c-tess2018360042939-s0006-1-1-0126_cal_img_bkgdsub-xtrns.fits-kernel')
+
+def read_kernel_img(kernelpath):
+
+    with open(kernelpath, mode='r') as f:
+        lines = f.readlines()
+
+    for ix, l in enumerate(lines):
+        if l.startswith('# Image:'):
+            startnum = ix
+
+    imglines = [l for l in lines[startnum+1:]]
+
+    clines = [','.join(l.split()) for l in imglines]
+    clines = [c[2:]+'\n' for c in clines]
+
+    temppath = os.path.abspath(kernelpath)+'temp'
+    with open(temppath, mode='w') as f:
+        f.writelines(clines)
+
+    header = ['u','v','p0-q0','p0-q1','p0-q2','p1-q1','p1-q2','p2-q2']
+
+    df = pd.read_csv(temppath, names=header)
+
+    os.remove(temppath)
+
+    return df
+
+
+def _make_kernel_plot(_kernel, kernelsize, order):
+
+    plt.close('all')
+    plt.rcParams['xtick.direction'] = 'in'
+    plt.rcParams['ytick.direction'] = 'in'
+
+    fig, ax = plt.subplots(ncols=1, nrows=1)
+
+    ##########################################
+
+    vmin, vmax = -0.025, 0.025
+    linnorm = colors.Normalize(vmin=vmin, vmax=vmax)
+
+    #extent=[horizontal_min,horizontal_max,vertical_min,vertical_max]
+    extent = [-3.5,3.5,-3.5,3.5]
+
+    cset1 = ax.imshow(_kernel.T, cmap='RdBu', vmin=vmin, vmax=vmax,
+                      norm=linnorm, interpolation='none', origin='lower',
+                      extent=extent)
+
+    for i in range(kernelsize):
+        for j in range(kernelsize):
+
+            u = i - int(np.floor(kernelsize/2))
+            v = j - int(np.floor(kernelsize/2))
+
[…]

### 2019-07-27 paper_I/ms.tex
paper update figs

@@
 
-\begin{figure}[!t]
+\begin{figure*}[!t]
 	\begin{center}
 		\leavevmode
-		\includegraphics[width=0.47\textwidth]{avg_acf.pdf}
+		\includegraphics[width=0.97\textwidth]{avg_acf.pdf}
 	\end{center}
@@
 shown in Figure~\ref{fig:lcgalactic}.  Black stars are the field stars
-for which we performed photometry, and of which a subset were used as
-template stars during TFA.  The blue stars are the \numberlcs stars
-with light curves available from \stscilink.  Most of the target stars
-are quite close to the galactic plane.  Gaps between CCD chips are
-also visible.  The highly clumped nature of the target stars is also
-apparent.
-
-%A zoom-in of Figure~\ref{fig:lcgalactic} is shown in Figure~\ref{fig:lcradeczoom}
-%for the Camera 1, Sector 6 field. The effects of galactic-latitude
-%dependent extinction are visible through the decreasing density of black
-%points towards the right of the image.
+for which we performed photometry, and from which we selected template
+stars for TFA, as well as the construction of the PCA eigenvectors.
+Blue points are the \numberlcs stars with light curves available from
+\stscilink.  Most of the target stars are quite close to the galactic
+plane.  Gaps between CCD chips are also visible.  The highly clumped
+nature of the target stars is also apparent.
 
@@
 $T$-band magnitudes for the target stars.  Though most of the targets
-are faint, $\approx3\times10^4$ are brighter than $T=13$. These
-targets are more promising for any detailed follow-up observtions.
+are faint, $\approx3\times10^4$ are brighter than $T=13$. The brighter
+targets will be more amenable to detailed spectroscopic observtions,
+should the need arise.
 
@@
 also shown (bottom).  About one-third of the stars are in this latter
-sample.  The close stars are predominantly on the main-sequence, or
-the pre-main-sequence.  A relatively large fraction of these come from
+sample.  Of the close stars, a relatively large fraction come from
 \citet{zari_3d_2018}, and are either on the PMS or upper
@@
 stars are sub-giants, red giants, and helium-burning red-clump stars.
-We failed to obtain light curves for roughly $5\%$ of the stars on
-silicon, primarily due to our masking of saturated stars and their
-nearby pixels.
 
@@
 the entire and close samples of stars on silicon.  Each clump
-signifies a different star cluster. The largest overdensity in the top
-figure is composed mainly of field star contaminants. It has two
+signifies a different star cluster. The large overdensity in the top
+panel is composed mainly of field star contaminants. It has two
 subcomponents, due to the two different directions in the Galaxy being

### 2019-07-28 drivers/paper_get_LC_and_target_star_stats.py
minor

@@ -6,12 +6,13 @@ analyze stats of both cdips target stars, and cdips light curves.
 * how many are single-source claims?
 * how many are multi-source claims?
 
-python paper_get_LC_and_target_star_stats.py &> logs/get_LC_and_target_star_stats.log &
+python -u paper_get_LC_and_target_star_stats.py &> logs/get_LC_and_target_star_stats.log &
 """
 
 import pandas as pd, numpy as np
 from collections import Counter
 from cdips.utils import collect_cdips_lightcurves as ccl
+import os
 
 def main():
     print('#'*42)
@@ -21,18 +22,21 @@ def main():
     print('#'*42)
     paper_get_CDIPS_star_stats()
 
-def paper_get_CDIPS_LC_stats(sector=None):
+def paper_get_CDIPS_LC_stats(sector=None, ndet_cut=300, ncluster_cut=200):
 
     statdir = (
         '/nfs/phtess2/ar0/TESS/PROJ/lbouma/cdips/'+
         'results/cdips_lc_stats/sector-{}'.format(sector)
     )
 
-    statfile = os.path.join(statsdir, 'supplemented_cdips_lc_statistics.txt')
+    statfile = os.path.join(statdir, 'supplemented_cdips_lc_statistics.txt')
 
-    df = pd.read_csv(statfile)
+    df = pd.read_csv(statfile, sep=';')
 
-    get_CDIPS_stats(df)
+    df = df[df['ndet_rm2'] > ndet_cut]
+
+    print('Sector {}'.format(sector))
+    get_CDIPS_stats(df, ncluster_cut=ncluster_cut)
 
 
 def paper_get_CDIPS_star_stats():
@@ -42,7 +46,7 @@ def paper_get_CDIPS_star_stats():
     get_CDIPS_stats(df)
 
 
-def get_CDIPS_stats(df):
+def get_CDIPS_stats(df, ncluster_cut=100):
     """
     df (pd.DataFrame): dataframe with stats information from either the
     (publication-level) target star catalog (ccl.get_cdips_catalog), or the
@@ -53,7 +57,7 @@ def get_CDIPS_stats(df):
 
     ucname = np.array(df['unique_cluster_name'])
     cname_cnt = Counter(ucname)
-    cname_mostcommon = cname_cnt.most_common(n=30)
+    cname_mostcommon = cname_cnt.most_common(n=ncluster_cut)
 
     refs = np.array(df['reference'])
     cnt = Counter(refs)
[…]

### 2019-07-28 paper_I/ms.tex
add a few words

@@
 \newcommand{\numberclusterpcs}{29\ }  % 2019/06/28 unanimous gold
-\newcommand{\sVInumberlcs}{67{,}601\ }  % 2019/06/20 not allnan
-\newcommand{\sVIInumberlcs}{91{,}736\ }  % 2019/06/20 not allnan
-\newcommand{\numberlcs}{159{,}337\ } % 2019/06/20 sum
+\newcommand{\sVInumberlcs}{67{,}612\ }  % 2019/07/27 not allnan
+\newcommand{\sVIInumberlcs}{91{,}731\ }  % 2019/07/27 not allnan
+\newcommand{\numberlcs}{159{,}343\ } % 2019/06/20 sum
 \newcommand{\numberclusters}{596\ } % 2019/07/01 paper_plot_all_figures.py
@@
 
+Despite our goal being completeness, there may be clusters with
+missing members, if those members were not included in any of our
+membership catalogs.
+A good example is the Orion Nebula (M42; NGC 1976).
+While it was observed by TESS in Sector~6, our reduction process resulted in
+only 85 light curves being made for its members.
+It is known to have far more (CITE OLD PAPER).
+This is an issue partially with the membership catalogs, and perhaps
+partially with our selection
+criteria from them.
+For instance,
+\cite{cantat-gaudin_gaua_2018} failed to detect it.
+\citet{Kharchenko_et_al_2013} lists 42 ``1$\sigma$'' members within
+the angular radius of the cluster.
+(CITE) DIAS lists 221 objects with prob gt 50, and finite i mags.
+A number of the Dias objects maybe were lost in cross-match?! Or else
+maybe the stars were dropped or flagged as bad photometry b/c of the
+high background?
+
 \paragraph{Sector 7}

### 2019-08-03 drivers/table_of_most_common_clusters.py
add tables of common clusters

@@ -11,7 +11,8 @@ where comment is like "flag,Type,n_Type,SType" from Kharchenko.
 unique name. More light curves in these cluisters may exist in the dataset, but
 as unlabelled neighbor stars.
 
-
+To make the latex header tables and associated csv files:
+$ python table_of_most_common_clusters.py
 """
 
 import os
@@ -54,9 +55,6 @@ def get_k13_index():
             k13_index[c] = k13_index[c].str.decode('utf-8')
 
     return k13_index
-
-
-
 
 def make_table():
 
@@ -120,20 +118,26 @@ def make_table():
     # sector 6                         sector 7
     # unique name | N_LCs | comment    unique name | N_LCs | comment
     #
-    # where comment is like "flag,Type,n_Type,SType" from Kharchenko.
+    # where comment (or description) is like "flag,Type,n_Type,SType" from
+    # Kharchenko.
     tab_s6 = pd.DataFrame(allentries[0], columns=['name','n_lc','description'])
     tab_s7 = pd.DataFrame(allentries[1], columns=['name','n_lc','description'])
 
     outfull_s6 = '../paper_I/table_s6_most_common_clusters_full.csv'
     outfull_s7 = '../paper_I/table_s7_most_common_clusters_full.csv'
-    outtab_s6 = '../paper_I/table_s6_most_common_clusters.tex'
-    outtab_s7 = '../paper_I/table_s7_most_common_clusters.tex'
+    outtex_s6 = '../paper_I/table_s6_most_common_clusters.tex'
+    outtex_s7 = '../paper_I/table_s7_most_common_clusters.tex'
+    outpaths = [outfull_s6, outfull_s7, outtex_s6, outfull_s7]
 
     tab_s6.to_csv(outfull_s6, index=False)
     tab_s7.to_csv(outfull_s7, index=False)
 
+    tab_s6.head(n=20).to_latex(outtex_s6, index=False)
+    tab_s7.head(n=20).to_latex(outtex_s7, index=False)
 
-    import IPython; IPython.embed()
+    for p in outpaths:
+        print('made {}'.format(p))
+
 
 if __name__ == "__main__":
     make_table()

### 2019-08-03 drivers/table_of_most_common_clusters.py
clean up common cluster table

@@ -120,8 +120,8 @@ def make_table():
     #
     # where comment (or description) is like "flag,Type,n_Type,SType" from
     # Kharchenko.
-    tab_s6 = pd.DataFrame(allentries[0], columns=['name','n_lc','description'])
-    tab_s7 = pd.DataFrame(allentries[1], columns=['name','n_lc','description'])
+    tab_s6 = pd.DataFrame(allentries[0], columns=['Name','$N_{\\mathrm{lc}}$','Description'])
+    tab_s7 = pd.DataFrame(allentries[1], columns=['Name','$N_{\\mathrm{lc}}$','Description'])
 
     outfull_s6 = '../paper_I/table_s6_most_common_clusters_full.csv'
     outfull_s7 = '../paper_I/table_s7_most_common_clusters_full.csv'
@@ -132,11 +132,27 @@ def make_table():
     tab_s6.to_csv(outfull_s6, index=False)
     tab_s7.to_csv(outfull_s7, index=False)
 
-    tab_s6.head(n=20).to_latex(outtex_s6, index=False)
-    tab_s7.head(n=20).to_latex(outtex_s7, index=False)
+    tab_s6.head(n=20).to_latex(outtex_s6, index=False, column_format='lll')
+    tab_s7.head(n=20).to_latex(outtex_s7, index=False, column_format='lll')
 
     for p in outpaths:
         print('made {}'.format(p))
+
+    for p in [outtex_s6, outtex_s7]:
+        print('{}: cutting head and bottom off tabular tables...'.format(p))
+        with open(p, 'r') as f:
+            lines = f.readlines()
+
+        startline = [ix for ix, l in enumerate(lines) if
+                     l.startswith(r'\midrule')][0]
+        endline = [ix for ix, l in enumerate(lines) if
+                   l.startswith(r'\bottomrule')][0]
+
+        sel_lines = lines[startline+1: endline]
+
+        with open(p, 'w') as f:
+            f.writelines(sel_lines)
+
 
 
 if __name__ == "__main__":

### 2019-08-03 paper_I/ms.tex
update paper

--- 2019-07-27 paper_I/ms.tex
@@
 
-The clusters with the largest claimed numbers of sources are the
-Platais~6, Platais~5, and Mamajek~3 moving groups, all from
-\citet{dias_proper_2014}, composing about 7000, 7000, and 3500 sources
-respectively. These membership claims should be regarded with some
+Table~\ref{tbl:s6_lcs} shows the clusters with the largest claimed 
+numbers of sources. The top 4 are all moving groups or stellar
+associations from
+\citet{dias_proper_2014}: Platais~5, Platais~6, Mamajek~, and Collinder~70.
+These membership claims should be regarded with serious
 skepticism on a source-by-source basis.  For Platais~6,
@@
 (1$\sigma$) to exist within the angular radius of the cluster.
-Mamajek~3 (= 32$\,$Ori) has only about 50 confirmed members
+Mamajek~3 (= 32$\,$Ori) similarly has only about 50 confirmed members
 \citep{bell_32ori_2017}.
-
-We remind the reader that our goal in creating our target catalog was
-completeness, rather than fidelity. The \citet{dias_proper_2014} stars
-in particular were included if they were listed with membership
-probability exceeding 50\%.  To create cleaner sub-samples, we advise
-use of the \texttt{CDEXTCAT} header keyword, which can be used to
-merge against the original source catalog to obtain the membership
-probabilities claimed by the original catalog.
 
@@
 
+\section{Discussion}
+\label{sec: discussion}
+
+We remind the reader that our goal in creating our target catalog was
+completeness, rather than fidelity. The \citet{dias_proper_2014} stars
+in particular were included if they were listed with membership
+probability exceeding 50\%.  To create cleaner sub-samples, we advise
+use of the \texttt{CDEXTCAT} header keyword, which can be used to
+merge against the original source catalog to obtain the membership
+probabilities claimed by the original catalog.
+
+Despite our goal of completeness, some clusters may still be missing
+members~--~the census of nearby coeval stellar populations is still
+very much in flux ({\it e.g.}, \citealt{sim_open_2019};
+\citealt{kounkel_untangling_2019}).  One particular area for concern in
+the present work is sub-clusters of broader star-forming complexes,
+for instance the Orion Nebula (M42; NGC 1976).  While it was observed
+by TESS in Sector~6, searching our light curves for stars within 40
+arcminutes, and 100 parsecs of the Orion Nebula's center yielded only
+180 light curves, with 85 labelled members.  The Orion Nebula has
+thousands of known members \citep{jones_proper_1988}.  However, due to
+a combination of the spatially distributed nature of the broader
+complex, as well as differential extinction, the automated methods of
+the \citet{Kharchenko_et_al_2013} and \citet{dias_proper_2014}
+assigned the Orion Nebula only 44 and 326 members, respectively.
+\citet{cantat-gaudin_gaia_2018} explicitly excluded young star-forming
+regions from their search, since the underlying assumption of their
+clustering method (uniformity in the field star distribution) breaks
+down in highly clustered star-forming regions.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+\begin{deluxetable}{lll}
+	\tablecaption{Counts of light curves per cluster in Sector 6, sorted
+		in descending order.  \label{tbl:s6_lcs}}
+	\tablenum{2}
+
+	\tablehead{
+		\colhead{\hspace{.9cm}Name}\hspace{.9cm}
+		& \colhead{\hspace{.9cm}$N_{\rm lc}$}\hspace{.9cm}
+		& \colhead{\hspace{.9cm}Description}\hspace{.2cm}
+	}
+
+	\startdata
+	\input{table_s6_most_common_clusters.tex}
+	\enddata
+
+	\tablecomments{
+		Table~\ref{tbl:s6_lcs} is published in its entirety in a machine-readable format.
+		A portion is shown here for guidance regarding its form and content.
+		Names are matched against \citet{Kharchenko_et_al_2013} as
+		described in Appendix~\ref{appendix:uniquenames}, and $N_{\rm lc}$
+		is the number of light curves associated with the cluster from this
+		data release.
+		The description column matches \citet{Kharchenko_et_al_2013},
+		and is in the format ``\texttt{a},\texttt{b},\texttt{c},\texttt{d}''.
+		Meanings of displayed symbols are as follows.
+		\texttt{a}:
+		``='' = cluster parameters were determined,
+		``\&'' = duplicated/coincides with other cluster;
+		\texttt{b}:
+		``blank'' = open cluster,
+		``a'' =	association,
+		``m'' =	moving group,
+		``n'' =	nebulosity;
+		\texttt{c}:
+		``o'' = object,
+		``c'' = candidate;
+		\texttt{d}:
+		``ass'' =	stellar association,
+		``var'' =	clusters with variable extinction.
+	}
+
+	\vspace{-1cm}
+\end{deluxetable}
+
+\begin{deluxetable}{lll}
+	\tablecaption{Counts of light curves per cluster in Sector 7, sorted
+		in descending order.  \label{tbl:s7_lcs}}
+	\tablenum{3}
+
+	\tablehead{
+		\colhead{\hspace{.9cm}Name}\hspace{.9cm}
+		& \colhead{\hspace{.9cm}$N_{\rm lc}$}\hspace{.9cm}
+		& \colhead{\hspace{.9cm}Description}\hspace{.2cm}
+	}
+
+	\startdata
+	\input{table_s7_most_common_clusters.tex}
+	\enddata
+
+	\tablecomments{
+		Table~\ref{tbl:s7_lcs} is published in its entirety in a machine-readable format.
+		A portion is shown here for guidance regarding its form and content.
+		Format is same as Table~\ref{tbl:s6_lcs}.
+	}
+
+	\vspace{-1cm}
+\end{deluxetable}
+
 \clearpage

### 2019-08-03 paper_I/ms.tex
update paper s7 provenace

@@
 In Sector 6, \sVInumberlcs light curves of candidate cluster stars
-were made. The provenance of the claimed cluster origin of these
-sources is \citet{dias_proper_2014} for 59\% of the sources;
-\citet{zari_3d_2018} for 16\% of sources from their upper
-main-sequence table and 1\% of sources from their PMS table;
-\citet{Kharchenko_et_al_2013} for 8\% of sources,
-\citet{cantat-gaudin_gaia_2018} for 6\% of sources, and more than two
+were made. The provenance of the target star for these
+sources is \citet{dias_proper_2014} for 40\% of the sources;
+\citet{zari_3d_2018} for 11\% of sources from their upper
+main-sequence table and 7\% of sources from their PMS table;
+\citet{Kharchenko_et_al_2013} for 18\% of sources,
+\citet{cantat-gaudin_gaia_2018} for 14\% of sources, and more than two
 catalogs for the remaining 10\% of sources.
 
-Table~\ref{tbl:s6_lcs} shows the clusters with the largest claimed 
-numbers of sources. The top 4 are all moving groups or stellar
-associations from
-\citet{dias_proper_2014}: Platais~5, Platais~6, Mamajek~, and Collinder~70.
-These membership claims should be regarded with serious
-skepticism on a source-by-source basis.  For Platais~6,
-\citet{Kharchenko_et_al_2013} claimed only about 400 probable members
-(1$\sigma$) to exist within the angular radius of the cluster.
-Mamajek~3 (= 32$\,$Ori) similarly has only about 50 confirmed members
-\citep{bell_32ori_2017}.
+Table~\ref{tbl:s6_lcs} shows the clusters in Sector 6 with the largest
+numbers of light curves. The top four clusters are all moving groups
+or stellar associations from \citet{dias_proper_2014}: Platais~5,
+Platais~6, Mamajek~3, and Collinder~70.  These membership claims
+should be regarded with serious skepticism on a source-by-source
+basis.  For Platais~6, \citet{Kharchenko_et_al_2013} claimed only
+about 400 probable members (1$\sigma$) to exist within the angular
+radius of the cluster.  Mamajek~3 (= 32$\,$Ori) similarly has only
+about 50 confirmed members \citep{bell_32ori_2017}.
 
@@
 were made.  The provenance of the claimed cluster origin of these
-sources is  ... LGBTODO
-
-The clusters with the largest claimed numbers of sources are ...
-LGBTODO
+sources is \citet{dias_proper_2014} for 28\% of the sources;
+\citet{Kharchenko_et_al_2013} for 24\% of sources;
+\citet{zari_3d_2018} for 8\% of sources from their upper main-sequence
+table and 3\% of sources from their PMS table;
+\citet{cantat-gaudin_gaia_2018} for 22\% of sources, and more than two
+catalogs for the remaining 15\% of sources.
+
+Table~\ref{tbl:s7_lcs} shows the clusters from Sector 7 with the
+largest number of light curves.  Many rich open clusters, including
+NGC 2437, 2477, 2546, and 2451 are in the field.  The cluster listed
+with the most light curves is the Collinder 173 association, chiefly
+due to the \citet{dias_proper_2014} memberships.
+\citet{Kharchenko_et_al_2013} note Collinder 173 as being coincident
+with the Vela OB2 association, and hence they flag it as a
+``duplicate''.  Along with Sco-Cen and the Orion star forming complex,
+the Vela OB2 association is one of the largest young associations
+within 500~pc \citep{zari_3d_2018}.  Crucially though,
+\citet{cantat-gaudin_velaOB2_2019} recently studied the region using
+Gaia DR2 astrometry, and found that they could subdivide the complex
+into seven distinct stellar populations, with a total of $\sim$11,000
+members.  None of these populations map one-to-one to the classic
+labels of ``Collinder 173'' or ``Vela OB2''~--~so the
+\citet{cantat-gaudin_velaOB2_2019} catalog is likely a more reliable
+source of information for this particular region of the sky.
 

### 2019-08-03 paper_I/ms.tex
minor

@@
 Platais~6, Mamajek~3, and Collinder~70.  These membership claims
-should be regarded with serious skepticism on a source-by-source
-basis.  For Platais~6, \citet{Kharchenko_et_al_2013} claimed only
-about 400 probable members (1$\sigma$) to exist within the angular
-radius of the cluster.  Mamajek~3 (= 32$\,$Ori) similarly has only
-about 50 confirmed members \citep{bell_32ori_2017}.
+should be regarded with serious skepticism.  For Platais~6,
+\citet{Kharchenko_et_al_2013} claimed only about 400 probable members
+(1$\sigma$) to exist within the angular radius of the cluster.
+Mamajek~3 (= 32$\,$Ori) similarly has only about 50 confirmed members
+\citep{bell_32ori_2017}.
+Some rich open clusters in the Sector 6 field with many light curves,
+and more reliable membership lists include Trumpler~5,
+Collinder~69 (the $\lambda$ Orionis cluster), and NGC~2287.
 

### 2019-08-03 drivers/paper_get_LC_and_target_star_stats.py
minor

@@ -104,6 +104,8 @@ def get_CDIPS_stats(df, ncluster_cut=100, find_cluster_prox=False):
     cnt = Counter(refs)
     mostcommon = cnt.most_common(n=20)
 
+    fracmostcommon = [(k, np.round(v/len(df), 3)) for k,v in mostcommon]
+
     ismult = np.array([',' in r for r in refs])
     issing = ~ismult
 
@@ -120,6 +122,9 @@ def get_CDIPS_stats(df, ncluster_cut=100, find_cluster_prox=False):
     Top 20 most common references are:
     {mostcommon}
 
+    By fraction, top 20 most common references are:
+    {fracmostcommon}
+
     There are {n_single} single-source claims.
 
     There are {n_mult} claims from multiple sources.
@@ -128,6 +133,7 @@ def get_CDIPS_stats(df, ncluster_cut=100, find_cluster_prox=False):
         ncluster_cut=ncluster_cut,
         cname_mostcommon=repr(cname_mostcommon),
         mostcommon=repr(mostcommon),
+        fracmostcommon=repr(fracmostcommon),
         n_single=n_single,
         n_mult=n_mult
     )

### 2019-08-06 paper_I/ms.tex
update paper

@@
 
+\begin{figure*}[!t]
+	\begin{center}
+		\leavevmode
+		\includegraphics[width=1\textwidth]{quilt_s6_s7.pdf}
+	\end{center}
+	\vspace{-0.8cm}
+	\caption{
+		Phased light curves for a few objects of interest.
+		{\it Top row, left to right}:
+		TOI~496, in NGC 2548;
+		TOI~625;
+		an eccentric EB, masquerading as a planet.
+		{\it Middle row, left to right}:
+		A detached EB in a 80~Myr old cluster;
+		V684 Mon (a 10 Myr old detached EB);
+		a semi-detached EB in NGC 2548.
+		{\it Bottom row, left to right}:
+		Spotted rotator in NGC 2184;
+		Pulsator or perhaps EB, flagged by \citet{zari_3d_2018} as a pre-MS star;
+		Quasi-periodic pulsator, also with a pre-MS host.
+		Gaia source identifiers are given in a footnote.
+	\label{fig:quilt}
+	}
+\end{figure*}
+
 \subsection{Light Curve Statistics}
@@
 
-\begin{figure}[!t]
-	\gridline{\fig{tls_sde_vs_period_scatter.pdf}{0.45\textwidth}{}}
-	\vspace{-0.8cm}
-	\caption{
-    Transiting planet search periodogram summary.
-    Each point represents the TLS periodogram peak signal detection
-    efficiency (SDE) and corresponding period from one light curve.
-    Significance thresholds (orange lines) are empirically defined for
-    the transiting planet search described in
-    \S~\ref{subsec:identifying_variability}.  
-    {\it Top.} Sector 6.  {\it Bottom.} Sector 7.
-	}
-	\label{fig:tlsresults}
-\end{figure}
-
-Below, we provide a few examples of how one might go about identifying
-pulsating stars, strong stellar rotators, eclipsing binaries, and
-transiting planets in the light curves.
+A detailed search for transiting planets will be the subject of future
+work.
+The light curves provide opportunities for studying many other types of
+variables, including
+pulsating stars, rotators, and eclipsing binaries.
+A few hand-picked examples are shown in Figure~\ref{fig:quilt}.
+The soure identifiers are in a footnote\footnote{
+	Top-left to bottom-right:
+	3064530810048196352, 
+	3080104185367102592, 
+	3027361888196408832,
+	3125738423345810048,
+	3326715714242517248,
+	3064487241899832832,
+	3024952755135530496,
+	2949587413510194688, 
+	5274902193830445312 
+}.
 
@@
 \texttt{348eea7}.}.
-
-%FIXME
-%FIXME
-%FIXME
-%FIXME
 

### 2019-08-06 paper_I/collect_figures.sh

@@ -46,8 +46,9 @@ cp ${fdir}raw_light_curve_systematics_sec6cam1ccd2.pdf \
 cp ${fdir}tls_sde_vs_period_scatter.pdf \
    ${pdir}tls_sde_vs_period_scatter.pdf
 
-# quilt of PCs
+# quilts
 cp ${fdir}quilt_PCs.pdf ${pdir}quilt_PCs.pdf
+cp ${fdir}quilt_s6_s7.pdf ${pdir}quilt_s6_s7.pdf
 
 # time evolution of LS peak period
 cp ${fdir}LS_period_vs_color_and_age.pdf ${pdir}LS_period_vs_color_and_age.pdf

### 2019-08-06 paper_I/ms.tex
updated paper
it's beginning to look better (!)

--- 2019-08-03 paper_I/ms.tex
@@
 \citep{meibom_robust_2005,milliman_wiyn_2014,price-whelan_binary_2018}.
-The detection of eclipsing binaries can also lead to the precise
+The detection of eclipsing binaries (EBs) can also lead to the precise
 determination of the absolute dimensions of the stars and stringent
@@
 
-\begin{figure}[!t]
+\begin{figure*}[!t]
 	\begin{center}
 		\leavevmode
-		\includegraphics[width=0.48\textwidth]{target_star_positions.png}
+		\includegraphics[width=0.9\textwidth]{target_star_positions.png}
 		%\gridline{\fig{target_star_cumulative_counts.pdf}{0.41\textwidth}{}}
@@
 	\caption{
-    Target star positions (blue) and predicted TESS observing
+    Target star positions (blue) and nominal TESS observing
     footprint (gray).  Target stars are either candidate members of
@@
 		%\includegraphics[width=0.45\textwidth]{target_star_cumulative_counts.png}
-		\gridline{\fig{target_star_cumulative_counts.pdf}{0.41\textwidth}{}}
+		\gridline{\fig{target_star_cumulative_counts.pdf}{0.43\textwidth}{}}
 		\vspace{-0.8cm}
-		\gridline{\fig{target_star_hist_logt.pdf}{0.41\textwidth}{}}
+		\gridline{\fig{target_star_hist_logt.pdf}{0.43\textwidth}{}}
 		\vspace{-0.8cm}
-		\gridline{\fig{target_star_reference_pie_chart.pdf}{0.41\textwidth}{}}
+		\gridline{\fig{target_star_reference_pie_chart.pdf}{0.43\textwidth}{}}
 	\end{center}
@@
 \begin{figure*}[!t]
-	\gridline{\fig{mwscmatchstats.pdf}{0.75\textwidth}{}}
-	\vspace{-0.8cm}
-	\gridline{\fig{dias14matchstats.pdf}{0.75\textwidth}{}}
+	\gridline{\fig{mwscmatchstats.pdf}{0.83\textwidth}{}}
+	\vspace{-1.1cm}
+	\gridline{\fig{dias14matchstats.pdf}{0.83\textwidth}{}}
 	\vspace{-0.8cm}
@@
 
-The resulting CDIPS target star list is given in Table~N.
+%FIXME: make table
+The resulting CDIPS target star list is given in Table~\ref{tbl:cdips_targets}.
 The cumulative distribution of target star brightnesses, as well as a
@@
 		\leavevmode
-		\includegraphics[width=0.3\textwidth]{pipelineoverview.pdf}
+		\includegraphics[width=0.25\textwidth]{pipelineoverview.pdf}
 	\end{center}
@@
     Details are given in \S~\ref{sec:method}.
-    %TODO: add latex section numbers!
-    %TODO: do FORCED aperture photomery on differenced images
-    %TODO: improve text generally
 	\label{fig:pipeline}
@@
         \leavevmode
-        \includegraphics[width=0.95\textwidth]{stages_of_image_processing_good.png}
+        \includegraphics[width=0.93\textwidth]{stages_of_image_processing_good.png}
     \end{center}
@@
         \leavevmode
-        \includegraphics[width=0.95\textwidth]{stages_of_image_processing_bad.png}
+        \includegraphics[width=0.93\textwidth]{stages_of_image_processing_bad.png}
     \end{center}
@@
 \begin{figure}[!t]
-	\gridline{\fig{astromresidual_hist.pdf}{0.5\textwidth}{}}
+	\gridline{\fig{astromresidual_hist.pdf}{0.45\textwidth}{}}
 	\vspace{-0.8cm}
@@
 pixels, and 2.25 pixels.  These sizes were chosen to roughly span the
-range of optimal aperture sizes for stars in our sample, as calcuated
+range of optimal aperture sizes for stars in our sample, as calculated
 from the pre-flight \citet{Sullivan_et_al_2015} noise model.  Finally,
@@
 number of components\footnote{See for example
-\url{https://scikit-learn.org/stable/auto_examples/decomposition/plot_pca_vs_fa_model_selection.html}}.
+\url{https://scikit-learn.org/stable/auto_examples/decomposition/plot_pca_vs_fa_model_selection.html}
+ (2019/08/06).}.
 However, the factor analysis typically maximized the cross-validation
@@
 	\end{center}
-	\vspace{-0.5cm}
+	\vspace{-0.7cm}
 	\caption{
@@
 	\gridline{\fig{hrd_scat_all_CDIPS_LCs.pdf}{0.45\textwidth}{}}
-	\vspace{-0.8cm}
+	\vspace{-1.1cm}
 	\gridline{\fig{hrd_scat_close_subset.pdf}{0.45\textwidth}{}}
-	\vspace{-0.8cm}
+	\vspace{-0.9cm}
 	\caption{
@@
 	\gridline{\fig{pm_scat_all_CDIPS_LCs.pdf}{0.45\textwidth}{}}
-	\vspace{-0.8cm}
+	\vspace{-0.9cm}
 	\gridline{\fig{pm_scat_close_subset.pdf}{0.45\textwidth}{}}
-	\vspace{-0.8cm}
+	\vspace{-0.9cm}
 	\caption{
@@
 		\leavevmode
-		\includegraphics[width=0.97\textwidth]{IRM-PCA-TFA_rms_vs_mag.pdf}
+		\includegraphics[width=0.9\textwidth]{IRM-PCA-TFA_rms_vs_mag.pdf}
 	\end{center}
@@
 		\leavevmode
-		\includegraphics[width=0.97\textwidth]{avg_acf.pdf}
+		\includegraphics[width=0.85\textwidth]{avg_acf.pdf}
 	\end{center}
-	\vspace{-0.5cm}
+	\vspace{-0.7cm}
   \caption{
@@
 
-\subsection{Light Curve Statistics}
+\begin{figure*}[!t]
+	\begin{center}
+		\leavevmode
+		\includegraphics[width=1\textwidth]{quilt_s6_s7.pdf}
+	\end{center}
+	\vspace{-0.8cm}
+	\caption{
+		Phased light curves for a few objects of interest.
+		{\it Top row, left to right}:
+		TOI~496 in Messier 48;
+		TOI~625 orbiting a late A dwarf;
+		and an eccentric EB in Bochum~5.
+		{\it Middle row, left to right}:
+		A detached EB in a 80~Myr old cluster;
+		V684 Mon (a 10 Myr old detached EB);
+		and a semi-detached EB in NGC 2548.
+		{\it Bottom row, left to right}:
+		Spotted rotator in NGC 2184;
+		a pulsator or perhaps EB flagged by \citet{zari_3d_2018} as a pre-MS 
+		star;
+		and a quasi-periodic pulsator, also with a pre-MS host.
+		Gaia source identifiers are given in the text.
+	\label{fig:quilt}
+	}
+\end{figure*}
+
+\subsection{Light curve statistics}
 \label{subsec:lcstatistics}
@@
 $180^\circ$, and the empirical coefficients were found to be $a_0 =
-18.9733$, $a_1=8.833$, $a_2=4.007$, and $a_3=0.805$.  This fit was
+18.9733$, $a_1=8.833$, $a_2=4.007$, and $a_3=0.805$.  The fit was
 cautioned to be {\it very approximate}.  It is sensitive to the
@@
 
-\subsection{A Few Objects of Interest}
+\subsection{Exploring the variability}
 \label{subsec:identifying_variability}
 
-\begin{figure}[!t]
-	\gridline{\fig{tls_sde_vs_period_scatter.pdf}{0.45\textwidth}{}}
-	\vspace{-0.8cm}
-	\caption{
-    Transiting planet search periodogram summary.
-    Each point represents the TLS periodogram peak signal detection
-    efficiency (SDE) and corresponding period from one light curve.
-    Significance thresholds (orange lines) are empirically defined for
-    the transiting planet search described in
-    \S~\ref{subsec:identifying_variability}.  
-    {\it Top.} Sector 6.  {\it Bottom.} Sector 7.
-	}
-	\label{fig:tlsresults}
-\end{figure}
-
-Below, we provide a few examples of how one might go about identifying
-pulsating stars, strong stellar rotators, eclipsing binaries, and
-transiting planets in the light curves.
-
-\paragraph{Sinusoidal signals}
-For pulsating stars and strong stellar rotators, the Lomb-Scargle
-periodogram (CITE) is a tried-and-true discovery method.
-
-We measured rotation periods for stars in X, Y clean cluster.
-
-A figure is given here.
-
-To identify an initial set of transiting planets, strong
-stellar rotators, and eclipsing binaries, we performed a few steps of
-post-processing on the light curves.  This processing was done
-independently of the data release, since it was quite specific to our
-own scientific interests.  The code used to do this additional
-processing is also available
-online\footnote{\url{github.com/lgbouma/cdips}, commit
-\texttt{348eea7}.}.
-
-%FIXME
-%FIXME
-%FIXME
-%FIXME
-
-\section{Discussion}
-\label{sec: discussion}
+The light curves provide an opportunity to study many types of
+variables, including pulsating stars, rotators, eclipsing binaries,
+and transiting planets.
+A few hand-picked examples are shown in Figure~\ref{fig:quilt}.
+The sources\footnote{
+	Top-left to bottom-right:
+	3064530810048196352, 
+	3080104185367102592, 
+	3027361888196408832,
+	3125738423345810048,
+	3326715714242517248,
+	3064487241899832832,
+	3024952755135530496,
+	2949587413510194688, 
+	5274902193830445312 
+} were identified by calculating Lomb-Scargle and transit-least
+squares periodograms for a subset of the light curves, and inspecting
+the peaks with the greatest power
+\citep{lomb_1976,scargle_studies_1982,kovacs_box-fitting_2002,vanderplas_periodograms_2015,hippke_TLS_2019}.
+We calculated the periodograms using
+\texttt{astrobase}.
+Our search was extremely cursory~--~a detailed search for transiting
+exoplanets will be the subject of future work.
+To make the figure, we used the ``PCA2'' light curve for each
+star, for simplicity's sake.
+To remove outliers, we omitted
+data points within 6 hours of the beginning or end of each orbit.
+No additional detrending was performed.
+
+The top row of Figure~\ref{fig:quilt} shows two TESS objects of
+interest, and an eccentric eclipsing binary.  TOI~496 is a member of M~48 
+(NGC~2548,
+\citealt{gaia_collaboration_gaia_2018,cantat-gaudin_gaia_2018}), a
+$\sim$500 Myr old open cluster \citep{Kharchenko_et_al_2013}.  The
+phase variations suggest that it is an eclipsing binary.  TOI~625 is a
+potential hot Jupiter orbiting an upper main sequence star, and was
+included as a CDIPS target through the \citet{zari_3d_2018}
+catalog.  The eccentric EB was claimed by \citet{dias_proper_2014} to
+be a member of the $\sim$50 Myr Bochum~5 cluster.  This EB is also of
+note because its TFA light curve heavily whitens the out-of-eclipse
+signal, leaving an eclipse signal would could be mistaken for a planet 
+candidate.  The important
+check for potential users of the light curves is of course to consider
+light curves with different types of detrending, to prevent these types of
+misinterpretations.
+
+The middle row of Figure~\ref{fig:quilt} shows a few more interesting
+eclipsing binaries.  On the left is a detached EB exhibiting large
+out-of-eclipse modulations in a $\sim$80~Myr
+open cluster (``vdBergh 85'', \citealt{Kharchenko_et_al_2013}).
+In the middle we have V684 Mon, a well-known $\sim$10~Myr old
+detached EB in the very young star-forming region NGC 2264.
+Finally on the right, we have a semi-detached EB in Messier~48.
+
+The bottom row of Figure~\ref{fig:quilt} gives a few examples
+of rotators and pulsators.  On the left, a spotted rotator in the
+$\sim$400 Myr NGC~2184 \citep{cantat-gaudin_gaia_2018}.
+In the middle, we have a pulsator, or perhaps EB flagged by
+\citet{zari_3d_2018} as a pre-MS star.
+Finally on the right is a quasi-periodic pulsator, or perhaps rotator,
+also with a pre-MS host.
+
+The overall point is that a great number of systems with known ages
+should be identifiable from the data at their current level of
+preparation.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Discussion \& Conclusion}
+\label{sec:conclusion}
+
+In this study, we first collected an all-sky sample of about one
+million stars brighter than $G_{\rm Rp}$ of 16.  82\%
+of this target star sample are candidate ``cluster'' members, 
+where we use the generic ``cluster'' to refer to 
+open clusters, stellar associations, and moving groups.
+The remaining stars had photometric or astrometric indications of
+their youth, and either reside on the pre-main-sequence or upper main
+sequence.
+
+We then reduced TESS full frame images taken over the course of about
+two months (Sectors 6 and 7; the first fields very close to the
+galactic plane).  We performed difference imaging in order to minimize
+the complications of the crowded background.  Using forced aperture
+photometry, we made light curves for all stars brighter than $G_{\rm
+Rp}$ of 13, and went three magnitudes deeper for our target star
+sample.  This yielded \numberlcs light curves of candidate young stars
+across \numberclusters distinct clusters.
+
+The light curves seem to be limited in precision by photon noise at
+the bright end, and by unresolved background stars at the faint end
+(Figure~\ref{fig:rms_vs_mag}).
+Though the raw light curves show significant red noise, decorrelating
+against a set of template stars led to an ensemble of light curves
+with very nearly gaussian noise properties 
+(Figures~\ref{fig:lc_systematics_dtr} and~\ref{fig:avg_acf}).
+
+Brief exploration of the data revealed pulsating stars, eclipsing
+binaries, and planet candidates (Figure~\ref{fig:quilt}).  A detailed planet 
+search is the
+subject of ongoing work.
+
+A point worth re-emphasizing is that the stars in the
+sample must be understood to be {\it candidate} cluster stars, and the
+possibility of photometric blends is important to rule out in
+subsequent vetting efforts of any variable object.  Careful
+understanding of the cluster itself is also important, as some
+clusters are less certain to exist than others \citep[{\it
+e.g.}, the infra-red clusters identified by][]{froebrich_FSR_2007}.
 
 We remind the reader that our goal in creating our target catalog was
-completeness, rather than fidelity. The \citet{dias_proper_2014} stars
-in particular were included if they were listed with membership
-probability exceeding 50\%.  To create cleaner sub-samples, we advise
-use of the \texttt{CDEXTCAT} header keyword, which can be used to
-merge against the original source catalog to obtain the membership
-probabilities claimed by the original catalog.
+completeness, rather than fidelity.  To create clean sub-samples, we
+advise using the \texttt{CDEXTCAT} header keyword available in the
+FITS files, which can be used to merge against the original source
+catalog to obtain the membership probabilities claimed by the original
+catalog.  Alternatively, simply restricting the targets of interest to
+those with provenance from {\it e.g.}, the Gaia-DR2 data is another
+way to produce a cleaner sample of cluster targets.
 
@@
 members~--~the census of nearby coeval stellar populations is still
-very much in flux ({\it e.g.}, \citealt{sim_open_2019};
-\citealt{kounkel_untangling_2019}).  One particular area for concern in
-the present work is sub-clusters of broader star-forming complexes,
-for instance the Orion Nebula (M42; NGC 1976).  While it was observed
-by TESS in Sector~6, searching our light curves for stars within 40
-arcminutes, and 100 parsecs of the Orion Nebula's center yielded only
-180 light curves, with 85 labelled members.  The Orion Nebula has
-thousands of known members \citep{jones_proper_1988}.  However, due to
-a combination of the spatially distributed nature of the broader
-complex, as well as differential extinction, the automated methods of
-the \citet{Kharchenko_et_al_2013} and \citet{dias_proper_2014}
-assigned the Orion Nebula only 44 and 326 members, respectively.
+very much in flux. For instance, in the preparation of this work,
+\citet{sim_open_2019} identified 209 new open cluster candidates
+within 1~kpc through visual inspection of Gaia-DR2 data.  Similarly,
+\citet{kounkel_untangling_2019} searched for groups near
+the galactic plane within 1~kpc, and along with the known clusters
+found hundreds of new ``strings'' of kinematically associated stars, which
+could be coeval.
+
+Another area in which we may be incomplete is in sub-clusters
+of broader star-forming complexes. One important example is
+the Orion Nebula (M42; NGC 1976).  While it was observed by TESS in
+Sector~6, searching our light curves for stars within 40 arcminutes
+and 100 parsecs of the Orion Nebula's center yielded only 180 light
+curves, with 85 labelled members.  The Orion Nebula has far more known
+members \citep{jones_proper_1988}.  However, due to a combination of
+the spatially distributed nature of the broader complex, as well as
+differential extinction, the automated methods of the
+\citet{Kharchenko_et_al_2013} and \citet{dias_proper_2014} assigned
+the Orion Nebula only 44 and 326 members, respectively.
 \citet{cantat-gaudin_gaia_2018} explicitly excluded young star-forming
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusion}
-\label{sec:conclusion}
-
-%FIXME: paraphrase / improve all the below
-In this study, we first collected an all-sky sample of about one million
-candidate young stars brighter than $G_{\rm Rp}$ of 16.
-82\% of the target star sample resides in a ``cluster'', a generic
-term we adopted for open clusters, stellar associations, and moving
-groups.
-The remaining stars have photometric or astrometric indications of
-their youth, and either reside on the pre-main-sequence or upper
-main sequence.
-
-We then reduced TESS full frame images taken over the course of about
-two months (Sectors 6 and 7; the first fields very close to the galactic
-plane).
-We performed difference imaging in order to minimize the complications
-of the crowded background.
-Using forced aperture photometry, we made light curves for all stars
-brighter than $G_{\rm Rp}$ of 13, and went three magnitudes deeper for
-our target star sample.
-This yielded \numberlcs light curves of candidate young stars across
-\numberclusters distinct clusters.
-
-The light curves seem to be limited in precision by photon noise at
-the bright end, and by unresolved background stars at the faint end.
-Though the raw light curves show significant red noise, decorrelating
-against a set of template stars led to an ensemble of light curves
-with very nearly gaussian noise properties.
-
-An initial search for objects that were photometrically variable
-returned pulsating stars, eclipsing binaries, and planet candidates.
-A detailed planet search is the subject of ongoing work.
-An of the stars in the sample must be understood to be {\it candidate}
-cluster stars, and the possibility of photometric blends 
-is important to rule out in subsequent vetting efforts of any variable
-object.
-
-As a brief exploration of the photometric variability in the dataset,
-we looked at the age-evolution of extremely high-SNR variability,
-which seems to show some evolution in the space of LS peak-period
-versus color (Figure~\ref{fig:ls_peak_vs_time}), but interpreting this
-result will require a more careful exploration.  In searching for
-transiting planets, we found many eclipsing binaries, as well as
-stellar rotation and pulsation signals.
-
-Those who wish to explore the
-time-evolution in these and any other systems are invited to explore
-the data at \stscilink.
+These concerns will likely drive us to expand beyond the current
+sample of target stars in future work.  For the time being though, 
+the light curves exist and are amenable for astrophysical studies.  We
+invite any who wish to explore the time evolution of stellar or
+exoplanetary systems to interact with the data at \stscilink.
 
 \acknowledgements
-L.G.B.\ gladly acknowledges helpful discussions with
-C Huang, M Soares-Furtado, ...
-..., and is
-grateful to the people who have turned TESS from an idea into reality.
-%
-J.N.W.\ thanks ...
+L.G.B.\ acknowledges helpful discussions with 
+T.~Cantat-Gaudin,
+C.~Huang,
+and M.~Soares-Furtado.  The authors are also
+grateful to the many people who have turned TESS from an idea into
+reality.
+%
+Coauthors thank ... %FIXME
+%
+L.G.B. and J.H. acknowledge support by the TESS GI Program, program
+G011103.
 %
@@
 
+\clearpage
+\newpage
+
+\begin{deluxetable}{lll}
+    \tablecaption{CDIPS target stars collected for the present work.  
+    \label{tbl:cdips_targets}}
+    \tablenum{1}
+
+    \tablehead{
+        \colhead{\hspace{.9cm}Name}\hspace{.9cm}
+        & \colhead{\hspace{.9cm}$N_{\rm lc}$}\hspace{.9cm}
+        & \colhead{\hspace{.9cm}Description}\hspace{.2cm}
+    }
+
+    \startdata
+    \input{table_s6_most_common_clusters.tex}
+    \enddata
+
+    \tablecomments{
+        Table~\ref{tbl:cdips_targets} is published in its entirety in a 
+        machine-readable format.
+        A portion is shown here for guidance regarding its form and content.
+    }
+
+    \vspace{-1cm}
+\end{deluxetable}
+
 \begin{deluxetable}{lll}

### 2019-08-06 paper_I/table_cdips_targets.tex
add paper_I/table_cdips_targets.tex

  212898200266481408 &           NGC\_1798 &  CantatGaudin\_2018 &     212898200266481408 &   77.836762 &  47.602184 &   0.804664 &  -0.306808 &  0.079538 &        15.239067 &         16.137050 &         14.300698 &       NGC\_1798 &            NGC\_1798 &                  string\_match &      False &                                                NaN &     9.300 &         NaN \\
  436314118309711616 &         Melotte 20 &           Dias2014 &             694-021435 &   48.197155 &  48.642080 &   6.375356 &  -2.441825 &  0.571211 &        16.312990 &         16.868382 &         15.480946 &     Melotte\_20 &          Melotte\_20 &                  string\_match &      False &                                stellar association &     7.700 &         NaN \\
  441656473511397504 &         Melotte 20 &           Dias2014 &             697-023323 &   50.495676 &  49.275058 &   5.990684 &  -2.017660 &  1.224379 &        15.746423 &         16.410664 &         14.962594 &     Melotte\_20 &          Melotte\_20 &                  string\_match &      False &                                stellar association &     7.700 &         NaN \\
  441814425228579968 &         Melotte 20 &           Dias2014 &             702-024826 &   52.294234 &  50.339258 &   2.636974 &  -6.331214 &  0.612354 &        12.820641 &         13.845972 &         11.826541 &     Melotte\_20 &          Melotte\_20 &                  string\_match &      False &                                stellar association &     7.700 &         NaN \\
  534326573375563008 &      Collinder 463 &           Dias2014 &             809-006294 &   26.385454 &  71.730761 &  -2.234133 &  -0.254922 &  1.339348 &         9.017250 &          9.168780 &          8.777838 &  Collinder\_463 &       Collinder\_463 &                  string\_match &      False &                                                NaN &     8.450 &       0.066 \\
 2003032425991508224 &           ASCC 123 &           Dias2014 &             718-100888 &  339.167259 &  53.587715 &  -3.523145 &  -1.026365 &  0.080821 &        15.595959 &         16.562428 &         14.616383 &       ASCC\_123 &            ASCC\_123 &                  string\_match &      False &                                                NaN &     8.191 &         NaN \\
 2031125085568334848 &  ASCC 105,ASCC 105 &  Dias2014,Dias2014 &  587-091022,587-091016 &  295.309048 &  27.374026 &  -4.300105 &  -6.154838 &  0.134811 &        16.256998 &         17.375406 &         15.173058 &       ASCC\_105 &            ASCC\_105 &                  string\_match &      False &                                                NaN &     7.910 &         NaN \\
 2203397563780025216 &                NaN &      Zari\_2018\_UMS &    2203397563780025216 &  326.249614 &  59.270811 &   1.008246 &  -4.504666 &  2.550234 &        10.899773 &         11.129973 &         10.515632 &            NaN &                 NaN &                           NaN &        NaN &                                                NaN &       NaN &         NaN \\
 2921370238592116224 &            ASCC 33 &           Dias2014 &             327-019044 &  106.101530 & -24.633675 &  -1.830129 &   2.907392 &  0.354147 &        15.540529 &         15.834187 &         15.075217 &        ASCC\_33 &             ASCC\_33 &                  string\_match &      False &                                                NaN &     7.700 &         NaN \\
 2944678923021117824 &                NaN &      Zari\_2018\_PMS &    2944678923021117824 &   94.221472 & -16.524928 &  -4.891108 &   5.187349 &  2.782549 &        17.017532 &         18.707790 &         15.741343 &            NaN &                 NaN &                           NaN &        NaN &                                                NaN &       NaN &         NaN \\
 3061987330417564928 &                NaN &      Zari\_2018\_UMS &    3061987330417564928 &  111.999764 &  -1.654681 & -16.693736 &  11.698526 &  4.483383 &         9.060237 &          9.296353 &          8.706912 &            NaN &                 NaN &                           NaN &        NaN &                                                NaN &       NaN &         NaN \\
 4468588570104961536 &      Collinder 359 &           Dias2014 &             465-071806 &  271.337344 &   2.859011 &  -6.067793 & -11.841687 &  0.222911 &        16.597385 &         17.202381 &         15.849189 &  Collinder\_359 &       Collinder\_359 &                  string\_match &      False &                                                NaN &     7.450 &         NaN \\
 5237684579941961856 &        Melotte\_105 &  CantatGaudin\_2018 &    5237684579941961856 &  170.158607 & -63.573204 &  -6.292756 &   1.531851 &  0.294776 &        14.673732 &         15.888803 &         13.571835 &    Melotte\_105 &         Melotte\_105 &                  string\_match &      False &                                                NaN &     8.375 &         NaN \\
 5517771771107237888 &      Collinder 173 &           Dias2014 &             207-016493 &  119.352691 & -48.671736 &  -4.453542 &   5.411883 &  0.362699 &        15.930569 &         16.325560 &         15.368135 &  Collinder\_173 &       Collinder\_173 &  K13\_index\_table\_string\_match &      False &  K13index: duplicated/coincides with other clus... &       NaN &         NaN \\
 5852217060603554816 &         Platais 11 &           Dias2014 &             124-103457 &  206.927830 & -65.255509 &  -6.012783 &  -1.985373 &  0.119739 &        15.898413 &         16.775694 &         14.973198 &     Platais\_11 &          Platais\_11 &  K13\_index\_table\_string\_match &      False &  K13index: possibly this is a cluster, but para... &       NaN &         NaN \\
 5867315416772454400 &         Platais 10 &           Dias2014 &             149-141566 &  210.294439 & -60.295024 &  -4.568015 &  -0.810601 &  0.368087 &        15.197055 &         15.521402 &         14.684991 &     Platais\_10 &          Platais\_10 &                  string\_match &      False &                                                NaN &     8.340 &         NaN \\
 5867551536877904640 &           NGC\_5381 &  CantatGaudin\_2018 &    5867551536877904640 &  210.348670 & -59.508581 &  -6.412219 &  -3.052808 &  0.364516 &        16.601406 &         17.142036 &         15.814178 &       NGC\_5381 &            NGC\_5381 &                  string\_match &      False &                                                NaN &     8.650 &         NaN \\
 5874572743305780480 &            ASCC\_79 &  CantatGaudin\_2018 &    5874572743305780480 &  226.986254 & -61.942703 &  -3.765162 &  -4.668764 &  0.981699 &        11.241166 &         11.451314 &         10.888834 &        ASCC\_79 &             ASCC\_79 &                  string\_match &      False &                                                NaN &     6.950 &         NaN \\
 5878616953190551168 &           NGC\_5617 &  CantatGaudin\_2018 &    5878616953190551168 &  217.533631 & -60.768071 &  -5.738512 &  -3.337642 &  0.473326 &        15.280778 &         15.662171 &         14.728349 &       NGC\_5617 &            NGC\_5617 &                  string\_match &      False &                                                NaN &     8.250 &         NaN \\
 5997629225643484416 &                NaN &      Zari\_2018\_PMS &    5997629225643484416 &  242.843543 & -37.812758 & -15.520921 & -25.141830 &  6.849145 &        14.319747 &         15.803695 &         13.119771 &            NaN &                 NaN &                           NaN &        NaN &                                                NaN &       NaN &         NaN \\

### 2019-08-06 drivers/table_cdips_targets.py

@@ -1,0 +1,41 @@
+"""
+make TeX table with
+
+source_id;cluster;reference;ext_catalog_name;ra;dec;pmra;pmdec;parallax;phot_g_mean_mag;phot_bp_mean_mag;phot_rp_mean_mag;k13_name_match;unique_cluster_name;how_match;not_in_k13;comment;k13_logt;k13_e_logt
+
+To make the latex data table:
+$ python table_of_cdips_targets.py
+"""
+
+import os
+import pandas as pd, numpy as np
+from numpy import array as nparr
+
+from cdips.utils import collect_cdips_lightcurves as ccl
+
+cdips_df = ccl.get_cdips_pub_catalog(ver=0.3)
+
+N_rows = 20
+sdf = cdips_df.sample(n=N_rows, random_state=42)
+
+outtex = '../paper_I/table_cdips_targets.tex'
+sdf.sort_values(by='source_id').to_latex(outtex, index=False)
+
+print('made {}'.format(outtex))
+
+# trim out the header and footer
+print('{}: cutting head and bottom off tabular tables...'.format(outtex))
+with open(outtex, 'r') as f:
+    lines = f.readlines()
+
+startline = [ix for ix, l in enumerate(lines) if
+             l.startswith(r'\midrule')][0]
+endline = [ix for ix, l in enumerate(lines) if
+           l.startswith(r'\bottomrule')][0]
+
+sel_lines = lines[startline+1: endline]
+
+with open(outtex, 'w') as f:
+    f.writelines(sel_lines)
+
+

### 2019-08-06 drivers/table_of_most_common_clusters.py

@@ -1,5 +1,5 @@
 """
-make table like:
+make TeX table like:
 
     sector 6                       sector 7
 

### 2019-08-07 paper_I/table_cdips_targets.tex
update target table for page fit

@@
-  212898200266481408 &           NGC\_1798 &  CantatGaudin\_2018 &     212898200266481408 &   77.836762 &  47.602184 &   0.804664 &  -0.306808 &  0.079538 &        15.239067 &         16.137050 &         14.300698 &       NGC\_1798 &            NGC\_1798 &                  string\_match &      False &                                                NaN &     9.300 &         NaN \\
-  436314118309711616 &         Melotte 20 &           Dias2014 &             694-021435 &   48.197155 &  48.642080 &   6.375356 &  -2.441825 &  0.571211 &        16.312990 &         16.868382 &         15.480946 &     Melotte\_20 &          Melotte\_20 &                  string\_match &      False &                                stellar association &     7.700 &         NaN \\
-  441656473511397504 &         Melotte 20 &           Dias2014 &             697-023323 &   50.495676 &  49.275058 &   5.990684 &  -2.017660 &  1.224379 &        15.746423 &         16.410664 &         14.962594 &     Melotte\_20 &          Melotte\_20 &                  string\_match &      False &                                stellar association &     7.700 &         NaN \\
-  441814425228579968 &         Melotte 20 &           Dias2014 &             702-024826 &   52.294234 &  50.339258 &   2.636974 &  -6.331214 &  0.612354 &        12.820641 &         13.845972 &         11.826541 &     Melotte\_20 &          Melotte\_20 &                  string\_match &      False &                                stellar association &     7.700 &         NaN \\
-  534326573375563008 &      Collinder 463 &           Dias2014 &             809-006294 &   26.385454 &  71.730761 &  -2.234133 &  -0.254922 &  1.339348 &         9.017250 &          9.168780 &          8.777838 &  Collinder\_463 &       Collinder\_463 &                  string\_match &      False &                                                NaN &     8.450 &       0.066 \\
- 2003032425991508224 &           ASCC 123 &           Dias2014 &             718-100888 &  339.167259 &  53.587715 &  -3.523145 &  -1.026365 &  0.080821 &        15.595959 &         16.562428 &         14.616383 &       ASCC\_123 &            ASCC\_123 &                  string\_match &      False &                                                NaN &     8.191 &         NaN \\
- 2031125085568334848 &  ASCC 105,ASCC 105 &  Dias2014,Dias2014 &  587-091022,587-091016 &  295.309048 &  27.374026 &  -4.300105 &  -6.154838 &  0.134811 &        16.256998 &         17.375406 &         15.173058 &       ASCC\_105 &            ASCC\_105 &                  string\_match &      False &                                                NaN &     7.910 &         NaN \\
- 2203397563780025216 &                NaN &      Zari\_2018\_UMS &    2203397563780025216 &  326.249614 &  59.270811 &   1.008246 &  -4.504666 &  2.550234 &        10.899773 &         11.129973 &         10.515632 &            NaN &                 NaN &                           NaN &        NaN &                                                NaN &       NaN &         NaN \\
- 2921370238592116224 &            ASCC 33 &           Dias2014 &             327-019044 &  106.101530 & -24.633675 &  -1.830129 &   2.907392 &  0.354147 &        15.540529 &         15.834187 &         15.075217 &        ASCC\_33 &             ASCC\_33 &                  string\_match &      False &                                                NaN &     7.700 &         NaN \\
- 2944678923021117824 &                NaN &      Zari\_2018\_PMS &    2944678923021117824 &   94.221472 & -16.524928 &  -4.891108 &   5.187349 &  2.782549 &        17.017532 &         18.707790 &         15.741343 &            NaN &                 NaN &                           NaN &        NaN &                                                NaN &       NaN &         NaN \\
- 3061987330417564928 &                NaN &      Zari\_2018\_UMS &    3061987330417564928 &  111.999764 &  -1.654681 & -16.693736 &  11.698526 &  4.483383 &         9.060237 &          9.296353 &          8.706912 &            NaN &                 NaN &                           NaN &        NaN &                                                NaN &       NaN &         NaN \\
- 4468588570104961536 &      Collinder 359 &           Dias2014 &             465-071806 &  271.337344 &   2.859011 &  -6.067793 & -11.841687 &  0.222911 &        16.597385 &         17.202381 &         15.849189 &  Collinder\_359 &       Collinder\_359 &                  string\_match &      False &                                                NaN &     7.450 &         NaN \\
- 5237684579941961856 &        Melotte\_105 &  CantatGaudin\_2018 &    5237684579941961856 &  170.158607 & -63.573204 &  -6.292756 &   1.531851 &  0.294776 &        14.673732 &         15.888803 &         13.571835 &    Melotte\_105 &         Melotte\_105 &                  string\_match &      False &                                                NaN &     8.375 &         NaN \\
- 5517771771107237888 &      Collinder 173 &           Dias2014 &             207-016493 &  119.352691 & -48.671736 &  -4.453542 &   5.411883 &  0.362699 &        15.930569 &         16.325560 &         15.368135 &  Collinder\_173 &       Collinder\_173 &  K13\_index\_table\_string\_match &      False &  K13index: duplicated/coincides with other clus...
-&       NaN &         NaN \\
- 5852217060603554816 &         Platais 11 &           Dias2014 &             124-103457 &  206.927830 & -65.255509 &  -6.012783 &  -1.985373 &  0.119739 &        15.898413 &         16.775694 &         14.973198 &     Platais\_11 &          Platais\_11 &  K13\_index\_table\_string\_match &      False &  K13index: possibly this is a cluster, but para...
-&       NaN &         NaN \\
- 5867315416772454400 &         Platais 10 &           Dias2014 &             149-141566 &  210.294439 & -60.295024 &  -4.568015 &  -0.810601 &  0.368087 &        15.197055 &         15.521402 &         14.684991 &     Platais\_10 &          Platais\_10 &                  string\_match &      False &                                                NaN &     8.340 &         NaN \\
- 5867551536877904640 &           NGC\_5381 &  CantatGaudin\_2018 &    5867551536877904640 &  210.348670 & -59.508581 &  -6.412219 &  -3.052808 &  0.364516 &        16.601406 &         17.142036 &         15.814178 &       NGC\_5381 &            NGC\_5381 &                  string\_match &      False &                                                NaN &     8.650 &         NaN \\
- 5874572743305780480 &            ASCC\_79 &  CantatGaudin\_2018 &    5874572743305780480 &  226.986254 & -61.942703 &  -3.765162 &  -4.668764 &  0.981699 &        11.241166 &         11.451314 &         10.888834 &        ASCC\_79 &             ASCC\_79 &                  string\_match &      False &                                                NaN &     6.950 &         NaN \\
- 5878616953190551168 &           NGC\_5617 &  CantatGaudin\_2018 &    5878616953190551168 &  217.533631 & -60.768071 &  -5.738512 &  -3.337642 &  0.473326 &        15.280778 &         15.662171 &         14.728349 &       NGC\_5617 &            NGC\_5617 &                  string\_match &      False &                                                NaN &     8.250 &         NaN \\
- 5997629225643484416 &                NaN &      Zari\_2018\_PMS &    5997629225643484416 &  242.843543 & -37.812758 & -15.520921 & -25.141830 &  6.849145 &        14.319747 &         15.803695 &         13.119771 &            NaN &                 NaN &                           NaN &        NaN &                                                NaN &       NaN &         NaN \\
+ 497093746702988672 &  2006361919000756992 &  2048442943413035776 &  5867618572762132864 \\
+          Platais 3 &             ASCC 121 &           Teutsch 35 &           Loden\_1152 \\
+           Dias2014 &             Dias2014 &             Dias2014 &       Kharchenko2013 \\
+         799-012054 &           724-092321 &           630-074483 &            650278772 \\
+            71.4458 &              337.708 &              294.081 &              209.832 \\
+            69.6454 &              54.6607 &              35.8782 &             -59.2883 \\
+            -5.1826 &             -3.48356 &             -3.19716 &              -3.6399 \\
+          -0.478063 &             -1.28297 &             -2.04354 &             -3.93699 \\
+           0.579745 &             0.196117 &             0.324896 &             0.397703 \\
+            15.1735 &              15.4843 &              15.1863 &              16.4277 \\
+            15.5786 &              16.3805 &              15.7505 &               16.991 \\
+            14.6008 &              14.5227 &              14.4853 &              15.6807 \\
+          Platais\_3 &             ASCC\_121 &             ASCC\_103 &           Loden\_1152 \\
+          Platais\_3 &             ASCC\_121 &             ASCC\_103 &           Loden\_1152 \\
+       string\_match &         string\_match &         string\_match &         string\_match \\
+              False &                False &                False &                False \\
+                NaN &                  NaN &                  NaN &                  NaN \\
+                8.8 &                  6.4 &                 8.39 &                8.065 \\
+                NaN &                  NaN &                  NaN &                0.092 \\

### 2019-08-07 drivers/table_cdips_targets.py

@@ -15,11 +15,11 @@ from cdips.utils import collect_cdips_lightcurves as ccl
 
 cdips_df = ccl.get_cdips_pub_catalog(ver=0.3)
 
-N_rows = 20
-sdf = cdips_df.sample(n=N_rows, random_state=42)
+N_rows = 4
+sdf = cdips_df.sample(n=N_rows, random_state=43)
 
 outtex = '../paper_I/table_cdips_targets.tex'
-sdf.sort_values(by='source_id').to_latex(outtex, index=False)
+sdf.sort_values(by='source_id').T.to_latex(outtex, index=False)
 
 print('made {}'.format(outtex))
 

### 2019-08-07 paper_I/ms.tex
[wip] update target table
cdips target table now good

@@
 
-%FIXME: make table
-
 \subsection{Big catalogs: open clusters}
@@
 
-%FIXME: make table
-The resulting CDIPS target star list is given in Table~\ref{tbl:cdips_targets}.
-The cumulative distribution of target star brightnesses, as well as a
-histogram of the ages, is shown in Figure~\ref{fig:cdips_targets}.
-Relative to field stars, our target star sample is young, with a
-typical age of 100$\,$Myr.
+The resulting CDIPS target star list is given in
+Table~\ref{tbl:cdips_targets}.  The cumulative distribution of target
+star brightnesses, as well as a histogram of the ages, is shown in
+Figure~\ref{fig:cdips_targets}.  Relative to field stars, our target
+star sample is young, with a typical age of 100$\,$Myr.
 
@@
 
-\clearpage
-\newpage
-
-\begin{deluxetable}{lll}
-    \tablecaption{CDIPS target stars collected for the present work.  
-    \label{tbl:cdips_targets}}
+\begin{deluxetable*}{lllll}
+
+	\tabletypesize{\footnotesize}
+
+    \tablecaption{
+    	CDIPS target star catalog, \texttt{v0.3}.
+    	\label{tbl:cdips_targets}
+	}
     \tablenum{1}
@@
     \tablehead{
-        \colhead{\hspace{.9cm}Name}\hspace{.9cm}
-        & \colhead{\hspace{.9cm}$N_{\rm lc}$}\hspace{.9cm}
-        & \colhead{\hspace{.9cm}Description}\hspace{.2cm}
+      \colhead{ID} &
+      \colhead{497093746702988672} &
+      \colhead{2006361919000756992} &
+      \colhead{2048442943413035776} & 
+      \colhead{5867618572762132864}
     }
@@
     \startdata
-    \input{table_s6_most_common_clusters.tex}
+    \input{table_cdips_targets.tex}
     \enddata
@@
     \tablecomments{
-        Table~\ref{tbl:cdips_targets} is published in its entirety in a 
+    This table is published in its entirety in a 
     machine-readable format.
-        A portion is shown here for guidance regarding its form and content.
-    }
-
-    \vspace{-1cm}
-\end{deluxetable}
+    A portion of the transposed version
+    is shown here for guidance regarding its form and content.
+    Each row in the machine-readable version (each column in this
+    version) represents a target star.
+    The unique identifier, ``ID'', is the Gaia-DR2 source identifier.
+    The external catalog(s) claiming cluster membership is given 
+    as a comma-separated string in
+    ``Reference'', and the name they assign is given as a comma-separated
+    string in ``Cluster''.
+    ``Ext catalog name'' is the name the external catalog assigns.
+    Positions, proper motions, and the parallax are from Gaia-DR2.
+    The magnitudes in Gaia $G$, $G_{\rm Bp}$, and $G_{\rm Rp}$ bands
+    is given.
+    The naming matching described in Appendix~\ref{appendix:uniquenames}
+    most often succeeds in finding the
+    \citet{Kharchenko_et_al_2013} (K13) cluster corresponding to
+    the external catalog claiming membership.
+    This, or else the external name is used to assign the unique
+    cluster name.
+    The method for name matching (Appendix~\ref{appendix:uniquenames}) is
+    also given as a string, as is a ``Comment'' summarizing
+    information from \citet{Kharchenko_et_al_2013} about the
+    cluster.
+    The age and error as quoted by \citet{Kharchenko_et_al_2013}
+    are also given.
+}
+
+\end{deluxetable*}
 

### 2019-08-07 paper_I/table_cdips_targets.tex
cdips target table now good

@@
- 497093746702988672 &  2006361919000756992 &  2048442943413035776 &  5867618572762132864 \\
-          Platais 3 &             ASCC 121 &           Teutsch 35 &           Loden\_1152 \\
-           Dias2014 &             Dias2014 &             Dias2014 &       Kharchenko2013 \\
-         799-012054 &           724-092321 &           630-074483 &            650278772 \\
-            71.4458 &              337.708 &              294.081 &              209.832 \\
-            69.6454 &              54.6607 &              35.8782 &             -59.2883 \\
-            -5.1826 &             -3.48356 &             -3.19716 &              -3.6399 \\
-          -0.478063 &             -1.28297 &             -2.04354 &             -3.93699 \\
-           0.579745 &             0.196117 &             0.324896 &             0.397703 \\
-            15.1735 &              15.4843 &              15.1863 &              16.4277 \\
-            15.5786 &              16.3805 &              15.7505 &               16.991 \\
-            14.6008 &              14.5227 &              14.4853 &              15.6807 \\
-          Platais\_3 &             ASCC\_121 &             ASCC\_103 &           Loden\_1152 \\
-          Platais\_3 &             ASCC\_121 &             ASCC\_103 &           Loden\_1152 \\
-       string\_match &         string\_match &         string\_match &         string\_match \\
-              False &                False &                False &                False \\
-                NaN &                  NaN &                  NaN &                  NaN \\
-                8.8 &                  6.4 &                 8.39 &                8.065 \\
-                NaN &                  NaN &                  NaN &                0.092 \\
+ Cluster &                                                 Platais 3 &             ASCC 121 &           Teutsch 35 &           Loden\_1152 \\
+ Reference &                                                Dias2014 &             Dias2014 &             Dias2014 &       Kharchenko2013 \\
+ Ext catalog name &                                       799-012054 &           724-092321 &           630-074483 &            650278772 \\
+ RA &                                                        71.4458 &              337.708 &              294.081 &              209.832 \\
+ Dec &                                                       69.6454 &              54.6607 &              35.8782 &             -59.2883 \\
+ PMra &                                                      -5.1826 &             -3.48356 &             -3.19716 &              -3.6399 \\
+ PMdec &                                                   -0.478063 &             -1.28297 &             -2.04354 &             -3.93699 \\
+ Plx &                                                      0.579745 &             0.196117 &             0.324896 &             0.397703 \\
+ $G$ &                                                       15.1735 &              15.4843 &              15.1863 &              16.4277 \\
+ $G_{\rm Bp}$ &                                              15.5786 &              16.3805 &              15.7505 &               16.991 \\
+ $G_{\rm Rp}$ &                                              14.6008 &              14.5227 &              14.4853 &              15.6807 \\
+ K13 name match &                                          Platais\_3 &             ASCC\_121 &             ASCC\_103 &           Loden\_1152 \\
+ Unique cluster name &                                     Platais\_3 &             ASCC\_121 &             ASCC\_103 &           Loden\_1152 \\
+ How match &                                            string\_match &         string\_match &         string\_match &         string\_match \\
+ Not in K13? &                                                 False &                False &                False &                False \\
+ Comment &                                                       NaN &                  NaN &                  NaN &                  NaN \\
+ K13 logt &                                                      8.8 &                  6.4 &                 8.39 &                8.065 \\
+ K13 err logt                                                    NaN &                  NaN &                  NaN &                0.092 \\

### 2019-08-10 paper_I/ms.tex
update intro
Co-authored-by: joshwinn <jwinn@astro.princeton.edu>

@@
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% TODO
+% * update keywords per new AAS format
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \documentclass[12pt,twocolumn,tighten]{aastex62}
@@
 \title{
-  CDIPS. I. Light Curves in Open Clusters from TESS Sectors 6 \& 7
+  Cluster Difference Imaging Photometric Survey. I.
+  Light Curves of Stars in Open Clusters from TESS Sectors 6 \& 7
 }
@@
   % Context
-  The Transiting Exoplanet Survey Satellite (TESS) has begun to
-  photometrically monitor almost every star cluster in the solar
-  neighborhood.
+  The Transiting Exoplanet Survey Satellite (TESS) is providing
+  precise time-series photometry for hundreds of nearby star clusters.
   % Aims
@@
   are candidate cluster members, or else show other indications of
-  youth relative to field stars.
-  %
-  Our aims are to discover giant transiting planets with known
-  ages, and also to provide a light curve sample fit for studies in
-  stellar astrophysics.
+  youth.
+  %
+  Our aims are to discover giant transiting planets with known ages,
+  and to provide light curves suitable for studies in stellar
+  astrophysics.
   %
@@
   represents between 20 and 25 days of observations of a star brighter
-  than $G_{Rp}=16$, sampled at 30 minute cadence.
+  than $G_{Rp}=16$, with 30-minute sampling.
   % Methods
@@
   %
-  We also comment on the possible utility of the light curve sample for
-  studies of stellar rotation evolution, and binary eccentricity
+  We also comment on the possible utility of the light curve sample
+  for studies of stellar rotation evolution, and binary eccentricity
   damping.
@@
 
-Each of the $\sim$3000 known star clusters of the Milky Way is a gift
-to astrophysics, providing a sample of stars that vary widely in mass
-but all have approximately the same age and composition.  Time-series
-photometry of clusters has many applications. By measuring rotation
-periods over a range of ages, we can study the angular momentum
-evolution of stars and improve our ability to determine stellar ages
-through gyrochronology \citep[{\it
+Each of the several thousand star clusters of the Milky Way is a
+gift to astrophysics, providing a sample of stars that vary widely in
+mass but all have approximately the same age and composition.
+Time-series photometry of clusters has many applications. By measuring
+rotation periods over a range of ages, we can study the angular
+momentum evolution of stars and improve our ability to determine
+stellar ages through gyrochronology \citep[{\it
 e.g.},][]{skumanich_time_1972,barnes_color-period_2015,meibom_spin-down_2015,curtis_tess_2019}.
-By measuring eccenticities as a function age, we can study the tidal
-circularization of binaries
+By measuring the eccentricity distribution of binary stars as a
+function of age, we can study the tidal circularization process
 \citep{meibom_robust_2005,milliman_wiyn_2014,price-whelan_binary_2018}.
@@
 
-The TESS mission \citep{ricker_transiting_2015}, though designed for
-other purposes, holds the promise to deliver the most homogeneous and
-comprehensive cluster photometric survey in history.  More
-quantitatively, the \citet{Kharchenko_et_al_2013} cluster member
-database indicates that $\approx 2\times10^5$ open cluster members
-brighter than $T=16$ will be observed in the full-frame images over
-the first two years of TESS observations.  This count includes the
-``most probable'' members within each cluster's radius, which by the
+The Transiting Exoplanet Survey Satellite (TESS,
+\citealt{ricker_transiting_2015}) holds the promise to deliver the
+most homogeneous and comprehensive cluster photometric survey in
+history.  Based on the cluster membership data of
+\citet{Kharchenko_et_al_2013}, approximately $2\times10^5$ open
+cluster members brighter than $T=16$ will be observed in the
+full-frame images over the first two years of TESS observations.  This
+count includes the ``most probable'' members, which by the
 \citet{kharchenko_global_2012} definition requires the independent
@@
 exceed 61\%.  The actual number of stars in clusters is larger, as the
-membership catalogs are not yet complete, even at these
-relatively bright magnitudes \citep[{\it
-e.g.},][]{roser_nine_RSG_2016,cantat-gaudin_gaia_2018,cantat-gaudin_newOCs_2019}.
+membership catalogs are not yet complete, even at these relatively
+bright magnitudes \citep[{\it
+e.g.},][]{roser_nine_RSG_2016,cantat-gaudin_gaia_2018,cantat-gaudin_newOCs_2019,kounkel_untangling_2019,sim_open_2019}.
 
 A major barrier to deriving precise photometry from the TESS images is
-the relatively poor angular resolution ($\approx 21''$ per pixel).
-Almost all clusters are within 10 degrees of the Galactic plane. The
-problems with crowding and complex backgrounds become so severe
-that the TESS Candidate Target List deprioritizes
-2-minute targets at galactic latitudes less than $\approx
-15^\circ$~\citep{stassun_TIC_2018,stassun_TIC8_2019}. This includes
-almost all star clusters\footnote{TICv8 updated the cutoff to
-$10^\circ$. During the first year of TESS observations, the number
-used when selecting 2-minute target stars was $15^\circ$.}.  This decision
-was made because
-the large pixel size and the high stellar surface density make
-aperture photometry unreliable.  However, it means that most
-stars in clusters, though capable of yielding a cornucopia of science,
-will go unprocessed by the official {\it TESS} data reduction
-pipeline.
-
-One way to quantify the blending problem is to determine what fraction of
-the total flux in a photometric aperture is contributed by a
+the relatively poor angular resolution ($21''$ per pixel).  Almost all
+clusters are within 10 degrees of the Galactic plane. The problems
+with crowding and complex backgrounds are so severe that the TESS
+Candidate Target List deprioritizes 2-minute targets within $15^\circ$
+of the galactic plane\footnote{During the first year of TESS
+observations, objects within $15^\circ$ of the galactic plane were
+deprioritized. Starting in the second year of observations,
+the cutoff was changed to
+objects within $10^\circ$ of the galactic plane
+\citep{stassun_TIC8_2019}.}~\citep{stassun_TIC_2018,stassun_TIC8_2019}.
+This decision was made because the large pixel size and the high
+stellar surface density make aperture photometry unreliable.  However,
+it implies that most stars in clusters, though capable of yielding a
+cornucopia of science, will go unprocessed by the official {\it TESS}
+data reduction pipeline.
+
+One way to quantify the blending problem is to determine what fraction
+of the total flux in a photometric aperture is contributed by a
 particular target star. Aperture photometry is reliable when this
-fraction is close to unity.  
-Difference imaging \citep{Alard_Lupton_1998,miller_optimal_2008}, in
-our group's experience, can be viable down to crowding fractions
-of perhaps 1 part in 10.
-Based on the
-\citet{Kharchenko_et_al_2013} cluster membership data, and the density
-of background stars, we calculated that the median dilution fraction of
-cluster stars with $T< 16$ is 0.13, for an aperture radius of 2 pixels.
-For at least $\sim$$10^5$ cluster stars then, it seems that difference
-imaging may be worthwhile.
+fraction is close to unity.  Difference imaging
+\citep{Alard_Lupton_1998,miller_optimal_2008}, in our group's
+experience, can be viable down to crowding fractions of 10\%.  Based
+on the \citet{Kharchenko_et_al_2013} cluster membership data, and the
+density of background stars, we calculated that the median dilution
+fraction is 0.13, for cluster stars with $T< 16$ and an aperture
+radius of 2 pixels.  Thus, for at least $\sim$$10^5$ cluster stars,
+difference imaging may be advantageous.
 
@@
 forced-aperture photometry.  In this method,
-the positions of stars are predicted from an astrometric
+the pixel coordinates
+of stars are calculated from an astrometric
 solution, and the reference fluxes are determined from a calibrated
-catalog magnitude-to-flux relation.  The deviation from the reference
+catalog magnitude-to-flux relation (see \S~\ref{subsubsec:photref}).
+The deviation from the reference
 flux is measured on the difference image.  Assuming that only a single
-source causes the variability, blended neighbor stars only act to
-increase Poisson noise, and do not ``dilute'' transit signals, down to
+source is variable, blended neighbor stars only act to
+increase Poisson noise, down to
 the angular resolution of the source catalog used to determine the
@@
 TESS images, with a focus on any star that could be a member
-of a coeval group.  We
+of a group.  We
 are also including some stars that we suspect are young due to
@@
 simply cluster, to refer to a coeval group of stars.  This includes
-the open clusters of yore, as well as the moving groups and stellar
-associations that have been discovered since the late
-1990s \citep{zuckerman_young_2004}.
+open clusters, as well as the moving groups and stellar associations
+that have been discovered since the late 1990s
+\citep{zuckerman_young_2004}.
 
 The plan of action is as follows. In \S~\ref{sec:starselection}, we
-describe how target stars were selected. \S~\ref{sec:method} presents
-the photometric and image processing methods we used to produce light
-curves for these stars.  The statistical properties of the \numberlcs
-light curves from TESS Sectors 6 and 7 are then summarized
-(\S~\ref{subsec:lcstatistics}).  An example of how we might use the
-data to identify pulsating stars, eclipsing binaries, and transiting
-planets is then given (\S~\ref{subsec:identifying_variability}).
-\S~\ref{sec:conclusion} summarizes our findings, and discusses them
-with an eye towards the studies we hope this and subsequent rounds of
-data processing will enable.
+describe how target stars were selected. We then present the
+photometric and image processing methods we used to produce light
+curves for these stars (\S~\ref{sec:method}).  In TESS Sectors 6 and
+7, these methods yielded \numberlcs light curves, and in
+\S~\ref{subsec:lcstatistics} we summarize their statistical properties.
+An example of how we might use the data to identify pulsating stars,
+eclipsing binaries, and transiting planets is then given
+(\S~\ref{subsec:identifying_variability}).  We close in
+\S~\ref{sec:conclusion} by summarizing our findings, and discuss them
+with an eye towards the studies we hope this and further data
+processing will enable.
 
@@
 \subsubsection{Photometric reference frame construction \& reference flux measurement}
+\label{subsubsec:photref}
 

### 2019-08-10 paper_I/ms.tex
section 2 updates
Co-authored-by: joshwinn <jwinn@astro.princeton.edu>

@@
     \S~\ref{sec:starselection}).  Most will be observed for one or two
-    lunar months over the TESS Prime Mission.
+    lunar months during the TESS Prime Mission.
     \label{fig:cdips_targets_positions}
@@
 		{\it Bottom.} Provenance of cluster membership.  Percentages are
-		relative to $N_{\rm total}=1061446$ target stars. Symbols
+		relative to $N_{\rm total}=1{,}061{,}446$ target stars. Symbols
 		are as follows.
@@
 A homogeneous membership calculation for every known cluster is a
-rather large undertaking, and currently falls outside our scope.  So
+large undertaking, and currently falls outside our scope.  So
 too is a homogeneous search for young stars across the galaxy.
-Instead, we have opted to collect and concatenate appropriate catalogs
-from across the literature.  We then use the resulting meta-catalog to
-identify our target stars within the TESS images.
-
-The probabilistic criteria for inclusion in our target star list is
-necessarily heterogeneous across different catalogs.  However, in our
-initial stellar selection we aim for completeness, not accuracy.  If
+Instead, we have opted to collect and concatenate catalogs
+from the literature.  We then use the resulting meta-catalog to
+identify target stars within the TESS images.
+
+The criteria for inclusion in our target star list are
+necessarily heterogeneous across different catalogs.  
+We aim for completeness, not accuracy.  If
 there has been a claim in the literature that a star should be
@@
 
-\S~\ref{subsec:oc} describes the catalogs we used to identify
-candidate members of open clusters.  \S~\ref{subsec:mg} describes the
-catalogs we used to identify candidate members of moving groups,
-stellar associations, as well as young stars identified through
-combined Gaia photometry and astrometry.  \S~\ref{subsec:ocmgsummary}
-and Figure~\ref{fig:cdips_targets} describe summary statistics for the
+First, we describe the catalogs we used to identify
+members of open clusters (\S~\ref{subsec:oc}). 
+Then, we discuss the
+catalogs we used to identify members of moving groups,
+stellar associations, and more generally young stellar
+populations (\S~\ref{subsec:mg}).
+In
+ \S~\ref{subsec:ocmgsummary}
+and Figure~\ref{fig:cdips_targets} we give summary statistics for the
 entire sample of about one million target stars.
@@
 At the time of writing, two relatively large, homogeneous cluster
-memberships studies had been performed using {\it Gaia}-DR2: those by
+memberships studies had been performed using Gaia-DR2: those by
 \citet{cantat-gaudin_gaia_2018} and \citet{gaia_hr_2018}.
@@
 
-\citet{cantat-gaudin_gaia_2018} used the UPMASK unsupervised membership
+\citet{cantat-gaudin_gaia_2018} used an unsupervised membership
 assignment algorithm \citep{krone-martins_upmask_2014} to identify cluster
 members using Gaia-DR2 positions, proper motions, and parallaxes.
-They used {\it Gaia} photometry and radial velocities to then verify the
-claimed membership properties.  From their Table~2, we collect an initial
+They used Gaia photometry and radial velocities to verify the
+membership claims.  From their Table~2, we collect
 401{,}448 cluster members, in 1229 clusters, down to their limiting magnitude
@@
 
-\citet{gaia_hr_2018} reported memberships for stars in a smaller, more
+\citet{gaia_hr_2018} reported members of a smaller, more
 select group of well-studied open clusters. From their Table~A1, we
@@
 $500\,{\rm pc}$. While this work also included memberships for
-globular clusters, we omitted these from consideration.
-
-Given the unprecedented quality of Gaia-DR2 astrometry, these two
+globular clusters, we omitted them from consideration.
+
+Given the high quality of Gaia-DR2 astrometry, these two
 membership sources are our most reliable sources of membership
@@
 for all sources is correspondingly the Gaia-DR2 \texttt{source\_id}.
-The TIC identifiers are found through a spatial cross-match after the
-light curves have been made, subject to the requirement that the
-Gaia-DR2 source identifiers match
-\citep{stassun_TIC_2018,stassun_TIC8_2019}.
+The TESS Input Catalog (TIC) data for each target star are then collected
+using the Gaia-DR2 source identifier \citep{stassun_TIC_2018,stassun_TIC8_2019}.
 
@@
 Gaia}-DR2 source identifiers for the members, we performed a
-crossmatch for {\it Gaia}-DR2 sources within 5 arcseconds of the
+crossmatch for Gaia-DR2 sources within 5 arcseconds of the
 listed positions.  To improve the quality of the cross-match, we
-additionally used the 2MASS photometry to predict the $G$-band
+used the 2MASS photometry to predict the $G$-band
 magnitudes\footnote{See
@@
 
-%FIXME is this it?
 The second (non-{\it Gaia} derived) open cluster membership catalog we
@@
 quoted membership probability above 50\%.
-To obtain {\it Gaia}-DR2 source identifiers for the members, we
+To obtain Gaia-DR2 source identifiers for the members, we
 performed a similar crossmatch as before, looking for sources within 5
@@
 Figure~\ref{fig:xmatch_info}.  The distances between matches is
-typically below 1 arcsecond.  The Dias catalog shows somewhat stronger
-crowding effects at the faint end compared to the Kharchenko catalog,
+typically below 1 arcsecond.  The \citeauthor{dias_proper_2014} catalog shows stronger
+crowding effects at the faint end compared to the \citeauthor{Kharchenko_et_al_2013} catalog,
 and likely has a larger number of false matches.
 At their faint ends, both catalogs show a tendency for true $G$-band
-magnitudes being somewhat larger than predicted $G$-band magnitudes,
+magnitudes to be larger than predicted $G$-band magnitudes,
 presumably due to dust reddening.
@@
 
-For the Gagn\'e et al{.} catalogs, a large
+For the Gagn\'e et al{.}~catalogs, a large
 number of the stars have high proper motions.
-However, a number of the stars do not have proper motions quoted.
+However, some of the stars do not have reported proper motions.
 To perform the cross-match,
@@
 the Hyades, and 32$\,$Ori respectively.  Applying the same procedure as
-for the Gagn\'e catalogs gave 187, 684, and 119 best-neighbors
+for the Gagn\'e catalogs gave 187, 684, and 119 matches
 respectively, compared to 205, 724, and 141 initially reported
@@
 $\sim$70\% of their listed members have spectroscopic indicators
-consistent with their membership in Tucana-Horologium.
-
-\citet{rizzuto_multidimensional_2011} focused on a single moving
+consistent with membership in Tucana-Horologium.
+
+\citet{rizzuto_multidimensional_2011} focused on a single
 group: the Sco OB2 association. We used their reported Hipparcos
@@
 
-Next, \citet{oh_comoving_2017} searched for comoving stars in the
-$\approx$2 million stars that overlapped between Tycho-2 and {\it
-Gaia}-DR1.  They found many wide binaries, and also identified a large
+\citet{oh_comoving_2017} searched for comoving stars in the
+$\approx$2 million stars that appear in both the Tycho-2 and {\it
+Gaia}-DR1 catalogs.  They found many wide binaries, and also identified a large
 number of comoving groups.  We chose the 2{,}134 stars that they
 reported were in groups with sizes of at least 3 stars.  Using their
-{\it Gaia}-DR1 source identifiers, we matched against the {\it Gaia}
+Gaia-DR1 source identifiers, we matched against the {\it Gaia}
 archive's \texttt{dr1\_neighbourhood} table, which gave 1{,}881
@@
 After collecting the aforementioned lists, we merged them into a
-single table. We queried the \texttt{gaiadr2.gaia\_source} table to
-retrieve their photometric $G$, $G_{\rm Rp}$, and $G_{\rm Bp}$
+single table. We queried Gaia-DR2's \texttt{gaia\_source} table to
+retrieve their apparent $G$, $G_{\rm Rp}$, and $G_{\rm Bp}$
 magnitudes, as well as their astrometric measurements $(\alpha,
 \delta, \mu_\alpha, \mu_\delta, \pi)$.  Finally, we required that
-$G_{\rm Rp} < 16$, which is roughly where the 1-hour photometric
-precision of TESS is predicted to reach 1\%
+$G_{\rm Rp} < 16$, which is roughly the level for which
+the 1-hour photometric
+precision of TESS is predicted to be 1\%
 \citep{ricker_transiting_2015}.
 
-All told, this procedure yielded 1{,}061{,}447 unique stars, from 13
-distinct membership catalogs.
-
-The relative fractions of stars from each catalog are shown in
-Figure~\ref{fig:cdips_targets}.
+The resulting CDIPS target star list, consisting of 1{,}061{,}447 unique stars from 13
+distinct catalogs, is given in
+Table~\ref{tbl:cdips_targets}.  The cumulative distribution of target
+star brightnesses, as well as a histogram of the ages, is shown in
+Figure~\ref{fig:cdips_targets}.  Relative to field stars, our target
+star sample is young, with a most probable age of 100$\,$Myr.
+
+Figure~\ref{fig:cdips_targets} also shows
+the relative fraction of stars from each catalog.
 The largest number of stars come from \citealt{dias_proper_2014}
-(44.3\% of stars), \citealt{Kharchenko_et_al_2013} (17.3\%),
+(44.3\%), \citealt{Kharchenko_et_al_2013} (17.3\%),
 \citealt{cantat-gaudin_gaia_2018} (16.7\%), and \citealt{zari_3d_2018}
@@
 on a given star's cluster membership is a helpful indication of it
-being a bonafide member.
-Stars reported in multiple catalogs have all available reference information
-concatenated.
-
-The fraction of target stars from each catalog which are bonafide
-cluster members should be understood to be heterogeneous.  For the
+being a member.
+
+Different catalogs have different standards for deciding
+which stars are members.  For the
 \citet{dias_proper_2014} catalog, their membership calculation
@@
 kinematic, and photometric information to derive their membership
-probabilities.  We also used a somewhat more restrictive membership
+probabilities.  We also used a more restrictive membership
 probability cut (again, following the criteria they used for their
@@
 
-To assign unique cluster names, we adopted the name matched against
+To assign unique cluster names, we adopted the name given by
 \citet{Kharchenko_et_al_2013} whenever possible.
 Appendix~\ref{appendix:uniquenames} describes  how this was done in detail.
-For moving groups not identified in \citet{Kharchenko_et_al_2013}, we used
+For moving groups not identified by \citet{Kharchenko_et_al_2013}, we used
 the constellation-based naming convention from
@@
 the original catalog claiming membership.  This process reduced 16,425
-name permutations down to 3,216 unique cluster names.  Though we have
+name variants down to 3,216 unique cluster names.  Though we have
 made every effort to avoid duplicates, a small number may remain, so we
@@
 of interest.  Nonetheless, 87.7\% of the $\sim$million unique target
-stars are matched to clusters within \citet{Kharchenko_et_al_2013},
+stars are matched to clusters named by \citet{Kharchenko_et_al_2013},
 and 88.8\% are assigned a cluster name.  The remainder are mostly the
 young stars from \citet{zari_3d_2018}.
-Ages and their uncertainties are then merged against the 
+Ages and their uncertainties were then assigned using the 
 parameters reported by \citet{Kharchenko_et_al_2013}.
-
-The resulting CDIPS target star list is given in
-Table~\ref{tbl:cdips_targets}.  The cumulative distribution of target
-star brightnesses, as well as a histogram of the ages, is shown in
-Figure~\ref{fig:cdips_targets}.  Relative to field stars, our target
-star sample is young, with a typical age of 100$\,$Myr.
 

### 2019-08-10 paper_I/ms.tex
update section 3
Co-authored-by: joshwinn <jwinn@astro.princeton.edu>

@@
     \caption{
-        Stages of image processing for an image taken during the middle
+        Stages of image processing for an image obtained during the middle
         of an orbit.
@@
     \caption{
-        Same sector, camera and CCD as Figure~\ref{fig:stages_good}, but for an image taken during
+        Same sector, camera and CCD as Figure~\ref{fig:stages_good}, but for an image obtained during
         perigee passage, when scattered light from the Earth is
@@
 difference imaging approach.  The overall method is in the spirit of the
-reduction pipelines developed by \citet{Pal_2009},
-\citet{huang_high-precision_2015}, \citet{soares-furtado_image_2017}
-and \citet{oelkers_precision_2018}; a conceptual overview is given in
-Figure~\ref{fig:pipeline}.  Most sub-modules of our pipeline have been
-developed over the past decade to process HAT data \citep[{\it
-e.g.},][]{bakos_hat_review_2018}.  The specific high-level framework
+pipelines developed by \citet{Pal_2009},
+\citet{huang_high-precision_2015}, \citet{soares-furtado_image_2017}, \citet{oelkers_precision_2018} and \citet{wallace_search_2019}.
+Figure~\ref{fig:pipeline} shows a conceptual overview of
+our pipeline.  Most modules have been
+developed over the past decade to reduce
+images taken by the Hungarian Automated Telescope (HAT) network \citep{bakos_hat_review_2018}.  The specific high-level framework
 used for this reduction was adapted from a pipeline called
@@
 collected from these initial steps, we select an astrometric reference
-frame to which we transform all of the calibrated images.  We
-construct a photometric reference by stacking a subset of these
-transformed frames, after having convolved the frames to have
-identical stellar profiles. Finally, we subtract each target frame
-from the photometric reference (\S~\ref{subsec:imagesubtraction}).  We
+frame to which we transform all of the calibrated images. 
+To construct a photometric reference frame,
+we first convolve a subset of the frames to have identical stellar profiles,
+and then stack them. Finally, we subtract each target frame
+from the photometric reference frame (\S~\ref{subsec:imagesubtraction}).  We
 perform aperture photometry on the subtracted images using positions
@@
 $\approx$$28$ degrees east in ecliptic longitude every lunar month.
-Data acquired throughout each ``sector'' are downlinked at spacecraft
+Data acquired throughout each one-month ``sector'' are downlinked at spacecraft
 perigee through the Deep Space Network.  Descriptions of the
 spacecraft's design and operations are given by
-\citet{ricker_transiting_2015} and the instrument handbook
-\citep{vanderspek_2018}.
+\citet{ricker_transiting_2015} and
+\citet{vanderspek_2018}.
 
 For us, the main data product of interest is the calibrated full frame
-image (FFI).  Each TESS camera is read out every 2 seconds.  To
-produce a manageable telemetric load, the resulting pixel values are
+image (FFI).  Each TESS camera is read out every 2 seconds.  
+The resulting pixel values are
 averaged by the onboard computer into 30 minute exposures. An on-board
@@
 
-We perform our processing using the calibrated images, their
+We perform our processing using the calibrated images, the
 corresponding uncertainty images, and the associated headers.  The
 spacecraft has four cameras, and each camera has four CCDs.  In the
-following analysis, all image-level operations are thus performed on
-the images for each CCD, so that at any instant of time there are 16
-independent images that require analysis.
-
-While we performed numerous initial tests on the first sectors of
-data, by geometric coincidence Sectors 1--5 were pointed away from the
-galactic plane.  Consequently, less than 2\% of the CDIPS target star
-sample was observed in the first five TESS sectors.  Though a few
+following analysis, all image-level operations are performed on
+individual CCD images, so that at any instant of time there are 16
+images that require analysis.
+
+Sectors 1--5 mainly covered portions of the sky away from
+the galactic plane.  Consequently, fewer than 2\% of the CDIPS target stars
+were observed in the first five TESS sectors.  Although a few
 interesting clusters are present in these observations ({\it e.g.},
 Blanco~1, NGC~2516, NGC~1901), for the present work we opted to focus
-on sectors in which there were more stars of interest for our intended
-science.  These begin in Sector 6 (2018-12-12, spacecraft orbit \#19).
-For this run of processing, they conclude at the end of Sector 7
+on Sectors 6 \& 7, for which there were more stars of interest.
+These begin in Sector 6 (2018-12-12, spacecraft orbit \#19),
+and conclude at the end of Sector 7
 (2019-02-01, spacecraft orbit \#22).
 Sectors 6 and 7 cover galactic longitudes from roughly 200$^\circ$ to 280$^\circ$, 
-with fair coverage within $\pm 20^\circ$ of the galactic plane
+with coverage within $\pm 20^\circ$ of the galactic plane
 (Figure~\ref{fig:cdips_targets_positions}).
@@
 First, we convert the multi-extension calibrated FITS image from MAST
-into a single-extension FITS image, and trim to remove virtual rows
+into a single-extension FITS image, and trim the image to remove virtual rows
 and columns using the \texttt{SCIROWS}, \texttt{SCIROWE},
@@
 
-In order to preemptively address the background variations present in
+In order to account for the background variations present in
 some frames due to scattered light from the Earth and Moon
-\citep[see][\S 7.3.1--7.3.4]{vanderspek_2018}, we then estimate and
-subtract the large-scale background.  We do this by temporarily
+\citep[see][\S 7.3.1--7.3.4]{vanderspek_2018}, we determine and
+subtract a model of the large-scale background.  We do this by temporarily
 masking out pixels more than $2\sigma$ from the image median, and then
@@
 estimate has low-amplitude structure over spatial scales of a few
-pixels, so we then blur it with a gaussian kernel to produce a smooth
-background estimate for each image.  These steps also remove a
-low-level vignetting present in the corners of many images, which
+pixels. We then blur the model image with a gaussian kernel of size 48 pixels,
+which produces a smooth
+background estimate.  These steps also remove
+low-level vignetting in the corners of many images, which
 remains even after flat-fielding \citep[see][\S
@@
 Features with spatial scales smaller than $\approx$48 pixels remain, 
-but large scale scattered light patches are removed.
+but large scale patterns of scattered light are removed.
 
@@
 After subtracting the background, we mask out saturated pixels using a
-fixed saturation level of $8\times10^4\,{\rm ADU}$. This value was
+fixed saturation level of $8\times10^4$ analog-to-digital units (ADU). This value was
 chosen based on the onset of bleeding charge trails in the images, and
 is slightly greater than the saturation level of $2\times10^5$
-electrons, or about $4\times10^4\,{\rm ADU}$, quoted by
+electrons, or about $4\times10^4\,{\rm ADU}$, reported by
 \citet{vanderspek_2018}. 
-We correspondingly do not analyze stars brighter than $T\approx 6.5$.
-As described by \citet{Pal_2009}, the pixel masks are metadata to the
-image, and are only applied to the pixel values during the specific
+As a consequence, we do not analyze stars brighter than $T\approx 6.5$.
+As described by \citet{Pal_2009}, the pixel masks are metadata attached
+to the image file, and are only applied to the pixel values during the specific
 image processing steps in which they are necessary ({\it e.g.},
@@
 with anomalous spacecraft performance, which we omit from
-consideration.  For Sectors 6 and 7, this included three days at the
+consideration.  This included three days at the
 beginning of Sector 6 dedicated to acquiring pixel response function
-data, and no additional gaps in Sector 7.
+data. There were no additional gaps in Sector 7.
 %For Sectors 1 through 5, these
@@
 simultaneously
-fit elongated gaussians to their profiles, yielding the shape
+fit elliptical gaussians to their profiles, yielding the shape
 parameters $(s,d,k)$, where the flux $f$ as a function of position
@@
 measuring their positions.
-Nonetheless, we did find that extending the astrometric correction
-to sixth order (compared to the fourth-order polynomial coefficients
-in the SPOC solution) did not improve the quality of the fit.
+%Nonetheless, we did find that extending the astrometric correction
+%to sixth order (compared to the fourth-order polynomial coefficients
+%in the SPOC solution) did not improve the quality of the fit.
 
@@
 photometry,
-rather than attempting to detect the positions.  Such
+rather than attempting to measure the positions.  Such
 ``forced-aperture photometry'' is preferable to source
@@
 
-The residual between the measured and projected stellar centroid
-positions is displayed for one photometric reference frame in
-Figure~\ref{fig:astromresid}.
-The construction of this frame will be described shortly, however
-a few salient points can first be made.
-First, the typical median precision of the WCS solution is a bit below
+Figure~\ref{fig:astromresid} displays the residual between
+the measured and projected stellar centroid
+positions for one photometric reference image.
+The plot shows that the errors
+are typically largest in the corners of the image,
+where the non-linearity of the focal plane is most significant, and
+the corrections required by the SIP coefficients are largest.
+Also, the typical median precision of the WCS solution is a bit below
 0.1 pixels, and its $90^{\rm th}$ percentile is typically less than
-0.3 pixels\footnote{In fact, in our reduction we automatically impose
-that the median residual and 90th percentile remain below 0.2 and 0.4
-pixels, respectively.}.
+0.3 pixels.
+In our reduction,
+we therefore require
+that each frame's median residual and 90th percentile remain
+below 0.2 and 0.4
+pixels, respectively. If this constraint is not met, the reduction fails.
+This is an essential quality-control check for any forced-aperture
+photometry pipeline.
 %The distribution has a outlier tail of saturated stars which were
 %masked, and thus do not have measureable centroid positions.
-The errors are typically largest in the corners of the field of view,
-where the non-linearity of the focal plane is most significant, and
-the corrections required by the SIP coefficients are largest.
 %The final sub-panel of Figure~\ref{fig:astrometricresidual} is a
@@
 The pixel weights are equal to the fraction of the pixel
-that falls within the aperture.  They are unity for pixels
+that falls within the circular aperture.  They are unity for pixels
 entirely within the aperture, and fractional along the aperture
 boundary. % (see \citealt{Pal_2009} Fig 17). 
-The background levels are measured in annuli around each aperture
-center. 
+The background levels are measured in annuli surrounding
+the center of each aperture. 
 %The raw flux of the object after background removal is then
@@
 %\end{equation}
-The resulting measurements, for instance of the background level of
-each aperture, and the number of stars with ``good'' photometry,
-can then be used to assess the photometric quality of each frame.
+%The resulting measurements, for instance of the background level of
+%each aperture, and the number of stars with ``good'' photometry,
+%can then be used to assess the photometric quality of each frame.
 
@@
 
-The core operation of ``classical'' image subtraction attempts to
-match a photometric reference $R$ and a target image $I$ by computing
+The core operation of ``classical'' image subtraction is to
+match a photometric reference image $R$ and a target image $I$ by computing
 and applying a convolution kernel.  For ground-based data, this
@@
 set $B_{xy}=0$.  The convolution kernel $K$ is typically decomposed
-onto a basis, $K = \sum_i c_i K_i$, and the coefficients are found by
-minimizing
+onto a basis,
+\begin{equation}
+K = \sum_i c_i K_i,
+\end{equation}
+where the coefficients $c_i$ are found by minimizing
 \begin{equation}
@@
 two ``reference frames'':
-(1) the astrometric reference; and (2) the photometric reference.
-
-To choose the astrometric reference, we search for frames with
+(1) the astrometric reference frame; and (2) the photometric reference frame.
+
+To choose the astrometric reference frame, we search for frames with
 large, round stars (big $s$, small $d$ and $k$ values).  We also
-require that the frame have minimal background noise, as measured in
+require that the frame have a low background level, as measured in
 annuli around the bright stars selected in
 \S~\ref{subsec:preparation}.  Finally, the astrometric reference
-needs to have, relative to the other frames being considered, a large
-number of detected sources (though the variance between frames was rather 
-small).  We sort the frames
-using these metrics, and then select the astrometric reference from
+frame needs to have a large
+number of detected sources (though the variance between TESS images was rather 
+small).  We sort the image
+using these metrics, and then select the astrometric reference frame from
 successive intersections of each sorted list.
@@
 
-The second required reference frame is the photometric reference,
+The second required reference frame is the photometric reference frame,
 which is used both to calculate the convolution kernel, and to obtain
@@
 out during the background measurement.  If we were to stop
-here, {\it it would be a bad mistake}.  The reference fluxes for faint
+here, {\it it would be a mistake}.  The reference fluxes for faint
 stars would be overestimated, due to crowding.  The relative amplitude
 of photometric signals for faint stars would correspondingly be biased
-small, which would hinder exoplanet detection, among other
-applications.
+to lower values.
 
 To avoid this problem, after performing simple aperture photometry on
-the reference frame, we fitted a line between the catalog $T$-band
-magnitude of each star, and its measured flux.  The $T$-band magnitude
+the reference frame, we fitted a line between the Gaia-DR2
+magnitude of each star, and its measured flux.  The TESS $T$-band magnitude
 was calculated according to Equation~1 of \citet{stassun_TIC8_2019}.
 We then use the known catalog magnitude to predict the expected
-reference flux for each star.  This minimizes crowding down to Gaia's
+reference flux for each star.  This accounts for crowding down to Gaia's
 resolution limit of $\approx$1$''$, rather than the TESS limit of
@@
 +
-\frac{1}{|| K ||_1^2} \sum_{x,y} D_{x,y} (w \otimes K)_{x,y}.
+\frac{1}{|| K ||_1^2} \sum_{x,y} D_{xy} (w \otimes K)_{xy}.
 \label{eq:ism_flux_measurement}
@@
 The function $g$ takes as input the target star's catalog magnitude
-$T_{\rm cat}$, and returns the reference flux.  Its coefficients have
-been fit per the procedure just discussed, independently for each
-aperture.  The difference image $D$ is equal to $I -  R\otimes K$,
+$T_{\rm cat}$, and returns the reference flux.  Its coefficients are
+found independently for each
+aperture.  The difference image $D$ is equal to $I -  (R\otimes K)$,
 where as in Equation~\ref{eq:imagemodel}, $I$ is the target image
@@
 
-To solve for the coefficients to the convolution kernel, a
+To solve for the coefficients $c_i$ of the convolution kernel, a
 few further assumptions are necessary.  The procedure implemented in
@@
 flux scaling.  We performed a grid-search to tune these parameters, in
-which our ``loss functions'' were the measured RMS as a function
-of magnitude, and the recovered SNR of transits from the catalog
+which our ``loss functions'' were the light curve standard deviation (RMS)
+as a function of magnitude, and the recovered SNR of transits from the catalog
 of known TOIs (TESS Objects of Interest; N.~Guerrero, in prep).
@@
 pixels, and 2.25 pixels.  These sizes were chosen to roughly span the
-range of optimal aperture sizes for stars in our sample, as calculated
-from the pre-flight \citet{Sullivan_et_al_2015} noise model.  Finally,
+range of optimal aperture sizes reported by
+\citet{Sullivan_et_al_2015}.  Finally,
 to convert from a list of flux measurements for each source on a frame
@@
 In such cases, an effective model of the systematics comes from
-constructing a set of vectors that empirically captures trends common
+constructing a set of basis vectors that empirically captures trends common
 to many stars.  Each target light curve is then assumed to be a linear

### 2019-08-11 paper_I/ms.tex
update results + discussion
Co-authored-by: joshwinn <jwinn@astro.princeton.edu>

@@
 
-The on-sky locations of the light curves from Sectors 6 and 7 are
-shown in Figure~\ref{fig:lcgalactic}.  Black stars are the field stars
-for which we performed photometry, and from which we selected template
-stars for TFA, as well as the construction of the PCA eigenvectors.
-Blue points are the \numberlcs stars with light curves available from
-\stscilink.  Most of the target stars are quite close to the galactic
-plane.  Gaps between CCD chips are also visible.  The highly clumped
-nature of the target stars is also apparent.
+Figure~\ref{fig:lcgalactic} shows the on-sky locations of the 
+light curves from Sectors 6 and 7.  Black points are the field stars
+for which we performed photometry in order to construct
+basis vector sets for TFA and PCA.
+Blue points are the \numberlcs target stars for which light curves are available at
+\stscilink.  Most of the target stars are close to the galactic
+plane, and are spatially clustered. 
+Gaps between CCD chips are also visible.
 
@@
 are faint, $\approx3\times10^4$ are brighter than $T=13$. The brighter
-targets will be more amenable to detailed spectroscopic observtions,
+targets will be more amenable to detailed spectroscopic observations,
 should the need arise.
@@
 main-sequence.  The latter set of OBA dwarf stars, while ``younger''
-than the typical field dwarf, are likely the least interesting subset
+than the typical field dwarf, are the least interesting subset
 of our target sample from the perspective of age analyses.  In the
@@
 
-Table~\ref{tbl:s6_lcs} shows the clusters in Sector 6 with the largest
+Table~\ref{tbl:s6_lcs} lists the clusters in Sector 6 with the largest
 numbers of light curves. The top four clusters are all moving groups
@@
 Platais~6, Mamajek~3, and Collinder~70.  These membership claims
-should be regarded with serious skepticism.  For Platais~6,
+should be regarded with skepticism.  For Platais~6,
 \citet{Kharchenko_et_al_2013} claimed only about 400 probable members
@@
 \citep{bell_32ori_2017}.
-Some rich open clusters in the Sector 6 field with many light curves,
-and more reliable membership lists include Trumpler~5,
+Some rich open clusters in the Sector 6 field with
+both many light curves and more reliable membership lists
+include Trumpler~5,
 Collinder~69 (the $\lambda$ Orionis cluster), and NGC~2287.
@@
 \paragraph{Observed RMS vs magnitude.}
-The standard deviation of the TFA-detrended light curves is plotted as
-a function of the catalog $T$-band magnitude for CDIPS light curves in
-Figure~\ref{fig:rms_vs_mag}.
+Figure~\ref{fig:rms_vs_mag} shows
+the standard deviation of the TFA-detrended light curves as
+a function of the catalog $T$-band magnitude for CDIPS target stars.
 For the $y$-axis of this plot, we have taken
@@
 number of points in the time-series, and $M$ is the number
-of template light curves used during TFA detrending.
-The correction in the denominator penalizes the natural degree of
-overfitting inherent to the TFA algorithm.
-
-The observed RMS (black points) follows the usual shape, with photon
+of template light curves (principal components) used during TFA (PCA) detrending.
+The correction in the denominator is for the overfitting inherent
+in any ensemble detrending method.
+
+The observed RMS (black points) follows the usual shape, with source photon
 noise dominating from $T=9$ to $T=12$, beyond which the onset of the
@@
 steep.  For the brightest stars ($T\lesssim 9$), a ``systematic
-floor'' was part of the mission's error budget
+floor'' of 60$\,$ppm$\,$hr$^{1/2}$ was part of the mission's error budget
 \citep{ricker_transiting_2015}, but has not been observed in early
@@
 
-Importantly, the faint stars do not noticeably exhibit
-the typical effects of crowding at the faint end 
-\citep[{\it e.g.},][Figure~5]{feinstein_eleanor_2019}.
-In aperture photometry pipelines, stars in very crowded regions typically 
-have their flux overestimated relative to the actual number of photons
-that fall on silicon.
-This leads to systematic underestimates of the uncertainty in the relative 
-fluxes, as well as ``flux contamination'' (the reduction in amplitude of say, 
-transit signals, due to diluting flux from neighbor stars).
-Our method to work around this problem -- using the catalog magnitudes to 
+An essential feature of our RMS diagram is that faint stars in
+crowded regions are not spuriously driven below theoretical limits.
+In aperture photometry pipelines, a star in a crowded region
+has its reference flux overestimated relative to the true number of 
+photons it contributes (due to contamination from neighbor stars).
+As a result, changes in relative flux in the faint star's light curve are 
+underestimated, and its RMS is driven low 
+\citep[{\it e.g.}, the faint end of][Figure~5]{feinstein_eleanor_2019}.
+Our method to work around this issue -- using the catalog magnitudes to 
 predict the reference flux values, and measuring deviations from these 
-reference fluxes on the subtracted images -- seems to be performing well.
+reference fluxes on the subtracted images -- seems to be performing 
+as intended.
 
@@
 plane, and the faint star background is brightest near the galactic
-plane (and towards the galactic center).  
+plane.  
 When performing pre-launch noise estimates,
@@
 but the faint star component was not emphasized since the Sullivan
-simulations were performed away from the galactic plane.
+simulations were performed for fields away from the galactic plane.
 
@@
 $180^\circ$, and the empirical coefficients were found to be $a_0 =
-18.9733$, $a_1=8.833$, $a_2=4.007$, and $a_3=0.805$.  The fit was
-cautioned to be {\it very approximate}.  It is sensitive to the
+18.9733$, $a_1=8.833$, $a_2=4.007$, and $a_3=0.805$.  The model
+is {\it very approximate}.  It is sensitive to the
 threshold used to select ``unresolved'' stars, and likely no more
@@
 In Figure~\ref{fig:avg_acf} we show the average autocorrelation of the
-raw and TFA-filtered light curves.
-The raw light curves have substantial systematic red noise; 
-their average autocorrelation, evaluated at various time lags, is
+raw, PCA, and TFA light curves.
+The raw light curves have substantial red noise, and
+their average autocorrelation across many time lags is
 positive.
-The TFA-filtered light curves are much closer to gaussian~--~the
+The PCA and TFA light curves are much closer to gaussian~--~the
 average autocorrelation between any two points in these light curves
 is close to zero.
-However, the average TFA-filtered light curve is not {\it exactly}
+However, the average PCA and TFA light curves are not {\it exactly}
 gaussian.
@@
 This suggests that additional detrending may be
-necessary to maximize the effectiveness of planet searches (or the discovery of
-any other signals via matched-filter techniques).
+necessary to maximize the effectiveness of planet searches, or the discovery of
+any other signals via matched-filter techniques.
 
@@
 \texttt{astrobase}.
-Our search was extremely cursory~--~a detailed search for transiting
+Our search was cursory~--~a detailed search for transiting
 exoplanets will be the subject of future work.
@@
 catalog.  The eccentric EB was claimed by \citet{dias_proper_2014} to
-be a member of the $\sim$50 Myr Bochum~5 cluster.  This EB is also of
-note because its TFA light curve heavily whitens the out-of-eclipse
-signal, leaving an eclipse signal would could be mistaken for a planet 
-candidate.  The important
-check for potential users of the light curves is of course to consider
-light curves with different types of detrending, to prevent these types of
-misinterpretations.
+be a member of the $\sim$50 Myr Bochum~5 cluster.  This EB is also
+notable because its TFA light curve heavily whitens the out-of-eclipse
+signal, leaving an eclipse signal that could be mistaken for a planet 
+candidate.  The relevant lesson
+for anyone using the light curves is to verify
+that detrending does not introduce or remove signals
+that alter the interpretation of the system.
 
@@
 
-In this study, we first collected an all-sky sample of about one
+In this study, we collected an all-sky sample of about one
 million stars brighter than $G_{\rm Rp}$ of 16.  82\%
@@
 We then reduced TESS full frame images taken over the course of about
-two months (Sectors 6 and 7; the first fields very close to the
-galactic plane).  We performed difference imaging in order to minimize
-the complications of the crowded background.  Using forced aperture
+two months (Sectors 6 and 7; the first fields close to the
+galactic plane).  We performed difference imaging in order to 
+deal with the complex background.  Using forced aperture
 photometry, we made light curves for all stars brighter than $G_{\rm
@@
 
-The light curves seem to be limited in precision by photon noise at
+The light curves seem to be limited in precision by photon-counting noise 
+from the target star at
 the bright end, and by unresolved background stars at the faint end
@@
 We remind the reader that our goal in creating our target catalog was
-completeness, rather than fidelity.  To create clean sub-samples, we
+completeness, rather than reliability.  To create clean sub-samples, we
 advise using the \texttt{CDEXTCAT} header keyword available in the

### 2019-08-12 paper_I/ms.tex
update with (most) JH comments
Co-authored-by: joeldhartman <jhartman@astro.princeton.edu>

@@
 \citet{cantat-gaudin_gaia_2018} and \citet{gaia_hr_2018}.
-There were also two large membership studies based on proper motion and 
-photometric catalogs that were of interest: the studies of
+There were also two large membership studies pre-dating Gaia-DR2 based on proper motion and 
+photometric catalogs: the studies of
 \citet{Kharchenko_et_al_2013} and \citet{dias_proper_2014}.
@@
 developed over the past decade to reduce
-images taken by the Hungarian Automated Telescope (HAT) network \citep{bakos_hat_review_2018}.  The specific high-level framework
-used for this reduction was adapted from a pipeline called
+images taken by the Hungarian Automated Telescope (HAT) network \citep{bakos_hat_review_2018}.
+The work of \citet{Pal_2009}, embodied in the \texttt{fitsh} software package,
+was an especially crucial component.
+The specific high-level framework
+we used for this reduction was adapted from a pipeline called
 \texttt{pipe-trex}, under development primarily for the HATPI project
@@
 perform aperture photometry on the subtracted images using positions
-projected onto the frame from the Gaia-DR2 source catalog.  We detrend
+projected onto the frame from the Gaia-DR2 source catalog.  
+The resulting differential flux measurements are converted to total flux measurements using photometric information from Gaia-DR2 to estimate the total flux of each source on the reference image.
+We detrend
 the resulting light curves (\S~\ref{subsec:lcdetrending}).  The
@@
 For a nearly circular shape profile, the sharpness $s$ is related to
-the FWHM as ${\rm FWHM} \approx 2.35\sqrt{s}$ \citep[{\it
+the FWHM as ${\rm FWHM} \approx 2.35s^{-1/2}$ \citep[{\it
 e.g.},][]{Pal_2009}.  These shape parameters are later used when
@@
 center of each camera's field are round, while
-stars near the field edges are more triangular.
+stars near the field edges are more elongated.
 
@@
 the measured and projected stellar centroid
-positions for one photometric reference image.
+positions for one photometric reference frame.
+The construction of this frame will be described shortly.
 The plot shows that the errors
@@
 
-\subsubsection{History of image subtraction method}
+\subsubsection{Synopsis of image subtraction method}
 
@@
 To choose the astrometric reference frame, we search for frames with
-large, round stars (big $s$, small $d$ and $k$ values).  We also
+compact, round stars (big $s$, small $d$ and $k$ values).  We also
 require that the frame have a low background level, as measured in
@@
 
-This kernel model has three free parameters: (1) the box-size; 
+This kernel model has three parameters that must be
+specified, but are not automatically optimized by the procedure: (1) the box-size; 
 (2) the maximum order of the polynomial weighting the delta
@@
 to convert from a list of flux measurements for each source on a frame
-to a list of flux values at any given time, we used the
+to light curves, we used the
 \texttt{fitsh} transposition tool \texttt{grcollect}.
@@
 		\leavevmode
-		\includegraphics[width=0.44\textwidth]{external_parameters_vs_time_sec6cam1ccd1.pdf}
+		\includegraphics[width=0.45\textwidth]{external_parameters_vs_time_sec6cam1ccd1.pdf}
 	\end{center}
@@
     particular aperture size), as a function of time.  Continuing in
-    order are $x$ and $y$ centroid positions as a functions of time,
+    order are $x$ and $y$ centroid positions as functions of time,
     the $(s,d,k)$ PSF shape parameters, the CCD temperature,  and the
-    measured background value.  Differential aberration affect the
+    measured background value.  Differential aberration affects the
     centroid position over the span of each orbit.  Momentum dumps are
@@
 the instrumental systematics seem to dominate.  This problem is
-generic to most wide-field photometric datasets, including the WASP,
+generic in wide-field photometric datasets, including the WASP,
 Kepler, and HAT surveys
-\cite{Pollacco_2006,borucki_kepler_2010,bakos_hat_review_2018}.  To
+\citep{Pollacco_2006,borucki_kepler_2010,bakos_hat_review_2018}.  To
 remove the systematic variability, we adopted two different
@@
 \citealt{kovacs_trend_2005}), and {\it (ii)} a principal component
-analysis (PCA).
+analysis (PCA, see {\it e.g.}, \citealt{ivezic_statistics_2014} for a review).
 
@@
 When trying to find periodic signals, $A(i)$ represents our prior
-knowledge of the light curve's shape.  This prior is simply that stars
+knowledge of the light curve's shape.  Initially, this prior is simply that stars
 on average maintain a constant brightness:
@@
 stars have intermediate brightness ($8.5 > T > 13$), and have a
-relatively large number of time-series data points.  We then performed
+relatively large number of time-series data points.  
+We excluded templates within 20 pixels of any given target star.
+We then performed
 an initial iteration of TFA, on only the candidate template stars.  We
@@
 {\it e.g.}, stellar rotation signals, we adopted a simple variant of
-PCA (see {\it e.g.}, \citealt{ivezic_statistics_2014} for a review).
+PCA.
 A similar approach was taken by \citet{feinstein_eleanor_2019} in
@@
 modelled each target light curve as a linear combination of a subset
-of these principal components, with weights determined by linear least
-squares.
-
-To determine the ``optimal'' number of principal components to use, we
-performed a cross-validation analysis on the template stars using the
-components derived both from PCA, as well as a separate factor
-analysis.  As is typically the case when the noise variance is
+of these principal components, and determined the weights via linear least
+squares. Both steps were performed using \texttt{scikit-learn}
+\citep{sklearn_2011}.
+
+To determine the number of principal components at which to truncate
+the model, we
+performed a cross-validation analysis.
+Again, this was achieved using \texttt{scikit-learn}.
+As is typically the case when the noise variance is
 different for each ``feature'' (each point in time), we found that
-$k$-folding cross-validation using PCA failed to recover a plausible
+$k$-folding cross-validation of the PCA components
+gave a cross-validation score that monotonically increased with
+an increasing 
 number of components\footnote{See for example
@@
  (2019/08/06).}.
-However, the factor analysis typically maximized the cross-validation
-score with anywhere from $10$ to $15$ components, which agreed with a
+We found that if we instead performed a factor analysis, the
+cross-validation
+score was typically maximized with anywhere from $10$ to $15$ components.
+This agreed with a
 visual analysis of the number of PCA components past which overfitting
 began.  We therefore used the maximum cross-validation score from
-thefactor analysis as the number of principal components to use in
+the factor analysis as the number of principal components to use in
 each light curve.  This number is documented in the \texttt{FITS}
 header of each light curve.
+
+While the PCA detrending should help remove the most egregious
+systematic artifacts, it remains possible that PCA can distort signals,
+and even inject correlated noise into a light curve ({\it e.g.}, Figure~\ref{fig:lc_systematics_dtr}).
+For any object of interest, it is worth inspecting the raw, PCA, and TFA
+light curves to ensure
+that the variability of interest is not adversely affected by the
+detrending procedures.
+If it is, alternative approaches may be necessary.
 
@@
 	\caption{
-		Phased light curves for a few objects of interest.
+		Phased PCA light curves for a few objects of interest.
 		{\it Top row, left to right}:
@@
 main-sequence table and 7\% of sources from their PMS table;
-\citet{Kharchenko_et_al_2013} for 18\% of sources,
-\citet{cantat-gaudin_gaia_2018} for 14\% of sources, and more than two
+\citet{Kharchenko_et_al_2013} for 18\% of sources;
+\citet{cantat-gaudin_gaia_2018} for 14\% of sources; and more than two
 catalogs for the remaining 10\% of sources.
@@
 positive.
-The PCA and TFA light curves are much closer to gaussian~--~the
+The PCA and TFA light curves are much closer to white noise~--~the
 average autocorrelation between any two points in these light curves
 is close to zero.
-However, the average PCA and TFA light curves are not {\it exactly}
-gaussian.
+However, the average PCA and TFA light curves are not {\it completely}
+uncorrelated.
 At time lags of a few hours or less, there is some excess power.
@@
 
-The overall point is that a great number of systems with known ages
+Overall, our periodogram search showed that 7\% of the light curves
+have Lomb-Scargle peak false alarm probabilities below $10^{-30}$.
+Even more stars are variable at lower levels of signifiance.
+The implication is that thousands of variable stars with known ages
 should be identifiable from the data at their current level of
@@
 against a set of template stars led to an ensemble of light curves
-with very nearly gaussian noise properties 
+with very nearly white noise properties 
 (Figures~\ref{fig:lc_systematics_dtr} and~\ref{fig:avg_acf}).
@@
 members~--~the census of nearby coeval stellar populations is still
-very much in flux. For instance, in the preparation of this work,
+very much in flux. For instance, during the preparation of this work,
 \citet{sim_open_2019} identified 209 new open cluster candidates
@@
 L.G.B. and J.H. acknowledge support by the TESS GI Program, program
-G011103.
+G011103, through NASA grant 80NSSC19K0386.
 %
@@
     The magnitudes in Gaia $G$, $G_{\rm Bp}$, and $G_{\rm Rp}$ bands
-    is given.
-    The naming matching described in Appendix~\ref{appendix:uniquenames}
+    are given.
+    The name matching described in Appendix~\ref{appendix:uniquenames}
     most often succeeds in finding the
@@
 	\tablecaption{Counts of light curves per cluster in Sector 7, sorted
-		in descending order.  \label{tbl:s7_lcs}}
+		in descending order.  See Table~\ref{tbl:s6_lcs} for notes. \label{tbl:s7_lcs}}
 	\tablenum{3}
@@
 correction in a direction that is slightly wrong.
-Perhaps due to the lead author's obsession with getting time-stamps correct 
-\citep{bouma_wasp-4b_2019},
+Nonetheless, following
+\citet{bouma_wasp-4b_2019},
 we perform our own barycentric correction using the appropriate
@@
 
-A few edge-cases, including for instance sub-clusters  larger
+A few edge-cases, including sub-clusters of larger
 star-forming complexes like in Sco-Cen or Collinder~33, were 

### 2019-08-12 paper_I/ms.tex
update with JH comments
(and GB comments)

Co-authored-by: joeldhartman <jhartman@astro.princeton.edu>
clean up tex

@@
   The Transiting Exoplanet Survey Satellite (TESS) is providing
-  precise time-series photometry for hundreds of nearby star clusters.
+  precise time-series photometry for almost every star cluster in the
+  solar neighborhood.
   % Aims
@@
 
-Each of the several thousand star clusters of the Milky Way is a
-gift to astrophysics, providing a sample of stars that vary widely in
-mass but all have approximately the same age and composition.
-Time-series photometry of clusters has many applications. By measuring
-rotation periods over a range of ages, we can study the angular
-momentum evolution of stars and improve our ability to determine
-stellar ages through gyrochronology \citep[{\it
+Each of the several thousand star clusters of the Milky Way is a gift
+to astrophysics, providing a sample of stars that vary widely in mass
+but all have approximately the same age and composition.  Time-series
+photometry of clusters has many applications. By measuring rotation
+periods over a range of ages, we can study the angular momentum
+evolution of stars and improve our ability to determine stellar ages
+through gyrochronology \citep[{\it
 e.g.},][]{skumanich_time_1972,barnes_color-period_2015,meibom_spin-down_2015,curtis_tess_2019}.
@@
 A major barrier to deriving precise photometry from the TESS images is
-the relatively poor angular resolution ($21''$ per pixel).  Almost all
-clusters are within 10 degrees of the Galactic plane. The problems
-with crowding and complex backgrounds are so severe that the TESS
-Candidate Target List deprioritizes 2-minute targets within $15^\circ$
-of the galactic plane\footnote{During the first year of TESS
-observations, objects within $15^\circ$ of the galactic plane were
-deprioritized. Starting in the second year of observations,
-the cutoff was changed to
-objects within $10^\circ$ of the galactic plane
+the relatively poor angular resolution ($21''$ per pixel).   The
+problems with crowding and complex backgrounds are so severe that the
+TESS Candidate Target List deprioritizes 2-minute targets within
+$15^\circ$ of the galactic plane\footnote{During the first year of
+TESS observations, objects within $15^\circ$ of the galactic plane
+were deprioritized. Starting in the second year of observations, the
+cutoff changed to objects within $10^\circ$ of the galactic plane
 \citep{stassun_TIC8_2019}.}~\citep{stassun_TIC_2018,stassun_TIC8_2019}.
@@
 stellar surface density make aperture photometry unreliable.  However,
-it implies that most stars in clusters, though capable of yielding a
-cornucopia of science, will go unprocessed by the official {\it TESS}
+it implies that most stars in clusters, which are almost always near
+the galactic plane, will go unprocessed by the official {\it TESS}
 data reduction pipeline.
@@
 Difference imaging avoids the primary effects of blending through
-forced-aperture photometry.  In this method,
-the pixel coordinates
-of stars are calculated from an astrometric
-solution, and the reference fluxes are determined from a calibrated
-catalog magnitude-to-flux relation (see \S~\ref{subsubsec:photref}).
-The deviation from the reference
-flux is measured on the difference image.  Assuming that only a single
-source is variable, blended neighbor stars only act to
-increase Poisson noise, down to
-the angular resolution of the source catalog used to determine the
-reference flux.  This is a major benefit of performing image
-subtraction in crowded fields.
-
-We have therefore begun to apply difference imaging to the
-TESS images, with a focus on any star that could be a member
-of a group.  We
-are also including some stars that we suspect are young due to
-combined photometric and astrometric indicators.
-A major motivation for
-this effort is to discover giant transiting planets with known ages.
-The focus of the present study however is to describe our
-methods, and to produce a general-purpose
-dataset applicable for studies both in exoplanetary and also
-stellar astrophysics.
+forced-aperture photometry.  In this method, the pixel coordinates of
+stars are calculated from an astrometric solution, and the reference
+fluxes are determined from a calibrated catalog magnitude-to-flux
+relation (see \S~\ref{subsubsec:photref}).  The deviation from the
+reference flux is measured on the difference image.  Assuming that
+only a single source is variable, blended neighbor stars only act to
+increase Poisson noise, down to the angular resolution of the source
+catalog used to determine the reference flux.  This is a major benefit
+of performing image subtraction in crowded fields.
+
+We have therefore begun to apply difference imaging to the TESS
+images, with a focus on any star that could be a member of a group.
+We are also including some stars that we suspect are young due to
+combined photometric and astrometric indicators.  A major motivation
+for this effort is to discover giant transiting planets with known
+ages.  The focus of the present study however is to describe our
+methods, and to produce a general-purpose dataset applicable for
+studies both in exoplanetary and also stellar astrophysics.
 
@@
 7, these methods yielded \numberlcs light curves, and in
-\S~\ref{subsec:lcstatistics} we summarize their statistical properties.
-An example of how we might use the data to identify pulsating stars,
-eclipsing binaries, and transiting planets is then given
-(\S~\ref{subsec:identifying_variability}).  We close in
+\S~\ref{subsec:lcstatistics} we summarize their statistical
+properties.  An example of how we might use the data to identify
+pulsating stars, eclipsing binaries, and transiting planets is then
+given (\S~\ref{subsec:identifying_variability}).  We close in
 \S~\ref{sec:conclusion} by summarizing our findings, and discuss them
@@
 	\caption{
-    Target star positions (blue) and nominal TESS observing
-    footprint (gray).  Target stars are either candidate members of
-    clusters, or else have other youth indicators (see
-    \S~\ref{sec:starselection}).  Most will be observed for one or two
-    lunar months during the TESS Prime Mission.
+    Target star positions (blue) and nominal TESS observing footprint
+    (gray).  Target stars are either candidate members of clusters, or
+    else have other youth indicators (see \S~\ref{sec:starselection}).
+    Most will be observed for one or two lunar months during the TESS
+    Prime Mission.  Camera 1 is centered at $(l,b)=(203^\circ,
+    -6^\circ)$ and $(218^\circ,15^\circ)$ in Sectors 6 and 7,
+    respectively.
     \label{fig:cdips_targets_positions}
@@
     {\it Top.} Quality diagnostics from cross-matching
-		\cite{Kharchenko_et_al_2013} cluster members against Gaia-DR2.
-		A histogram of the distances between matched stars is on the left; a
+    \cite{Kharchenko_et_al_2013} cluster members against Gaia-DR2.  A
+    histogram of the distances between matched stars is on the left; a
     histogram of the difference between the true $G$-band magnitude
-		and that predicted from 2MASS photometry is in the middle; a scatter
-		plot of the same magnitude difference as a function of $G$-band
-		magnitude is on the right.
+    and that predicted from 2MASS photometry is in the middle; a
+    scatter plot of the same magnitude difference as a function of
+    $G$-band magnitude is on the right.
 		{\it Bottom.} Same, but cross-matching \cite{dias_proper_2014}
@@
 facilitate studies of exoplanetary and stellar processes across
-different times and stellar environments.  A key step is
-therefore to define a sample of stars that are thought to be young, or
-members of clusters, or both.
+different times and stellar environments.  A key step is therefore to
+define a sample of stars that are thought to be young, or members of
+clusters, or both.
 
 A homogeneous membership calculation for every known cluster is a
-large undertaking, and currently falls outside our scope.  So
-too is a homogeneous search for young stars across the galaxy.
-Instead, we have opted to collect and concatenate catalogs
-from the literature.  We then use the resulting meta-catalog to
-identify target stars within the TESS images.
-
-The criteria for inclusion in our target star list are
-necessarily heterogeneous across different catalogs.  
-We aim for completeness, not accuracy.  If
-there has been a claim in the literature that a star should be
-considered a cluster member, or a young star, we would like to err on
-the side of reporting a light curve for the star.  For stars that are
-photometrically interesting, we can then perform post-hoc quality
-checks using Gaia-DR2 astrometry and photometry to assess cluster
-membership and youth.
-
-First, we describe the catalogs we used to identify
-members of open clusters (\S~\ref{subsec:oc}). 
-Then, we discuss the
-catalogs we used to identify members of moving groups,
-stellar associations, and more generally young stellar
-populations (\S~\ref{subsec:mg}).
-In
- \S~\ref{subsec:ocmgsummary}
-and Figure~\ref{fig:cdips_targets} we give summary statistics for the
-entire sample of about one million target stars.
+large undertaking, and currently falls outside our scope.  So too is a
+homogeneous search for young stars across the galaxy.  Instead, we
+have opted to collect and concatenate catalogs from the literature.
+We then use the resulting meta-catalog to identify target stars within
+the TESS images.
+
+The criteria for inclusion in our target star list are necessarily
+heterogeneous across different catalogs.  We aim for completeness, not
+accuracy.  If there has been a claim in the literature that a star
+should be considered a cluster member, or a young star, we would like
+to err on the side of reporting a light curve for the star.  For stars
+that are photometrically interesting, we can then perform post-hoc
+quality checks using Gaia-DR2 astrometry and photometry to assess
+cluster membership and youth.
+
+First, we describe the catalogs we used to identify members of open
+clusters (\S~\ref{subsec:oc}).  Then, we discuss the catalogs we used
+to identify members of moving groups, stellar associations, and more
+generally young stellar populations (\S~\ref{subsec:mg}).  In
+\S~\ref{subsec:ocmgsummary} and Figure~\ref{fig:cdips_targets} we give
+summary statistics for the entire sample of about one million target
+stars.
 
@@
 memberships studies had been performed using Gaia-DR2: those by
-\citet{cantat-gaudin_gaia_2018} and \citet{gaia_hr_2018}.
-There were also two large membership studies pre-dating Gaia-DR2 based on proper motion and 
-photometric catalogs: the studies of
+\citet{cantat-gaudin_gaia_2018} and \citet{gaia_hr_2018}.  There were
+also two large membership studies pre-dating Gaia-DR2 based on proper
+motion and photometric catalogs: the studies of
 \citet{Kharchenko_et_al_2013} and \citet{dias_proper_2014}.
@@
 \citet{cantat-gaudin_gaia_2018} used an unsupervised membership
-assignment algorithm \citep{krone-martins_upmask_2014} to identify cluster
-members using Gaia-DR2 positions, proper motions, and parallaxes.
-They used Gaia photometry and radial velocities to verify the
-membership claims.  From their Table~2, we collect
-401{,}448 cluster members, in 1229 clusters, down to their limiting magnitude
-of $G=18$.
-
-\citet{gaia_hr_2018} reported members of a smaller, more
-select group of well-studied open clusters. From their Table~A1, we
-collect 40{,}903 cluster members, in 41 open clusters, mostly within
+assignment algorithm \citep{krone-martins_upmask_2014} to identify
+cluster members using Gaia-DR2 positions, proper motions, and
+parallaxes.  They used Gaia photometry and radial velocities to verify
+the membership claims.  From their Table~2, we collect 401{,}448
+cluster members, in 1229 clusters, down to their limiting magnitude of
+$G=18$.
+
+\citet{gaia_hr_2018} reported members of a smaller, more select group
+of well-studied open clusters. From their Table~A1, we collect
+40{,}903 cluster members, in 41 open clusters, mostly within
 $500\,{\rm pc}$. While this work also included memberships for
@@
 
-Given the high quality of Gaia-DR2 astrometry, these two
-membership sources are our most reliable sources of membership
-information.  In our photometric reduction,  our default identifier
-for all sources is correspondingly the Gaia-DR2 \texttt{source\_id}.
-The TESS Input Catalog (TIC) data for each target star are then collected
-using the Gaia-DR2 source identifier \citep{stassun_TIC_2018,stassun_TIC8_2019}.
-
-% We take this approach
-% because Gaia-DR2 is the base-catalog used to project sources from
-% celestial coordinates to the imaging plane (\S~\ref{sec:method}).  It
-% also has the advantage that for any Gaia-derived cluster memberships,
-% we can cross-match directly against source identifiers.
+Given the high quality of Gaia-DR2 astrometry, these two membership
+sources are our most reliable sources of membership information.  In
+our photometric reduction,  our default identifier for all sources is
+correspondingly the Gaia-DR2 \texttt{source\_id}.  The TESS Input
+Catalog (TIC) data for each target star are then collected using the
+Gaia-DR2 source identifier \citep{stassun_TIC_2018,stassun_TIC8_2019}.
+
+% We take this approach because Gaia-DR2 is the base-catalog used to
+% project sources from celestial coordinates to the imaging plane
+% (\S~\ref{sec:method}).  It also has the advantage that for any
+% Gaia-derived cluster memberships, we can cross-match directly
+% against source identifiers.
 
@@
 Gaia}-DR2 source identifiers for the members, we performed a
-crossmatch for Gaia-DR2 sources within 5 arcseconds of the
-listed positions.  To improve the quality of the cross-match, we
-used the 2MASS photometry to predict the $G$-band
-magnitudes\footnote{See
+crossmatch for Gaia-DR2 sources within 5 arcseconds of the listed
+positions.  To improve the quality of the cross-match, we used the
+2MASS photometry to predict the $G$-band magnitudes\footnote{See
 \url{https://gea.esac.esa.int/archive/documentation/GDR2/Data_processing/chap_cu5pho/sec_cu5pho_calibr/ssec_cu5pho_PhotTransf.html},
@@
 UCAC4 proper motions acquired by the US Naval Observatory
-\citep{zacharias_fourth_2013}.
-From their 1805 reported open clusters, we selected sources with
-quoted membership probability above 50\%.
-To obtain Gaia-DR2 source identifiers for the members, we
+\citep{zacharias_fourth_2013}.  From their 1805 reported open
+clusters, we selected sources with quoted membership probability above
+50\%.  To obtain Gaia-DR2 source identifiers for the members, we
 performed a similar crossmatch as before, looking for sources within 5
 arcseconds of the listed positions, and within $\pm$2 $G$-band
-magnitudes of the prediction.
-From 2{,}034{,}269 stars, this yielded a unique
-best neighbor for 1{,}828{,}630 stars (89.9\% of the sample), and a choice
-between two neighbors for 8.7\% of the remaining sample.
+magnitudes of the prediction.  From 2{,}034{,}269 stars, this yielded
+a unique best neighbor for 1{,}828{,}630 stars (89.9\% of the sample),
+and a choice between two neighbors for 8.7\% of the remaining sample.
 
@@
 Figure~\ref{fig:xmatch_info}.  The distances between matches is
-typically below 1 arcsecond.  The \citeauthor{dias_proper_2014} catalog shows stronger
-crowding effects at the faint end compared to the \citeauthor{Kharchenko_et_al_2013} catalog,
-and likely has a larger number of false matches.
-At their faint ends, both catalogs show a tendency for true $G$-band
-magnitudes to be larger than predicted $G$-band magnitudes,
-presumably due to dust reddening.
+typically below 1 arcsecond.  The \citeauthor{dias_proper_2014}
+catalog shows stronger crowding effects at the faint end compared to
+the \citeauthor{Kharchenko_et_al_2013} catalog, and likely has a
+larger number of false matches.  At their faint ends, both catalogs
+show a tendency for true $G$-band magnitudes to be larger than
+predicted $G$-band magnitudes, presumably due to dust reddening.
 
@@
 
-For the Gagn\'e et al{.}~catalogs, a large
-number of the stars have high proper motions.
-However, some of the stars do not have reported proper motions.
-To perform the cross-match,
-we searched the Gaia-DR2 archive for
-sources within 10 arcseconds of the listed positions (propagated to the
-Gaia-DR2 J2015.5 epoch, if the proper motions were available, otherwise
-simply using the listed J2000 positions).
-We also imposed a $G<18$ cut on any putative matches. 
-We then chose the nearest neighbor by spatial separation.
-Of 3012 moving group members collected from the
-three combined Gagn\'e et al{.}
-catalogs, this procedure yielded 2702 matches.
+For the Gagn\'e et al{.}~catalogs, a large number of the stars have
+high proper motions.  However, some of the stars do not have reported
+proper motions.  To perform the cross-match, we searched the Gaia-DR2
+archive for sources within 10 arcseconds of the listed positions
+(propagated to the Gaia-DR2 J2015.5 epoch, if the proper motions were
+available, otherwise simply using the listed J2000 positions).  We
+also imposed a $G<18$ cut on any putative matches.  We then chose the
+nearest neighbor by spatial separation.  Of 3012 moving group members
+collected from the three combined Gagn\'e et al{.} catalogs, this
+procedure yielded 2702 matches.
 
@@
 \citet{bell_32ori_2017} studies reported members in Tucana-Horologium,
-the Hyades, and 32$\,$Ori respectively.  Applying the same procedure as
-for the Gagn\'e catalogs gave 187, 684, and 119 matches
+the Hyades, and 32$\,$Ori respectively.  Applying the same procedure
+as for the Gagn\'e catalogs gave 187, 684, and 119 matches
 respectively, compared to 205, 724, and 141 initially reported
@@
 
-\citet{rizzuto_multidimensional_2011} focused on a single
-group: the Sco OB2 association. We used their reported Hipparcos
-identifiers, and matched against the {\it Gaia} archive's
+\citet{rizzuto_multidimensional_2011} focused on a single group: the
+Sco OB2 association. We used their reported Hipparcos identifiers, and
+matched against the {\it Gaia} archive's
 \texttt{hipparcos2\_best\_neighbour} table, which gave 319
@@
 
-\citet{oh_comoving_2017} searched for comoving stars in the
-$\approx$2 million stars that appear in both the Tycho-2 and {\it
-Gaia}-DR1 catalogs.  They found many wide binaries, and also identified a large
+\citet{oh_comoving_2017} searched for comoving stars in the $\approx$2
+million stars that appear in both the Tycho-2 and {\it Gaia}-DR1
+catalogs.  They found many wide binaries, and also identified a large
 number of comoving groups.  We chose the 2{,}134 stars that they
@@
 regions of the sky.  Though most of these stars are not directly
-identified with moving groups or open clusters, their reported
-youth and proximity to star
-forming regions justifies their inclusion in our search sample.
+identified with moving groups or open clusters, their reported youth
+and proximity to star forming regions justifies their inclusion in our
+search sample.
 
@@
 \delta, \mu_\alpha, \mu_\delta, \pi)$.  Finally, we required that
-$G_{\rm Rp} < 16$, which is roughly the level for which
-the 1-hour photometric
-precision of TESS is predicted to be 1\%
+$G_{\rm Rp} < 16$, which is roughly the level for which the 1-hour
+photometric precision of TESS is predicted to be 1\%
 \citep{ricker_transiting_2015}.
 
-The resulting CDIPS target star list, consisting of 1{,}061{,}447 unique stars from 13
-distinct catalogs, is given in
+The resulting CDIPS target star list, consisting of 1{,}061{,}447
+unique stars from 13 distinct catalogs, is given in
 Table~\ref{tbl:cdips_targets}.  The cumulative distribution of target
@@
 
-Figure~\ref{fig:cdips_targets} also shows
-the relative fraction of stars from each catalog.
-The largest number of stars come from \citealt{dias_proper_2014}
-(44.3\%), \citealt{Kharchenko_et_al_2013} (17.3\%),
-\citealt{cantat-gaudin_gaia_2018} (16.7\%), and \citealt{zari_3d_2018}
-(11.1\%, of which 7.8\% are OBA stars, and 3.3\% are pre-MS stars).
-107{,}647 of the stars, or about 10\%
-of the collection, have cluster memberships reported by multiple
-authors.  Since the membership probability calculations often use
-independent data and methods, agreement between multiple investigators
-on a given star's cluster membership is a helpful indication of it
-being a member.
-
-Different catalogs have different standards for deciding
-which stars are members.  For the
-\citet{dias_proper_2014} catalog, their membership calculation
-included only spatial and kinematic information, and we used a
-relatively low probability threshold when including their stars (based
-on the criteria \citealt{dias_proper_2014} used for their star
-counts).  The \citet{Kharchenko_et_al_2013} catalog combined spatial,
-kinematic, and photometric information to derive their membership
-probabilities.  We also used a more restrictive membership
-probability cut (again, following the criteria they used for their
-star counts), and so this sub-sample is likely less contaminated
-with field interlopers.
+Figure~\ref{fig:cdips_targets} also shows the relative fraction of
+stars from each catalog.  The largest number of stars come from
+\citealt{dias_proper_2014} (44.3\%), \citealt{Kharchenko_et_al_2013}
+(17.3\%), \citealt{cantat-gaudin_gaia_2018} (16.7\%), and
+\citealt{zari_3d_2018} (11.1\%, of which 7.8\% are OBA stars, and
+3.3\% are pre-MS stars).  107{,}647 of the stars, or about 10\% of the
+collection, have cluster memberships reported by multiple authors.
+Since the membership probability calculations often use independent
+data and methods, agreement between multiple investigators on a given
+star's cluster membership is a helpful indication of it being a
+member.
+
+Different catalogs have different standards for deciding which stars
+are members.  For the \citet{dias_proper_2014} catalog, their
+membership calculation included only spatial and kinematic
+information, and we used a relatively low probability threshold when
+including their stars (based on the criteria
+\citealt{dias_proper_2014} used for their star counts).  The
+\citet{Kharchenko_et_al_2013} catalog combined spatial, kinematic, and
+photometric information to derive their membership probabilities.  We
+also used a more restrictive membership probability cut (again,
+following the criteria they used for their star counts), and so this
+sub-sample is likely less contaminated with field interlopers.
 \citet{cantat-gaudin_gaia_2018} used spatial, kinematic, and
-astrometric information from Gaia-DR2. Despite the lack of
-photometric information, the quality of the Gaia data suggest that the
-field contamination rate will be lowest for the
+astrometric information from Gaia-DR2. Despite the lack of photometric
+information, the quality of the Gaia data suggest that the field
+contamination rate will be lowest for the
 \citet{cantat-gaudin_gaia_2018} sample.
@@
 \citet{Kharchenko_et_al_2013} whenever possible.
-Appendix~\ref{appendix:uniquenames} describes  how this was done in detail.
-For moving groups not identified by \citet{Kharchenko_et_al_2013}, we used
-the constellation-based naming convention from
-\citet{gagne_banyan_XI_2018}.  Otherwise, we used the name reported by
-the original catalog claiming membership.  This process reduced 16,425
-name variants down to 3,216 unique cluster names.  Though we have
-made every effort to avoid duplicates, a small number may remain, so we
-advise inspection of the \texttt{cluster} column
-as well as the references given in the
-\texttt{reference} column rather than using the
-\texttt{unique\_cluster\_name} column to analyze individual objects
-of interest.  Nonetheless, 87.7\% of the $\sim$million unique target
-stars are matched to clusters named by \citet{Kharchenko_et_al_2013},
-and 88.8\% are assigned a cluster name.  The remainder are mostly the
-young stars from \citet{zari_3d_2018}.
-Ages and their uncertainties were then assigned using the 
-parameters reported by \citet{Kharchenko_et_al_2013}.
+Appendix~\ref{appendix:uniquenames} describes  how this was done in
+detail.  For moving groups not identified by
+\citet{Kharchenko_et_al_2013}, we used the constellation-based naming
+convention from \citet{gagne_banyan_XI_2018}.  Otherwise, we used the
+name reported by the original catalog claiming membership.  This
+process reduced 16,425 name variants down to 3,216 unique cluster
+names.  Though we have made every effort to avoid duplicates, a small
+number may remain, so we advise inspection of the \texttt{cluster}
+column as well as the references given in the \texttt{reference}
+column rather than using the \texttt{unique\_cluster\_name} column to
+analyze individual objects of interest.  Nonetheless, 87.7\% of the
+$\sim$million unique target stars are matched to clusters named by
+\citet{Kharchenko_et_al_2013}, and 88.8\% are assigned a cluster name.
+The remainder are mostly the young stars from \citet{zari_3d_2018}.
+Ages and their uncertainties were then assigned using the parameters
+reported by \citet{Kharchenko_et_al_2013}.
 
@@
         {\it Bottom right}. Zoom of difference image.
-        Each image is $(2048\times2048)$ pixels, except for the bottom-right 
-        image, which is $(500\times500)$.
-        All images except the top-right have the same color map.
-        The sector, camera, and CCD are (6, 1, 2).
+        Each image is $(2048\times2048)$ pixels, except for the
+        bottom-right image, which is $(500\times500)$.  All images
+        except the top-right have the same color map.  The sector,
+        camera, and CCD are (6, 1, 2).
         \label{fig:stages_good}
@@
     \caption{
-        Same sector, camera and CCD as Figure~\ref{fig:stages_good}, but for an image obtained during
-        perigee passage, when scattered light from the Earth is
-        prominent.
-        A number of systematic artifacts are present,
-        including vertical ``straps'' and small-scale structure in scattered light
-        patches.
-        The quality of astrometric registration in the difference image is also
-        worse, leading to larger residuals in the lower-right panel.
+        Same sector, camera and CCD as Figure~\ref{fig:stages_good},
+        but for an image obtained during perigee passage, when
+        scattered light from the Earth is prominent.  A number of
+        systematic artifacts are present, including vertical
+        ``straps'' and small-scale structure in scattered light
+        patches.  The quality of astrometric registration in the
+        difference image is also worse, leading to larger residuals in
+        the lower-right panel.
         \label{fig:stages_bad}
@@
 
-To reduce the TESS images to light curves, we adopted a
-difference imaging approach.  The overall method is in the spirit of the
+To reduce the TESS images to light curves, we adopted a difference
+imaging approach.  The overall method is in the spirit of the
 pipelines developed by \citet{Pal_2009},
-\citet{huang_high-precision_2015}, \citet{soares-furtado_image_2017}, \citet{oelkers_precision_2018} and \citet{wallace_search_2019}.
-Figure~\ref{fig:pipeline} shows a conceptual overview of
-our pipeline.  Most modules have been
-developed over the past decade to reduce
-images taken by the Hungarian Automated Telescope (HAT) network \citep{bakos_hat_review_2018}.
-The work of \citet{Pal_2009}, embodied in the \texttt{fitsh} software package,
-was an especially crucial component.
-The specific high-level framework
-we used for this reduction was adapted from a pipeline called
-\texttt{pipe-trex}, under development primarily for the HATPI project
-(\url{hatpi.org}).  The code is available
+\citet{huang_high-precision_2015}, \citet{soares-furtado_image_2017},
+\citet{oelkers_precision_2018} and \citet{wallace_search_2019}.
+Figure~\ref{fig:pipeline} shows a conceptual overview of our pipeline.
+Most modules have been developed over the past decade to reduce images
+taken by the Hungarian Automated Telescope (HAT) network
+\citep{bakos_hat_review_2018}.  The work of \citet{Pal_2009}, embodied
+in the \texttt{fitsh} software package, was an especially crucial
+component.  The specific high-level framework we used for this
+reduction was adapted from a pipeline called \texttt{pipe-trex}, under
+development primarily for the HATPI project (\url{hatpi.org}).  The
+code is available
 online\footnote{\url{github.com/waqasbhatti/pipe-trex}, commit
@@
 collected from these initial steps, we select an astrometric reference
-frame to which we transform all of the calibrated images. 
-To construct a photometric reference frame,
-we first convolve a subset of the frames to have identical stellar profiles,
-and then stack them. Finally, we subtract each target frame
-from the photometric reference frame (\S~\ref{subsec:imagesubtraction}).  We
-perform aperture photometry on the subtracted images using positions
-projected onto the frame from the Gaia-DR2 source catalog.  
-The resulting differential flux measurements are converted to total flux measurements using photometric information from Gaia-DR2 to estimate the total flux of each source on the reference image.
-We detrend
-the resulting light curves (\S~\ref{subsec:lcdetrending}).  The
-resulting white noise and red noise properties of the light curves,
-and a few interesting cases of variability, are discussed in
-\S~\ref{sec:results}.
+frame to which we transform all of the calibrated images.  To
+construct a photometric reference frame, we first convolve a subset of
+the frames to have identical stellar profiles, and then stack them.
+Finally, we subtract each target frame from the photometric reference
+frame (\S~\ref{subsec:imagesubtraction}).  We perform aperture
+photometry on the subtracted images using positions projected onto the
+frame from the Gaia-DR2 source catalog.  The resulting differential
+flux measurements are converted to total flux measurements using
+photometric information from Gaia-DR2 to estimate the total flux of
+each source on the reference image.  We detrend the resulting light
+curves (\S~\ref{subsec:lcdetrending}).  The resulting white noise and
+red noise properties of the light curves, and a few interesting cases
+of variability, are discussed in \S~\ref{sec:results}.
 
@@
 \label{subsec:observations}
-
-% How did TESS observe?
-% What processing steps happened in order to get the calibrated frames?
-% Why did we choose to start with them?
 
@@
 $\approx$$28$ degrees east in ecliptic longitude every lunar month.
-Data acquired throughout each one-month ``sector'' are downlinked at spacecraft
-perigee through the Deep Space Network.  Descriptions of the
-spacecraft's design and operations are given by
-\citet{ricker_transiting_2015} and
-\citet{vanderspek_2018}.
+Data acquired throughout each one-month ``sector'' are downlinked at
+spacecraft perigee through the Deep Space Network.  Descriptions of
+the spacecraft's design and operations are given by
+\citet{ricker_transiting_2015} and \citet{vanderspek_2018}.
 
 For us, the main data product of interest is the calibrated full frame
-image (FFI).  Each TESS camera is read out every 2 seconds.  
-The resulting pixel values are
-averaged by the onboard computer into 30 minute exposures. An on-board
-cosmic ray mitigation algorithm is applied \citep[][\S
-5.1]{vanderspek_2018}. Once transmitted to the ground, the raw images
-are calibrated by the Science Processing Operations Center (SPOC).  The
-calibration process includes an overscan, bias, and dark current
-correction, and also divides out a flat field.  Details are discussed
-by \citet{clarke_kepler_2017}, and the resulting science data products
-are described by \citet{tess_data_product_description_2018}.
+image (FFI).  Each TESS camera is read out every 2 seconds.  The
+resulting pixel values are averaged by the onboard computer into 30
+minute exposures. An on-board cosmic ray mitigation algorithm is
+applied \citep[][\S 5.1]{vanderspek_2018}. Once transmitted to the
+ground, the raw images are calibrated by the Science Processing
+Operations Center (SPOC).  The calibration process includes an
+overscan, bias, and dark current correction, and also divides out a
+flat field.  Details are discussed by \citet{clarke_kepler_2017}, and
+the resulting science data products are described by
+\citet{tess_data_product_description_2018}.
 
@@
 
-Sectors 1--5 mainly covered portions of the sky away from
-the galactic plane.  Consequently, fewer than 2\% of the CDIPS target stars
-were observed in the first five TESS sectors.  Although a few
-interesting clusters are present in these observations ({\it e.g.},
-Blanco~1, NGC~2516, NGC~1901), for the present work we opted to focus
-on Sectors 6 \& 7, for which there were more stars of interest.
-These begin in Sector 6 (2018-12-12, spacecraft orbit \#19),
-and conclude at the end of Sector 7
-(2019-02-01, spacecraft orbit \#22).
-Sectors 6 and 7 cover galactic longitudes from roughly 200$^\circ$ to 280$^\circ$, 
+Sectors 1--5 mainly covered portions of the sky away from the galactic
+plane.  Consequently, fewer than 2\% of the CDIPS target stars were
+observed in the first five TESS sectors.  Although a few interesting
+clusters are present in these observations ({\it e.g.}, Blanco~1,
+NGC~2516, NGC~1901), for the present work we opted to focus on Sectors
+6 \& 7, for which there were more stars of interest.  These begin in
+Sector 6 (2018-12-12, spacecraft orbit \#19), and conclude at the end
+of Sector 7 (2019-02-01, spacecraft orbit \#22).  Sectors 6 and 7
+cover galactic longitudes from roughly 200$^\circ$ to 280$^\circ$,
 with coverage within $\pm 20^\circ$ of the galactic plane
@@
 Before we can perform any kind of photometry, a few janitorial tasks
-are required.
-First, we convert the multi-extension calibrated FITS image from MAST
-into a single-extension FITS image, and trim the image to remove virtual rows
-and columns using the \texttt{SCIROWS}, \texttt{SCIROWE},
-\texttt{SCCSA}, and \texttt{SCCED} header values.
-
-In order to account for the background variations present in
-some frames due to scattered light from the Earth and Moon
-\citep[see][\S 7.3.1--7.3.4]{vanderspek_2018}, we determine and
-subtract a model of the large-scale background.  We do this by temporarily
-masking out pixels more than $2\sigma$ from the image median, and then
-pass a $48\times48$ median box filter over each pixel in the image,
-with reflective boundary conditions.  The resulting background
-estimate has low-amplitude structure over spatial scales of a few
-pixels. We then blur the model image with a gaussian kernel of size 48 pixels,
-which produces a smooth
-background estimate.  These steps also remove
-low-level vignetting in the corners of many images, which
-remains even after flat-fielding \citep[see][\S
-7.3.5]{vanderspek_2018}.  
-The results are shown in the upper four panels of Figures~\ref{fig:stages_good}
-and~\ref{fig:stages_bad}.
-Features with spatial scales smaller than $\approx$48 pixels remain, 
-but large scale patterns of scattered light are removed.
+are required.  First, we convert the multi-extension calibrated FITS
+image from MAST into a single-extension FITS image, and trim the image
+to remove virtual rows and columns using the \texttt{SCIROWS},
+\texttt{SCIROWE}, \texttt{SCCSA}, and \texttt{SCCED} header values.
+
+In order to account for the background variations present in some
+frames due to scattered light from the Earth and Moon \citep[see][\S
+7.3.1--7.3.4]{vanderspek_2018}, we determine and subtract a model of
+the large-scale background.  We do this by temporarily masking out
+pixels more than $2\sigma$ from the image median, and then pass a
+$48\times48$ median box filter over each pixel in the image, with
+reflective boundary conditions.  The resulting background estimate has
+low-amplitude structure over spatial scales of a few pixels. We then
+blur the model image with a gaussian kernel of size 48 pixels, which
+produces a smooth background estimate.  These steps also remove
+low-level vignetting in the corners of many images, which remains even
+after flat-fielding \citep[see][\S 7.3.5]{vanderspek_2018}.  The
+results are shown in the upper four panels of
+Figures~\ref{fig:stages_good} and~\ref{fig:stages_bad}.  Features with
+spatial scales smaller than $\approx$48 pixels remain, but large scale
+patterns of scattered light are removed.
 
@@
 After subtracting the background, we mask out saturated pixels using a
-fixed saturation level of $8\times10^4$ analog-to-digital units (ADU). This value was
-chosen based on the onset of bleeding charge trails in the images, and
-is slightly greater than the saturation level of $2\times10^5$
-electrons, or about $4\times10^4\,{\rm ADU}$, reported by
-\citet{vanderspek_2018}. 
-As a consequence, we do not analyze stars brighter than $T\approx 6.5$.
-As described by \citet{Pal_2009}, the pixel masks are metadata attached
-to the image file, and are only applied to the pixel values during the specific
-image processing steps in which they are necessary ({\it e.g.},
-convolution). We also extend the masks beyond purely saturated pixels
-to ``bloomed'' pixels horizontally and vertically adjacent to the
-saturated pixels (see Figure~6 of \citealt{Pal_2009}).
+fixed saturation level of $8\times10^4$ analog-to-digital units (ADU).
+This value was chosen based on the onset of bleeding charge trails in
+the images, and is slightly greater than the saturation level of
+$2\times10^5$ electrons, or about $4\times10^4\,{\rm ADU}$, reported
+by \citet{vanderspek_2018}.  As a consequence, we do not analyze stars
+brighter than $T\approx 6.5$.  As described by \citet{Pal_2009}, the
+pixel masks are metadata attached to the image file, and are only
+applied to the pixel values during the specific image processing steps
+in which they are necessary ({\it e.g.}, convolution). We also extend
+the masks beyond purely saturated pixels to ``bloomed'' pixels
+horizontally and vertically adjacent to the saturated pixels (see
+Figure~6 of \citealt{Pal_2009}).
 
@@
 with anomalous spacecraft performance, which we omit from
-consideration.  This included three days at the
-beginning of Sector 6 dedicated to acquiring pixel response function
-data. There were no additional gaps in Sector 7.
+consideration.  This included three days at the beginning of Sector 6
+dedicated to acquiring pixel response function data. There were no
+additional gaps in Sector 7.
 %For Sectors 1 through 5, these
@@
     the vector from the measured to the projected star position.
-		Directions are correct, but lengths are 50 times their true size for 
-		visualization purposes.
-    The systematic error in the top-right corner is a typical
-    problem generic to wide-field astrometry.
-    The frame chosen for this plot is the photometric reference frame used 
-    for Sector 6, Camera 1, CCD 1; we automatically 
-    impose cutoffs on the median and $90^{\rm th}$ percentile of the 
-    astrometric residual in order to ensure similar levels of astrometric 
+    Directions are correct, but lengths are 50 times their true size
+    for visualization purposes.  The systematic error in the top-right
+    corner is a typical problem generic to wide-field astrometry.  The
+    frame chosen for this plot is the photometric reference frame used
+    for Sector 6, Camera 1, CCD 1; we automatically impose cutoffs on
+    the median and $90^{\rm th}$ percentile of the astrometric
+    residual in order to ensure similar levels of astrometric
     precision are maintained throughout the reduction.
@@
 
-First, we perform source extraction on the
-thousand or so brightest, non-saturated stars in each image.  
-This is done using a \texttt{fitsh} tool, \texttt{fistar}.
-We derive centroid positions for the stars, and
-simultaneously
-fit elliptical gaussians to their profiles, yielding the shape
-parameters $(s,d,k)$, where the flux $f$ as a function of position
-$(x,y)$ in the CCD image plane is assumed to take the form
+First, we perform source extraction on the thousand or so brightest,
+non-saturated stars in each image.  This is done using a
+\texttt{fitsh} tool, \texttt{fistar}.  We derive centroid positions
+for the stars, and simultaneously fit elliptical gaussians to their
+profiles, yielding the shape parameters $(s,d,k)$, where the flux $f$
+as a function of position $(x,y)$ in the CCD image plane is assumed to
+take the form
 \begin{align}
@@
 \end{align}
-for $(x_0,y_0)$ the central coordinates of the star,
-$\Delta x = x-x_0$, $\Delta y = y - y_0$, $B$ the background
-level, and $A$ an arbitrary
-flux-scaling constant.
-For a nearly circular shape profile, the sharpness $s$ is related to
-the FWHM as ${\rm FWHM} \approx 2.35s^{-1/2}$ \citep[{\it
-e.g.},][]{Pal_2009}.  These shape parameters are later used when
-selecting an astrometric reference frame
-(\S~\ref{subsec:imagesubtraction}).  
-In agreement with what is obvious upon visual inspection, this 
-fitting process shows that stars closer to the
-center of each camera's field are round, while
-stars near the field edges are more elongated.
+for $(x_0,y_0)$ the central coordinates of the star, $\Delta x =
+x-x_0$, $\Delta y = y - y_0$, $B$ the background level, and $A$ an
+arbitrary flux-scaling constant.  For a nearly circular shape profile,
+the sharpness $s$ is related to the FWHM as ${\rm FWHM} \approx
+2.35s^{-1/2}$ \citep[{\it e.g.},][]{Pal_2009}.  These shape parameters
+are later used when selecting an astrometric reference frame
+(\S~\ref{subsec:imagesubtraction}).  In agreement with what is obvious
+upon visual inspection, this fitting process shows that stars closer
+to the center of each camera's field are round, while stars near the
+field edges are more elongated.
 
 For the astrometric solution, we use the World Coordinate System (WCS)
-and fourth-order Simple Imaging Polynomial (SIP) coefficients
-derived by SPOC and included in the FFI headers
+and fourth-order Simple Imaging Polynomial (SIP) coefficients derived
+by SPOC and included in the FFI headers
 \citep[][Sec.~8]{pence_fits_2010}.  We explored the possibility of
@@
 positions) was consistently a factor of 1.5-2 times higher in our WCS
-solutions than in those given by SPOC.  This was perhaps because
-we did not develop a robust
-algorithm to select non-blended stars of intermediate brightness before
-measuring their positions.
+solutions than in those given by SPOC.  This was perhaps because we
+did not develop a robust algorithm to select non-blended stars of
+intermediate brightness before measuring their positions.
 %Nonetheless, we did find that extending the astrometric correction
@@
 With the resulting WCS information, we then project a source catalog
-onto each frame. 
-We use the
-projected positions of the sources to center the apertures in our
-photometry,
-rather than attempting to measure the positions.  Such
-``forced-aperture photometry'' is preferable to source
-extraction in the crowded fields that are central to this work.  The
-Gaia-DR2 epoch is J2015.5, so even the fastest-moving stars with
-proper motions of $\sim$$1\,{\rm arcsecond}\,{\rm yr}^{-1}$ are still
-well within one pixel of their predicted positions in the TESS images.
-The projection from catalog sky-coordinate positions to pixel
-coordinates is performed using an analog of the \texttt{wcs-rd2xy}
-program that performs the standard matrix algebra \citep{lang_2010}.
-The source catalog look-up is performed using
+onto each frame.  We use the projected positions of the sources to
+center the apertures in our photometry, rather than attempting to
+measure the positions.  Such ``forced-aperture photometry'' is
+preferable to source extraction in the crowded fields that are central
+to this work.  The Gaia-DR2 epoch is J2015.5, so even the
+fastest-moving stars with proper motions of $\sim$$1\,{\rm
+arcsecond}\,{\rm yr}^{-1}$ are still well within one pixel of their
+predicted positions in the TESS images.  The projection from catalog
+sky-coordinate positions to pixel coordinates is performed using an
+analog of the \texttt{wcs-rd2xy} program that performs the standard
+matrix algebra \citep{lang_2010}.  The source catalog look-up is
+performed using
 \texttt{gaia2read}\footnote{\url{github.com/samuelyeewl/gaia2read}}
@@
 
-For the source catalog itself, we initially planned to photometer all Gaia-DR2
-sources in each field down to a cutoff of $G_{Rp} < 16$.  However,
-for the galactic plane fields this produced an excessively
+For the source catalog itself, we initially planned to photometer all
+Gaia-DR2 sources in each field down to a cutoff of $G_{Rp} < 16$.
+However, for the galactic plane fields this produced an excessively
 large number of sources (millions of stars per
 $12^\circ\times12^\circ$ CCD).  We therefore limited our source
-catalog for each frame to be
-a combination of the CDIPS target stars ($G_{Rp} < 16$), and
-all Gaia-DR2 sources down to $G_{Rp} < 13$.  
-The latter set of stars are used for image processing and
-light curve detrending.
-
-Figure~\ref{fig:astromresid} displays the residual between
-the measured and projected stellar centroid
-positions for one photometric reference frame.
-The construction of this frame will be described shortly.
-The plot shows that the errors
-are typically largest in the corners of the image,
-where the non-linearity of the focal plane is most significant, and
-the corrections required by the SIP coefficients are largest.
-Also, the typical median precision of the WCS solution is a bit below
-0.1 pixels, and its $90^{\rm th}$ percentile is typically less than
-0.3 pixels.
-In our reduction,
-we therefore require
-that each frame's median residual and 90th percentile remain
-below 0.2 and 0.4
-pixels, respectively. If this constraint is not met, the reduction fails.
-This is an essential quality-control check for any forced-aperture
-photometry pipeline.
-%The distribution has a outlier tail of saturated stars which were
-%masked, and thus do not have measureable centroid positions.
-%The final sub-panel of Figure~\ref{fig:astrometricresidual} is a
-%sanity check on the location of the projected positions, and also
-%gives some context for our chosen aperture radii of 1, 1.5, and 2.25
-%pixels.
-
-Finally, to collect the metadata needed
-to select photometric reference frames,
-we perform
-aperture photometry on the
-bright stars.
-This task is
-performed by using \texttt{fiphot} to
-sum the counts inside 
-circular apertures centered on the projected stellar positions.
-The pixel weights are equal to the fraction of the pixel
-that falls within the circular aperture.  They are unity for pixels
-entirely within the aperture, and fractional along the aperture
-boundary. % (see \citealt{Pal_2009} Fig 17). 
-The background levels are measured in annuli surrounding
-the center of each aperture. 
-%The raw flux of the object after background removal is then
-%(\citealt{Pal_2009} Eq 65)
-%\begin{equation}
-%  f = \sum_{x,y} w_{x,y} (I_{x,y} - B) = f_{\rm total} - B r_0^2.
-%  \label{eq:simple_aperture_phot}
-%\end{equation}
-%The resulting measurements, for instance of the background level of
-%each aperture, and the number of stars with ``good'' photometry,
-%can then be used to assess the photometric quality of each frame.
+catalog for each frame to be a combination of the CDIPS target stars
+($G_{Rp} < 16$), and all Gaia-DR2 sources down to $G_{Rp} < 13$.  The
+latter set of stars are used for image processing and light curve
+detrending.
+
+Figure~\ref{fig:astromresid} displays the residual between the
+measured and projected stellar centroid positions for one photometric
+reference frame.  The construction of this frame will be described
+shortly.  The plot shows that the errors are typically largest in the
+corners of the image, where the non-linearity of the focal plane is
+most significant, and the corrections required by the SIP coefficients
+are largest.  Also, the typical median precision of the WCS solution
+is a bit below 0.1 pixels, and its $90^{\rm th}$ percentile is
+typically less than 0.3 pixels.  In our reduction, we therefore
+require that each frame's median residual and 90th percentile remain
+below 0.2 and 0.4 pixels, respectively. If this constraint is not met,
+the reduction fails.  This is an essential quality-control check for
+any forced-aperture photometry pipeline.
+
+Finally, to collect the metadata needed to select photometric
+reference frames, we perform aperture photometry on the bright stars.
+This task is performed by using \texttt{fiphot} to sum the counts
+inside circular apertures centered on the projected stellar positions.
+The pixel weights are equal to the fraction of the pixel that falls
+within the circular aperture.  They are unity for pixels entirely
+within the aperture, and fractional along the aperture boundary.  The
+background levels are measured in annuli surrounding the center of
+each aperture.
 
@@
 
-The core operation of ``classical'' image subtraction is to
-match a photometric reference image $R$ and a target image $I$ by computing
+The core operation of ``classical'' image subtraction is to match a
+photometric reference image $R$ and a target image $I$ by computing
 and applying a convolution kernel.  For ground-based data, this
@@
 kernel was further explored by \citet{bramich_new_2008}, who showed
-that using a linear combination of delta functions (also called
-a ``discrete kernel'') had advantages
-compared to a basis of gaussians.  We perform the convolution using
-\texttt{ficonv}, and opt for the implementation of Bramich's method
-(see \citealt{Pal_2009} \S~2.8).  The lower panels of
-Figure~\ref{fig:stages_good} show the procedure working well, and
-producing a ``clean'' difference image.  Figure~\ref{fig:stages_bad}
-shows what happens for an image taken when scattered light from the
-Earth causes the model image to be a poor fit to the target
-image.
+that using a linear combination of delta functions (also called a
+``discrete kernel'') had advantages compared to a basis of gaussians.
+We perform the convolution using \texttt{ficonv}, and opt for the
+implementation of Bramich's method (see \citealt{Pal_2009} \S~2.8).
+The lower panels of Figure~\ref{fig:stages_good} show the procedure
+working well, and producing a ``clean'' difference image.
+Figure~\ref{fig:stages_bad} shows what happens for an image taken when
+scattered light from the Earth causes the model image to be a poor fit
+to the target image.
 
@@
 
-To make the above high-level picture work, we need to select
-two ``reference frames'':
-(1) the astrometric reference frame; and (2) the photometric reference frame.
+To make the above high-level picture work, we need to select two
+``reference frames'': (1) the astrometric reference frame; and (2) the
+photometric reference frame.
 
@@
 annuli around the bright stars selected in
-\S~\ref{subsec:preparation}.  Finally, the astrometric reference
-frame needs to have a large
-number of detected sources (though the variance between TESS images was rather 
-small).  We sort the image
-using these metrics, and then select the astrometric reference frame from
+\S~\ref{subsec:preparation}.  Finally, the astrometric reference frame
+needs to have a large number of detected sources (though the variance
+between TESS images was rather small).  We sort the image using these
+metrics, and then select the astrometric reference frame from
 successive intersections of each sorted list.
@@
 translation~--~typically moves stars by less than a pixel, since the
-TESS spacecraft pointing is quite stable.  We calculate the transformation
-using the measured source positions found in
+TESS spacecraft pointing is quite stable.  We calculate the
+transformation using the measured source positions found in
 ~\S~\ref{subsec:metadatacollection}, and the symmetric triangle
 point-matching scheme described by \citet[][~\S~2.5.2]{Pal_2009}.
-This step is achieved using the \texttt{fitsh} tools \texttt{grmatch} and
-\texttt{grtrans}.  To help ensure the precision of the transformation,
-we require the ``unitarity'' $\Lambda$
+This step is achieved using the \texttt{fitsh} tools \texttt{grmatch}
+and \texttt{grtrans}.  To help ensure the precision of the
+transformation, we require the ``unitarity'' $\Lambda$
 \citep[][~Eq.~54]{Pal_2009}, which characterizes the degree of
@@
 
-The second required reference frame is the photometric reference frame,
-which is used both to calculate the convolution kernel, and to obtain
-a reference flux for each star.  To make it, we first choose 50 images
-with low background measurements (measured for each frame from the
-annuli around bright stars), and only consider frames with a
+The second required reference frame is the photometric reference
+frame, which is used both to calculate the convolution kernel, and to
+obtain a reference flux for each star.  To make it, we first choose 50
+images with low background measurements (measured for each frame from
+the annuli around bright stars), and only consider frames with a
 relatively large number of detected bright objects.  We then convolve
 these candidate photometric reference frames to the frame with the
-lowest background measurement, and construct the photometric
-reference as the median image across the 50 frame stack.
-
-Measuring the reference flux for each star is a non-trivial
-operation.  First, we perform forced simple aperture photometry on the
-photometric reference frame to measure the flux for each source.  The
-local background is estimated in annuli, with neighboring stars masked
-out during the background measurement.  If we were to stop
-here, {\it it would be a mistake}.  The reference fluxes for faint
-stars would be overestimated, due to crowding.  The relative amplitude
-of photometric signals for faint stars would correspondingly be biased
-to lower values.
+lowest background measurement, and construct the photometric reference
+as the median image across the 50 frame stack.
+
+Measuring the reference flux for each star is a non-trivial operation.
+First, we perform forced simple aperture photometry on the photometric
+reference frame to measure the flux for each source.  The local
+background is estimated in annuli, with neighboring stars masked out
+during the background measurement.  If we were to stop here, {\it it
+would be a mistake}.  The reference fluxes for faint stars would be
+overestimated, due to crowding.  The relative amplitude of photometric
+signals for faint stars would correspondingly be biased to lower
+values.
 
 To avoid this problem, after performing simple aperture photometry on
-the reference frame, we fitted a line between the Gaia-DR2
-magnitude of each star, and its measured flux.  The TESS $T$-band magnitude
-was calculated according to Equation~1 of \citet{stassun_TIC8_2019}.
-We then use the known catalog magnitude to predict the expected
-reference flux for each star.  This accounts for crowding down to Gaia's
+the reference frame, we fitted a line between the Gaia-DR2 magnitude
+of each star, and its measured flux.  The TESS $T$-band magnitude was
+calculated according to Equation~1 of \citet{stassun_TIC8_2019}.  We
+then use the known catalog magnitude to predict the expected reference
+flux for each star.  This accounts for crowding down to Gaia's
 resolution limit of $\approx$1$''$, rather than the TESS limit of
@@
 
-The final instrumental flux
-values $f$ we report are given by \citep[][Equation~83]{Pal_2009} 
+The final instrumental flux values $f$ we report are given by
+\citep[][Equation~83]{Pal_2009} 
 \begin{align}
@@
 $T_{\rm cat}$, and returns the reference flux.  Its coefficients are
-found independently for each
-aperture.  The difference image $D$ is equal to $I -  (R\otimes K)$,
-where as in Equation~\ref{eq:imagemodel}, $I$ is the target image
-transformed to the astrometric reference, $R$ is the photometric
-reference, and $K$ is the convolution kernel.  The weights $w$ from
-the circular aperture mask are included in the convolution.  The norm
-$|| K ||_1$ is defined by \citet{Pal_2009}~Equation~81.
+found independently for each aperture.  The difference image $D$ is
+equal to $I -  (R\otimes K)$, where as in
+Equation~\ref{eq:imagemodel}, $I$ is the target image transformed to
+the astrometric reference, $R$ is the photometric reference, and $K$
+is the convolution kernel.  The weights $w$ from the circular aperture
+mask are included in the convolution.  The norm $|| K ||_1$ is defined
+by \citet{Pal_2009}~Equation~81.
 
@@
 
-To solve for the coefficients $c_i$ of the convolution kernel, a
-few further assumptions are necessary.  The procedure implemented in
+To solve for the coefficients $c_i$ of the convolution kernel, a few
+further assumptions are necessary.  The procedure implemented in
 \texttt{ficonv} is to subdivide the image, and within each grid
@@
 kernel, by minimizing Equation~\ref{eq:chisq_conv} over the sum of all
-stamps.  For the kernel basis, we use a linear combination of
-delta functions with a flux scaling term
+stamps.  For the kernel basis, we use a linear combination of delta
+functions with a flux scaling term
 (\citealt{soares-furtado_image_2017} Section 3.3.1 gives the
@@
 
-%NOTE : this is kind of incomprehensible
-%CHECK: does the polynomial weighting actually do what you want it to do?
-
-This kernel model has three parameters that must be
-specified, but are not automatically optimized by the procedure: (1) the box-size; 
-(2) the maximum order of the polynomial weighting the delta
-function terms; (3) the maximum order of the polynomial weighting the
-flux scaling.  We performed a grid-search to tune these parameters, in
-which our ``loss functions'' were the light curve standard deviation (RMS)
-as a function of magnitude, and the recovered SNR of transits from the catalog
-of known TOIs (TESS Objects of Interest; N.~Guerrero, in prep).
+This kernel model has three parameters that must be specified, but are
+not automatically optimized by the procedure: (1) the box-size; (2)
+the maximum order of the polynomial weighting the delta function
+terms; (3) the maximum order of the polynomial weighting the flux
+scaling.  We performed a grid-search to tune these parameters, in
+which our ``loss functions'' were the light curve standard deviation
+(RMS) as a function of magnitude, and the recovered SNR of transits
+from the catalog of known TOIs (TESS Objects of Interest; N.~Guerrero,
+in prep).
 
@@
 stars.  The largest kernels, of $(11\times11)$ pixels, returned
-slightly lower signal-to-noise for recovered transits than kernels
-of intermediate size.  We settled on a kernel box-size of $(7\times7)$
-pixels, which is $\approx$2 times larger than the typical TESS FWHM
-at field center.
+slightly lower signal-to-noise for recovered transits than kernels of
+intermediate size.  We settled on a kernel box-size of $(7\times7)$
+pixels, which is $\approx$2 times larger than the typical TESS FWHM at
+field center.
 
@@
 range of optimal aperture sizes reported by
-\citet{Sullivan_et_al_2015}.  Finally,
-to convert from a list of flux measurements for each source on a frame
-to light curves, we used the
+\citet{Sullivan_et_al_2015}.  Finally, to convert from a list of flux
+measurements for each source on a frame to light curves, we used the
 \texttt{fitsh} transposition tool \texttt{grcollect}.
@@
 \citealt{kovacs_trend_2005}), and {\it (ii)} a principal component
-analysis (PCA, see {\it e.g.}, \citealt{ivezic_statistics_2014} for a review).
+analysis (PCA, see {\it e.g.}, \citealt{ivezic_statistics_2014} for a
+review).
 
@@
 In such cases, an effective model of the systematics comes from
-constructing a set of basis vectors that empirically captures trends common
-to many stars.  Each target light curve is then assumed to be a linear
-combination of the trend vectors.
+constructing a set of basis vectors that empirically captures trends
+common to many stars.  Each target light curve is then assumed to be a
+linear combination of the trend vectors.
 
@@
 
-We opted to use two different detrending approaches, each aimed
-at a different use case.  For transit-search related science,
-we used TFA, as implemented in \texttt{VARTOOLS}
+We opted to use two different detrending approaches, each aimed at a
+different use case.  For transit-search related science, we used TFA,
+as implemented in \texttt{VARTOOLS}
 \citep{kovacs_trend_2005,Hartman_Bakos_2016}.  For stellar
@@
 When trying to find periodic signals, $A(i)$ represents our prior
-knowledge of the light curve's shape.  Initially, this prior is simply that stars
-on average maintain a constant brightness:
+knowledge of the light curve's shape.  Initially, this prior is simply
+that stars on average maintain a constant brightness:
 \begin{equation}
@@
 stars have intermediate brightness ($8.5 > T > 13$), and have a
-relatively large number of time-series data points.  
-We excluded templates within 20 pixels of any given target star.
-We then performed
-an initial iteration of TFA, on only the candidate template stars.  We
-inspected the resulting detrended light curves for residual structure
-by computing a Lomb-Scargle periodogram.  If the maximum-power peak
-had a false alarm probability below 0.1\%, we excluded the star from
-the list of candidate template stars, on the basis of its presumed
-periodic variability.  We then randomly selected at most 200 template
-stars from the remaining non-variable candidates.  The choice of
-number of template stars was discussed by \citet{kovacs_trend_2005},
-and is another free parameter in the broad problem of light curve
-production.  This choice is analogous to the issue of how many
-cotrending basis vectors to choose in PDC-MAP or ARC2
-\citep{aigrain_robust_2017}.  While the number of template stars can
-be optimized by constructing and minimizing a BIC-like quantity, a
+relatively large number of time-series data points.  We excluded
+templates within 20 pixels of any given target star.  We then
+performed an initial iteration of TFA, on only the candidate template
+stars.  We inspected the resulting detrended light curves for residual
+structure by computing a Lomb-Scargle periodogram.  If the
+maximum-power peak had a false alarm probability below 0.1\%, we
+excluded the star from the list of candidate template stars, on the
+basis of its presumed periodic variability.  We then randomly selected
+at most 200 template stars from the remaining non-variable candidates.
+The choice of number of template stars was discussed by
+\citet{kovacs_trend_2005}, and is another free parameter in the broad
+problem of light curve production.  This choice is analogous to the
+issue of how many cotrending basis vectors to choose in PDC-MAP or
+ARC2 \citep{aigrain_robust_2017}.  While the number of template stars
+can be optimized by constructing and minimizing a BIC-like quantity, a
 little overfitting is acceptable for our pupose of finding planetary
@@
 {\it e.g.}, stellar rotation signals, we adopted a simple variant of
-PCA.
-A similar approach was taken by \citet{feinstein_eleanor_2019} in
-\texttt{eleanor}.  We derived the principal components for each CCD
+PCA.  A similar approach was taken by \citet{feinstein_eleanor_2019}
+in \texttt{eleanor}.  We derived the principal components for each CCD
 using the 200 template stars previously selected for TFA.  We then
 modelled each target light curve as a linear combination of a subset
-of these principal components, and determined the weights via linear least
-squares. Both steps were performed using \texttt{scikit-learn}
+of these principal components, and determined the weights via linear
+least squares. Both steps were performed using \texttt{scikit-learn}
 \citep{sklearn_2011}.
@@
 To determine the number of principal components at which to truncate
-the model, we
-performed a cross-validation analysis.
-Again, this was achieved using \texttt{scikit-learn}.
-As is typically the case when the noise variance is
-different for each ``feature'' (each point in time), we found that
-$k$-folding cross-validation of the PCA components
-gave a cross-validation score that monotonically increased with
-an increasing 
-number of components\footnote{See for example
+the model, we performed a cross-validation analysis.  Again, this was
+achieved using \texttt{scikit-learn}.  As is typically the case when
+the noise variance is different for each ``feature'' (each point in
+time), we found that $k$-folding cross-validation of the PCA
+components gave a cross-validation score that monotonically increased
+with an increasing number of components\footnote{See for example
 \url{https://scikit-learn.org/stable/auto_examples/decomposition/plot_pca_vs_fa_model_selection.html}
- (2019/08/06).}.
-We found that if we instead performed a factor analysis, the
-cross-validation
-score was typically maximized with anywhere from $10$ to $15$ components.
-This agreed with a
-visual analysis of the number of PCA components past which overfitting
-began.  We therefore used the maximum cross-validation score from
-the factor analysis as the number of principal components to use in
-each light curve.  This number is documented in the \texttt{FITS}
-header of each light curve.
+(2019/08/06).}.  We found that if we instead performed a factor
+analysis, the cross-validation score was typically maximized with
+anywhere from $10$ to $15$ components.  This agreed with a visual
+analysis of the number of PCA components past which overfitting began.
+We therefore used the maximum cross-validation score from the factor
+analysis as the number of principal components to use in each light
+curve.  This number is documented in the \texttt{FITS} header of each
+light curve.
 
 While the PCA detrending should help remove the most egregious
-systematic artifacts, it remains possible that PCA can distort signals,
-and even inject correlated noise into a light curve ({\it e.g.}, Figure~\ref{fig:lc_systematics_dtr}).
-For any object of interest, it is worth inspecting the raw, PCA, and TFA
-light curves to ensure
-that the variability of interest is not adversely affected by the
-detrending procedures.
-If it is, alternative approaches may be necessary.
-
-% In \S~\ref{sec:flux_vs_external_parameters}, we describe the
-% ``external parameter'' dependence visible in our reduction of
-% the TESS data.
-% Ordinary linear model-fitting, as well as an initial attempts
-% at non-linear model fitting, are poor descriptions of the data.  
-% In a similar vein ``magnitude-fitting'' is minimally justified, given
-% how the TESS magnitudes correlate against these external parameters.
-% We go on to show (\S~\ref{sec:tfa_is_good_enough}) that a plausible
-% detrending approach for the purpose of transit discovery is to simply
-% decorrelate against other nearby stars with standard TFA.
-%
-
-% \subsubsection{Flux versus external parameters}
-% \label{sec:flux_vs_external_parameters}
-% 
-% 
-% % \begin{figure*}[t]
-% %     \begin{center}
-% % 		\includegraphics[height=0.9\textheight]{mag_vs_epdparams.png}
-% %     \end{center}
-% %     \vspace{-0.5cm}
-% %     \caption{
-% %       {\bf Flux as a function of ``external parameters'' for four
-% %       representative stars.} The left two columns are stars at the
-% %       corner of a camera's field; the right two columns are from the
-% %       centers.
-% %       Each row shows a different parameter along the $x$-axis, given
-% %       in text at the bottom right of each subplot.
-% %       ``Hooks'' are common features in flux as a function of
-% %       temperature and centroid position.
-% %       \S~\ref{sec:flux_vs_external_parameters} gives a verbose
-% %       description.
-% %      \label{fig:flux_vs_external_parameters}
-% %     }
-% % \end{figure*}
-% 
-% The traditional approach to EPD is to fit and
-% subtract a model for the magnitudes $m$ of the form
-% \begin{equation}
-%   m = {\rm const.} + \sum_i c_i \theta_i,
-%   \label{eq:classical_EPD}
-% \end{equation}
-% where $\vec{\theta}$ is a vector of parameters such as the shape
-% parameters $(s,d,k)$, their products $(s^2, s\cdot d, d^2, \ldots)$,
-% the temperature $T$ of the instrument or environment\footnote{ We used
-% the temperature from the on-chip aluminum-copper sensor measurements
-% included in the engineering
-% data: \url{archive.stsci.edu/missions/tess/engineering/}.  },
-% the centroid positions $(x,y)$, the fractional part of the
-% centroid positions $(\{x\},\{y\})$, and any other parameters that are
-% expected\footnote{ The fractional centroid positions might matter
-% because intra-pixel quantum efficiency variations could affect the
-% measured stellar brightness.  The varying temperature $T$ of the CCD
-% electronics might matter.  } to correlate strongly with the observed
-% flux.  The coefficients $c_i$ are calculated through linear
-% least-squares, and subtracted to produce ``EPD'' light curves.
-% 
-% The premise of this model is that the correlations between the
-% magnitudes and the external parameters are linear.  For ground-based
-% CCD data (e.g., HATNet, HATS, and Nikon DSLRs), \citet{bakos_2010} and
-% \citet{zhang_precision_2016} have verified that this model is a
-% good description to the data.
-% To discern whether such a model extends to the TESS data, we examined
-% scatter plots of each parameter, as a function of all the other
-% parameters.  We also examined plots of each parameter as a function of
-% time.  A few prominent trends were present.
-% 
-% \begin{enumerate}
-% 
-% \item {\it Flux vs.\ time}. Most of the light curves we examined showed a secular
-%     drift with amplitude $0.01\,{\rm mag}$ over the timescale of each
-%     orbit.  Sharper trends (``hooks'') at the beginning of each orbit
-%     seemed to be less prominent for stars at the corners of the fields
-%     than stars at the center.  The periodicity incurred by the
-%     2.5$\,{\rm day}$ momentum dumps was also noticeable in more of the
-%     light curves at the center of the field than at the corners.
-% 
-% \item {\it Flux vs.\ centroid positions}. The flux as a function of
-%   centroid position often showed non-linear ``hooks''
-%     %(see Figure \ref{fig:flux_vs_external_parameters}).
-%     Most of the data points from a given orbit reside at a given
-%     level, but about 10\% are in a tail. This was seen in light curves
-%     all across the TESS field of view.
-% 
-% \item {\it Flux vs.\ temperature} exhibited similar hooks, with most of
-%   the flux values residing at a particular level, and perhaps 10\%
-%     following a non-linear path (often resembling the Nike ``swoosh'')
-%     away from the bulk of points.
-% 
-% \item {\it Flux vs.\ shape parameters}.  For light curves in the corner
-%   of the field of view, similar hooks are present in flux {\it vs.}
-%     $(s,d,k)$, though the hooks are less sharp.  In the center of the
-%     field of view, gaussian ellipses are a better description of the
-%     flux {\it vs.} the shape parameters.
-%     
-% \end{enumerate}
-% 
-% Considering the timeseries of parameters other than flux 
-% (Figure~\ref{fig:external_parameter_timeseries}):
-% 
-% \begin{enumerate}
-% 
-% \item {\it Centroid positions vs\ time}.  The main variability in the
-%   centroid positions as a function of time is a secular drift, that is
-%     reset every orbit.  The 2.5 day momentum wheel dump is
-%     superimposed on this secular drift, and has smaller amplitude than
-%     the drift.
-% 
-% \item {\it Temperature vs.\ time}.  The main variability in temperature
-%   {\it vs.} time is a secular drift of the same timescale as that for
-%     the centroid positions timeseries.
-% 
-% \item {\it Shape parameters vs.\ time}.  The main variability in the
-%   shape parameters as a function of time is the 2.5 day momentum wheel
-%     dump periodicity, with hooks before each momentum dump.
-% 
-% \item {\it Background value vs.\ time}.  The background is typically stable, 
-% except when scattered light from the Earth or Moon enters the frame (visible 
-% towards the end of each orbit in 
-% Figure~\ref{fig:external_parameter_timeseries}).
-% 
-% \end{enumerate}
-% 
-% Given the characteristics of the variability, a linear model of the
-% form given in Equation~\ref{eq:classical_EPD} is not applicable.  To
-% fit out the correlations between flux and parameters which most
-% commonly exhibited ``hooks'', we explored fitting a parametric open
-% curve (an $N$-dimensional B-spline, \citealt{dierckx_curve_1996}) to
-% the flux, centroid positions, and temperatures simultaneously.  We
-% selected the number of knots through brute-force, by calculating
-% $\chi^2$ for the model fit over a grid of possible knots, and
-% minimizing the Bayesian Information Criterion.  Though this approach
-% showed some initial promise, even with ``optimal'' knot-selection (in
-% the BIC sense) it introduced undesirable residuals in the light curves,
-% and also distorted transits.
-% One thought that we did not try but may explore in future work
-% is to use the decorrelate against the scatter of the quartnerion 
-% time-series \citep{vanderburg_hr858_2019}.
-% 
-% Given these complications, for the time being we omit the step of
-% ``detrending'' as a function of external parameters. To
-% enable further exploration of the issue, we include all the necessary
-% vectors of {\it e.g.}, centroid positions, temperatures, and shape
-% parameters in our reported light curves.
+systematic artifacts, it remains possible that PCA can distort
+signals, and even inject correlated noise into a light curve ({\it
+e.g.}, Figure~\ref{fig:lc_systematics_dtr}).  For any object of
+interest, it is worth inspecting the raw, PCA, and TFA light curves to
+ensure that the variability of interest is not adversely affected by
+the detrending procedures.  If it is, alternative approaches may be
+necessary.
 
@@
 \end{figure*}
-
-%\begin{figure}[!t]
-%	\begin{center}
-%		\leavevmode
-%		\includegraphics[width=0.47\textwidth]{sector6_cam[1]_ccd[1-2-3-4]cluster_field_star_positions.png}
-%	\end{center}
-%	\vspace{-0.5cm}
-%	\caption{
-%		{\bf  Zoom and coordinate transformation
-%			of Sector 6, Camera 1 from Figure~\ref{fig:lcgalactic}.}
-%		The most populated cluster is XXX, primarily due to candidate
-%		members proposed by \citet{dias_proper_2014}.
-%		\label{fig:lcradeczoom}
-%	}
-%\end{figure}
 
@@
 
-Figure~\ref{fig:lcgalactic} shows the on-sky locations of the 
-light curves from Sectors 6 and 7.  Black points are the field stars
-for which we performed photometry in order to construct
-basis vector sets for TFA and PCA.
-Blue points are the \numberlcs target stars for which light curves are available at
-\stscilink.  Most of the target stars are close to the galactic
-plane, and are spatially clustered. 
+Figure~\ref{fig:lcgalactic} shows the on-sky locations of the light
+curves from Sectors 6 and 7.  Black points are the field stars for
+which we performed photometry in order to construct basis vector sets
+for TFA and PCA.  Blue points are the \numberlcs target stars for
+which light curves are available at \stscilink.  Most of the target
+stars are close to the galactic plane, and are spatially clustered.
 Gaps between CCD chips are also visible.
@@
 main-sequence.  The latter set of OBA dwarf stars, while ``younger''
-than the typical field dwarf, are the least interesting subset
-of our target sample from the perspective of age analyses.  In the
-entire sample (Figure~\ref{fig:hrd} top), a much larger fraction of
-stars are sub-giants, red giants, and helium-burning red-clump stars.
+than the typical field dwarf, are the least interesting subset of our
+target sample from the perspective of age analyses.  In the entire
+sample (Figure~\ref{fig:hrd} top), a much larger fraction of stars are
+sub-giants, red giants, and helium-burning red-clump stars.
 
@@
 In Sector 6, \sVInumberlcs light curves of candidate cluster stars
-were made. The provenance of the target star for these
-sources is \citet{dias_proper_2014} for 40\% of the sources;
-\citet{zari_3d_2018} for 11\% of sources from their upper
-main-sequence table and 7\% of sources from their PMS table;
-\citet{Kharchenko_et_al_2013} for 18\% of sources;
-\citet{cantat-gaudin_gaia_2018} for 14\% of sources; and more than two
-catalogs for the remaining 10\% of sources.
+were made. The provenance of the target star for these sources is
+\citet{dias_proper_2014} for 40\% of the sources; \citet{zari_3d_2018}
+for 11\% of sources from their upper main-sequence table and 7\% of
+sources from their PMS table; \citet{Kharchenko_et_al_2013} for 18\%
+of sources; \citet{cantat-gaudin_gaia_2018} for 14\% of sources; and
+more than two catalogs for the remaining 10\% of sources.
 
@@
 Mamajek~3 (= 32$\,$Ori) similarly has only about 50 confirmed members
-\citep{bell_32ori_2017}.
-Some rich open clusters in the Sector 6 field with
-both many light curves and more reliable membership lists
-include Trumpler~5,
-Collinder~69 (the $\lambda$ Orionis cluster), and NGC~2287.
+\citep{bell_32ori_2017}.  Some rich open clusters in the Sector 6
+field with both many light curves and more reliable membership lists
+include Trumpler~5, Collinder~69 (the $\lambda$ Orionis cluster), and
+NGC~2287.
 
@@
 \paragraph{Observed RMS vs magnitude.}
-Figure~\ref{fig:rms_vs_mag} shows
-the standard deviation of the TFA-detrended light curves as
-a function of the catalog $T$-band magnitude for CDIPS target stars.
-For the $y$-axis of this plot, we have taken
+Figure~\ref{fig:rms_vs_mag} shows the standard deviation of the
+TFA-detrended light curves as a function of the catalog $T$-band
+magnitude for CDIPS target stars.  For the $y$-axis of this plot, we
+have taken
 \begin{equation}
@@
 where $f_i$ is the value of the flux at the $i^{\rm th}$ point in the
-time-series, $\bar{f}$ is the mean flux, $N$ is the
-number of points in the time-series, and $M$ is the number
-of template light curves (principal components) used during TFA (PCA) detrending.
-The correction in the denominator is for the overfitting inherent
-in any ensemble detrending method.
-
-The observed RMS (black points) follows the usual shape, with source photon
-noise dominating from $T=9$ to $T=12$, beyond which the onset of the
-``sky'' background changes the overall slope of the curve to be more
-steep.  For the brightest stars ($T\lesssim 9$), a ``systematic
-floor'' of 60$\,$ppm$\,$hr$^{1/2}$ was part of the mission's error budget
-\citep{ricker_transiting_2015}, but has not been observed in early
-reports of the photometric performance of various aperture photometry
-pipelines ({\it e.g.,} the SPOC pipeline \citealt{jenkins_spoc_2010},
-the MIT-QLP \citealt{huang_tess_2018}, and \texttt{eleanor}
-\citealt{feinstein_eleanor_2019}).  The fact that our light curves for
-the brightest stars are above this purported ``floor'', rather than
-below it, suggests that our image subtraction techniques could be
-introducing some small degree of noise to the light curves of the
-brightest stars.  It is also true however that our largest aperture
-contains only about 16 pixels, which is sub-optimal for stars brighter
-than $T\approx9$ \citep[see][Figure~14]{Sullivan_et_al_2015}.  Since
-the brightest stars are not the focus of the present work, we leave
-this issue unaddressed for the time being.
-
-An essential feature of our RMS diagram is that faint stars in
-crowded regions are not spuriously driven below theoretical limits.
-In aperture photometry pipelines, a star in a crowded region
-has its reference flux overestimated relative to the true number of 
-photons it contributes (due to contamination from neighbor stars).
-As a result, changes in relative flux in the faint star's light curve are 
-underestimated, and its RMS is driven low 
-\citep[{\it e.g.}, the faint end of][Figure~5]{feinstein_eleanor_2019}.
-Our method to work around this issue -- using the catalog magnitudes to 
-predict the reference flux values, and measuring deviations from these 
-reference fluxes on the subtracted images -- seems to be performing 
-as intended.
+time-series, $\bar{f}$ is the mean flux, $N$ is the number of points
+in the time-series, and $M$ is the number of template light curves
+(principal components) used during TFA (PCA) detrending.  The
+correction in the denominator is for the overfitting inherent in any
+ensemble detrending method.
+
+The observed RMS (black points) follows the usual shape, with source
+photon noise dominating from $T=9$ to $T=12$, beyond which the onset
+of the ``sky'' background changes the overall slope of the curve to be
+more steep.  For the brightest stars ($T\lesssim 9$), a ``systematic
+floor'' of 60$\,$ppm$\,$hr$^{1/2}$ was part of the mission's error
+budget \citep{ricker_transiting_2015}, but has not been observed in
+early reports of the photometric performance of various aperture
+photometry pipelines ({\it e.g.,} the SPOC pipeline
+\citealt{jenkins_spoc_2010}, the MIT-QLP \citealt{huang_tess_2018},
+and \texttt{eleanor} \citealt{feinstein_eleanor_2019}).  The fact that
+our light curves for the brightest stars are above this purported
+``floor'', rather than below it, suggests that our image subtraction
+techniques could be introducing some small degree of noise to the
+light curves of the brightest stars.  It is also true however that our
+largest aperture contains only about 16 pixels, which is sub-optimal
+for stars brighter than $T\approx9$
+\citep[see][Figure~14]{Sullivan_et_al_2015}.  Since the brightest
+stars are not the focus of the present work, we leave this issue
+unaddressed for the time being.
+
+An essential feature of our RMS diagram is that faint stars in crowded
+regions are not spuriously driven below theoretical limits.  In
+aperture photometry pipelines, a star in a crowded region has its
+reference flux overestimated relative to the true number of photons it
+contributes (due to contamination from neighbor stars).  As a result,
+changes in relative flux in the faint star's light curve are
+underestimated, and its RMS is driven low \citep[{\it e.g.}, the faint
+end of][Figure~5]{feinstein_eleanor_2019}.  Our method to work around
+this issue -- using the catalog magnitudes to predict the reference
+flux values, and measuring deviations from these reference fluxes on
+the subtracted images -- seems to be performing as intended.
 
@@
 The noise model shown in Figure~\ref{fig:rms_vs_mag} is quite similar
-to that of \citet{Sullivan_et_al_2015}, save for two changes.
-The first change is that the effective area of the telescope is
-updated to be $86.6\,{\rm cm}^2$, per the measurements by
+to that of \citet{Sullivan_et_al_2015}, save for two changes.  The
+first change is that the effective area of the telescope is updated to
+be $86.6\,{\rm cm}^2$, per the measurements by
 \citet{vanderspek_2018}.
 
-The second change is that we have explicitly included the
-estimated noise contribution from unresolved faint stars.  The
-brightness of the diffuse sky is dominated by different sources at
-different wavelengths.  For instance, the CMB is most important in
-the microwave, and thermal radiation from dust grains in the solar
-system (zodiacal light) is dominant in the far infra-red
+The second change is that we have explicitly included the estimated
+noise contribution from unresolved faint stars.  The brightness of the
+diffuse sky is dominated by different sources at different
+wavelengths.  For instance, the CMB is most important in the
+microwave, and thermal radiation from dust grains in the solar system
+(zodiacal light) is dominant in the far infra-red
 \citep{leinert_1997_1998}.  In the TESS-band, both zodiacal light and
@@
 plane, and the faint star background is brightest near the galactic
-plane.  
-When performing pre-launch noise estimates,
-\citet{winn_background_2013}
-estimated the photon-counts from each component.
-His zodiacal light model was presented by \citet{Sullivan_et_al_2015},
-but the faint star component was not emphasized since the Sullivan
-simulations were performed for fields away from the galactic plane.
+plane.  When performing pre-launch noise estimates,
+\citet{winn_background_2013} estimated the photon-counts from each
+component.  His zodiacal light model was presented by
+\citet{Sullivan_et_al_2015}, but the faint star component was not
+emphasized since the Sullivan simulations were performed for fields
+away from the galactic plane.
 
@@
 adopted explicitly because most of our target stars are near the
-galactic plane.
-Stars are judged to be ``unresolved'' and part of the background if
-their surface density exceeds the angular resolution of the telescope.
-TESS has an angular resolution of $\Delta \theta \sim 1'$, set by a
-combination of the pixel size as well as the typical stellar FWHM.
-Sources with sky surface density exceeding $\Delta \theta^{-2}$
-therefore contribute to the background.
-
-The relevant quantity needed to calculate the integrated 
-photon counts from faint sources
-is  $N(<m,l,b)$ --- the number of stars per square arcsecond
-brighter than magnitude $m$, along a line of sight with galactic
-longitude and latitude $(l,b)$.
-To calculate this surface density, \citet{winn_background_2013}
-queried the Besan\c con model
+galactic plane.  Stars are judged to be ``unresolved'' and part of the
+background if their surface density exceeds the angular resolution of
+the telescope.  TESS has an angular resolution of $\Delta \theta \sim
+1'$, set by a combination of the pixel size as well as the typical
+stellar FWHM.  Sources with sky surface density exceeding $\Delta
+\theta^{-2}$ therefore contribute to the background.
+
+The relevant quantity needed to calculate the integrated photon counts
+from faint sources is  $N(<m,l,b)$ --- the number of stars per square
+arcsecond brighter than magnitude $m$, along a line of sight with
+galactic longitude and latitude $(l,b)$.  To calculate this surface
+density, \citet{winn_background_2013} queried the Besan\c con model
 \citep{robin_synthetic_2003}  along a grid of galactic sight-lines,
-and then converted to $I$-band surface brightnesses.
-Fitting a smooth function to the results, \citet{winn_background_2013}
-found
+and then converted to $I$-band surface brightnesses.  Fitting a smooth
+function to the results, \citet{winn_background_2013} found
 \begin{equation}
@@
 $180^\circ$, and the empirical coefficients were found to be $a_0 =
-18.9733$, $a_1=8.833$, $a_2=4.007$, and $a_3=0.805$.  The model
-is {\it very approximate}.  It is sensitive to the
-threshold used to select ``unresolved'' stars, and likely no more
-accurate than 0.5 mag on average.  In regions with exceptionally high
-extinction ({\it e.g.}, star forming regions) it is expected to
-systematic underestimate the background brightness by an even larger
-degree.
-Nonetheless, this model for the diffuse sky background seems
-to agree reasonably well with the observed trend of standard deviation
-versus stellar magnitude.
+18.9733$, $a_1=8.833$, $a_2=4.007$, and $a_3=0.805$.  The model is
+{\it very approximate}.  It is sensitive to the threshold used to
+select ``unresolved'' stars, and likely no more accurate than 0.5 mag
+on average.  In regions with exceptionally high extinction ({\it
+e.g.}, star forming regions) it is expected to systematic
+underestimate the background brightness by an even larger degree.
+Nonetheless, this model for the diffuse sky background seems to agree
+reasonably well with the observed trend of standard deviation versus
+stellar magnitude.
 
@@
 Beyond the white noise properties of the light curves, the red noise
-properties are also important. 
-In Figure~\ref{fig:avg_acf} we show the average autocorrelation of the
-raw, PCA, and TFA light curves.
-The raw light curves have substantial red noise, and
-their average autocorrelation across many time lags is
-positive.
-The PCA and TFA light curves are much closer to white noise~--~the
-average autocorrelation between any two points in these light curves
-is close to zero.
-However, the average PCA and TFA light curves are not {\it completely}
-uncorrelated.
-At time lags of a few hours or less, there is some excess power.
-This suggests that additional detrending may be
-necessary to maximize the effectiveness of planet searches, or the discovery of
-any other signals via matched-filter techniques.
+properties are also important.  In Figure~\ref{fig:avg_acf} we show
+the average autocorrelation of the raw, PCA, and TFA light curves.
+The raw light curves have substantial red noise, and their average
+autocorrelation across many time lags is positive.  The PCA and TFA
+light curves are much closer to white noise~--~the average
+autocorrelation between any two points in these light curves is close
+to zero.  However, the average PCA and TFA light curves are not {\it
+completely} uncorrelated.  At time lags of a few hours or less, there
+is some excess power.  This suggests that additional detrending may be
+necessary to maximize the effectiveness of planet searches, or the
+discovery of any other signals via matched-filter techniques.
 
@@
 variables, including pulsating stars, rotators, eclipsing binaries,
-and transiting planets.
-A few hand-picked examples are shown in Figure~\ref{fig:quilt}.
+and transiting planets.  A few hand-picked examples are shown in
+Figure~\ref{fig:quilt}.
 The sources\footnote{
@@
 \citep{lomb_1976,scargle_studies_1982,kovacs_box-fitting_2002,vanderplas_periodograms_2015,hippke_TLS_2019}.
-We calculated the periodograms using
-\texttt{astrobase}.
-Our search was cursory~--~a detailed search for transiting
-exoplanets will be the subject of future work.
-To make the figure, we used the ``PCA2'' light curve for each
-star, for simplicity's sake.
-To remove outliers, we omitted
-data points within 6 hours of the beginning or end of each orbit.
-No additional detrending was performed.
+We calculated the periodograms using \texttt{astrobase}.  Our search
+was cursory~--~a detailed search for transiting exoplanets will be the
+subject of future work.  To make the figure, we used the ``PCA2''
+light curve for each star, for simplicity's sake.  To remove outliers,
+we omitted data points within 6 hours of the beginning or end of each
+orbit.  No additional detrending was performed.
 
 The top row of Figure~\ref{fig:quilt} shows two TESS objects of
-interest, and an eccentric eclipsing binary.  TOI~496 is a member of M~48 
-(NGC~2548,
+interest, and an eccentric eclipsing binary.  TOI~496 is a member of
+M~48 (NGC~2548,
 \citealt{gaia_collaboration_gaia_2018,cantat-gaudin_gaia_2018}), a
@@
 potential hot Jupiter orbiting an upper main sequence star, and was
-included as a CDIPS target through the \citet{zari_3d_2018}
-catalog.  The eccentric EB was claimed by \citet{dias_proper_2014} to
-be a member of the $\sim$50 Myr Bochum~5 cluster.  This EB is also
-notable because its TFA light curve heavily whitens the out-of-eclipse
-signal, leaving an eclipse signal that could be mistaken for a planet 
-candidate.  The relevant lesson
-for anyone using the light curves is to verify
-that detrending does not introduce or remove signals
-that alter the interpretation of the system.
+included as a CDIPS target through the \citet{zari_3d_2018} catalog.
+The eccentric EB was claimed by \citet{dias_proper_2014} to be a
+member of the $\sim$50 Myr Bochum~5 cluster.  This EB is also notable
+because its TFA light curve heavily whitens the out-of-eclipse signal,
+leaving an eclipse signal that could be mistaken for a planet
+candidate.  The relevant lesson for anyone using the light curves is
+to verify that detrending does not introduce or remove signals that
+alter the interpretation of the system.
 
@@
 eclipsing binaries.  On the left is a detached EB exhibiting large
-out-of-eclipse modulations in a $\sim$80~Myr
-open cluster (``vdBergh 85'', \citealt{Kharchenko_et_al_2013}).
-In the middle we have V684 Mon, a well-known $\sim$10~Myr old
-detached EB in the very young star-forming region NGC 2264.
-Finally on the right, we have a semi-detached EB in Messier~48.
-
-The bottom row of Figure~\ref{fig:quilt} gives a few examples
-of rotators and pulsators.  On the left, a spotted rotator in the
-$\sim$400 Myr NGC~2184 \citep{cantat-gaudin_gaia_2018}.
-In the middle, we have a pulsator, or perhaps EB flagged by
-\citet{zari_3d_2018} as a pre-MS star.
-Finally on the right is a quasi-periodic pulsator, or perhaps rotator,
-also with a pre-MS host.
+out-of-eclipse modulations in a $\sim$80~Myr open cluster (``vdBergh
+85'', \citealt{Kharchenko_et_al_2013}).  In the middle we have V684
+Mon, a well-known $\sim$10~Myr old detached EB in the very young
+star-forming region NGC 2264.  Finally on the right, we have a
+semi-detached EB in Messier~48.
+
+The bottom row of Figure~\ref{fig:quilt} gives a few examples of
+rotators and pulsators.  On the left, a spotted rotator in the
+$\sim$400 Myr NGC~2184 \citep{cantat-gaudin_gaia_2018}.  In the
+middle, we have a pulsator, or perhaps EB flagged by
+\citet{zari_3d_2018} as a pre-MS star.  Finally on the right is a
+quasi-periodic pulsator, or perhaps rotator, also with a pre-MS host.
 
@@
 have Lomb-Scargle peak false alarm probabilities below $10^{-30}$.
-Even more stars are variable at lower levels of signifiance.
-The implication is that thousands of variable stars with known ages
-should be identifiable from the data at their current level of
-preparation.
+Even more stars are variable at lower levels of signifiance.  The
+implication is that thousands of variable stars with known ages should
+be identifiable from the data at their current level of preparation.
 
@@
 
-In this study, we collected an all-sky sample of about one
-million stars brighter than $G_{\rm Rp}$ of 16.  82\%
-of this target star sample are candidate ``cluster'' members, 
-where we use the generic ``cluster'' to refer to 
-open clusters, stellar associations, and moving groups.
-The remaining stars had photometric or astrometric indications of
-their youth, and either reside on the pre-main-sequence or upper main
-sequence.
+In this study, we collected an all-sky sample of about one million
+stars brighter than $G_{\rm Rp}$ of 16.  82\% of this target star
+sample are candidate ``cluster'' members, where we use the generic
+``cluster'' to refer to open clusters, stellar associations, and
+moving groups.  The remaining stars had photometric or astrometric
+indications of their youth, and either reside on the pre-main-sequence
+or upper main sequence.
 
 We then reduced TESS full frame images taken over the course of about
-two months (Sectors 6 and 7; the first fields close to the
-galactic plane).  We performed difference imaging in order to 
-deal with the complex background.  Using forced aperture
-photometry, we made light curves for all stars brighter than $G_{\rm
-Rp}$ of 13, and went three magnitudes deeper for our target star
-sample.  This yielded \numberlcs light curves of candidate young stars
-across \numberclusters distinct clusters.
-
-The light curves seem to be limited in precision by photon-counting noise 
-from the target star at
-the bright end, and by unresolved background stars at the faint end
-(Figure~\ref{fig:rms_vs_mag}).
+two months (Sectors 6 and 7; the first fields close to the galactic
+plane).  We performed difference imaging in order to deal with the
+complex background.  Using forced aperture photometry, we made light
+curves for all stars brighter than $G_{\rm Rp}$ of 13, and went three
+magnitudes deeper for our target star sample.  This yielded \numberlcs
+light curves of candidate young stars across \numberclusters distinct
+clusters.
+
+The light curves seem to be limited in precision by photon-counting
+noise from the target star at the bright end, and by unresolved
+background stars at the faint end (Figure~\ref{fig:rms_vs_mag}).
 Though the raw light curves show significant red noise, decorrelating
@@
 Brief exploration of the data revealed pulsating stars, eclipsing
-binaries, and planet candidates (Figure~\ref{fig:quilt}).  A detailed planet 
-search is the
-subject of ongoing work.
-
-A point worth re-emphasizing is that the stars in the
-sample must be understood to be {\it candidate} cluster stars, and the
-possibility of photometric blends is important to rule out in
-subsequent vetting efforts of any variable object.  Careful
-understanding of the cluster itself is also important, as some
-clusters are less certain to exist than others \citep[{\it
-e.g.}, the infra-red clusters identified by][]{froebrich_FSR_2007}.
+binaries, and planet candidates (Figure~\ref{fig:quilt}).  A detailed
+planet search is the subject of ongoing work.
+
+A point worth re-emphasizing is that the stars in the sample must be
+understood to be {\it candidate} cluster stars, and the possibility of
+photometric blends is important to rule out in subsequent vetting
+efforts of any variable object.  Careful understanding of the cluster
+itself is also important, as some clusters are less certain to exist
+than others \citep[{\it e.g.}, the infra-red clusters identified
+by][]{froebrich_FSR_2007}.
 
 We remind the reader that our goal in creating our target catalog was
-completeness, rather than reliability.  To create clean sub-samples, we
-advise using the \texttt{CDEXTCAT} header keyword available in the
+completeness, rather than reliability.  To create clean sub-samples,
+we advise using the \texttt{CDEXTCAT} header keyword available in the
 FITS files, which can be used to merge against the original source
@@
 within 1~kpc through visual inspection of Gaia-DR2 data.  Similarly,
-\citet{kounkel_untangling_2019} searched for groups near
-the galactic plane within 1~kpc, and along with the known clusters
-found hundreds of new ``strings'' of kinematically associated stars, which
-could be coeval.
-
-Another area in which we may be incomplete is in sub-clusters
-of broader star-forming complexes. One important example is
-the Orion Nebula (M42; NGC 1976).  While it was observed by TESS in
-Sector~6, searching our light curves for stars within 40 arcminutes
-and 100 parsecs of the Orion Nebula's center yielded only 180 light
-curves, with 85 labelled members.  The Orion Nebula has far more known
-members \citep{jones_proper_1988}.  However, due to a combination of
-the spatially distributed nature of the broader complex, as well as
+\citet{kounkel_untangling_2019} searched for groups near the galactic
+plane within 1~kpc, and along with the known clusters found hundreds
+of new ``strings'' of kinematically associated stars, which could be
+coeval.
+
+Another area in which we may be incomplete is in sub-clusters of
+broader star-forming complexes. One important example is the Orion
+Nebula (M42; NGC 1976).  While it was observed by TESS in Sector~6,
+searching our light curves for stars within 40 arcminutes and 100
+parsecs of the Orion Nebula's center yielded only 180 light curves,
+with 85 labelled members.  The Orion Nebula has far more known members
+\citep{jones_proper_1988}.  However, due to a combination of the
+spatially distributed nature of the broader complex, as well as
 differential extinction, the automated methods of the
@@
 These concerns will likely drive us to expand beyond the current
-sample of target stars in future work.  For the time being though, 
-the light curves exist and are amenable for astrophysical studies.  We
+sample of target stars in future work.  For the time being though, the
+light curves exist and are amenable for astrophysical studies.  We
 invite any who wish to explore the time evolution of stellar or
@@
 G011103, through NASA grant 80NSSC19K0386.
+%
+G.B. acknowledges support through NASA grant NNG14FC03C.
 %
@@
     \tablecaption{
-    	CDIPS target star catalog, \texttt{v0.3}.
+    	CDIPS target star catalog assembled for this work. % version 0.3
     	\label{tbl:cdips_targets}

### 2019-08-12 paper_I/ms.tex
improve discussion / conclusion
* add context w.r.t. other reduction efforts
* mv hyperparameter discussion out of methods, to discussion

@@
 % BEGIN NUMBERS
-\newcommand{\numberpcs}{39\ }  % 2019/06/28 unanimous gold
+\newcommand{\numberpcs}{24\ }  % 2019/08/12 gold post-vet
 \newcommand{\numberzaripcs}{10\ }  % 2019/06/28 unanimous gold
@@
 cluster members brighter than $T=16$ will be observed in the
-full-frame images over the first two years of TESS observations.  This
-count includes the ``most probable'' members, which by the
-\citet{kharchenko_global_2012} definition requires the independent
-kinematic, photometric, and spatial membership probabilities to each
-exceed 61\%.  The actual number of stars in clusters is larger, as the
-membership catalogs are not yet complete, even at these relatively
-bright magnitudes \citep[{\it
+full-frame images (FFIs) over the first two years of TESS
+observations.  This count includes the ``most probable'' members,
+which by the \citet{kharchenko_global_2012} definition requires the
+independent kinematic, photometric, and spatial membership
+probabilities to each exceed 61\%.  The actual number of stars in
+clusters is larger, as the membership catalogs are not yet complete,
+even at these relatively bright magnitudes \citep[{\it
 e.g.},][]{roser_nine_RSG_2016,cantat-gaudin_gaia_2018,cantat-gaudin_newOCs_2019,kounkel_untangling_2019,sim_open_2019}.
@@
 experience, can be viable down to crowding fractions of 10\%.  Based
-on the \citet{Kharchenko_et_al_2013} cluster membership data, and the
+on the \citet{Kharchenko_et_al_2013} cluster membership data and the
 density of background stars, we calculated that the median dilution
@@
 We have therefore begun to apply difference imaging to the TESS
-images, with a focus on any star that could be a member of a group.
+FFIs, with a focus on any star that could be a member of a group.
 We are also including some stars that we suspect are young due to
@@
 \subsection{Choice of convolution kernel}
+\label{subsec:tuneconvkernel}
 
@@
 
-However, we caution that within these fine-tuning experiments, we
-found that transit signals near the noise floor could fall under the
-noise floor for different cases of tuned parameters.  In the longer
-term, developing an image-subtraction method that marginalizes over
-uncertainties of how to chose ``optimal'' kernels would be desirable.
-Pixel-level image subtraction methods that omit these parameters
-entirely are similarly worth exploring \citep{wang_pixel-level_2017}.
-
 With a kernel selected, and the convolution and subtraction performed,
-we calculate the instrumental fluxes for each frame per
+we calculated the instrumental fluxes for each frame per
 Equation~\ref{eq:ism_flux_measurement}.  We did this with three
@@
 
-A point worth re-emphasizing is that the stars in the sample must be
-understood to be {\it candidate} cluster stars, and the possibility of
-photometric blends is important to rule out in subsequent vetting
+There are a number of other TESS data
+processing efforts that we expect will complement our results.
+These include the NASA Ames SPOC pipeline \citep{jenkins_spoc_2010}, the MIT
+Quick-Look-Pipeline \citep{huang_tess_2018}, \texttt{eleanor}
+\citep{feinstein_eleanor_2019}, the \citet{oelkers_precision_2018}
+difference imaging pipeline, the TESS Asteroseismic Consortium (TASOC)
+pipeline \citep{lund_k2p_2015,handberg_tess_2019}, and the Padova
+team's effort (D{.} Nardiello, submitted; {\it e.g.},
+\citealt{libralato_psf-based_2016}).
+
+Most of these pipelines are geared towards tasks more general than our
+own, and use aperture photometry.  The SPOC pipeline
+produces the calibrated FFIs from raw images, processes 2 minute data,
+identifies exoplanets, and produces the TESS data
+products of record.  The MIT-QLP processes a subset of stars on the
+FFIs, identifies exoplanets, and the affiliated TESS Science Office
+alerts object of interest for ground and space-based followup.  The
+\texttt{eleanor} pipeline is a user-friendly tool for
+extracting light curves from the FFIs.  The team developing it is
+also performing transit searches across the full set of FFIs.  The
+TASOC pipeline is primarily aimed towards asteroseismology.  The
+\citeauthor{oelkers_precision_2018} pipeline was aimed at broad,
+all-sky variability searches, and used similar difference
+imaging methods as our own.  Finally, the Padova team's effort is
+developed with a similar focus towards clusters as our work, but uses
+PSF subtraction to mitigate crowding.  This ecosystem
+provides many opportunities for methodological improvements as light
+curve products continue to be made public.
+
+There are of course caveats and possible areas for improvement
+in our own work.
+One methodological point concerns the hyperparameter tuning
+required by our difference imaging method (\S~\ref{subsec:tuneconvkernel}).
+Within our fine-tuning experiments over different kernel box-sizes
+and polynomial weightings,
+we found that low-significance transit signals could be ``lost''
+relative to the noise for different choices of parameters that
+ideally would not affect the photometric pipeline's results.
+In the longer
+term, developing an image-subtraction method that marginalizes over
+uncertainties of how to chose ``optimal'' kernels would be desirable.
+Pixel-level image subtraction methods that omit these parameters
+entirely are also worth exploring \citep{wang_pixel-level_2017}.
+
+A separate point to re-emphasize is that stars in our sample must be
+understood to be {\it candidate} cluster stars, and ruling out the possibility of
+photometric blending is important in subsequent vetting
 efforts of any variable object.  Careful understanding of the cluster
 itself is also important, as some clusters are less certain to exist
-than others \citep[{\it e.g.}, the infra-red clusters identified
+than others \citep[{\it e.g.}, the infrared clusters identified
 by][]{froebrich_FSR_2007}.
@@
 those with provenance from {\it e.g.}, the Gaia-DR2 data is another
-way to produce a cleaner sample of cluster targets.
-
-Despite our goal of completeness, some clusters may still be missing
-members~--~the census of nearby coeval stellar populations is still
+way to produce a clean sample of cluster targets.
+
+Despite our goal of completeness, some clusters still may be missing
+members~--~the census of nearby coeval stellar populations is
 very much in flux. For instance, during the preparation of this work,
@@
 \citet{kounkel_untangling_2019} searched for groups near the galactic
-plane within 1~kpc, and along with the known clusters found hundreds
+plane within 1~kpc, and along with known clusters found hundreds
 of new ``strings'' of kinematically associated stars, which could be
@@
 Another area in which we may be incomplete is in sub-clusters of
-broader star-forming complexes. One important example is the Orion
+large star-forming complexes. One important example is the Orion
 Nebula (M42; NGC 1976).  While it was observed by TESS in Sector~6,
@@
 These concerns will likely drive us to expand beyond the current
-sample of target stars in future work.  For the time being though, the
+sample of target stars in future work.  For the time being, the
 light curves exist and are amenable for astrophysical studies.  We
@@
 C.~Huang,
-and M.~Soares-Furtado.  The authors are also
+M.~Soares-Furtado,
+J.~Wallace, and
+S.~Yee.  The authors are also
 grateful to the many people who have turned TESS from an idea into
 reality.
-%
-Coauthors thank ... %FIXME
 %

### 2019-08-12 paper_I/ms.tex
paper: minor

@@
 Most of these pipelines are geared towards tasks more general than our
-own, and use aperture photometry.  The SPOC pipeline
-produces the calibrated FFIs from raw images, processes 2 minute data,
-identifies exoplanets, and produces the TESS data
-products of record.  The MIT-QLP processes a subset of stars on the
-FFIs, identifies exoplanets, and the affiliated TESS Science Office
-alerts object of interest for ground and space-based followup.  The
-\texttt{eleanor} pipeline is a user-friendly tool for
-extracting light curves from the FFIs.  The team developing it is
-also performing transit searches across the full set of FFIs.  The
-TASOC pipeline is primarily aimed towards asteroseismology.  The
+own, and use aperture photometry.  The SPOC pipeline produces the
+calibrated FFIs from raw images, processes 2 minute data, identifies
+exoplanets, and produces the TESS data products of record.  The
+MIT-QLP processes a subset of stars on the FFIs, identifies
+exoplanets, and the affiliated TESS Science Office alerts object of
+interest for ground and space-based followup.  The \texttt{eleanor}
+pipeline is a user-friendly tool for extracting light curves from the
+FFIs.  The team developing it is also performing transit searches
+across the full set of FFIs.  The TASOC pipeline is primarily aimed at
+asteroseismology and variable star classification.  The
 \citeauthor{oelkers_precision_2018} pipeline was aimed at broad,
-all-sky variability searches, and used similar difference
-imaging methods as our own.  Finally, the Padova team's effort is
-developed with a similar focus towards clusters as our work, but uses
-PSF subtraction to mitigate crowding.  This ecosystem
-provides many opportunities for methodological improvements as light
-curve products continue to be made public.
-
-There are of course caveats and possible areas for improvement
-in our own work.
-One methodological point concerns the hyperparameter tuning
-required by our difference imaging method (\S~\ref{subsec:tuneconvkernel}).
-Within our fine-tuning experiments over different kernel box-sizes
-and polynomial weightings,
-we found that low-significance transit signals could be ``lost''
-relative to the noise for different choices of parameters that
-ideally would not affect the photometric pipeline's results.
-In the longer
-term, developing an image-subtraction method that marginalizes over
-uncertainties of how to chose ``optimal'' kernels would be desirable.
-Pixel-level image subtraction methods that omit these parameters
-entirely are also worth exploring \citep{wang_pixel-level_2017}.
+all-sky variability searches, and used difference imaging methods
+similar to our own.  Finally, the Padova team's effort is also
+directed towards star clusters, but uses PSF subtraction to mitigate
+crowding.  This ecosystem provides many opportunities for
+methodological improvements as light curve products continue to be
+made public.
+
+There are of course caveats and possible areas for improvement in our
+own work.  One methodological point concerns the hyperparameter tuning
+required by our difference imaging method
+(\S~\ref{subsec:tuneconvkernel}).  Within our fine-tuning experiments
+over different kernel box-sizes and polynomial weightings, we found
+that low-significance transits  could be ``lost'' to the noise for
+different choices of parameters that ideally should not affect the
+photometric pipeline's results.  In the longer term, developing an
+image-subtraction method that marginalizes over uncertainties of how
+to chose ``optimal'' kernels would be desirable.  Pixel-level image
+subtraction methods that omit these parameters entirely are also worth
+exploring \citep{wang_pixel-level_2017}.
 
 A separate point to re-emphasize is that stars in our sample must be
-understood to be {\it candidate} cluster stars, and ruling out the possibility of
-photometric blending is important in subsequent vetting
+understood to be {\it candidate} cluster stars, and ruling out the
+possibility of photometric blending is important in subsequent vetting
 efforts of any variable object.  Careful understanding of the cluster

### 2019-08-12 paper_I/ms.tex
update paper for quilt plot

@@
 
-% We take this approach because Gaia-DR2 is the base-catalog used to
-% project sources from celestial coordinates to the imaging plane
-% (\S~\ref{sec:method}).  It also has the advantage that for any
-% Gaia-derived cluster memberships, we can cross-match directly
-% against source identifiers.
-
 \paragraph{Pre-{\it Gaia} OC memberships}
+
 \citet{Kharchenko_et_al_2013} used proper motions calculated in PPMXL
@@
 		{\it Top row, left to right}:
-		TOI~496 in Messier 48;
-		TOI~625 orbiting a late A dwarf;
-		and an eccentric EB in Bochum~5.
+    TOI~496 in Messier~48; TOI~625 orbiting a late A dwarf; and an
+    eccentric EB in Bochum~5.
 		{\it Middle row, left to right}:
-		A detached EB in a 80~Myr old cluster;
-		V684 Mon (a 10 Myr old detached EB);
-		and a semi-detached EB in NGC 2548.
+    A detached EB in a 80 Myr old cluster; V684~Mon (a 10 Myr old
+    detached EB); and a semi-detached EB in NGC~2548.
 		{\it Bottom row, left to right}:
-		Spotted rotator in NGC 2184;
-		a pulsator or perhaps EB flagged by \citet{zari_3d_2018} as a pre-MS 
-		star;
-		and a quasi-periodic pulsator, also with a pre-MS host.
-		Gaia source identifiers are given in the text.
+    Spotted rotator in NGC~2184; V468~Ori, a flaring M dwarf in
+    Messier~42 with a strong rotation signal; Rapidly rotating 30 Myr
+    old M dwarf, similar to those described by
+    \citet{zhan_complex_2019}.  Gaia source identifiers are given in
+    the text.
 	\label{fig:quilt}
@@
 \paragraph{Sector 6}
+
 In Sector 6, \sVInumberlcs light curves of candidate cluster stars
@@
 \paragraph{Sector 7}
+
 In Sector 7, \sVIInumberlcs light curves of candidate cluster stars
@@
 largest number of light curves.  Many rich open clusters, including
-NGC 2437, 2477, 2546, and 2451 are in the field.  The cluster listed
+NGC~2437, 2477, 2546, and 2451 are in the field.  The cluster listed
 with the most light curves is the Collinder 173 association, chiefly
@@
 \paragraph{Observed RMS vs magnitude.}
+
 Figure~\ref{fig:rms_vs_mag} shows the standard deviation of the
@@
 	3024952755135530496,
-	2949587413510194688, 
-	5274902193830445312 
+  3209428644243836928,
+  3214130293403123712 
 } were identified by calculating Lomb-Scargle and transit-least
@@
 Mon, a well-known $\sim$10~Myr old detached EB in the very young
-star-forming region NGC 2264.  Finally on the right, we have a
+star-forming region NGC~2264.  Finally on the right, we have a
 semi-detached EB in Messier~48.
@@
 The bottom row of Figure~\ref{fig:quilt} gives a few examples of
-rotators and pulsators.  On the left, a spotted rotator in the
+rotational variables.  On the left, a spotted rotator in the
 $\sim$400 Myr NGC~2184 \citep{cantat-gaudin_gaia_2018}.  In the
-middle, we have a pulsator, or perhaps EB flagged by
-\citet{zari_3d_2018} as a pre-MS star.  Finally on the right is a
-quasi-periodic pulsator, or perhaps rotator, also with a pre-MS host.
+middle we have V468~Ori, a flaring M dwarf in Messier~42 with a strong
+rotation signal.
+Finally on the right is an M dwarf in ASCC~19, a $\sim$30 Myr M dwarf
+with complex rotational modulation.
+The star was also flagged by \citet{zari_3d_2018} as a pre-MS star.
+Similar modulations were described by \citet{zhan_complex_2019} for
+rapidly rotating M dwarfs in other moving groups, and were suggested
+to be caused by star spot occulations behind a protostellar disk.
 
@@
 large star-forming complexes. One important example is the Orion
-Nebula (M42; NGC 1976).  While it was observed by TESS in Sector~6,
+Nebula (M~42; NGC~1976).  While it was observed by TESS in Sector~6,
 searching our light curves for stars within 40 arcminutes and 100

### 2019-08-12 cdips/plotting/plot_quilt_s6_s7.py

@@ -48,7 +48,7 @@ def plot_quilt_s6_s7(overwrite=1):
         3064487241899832832, # semidetached EB, NGC 2548
         3024952755135530496, # two-spotted pulsator, NGC 2184
         3209428644243836928, # M42 Dias, rapid rotating m dwarf, V468 Ori
-        3214130293403123712 # zhuchang-class weirdo.
+        3214130293403123712  # zhuchang-class weirdo.
         #2949587413510194688, # double-hump rotator / pulsator??
         #5274902193830445312  # sick PMS star. pulsating? spots??
     ]

### 2019-08-12 paper_I/ms.tex
paper: update figures. minor tweaks.

@@
 		\includegraphics[width=0.9\textwidth]{target_star_positions.png}
-		%\gridline{\fig{target_star_cumulative_counts.pdf}{0.41\textwidth}{}}
 	\end{center}
@@
 		\leavevmode
-		%\includegraphics[width=0.45\textwidth]{target_star_cumulative_counts.png}
 		\gridline{\fig{target_star_cumulative_counts.pdf}{0.43\textwidth}{}}
@@
 		Target star statistics.
-		{\it Top.} Cumulative counts as a function of Gaia $Rp$-band
+		{\it Top.} Cumulative counts as a function of apparent Gaia $Rp$-band
 		magnitude.  
@@
 \url{https://gea.esac.esa.int/archive/documentation/GDR2/Data_processing/chap_cu5pho/sec_cu5pho_calibr/ssec_cu5pho_PhotTransf.html},
-online, \texttt{2019-03-29}, or \citet{carrasco_gaia_2016}}, and
+(accessed \texttt{2019-03-29}), or \citet{carrasco_gaia_2016}}, and
 required that the measured $G$-magnitude fall within 2 magnitudes of
@@
 		\leavevmode
-		\includegraphics[width=0.25\textwidth]{pipelineoverview.pdf}
+		\includegraphics[width=0.35\textwidth]{pipelineoverview.pdf}
 	\end{center}
@@
     \end{center}
-    \vspace{-0.6cm}
+    \vspace{-0.9cm}
     \caption{
         Stages of image processing for an image obtained during the middle
-        of an orbit.
+        of an orbit. Counts are in ADU.
         {\it Top right}. Calibrated image.
@@
         {\it Middle left}. Calibrated image minus smooth background.
-        {\it Bottom left}. Registered difference image.
-        {\it Bottom right}. Zoom of difference image.
+        {\it Bottom left}. Difference image.
+        {\it Bottom right}. Zoom of difference image, corresponding to
+        the square with dashed lines.
         Each image is $(2048\times2048)$ pixels, except for the
-        bottom-right image, which is $(500\times500)$.  All images
-        except the top-right have the same color map.  The sector,
+        bottom-right image, which is $(512\times512)$.  All images
+        except the top-right have identical color maps.  The sector,
         camera, and CCD are (6, 1, 2).
@@
     \end{center}
-    \vspace{-0.6cm}
+    \vspace{-0.7cm}
     \caption{
@@
 addition, we use the sector-specific data release notes\footnote{\url{
-  archive.stsci.edu/tess/tess_drn.html}} to identify further times
+  archive.stsci.edu/tess/tess_drn.html}, accessed \texttt{2019-08-12}} to identify further times
 with anomalous spacecraft performance, which we omit from
@@
 additional gaps in Sector 7.
-%For Sectors 1 through 5, these
-%include coarse pointing windows from orbits 10, 13, 14, and an
-%instrumetal anomaly window in orbit 15.
-% For Sectors 6 through 8, these include three days at the beginning of
-% Sector 6 dedicated to acquiring pixel response function data, and also
-% about three days during Sector 8 lost to an instrument anomaly.
 
@@
 performed using
-\texttt{gaia2read}\footnote{\url{github.com/samuelyeewl/gaia2read}}
+\texttt{gaia2read}\footnote{\url{github.com/samuelyeewl/gaia2read}, commit \texttt{4b472d}}
 \citep{kim_2018_gaia2read}.
@@
   }
-	\vspace{-0.5cm}
+	\vspace{-0.85cm}
 	\caption{
@@
 with an increasing number of components\footnote{See for example
-\url{https://scikit-learn.org/stable/auto_examples/decomposition/plot_pca_vs_fa_model_selection.html}
-(2019/08/06).}.  We found that if we instead performed a factor
+\url{https://scikit-learn.org/stable/auto_examples/decomposition/plot_pca_vs_fa_model_selection.html}, accessed \texttt{2019-08-06}.}.  We found that if we instead performed a factor
 analysis, the cross-validation score was typically maximized with
@@
 Schmidt Telescope on Palomar Mountain and the UK Schmidt Telescope.
-The plates were processed into the present compressed digital form
-with the permission of these institutions.
 %
@@
   \item Checked the WEBDA double name
-    list\footnote{\url{https://webda.physics.muni.cz/double_names.html}},
+    list\footnote{\url{https://webda.physics.muni.cz/double_names.html}, accessed \texttt{2019-08-12}},
     and repeated Steps 1-4 with any matches.

### 2019-08-12 paper_I/ms.tex
minor
update keywords

@@
 \keywords{
-  planets and satellites: detection  --
-  methods: data analysis ---
-  techniques: photometric ---
-  (Galaxy:) open clusters and associations: general ---
+Astronomy data reduction (1861),
+Transit photometry (1709),
+Stellar ages (1581),
+Open star clusters (1160),
+Stellar associations (1582),
+Exoplanet evolution (491),
+Stellar rotation (1629),
+Variable stars (1761),
+Eclipsing binary stars (444), 
+Time series analysis (1916)
 }
@@
 online\footnote{\url{github.com/waqasbhatti/pipe-trex}, commit
-\texttt{cd9f9bb}.}.
+\texttt{9d7020e}.}.
 

### 2019-08-16 drivers/fit_models_to_gold.py
fit_models_to_gold: fine-tune for convergence
* improves logging

* moves some PCs to require "long runs" s.t. the MCMC sampling converges

@@ -34,12 +34,20 @@ from cdips.utils import today_YYYYMMDD
 import make_vetting_multipg_pdf as mvp
 import imageutils as iu
 
+# TODO: 3217331693306617344 fails to get rstar
+
 LONG_RUN_IDENTIFIERS = [
     3217331693306617344, # s6 begin
+    3126526081688850304,
     3107333698210242176,
     3340674976430098688,
     4827527233363019776,
+    5584409013334503936,
     3050033749239975552, # s7 begin
+    2919143383943171200,
+    5541111035713815552,
+    5599752663752776192,
+    5516140233292943872,
     3064530810048196352,
     3114869682184835584
 ]
@@ -164,6 +172,10 @@ def main(overwrite=0, sector=7, nworkers=40, cdipsvnum=1, cdips_cat_vnum=0.3):
                                lcname.replace('.fits',''),
                                lcname.replace('.fits','_fitparameters.csv'))
 
+        #
+        # if you haven't already made the output parameter file (which requires
+        # convergence) then start fitting.
+        #
         if not os.path.exists(outpath):
 
             _fit_transit_model_single_sector(tfa_sr_path, lcpath, outpath, mdf,
@@ -172,6 +184,24 @@ def main(overwrite=0, sector=7, nworkers=40, cdipsvnum=1, cdips_cat_vnum=0.3):
                                              sector, nworkers,
                                              cdipsvnum=cdipsvnum,
                                              overwrite=overwrite)
+
+        else:
+
+            status_file = os.path.join(
+                os.path.dirname(outpath), 'run_status.stat'
+            )
+            status = load_status(status_file)
+
+            fittype = 'fivetransitparam_fit'
+            if str2bool(status[fittype]['is_converged']):
+                print('{} converged and already wrote wrote ctoi csv.'.
+                      format(sourceid))
+
+            else:
+                raise ValueError(
+                    'got parameter file existing, but not converged.'
+                    'should never happen. for DR2 {}'.format(sourceid)
+                )
 
 
 def _get_data(sector, cdips_cat_vnum=0.3):

### 2019-08-16 paper_I/ms.tex
add another list of labelled variable stars

@@
 % TODO
-% * update keywords per new AAS format
 
@@
   The Transiting Exoplanet Survey Satellite (TESS) is providing
-  precise time-series photometry for almost every star cluster in the
+  precise time-series photometry for most star clusters in the
   solar neighborhood.
@@
   Using the TESS images, we have begun a Cluster Difference Imaging
-  Photometric Survey (CDIPS), in which we are focusing on stars that
-  are candidate cluster members, or else show other indications of
-  youth.
+  Photometric Survey (CDIPS), in which we are focusing 
+  both on stars that are candidate cluster members, and on stars that show indications of youth.
   %
@@
 stellar surface density make aperture photometry unreliable.  However,
-it implies that most stars in clusters, which are almost always near
+it implies that most stars in clusters, which are usually near
 the galactic plane, will go unprocessed by the official {\it TESS}
@@
 We have therefore begun to apply difference imaging to the TESS
-FFIs, with a focus on any star that could be a member of a group.
+FFIs, with a focus on any star that could be a cluster member.
 We are also including some stars that we suspect are young due to
@@
 \S~\ref{subsec:lcstatistics} we summarize their statistical
-properties.  An example of how we might use the data to identify
-pulsating stars, eclipsing binaries, and transiting planets is then
-given (\S~\ref{subsec:identifying_variability}).  We close in
-\S~\ref{sec:conclusion} by summarizing our findings, and discuss them
+properties.  We then give an example of how to use the data to identify
+pulsating stars, eclipsing binaries, and transiting planets
+(\S~\ref{subsec:identifying_variability}).  We close in
+\S~\ref{sec:conclusion} with a summary of our findings, and discuss them
 with an eye towards the studies we hope this and further data
@@
 generally young stellar populations (\S~\ref{subsec:mg}).  In
-\S~\ref{subsec:ocmgsummary} and Figure~\ref{fig:cdips_targets} we give
+\S~\ref{subsec:ocmgsummary} we give
 summary statistics for the entire sample of about one million target
-stars.
+stars, and we list the targets in Table~\ref{tbl:cdips_targets}.
 
@@
 
-At the time of writing, two relatively large, homogeneous cluster
+At the time of our analysis, two relatively large, homogeneous cluster
 memberships studies had been performed using Gaia-DR2: those by
@@
 parallaxes.  They used Gaia photometry and radial velocities to verify
-the membership claims.  From their Table~2, we collect 401{,}448
+the membership claims.  From their Table~2, we collected 401{,}448
 cluster members, in 1229 clusters, down to their limiting magnitude of
@@
 \citet{gaia_hr_2018} reported members of a smaller, more select group
-of well-studied open clusters. From their Table~A1, we collect
+of well-studied open clusters. From their Table~A1, we collected
 40{,}903 cluster members, in 41 open clusters, mostly within
@@
 \citep{skrutskie_tmass_2006} to report the existence of 2859 open
-clusters and stellar associations (globular clusters were omitted by
-excluding any entry of type \texttt{'g'}).  We selected the most
+clusters and stellar associations. We omitted globular clusters by
+excluding any entry of type `\texttt{g}'.  We selected the most
 probable cluster members (``$1\sigma$ members'') using the combined
 photometric, kinematic, and spatial criteria described by
-\citet[][Section~3.3]{kharchenko_global_2012}.  Then, to obtain {\it
+\citet{kharchenko_global_2012}.  Then, to obtain {\it
 Gaia}-DR2 source identifiers for the members, we performed a
@@
 50\%.  To obtain Gaia-DR2 source identifiers for the members, we
-performed a similar crossmatch as before, looking for sources within 5
+performed a similar crossmatch, looking for sources within 5
 arcseconds of the listed positions, and within $\pm$2 $G$-band
@@
 typically below 1 arcsecond.  The \citeauthor{dias_proper_2014}
-catalog shows stronger crowding effects at the faint end compared to
+catalog shows stronger crowding effects at the faint end than
 the \citeauthor{Kharchenko_et_al_2013} catalog, and likely has a
@@
 
-Stars, moving groups and stellar associations are of interest for
-similar reasons as stars in open clusters.  Though fewer stars
-are known to exist in moving groups, they are of particular interest
-because moving groups are less crowded than open clusters, and are
-often closer to the Sun.
-
-We obtained Gaia-DR2 identifiers from the results of the following
-studies:
+Stars in moving groups and stellar associations are interesting for
+similar reasons as stars in open clusters.  
+Relative to open cluster members though, stars in moving groups are 
+usually closer, brighter, and
+exist in less crowded environments.
+
+To identify stars in these types of groups, we matched the following studies
+against Gaia-DR2:
+\citet{gagne_banyan_XII_2018},
 \citet{gagne_banyan_XI_2018},
-\citet{gagne_banyan_XII_2018},
 \citet{gagne_banyan_XIII_2018},
@@
 \citet{oh_comoving_2017} searched for comoving stars in the $\approx$2
-million stars that appear in both the Tycho-2 and {\it Gaia}-DR1
+million stars that appear in both the Tycho-2 and Gaia-DR1
 catalogs.  They found many wide binaries, and also identified a large
@@
 within $500\,{\rm pc}$ using data from Gaia-DR2. Two subsamples were
-made: (a) an upper main sequence (MS) sample, with 86{,}102 stars, and
-(b) a pre-MS sample, with 43{,}719 stars.  Each was created from a
+made: an upper main sequence (MS) sample, with 86{,}102 stars, and
+a pre-MS sample, with 43{,}719 stars.  Each was created from a
 careful combination of distinct astrometric and photometric cuts.
@@
 single table. We queried Gaia-DR2's \texttt{gaia\_source} table to
-retrieve their apparent $G$, $G_{\rm Rp}$, and $G_{\rm Bp}$
+retrieve each star's apparent $G$, $G_{\rm Rp}$, and $G_{\rm Bp}$
 magnitudes, as well as their astrometric measurements $(\alpha,
@@
 also used a more restrictive membership probability cut (again,
-following the criteria they used for their star counts), and so this
+following the criteria they used for their star counts), so this
 sub-sample is likely less contaminated with field interlopers.
@@
 \citet{Kharchenko_et_al_2013}, and 88.8\% are assigned a cluster name.
-The remainder are mostly the young stars from \citet{zari_3d_2018}.
+The remainder are mostly young stars from \citet{zari_3d_2018}.
 Ages and their uncertainties were then assigned using the parameters
@@
 reduction was adapted from a pipeline called \texttt{pipe-trex}, under
-development primarily for the HATPI project (\url{hatpi.org}).  The
+development for the HATPI project (\url{hatpi.org}).  The
 code is available
@@
 flux measurements are converted to total flux measurements using
-photometric information from Gaia-DR2 to estimate the total flux of
+photometric information from Gaia-DR2 to determine the total flux of
 each source on the reference image.  We detrend the resulting light
@@
 red noise properties of the light curves, and a few interesting cases
-of variability, are discussed in \S~\ref{sec:results}.
+of variability, are explored in \S~\ref{sec:results}.
 
@@
 NGC~2516, NGC~1901), for the present work we opted to focus on Sectors
-6 \& 7, for which there were more stars of interest.  These begin in
-Sector 6 (2018-12-12, spacecraft orbit \#19), and conclude at the end
-of Sector 7 (2019-02-01, spacecraft orbit \#22).  Sectors 6 and 7
+6 and 7, for which there were more stars of interest.  Sector 6
+began on December 12, 2018 (space orbit \#19). Sector 7 concluded
+on February 1, 2019. Combined, the two sectors
 cover galactic longitudes from roughly 200$^\circ$ to 280$^\circ$,
@@
 
-Having prepared the images, we perform some initial analysis steps to
+After preparing the images, we perform some initial analysis steps to
 produce metadata needed during image subtraction.
@@
 non-saturated stars in each image.  This is done using a
-\texttt{fitsh} tool, \texttt{fistar}.  We derive centroid positions
+\texttt{fitsh} module, \texttt{fistar}.  We derive centroid positions
 for the stars, and simultaneously fit elliptical gaussians to their
@@
 \end{equation}
-where $\sigma_{xy}$ is the uncertainty in the target image pixel
+for $\sigma_{xy}$ the uncertainty in the target image pixel
 values.  Photometry is then performed on the difference image
@@
 needs to have a large number of detected sources (though the variance
-between TESS images was rather small).  We sort the image using these
+between TESS images was rather small).  We sort the images using these
 metrics, and then select the astrometric reference frame from
@@
 
-We then compute and apply a spatial transformation of each calibrated
-frame to match the astrometric reference frame.  This
-transformation~--~a combination of rotation, dilation, and
+We then compute and apply a spatial transformation 
+to each calibrated frame in order to match the astrometric reference.
+This transformation~--~a combination of rotation, dilation, and
 translation~--~typically moves stars by less than a pixel, since the
@@
 To avoid this problem, after performing simple aperture photometry on
-the reference frame, we fitted a line between the Gaia-DR2 magnitude
-of each star, and its measured flux.  The TESS $T$-band magnitude was
-calculated according to Equation~1 of \citet{stassun_TIC8_2019}.  We
-then use the known catalog magnitude to predict the expected reference
+the reference frame, we fitted a line between the TESS T-band magnitude
+of the bright stars, and their measured fluxes.  The TESS $T$-band magnitudes were
+calculated using the Gaia-DR2 magnitudes of each star, and
+Equation~1 of \citet{stassun_TIC8_2019}.  We
+then used the known catalog magnitudes for all the stars on
+each image to predict the expected reference
 flux for each star.  This accounts for crowding down to Gaia's
@@
 from the catalog of known TOIs (TESS Objects of Interest; N.~Guerrero,
-in prep).
+in preparation).
 
@@
     TFA-detrended light curves. Black points correspond to the minimum
-    RMS across the available three aperture sizes.  The model (orange
-    and gray lines) assumes aperture sizes reported by
+    RMS across the three available aperture sizes.  The model (orange
+    and gray lines) assumes aperture sizes calculated by
     \citet{Sullivan_et_al_2015}, and the effective area from
@@
 for stars brighter than $T\approx9$
-\citep[see][Figure~14]{Sullivan_et_al_2015}.  Since the brightest
+\citep[][Figure~14]{Sullivan_et_al_2015}.  Since the brightest
 stars are not the focus of the present work, we leave this issue
@@
 subject of future work.  To make the figure, we used the ``PCA2''
-light curve for each star, for simplicity's sake.  To remove outliers,
+light curve for each star.  To remove outliers,
 we omitted data points within 6 hours of the beginning or end of each
@@
 interest, and an eccentric eclipsing binary.  TOI~496 is a member of
-M~48 (NGC~2548,
+Messier~48 (NGC~2548,
 \citealt{gaia_collaboration_gaia_2018,cantat-gaudin_gaia_2018}), a
@@
 rotation signal.
-Finally on the right is an M dwarf in ASCC~19, a $\sim$30 Myr M dwarf
+Finally on the right is a $\sim$30 Myr old M dwarf in ASCC~19
 with complex rotational modulation.
@@
 have Lomb-Scargle peak false alarm probabilities below $10^{-30}$.
-Even more stars are variable at lower levels of signifiance.  The
-implication is that thousands of variable stars with known ages should
+Even more stars are variable at lower levels of signifiance.  This implies
+that thousands of variable stars with known ages should
 be identifiable from the data at their current level of preparation.
@@
 In this study, we collected an all-sky sample of about one million
-stars brighter than $G_{\rm Rp}$ of 16.  82\% of this target star
-sample are candidate ``cluster'' members, where we use the generic
+stars brighter than $16^{\rm th}$ magnitude in $G_{\rm Rp}$.
+82\% of these target stars
+are candidate ``cluster'' members, where we use the generic
 ``cluster'' to refer to open clusters, stellar associations, and
-moving groups.  The remaining stars had photometric or astrometric
+moving groups.  The remaining stars have photometric or astrometric
 indications of their youth, and either reside on the pre-main-sequence
@@
 complex background.  Using forced aperture photometry, we made light
-curves for all stars brighter than $G_{\rm Rp}$ of 13, and went three
+curves for all Gaia-DR2 sources brighter than $G_{\rm Rp}$ of 13, and went three
 magnitudes deeper for our target star sample.  This yielded \numberlcs
-light curves of candidate young stars across \numberclusters distinct
+target star light curves across \numberclusters distinct
 clusters.
@@
 
-There are a number of other TESS data
-processing efforts that we expect will complement our results.
+We expect that our results will complement a number of other
+TESS data processing efforts.
 These include the NASA Ames SPOC pipeline \citep{jenkins_spoc_2010}, the MIT
@@
 Most of these pipelines are geared towards tasks more general than our
-own, and use aperture photometry.  The SPOC pipeline produces the
+own, and most use aperture photometry.  The SPOC pipeline produces the
 calibrated FFIs from raw images, processes 2 minute data, identifies
@@
 pipeline is a user-friendly tool for extracting light curves from the
-FFIs.  The team developing it is also performing transit searches
-across the full set of FFIs.  The TASOC pipeline is primarily aimed at
-asteroseismology and variable star classification.  The
+FFIs.  The team developing \texttt{eleanor} is also reporting planet candidates
+to ExoFOP-TESS\footnote{\url{exofop.ipac.caltech.edu/tess/index.php}}.  The TASOC pipeline is primarily aimed at
+asteroseismology and also includes classification modules for many types of variable stars. The
 \citeauthor{oelkers_precision_2018} pipeline was aimed at broad,
@@
 directed towards star clusters, but uses PSF subtraction to mitigate
-crowding.  This ecosystem provides many opportunities for
-methodological improvements as light curve products continue to be
-made public.
-
-There are of course caveats and possible areas for improvement in our
+crowding.  As light curves from these groups continue to be released, this ecosystem should provide many opportunities to compare and improve data analysis techniques.
+
+There are of course caveats and areas for improvement in our
 own work.  One methodological point concerns the hyperparameter tuning
@@
 over different kernel box-sizes and polynomial weightings, we found
-that low-significance transits  could be ``lost'' to the noise for
+that low-significance transits  can be ``lost'' for
 different choices of parameters that ideally should not affect the
@@
 itself is also important, as some clusters are less certain to exist
-than others \citep[{\it e.g.}, the infrared clusters identified
+than others \citep[{\it e.g.}, the infrared clusters described
 by][]{froebrich_FSR_2007}.
@@
 we advise using the \texttt{CDEXTCAT} header keyword available in the
-FITS files, which can be used to merge against the original source
-catalog to obtain the membership probabilities claimed by the original
-catalog.  Alternatively, simply restricting the targets of interest to
+FITS files, which can be merged against the original source
+catalog to obtain the membership probabilities reported by the
+original authors.  Alternatively, simply restricting the targets of interest to
 those with provenance from {\it e.g.}, the Gaia-DR2 data is another
@@
 large star-forming complexes. One important example is the Orion
-Nebula (M~42; NGC~1976).  While it was observed by TESS in Sector~6,
+Nebula (Messier~42; NGC~1976).  While it was observed by TESS in Sector~6,
 searching our light curves for stars within 40 arcminutes and 100
@@
 
-These concerns will likely drive us to expand beyond the current
-sample of target stars in future work.  For the time being, the
-light curves exist and are amenable for astrophysical studies.  We
+In future work, these concerns will likely drive us to expand beyond the current
+sample of target stars.  For the time being, the
+light curves are of sufficient quality to begin astrophysical studies.  We
 invite any who wish to explore the time evolution of stellar or
@@
 %
+This research has made use of the Exoplanet Follow-up Observation
+Program website, which is operated by the California Institute of
+Technology, under contract with the National Aeronautics and Space
+Administration under the Exoplanet Exploration Program.
+%
 \newline

### 2019-08-17 paper_I/ms.tex
paper add citation to cdips-pipeline

@@
 component.  The specific high-level framework we used for this
-reduction was adapted from a pipeline called \texttt{pipe-trex}, under
-development for the HATPI project (\url{hatpi.org}).  The
-code is available
-online\footnote{\url{github.com/waqasbhatti/pipe-trex}, commit
-\texttt{9d7020e}.}.
+reduction was adapted from a pipeline under development for the HATPI
+project (\url{hatpi.org}).  The code is available
+online\footnote{\url{github.com/waqasbhatti/cdips-pipeline}, commit
+\texttt{7175c48}.}, and the pipeline reference is
+\citet{bhatti_cdips-pipeline_2019}.
 
@@
 \citep{lomb_1976,scargle_studies_1982,kovacs_box-fitting_2002,vanderplas_periodograms_2015,hippke_TLS_2019}.
-We calculated the periodograms using \texttt{astrobase}.  Our search
-was cursory~--~a detailed search for transiting exoplanets will be the
-subject of future work.  To make the figure, we used the ``PCA2''
-light curve for each star.  To remove outliers,
-we omitted data points within 6 hours of the beginning or end of each
-orbit.  No additional detrending was performed.
+We calculated the periodograms using \texttt{astrobase}
+\citep{bhatti_astrobase_2018}.  Our search was cursory~--~a detailed
+search for transiting exoplanets will be the subject of future work.
+To make the figure, we used the ``PCA2'' light curve for each star.
+To remove outliers, we omitted data points within 6 hours of the
+beginning or end of each orbit.  No additional detrending was
+performed.
 
@@
   \texttt{BATMAN} \citep{kreidberg_batman_2015},
+  \texttt{cdips-pipeline} \citep{bhatti_cdips-pipeline_2019}
   \texttt{corner} \citep{corner_2016},

### 2019-08-18 paper_I/ms.tex
aas journals: submitted!
to ApJS, but we'll see what the editors think

@@
 cluster members brighter than $T=16$ will be observed in the
-full-frame images (FFIs) over the first two years of TESS
-observations.  This count includes the ``most probable'' members,
-which by the \citet{kharchenko_global_2012} definition requires the
-independent kinematic, photometric, and spatial membership
-probabilities to each exceed 61\%.  The actual number of stars in
-clusters is larger, as the membership catalogs are not yet complete,
-even at these relatively bright magnitudes \citep[{\it
+full-frame images (FFIs) over the first two years of TESS.  This count includes the
+\citeauthor{Kharchenko_et_al_2013} ``most probable'' members, which
+are stars
+with kinematic, photometric, and spatial membership
+probabilities each independently exceeding 61\% \citep{kharchenko_global_2012}.  The
+actual number of stars in clusters is likely larger, as the membership
+catalogs are not yet complete, even within the nearest kiloparsec
+\citep[{\it
 e.g.},][]{roser_nine_RSG_2016,cantat-gaudin_gaia_2018,cantat-gaudin_newOCs_2019,kounkel_untangling_2019,sim_open_2019}.
@@
 This decision was made because the large pixel size and the high
-stellar surface density make aperture photometry unreliable.  However,
-it implies that most stars in clusters, which are usually near
+stellar surface density make aperture photometry unreliable. 
+By consequence, most stars in clusters, which are usually near
 the galactic plane, will go unprocessed by the official {\it TESS}
@@
 		\leavevmode
-		\gridline{\fig{target_star_cumulative_counts.pdf}{0.43\textwidth}{}}
+		\gridline{\fig{target_star_cumulative_counts.pdf}{0.42\textwidth}{}}
 		\vspace{-0.8cm}
-		\gridline{\fig{target_star_hist_logt.pdf}{0.43\textwidth}{}}
+		\gridline{\fig{target_star_hist_logt.pdf}{0.42\textwidth}{}}
 		\vspace{-0.8cm}
-		\gridline{\fig{target_star_reference_pie_chart.pdf}{0.43\textwidth}{}}
+		\gridline{\fig{target_star_reference_pie_chart.pdf}{0.42\textwidth}{}}
 	\end{center}
@@
 		{\it Bottom.} Provenance of cluster membership.  Percentages are
-		relative to $N_{\rm total}=1{,}061{,}446$ target stars. Symbols
+		relative to the $N_{\rm total}=1{,}061{,}446$ target stars, which are listed in
+		Table~\ref{tbl:cdips_targets}. Symbols
 		are as follows.
@@
     Directions are correct, but lengths are 50 times their true size
-    for visualization purposes.  The systematic error in the top-right
+    for visual clarity.  The systematic error in the top-right
     corner is a typical problem generic to wide-field astrometry.  The
@@
 In this study, we collected an all-sky sample of about one million
-stars brighter than $16^{\rm th}$ magnitude in $G_{\rm Rp}$.
-82\% of these target stars
-are candidate ``cluster'' members, where we use the generic
-``cluster'' to refer to open clusters, stellar associations, and
-moving groups.  The remaining stars have photometric or astrometric
-indications of their youth, and either reside on the pre-main-sequence
-or upper main sequence.
+stars brighter than $16^{\rm th}$ magnitude in $G_{\rm Rp}$.  82\% of
+these target stars are candidate ``cluster'' members, where we use the
+generic ``cluster'' to refer to open clusters, stellar associations,
+and moving groups.  The remaining stars have photometric or
+astrometric indications of their youth, and either reside on the
+pre-main-sequence or upper main sequence.
 
@@
 two months (Sectors 6 and 7; the first fields close to the galactic
-plane).  We performed difference imaging in order to deal with the
-complex background.  Using forced aperture photometry, we made light
-curves for all Gaia-DR2 sources brighter than $G_{\rm Rp}$ of 13, and went three
-magnitudes deeper for our target star sample.  This yielded \numberlcs
-target star light curves across \numberclusters distinct
-clusters.
+plane).  We performed difference imaging to deal with the complex
+background.  Using forced aperture photometry, we made light curves
+for all Gaia-DR2 sources brighter than $G_{\rm Rp}$ of 13, and went
+three magnitudes deeper for our target star sample.  This yielded
+\numberlcs target star light curves across \numberclusters distinct
+clusters.  The number of light curves per cluster was reported
+(Tables~\ref{tbl:s6_lcs} and~\ref{tbl:s7_lcs}).  The software
+developed for the reduction is available online
+\citep{bhatti_cdips-pipeline_2019}.
 
@@
 
-We expect that our results will complement a number of other
-TESS data processing efforts.
-These include the NASA Ames SPOC pipeline \citep{jenkins_spoc_2010}, the MIT
-Quick-Look-Pipeline \citep{huang_tess_2018}, \texttt{eleanor}
+We expect that our results will complement a number of other TESS data
+processing efforts.  These include the NASA Ames SPOC pipeline
+\citep{jenkins_spoc_2010}, the MIT Quick-Look-Pipeline
+\citep{huang_tess_2018}, \texttt{eleanor}
 \citep{feinstein_eleanor_2019}, the \citet{oelkers_precision_2018}
@@
 pipeline is a user-friendly tool for extracting light curves from the
-FFIs.  The team developing \texttt{eleanor} is also reporting planet candidates
-to ExoFOP-TESS\footnote{\url{exofop.ipac.caltech.edu/tess/index.php}}.  The TASOC pipeline is primarily aimed at
-asteroseismology and also includes classification modules for many types of variable stars. The
+FFIs.  The team developing \texttt{eleanor} is also reporting planet
+candidates to
+ExoFOP-TESS\footnote{\url{exofop.ipac.caltech.edu/tess/index.php}}.
+The TASOC pipeline is primarily aimed at asteroseismology and includes
+classification modules for many types of variable stars. The
 \citeauthor{oelkers_precision_2018} pipeline was aimed at broad,
@@
 directed towards star clusters, but uses PSF subtraction to mitigate
-crowding.  As light curves from these groups continue to be released, this ecosystem should provide many opportunities to compare and improve data analysis techniques.
-
-There are of course caveats and areas for improvement in our
-own work.  One methodological point concerns the hyperparameter tuning
-required by our difference imaging method
-(\S~\ref{subsec:tuneconvkernel}).  Within our fine-tuning experiments
-over different kernel box-sizes and polynomial weightings, we found
-that low-significance transits  can be ``lost'' for
-different choices of parameters that ideally should not affect the
-photometric pipeline's results.  In the longer term, developing an
-image-subtraction method that marginalizes over uncertainties of how
-to chose ``optimal'' kernels would be desirable.  Pixel-level image
-subtraction methods that omit these parameters entirely are also worth
-exploring \citep{wang_pixel-level_2017}.
+crowding.  As light curves from these groups continue to be released,
+this ecosystem should provide many opportunities to compare and
+improve data analysis techniques.
+
+There are of course caveats and areas for improvement in our own work.
+One methodological point concerns the hyperparameter tuning required
+by our difference imaging method (\S~\ref{subsec:tuneconvkernel}).
+Within our fine-tuning experiments over different kernel box-sizes and
+polynomial weightings, we found that low-significance transits  can be
+``lost'' for different choices of parameters that ideally should not
+affect the photometric pipeline's results.  In the longer term,
+developing an image-subtraction method that marginalizes over
+uncertainties of how to chose ``optimal'' kernels would be desirable.
+Pixel-level image subtraction methods that omit these parameters
+entirely are also worth exploring \citep{wang_pixel-level_2017}.
 
@@
 we advise using the \texttt{CDEXTCAT} header keyword available in the
-FITS files, which can be merged against the original source
-catalog to obtain the membership probabilities reported by the
-original authors.  Alternatively, simply restricting the targets of interest to
-those with provenance from {\it e.g.}, the Gaia-DR2 data is another
-way to produce a clean sample of cluster targets.
+FITS files, which can be merged against the original source catalog to
+obtain the membership probabilities reported by the original authors.
+Alternatively, simply restricting the targets of interest to those
+with provenance from {\it e.g.}, the Gaia-DR2 data is another way to
+produce a clean sample of cluster targets.
 
 Despite our goal of completeness, some clusters still may be missing
-members~--~the census of nearby coeval stellar populations is
-very much in flux. For instance, during the preparation of this work,
+members~--~the census of nearby coeval stellar populations is very
+much in flux. For instance, during the preparation of this work,
 \citet{sim_open_2019} identified 209 new open cluster candidates
@@
 \citet{kounkel_untangling_2019} searched for groups near the galactic
-plane within 1~kpc, and along with known clusters found hundreds
-of new ``strings'' of kinematically associated stars, which could be
+plane within 1~kpc, and along with known clusters found hundreds of
+new ``strings'' of kinematically associated stars, which could be
 coeval.
@@
 
-In future work, these concerns will likely drive us to expand beyond the current
-sample of target stars.  For the time being, the
-light curves are of sufficient quality to begin astrophysical studies.  We
-invite any who wish to explore the time evolution of stellar or
-exoplanetary systems to interact with the data at \stscilink.
+In future work, these concerns will likely drive us to expand beyond
+the current sample of target stars.  For the time being, the light
+curves are of sufficient quality and quantity to begin astrophysical
+studies.  We invite any who wish to explore the time evolution of
+stellar or exoplanetary systems to interact with the data at
+\stscilink.
 
@@
 		Table~\ref{tbl:s6_lcs} is published in its entirety in a machine-readable format.
-		A portion is shown here for guidance regarding its form and content.
+		The top twenty entries are shown here for guidance regarding form and content.
 		Names are matched against \citet{Kharchenko_et_al_2013} as

### 2019-08-18 paper_I/collect_figures.sh

@@ -4,79 +4,14 @@
 # USAGE: ./collect_figures.sh
 ##########################################
 
-fdir=../paper_I/figures/
+fdir=../results/paper_figures/
 pdir=../paper_I/
 
-# # positions of clusters
-# cp ${fdir}GI_figs/cluster_positions_ecliptic_scicase.pdf \
-#    ${pdir}cluster_positions.pdf
-
-# what our pipeline does
-cp ${fdir}trex_overview.pdf ${pdir}pipelineoverview.pdf
-
-# rms vs mag 
-fdir=../results/paper_figures/
-
-cp ${fdir}detrended_light_curves_sec7cam3ccd2.pdf \
-   ${pdir}detrended_light_curves_sec7cam3ccd2.pdf
-
-cp ${fdir}detrended_light_curves_sec6cam1ccd4.pdf \
-   ${pdir}detrended_light_curves_sec6cam1ccd4.pdf
-
-cp ${fdir}external_parameters_vs_time_sec6cam1ccd1.pdf \
-   ${pdir}external_parameters_vs_time_sec6cam1ccd1.pdf
-
-cp ${fdir}stages_of_image_processing_good.png \
-   ${pdir}stages_of_image_processing_good.png
-
-cp ${fdir}stages_of_image_processing_bad.png \
-   ${pdir}stages_of_image_processing_bad.png
-
+# figure 1
 cp ${fdir}primary_mission_galacticmap_forproposal_cdipsoverplot.png \
    ${pdir}target_star_positions.png
 
-cp ${fdir}IRM-PCA-TFA_rms_vs_mag.pdf ${pdir}IRM-PCA-TFA_rms_vs_mag.pdf
-cp ${fdir}avg_acf.pdf ${pdir}avg_acf.pdf
-
-cp ${fdir}raw_light_curve_systematics_sec7cam2ccd4.pdf \
-   ${pdir}raw_light_curve_systematics_sec7cam2ccd4.pdf
-cp ${fdir}raw_light_curve_systematics_sec6cam1ccd2.pdf \
-   ${pdir}raw_light_curve_systematics_sec6cam1ccd2.pdf
-
-cp ${fdir}tls_sde_vs_period_scatter.pdf \
-   ${pdir}tls_sde_vs_period_scatter.pdf
-
-# quilts
-cp ${fdir}quilt_PCs.pdf ${pdir}quilt_PCs.pdf
-cp ${fdir}quilt_s6_s7.pdf ${pdir}quilt_s6_s7.pdf
-
[…]

### 2019-09-20 paper_I/ms.tex
add comments per referee report

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\documentclass[12pt,twocolumn,tighten]{aastex62}
+%\documentclass[12pt,twocolumn,tighten]{aastex62}
+\documentclass[12pt,twocolumn,tighten,trackchanges]{aastex62}
 %\pdfoutput=1 %for arXiv submission
@@
 
-\newcommand{\stscilink}{\url{archive.stsci.edu/prepds/cdips}}
+\newcommand{\stscilink}{\textsc{\url{archive.stsci.edu/hlsp/cdips}}}
 \newcommand{\stscivetlink}{\url{archive.stsci.edu/prepds/cdips/vetting}}
@@
 %\NewPageAfterKeywords
+\listofchanges
 
@@
   The Transiting Exoplanet Survey Satellite (TESS) is providing
-  precise time-series photometry for most star clusters in the
-  solar neighborhood.
+  precise time-series photometry for most star clusters in the solar
+  neighborhood.
   % Aims
   Using the TESS images, we have begun a Cluster Difference Imaging
-  Photometric Survey (CDIPS), in which we are focusing 
-  both on stars that are candidate cluster members, and on stars that show indications of youth.
+  Photometric Survey (CDIPS), in which we are focusing both on stars
+  that are candidate cluster members, and on stars that show
+  indications of youth.
   %
@@
 This value was chosen based on the onset of bleeding charge trails in
-the images, and is slightly greater than the saturation level of
+the images, and is \deleted{slightly}\added{a factor of two} greater than the 
+saturation level of
 $2\times10^5$ electrons, or about $4\times10^4\,{\rm ADU}$, reported
 by \citet{vanderspek_2018}.  As a consequence, we do not analyze stars
-brighter than $T\approx 6.5$.  As described by \citet{Pal_2009}, the
+brighter than $T\approx 6.5$\deleted{.}\added{, even though the TESS CCID-80 
+CCDs conserve charge across bloom trails up to at least
+$T\approx 4$ \citet{vanderspek_2018}.}
+As described by \citet{Pal_2009}, the
 pixel masks are metadata attached to the image file, and are only
@@
 They might also include the standard deviation of the spacecraft
-quartnerion time-series \citep{vanderburg_hr858_2019}.  Some example
-``external'' parameters that we include with our light curves are
-shown as functions of time in
-Figure~\ref{fig:external_parameter_timeseries}.
+\deleted{quartnerion}\added{quaternion} time-series
+\citep{vanderburg_hr858_2019}.  Some example ``external'' parameters
+that we include with our light curves are shown as functions of time
+in Figure~\ref{fig:external_parameter_timeseries}.
 
@@
 
+\listofchanges
 \end{document}

### 2019-09-20 paper_I/ms.tex
fix typos

@@
 		CG18 is \citet{cantat-gaudin_gaia_2018}.
-		Z18 is \citet{zari_3d_2018}, with upper main sequence and
+		Z18 is \citet{zari_3d_2018}, with upper main-sequence and
 		pre-main-sequence samples sub-divided.
@@
 within $500\,{\rm pc}$ using data from Gaia-DR2. Two subsamples were
-made: an upper main sequence (MS) sample, with 86{,}102 stars, and
+made: an upper main-sequence (MS) sample, with 86{,}102 stars, and
 a pre-MS sample, with 43{,}719 stars.  Each was created from a
@@
 on average.  In regions with exceptionally high extinction ({\it
-e.g.}, star forming regions) it is expected to systematic
+e.g.}, star forming regions) it is expected to
+\deleted{systematic}\added{systematically}
 underestimate the background brightness by an even larger degree.
@@
 search for transiting exoplanets will be the subject of future work.
-To make the figure, we used the ``PCA2'' light curve for each star.
+To make the figure, we used the \texttt{PCA2} light curve for each star.
 To remove outliers, we omitted data points within 6 hours of the
@@
 phase variations suggest that it is an eclipsing binary.  TOI~625 is a
-potential hot Jupiter orbiting an upper main sequence star, and was
+potential hot Jupiter orbiting an upper main-sequence star, and was
 included as a CDIPS target through the \citet{zari_3d_2018} catalog.
@@
 astrometric indications of their youth, and either reside on the
-pre-main-sequence or upper main sequence.
+pre-main-sequence or upper main-sequence.
 

### 2019-09-30 paper_I/ms.tex
update received accepted args
cdips-I: link fixing

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\documentclass[12pt,twocolumn,tighten]{aastex62}
-\documentclass[12pt,twocolumn,tighten,trackchanges]{aastex62}
+\documentclass[12pt,twocolumn,tighten]{aastex62}
+%\documentclass[12pt,twocolumn,tighten,trackchanges]{aastex62}
 %\pdfoutput=1 %for arXiv submission
@@
 %% Add "Submitted to " argument.
-\received{\today}
-\revised{---}
-\accepted{---}
-\submitjournal{AAS journals.}
+\received{August 18, 2019}
+\revised{September 20, 2019}
+\accepted{September 23, 2019}
+\submitjournal{{\it The Astrophysical Journal Supplement}}
 
@@
 \newcommand{\stscivetlink}{\url{archive.stsci.edu/prepds/cdips/vetting}}
+\newcommand{\datasetlink}{\textsc{\dataset[doi.org/10.17909/t9-ayd0-k727]{https://doi.org/10.17909/t9-ayd0-k727}}}
 
@@
   represents between 20 and 25 days of observations of a star brighter
-  than $G_{Rp}=16$, with 30-minute sampling.
+  than $G_{\rm Rp}=16$, with 30-minute sampling.
   % Methods
@@
   %
-  The light curves, which cover about one sixth of the galactic plane,
-  are available at \stscilink.
+  The light curves\footnote{\stscilink}, which cover about one
+  sixth of the galactic plane, are available as a High Level Science
+  Product at MAST: \datasetlink.
 \end{abstract}
@@
 		\vspace{-0.8cm}
-		\gridline{\fig{target_star_reference_pie_chart.pdf}{0.42\textwidth}{}}
+		\gridline{\fig{target_star_reference_pie_chart.png}{0.42\textwidth}{}}
 	\end{center}
@@
 for TFA and PCA.  Blue points are the \numberlcs target stars for
-which light curves are available at \stscilink.  Most of the target
+which light curves are available at \datasetlink.  Most of the target
 stars are close to the galactic plane, and are spatially clustered.
@@
 studies.  We invite any who wish to explore the time evolution of
-stellar or exoplanetary systems to interact with the data at
-\stscilink.
+stellar or exoplanetary systems to interact with the
+data\footnote{\stscilink} at \datasetlink.
 

### 2019-10-02 paper_I/ms.tex
minor paper typo fixes

@@
 \begin{abstract}
-  % Context
   The Transiting Exoplanet Survey Satellite (TESS) is providing
@@
   neighborhood.
-  % Aims
   Using the TESS images, we have begun a Cluster Difference Imaging
@@
   indications of youth.
-  %
   Our aims are to discover giant transiting planets with known ages,
@@
   astrophysics.
-  %
   For this work, we made \numberlcs light curves of candidate young
@@
   than $G_{\rm Rp}=16$, with 30-minute sampling.
-  % Methods
   We describe the image subtraction and time-series analysis
@@
   properties that agree with theoretical expectations.
-  %
   We also comment on the possible utility of the light curve sample
@@
   damping.
-  %
   The light curves\footnote{\stscilink}, which cover about one

### 2019-10-05 cdips/utils/pipelineutils.py
fit_models_to_gold: minor tweaks
two planet candidates worth noting still to be uploaded to eoxfop-TESS
because of convergence issues.  (running...)

@@ -1,3 +1,4 @@
+import os
 import configparser
 
 def save_status(status_file, section, state_vars):

### 2019-10-05 drivers/fit_models_to_gold.py

@@ -50,13 +50,15 @@ LONG_RUN_IDENTIFIERS = [
     5599752663752776192,
     5516140233292943872,
     3064530810048196352,
-    3114869682184835584
+    3114869682184835584,
+    5715454237977779968
 ]
 
 KNOWN_CUSTOM = [
     5290761583912487424, # s7, TLS gets 2x period, and extra detrending needed.
     5290781443841554432, # s7, systematic trends in TFASR LC, 2 transit
     5290968085934209152, # s7, systematic trends in TFASR LC, 2 transit
+    5618515825371166464, # s7, wonky cluster ASCC 39 (skip)
 ]
 
 host = socket.gethostname()
@@ -127,9 +129,6 @@ def main(overwrite=0, sector=7, nworkers=40, cdipsvnum=1, cdips_cat_vnum=0.3):
         sector, cdips_cat_vnum=cdips_cat_vnum)
 
     tfa_sr_paths = _get_lcpaths(df, tfasrdir)
-
-    import IPython; IPython.embed() #FIXME
-    assert 0
 
     for tfa_sr_path in tfa_sr_paths:
 
@@ -238,7 +237,7 @@ def _get_data(sector, cdips_cat_vnum=0.3):
     toipath = os.path.join(database, 'toi-plus-2019-08-29.csv')
     toidf = pd.read_csv(toipath, sep=',')
 
-    ctoipath = os.path.join(database, 'ctoi-exofop-2019-08-29.txt')
+    ctoipath = os.path.join(database, 'ctoi-exofop-2019-08-29.csv')
     ctoidf = pd.read_csv(ctoipath, sep='|')
 
     return df, cdips_df, pfdf, supplementstatsdf, toidf, ctoidf

### 2019-11-27 doc/vetting_report_documentation/doc_TeX/ms.tex
add vetting report description documentation

--- 2019-07-22 paper/ms.tex
@@
 %% Add "Submitted to " argument.
-\received{\today}
-\revised{---}
-\accepted{---}
-\submitjournal{AAS journals.}
+%\received{---}
+%\revised{---}
+%\accepted{---}
+%\submitjournal{}
 
 \shortauthors{Bouma et al.}
-\shorttitle{CDIPS I}
+\shorttitle{Vetting Report Description Document}
 
@@
 
-% BEGIN NUMBERS
-\newcommand{\numberpcs}{39\ }  % 2019/06/28 unanimous gold
-\newcommand{\numberzaripcs}{10\ }  % 2019/06/28 unanimous gold
-\newcommand{\numberclusterpcs}{29\ }  % 2019/06/28 unanimous gold
-\newcommand{\sVInumberlcs}{67{,}601\ }  % 2019/06/20 not allnan
-\newcommand{\sVIInumberlcs}{91{,}736\ }  % 2019/06/20 not allnan
-\newcommand{\numberlcs}{159{,}337\ } % 2019/06/20 sum
-\newcommand{\numberclusters}{596\ } % 2019/07/01 paper_plot_all_figures.py
-\newcommand{\pctoflcswithage}{77} %  2019/07/02 from hist_logt.png
-
 \newcommand{\stscilink}{\url{archive.stsci.edu/prepds/cdips}}
@@
 \title{
-  Light Curves \& Planet Candidates in Open Clusters from TESS Sectors 6 \& 7
+  Cluster Difference Imaging Photometric Survey.
+  Vetting Report Description Document
 }
@@
 \begin{abstract}
-  % Context
-  The Transiting Exoplanet Survey Satellite (TESS) has begun to
-  photometrically monitor almost every star cluster in
-  the solar neighborhood.
-  % Aims
-  To make light curves of stars that could be members of stellar
-  associations, moving groups, or open clusters, we have begun a
-  Cluster Difference Imaging Photometric Survey (CDIPS).
-  %
-  Our aim is to discover giant transiting planets with known
-  ages, and to probe the exoplanet size and separation distributions for
-  planets younger than one gigayear.
-  %
-  In this study, we made \numberlcs light curves of candidate young
-  stars, across \numberclusters distinct clusters.
-  Each light curve represents between 20 and 25 days of observations
-  of a star brighter than $G_{Rp}=16$, sampled at 30 minute cadence.
-  % Methods
-  We describe in detail the image subtraction and time-series analysis 
-  techniques we used to create the light curves, which
-  have noise properties that agree with theoretical expectations.
-  % Results
-  We then highlight the \numberpcs planet candidates we identified in
-  an initial search.
-  \numberclusterpcs of these planet candidates are candidate cluster
-  members, and the remaining \numberzaripcs have indications of youth
-  relative to field stars.
-  We describe the vetting procedures that these objects have survived,
-  and emphasize the additional spectroscopic, photometric, and imaging
-  observations that are needed to determine (i) whether these candidates
-  are planets and (ii) for which cases the host stars are cluster members.
-  %
-  We also comment on the possible utility of the light curve sample for
-  studies of stellar rotation evolution, and binary eccentricity
-  damping.
-  %
-  The light curves and vetting reports are available at
-  \stscilink.
+To find planet candidates in clusters,
+we make vetting reports using our light-curves \citep{bouma_cdips_2019} and
+auxiliary data.
+This document describes the CDIPS planet candidate vetting reports
+uploaded by \texttt{lbouma} to ExoFOP-TESS 2019-09-18 through 2019-11-25.
+\\
+
 \end{abstract}
 
-\keywords{
-  planets and satellites: detection  --
-  methods: data analysis ---
-  techniques: photometric ---
-  (Galaxy:) open clusters and associations: general ---
-}
+%\keywords{
+%	Transit photometry (1709),
+%	Stellar ages (1581)
+%}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% The exoplanet field is evolving.
-% At the beginning, Doppler spectroscopy by the Geneva and California groups
-% led to the first exoplanet detections (CITE: Mayor 95, Butler, Marcy).
-% Some of these planets transited (CITE: Henry, Charbonneau).
-% Despite the geometric rarity of transits, photometric monitoring can
-% be performed in parallel; with precise spectroscopy this has not
-% yet been achieved.
-% Parallel photometric monitoring enabled thousands of planet detections
-% with the Kepler spacecraft (CITE: Borucki, Morton).
-% The abundance of planets from Kepler taught us about statistics
-% (CITE: Howard, Fressin, Petigura).
-% By nature of its design, Kepler left open two major avenues for
-% improvement: (i) brighter stars, (ii) rare weirdos.
-% TESS (CITE: Ricker), by nature of its small, wide-field cameras, and
-% nearly all-sky coverage, can capitalize on both.
-
-% One class of rare weirdo to which TESS is sensitive is stars in
-% clusters.  For brevity, we use the term ``cluster'' to refer to open
-% clusters, moving groups, associations, and star-forming regions.
-% Each of the $\sim$1000 star clusters of the Milky Way is a gift to
-% astrophysics, providing a sample of stars that vary widely in mass
-% but all have approximately the same age and composition.
-
-\section{Introduction}
-\label{sec:intro}
-
-Many evolutionary processes are expected to occur over the lives of
-stars and exoplanets; it would be interesting to statistically observe
-these changes as functions of time.  However, since most dwarf stars
-do not appreciably change until evolving off the
-main sequence, creative approaches must be used to infer stellar ages
-\citep{soderblom_ages_2010}.  One approach beginning to bear fruit in
-exoplanet studies is to search for planets in coeval groups of stars,
-hereafter ``clusters''.  This includes the open clusters of yore, as
-well as the moving groups and stellar associations that began to be
-uncovered in the late 1990s \citep{zuckerman_young_2004}.  The ages of
-these stellar ensembles are inferred through isochrone analyses of
-color-magnitude diagrams, using an appropriate combination of
-main-sequence turnoff locations, pre-main-sequence turnon locations,
-and averaged MS isochronal ages across known cluster members
-\citep[{\it e.g.},][Section 3.4.3]{kharchenko_global_2012}.  Once
-calibrated, gyrochronology can also be used to verify the age of a
-stellar ensemble \citep[{\it
-e.g.},][]{barnes_color-period_2015,meibom_spin-down_2015,curtis_tess_2019}.
-The ages of planets discovered in these cluster stars are then assumed
-to equal the age of the larger stellar ensemble.
-
-The first planets to be detected in open clusters were found through
-radial velocity (RV) measurements of red giants in the Hyades and
-NGC~2423 \citep{Sato_et_al_2007,lovis_mayor_2007}.
-Subsequent spectroscopic searches in Praesepe led to the detection of
-the first hot Jupiter in a cluster \citep{Quinn_et_al_2012}, and also
-the first multi-planet system in a cluster \citep{Malavolta_et_al_2016}.
-The youngest RV detections have come from surveys of T Tauri stars in the
-Taurus star-forming region, which showed signals of the hot Jupiter
-\citep[V830~Tau~b][]{donati_hj_2016} and of a giant planet on a 9-day orbit
-\citep[CI~Tau~b][]{johns-krull_candidate_2016,flagg_co_2019}.
-A final RV survey of note was conducted by
-\citet{brucalassi_search_2017}, who followed 88 stars in M~67 over 7
-years.  They reported detections of three hot Jupiters around main
-sequence stars, and of one giant planet around an evolved star.
-
-The transit method was comparatively slow to catch up.  Deep transit
-searches typically comprising days to weeks of observations were
-performed for NGC~2158, 6791, and 1245, among other clusters
-\citep{mochejska_planets_2005,mochejska_planets_2006,burke_survey_2006}.
-Related projects include a search of M~37 by
-\citet{hartman_MMT_IV_2009}, of Praesepe by
-\citet{pepper_photometric_2008}, and of nine young clusters in the
-solar neighborhood by the Monitor team
-\citep{aigrain_monitor_2007,irwin_monitordata_2007,miller_monitor_2008}.
-Though these studies led to measurements of stellar rotation periods
-\citep{hartman_rotation_2009,Irwin_NGC2516_2007} as well as the
-discovery of pre-main-sequence (PMS) eclipsing binaries (EBs)
-\citep{irwin_monitor_PMSEB_2007}, no definitive transiting planets in
-open clusters were found.  Transit searches in globular clusters were
-similarly met with null results \citep{gilliland_lack_2000,
-weldrake_searching_2006}.  These searches were typically sensitive to
-planets larger than Jupiter, on $\lesssim 3$ day orbital periods.  Hot
-Jupiter occurrence rate limits were derived at the $\lesssim 5\%$
-level \citep[{\it e.g.},][]{burke_survey_2006, hartman_MMT_IV_2009}.
-The modern 0.5-1\% occurrence rate suggests that these early transit
-surveys needed a greater data volume, at higher precision for
-detection to be possible
-\citep{mayor_harps_2011,wright_frequency_2012,howard_planet_2012,petigura_metallicity_2018}.
-
-Kepler \citep{borucki_kepler_2010} observed enough stars for long
-enough and with sufficient precision to detect transiting planets in
-open clusters:  Kepler-66b and 67b, in the gigayear-old NGC~6811
-\citep{Meibom_et_al_2013}.  Though a broken reaction wheel ended the
-prime Kepler mission, the repurposed K2 \citep{howell_k2_2014}
-switched between fields along the ecliptic every quarter-year, and was
-able to observe far more clusters and young stars.  The resulting
-discoveries made by K2 through its surveys of the Pleiades, Hyades,
-Praesepe, and Upper Sco were a major inspiration for the present work.
-
-K2-25b, discovered in the Hyades, has a radius ($3.43\,R_\oplus$) that
-is larger than older Kepler planets around M dwarfs at similar insolation levels
-\citep{Mann_K2_25_2016}.  This inflated radius is perhaps a hint that
-the planet is contracting, or losing its atmosphere \citep[{\it
-e.g.},][]{Fortney_et_al_2007,Owen_Wu_2013,Fulton_et_al_2017}.  The
-super-Neptune sized K2-33b ($P\approx 5.4\,{\rm d}$), found in Upper
-Sco, showed that at least some close-in planets must form within about
-10 Myr \citep{Mann_K2_33b_2016,David_et_al_2017}.  Further discoveries
-included six transiting planets in Praesepe
-\citep{obermeier_k2_2016,Mann_et_al_2017}, a long-period candidate
-super-Earth in the Hyades \citep{vanderburg_zeitVII_2018}, the
-three-planet K2-136 system in the Hyades
-\citep{ciardi_k2-136_2018,livingston_three_2018,mann_ZEITVI_2018}, and
-later the two-planet system K2-264 in Praesepe
-\citep{rizzuto_zeitVIII_2018,livingston_k2-264_2019}.  There has also
-recently been a detection by K2 of a Jupiter-sized planet orbiting
-every 24 days around V1298~Tau \citep{david_v1298_2019}.
-
-A significant amount of effort continues to be devoted towards the
-discovery and characterization of planets around young stars.
-Sometimes, cluster membership may not even be necessary, if a star's
-youth can be inferred from combined rotation, activity, and kinematic
-indicators \citep[{e.g.}, K2-233;][]{david_k2-233_2018}.  To
-investigate demographics in time, the detection sensitivities and
-reliabilities of these searchers need to be calibrated, likely with a
-machinery similar to that outlined by \citet{rizzuto_zeitV_2017}.  A
-separate requirement for population studies to be statistically
-robust, imposed by the geometric rarity of transits, is that many tens
-of thousands of stars with known ages must be monitored at high
-precision.
-
-The TESS mission \citep{ricker_transiting_2015}, though designed for
-other purposes, holds the promise to deliver the most homogeneous and
-comprehensive cluster photometric survey in history.  More
-quantitatively, the \citet{Kharchenko_et_al_2013} cluster member
-database indicates that $\approx 2\times10^5$ open cluster members
-brighter than $T=16$ will be observed in the full-frame images over
-the first two years of TESS observations.  This count includes the
-``most probable'' members within each cluster's radius, which by the
-\citet[][]{kharchenko_global_2012} definition requires the independent
-kinematic, photometric, and spatial membership probabilities to each
-exceed 61\%.  The actual number of stars in clusters may be larger, as
-the membership catalogs are not yet complete, even at these relatively
-bright magnitudes \citep[{\it
-e.g.},][]{roser_nine_RSG_2016,cantat-gaudin_gaia_2018,cantat-gaudin_newOCs_2019}.
-% Our target list currently sits at $\approx 1.0\times10^6$ candidate
-% young stars, perhaps one-third of which are bonafide cluster members
-% (see \S~\ref{sec:starselection}).
-
-One of the major barriers to deriving precise photometry from the TESS
-images is the relatively poor angular resolution ($\approx 21''$ per
-pixel).  Almost all clusters are within 10 degrees of the Galactic
-plane. The problems with crowding and complex backgrounds are so
-severe near the galactic plane that the TESS Candidate Target List has
-deprioritized 2-minute targets at galactic latitudes less than
-$\approx 15^\circ$~\citep{stassun_TIC_2018,stassun_TIC8_2019}, which
-includes almost all star clusters\footnote{TICv8 has updated this to
-$10^\circ$, but for the first year of TESS observations, the number
-used when selecting target stars was $15^\circ$.}.  This is sensible,
-since the large pixel size and the high stellar surface density
-make aperture photometry unreliable.  
-However, it also means that a
-large number of stars in clusters that could yield transiting planets
-will go unprocessed by the official {\it TESS} data reduction
-pipeline.
-
-One way to quantify the blending problem is to ask what fraction of
-the total flux in a photometric aperture is contributed by a
-particular target star. Aperture photometry is reliable if this
-fraction is close to unity.  Based on the
-\citet{Kharchenko_et_al_2013} cluster membership data, and the density
-of background stars, we find that the median dilution fraction of
-stars with $T< 16$ is 0.13 for an aperture radius of 2 pixels.
-
-By combining difference imaging with forced-aperture photometry, we
-can avoid the primary effects of blending.  This is because in
-forced-aperture photometry the reference flux is determined from a
-calibrated catalog magnitude-to-flux relation.  The deviation from the
-reference is measured on the difference image.  Assuming that only a
-single source is causing the variability, blended neighbor stars only
-act to increase the poisson noise, and down not ``dilute'' transit
-signals, down to the angular resoution of the source catalog being
-used to determine the reference flux.  This is one of the main
-benefits of performing image subtraction in crowded fields.
-
-Of course, not all young stars are in crowded fields.  TESS
-observations of a few nearby non-crowded stellar assocations have
-already begun bearing fruit, notably DS Tuc Ab (TOI 200;
-\citealt{benatti_dstuc_2019,newton_dstuc_2019}), and perhaps the
-planet candidates TOI-450 and 451.  These objects are close and
-bright, and will be benchmark systems because they are relatively easy
-to characterize.  However, statistical studies of how stellar and
-planetary properties are affected by ages require tens of thousands of
-target stars.  This motivates us to also search the more crowded, and
-fainter fields.
-
-We have therefore opted to produce time-series photometry from the
-TESS images of any star that could be a member of a coeval group.  We
-are also including some stars that we suspect are young due to
-combined photometric and astrometric indicators.  We are using the
-difference imaging technique because of its benefits in modelling
-complex backgrounds in crowded regions.  While we hope to discover at
-least a few giant transiting planets, a separate hope is that the
-dataset might be useful to those wishing to study the time evolution
-of stellar processes.
-
-In the following, \S~\ref{sec:starselection} describes how we selected
-target stars. \S~\ref{sec:method} presents the photometric and image
-processing methods we used to produce light curves for these stars.
-The statistical properties of the \numberlcs light curves from TESS Sectors
-6 and 7 are then summarized (\S~\ref{subsec:lcstatistics}).  The
-procedure we used to identify and vet transiting planets is
-described in \S~\ref{subsec:identifying_ctois}, and the candidate
-planets are presented in \S~\ref{subsec:ctois}.
-\S~\ref{sec:discussion} discusses the additional work that is required
-to confirm or reject the planetary nature of these objects, and
-\S~\ref{sec:conclusion} summarizes our findings.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Method: Star Selection}
-\label{sec:starselection}
-
-\begin{figure*}[!t]
-	\begin{center}
-		\leavevmode
-		\includegraphics[width=0.9\textwidth]{target_star_positions.png}
-		%\gridline{\fig{target_star_cumulative_counts.pdf}{0.41\textwidth}{}}
-	\end{center}
-	\vspace{-0.8cm}
-	\caption{
-    Target star positions (blue) and predicted TESS
-    observing footprint (gray).
-    Target stars are either candidate members of clusters, or
-    else have other youth indicators (see \S~\ref{sec:starselection}).
-    Most will be observed for one or two lunar months over the course
-    of the TESS Prime Mission.
-    \label{fig:cdips_targets_positions}
-	}
-\end{figure*}
-
-\begin{figure}[!t]
-	\begin{center}
-		\leavevmode
-		%\includegraphics[width=0.45\textwidth]{target_star_cumulative_counts.png}
-		\gridline{\fig{target_star_cumulative_counts.pdf}{0.41\textwidth}{}}
-		\vspace{-0.8cm}
-		\gridline{\fig{target_star_hist_logt.pdf}{0.41\textwidth}{}}
-		\vspace{-0.8cm}
-		\gridline{\fig{target_star_reference_pie_chart.pdf}{0.41\textwidth}{}}
-	\end{center}
-	\vspace{-0.8cm}
-	\caption{
-		Target star statistics.
-		{\it Top.} Cumulative counts as a function of Gaia $Rp$-band
-		magnitude.  
-		{\it Middle.} Histogram of target star ages, for the subset of
-		stars with ages matched against \citet{Kharchenko_et_al_2013}.
-		{\it Bottom.} Provenance of cluster membership.  Percentages are
-		relative to $N_{\rm total}=1061446$ target stars. Symbols
-		are as follows.
-		D14 is \citet{dias_proper_2014}.
-		K13 is \citet{Kharchenko_et_al_2013}.
-		CG18 is \citet{cantat-gaudin_gaia_2018}.
-		Z18 is \citet{zari_3d_2018}, with upper main sequence and
-		pre-main-sequence samples sub-divided.
-		``$\geq 2$'' indicates at least two authors reported a star as a
-		candidate cluster member.
-		%``Other'' refers to sources enumerated in \S~\ref{sec:starselection}.
-		\label{fig:cdips_targets}
-	}
-\end{figure}
-
-\begin{figure*}[!t]
-	\gridline{\fig{mwscmatchstats.pdf}{0.95\textwidth}{}}
-	\vspace{-0.8cm}
-	\gridline{\fig{dias14matchstats.pdf}{0.95\textwidth}{}}
-	\vspace{-0.8cm}
-	\caption{
-		{\it Top.} Quality diagnostics from cross-matching
-		\cite{Kharchenko_et_al_2013} cluster members against Gaia-DR2.
-		histogram of the distances between matched stars is on the left; a
-		histogram of the difference between the true $G$-band magnitude
-		and that predicted from 2MASS photometry is in the middle; a scatter
-		plot of the same magnitude difference as a function of $G$-band
-		magnitude is on the right.
-		{\it Bottom.} Same, but cross-matching \cite{dias_proper_2014}
-		cluster members to Gaia-DR2.
-	}
-	\label{fig:xmatch_info}
-\end{figure*}
-
-The main aim of the CDIPS project is to increase the number of cluster
-stars for which photometric time-series are available, and thereby
-facilitate studies of exoplanetary and stellar processes across
-different times and stellar environments.  An essential step is
-therefore to define a sample of stars that are thought to be young, or
-members or clusters, or both.
-
-A homogeneous membership calculation for every known cluster is a
-rather large undertaking, and currently falls outside our scope.  So
-too is a homogeneous search for young stars across the galaxy.
-Instead, we have opted to collect and concatenate appropriate catalogs
-from across the literature.  We then use the resulting meta-catalog to
-identify our target stars within the TESS images.
-
-The probabilistic criteria for inclusion in our target star list is
-necessarily heterogeneous across different catalogs.  However, in our
-initial stellar selection our aim is completeness, not accuracy.  If
-there has been a claim in the literature that a star should be
-considered a cluster member, or a young star, we would like to err on
-the side of reporting a light curve for the star.  For stars that are
-photometrically interesting, we can then perform post-hoc quality
-checks using Gaia-DR2 astrometry and photometry to assess cluster
-membership and youth.
-
-\S~\ref{subsec:oc} describes the catalogs we used to identify
-candidate members of open clusters.  \S~\ref{subsec:mg} describes the
-catalogs we used to identify candidate members of moving groups,
-stellar associations, as well as young stars identified through
-combined Gaia photometry and astrometry.  \S~\ref{subsec:ocmgsummary}
-and Figure~\ref{fig:cdips_targets} describe summary statistics for the
-entire sample of about one million target stars.
-
-%FIXME: make table
-
-\subsection{Big catalogs: open clusters}
-\label{subsec:oc}
-
-At the time of writing, two relatively large, homogeneous cluster
-memberships studies had been performed using {\it Gaia}-DR2: those by
-\citet{cantat-gaudin_gaia_2018} and \citet{gaia_hr_2018}.
-There were also two large membership studies based on proper motion and 
-photometric catalogs that were of interest: the studies of
-\citet{Kharchenko_et_al_2013} and \citet{dias_proper_2014}.
-
-\paragraph{{\it Gaia}-derived OC memberships}
-
-\citet{cantat-gaudin_gaia_2018} used the UPMASK unsupervised membership
-assignment algorithm \citep{krone-martins_upmask_2014} to identify cluster
-members using Gaia-DR2 positions, proper motions, and parallaxes.
-They used {\it Gaia} photometry and radial velocities to then verify the
-claimed membership properties.  From their Table~2, we collect an initial
-401{,}448 cluster members, in 1229 clusters, down to their limiting magnitude
-of $G=18$.
-
-\citet{gaia_hr_2018} reported memberships for stars in a smaller, more
-select group of well-studied open clusters. From their Table~A1, we
-collect 40{,}903 cluster members, in 41 open clusters, mostly within
-$500\,{\rm pc}$. While this work also included memberships for
-globular clusters, we omitted these from consideration.
-
-Given the unprecedented quality of Gaia-DR2 astrometry, these two
-membership sources are our most reliable sources of membership
-information.  In our photometric reduction,  our default identifier
-for all sources is correspondingly the Gaia-DR2 \texttt{source\_id}.
-The TIC identifiers are found through a spatial cross-match after the
-light curves have been made, subject to the requirement that the
-Gaia-DR2 source identifiers match
-\citep{stassun_TIC_2018,stassun_TIC8_2019}.
-
-% We take this approach
-% because Gaia-DR2 is the base-catalog used to project sources from
-% celestial coordinates to the imaging plane (\S~\ref{sec:method}).  It
-% also has the advantage that for any Gaia-derived cluster memberships,
-% we can cross-match directly against source identifiers.
-
-\paragraph{Pre-{\it Gaia} OC memberships}
-\citet{Kharchenko_et_al_2013} used proper motions calculated in PPMXL
-\citep[][a combination of USNO-B1{.}0 and 2MASS
-astrometry]{roeser_ppmxl_2010} and near-infrared photometry from 2MASS
-\citep{skrutskie_tmass_2006} to report the existence of 2859 open
-clusters and stellar associations (globular clusters were omitted by
-excluding any entry of type \texttt{'g'}).  We selected the most
-probable cluster members (``$1\sigma$ members'') using the combined
-photometric, kinematic, and spatial criteria described by
-\citet[][Section~3.3]{kharchenko_global_2012}.  Then, to obtain {\it
-Gaia}-DR2 source identifiers for the members, we performed a
-crossmatch for {\it Gaia}-DR2 sources within 5 arcseconds of the
-listed positions.  To improve the quality of the cross-match, we
-additionally used the 2MASS photometry to predict the $G$-band
-magnitudes\footnote{See
-\url{https://gea.esac.esa.int/archive/documentation/GDR2/Data_processing/chap_cu5pho/sec_cu5pho_calibr/ssec_cu5pho_PhotTransf.html},
-online, \texttt{2019-03-29}, or \citet{carrasco_gaia_2016}}, and
-required that the measured $G$-magnitude fall within 2 magnitudes of
-the predicted $G$-magnitude.  If multiple neighbors matched the
-position and magnitude constraints, we took the nearest spatial
-neighbor as the match.  From 373{,}226 stars, this yielded a unique
-best neighbor for 352{,}332 stars (94.4\% of the sample), and a choice
-between two neighbors for 17{,}774 stars.
-
-%FIXME is this it?
-The second (non-{\it Gaia} derived) open cluster membership catalog we
-used was the \citet{dias_proper_2014} catalog, which was based on
-UCAC4 proper motions acquired by the US Naval Observatory
-\citep{zacharias_fourth_2013}.
-From their 1805 reported open clusters, we selected sources with
-quoted membership probability above 50\%.
-To obtain {\it Gaia}-DR2 source identifiers for the members, we
-performed a similar crossmatch as before, looking for sources within 5
-arcseconds of the listed positions, and within $\pm$2 $G$-band
-magnitudes of the prediction.
-From 2{,}034{,}269 stars, this yielded a unique
-best neighbor for 1{,}828{,}630 stars (89.9\% of the sample), and a choice
-between two neighbors for 8.7\% of the remaining sample.
-
-The distributions of various cross-matching statistics are shown in
-Figure~\ref{fig:xmatch_info}.  The distances between matches is
-typically below 1 arcsecond.  The Dias catalog shows somewhat stronger
-crowding effects at the faint end compared to the Kharchenko catalog,
-and likely has a larger number of false matches.
-At their faint ends, both catalogs show a tendency for true $G$-band
-magnitudes being somewhat larger than predicted $G$-band magnitudes,
-due to dust reddening.
-
-\subsection{Smaller catalogs: moving groups and stellar associations}
-\label{subsec:mg}
-
-Stars, moving groups and stellar associations are of interest for
-similar reasons as stars in open clusters.  Though fewer stars
-are known to exist in moving groups, they are of particular interest
-because moving groups are less crowded than open clusters, and are
-often closer to the Sun.
-
-We obtained Gaia-DR2 identifiers from the results of the following
-studies:
-\citet{gagne_banyan_XI_2018},
-\citet{gagne_banyan_XII_2018},
-\citet{gagne_banyan_XIII_2018},
-\citet{kraus_tucanahor_2014},
-\citet{roser_deep_2011}, % OC, not MG...
-\citet{bell_32ori_2017},
-\citet{rizzuto_multidimensional_2011},
-\citet{oh_comoving_2017}, and
-\citet{zari_3d_2018}. The methods applied in these studies
-vary from kinematic analyses, to astrometric analyses included
-Gaia-DR1 parallaxes, to photometric searches for infrared excesses, to
-spectroscopic studies including RVs, H$\alpha$
-emission, and Li absorption.
-
-For the Gagn\'e et al{.} catalogs, we searched the Gaia-DR2 archive for
-sources within 10 arcseconds of the listed positions.  If Gagn\'e et
-al{.} gave a proper motion, we required that the sign of each the Gaia
-proper motion components match that of the Gagn\'e values (the stated
-proper motion uncertainties seemed to have been underestimated).  We
-also imposed a $G<18$ cut on any putative matches.  Of 3012 moving
-group members collected from the three combined Gagn\'e et al{.}
-catalogs, we found 2702 matches.
-
-The \citet{kraus_tucanahor_2014}, \citet{roser_deep_2011}, and
-\citet{bell_32ori_2017} studies reported members in Tucana-Horologium,
-the Hyades, and 32$\,$Ori respectively.  Applying the same procedure as
-for the Gagn\'e catalogs gave 187, 684, and 119 best-neighbors
-respectively, compared to 205, 724, and 141 initially reported
-members.  Note that \citet{kraus_tucanahor_2014} found that only
-$\sim$70\% of their listed members have spectroscopic indicators
-consistent with their membership in Tucana-Horologium.
-
-\citet{rizzuto_multidimensional_2011} also focused on a single moving
-group: the Sco OB2 association. We used their reported Hipparcos
-identifiers, and matched against the {\it Gaia} archive's
-\texttt{hipparcos2\_best\_neighbour} table, which gave 319
-nearest-neigbor stars from 436 candidate members.
-
-Next, \citet{oh_comoving_2017} searched for comoving stars in the
-$\approx$2 million stars that overlapped between Tycho-2 and {\it
-Gaia}-DR1.  They found many wide binaries, and also identified a large
-number of comoving groups.  We chose the 2{,}134 stars that they
-reported were in groups with sizes of at least 3 stars.  Using their
-{\it Gaia}-DR1 source identifiers, we matched against the {\it Gaia}
-archive's \texttt{dr1\_neighbourhood} table, which gave 1{,}881
-nearest-neigbor stars in groups of at least three stars
-\citep{marrese_gaia_2019}.
-
-Finally, \citet{zari_3d_2018} constructed a sample of young stars
-within $500\,{\rm pc}$ using data from Gaia-DR2. Two subsamples were
-made: (a) an upper main sequence (MS) sample, with 86{,}102 stars, and
-(b) a pre-MS sample, with 43{,}719 stars.  Each was created from a
-careful combination of distinct astrometric and photometric cuts.
-These stars are the youngest, closest stars, spread across
-star-forming complexes in Sco-Cen, Orion, Vela, Taurus, and other
-regions of the sky.  Though many are not strictly identified with
-moving groups or open clusters, their reported youth and proximity to star
-forming regions justifies their inclusion in our search sample.
-
-\subsection{Summary of target stars}
-\label{subsec:ocmgsummary}
-
-After collecting the aforementioned lists, we merged them into a
-single table. We queried the \texttt{gaiadr2.gaia\_source} table to
-retrieve their photometric $G$, $G_{\rm Rp}$, and $G_{\rm Bp}$
-magnitudes, as well as their astrometric measurements $(\alpha,
-\delta, \mu_\alpha, \mu_\delta, \pi)$.  Finally, we required that
-$G_{\rm Rp} < 16$, which is roughly where the 1-hour photometric
-precision of TESS is predicted to reach 1\%
-\citep{ricker_transiting_2015}.
-
-All told, this procedure yielded 1{,}061{,}447 unique stars, from 13
-distinct membership catalogs.
-
-The relative fractions of stars from each catalog are shown in
-Figure~\ref{fig:cdips_targets}.
-The largest number of stars come from \citealt{dias_proper_2014}
-(44.3\% of stars), \citealt{Kharchenko_et_al_2013} (17.3\%),
-\citealt{cantat-gaudin_gaia_2018} (16.7\%), and \citealt{zari_3d_2018}
-(11.1\%, of which 7.8\% are OBA stars, and 3.3\% are pre-MS stars).
-107{,}647 of the stars, or about 10\%
-of the collection, have cluster memberships reported by multiple
-authors.  Since the membership probability calculations often use
-independent data and methods, agreement between multiple investigators
-on a given star's cluster membership is a helpful indication of it
-being a bonafide member.
-Stars reported in multiple catalogs have all available reference information
-concatenated.
-
-The fraction of target stars from each catalog which are bonafide
-cluster members should be understood to be heterogeneous.  For the
-\citet{dias_proper_2014} catalog, their membership calculation
-included only spatial and kinematic information, and we used a
-relatively low probability threshold when including their stars (based
-on the criteria \citealt{dias_proper_2014} used for their star
-counts).  The \citet{Kharchenko_et_al_2013} catalog combined spatial,
-kinematic, and photometric information to derive their membership
-probabilities.  We also used a somewhat more restrictive membership
-probability cut (again, following the criteria they used for their
-star counts), and so this sub-sample is likely less contaminated
-with field interlopers.
-\citet{cantat-gaudin_gaia_2018} used spatial, kinematic, and
-astrometric information from Gaia-DR2. Despite the lack of
-photometric information, the quality of the Gaia data suggest that the
-field contamination rate will be lowest for the
-\citet{cantat-gaudin_gaia_2018} sample.
-
-To assign unique cluster names, we adopted the name matched against
-\citet{Kharchenko_et_al_2013} whenever possible.
-Appendix~\ref{appendix:uniquenames} describes  how this was done in detail.
-For moving groups not identified in \citet{Kharchenko_et_al_2013}, we used
-the constellation-based naming convention from
-\citet{gagne_banyan_XI_2018}.  Otherwise, we used the name reported by
-the original catalog claiming membership.  This process reduced 16,425
-name permutations down to 3,216 unique cluster names.  Though we have
-made every effort to avoid duplicates, a small number may remain, so we
-advise inspection of the \texttt{cluster} column
-as well as the references given in the
-\texttt{reference} column rather than using the
-\texttt{unique\_cluster\_name} column to analyze individual objects
-of interest.  Nonetheless, 87.7\% of the $\sim$million unique target
-stars are matched to clusters within \citet{Kharchenko_et_al_2013},
-and 88.8\% are assigned a cluster name.  The remainder are mostly the
-young stars from \citet{zari_3d_2018}.
-Ages and their uncertainties are then merged against the 
-parameters reported by \citet{Kharchenko_et_al_2013}.
-
-The resulting CDIPS target star list is given in Table~N.
-The cumulative distribution of target star brightnesses, as well as a
-histogram of the ages, is shown in Figure~\ref{fig:cdips_targets}.
-Relative to field stars, our target star sample is young, with a
-typical age of 100$\,$Myr.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Method: Photometry}
-\label{sec:method}
-
-\begin{figure}[!t]
-	\begin{center}
-		\leavevmode
-		\includegraphics[width=0.3\textwidth]{pipelineoverview.pdf}
-	\end{center}
-	\vspace{-0.2cm}
-	\caption{
-    Conceptual overview of photometric reduction pipeline.
-    Details are given in \S~\ref{sec:method}.
-    %TODO: add latex section numbers!
-    %TODO: do FORCED aperture photomery on differenced images
-    %TODO: improve text generally
-	\label{fig:pipeline}
-	}
-\end{figure}
-
-\begin{figure*}[!t]
-    \begin{center}
-        \leavevmode
-        \includegraphics[width=0.95\textwidth]{stages_of_image_processing_good.png}
-    \end{center}
-    \vspace{-0.6cm}
-    \caption{
-        Stages of image processing for an image taken during the middle
-        of an orbit.
-        {\it Top right}. Calibrated image.
-        {\it Top left}. Smooth background estimate.
-        {\it Middle right}. Calibrated image minus its median pixel value.
-        {\it Middle left}. Calibrated image minus smooth background.
-        {\it Bottom left}. Registered difference image.
-        {\it Bottom right}. Zoom of difference image.
-        Each image is $(2048\times2048)$ pixels, except for the bottom-right 
-        image, which is $(500\times500)$.
-        All images except the top-right have the same color map.
-        The sector, camera, and CCD are (6, 1, 2).
-        \label{fig:stages_good}
-    }
-\end{figure*}
-
-\begin{figure*}[!t]
-    \begin{center}
-        \leavevmode
-        \includegraphics[width=0.95\textwidth]{stages_of_image_processing_bad.png}
-    \end{center}
-    \vspace{-0.6cm}
-    \caption{
-        Same sector, camera and CCD as Figure~\ref{fig:stages_good}, but for an image taken during
-        perigee passage, when scattered light from the Earth is
-        prominent.
-        A number of systematic artifacts are present,
-        including vertical ``straps'' and small-scale structure in scattered light
-        patches.
-        The quality of astrometric registration in the difference image is also
-        worse, leading to larger residuals in the lower-right panel.
-        \label{fig:stages_bad}
-    }
-\end{figure*}
-
-\subsection{Overview}
-
-To reduce the TESS images to light curves, we adopted an image
-subtraction approach.  The overall method is in the spirit of the
-reduction pipelines developed by \citet{Pal_2009},
-\citet{huang_high-precision_2015}, \citet{soares-furtado_image_2017}
-and \citet{oelkers_precision_2018}; a conceptual overview is given in
-Figure~\ref{fig:pipeline}.  Most sub-modules of our pipeline have been
-developed over the past decade to process HAT data \citep[{\it
-e.g.},][]{bakos_hat_review_2018}.  The specific high-level framework
-used for this reduction was adapted from a pipeline called
-\texttt{pipe-trex}, under development primarily for the HATPI project
-(\url{hatpi.org}).  The code is available
-online\footnote{\url{github.com/waqasbhatti/pipe-trex}, commit
-\texttt{cd9f9bb}.}.
-
-We begin our processing with the calibrated full frame images produced
-by the Science Processing Operations Center at NASA Ames
-(\S~\ref{subsec:observations}).  We then perform a collection of
-preparatory steps, including source extraction of bright stars,
-astrometric verification, and coarse simple aperture photometry of
-bright stars (\S~\ref{subsec:preparation}).  Using the information
-collected from these initial steps, we select an astrometric reference
-frame to which we transform all of the calibrated images.  We
-construct a photometric reference by stacking a subset of these
-transformed frames, after having convolved the frames to have
-identical stellar profiles. Finally, we subtract each target frame
-from the photometric reference (\S~\ref{subsec:imagesubtraction}).  We
-perform aperture photometry on the subtracted images using positions
-projected onto the frame from the Gaia-DR2 source catalog.  We detrend
-the resulting light curves (\S~\ref{subsec:lcdetrending}).  The
-resulting white noise and red noise properties of the light curves,
-and a few interesting cases of variability, are discussed in
-\S~\ref{sec:results}.
-
-\subsection{Observations}
-\label{subsec:observations}
-
-% How did TESS observe?
-% What processing steps happened in order to get the calibrated frames?
-% Why did we choose to start with them?
-
-The TESS spacecraft began science operations on July 25, 2018.  To
-keep its cameras pointed opposite the Sun, the spacecraft advances by
-$\approx$$28$ degrees east in ecliptic longitude every lunar month.
-Data acquired throughout each ``sector'' are downlinked at spacecraft
-perigee through the Deep Space Network.  Descriptions of the
-spacecraft's design and operations are given by
-\citet{ricker_transiting_2015} and the instrument handbook
-\citep{vanderspek_2018}.
-
-For us, the main data product of interest is the calibrated full frame
-image (FFI).  Each TESS camera is read out every 2 seconds.  To
-produce a manageable telemetric load, the resulting pixel values are
-averaged by the onboard computer into 30 minute exposures. An on-board
-cosmic ray mitigation algorithm is applied \citep[][\S
-5.1]{vanderspek_2018}. Once transmitted to the ground, the raw images
-are calibrated by the Science Processing Operations Center (SPOC).  The
-calibration process includes an overscan, bias, and dark current
-correction, and also divides out a flat field.  Details are discussed
-by \citet{clarke_kepler_2017}, and the resulting science data products
-are described by \citet{tess_data_product_description_2018}.
-
-We perform our processing using the calibrated images, their
-corresponding uncertainty images, and the associated headers.  The
-spacecraft has four cameras, and each camera has four CCDs.  In the
-following analysis, all image-level operations are thus performed on
-the images for each CCD, so that at any instant of time there are 16
-independent images that require analysis.
-
-While we performed numerous initial tests on the first sectors of
-data, by geometric coincidence Sectors 1--5 were pointed away from the
-galactic plane.  Consequently, less than 2\% of the CDIPS target star
-sample was observed in the first five TESS sectors.  Though a few
-interesting clusters are present in these observations ({\it e.g.},
-Blanco~1, NGC~2516, NGC~1901), for the present work we opted to focus
-on sectors in which there were more stars of interest for our intended
-science.  These begin in Sector 6 (2018-12-12, spacecraft orbit \#19).
-For this run of processing, they conclude at the end of Sector 7
-(2019-02-01, spacecraft orbit \#22).
-Sectors 6 and 7 cover galactic longitudes from roughly 200$^\circ$ to 280$^\circ$, 
-with fair coverage within $\pm 20^\circ$ of the galactic plane
-(Figure~\ref{fig:cdips_targets_positions}).
-
-\subsection{Image preparation \& background removal}
-\label{subsec:preparation}
-
-Before we can perform any kind of photometry, a few janitorial tasks
-are required.
-First, we convert the multi-extension calibrated FITS image from MAST
-into a single-extension FITS image, and trim to remove virtual rows
-and columns using the \texttt{SCIROWS}, \texttt{SCIROWE},
-\texttt{SCCSA}, and \texttt{SCCED} header values.
-
-In order to preemptively address the background variations present in
-some frames due to scattered light from the Earth and Moon
-\citep[see][\S 7.3.1--7.3.4]{vanderspek_2018}, we then estimate and
-subtract the large-scale background.  We do this by temporarily
-masking out pixels more than $2\sigma$ from the image median, and then
-pass a $48\times48$ median box filter over each pixel in the image,
-with reflective boundary conditions.  The resulting background
-estimate has low-amplitude structure over spatial scales of a few
-pixels, so we then blur it with a gaussian kernel to produce a smooth
-background estimate for each image.  These steps also remove a
-low-level vignetting present in the corners of many images, which
-remains even after flat-fielding \citep[see][\S
-7.3.5]{vanderspek_2018}.  
-The results are shown in the upper four panels of Figures~\ref{fig:stages_good}
-and~\ref{fig:stages_bad}.
-Features with spatial scales smaller than $\approx$48 pixel remain, 
-and large spatial scale scattered light patches are removed.
-
-% We found this background subtraction step to be particularly important
-% in our subsequent difference imaging analysis. In its absense, the
-% scattered light artifacts could introduce erroneous residuals into the
-% kernel solution used to match reference and target images.  Including
-% this step mitigated such effects, and helped produce clean
-% subtractions.  Even after subtraction, a small fraction of frames also
-% show sharp features (caustics) below our median box filter's size
-% scale.  Such features may affect flux measurements at specific times
-% in a small subset of light curves.
-
-After subtracting the background, we mask out saturated pixels using a
-fixed saturation level of $8\times10^4\,{\rm ADU}$. This value was
-chosen based on the onset of bleeding charge trails in the images, and
-is slightly greater than the saturation level of $2\times10^5$
-electrons, or about $4\times10^4\,{\rm ADU}$, quoted by
-\citet{vanderspek_2018}. 
-We correspondingly do not analyze stars brighter than $T\approx 6.5$.
-As described by \citet{Pal_2009}, the pixel masks are metadata to the
-image, and are only applied to the pixel values during the specific
-image processing steps in which they are necessary ({\it e.g.},
-convolution). We also extend the masks beyond purely saturated pixels
-to ``bloomed'' pixels horizontally and vertically adjacent to the
-saturated pixels (see Figure~6 of \citealt{Pal_2009}).
-
-Finally, for frames with the \texttt{DQUALITY} bit-flag corresponding
-to the ``momentum dumps'' and ``coarse pointing modes'' described by
-\citet{vanderspek_2018}, we omit the entire frame.  This removes on
-average a few frames per sector, out of about one thousand. Through
-visual inspection, we see that the stars on these frames are extremely
-smeared, and are unlikely to produce useful science data.  In
-addition, we use the sector-specific data release notes\footnote{\url{
-  archive.stsci.edu/tess/tess_drn.html}} to identify further times
-with anomalous spacecraft performance, which we omit from
-consideration.  For Sectors 6 and 7, this included three days at the
-beginning of Sector 6 dedicated to acquiring pixel response function
-data, and no additional gaps in Sector 7.
-%For Sectors 1 through 5, these
-%include coarse pointing windows from orbits 10, 13, 14, and an
-%instrumetal anomaly window in orbit 15.
-% For Sectors 6 through 8, these include three days at the beginning of
-% Sector 6 dedicated to acquiring pixel response function data, and also
-% about three days during Sector 8 lost to an instrument anomaly.
-
-\subsection{Metadata collection \& WCS verification}
-\label{subsec:metadatacollection}
-
-\begin{figure}[!t]
-	\gridline{\fig{astromresidual_hist.pdf}{0.5\textwidth}{}}
-	\vspace{-0.8cm}
-	\gridline{\fig{astromresidual_quiver.pdf}{0.5\textwidth}{}}
-  %\vspace{-0.8cm}
-	%\gridline{\fig{astromresidual_apertures.pdf}{0.5\textwidth}{}}
-	\vspace{-0.8cm}
-    \caption{
-		{\it Top.} Histogram of astrometric residual. The $x$-axis shows 
-		the distance between the measured centroid positions of stars, 
-		compared to the predicted positions from the WCS solution.
-		{\it Bottom.} Vector plot of astrometric residual. Each arrow is 
-		the vector from the measured to the projected star position. 
-		Directions are correct, but lengths are 50 times their true size for 
-		visualization purposes.
-    The systematic error in the top-right corner is a typical
-    problem generic to wide-field astrometry.
-    The frame chosen for this plot is the photometric reference frame used 
-    for Sector 6, Camera 1, CCD 1; we automatically 
-    impose cutoffs on the median and $90^{\rm th}$ percentile of the 
-    astrometric residual in order to ensure similar levels of astrometric 
-    precision are maintained throughout the reduction.
-	}
-	\label{fig:astromresid}
-\end{figure}
-
-Having prepared the images, we perform some initial analysis steps to
-produce metadata needed during image subtraction.
-
-First, we use \texttt{fistar} to perform source extraction on the
-thousand or so brightest, non-saturated stars in each image.  The
-source extraction derives centroid positions for these stars, and also
-fits elongated gaussians to their profiles, yielding the shape
-parameters $(s,d,k)$, where the flux $f$ as a function of position
-$(x,y)$ in the CCD image plane is assumed to take the form
-\begin{align}
-  f(x,y) &= B + A \exp \{ -0.5 \times [
-    s(\Delta x^2 + \Delta y^2) + \\
-    \nonumber
-    &d(\Delta x^2 - \Delta y^2) +
-    k(2\Delta x \Delta y)
-  ]  \},
-\end{align}
-for $(x_0,y_0)$ arbitrary reference positions,
-$\Delta x = x-x_0$, $\Delta y = y - y_0$, $B$ is the background
-level, and $A$ is an arbitrary
-flux-scaling constant.
-For a nearly circular shape profile, the sharpness $s$ is related to
-the FWHM as ${\rm FWHM} \approx 2.35\sqrt{s}$ \citep[{\it
-e.g.},][]{Pal_2009}.  These shape parameters are later used when
-selecting an astrometric reference frame
-(\S~\ref{subsec:imagesubtraction}).  
-In agreement with what is obvious upon visual inspection, this 
-fitting process shows that stars closer to the
-center of each camera's field are round, while
-stars near the field edges are more triangular.
-
-For the astrometric solution, we use the World Coordinate System (WCS)
-and fourth-order Simple Imaging Polynomial (SIP) coefficients
-derived by SPOC and included in the FFI headers
-\citep[][Sec.~8]{pence_fits_2010}.  We explored the possibility of
-using \texttt{astrometry.net} \citep{lang_2010} to derive our own
-astrometric solutions for each frame, but found that the astrometric
-residual (the mean separation between projected and measured
-positions) was consistently a factor of 1.5-2 times higher in our WCS
-solutions than in those given by SPOC.  This was perhaps because
-we did not invest major amounts of time developing a robust
-algorithm to select non-blended stars of intermediate brightness before
-measuring their positions.
-
-With the resulting WCS information, we then project a source catalog
-onto each frame.  Initially, we planned to photometer all Gaia-DR2
-sources in each field down to a cutoff of $G_{Rp} < 16$.  However, we
-found that for the galactic plane fields this produces an excessively
-large number of sources (millions of stars per
-$12^\circ\times12^\circ$ CCD).  We therefore limited our source
-catalog for each frame to be
-a combination of the CDIPS target stars ($G_{Rp} < 16$), and
-all Gaia-DR2 sources down to $G_{Rp} < 13$.  We use the
-projected positions of these sources to center the apertures in our
-photometry,
-rather than attempting to detect the positions.  Such
-``forced-aperture photometry'' is preferable to source
-extraction in the crowded fields that are central to this work.  The
-Gaia-DR2 epoch is J2015.5, so even the fastest-moving stars with
-proper motions of $\sim$$1\,{\rm arcsecond}\,{\rm yr}^{-1}$ are still
-well within one pixel of their predicted positions in the TESS images.
-The projection from catalog sky-coordinate positions to pixel
-coordinates is performed using an analog of the \texttt{wcs-rd2xy}
-program that performs the standard matrix algebra \citep{lang_2010}.
-The source catalog look-up is performed using
-\texttt{gaia2read}\footnote{\url{github.com/samuelyeewl/gaia2read}}
-\citep{kim_2018_gaia2read}.
-
-The residual between the measured and projected stellar centroid
-positions is displayed for one photometric reference frame in
-Figure~\ref{fig:astromresid}.
-The construction of this frame will be described shortly, however
-a few salient points can first be made.
-First, the typical median precision of the WCS solution is a bit below
-0.1 pixels, and its $90^{\rm th}$ percentile is typically less than
-0.3 pixels\footnote{In fact, in our reduction we automatically impose
-that the median residual and 90th percentile remain below 0.2 and 0.4
-pixels, respectively.}.
-%The distribution has a outlier tail of saturated stars which were
-%masked, and thus do not have measureable centroid positions.
-The errors are typically largest in the corners of the field of view,
-where the non-linearity of the focal plane is most significant, and
-where the corrections required by the SIP coefficients are largest.
-%The final sub-panel of Figure~\ref{fig:astrometricresidual} is a
-%sanity check on the location of the projected positions, and also
-%gives some context for our chosen aperture radii of 1, 1.5, and 2.25
-%pixels.
-
-As a final step of metadata collection, we perform aperture photometry on the
-bright stars by summing the counts inside appropriately-weighted
-circular apertures centered on the projected positions. This task is
-performed using \texttt{fiphot}.
-The pixel weights are equal to the fraction of the pixel
-that falls within the aperture.  They are thus unity for pixels
-entirely within the aperture, and fractional along the aperture
-boundary. % (see \citealt{Pal_2009} Fig 17). 
-The background levels are measured in annuli around each aperture
-center. 
-%The raw flux of the object after background removal is then
-%(\citealt{Pal_2009} Eq 65)
-%\begin{equation}
-%  f = \sum_{x,y} w_{x,y} (I_{x,y} - B) = f_{\rm total} - B r_0^2.
-%  \label{eq:simple_aperture_phot}
-%\end{equation}
-The resulting measurements, for instance of the background level of
-each aperture, and the number of stars with ``good'' photometry,
-are later used to select photometric reference frames.
-
-\subsection{Image subtraction}
-\label{subsec:imagesubtraction}
-
-\subsubsection{History of image subtraction method}
-The core operation of ``classical'' image subtraction
-attempts to match a photometric reference $R$ and a target image $I$ by 
-computing and applying a convolution kernel.
-For ground-based data, this ``match'' typically corrects for
-differences in seeing or transparency between the reference and
-target; for space-based data, the match might correct for spacecraft
-jitter, or thermal and corresponding point-spread function (PSF)
-variations.
-The kernel, once applied to the high signal-to noise reference,
-produces a model image, $M_{xy}$,
-\begin{equation}
-    M_{xy} = (R \otimes K)_{xy} + B_{xy},
-    \label{eq:imagemodel}
-\end{equation}
-where $B_{xy}$ is a component of the model image that allows for
-background variations, and $\otimes$ denotes convolution.
-Since we modeled the background separately (\S~\ref{subsec:preparation}),
-we set $B_{xy}=0$.
-The convolution kernel $K$ is typically decomposed onto a
-basis, $K = \sum_i c_i K_i$, and the coefficients are found
-by minimizing
-\begin{equation}
-    \chi^2 = \sum_{xy} \left( \frac{I_{xy} - M_{xy}}{\sigma_{xy}} \right)^2,
-    \label{eq:chisq_conv}
-\end{equation}
-where $\sigma_{xy}$ is the uncertainty in the target image pixel values.
-Photometry is then performed on the difference image $D_{xy}$, where
-$D_{xy} = I_{xy} - M_{xy}$.
-For the present reduction, the uncertainty in each target image pixel was
-taken to be a constant.
-
-The general procedure described above was first proposed by \citet{Alard_Lupton_1998}.
-It was reviewed and clarified by \citet{miller_optimal_2008}.
-The choice of how to decompose the kernel was further explored by
-\citet{bramich_new_2008}, who showed that using a linear combination
-of delta functions had advantages compared to a basis of gaussians.
-We perform the convolution using \texttt{ficonv}, and opt for the
-implementation of Bramich's method (see \citealt{Pal_2009} \S~2.8).
-The lower panels of
-Figure~\ref{fig:stages_good} show the procedure
-working well, and producing a ``clean'' difference image.
-Figure~\ref{fig:stages_bad} shows what happens for an
-image taken when scattered light from the Earth causes the
-model image $M_{xy}$ to be a poor fit to the target image $I_{xy}$, 
-leading to a number of systematic artificats.
-
-\subsubsection{Astrometric registration}
-We now describe some implementation details we used to make the
-above high-level picture work.
-First, we needed to select two ``reference frames'' for image subtraction:
-(1) the astrometric reference; and (2) the photometric reference.
-
-To choose the astrometric reference, we searched for frames with
-large, round stars (big $s$, small $d$ and $k$ values).
-We also required
-that the frame have minimal background noise, as measured in annuli
-around the bright stars selected in \S~\ref{subsec:preparation}.
-Finally, the astrometric reference frame needed to have, relative to the 
-other frames being
-considered, a large number of detected sources.
-We sorted the frames using these metrics, and then selected the
-astrometric reference from successive intersections of each sorted
-list.
-
-We then
-used the \texttt{grmatch} and \texttt{grtrans} tools to
-compute and apply a spatial transformation of each calibrated frame
-to match the astrometric reference frame.
-The transformation is calculated using the measured source positions
-found in ~\S~\ref{subsec:metadatacollection},
-and the symmetric triangle point-matching scheme described
-by \citet[][~\S~2.5.2]{Pal_2009}.
-The transformation~--~a combination of rotation, dilation, and
-translation~--~typically moves stars by less than a pixel, since
-the TESS spacecraft is quite stable.
-The precision of the transformation is guaranteed by forcing 
-its unitarity $\Lambda$ to always be below 0.01, where 
-$\Lambda$ is defined by \citet[][~Eq.~54]{Pal_2009}.
-We reduced the photometric errors
-incurred during this step by using
-the flux-conserving interpolation
-scheme described by \citet{Pal_2009},
-which was necessary because polynomial interpolation schemes
-do not conserve stellar flux.
-
-\subsubsection{Photometric reference frame construction \& reference flux measurement}
-
-The second required reference frame is the
-photometric reference, which is used both to calculate the
-convolution kernel, and to obtain a
-reference flux for each star.  
-To make it, we first chose 50
-sub-frames with low scatter in their photometry
-and low background measurements, according to the metadata collected
-in \S~\ref{subsec:preparation}.
-We then convolved these candidate photometric reference frame to the best
-frame, and performed a median average over the entire stack
-to make the photometric reference.
-
-%\begin{enumerate}
-%  \item Lowest median scatter in photometry
-%  \item Lowest median error in photometry
-%  \item Lowest median background measurement
-%  \item Lowest median absolute deviation in background measurements
-%  \item Largest number of stars detected by \texttt{fiphot} with good
-%    flags.
-    % fiphot files used for all of this.
-%\end{enumerate}
-
-Measuring the reference flux for each star is a slightly non-trivial
-operation.
-First, we perform forced simple aperture photometry to measure
-the flux for each source.
-The local background is estimated in annuli, with neighboring stars
-masked out during the background measurement.
-However if we were to stop here, {\it it would be a bad mistake}.
-The reference fluxes for faint stars would be overestimated, due to
-crowding.
-The relative amplitude of photometric signals would correspondingly
-be biased small, hindering exoplanet detection.
-
-Therefore, after performing simple aperture photometry on the 
-reference frame, we fitted an aperture-size specific zero point
-between the catalog $T$-band magnitude of each star, and its
-measured flux.
-The $T$-band magnitude was calculated according to Equation~1 of 
-\citet{stassun_TIC8_2019}.
-We then use the known catalog magnitude to predict the expected
-reference flux for each star.
-In effect, this minimizes crowding down to Gaia's resolution limit of
-$\approx$1$''$, rather than the TESS limit of $\approx$20$''$.
-
-Following \citet{Pal_2009}~Equation~83,
-the final instrumental flux values $f$ we report\footnote{For example,
-the \texttt{IFL1} column.} are then equal to
-\begin{align}
-f &=  f_{\rm reference} + f_{\rm subtracted} \\
-&=
-g \left(T_{\rm cat} \right)
-+
-\frac{1}{|| K ||_1^2} \sum_{x,y} D_{x,y} (w \otimes K)_{x,y}.
-\label{eq:ism_flux_measurement}
-\end{align}
-The function $g$ takes as input the target star's
-catalog magnitude $T_{\rm cat}$, and returns the reference flux.
-Its coefficients have been fit per the procedure just discussed,
-independently for each aperture.
-The difference image $D$ is equal to $I -  R\otimes K$,
-where as in Equation~\ref{eq:imagemodel}, $I$ is the target image 
-transformed to the astrometric
-reference, $R$ is the photometric reference, and $K$ is the convolution
-kernel.
-The weights $w$ from the circular aperture mask are included in
-the convolution.
-The norm $|| K ||_1$ is defined by \citet{Pal_2009}~Equation~81.
-
-\subsection{Choice of convolution kernel}
-A few brief notes on the algorithm to actually solve for the
-coefficients to the convolution kernel.  The procedure implemented in
-\texttt{ficonv} is to subdivide the image, and within each grid
-element find the brightest non-saturated star. These isolated
-``stamp'' stars are then used to solve for the coefficients of the
-kernel, by minimizing Equation~\ref{eq:chisq_conv} over the sum of all
-stamps.
-
-%NOTE : this is kind of incomprehensible
-%CHECK: does the polynomial weighting actually do what you want it to do?
-For the choice of basis, we opt for a delta-function kernel with an additive
-flux scaling term (\citealt{soares-furtado_image_2017} Section 3.3.1
-gives the equations).
-The spatial variations of the PSF are captured by weighting the 
-delta function and the flux scaling terms with varying
-polynomial orders across the image.
-Choosing this kernel introduces three additional
-free parameters:
-(1) the kernel box-size;
-(2) the maximum order of the polynomial weighting the delta function terms;
-(3) the maximum order of the polynomial weighting the flux scaling.
-We performed a grid-search to tune these parameters, in
-which our metrics for success included the measured RMS as
-a function of magnitude, and also the recovered SNR of transits from
-the catalog of known TOIs (TESS Objects of Interest; N.~Guerrero, in prep).
-
-Varying the kernel box-size, we found that kernels with box-length smaller than the 
-typical TESS FWHM at field center ($\approx$3 pixels) produced light curves
-with the highest average scatter.
-Increasing the kernel box-size from a $3\times3$ box to a $7\times7$ box led
-to about a 50\% reduction in RMS for bright stars, and no difference for 
-faint stars.
-The largest kernels, of $(11\times11)$ pixels, had on average slightly lower 
-signal-to-noise for recovered transits than for kernels of intermediate size.
-We settled on a kernel box-size of $(7\times7)$ pixels, in part because the 
-FWHM at the camera corners can grow by factors of $\approx$2 relative to the 
-field center.
-
-Varying the polynomial orders, we found that the highest order polynomials 
-retrieved transits with $\approx10\%$ worse SNR compared to lower order
-polynomials.
-Varying the polynomial orders between 1 and 4 did not produce large 
-differences.
-
-Averaging over all TOIs present in the camera we used for these experiments, 
-we found that different choices 
-of kernel parameters produced variations of $\lesssim 12\%$ in the retrieved 
-transit SNR.  
-For computational expediency, we therefore chose a single
-$(7\times 7)$ kernel with 
-second-order spatial polynomial weights in the basis functions for the
-remainder of our reduction.
-However, we caution that within our parameter-tuning experiments, the 
-recovered SNR of perhaps a third of the TOIs varied by up to a factor of two,
-which in a few 
-cases led to non-detections of transit signals near the noise floor.
-In the longer term, developing an image-subtraction method that marginalizes 
-over uncertainties of how to chose ``optimal'' kernels would be desirable.
-Pixel-level image subtraction methods that omit these 
-parameters entirely 
-are also worth exploring \citep{wang_pixel-level_2017}.
-
-With a kernel selected, and the convolution and subtraction performed, 
-we calculate the instrumental fluxes for each frame per 
-Equation~\ref{eq:ism_flux_measurement}. 
-We did this with three different aperture sizes: for this work, circles
-of radii 1 pixel, 1.5 pixels, and 2.25 pixels.
-These sizes were chosen to roughly span the range of optimal aperture
-sizes for stars in our sample, as calcuated from the pre-flight
-\citet{Sullivan_et_al_2015} noise model.
-Finally, to convert from a list of 
-flux measurements for each source on a frame to a list of flux values
-at any given time, we used the 
-\texttt{grcollect} transposition tool.
-
-\subsection{Light curve detrending}
-\label{subsec:lcdetrending}
-
-\begin{figure*}[!t]
-	\gridline{
-    \fig{raw_light_curve_systematics_sec6cam1ccd2.pdf}{0.48\textwidth}{}
-    \fig{raw_light_curve_systematics_sec7cam2ccd4.pdf}{0.48\textwidth}{}
-  }
-	\vspace{-0.5cm}
-	\caption{
-	Twenty randomly selected raw image-subtracted light curves drawn
-	from the same sector, camera,
-	and CCD, for stars with $T$-band magnitudes between 13 and 14.
-	A number of systematic trends are shared across the light curves.
-	The sector, camera, and CCD numbers are 6, 1, 2 (left) and 7, 2, 4 (right).
-	\label{fig:lc_systematics}
-	}
-\end{figure*}
-
-\begin{figure}[!t]
-	\begin{center}
-		\leavevmode
-		\includegraphics[width=0.44\textwidth]{external_parameters_vs_time_sec6cam1ccd1.pdf}
-	\end{center}
-	\vspace{-0.5cm}
-	\caption{
-    The variability in flux is sometimes correlated with variability in
-	``external'' parameters, shown here for a representative star
-    over two orbits.  {\it Top}: Instrumental raw magnitude (with a
-    particular aperture size), as a function of time.  
-    Continuing in order are $x$ and $y$ centroid positions as a functions of
-    time, the $(s,d,k)$ PSF shape parameters,
-    the CCD temperature,  and the measured background value.
-    Differential aberration affect the centroid position over the span of each orbit.
-    Momentum dumps are
-    marked with vertical dashed lines, and affect the measured shapes of stars.
-		\label{fig:external_parameter_timeseries}
-	}
-\end{figure}
-
-The preceding steps produce light curves that include both
-instrumental systematics as well as astrophysical variability.
-Figure~\ref{fig:lc_systematics} shows twenty stars of
-comparable brightness randomly selected from two CCDs.  Stars that are
-far apart on the same CCD share similar changes in flux.
-In other words, the instrumental systematics seem to dominate.
-This problem is generic to most wide-field photometric datasets, including
-those from {\it e.g.}, the WASP, HAT, and Kepler surveys.
-To remove the systematic variability, we adopted two different
-approaches: {\it (i)} the trend-filtering algorithm (TFA,
-\citealt{kovacs_trend_2005}), and {\it (ii)} a principal component analysis
-(PCA).
-
-However, a number of other approaches to the problem
-were possible. To encourage
-future improvements, we describe the
-possibility of decorrelating against external parameters
-(\S~\ref{subsubsec:external}), and also describe different approaches
-to ensemble detrending (\S~\ref{subsubsec:ensemble}), before
-explaining our implementation.
-
-\subsubsection{Decorrelating against external parameters}
-\label{subsubsec:external}
-
-Often, ensemble trends of stellar magnitude with CCD position,
-sub-pixel position, catalog magnitude, and color are present in
-datasets.  One detrending step that can be valuable is to fit and
-subtract a linear combination of these trends as they appear across
-many light curves \citep[{\it
-e.g.},][\S~5.5]{zhang_precision_2016}.
-
-A separate step for each light curve can then be to fit out linear
-correlations of stellar magnitude with ``external parameters'' (EPD,
-\citealt[][]{bakos_2010,huang_high-precision_2015}).  For ground-based
-data these parameters might include zenith angle, or changing PSF shape.  For
-TESS data, they might include CCD temperature, or the angles of the
-Moon and Earth relative to each camera's boresight.  
-They might also include the standard deviation of the spacecraft
-quartnerion time-series \citep{vanderburg_hr858_2019}.
-Some example ``external'' parameters that we include with our light
-curves are shown as functions of time in
-Figure~\ref{fig:external_parameter_timeseries}.
-
-We explored the possibility of fitting linear models of flux as
-functions of {\it e.g.,} temperature, shape parameters, and centroid
-positions to each light curve.  We also briefly explored non-linear
-model fitting using $N$-dimensional B-splines to fit the flux,
-centroid positions, and temperatures simultaneously
-\citep{dierckx_curve_1996}.  The linear models typically underfit the
-light curves, particularly during the large shifts that happen as the
-spacecraft nears perigee.  The non-linear models showed some promise,
-but often seemed to overfit stellar variability signals.  Given these
-complications, for the time being we omitted the step of ``detrending''
-as a function of external parameters. To enable further exploration of
-the issue, we included all the necessary vectors of {\it e.g.},
-centroid positions, temperatures, and shape parameters in our reported
-light curves.
-
-\subsubsection{Ensemble detrending}
-\label{subsubsec:ensemble}
-
-The parameters that capture systematic trends are often poorly known.
-In such cases, an effective model of the systematics comes from
-constructing a set of vectors that empirically captures trends common
-to many stars.  Each target light curve is then assumed to be a linear
-combination of the trend vectors.
-
-The well-known algorithms, TFA, Sys-Rem, PDC-MAP, and ARC2, all take
-slightly different approaches to constructing this set of basis
-vectors, as well as to solving for the weights to assign each linear
-component
-\citep{kovacs_trend_2005,tamuz_correcting_2005,smith_pdc_2012,aigrain_robust_2017}.
-TFA selects individual ``template stars'' as basis vectors, and
-equally weights each template when solving for the coefficients via
-linear least squares.  PDC-MAP computes ``co-trending basis vectors''
-(CBVs) by applying singular value decomposition to the light curves
-that show the strongest mutual correlation.  It solves for the
-coefficients through a two-step procedure.  The first step is to
-calculate the coefficients through linear least squares.  The
-least-squares coefficients are then used to construct a prior over
-plausible coefficient values, which is then used to recompute the
-maximum likelihood coefficients for each star.  This latter step
-reduces overfitting for stars with variability not present in the set
-of CBVs.
-
-We opted to use two different detrending approaches, each aimed
-at a different use case.  For transit-search related science,
-we used TFA, as implemented by \texttt{VARTOOLS}
-\citep{kovacs_trend_2005,Hartman_Bakos_2016}.  For stellar
-astrophysics related work, we used a simple variant of PCA, as
-implemented in \texttt{scikit-learn} \citep{sklearn_2011}.  For
-self-consistency, we describe each method and its implementation in
-the following paragraphs.
-
-\paragraph{TFA detrending}
-
-The idea of TFA is as follows.  Suppose we have $M$ ``template
-stars'', which are a subsample of stars that represent all types of
-systematics across the dataset.  Each template star has a light curve
-with $N$ data points.  Denote the template time-series $X_j(i)$, where
-$j={1,\ldots,M}$ and $i={1,\ldots,N}$ is the time index.  We then want
-to find periodic signals in a target time-series $Y(i)$.  This is done
-by defining a filter function
-\begin{equation}
-  F(i) = \sum_{j=1}^{M} c_j X_j(i),
-\end{equation}
-for which the coefficients $c_j$ are found by minimizing
-\begin{equation}
-  \mathcal{D} = \sum_{i=1}^{N} \left[ Y(i) - A(i) - F(i) \right]^2.
-  \label{eq:tfa_to_minimize}
-\end{equation}
-When trying to find periodic signals, $A(i)$ represents our prior
-knowledge of the light curve's shape.  This prior is simply that stars
-on average maintain a constant brightness:
-\begin{equation}
-  A(i) = \langle Y \rangle = \frac{1}{N} \sum_{i=1}^{N} Y(i) = {\rm const.}
-\end{equation}
-If a signal is eventually found, for instance using the box-least
-squares method \citep{kovacs_box-fitting_2002}, this detrending
-process must then be repeated while accounting for our updated
-knowledge about the light curve's shape.
-
-Some implementation notes follow.  We selected template stars in two
-stages.  In the first stage, we fitted a parabola in the RMS-magnitude
-plane, and discarded stars more than $2\sigma$ away from the
-prediction of the fit.  We also required that these initial candidate
-stars have intermediate brightness ($8.5 > T > 13$), and have a
-relatively large number of time-series data points.  We then performed
-an initial iteration of TFA, on only the candidate template stars.  We
-inspected the resulting detrended light curves for residual structure
-by computing a Lomb-Scargle periodogram.  If the maximum-power peak
-had a false alarm probability below 0.1\%, we excluded the star from
-the list of candidate template stars, on the basis of its presumed
-periodic variability.  We then randomly selected at most 200 template
-stars from the remaining non-variable candidates.  The choice of
-number of template stars was discussed by \citet{kovacs_trend_2005},
-and is another free parameter in the broad problem of light curve
-production.  This choice is analogous to the issue of how many
-cotrending basis vectors to choose in PDC-MAP or ARC2
-\citep{aigrain_robust_2017}.  While the number of template stars can
-be optimized by constructing and minimizing a BIC-like quantity, a
-little overfitting is acceptable for our pupose of finding planetary
-transits.  For other applications, {\it e.g.,} stellar rotation period
-searches, it is almost certainly preferable to adopt a less forceful
-detrending approach.
-
-\paragraph{PCA detrending}
-
-To remove the largest systematic trends with minimal overfitting of
-{\it e.g.}, stellar rotation signals, we adopted a simple variant of PCA
-(see {\it e.g.}, \citealt{ivezic_statistics_2014} for a review).  A similar
-approach was taken by \citet{feinstein_eleanor_2019} in
-\texttt{eleanor}.  We derived the principal components for each CCD
-using the 200 template stars previously selected for TFA.
-We then modelled each target light curve as a linear combination of a
-subset of these principal components, with weights determined by
-linear least squares.
-
-To determine the ``optimal'' number of principal components to use, we
-performed a cross-validation analysis on the template stars using the
-components derived both from PCA, as well as a separate factor
-analysis.  As is typically the case when the noise variance is
-different for each ``feature'' (each point in time), we found that
-$k$-folding cross-validation using PCA failed to recover a plausible
-number of components\footnote{See for example
-\url{https://scikit-learn.org/stable/auto_examples/decomposition/plot_pca_vs_fa_model_selection.html}}.
-However, the factor analysis typically maximized the cross-validation
-score with anywhere from $10$ to $15$ components, which agreed with a
-visual analysis of the number of PCA components past which overfitting
-began.  We therefore used the maximum cross-validation score 
-from thefactor analysis
-as the number of principal components to use in each light curve.
-This number is
-documented in the \texttt{FITS} headers of each light curve.
-
-% In \S~\ref{sec:flux_vs_external_parameters}, we describe the
-% ``external parameter'' dependence visible in our reduction of
-% the TESS data.
-% Ordinary linear model-fitting, as well as an initial attempts
-% at non-linear model fitting, are poor descriptions of the data.  
-% In a similar vein ``magnitude-fitting'' is minimally justified, given
-% how the TESS magnitudes correlate against these external parameters.
-% We go on to show (\S~\ref{sec:tfa_is_good_enough}) that a plausible
-% detrending approach for the purpose of transit discovery is to simply
-% decorrelate against other nearby stars with standard TFA.
-%
-
-% \subsubsection{Flux versus external parameters}
-% \label{sec:flux_vs_external_parameters}
-% 
-% 
-% % \begin{figure*}[t]
-% %     \begin{center}
-% % 		\includegraphics[height=0.9\textheight]{mag_vs_epdparams.png}
-% %     \end{center}
-% %     \vspace{-0.5cm}
-% %     \caption{
-% %       {\bf Flux as a function of ``external parameters'' for four
-% %       representative stars.} The left two columns are stars at the
-% %       corner of a camera's field; the right two columns are from the
-% %       centers.
-% %       Each row shows a different parameter along the $x$-axis, given
-% %       in text at the bottom right of each subplot.
-% %       ``Hooks'' are common features in flux as a function of
-% %       temperature and centroid position.
-% %       \S~\ref{sec:flux_vs_external_parameters} gives a verbose
-% %       description.
-% %      \label{fig:flux_vs_external_parameters}
-% %     }
-% % \end{figure*}
-% 
-% The traditional approach to EPD is to fit and
-% subtract a model for the magnitudes $m$ of the form
-% \begin{equation}
-%   m = {\rm const.} + \sum_i c_i \theta_i,
-%   \label{eq:classical_EPD}
-% \end{equation}
-% where $\vec{\theta}$ is a vector of parameters such as the shape
-% parameters $(s,d,k)$, their products $(s^2, s\cdot d, d^2, \ldots)$,
-% the temperature $T$ of the instrument or environment\footnote{ We used
-% the temperature from the on-chip aluminum-copper sensor measurements
-% included in the engineering
-% data: \url{archive.stsci.edu/missions/tess/engineering/}.  },
-% the centroid positions $(x,y)$, the fractional part of the
-% centroid positions $(\{x\},\{y\})$, and any other parameters that are
-% expected\footnote{ The fractional centroid positions might matter
-% because intra-pixel quantum efficiency variations could affect the
-% measured stellar brightness.  The varying temperature $T$ of the CCD
-% electronics might matter.  } to correlate strongly with the observed
-% flux.  The coefficients $c_i$ are calculated through linear
-% least-squares, and subtracted to produce ``EPD'' light curves.
-% 
-% The premise of this model is that the correlations between the
-% magnitudes and the external parameters are linear.  For ground-based
-% CCD data (e.g., HATNet, HATS, and Nikon DSLRs), \citet{bakos_2010} and
-% \citet{zhang_precision_2016} have verified that this model is a
-% good description to the data.
-% To discern whether such a model extends to the TESS data, we examined
-% scatter plots of each parameter, as a function of all the other
-% parameters.  We also examined plots of each parameter as a function of
-% time.  A few prominent trends were present.
-% 
-% \begin{enumerate}
-% 
-% \item {\it Flux vs.\ time}. Most of the light curves we examined showed a secular
-%     drift with amplitude $0.01\,{\rm mag}$ over the timescale of each
-%     orbit.  Sharper trends (``hooks'') at the beginning of each orbit
-%     seemed to be less prominent for stars at the corners of the fields
-%     than stars at the center.  The periodicity incurred by the
-%     2.5$\,{\rm day}$ momentum dumps was also noticeable in more of the
-%     light curves at the center of the field than at the corners.
-% 
-% \item {\it Flux vs.\ centroid positions}. The flux as a function of
-%   centroid position often showed non-linear ``hooks''
-%     %(see Figure \ref{fig:flux_vs_external_parameters}).
-%     Most of the data points from a given orbit reside at a given
-%     level, but about 10\% are in a tail. This was seen in light curves
-%     all across the TESS field of view.
-% 
-% \item {\it Flux vs.\ temperature} exhibited similar hooks, with most of
-%   the flux values residing at a particular level, and perhaps 10\%
-%     following a non-linear path (often resembling the Nike ``swoosh'')
-%     away from the bulk of points.
-% 
-% \item {\it Flux vs.\ shape parameters}.  For light curves in the corner
-%   of the field of view, similar hooks are present in flux {\it vs.}
-%     $(s,d,k)$, though the hooks are less sharp.  In the center of the
-%     field of view, gaussian ellipses are a better description of the
-%     flux {\it vs.} the shape parameters.
-%     
-% \end{enumerate}
-% 
-% Considering the timeseries of parameters other than flux 
-% (Figure~\ref{fig:external_parameter_timeseries}):
-% 
-% \begin{enumerate}
-% 
-% \item {\it Centroid positions vs\ time}.  The main variability in the
-%   centroid positions as a function of time is a secular drift, that is
-%     reset every orbit.  The 2.5 day momentum wheel dump is
-%     superimposed on this secular drift, and has smaller amplitude than
-%     the drift.
-% 
-% \item {\it Temperature vs.\ time}.  The main variability in temperature
-%   {\it vs.} time is a secular drift of the same timescale as that for
-%     the centroid positions timeseries.
-% 
-% \item {\it Shape parameters vs.\ time}.  The main variability in the
-%   shape parameters as a function of time is the 2.5 day momentum wheel
-%     dump periodicity, with hooks before each momentum dump.
-% 
-% \item {\it Background value vs.\ time}.  The background is typically stable, 
-% except when scattered light from the Earth or Moon enters the frame (visible 
-% towards the end of each orbit in 
-% Figure~\ref{fig:external_parameter_timeseries}).
-% 
-% \end{enumerate}
-% 
-% Given the characteristics of the variability, a linear model of the
-% form given in Equation~\ref{eq:classical_EPD} is not applicable.  To
-% fit out the correlations between flux and parameters which most
-% commonly exhibited ``hooks'', we explored fitting a parametric open
-% curve (an $N$-dimensional B-spline, \citealt{dierckx_curve_1996}) to
-% the flux, centroid positions, and temperatures simultaneously.  We
-% selected the number of knots through brute-force, by calculating
-% $\chi^2$ for the model fit over a grid of possible knots, and
-% minimizing the Bayesian Information Criterion.  Though this approach
-% showed some initial promise, even with ``optimal'' knot-selection (in
-% the BIC sense) it introduced undesirable residuals in the light curves,
-% and also distorted transits.
-% One thought that we did not try but may explore in future work
-% is to use the decorrelate against the scatter of the quartnerion 
-% time-series \citep{vanderburg_hr858_2019}.
-% 
-% Given these complications, for the time being we omit the step of
-% ``detrending'' as a function of external parameters. To
-% enable further exploration of the issue, we include all the necessary
-% vectors of {\it e.g.}, centroid positions, temperatures, and shape
-% parameters in our reported light curves.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results}
-\label{sec:results}
-
-\begin{figure*}[!t]
-	\begin{center}
-		\leavevmode
-		\includegraphics[width=0.9\textwidth]{galacticcoords_cluster_field_star_positions.pdf}
-	\end{center}
-	\vspace{-0.5cm}
-	\caption{
-		Positions of light curves from TESS Sectors 6
-			and 7 in galactic coordinates.
-		Black: $G_{\rm Rp}<13$ field stars.  Blue: $G_{\rm Rp}<16$
-		target stars.  Target stars are mostly near the galactic
-		plane. The data for Sectors 6 and 7 cover about one-sixth of
-		the galactic plane.
-		\label{fig:lcgalactic}
-	}
-\end{figure*}
-
-%\begin{figure}[!t]
-%	\begin{center}
-%		\leavevmode
-%		\includegraphics[width=0.47\textwidth]{sector6_cam[1]_ccd[1-2-3-4]cluster_field_star_positions.png}
-%	\end{center}
-%	\vspace{-0.5cm}
-%	\caption{
-%		{\bf  Zoom and coordinate transformation
-%			of Sector 6, Camera 1 from Figure~\ref{fig:lcgalactic}.}
-%		The most populated cluster is XXX, primarily due to candidate
-%		members proposed by \citet{dias_proper_2014}.
-%		\label{fig:lcradeczoom}
-%	}
-%\end{figure}
-
-\begin{figure}[!t]
-	\begin{center}
-		\leavevmode
-		\includegraphics[width=0.45\textwidth]{cdf_T_mag.pdf}
-	\end{center}
-	\vspace{-0.5cm}
-	\caption{
-		Cumulative number of CDIPS light curves a function of TESS
-			$T$-band magnitude.  Light curves were made for the
-		target stars (Figure~\ref{fig:cdips_targets}) that were observed
-		in Sectors 6 or 7.
-		\label{fig:cdf_T_mag}
-	}
-\end{figure}
-
-\begin{figure}[!ht]
-	\gridline{\fig{hrd_scat_all_CDIPS_LCs.pdf}{0.45\textwidth}{}}
-	\vspace{-0.8cm}
-	\gridline{\fig{hrd_scat_close_subset.pdf}{0.45\textwidth}{}}
-	\vspace{-0.8cm}
-	\caption{
-		{\it Top.} HR diagram of CDIPS stars on silicon in this
-		data release.  {\it Bottom.} HR diagram of close CDIPS stars on
-		silicon. The wedge separating the pre-MS sample from the MS
-		stars was discussed by \citet{zari_3d_2018}, who introduced it in
-		order to avoid contamination by photometric binaries.
-	}
-	\label{fig:hrd}
-\end{figure}
-
-\begin{figure}[!t]
-	\gridline{\fig{pm_scat_all_CDIPS_LCs.pdf}{0.45\textwidth}{}}
-	\vspace{-0.8cm}
-	\gridline{\fig{pm_scat_close_subset.pdf}{0.45\textwidth}{}}
-	\vspace{-0.8cm}
-	\caption{
-		{\it Top.} Proper motions of CDIPS stars on silicon in this
-		data release.  Many of the stars in the central ``blob'' are possible
-		field-contaminants.
-		{\it Bottom.} Proper motions of close CDIPS stars
-		on silicon.
-	}
-	\label{fig:propermotions}
-\end{figure}
-
-\begin{figure}[!t]
-	\begin{center}
-		\leavevmode
-		\includegraphics[width=0.47\textwidth]{rms_vs_mag.pdf}
-	\end{center}
-	\vspace{-0.5cm}
-	\caption{
-    Standard deviation of trend-filtered CDIPS light curves as a
-    function of catalog TESS-band magnitude.  Black points correspond
-    to the minimum RMS across the available three aperture sizes.  The
-    model (orange and gray lines) assumes aperture sizes reported by
-    \citet{Sullivan_et_al_2015}, and the effective area from
-    \citet{vanderspek_2018}.  The noise from unresolved background
-    stars (dotted gray line) is a function of galactic latitude, and
-    dominates over zodiacal light for faint stars near the galactic
-    plane; the line shown assumes a sight-line towards the center of
-    Sector 6, Camera 1 (further details are in
-    \S~\ref{subsubsec:rmsvsmag}).
-		\label{fig:rms_vs_mag}
-	}
-\end{figure}
-
-\begin{figure}[!t]
-	\begin{center}
-		\leavevmode
-		\includegraphics[width=0.47\textwidth]{avg_acf.pdf}
-	\end{center}
-	\vspace{-0.5cm}
-  \caption{
-    Average autocorrelations of $10^4$ randomly selected light curves
-    from each sector.
-    The medians at time lags spaced by one hour are shown for 
-    raw light
-    curves (column name \texttt{IRM}) in gray, and for
-    TFA-detrended light curves in black.
-    The gray bands display the 25$^{\rm th}$ to 75$^{\rm th}$ percentile
-    range for each type of light curve.
-  \label{fig:avg_acf}
-	}
-\end{figure}
-
-\subsection{Light Curve Statistics}
-\label{subsec:lcstatistics}
-
-\subsubsection{Stellar properties}
-
-The on-sky locations of the light curves from Sectors 6 and 7
-are shown in Figure~\ref{fig:lcgalactic}.
-Black stars are the field stars for which we performed photometry,
-and of which a subset were used as template stars during TFA.
-The blue stars are the \numberlcs stars with light curves available
-from \stscilink.
-Most of the target stars are quite close to the galactic plane.
-Gaps between CCD chips are also visible.
-The highly clumped nature of the target stars is also apparent.
-
-%A zoom-in of Figure~\ref{fig:lcgalactic} is shown in Figure~\ref{fig:lcradeczoom}
-%for the Camera 1, Sector 6 field. The effects of galactic-latitude
-%dependent extinction are visible through the decreasing density of black
-%points towards the right of the image.
-
-Figure~\ref{fig:cdf_T_mag} shows the cumulative distribution of
-TESS $T$-band magnitudes for the target stars.
-Though most of the targets are faint, $\approx3\times10^4$ are
-brighter than $T=13$. These targets are more promising for any
-detailed follow-up observtions.
-
-An HR diagram for the entire sample of CDIPS stars on silicon
-is shown in Figure~\ref{fig:hrd} (top).
-The sub-sample of stars with
-measured positive parallaxes and naive distances less than
-$1\,{\rm kpc}$ is also shown (bottom).
-About one-third of the stars are in this latter sample.
-The close stars are predominantly on the main-sequence, or the pre-main-sequence.
-A relatively large fraction of these come from \citet{zari_3d_2018},
-and are either on the PMS or upper main-sequence.
-The latter set of OBA dwarf stars, while ``younger'' than the typical
-field dwarf, are likely the least interesting subset of our target sample
-from the perspective of age analyses.
-In the entire sample (Figure~\ref{fig:hrd} top), a much larger fraction of stars are sub-giants,
-red giants, and helium-burning red-clump stars.
-We failed to obtain light curves for roughly $5\%$ of the stars on silicon, 
-primarily due to our masking of saturated stars and their nearby pixels.
-
-Finally, Figure~\ref{fig:propermotions} shows the proper motions of
-the entire and close samples of stars on silicon.  Each clump
-signifies a different star cluster. The largest overdensity in the top
-figure is composed mainly of field star contaminants. It has two
-subcomponents, due to the two different directions in the Galaxy being
-observed in Sectors 6 and 7.
-
-\subsubsection{Cluster membership provenance}
-
-\paragraph{Sector 6}
-In Sector 6, \sVInumberlcs light curves of candidate cluster stars
-were made. The provenance of the claimed cluster origin of these
-sources is \citet{dias_proper_2014} for 59\% of the sources;
-\citet{zari_3d_2018} for 16\% of sources from their upper
-main-sequence table and 1\% of sources from their PMS table;
-\citet{Kharchenko_et_al_2013} for 8\% of sources,
-\citet{cantat-gaudin_gaia_2018} for 6\% of sources, and more than two
-catalogs for the remaining 10\% of sources.
-
-The clusters with the largest claimed numbers of sources are the
-Platais~6, Platais~5, and Mamajek~3 moving groups, all from
-\citet{dias_proper_2014}, composing about 7000, 7000, and 3500 sources
-respectively. These membership claims should be regarded with some
-skepticism on a source-by-source basis.  For Platais~6,
-\citet{Kharchenko_et_al_2013} claimed only about 400 probable members
-(1$\sigma$) to exist within the angular radius of the cluster.
-Mamajek~3 (= 32$\,$Ori) has only about 50 confirmed members
-\citep{bell_32ori_2017}.
-
-We remind the reader that our goal in creating our target catalog was
-completeness, rather than fidelity. The \citet{dias_proper_2014} stars
-in particular were included if they were listed with membership
-probability exceeding 50\%.  To create cleaner sub-samples, we advise
-use of the \texttt{CDEXTCAT} header keyword, which can be used
-to merge against the original source catalog to obtain the
-membership probabilities claimed by the original catalog.
-
-\paragraph{Sector 7}
-In Sector 7, \sVIInumberlcs light curves of candidate cluster stars
-were made. The provenance of the claimed cluster origin of these
-sources is  ... LGBTODO
-
-The clusters with the largest claimed numbers of sources are ...
-LGBTODO
-
-\subsubsection{Light curve noise properties}
-\label{subsubsec:rmsvsmag}
-
-\paragraph{Observed RMS vs magnitude.}
-The standard deviation of the TFA-detrended light curves is plotted as
-a function of the catalog $T$-band magnitude for CDIPS light curves in
-Figure~\ref{fig:rms_vs_mag}.
-For the $y$-axis of this plot, we have taken
-\begin{equation}
-  {\rm RMS} = \left[
-    \frac{1}{N-M-1}
-    \sum_{i=1}^{N} (f_i - \bar{f})^2
-  \right]^{1/2},
-\end{equation}
-where $f_i$ is the value of the flux at the $i^{\rm th}$ point in the
-time-series, $\bar{f}$ is the mean flux, $N$ is the
-number of points in the time-series, and $M$ is the number
-of template light curves used during TFA detrending.
-The correction in the denominator penalizes the natural degree of
-overfitting inherent to the TFA algorithm.
-
-The observed RMS (black points) follows the usual shape, with photon
-noise dominating from $T=9$ to $T=12$, beyond which the onset of the
-``sky'' background changes the overall slope of the curve to be more
-steep.  For the brightest stars ($T\lesssim 9$), a ``systematic
-floor'' was part of the mission's error budget
-\citep{ricker_transiting_2015}, but has not been observed in early
-reports of the photometric performance of various aperture photometry
-pipelines ({\it e.g.,} the SPOC pipeline \citealt{jenkins_spoc_2010},
-the MIT-QLP \citealt{huang_tess_2018}, and \texttt{eleanor}
-\citealt{feinstein_eleanor_2019}).  The fact that our light curves for
-the brightest stars are above this purported ``floor'', rather than
-below it, suggests that our image subtraction techniques could be
-introducing some small degree of noise to the light curves of the
-brightest stars.  It is also true however that our largest aperture
-contains only about 16 pixels, which is sub-optimal for stars brighter
-than $T\approx9$ \citep[see][Figure~14]{Sullivan_et_al_2015}.  Since
-the brightest stars are not the focus of the present work, we leave
-this issue unaddressed for the time being.
-
-Importantly, the faint stars do not noticeably exhibit
-the typical effects of crowding at the faint end 
-\citep[{\it e.g.},][Figure~5]{feinstein_eleanor_2019}.
-In aperture photometry pipelines, stars in very crowded regions typically 
-have their flux overestimated relative to the actual number of photons
-that fall on silicon.
-This leads to systematic underestimates of the uncertainty in the relative 
-fluxes, as well as ``flux contamination'' (the reduction in amplitude of say, 
-transit signals, due to diluting flux from neighbor stars).
-Our method to work around this problem -- using the catalog magnitudes to 
-predict the reference flux values, and measuring deviations from these 
-reference fluxes on the subtracted images -- seems to be performing well.
-
-\paragraph{Expected RMS vs magnitude.}
-
-The noise model shown in Figure~\ref{fig:rms_vs_mag} is quite similar
-to that of \citet{Sullivan_et_al_2015}, save for two changes.
-The first change is that the effective area of the telescope is
-updated to be $86.6\,{\rm cm}^2$, per the measurements by
-\citet{vanderspek_2018}.
-
-The second change is that we have explicitly included the
-estimated noise contribution from unresolved faint stars.  The
-brightness of the diffuse sky is dominated by different sources at
-different wavelengths.  For instance, the CMB is most important in
-the microwave, and thermal radiation from dust grains in the solar
-system (zodiacal light) is dominant in the far infra-red
-\citep{leinert_1997_1998}.  In the TESS-band, both zodiacal light and
-faint stars can play a role, depending on the line of sight under
-consideration. The zodiacal light is brightest near the ecliptic
-plane, and the faint star background is brightest near the galactic
-plane (and towards the galactic center).  
-When performing pre-launch noise estimates,
-\citet{winn_background_2013}
-estimated the photon-counts from each component.
-His zodiacal light model was presented by \citet{Sullivan_et_al_2015},
-but the faint star component was not emphasized since the Sullivan
-simulations were performed away from the galactic plane.
-
-The diffuse sky model we have used for Figure~\ref{fig:rms_vs_mag} is
-adopted explicitly because most of our target stars are near the
-galactic plane.
-Stars are judged to be ``unresolved'' and part of the background if
-their surface density exceeds the angular resolution of the telescope.
-TESS has an angular resolution of $\Delta \theta \sim 1'$, set by a
-combination of the pixel size as well as the typical stellar FWHM.
-Sources with sky surface density exceeding $\Delta \theta^{-2}$
-therefore contribute to the background.
-
-The relevant quantity needed to calculate the integrated 
-photon counts from faint sources
-is  $N(<m,l,b)$ --- the number of stars per square arcsecond
-brighter than magnitude $m$, along a line of sight with galactic
-longitude and latitude $(l,b)$.
-To calculate this surface density, \citet{winn_background_2013}
-queried the Besan\c con model
-\citep{robin_synthetic_2003}  along a grid of galactic sight-lines,
-and then converted to $I$-band surface brightnesses.
-Fitting a smooth function to the results, \citet{winn_background_2013}
-found
-\begin{equation}
-I\ {\rm mag\ arcsec}^{-2} =
-    a_0 + a_1 \left(\frac{|b|}{40^\circ}\right)
-    + a_2 \left(\frac{|l|}{180^\circ}\right)^{a_3},
-\end{equation}
-where the galactic longitude $l$ is measured from $-180^\circ$ to
-$180^\circ$, and the empirical coefficients were found to be $a_0 =
-18.9733$, $a_1=8.833$, $a_2=4.007$, and $a_3=0.805$.  This fit was
-cautioned to be {\it very approximate}.  It is sensitive to the
-threshold used to select ``unresolved'' stars, and likely no more
-accurate than 0.5 mag on average.  In regions with exceptionally high
-extinction ({\it e.g.}, star forming regions) it is expected to
-systematic underestimate the background brightness by an even larger
-degree.
-Nonetheless, this model for the diffuse sky background seems
-to agree reasonably well with the observed trend of standard deviation
-versus stellar magnitude.
-
-\paragraph{ACF statistics}
-
-Beyond the white noise properties of the light curves, the red noise
-properties are also important. 
-In Figure~\ref{fig:avg_acf} we show the average autocorrelation of the
-raw and TFA-filtered light curves.
-The raw light curves have substantial systematic red noise; 
-their average autocorrelation, evaluated at various time lags, is
-positive.
-The TFA-filtered light curves are much closer to gaussian~--~the
-average autocorrelation between any two points in these light curves
-is close to zero.
-However, the average TFA-filtered light curve is not {\it exactly}
-gaussian.
-At time lags of a few hours or less, there is some excess power.
-This suggests that additional detrending may be
-necessary to maximize the effectiveness of planet searches (or the discovery of
-any other signals via matched-filter techniques).
-
-\subsection{Identifying Planet Candidates}
-\label{subsec:identifying_ctois}
-
-\begin{figure}[!t]
-	\gridline{\fig{tls_sde_vs_period_scatter.pdf}{0.45\textwidth}{}}
-	\vspace{-0.8cm}
-	\caption{
-    Transiting planet search periodogram summary.
-    Each point represents the TLS periodogram peak signal detection
-    efficiency (SDE) and corresponding period from one light curve.
-    Significance thresholds (orange lines) are empirically defined for
-    the transiting planet search described in
-    \S~\ref{subsec:identifying_ctois}.  
-    {\it Top.} Sector 6.  {\it Bottom.} Sector 7.
-	}
-	\label{fig:tlsresults}
-\end{figure}
-
-To identify an initial set of transiting planets, strong stellar
-rotators, and eclipsing binaries, we performed a few steps of
-post-processing on the light curves.  This processing was done
-independently of the data release, since it was quite specific to our
-own scientific interests.  The code used to do this additional
-processing is also available
-online\footnote{\url{github.com/lgbouma/cdips}, commit
-\texttt{348eea7}.}.
-
-For simplicity, we first chose a single aperture size~--~``aperture
-2''~--~with a radius of 1.5  pixels.  Then, to identify periodic
-transit-like signals, we used \citet{hippke_TLS_2019}'s transit
-least-squares (TLS) tool.  The algorithm is the same as the canonical
-box least-squares \citep{kovacs_box-fitting_2002}, except in place of
-a box template, a transit template is used  for a marginal improvement
-of the detection efficiency.  In addition, the search grids in
-\texttt{tls} \footnote{\url{https://github.com/hippke/tls}} are
-slightly more efficient than in most BLS implementations, since
-\texttt{tls} uses the cubic-in-frequency sampling advocated by
-\citet{ofir_optimizing_2014}, rather than standard linear-in-frequency
-sampling.  Our grids typically consisted of about 30 different
-durations, and about 5000 periods between 0.5 and 21 days.
-
-Before performing the period search, we rejected $6\,{\rm hours}$ at
-the beginning and end of each spacecraft orbit, to mitigate the
-presence of correlated red noise in the results.  This shrank the data
-volume by about 5\%, but also lowered the number of systematic false
-positives in subsequent vetting.  We then performed an asymmetric
-sigma-clipping of $(50\sigma,5\sigma)$ about the median to preserve
-transits while omitting flares and other positive flux excursions.
-
-A number of the light curves show residual variability, often of
-stellar origin.  This is expected for a sample of young stars; the
-problem of finding transits in the face of large stellar rotation
-signals has been explored by both \citet{rizzuto_zeitV_2017} and also
-\citet{hippke_wotan_2019}.  The former adopted an approach that we
-have yet to explore, which is to pass a sliding window over the light
-curve that, within each step, performs a Bayesian model comparison
-between a spline and a spline-plus-notch model.  If the
-spline-plus-notch model is favored, the transits are preserved for
-subsequent discovery.  \citet{hippke_wotan_2019}, conversely,
-described a number of different detrending methods, and found that
-most performed more or less the same at recovering planetary transits
-for a sample of young stars with strong rotation signals.
-
-Our approach in this work is essentially identical to one of the
-methods described by \citet{hippke_wotan_2019}.  First, before
-sigma-clipping or omitting points near the edges of orbits we run a
-generalized Lomb-Scargle periodogram on each TFA light curve
-\citep{lomb_1976,scargle_studies_1982,vanderplas_periodograms_2015}.
-If a peak is found with false alarm probability below $10^{-5}$, we
-consider the star ``variable'', and opt to detrend the flux timeseries
-with robust penalized B-splines, which are splines with knot-length
-automatically determined via cross-validation
+\section{Vetting Report Description}
+\label{appendix:vetreport}
+
+The NASA team and MIT teams \citep{jenkins_spoc_2010,huang_tess_2018}
+produce vetting reports to assess the quality of planet candidates
+identified through their transiting planet serach pipelines.
+
+One goal of the CDIPS project is to detect transiting planets with
+known ages.  Therefore our vetting reports include information to help
+assess {\it (a)} whether the transiting planet candidate is real, and
+{\it (b)} whether the reported age is correct.
+The code used to make these reports for the 2019-09-18 through
+2019-11-25 planet candidates is available online\footnote{ 
+\url{https://github.com/lgbouma/cdips/tree/a83a30}}.
+
+Figures~\ref{fig:pg1} to~\ref{fig:pg6} summarize the document
+construed for these purposes.  The planet candidate chosen for these
+figures (Gaia-DR2 \texttt{5541111035713815552} = TIC
+\texttt{110718787}) was chosen in part because it passed all the
+tests.  It was reported\footnote{\url{https://exofop.ipac.caltech.edu/tess/view_ctoi.php}}
+as a giant planet candidate in an open cluster
+on Sep 9, 2019.  Higher
+resolution HATSouth photometry revealed about a month afterward that
+the dip signal comes from a neighboring eclipsing binary.
+
+\subsection{Transit search summary}
+\label{sec:pg1}
+
+Figure~\ref{fig:pg1}.
+Periodograms from TLS and phase-dispersion minimization, calculated
+with \texttt{astrobase.periodbase}, are shown in the top left and top
+center
+\citep{bhatti_astrobase_2018,hippke_TLS_2019,stellingwerf_period_1978}.
+The top three peaks from each method are shown in the second and third
+rows; the raw light-curve is in the top-right. A small finder chart
+from DSS is inset to the top left, with the 1.5-pixel radius aperture
+used to extract the light-curve in orange.
+
+\subsection{Light-curve diagnostics}
+\label{sec:pg2}
+
+Figure~\ref{fig:pg2}.
+Time-series of raw flux (\texttt{IRM2}),  TFA-detrended flux
+(\texttt{TF2}), stellar-variability detrended flux, and the background
+are shown as a function of barycentric Julian date.  The overplotted
+dashed vertical lines are the ephemeris of the highest-power TLS peak
+from Figure~\ref{fig:pg1}.  An important visual check is whether the flux
+dips are correlated with changes in the background level -- in this
+case, they are not.  The standard deviation and TESS magnitude are
+quoted in the upper right.  The red line in the second from the top
+plot is a spline fit, which in this case an essential step for finding
+the eclipse signal.
+
+The windowed spline is an optional feature: it is only fitted and
+removed if the star is found to be ``variable'' (the Lomb-Scargle peak
+period is found with false alarm probability below $10^{-5}$). The
+spline is a robust penalized B-spline, which is a B-spline with
+knot-length automatically determined via cross-validation
 \citep{eilers_flexible_1996}. The idea behind the cross-validation is
@@
 \citep{serven_pygam_2018_1476122,hippke_wotan_2019}.  The maximum
-number of spline knots is set to 50, which for each TESS sector
+number of spline knots was set to 50, which for each TESS sector
 ($\approx 25\,{\rm days}$) is commensurate with a $\approx0.5\,{\rm
@@
 
-We verified by injecting and recovering a 2.5 mmag, zero impact
-parameter 
-planet with variable period that this detrending approach marginally
-improved the recovery probability, compared to not doing anything.
-The main cases for which it helps are those with large residual
-stellar variability in the TFA light curve.
-
-After (optionally) detrending, we run the TLS search. To select
-``significant'' signals for visual inspection, we performed a cut on
-the TLS signal detection efficiency defined piecewise over the signal
-periods.  The overall lower limit is ${\rm SDE} > 12$, with higher
-limits imposed in regions with heavy contamination from systematic
-signals.  The signals for sectors 6 and 7 are shown in the space of
-SDE vs period in Figure~\ref{fig:tlsresults}.
-
-This yielded a few thousand light curves.  About two-thirds already
-had been detrended with splines, and were not processed further.  For
-the remaining third we performed TFA signal reconstruction using
-\texttt{VARTOOLS}.  In this process, the model lightcurve $A(i)$ in
-Equation~\ref{eq:tfa_to_minimize} is set to the phase-binned signal
-from the most powerful peak in the TLS spectrum, rather than being a
-constant function.  This helps lower the scatter of the light curve at
-frequencies away from the TLS peak.
-
-We then make a multi-page \texttt{.pdf}-format document report with
-the information necessary to make classifications for vetting.  These
-vetting reports are released along with the light curves, and are a
-useful summary for anyone interested in the subset of objects that we
-have analyzed.  A full description of each page of the report is given
-in Appendix~\ref{appendix:vetreport}.
-When classifying these reports, we assessed:
-\begin{enumerate}
-    \item {\it Morphology of photometric variability}. Designations
-      include tags for planet candidates, eclipsing binaries,
-      instrumental variations, stellar variations, and ``weirdos''.
-    %
-    \item {\it Cluster membership status}. By default, all light
-      curves were made for stars with at least one literature claim of
-      cluster membership.  However, some of these claims pre-dated the
-      availability of Gaia-DR2 parallaxes or proper motions.  We
-      therefore re-assess the membership status on a case-by-case
-      basis through inspection of the available astrometry and
-      photometry.  Known asterisms are also omitted at this point
-      \citep[{\it
-      e.g.},][]{sulentic_revised_1973,baumgardt_asterisms_1998,kos_galah_2018}.
-    %
-    \item {\it Photometric blends}. Tags are created to highlight
-      whether the depth of the photometric signal shows a strong
-      dependence on aperture size, and also whether the in-transit
-      minus the out-of-transit images reveal that the source of
-      variability is in fact far from the target star.
-\end{enumerate}
-The initial classifications were performed by LGB, and possible
-planet candidates were then vetted by JH and JNW.
-The \texttt{TagSpaces}
-software was used to easily assign labels to the documents.
-
-\subsection{Candidate TESS Objects of Interest}
-\label{subsec:ctois}
-
-\begin{figure*}[!t]
-	\begin{center}
-		\leavevmode
-		\includegraphics[width=0.9\textwidth]{quilt_PCs.pdf}
-	\end{center}
-	\vspace{-0.2cm}
-	\caption{
-		Phased light curves for six of the \numberpcs candidate
-			transiting planets identified in this work.
-		Black points are detrended flux measurements, phased to the
-		best-fit orbital period indicated in the lower right of each
-		panel.
-    Transit models are fitted as described in \S~\ref{subsec:ctois},
-    and plotted with blue lines.
-		For display purposes, a window of $\pm 4$ transit durations
-		centered on the transit mid-point is displayed.
-		The vetting reports for these objects are available at XXX.	%FIXME
-		% TODO: include age? T mag?
-		The Gaia source identifiers are
-		a): 5605128927705695232, 
-		b): 3125263468681400320, 
-		c): 5510676828723793920, 
-		d): 3007171311355035136, 
-		e): 5617126180115568256, 
-		f): 3220266049321724416.   
-		\label{fig:ctoi_quilt}
-	}
-\end{figure*}
-
-\begin{figure}[!t]
-	\begin{center}
-		\leavevmode
-		\includegraphics[width=0.45\textwidth]{LS_period_vs_color_and_age.pdf}
-	\end{center}
-	\vspace{-0.2cm}
-	\caption{
-    Time evolution of Lomb-Scargle periodogram peak period versus Gaia
-    color.
-		Red stars are on the right, blue stars are on the left.
-		Each point on this diagram is a star for which the false alarm
-		probability of the most powerful Lomb-Scargle peak is below
-		$10^{-15}$.
-		Additionally, we required (1) that the membership claim originate
-		from \citet{cantat-gaudin_gaia_2018},
-		\citet{Kharchenko_et_al_2013}, or \citet{gaia_hr_2018}; and (2)
-		that the cluster with claimed membership had an age reported by
-		\citet{Kharchenko_et_al_2013}.
-		Our approach for avoiding photometric blends is described in
-		\S~\ref{subsec:notplanets}.
-		\label{fig:ls_peak_vs_time}
-	}
-\end{figure}
-
-If all vetters identified an object as a planet candidate, we then
-proceeded to fit a transit model to the data.  The procedure closely
-mirrors that used by \citet{bouma_wasp-4b_2019} to create a
-phase-folded light curve for WASP-4.
-
-First, we selected points within 5 transit durations of each transit
-midpoint, using the orbital period, transit duration, and reference
-epoch found from applying TLS to the detrended light curve.  We then
-fitted a line to the out-of-transit flux measurements around each
-transit window, and divided it out.  We then fitted a standard transit
-model using the formulae given by \citet{mandel_analytic_2002} and
-implemented by \citet[][\texttt{BATMAN}]{kreidberg_batman_2015}.  The
-free parameters were the orbital period, the reference epoch, the
-planet to star radius ratio $R_{\rm p}/R_\star$, the orbital distance
-to stellar radius ratio $a/R_\star$, and the inclination $i$.  We
-assumed circular orbits.  To fix the quadratic limb-darkening
-parameters, we collected $T_{\rm eff}$ and $\log g$ from the TIC, and
-then interpolated against the \citet{claret_limb_2017} tables.  For
-stars hotter than the maximal effective temperature of these tables
-($12,000\,{\rm K}$), we simply used the coefficients of the hottest
-star.
-
-We then sampled the posterior probability distribution using the
-\citet{goodman_ensemble_2010} algorithm, as implemented by
-\citet[][\texttt{emcee}]{foreman-mackey_emcee_2013}.  Our main goal in
-this procedure was to provide an accurate ephemeris.  To ensure that
-the reported uncertainties are valid, after performing the initial fit
-using the photometric uncertainties reported in our light curves, we
-rescaled the the uncertainty in each photometric data point to equal
-the root-mean-square deviation of each transit-model subtracted light
-curve. We then refitted each light curve.
-
-The resulting parameters are given in Table YYY, and are also
-available as cTOIs NNN.01 - MMM.01 on exofop-TESS (LINK).
-Figure~\ref{fig:ctoi_quilt} shows the phase-folded lightcurves and
-their best-fitting moels.
-
-The physical parameters quoted in Table YYY, and on exofop-TESS,
-should be considered preliminary, and could be substantially improved
-with an object-by-object analysis.  A few additional assumptions were
-required to report some of the values.  For the stellar radii, we
-assumed the $R_\star$ values and uncertainties reported in the TIC.
-There were a few cases with null uncertainties in the stellar radii --
-for these, we simply invented a relative uncertainty of 30\%, and note
-in the comments that this was done.  There were also a few cases for
-which the TIC stellar temperatures and/or radii were not available,
-but the Gaia values were.  In these cases, we used the Gaia $T_{\rm
-eff}$ and $R_\star$ values \citep{andrae_apsis_2018}, and a stellar
-mass interpolated from the \citet{pecaut_intrinsic_2013} table
-(assuming the star is a dwarf) to estimate $\log g$ for the
-limb-darkening.  The uncertainties in e.g., the planetary radii and
-impact parameters were found using linear error propagation theory,
-under the idealized assumption that the covariance between all stellar
-and planetary parameters was zero.
-
-Finally, to assign the names of the planet candidates -- and determine
-whether they had already been identified as TOIs or cTOIs -- we used
-lists downloaded from the \url{tev.mit.edu} alert site for TOIs, and
-from \url{exofop.ipac.caltech.edu/tess} for cTOIs.  We
-cross-referenced based on a combination of the TIC identifier, spatial
-position, and the ephemeris of each object.
-
-\subsection{Eclipsing binaries, stellar rotation}
-\label{subsec:notplanets}
-
-To assess the prospects for studying forms of stellar variability
-other than that caused by transiting planets, we performed a brief
-additional exploration.
-Using the Lomb-Scargle periodogram results from
-\S~\ref{subsec:identifying_ctois}, we selected light curves 
-for which the periodogram peak power had a corresponding false alarm
-probability below $10^{-15}$.
-We chose this cutoff to be small enough to give us a reasonable number
-of objects, but large enough so that there would be no question that
-the signal being detected was astrophysical.
-
-Further, we then restricted our focus to stars with a cluster
-membership claim in \citet{cantat-gaudin_gaia_2018},
-\citet{Kharchenko_et_al_2013}, or \citet{gaia_hr_2018}, since from our
-experience these works have a relatively low false positive
-probability.
-We then further restricted our sample of stars to be those for which
-the claimed cluster also had an age reported by
-\citet{Kharchenko_et_al_2013}.
-
-To remove obvious photometrically-blended duplicates, for any signal,
-if any nearby stars had matching periods, we kept only the signal with
-the lowest false alarm probabilty.
-While this does not ensure that the detected signals originate from
-the target star, it removed a large number of the duplicate signals,
-and suits our exploratory purposes.
-
-All told, this yielded 4057 stars between the ages of about 25 Myr and
-1 Gyr.
-In Figure~\ref{fig:ls_peak_vs_time}, we plot the Lomb-Scargle peak period
-versus $G_{\rm Bp} - G_{\rm Rp}$ color over four different bins of
-time.
-The bins were chosen to match the sub-sample sizes within reasonable
-proximity.
-
-The youngest sample of stars is the reddest, as might be expected
-given that many of these stars have not yet reached the main sequence,
-and may exist along lines of sight with heavy extinction.
-Stars younger than about 200 Myr (the first two age bins) also tend
-to be bluer.
-The oldest stars, between about 450 Myr and 1 Gyr, show a hint in
-the detected periods of being ``bottom-heavy'', {\it i.e.}, there are
-relatively more short-period objects in this sample.
-The reason why is unclear~--~the effect could be due to systematic
-differences in the stellar samples, rather than being astrophysical.
-More investigation will be required.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Discussion}
-\label{sec:discussion}
-
-Maybe JH or JNW could work on these subsections?
-
-\subsection{The planet candidates require more observations}
-Additional observations are needed for two major goals:
-a) cluster membership confirmation
-(age indicators, across the board);
-b) verify the planetary nature of the signals
-(seeing-limited photometry, RV mass measurement).
-
-Different types of observations and analyses are needed to confirm 
-(i) the planetary nature of these signals, and
-(ii) whether the host stars are bonafide cluster members.
-For (i), follow-up photometry, high-resolution imaging, and in some
-cases spectroscopic mass measurement are needed.
-For (ii), one or two radial velocity measurements might kinematically
-exclude cluster membership in a number of cases.
-A full assessment of the target star's age indiciators, including
-photometric rotation signatures, spectroscopic Li and H$\alpha$
-measurements, and even an isochronal analysis, would be helpful.
-
-\subsection{Eclipsing binary and stellar variability analyses may also
-be feasible}
-
-JH?
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusion}
-\label{sec:conclusion}
-
-%FIXME: paraphrase / improve all the below
-In this study, we first collected an all-sky sample of about one million
-candidate young stars brighter than $G_{\rm Rp}$ of 16.
-82\% of the target star sample resides in a ``cluster'', a generic
-term we adopted for open clusters, stellar associations, and moving
-groups.
-The remaining stars have photometric or astrometric indications of
-their youth, and either reside on the pre-main-sequence or upper
-main sequence.
-
-We then reduced TESS full frame images taken over the course of about
-two months (Sectors 6 and 7; the first fields very close to the galactic
-plane).
-We performed difference imaging in order to minimize the complications
-of the crowded background.
-Using forced aperture photometry, we made light curves for all stars
-brighter than $G_{\rm Rp}$ of 13, and went three magnitudes deeper for
-our target star sample.
-This yielded \numberlcs light curves of candidate young stars across
-\numberclusters distinct clusters.
-
-The light curves seem to be limited in precision by photon noise at
-the bright end, and by unresolved background stars at the faint end.
-Though the raw light curves show significant red noise, decorrelating
-against a set of template stars led to an ensemble of light curves
-with very nearly gaussian noise properties.
-
-An initial search for transiting planets, along with subsequent
-vetting to remove obvious non-cluster members and photometric blends,
-has revealed \numberpcs planet candidates.
-\numberclusterpcs of these candidates are candidate cluster members,
-and the remaining \numberzaripcs have indications of youth, relative
-to field stars.
-The latter sub-sample is the less interesting one for this work, but
-may be of interest for other studies.
-Substantial follow-up efforts on these objects are needed to determine
-(i) whether the candidates are planets and (ii) whether the host stars
-are truly cluster members.
-We suspect that a sizeable fraction of our planet candidates may
-be eclipsing binaries, however it likely also includes real planets.
-The vetting reports are available at \stscivetlink, and also documented
-in Appendix~\ref{appendix:vetreport}.
-The planet candidate parameters are on exoFOP-TESS.
-
-We also briefly explored other forms of photometric variability in the
-dataset.
-The age-evolution of extremely high-SNR variability seems to show some
-evolution in the space of LS peak-period versus color
-(Figure~\ref{fig:ls_peak_vs_time}), but interpreting this result will
-require a more careful exploration.
-In searching for transiting planets, we found many eclipsing binaries,
-as well as stellar rotation and pulsation signals.
-Those who wish to explore the time-evolution in these and any other
-systems are invited to explore the data at \stscilink.
-
-\acknowledgements
-L.G.B.\ gladly acknowledges helpful discussions with
-C Huang, M Soares-Furtado, ...
-..., and is
-grateful to the people who have turned TESS from an idea into reality.
-%
-J.N.W.\ thanks ...
-%
-This paper includes data collected by the TESS mission, which are
-publicly available from the Mikulski Archive for Space Telescopes
-(MAST).
-%
-Funding for the TESS mission is provided by NASA's Science Mission
-directorate.
-%
-This research has made use of the NASA Exoplanet Archive, which is
-operated by the California Institute of Technology, under contract
-with the National Aeronautics and Space Administration under the
-Exoplanet Exploration Program.
-%
-This work made use of NASA's Astrophysics Data System Bibliographic
-Services.
-%
-This research has made use of the VizieR catalogue access tool, CDS,
-Strasbourg, France. The original description of the VizieR service was
-published in A\&AS 143, 23.
-%
-This work has made use of data from the European Space Agency (ESA)
-mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed
-by the {\it Gaia} Data Processing and Analysis Consortium (DPAC,
-\url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding
-for the DPAC has been provided by national institutions, in particular
-the institutions participating in the {\it Gaia} Multilateral
-Agreement.
-%
-The Digitized Sky Surveys were produced at the Space Telescope Science Institute under U.S.
-Government grant NAG W-2166.
-The images of these surveys are based on photographic data obtained using the Oschin Schmidt Telescope on Palomar Mountain and the UK Schmidt Telescope.
-The plates were processed into the present compressed digital form with the permission of these institutions.
-%
-\newline
-%
-\facility{
-	2MASS \citep{skrutskie_tmass_2006},
-	Gaia \citep{gaia_collaboration_gaia_2016,gaia_collaboration_gaia_2018},
-	TESS \citep{ricker_transiting_2015},
-	UCAC4 \citep{zacharias_fourth_2013}
-    %DSS (CITE)    
-}
-%
-\software{
-  \texttt{astrobase} \citep{bhatti_astrobase_2018},
-  \texttt{astropy} \citep{the_astropy_collaboration_astropy_2018},
-  \texttt{astroquery} \citep{astroquery_2018},
-  %\texttt{astroquery.gaia} CITE,
-  %\texttt{astroquery.simbad} CITE,
-  %\texttt{astroquery.mast} CITE,
-  %\texttt{astroquery.nasaexopanetarchive} CITE,
-  \texttt{BATMAN} \citep{kreidberg_batman_2015},
-  \texttt{corner} \citep{corner_2016},
-  \texttt{emcee} \citep{foreman-mackey_emcee_2013},
-  \texttt{fitsh} \citep{Pal_2012},
-  \texttt{IPython} \citep{perez_2007},
-  \texttt{matplotlib} \citep{hunter_matplotlib_2007}, 
-  \texttt{numpy} \citep{walt_numpy_2011}, 
-  \texttt{pandas} \citep{mckinney-proc-scipy-2010},
-  \texttt{pyGAM} \citep{serven_pygam_2018_1476122}
-  \texttt{psycopg2} (\url{initd.org/psycopg})
-  \texttt{scipy} \citep{jones_scipy_2001},
-  \texttt{scikit-learn} \citep{sklearn_2011},
-  \texttt{TagSpaces} (\url{tagspaces.org}),
-  \texttt{tesscut} \citep{brasseur_astrocut_2019},
-  \texttt{VARTOOLS} \citep{Hartman_Bakos_2016}
-  \texttt{wotan} \citep{hippke_wotan_2019},
-}
-
-\clearpage
-\newpage
-
-\bibliographystyle{yahapj}                            
-\bibliography{bibliography}
-
-\appendix
-\section{Time system \& barycentric correction}
-\label{appendix:time}
-
-The time-stamps included with the calibrated TESS Full Frame Images
-produced by SPOC include a barycenteric correction at
-a single reference pixel given at the middle of every frame.
-The barycentric correction is at maximum 16 minutes, corresponding to
-points on the sky separated by 180 degrees.
-The angular distance from a TESS camera's center of field to the corners
-is $\approx$17 degrees, so naively one might incur at worst an error of
-$\approx$90 seconds on the time-stamps due to using a barycentric
-correction in a direction that is slightly wrong.
-Perhaps due to the lead author's obsession with getting time-stamps correct 
-\citep{bouma_wasp-4b_2019},
-we perform our own barycentric correction using the appropriate
-sky coordinates for each light curve.
-We advise use of our \texttt{TMID\_BJD} column, which gives the
-mid-time of each exposure in the BJD$_{\rm TDB}$ time system, which
-is the defacto standard in exoplanet and stellar
-astronomy~\citep{eastman_achieving_2010}.
-
-\section{Assigning unique names to each cluster}
-\label{appendix:uniquenames}
-
-In assigning a single unique cluster name to each star, we matched
-against the \citet{Kharchenko_et_al_2013} name whenever possible,
-since this was the largest available catalog, and it also included
-homogeneous age determinations for many of the clusters.
-To find the matching name, in order of precedence we
-\begin{enumerate}
-  \item Checked for direct string matches from
-    \citet{Kharchenko_et_al_2013} clusters with determined parameters;
-  \item Checked whether the SIMBAD online name resolving service \citep{wenger_simbad_2000} had
-    any direct string matches against \citet{Kharchenko_et_al_2013}
-    clusters with determined parameters;
-  \item Checked for string matches in the full
-    \citet{Kharchenko_et_al_2013} index (including clusters without
-    determined parameters);
-  \item Searched for spatial matches between each star and cluster
-    centers from \citet{Kharchenko_et_al_2013} within 10 arcminutes.
-    In cases with multiple cluster matches, we ignored candidate
-    matches to avoid assigning incorrect names;
-  \item Checked the WEBDA double name
-    list\footnote{\url{https://webda.physics.muni.cz/double_names.html}},
-    and repeated Steps 1-4 with any matches.
-\end{enumerate}
-
-A few edge-cases, including for instance sub-clusters  larger
-star-forming complexes like in Sco-Cen or Collinder~33, were 
-manually resolved to the extent feasible (\citealt{rizzuto_multidimensional_2011}
-and \citealt{saurin_isolating_2015} give
-detailed pictures of the complex morphologies that frequently arise in
-young star-forming regions).
-
-The procedure described above failed to yield matches for a few of the
-infrared clusters identified by \citet{majaess_discovering_2013} and
-included in the \citet{dias_proper_2014} catalog.
-For these cases, we used the name given by \citet{dias_proper_2014}.
-The larger set of ``FSR'' infrared clusters from
-\citet{froebrich_FSR_2007} was incorporated to
-\citet{Kharchenko_et_al_2013}, and so did not present any
-complications.
-
-The Hyades and a number of other nearby moving groups were also
-missed, since they were not in the \citet{Kharchenko_et_al_2013}
-catalog.  For moving groups not identified in
-\citet{Kharchenko_et_al_2013}, we adopted the constellation-based
-naming convention from \citet{gagne_banyan_XI_2018}.
-
-Finally, the procedure enumerated above did not yield matches for
-recently discovered clusters, such as the ``RSG'' clusters found by
-\citet{roser_nine_RSG_2016} and the ``Gulliver'' clusters from
-\citet{cantat-gaudin_gaia_2018}.  In these cases, we used the names
-given by the original authors.
-
-\section{Vetting Document Description}
-\label{appendix:vetreport}
-
-In \S~\ref{subsec:ctois}, we described the process by which we made 
-vetting reports suitable for assessing which objects were interesting 
-enough to merit further study.
-
-Figures~\ref{fig:pg1} to~\ref{fig:pg6} of this
-section summarize this document. Updated versions and their 
-\texttt{README} files will live at this web-address: 
-\url{mast.stsci.edu/CDIPS}.
-The planet candidate chosen for these figures
-(Gaia-DR2 \texttt{5541111035713815552} = TIC \texttt{110718787}) was
-chosen for the demonstration in part because it passes all
-the tests.
-It is one of a number of the giant planet candidates that we note may
-be in open clusters.
-
-\begin{figure*}[!h]
-	\begin{center}
-		\leavevmode
-		\includegraphics[width=0.98\textwidth]{gaiatwo0005599752663752776192-0007_page01.pdf}
-	\end{center}
-	\vspace{-0.5cm}
-	\caption{
-		{\bf Transit search summary.}
-    Periodograms from TLS and phase-dispersion minimization, as
-    calculated with \texttt{astrobase.periodbase}, are shown in the
-    top left and top center
-    \citep{bhatti_astrobase_2018,hippke_TLS_2019,stellingwerf_period_1978}.
-    The top three peaks from each method are shown in the second and
-    third rows; the raw light curve is in the top-right. A small
-    finder chart from DSS is inset to the top left, with the 1.5-pixel
-    radius aperture used to extract the light curve in orange.
-		\label{fig:pg1}
-	}
-\end{figure*}
-
-\begin{figure*}[!h]
-	\begin{center}
-		\leavevmode
-		\includegraphics[width=0.98\textwidth]{gaiatwo0005599752663752776192-0007_page02.pdf}
-	\end{center}
-	\vspace{-0.5cm}
-	\caption{
-		{\bf Light curve diagnostics.} 
-    Time-series of raw flux (\texttt{IRM2}),  TFA-detrended flux
-    (\texttt{TF2}), stellar-variability detrended flux, and the
-    background are shown as a function of barycentric Julian date.
-    The overplotted dashed vertical lines are the ephemeris of the
-    highest-power TLS peak from Figure~\ref{fig:pg1}.
-    An important check is whether the flux dips are correlated with
-    changes in the background level -- in this case, they are not.
-    The standard deviation and TESS magnitude are quoted in the upper
-    right.  The red line in the second from the top plot is the
-    windowed spline described in Section~\ref{subsec:ctois}, in this
-    case an essential step for finding the eclipse signal.
-		\label{fig:pg2}
-	}
-\end{figure*}
-
-\begin{figure*}[!h]
-	\begin{center}
-		\leavevmode
-		\includegraphics[width=0.98\textwidth]{gaiatwo0005599752663752776192-0007_page03.pdf}
-	\end{center}
-	\vspace{-0.5cm}
-	\caption{
-    {\bf Transit diagnostics.}
-    The plots show the maximally-detrended light curve (top); the
-    phase-folded light curve centered over $\pm3$ transit durations of
-    the primary transit (middle left); the secondary eclipse (middle
-    right); the odd-numbered transits (lower left); and the
-    even-numbered transits (lower right).
-    The stellar parameters ($T_{\rm eff}, R_\star, M_\star$) are taken
-    from TICv8 when available \citep{stassun_TIC8_2019}.
+\subsection{Transit diagnostics}
+\label{sec:pg3}
+
+Figure~\ref{fig:pg3}.
+The plots show the maximally-detrended light-curve (top); the
+phase-folded light-curve centered over $\pm3$ transit durations of the
+primary transit (middle left); the secondary eclipse (middle right);
+the odd-numbered transits (lower left); and the even-numbered transits
+(lower right).  The stellar parameters ($T_{\rm eff}, R_\star,
+M_\star$) are taken from TICv8 when available
+\citep{stassun_TIC8_2019}.
+%FIXME: if not, what happens?!?!
 %Gaia-DR2 Apsis pipeline results when available
@@
 The first eight lines of text are parameters determined from the
-    best-fitting TLS model.  The one exception is the planet radius,
-    which uses the stellar radius as noted above.
-    The ``flux contamination'' (\texttt{TICCONT}) from neighboring
-    stars is {\it never} taken into account, because transit depth
-    dilution does not affect image subtraction analyses in the same
-    manner as aperture-photometry reductions.
-    The significance of the odd-to-even asymmetry is quoted,
-    but given the strong rotational variability in this object (Figure~\ref{fig:pg2}),
-   	the apparent odd-even asymmetry could have been caused by the detrending process.
-    To estimate the transit to occulation depth ratio $\delta_{\rm tra}/\delta_{\rm occ}$,
-    the phase-folded light curve is also fit by a sum of two
-    gaussians (in this case, the fit failed).
-    ``AstExc'' refers to the Gaia-DR2 astrometric excess, which can
-    indicate hints of astrometric binarity in the system.
-    ``$d_{\rm geom}$'' is the geometric distance from
-    \citet{bailer-jones_distances_2018}.
-    ``$R_\star + M_\star \rightarrow T_{b0}$'' gives the duration of a
-    zero-eccentricity central transit based on the TICv8 stellar
-    radius and mass if available. If the mass is not available, a
-    stellar mass is interpolated from the
+best-fitting TLS model.  The one exception is the planet radius, which
+uses the stellar radius as noted above.  The ``flux contamination''
+(\texttt{TICCONT}) from neighboring stars is {\it never} taken into
+account, because transit depth dilution does not affect image
+subtraction analyses in the same manner as aperture-photometry
+reductions.  The significance of the odd-to-even asymmetry is quoted,
+but given the strong rotational variability in this object
+(Figure~\ref{fig:pg2}), the apparent odd-even asymmetry could have
+been caused by the detrending process.  To estimate the transit to
+occulation depth ratio $\delta_{\rm tra}/\delta_{\rm occ}$, the
+phase-folded light-curve is also fit by a sum of two gaussians (in
+this case, the fit failed).  ``AstExc'' refers to the Gaia-DR2
+astrometric excess, which can indicate hints of astrometric binarity
+in the system.  ``$d_{\rm geom}$'' is the geometric distance from
+\citet{bailer-jones_distances_2018}.  ``$R_\star + M_\star \rightarrow
+T_{b0}$'' gives the duration of a zero-eccentricity central transit
+based on the TICv8 stellar radius and mass if available. If the mass
+is not available, a stellar mass is interpolated from the
 \citet{pecaut_intrinsic_2013} table, under the assumption that the
@@
 %\footnote{\url{http://www.pas.rochester.edu/~emamajek/EEM_dwarf_UBVIJHK_colors_Teff.txt}}.
-		\label{fig:pg3}
-	}
-\end{figure*}
-
-\begin{figure*}[!h]
-	\begin{center}
-		\leavevmode
-		\includegraphics[width=0.98\textwidth]{gaiatwo0005599752663752776192-0007_page04.pdf}
-	\end{center}
-	\vspace{-0.5cm}
-	\caption{
-		{\bf Light curves for increasing aperture sizes.} 
+
+\subsection{Light-curves for increasing aperture sizes}
+\label{sec:pg4}
+
+Figure~\ref{fig:pg4}.
 Apertures of radius 1, 1.5, and 2.25 pixels are shown from top to
 bottom.  The blue line is the reference transit depth from the
-    best-fitting TLS model.  Changes in depth with increasing aperture size
-    can indicate that the source of variability is off-center from the 
-    aperture, suggesting a photometric blend.
-		\label{fig:pg4}
-	}
-\end{figure*}
-
-\begin{figure*}[!h]
-	\begin{center}
-		\leavevmode
-		\includegraphics[width=0.98\textwidth]{gaiatwo0005599752663752776192-0007_page05.pdf}
-	\end{center}
-	\vspace{-0.5cm}
-	\caption{
-		{\bf Cluster membership assessment diagnostics.}
-    The star was considered a candidate cluster member by the
-    source(s) listed under ``Reference'', in this case
-    \citet{cantat-gaudin_gaia_2018}.  The name used in their catalog
-    in this case was \texttt{5599752663752776192}, a Gaia-DR2
-    identifier, which can be back-referenced to find that
+best-fitting TLS model.  Changes in depth with increasing aperture
+size can indicate that the source of variability is off-center from
+the aperture, suggesting a photometric blend.
+
+\subsection{Cluster membership assessment diagnostics}
+\label{sec:pg5}
+
+Figure~\ref{fig:pg5}.
+The star was considered a candidate cluster member by the source(s)
+listed under ``Reference'', in this case
+\citet{cantat-gaudin_gaia_2018}.  The name used in their catalog in
+this case was \texttt{5599752663752776192}, a Gaia-DR2 identifier,
+which can be back-referenced to find that
 \citet{cantat-gaudin_gaia_2018} assigned this star a membership
-    probability in Haffner 13 of just 10\%.
-    The base catalog for the plots is chiefly that of
-    \citet{Kharchenko_et_al_2013}, due to its homogeneous parameter
-    determination procedure (particularly for age).  If a match to the
-    \citet{Kharchenko_et_al_2013} catalog is found, then the remaining
-    plots are populated.  Top-left shows the parallax, with orange
-    points sampled from the Gaia-DR2 posterior, black points the other
-    cluster members in the Kharchenko catalog, and the blue line the
-    claimed Kharchenko parallax for the cluster.  A number of
-    field contaminants in the Kharchenko catalog are visible in this
-    case.  Top-right are the Gaia proper motions, where against black
-    points are cluster members from Kharchenko, and the orange is the
-    target star.  Bottom-left is the color-magnitude diagram, and
-    bottom-right are the on-sky positions.  In the text,
-    \texttt{N1sr2} is the number of $1\sigma$ cluster members reported
-    by \citet{Kharchenko_et_al_2013} within the cluster angular
-    radius; $\log t$ is the base-10 logarithm of the age in years;
-    \texttt{type} matches the type codes provided by
-    \citet{Kharchenko_et_al_2013}; \texttt{K13Note} gives the
-    description of the cluster from \citet{Kharchenko_et_al_2013}, if
-    available.
-    Extra caution must be taken when interpreting this set of plots,
-    since they can only show disagreement between the observed star's
-    properties and those of the listed Kharchenko members (and the
-    latter may be biased).
-		\label{fig:pg5}
-	}
-\end{figure*}
-
-\begin{figure*}[!h]
-	\begin{center}
-		\leavevmode
-		\includegraphics[width=0.98\textwidth]{gaiatwo0005599752663752776192-0007_page06.pdf}
-	\end{center}
-	\vspace{-0.5cm}
-	\caption{
-		{\bf Imaging variability diagnostics.} 
-    This page is intended to help diagnose which stars are producing
-    the observed variability.  Top-left and top-center are the mean
-    out-of-transit (OOT) and mean in-transit calibrated images
-    (separate from any of our image-subtraction analysis).  The OOT
-    images are based on the same number of exposures as the in-transit
-    images and split evenly before and after each transit
+probability in Haffner 13 of just 10\%.  The base catalog for the
+plots is chiefly that of \citet{Kharchenko_et_al_2013}, due to its
+homogeneous parameter determination procedure (particularly for age).
+If a match to the \citet{Kharchenko_et_al_2013} catalog is found, then
+the remaining plots are populated.  Top-left shows the parallax, with
+orange points sampled from the Gaia-DR2 posterior, black points the
+other cluster members in the Kharchenko catalog, and the blue line the
+claimed Kharchenko parallax for the cluster.  A number of field
+contaminants in the Kharchenko catalog are visible in this case.
+Top-right are the Gaia proper motions, where against black points are
+cluster members from Kharchenko, and the orange is the target star.
+Bottom-left is the color-magnitude diagram, and bottom-right are the
+on-sky positions.  In the text, \texttt{N1sr2} is the number of
+$1\sigma$ cluster members reported by \citet{Kharchenko_et_al_2013}
+within the cluster angular radius; $\log t$ is the base-10 logarithm
+of the age in years; \texttt{type} matches the type codes provided by
+\citet{Kharchenko_et_al_2013}; \texttt{K13Note} gives the description
+of the cluster from \citet{Kharchenko_et_al_2013}, if available.
+Extra caution must be taken when interpreting this set of plots, since
+they can only show disagreement between the observed star's properties
+and those of the listed Kharchenko members (and the latter may be
+biased).
+
+\subsection{Imaging variability diagnostics}
+\label{sec:pg6}
+
+Figure~\ref{fig:pg6}.
+This page helps diagnose which stars are producing the observed
+variability.  Top-left and top-center are the mean out-of-transit
+(OOT) and mean in-transit calibrated images (separate from any of our
+image-subtraction analysis).  The OOT images are based on the same
+number of exposures as the in-transit images and split evenly before
+and after each transit
 \citep[following][]{bryson_identification_2013,kostov_l9859_2019}.
 The yellow star is the target; cyan dots are the flux-weighted
-    centroid of the entire image for each transit event; small red
-    crosses are WCS-projected locations of neighbor stars.
-    Middle-left is the most important sub-panel: the difference
-    between the OOT and in-transit mean images.  If the variability
-    shown in background map (units: ADU) is off-target, the transit is
-    typically not from the target star.  Middle-center is the same,
-    normalized by the uncertainty map.  Lower left and lower center
-    show the DSS field in linear and log scales at roughly the same
-    pixel scale as the TESS image, with the 1, 1.5, and 2.25
-    pixel-radius apertures in blue, orange, and green respectively.
-    The brightness of neighborhood stars is given on the far right.
-    Note the slight coordinate rotation difference between DSS and TESS images;
-    DSS images are aligned north-up, east-left; TESS images are
-    oriented as closely as possible to this system without actually
-    performing the rotation.
+centroid of the entire image for each transit event; small red crosses
+are WCS-projected locations of neighbor stars.  Middle-left is the
+most important sub-panel: the difference between the OOT and
+in-transit mean images.  If the variability shown in background map
+(units: ADU) is off-target, the transit is typically not from the
+target star.  Middle-center is the same, normalized by the uncertainty
+map.  Lower left and lower center show the DSS field in linear and log
+scales at roughly the same pixel scale as the TESS image, with the 1,
+1.5, and 2.25 pixel-radius apertures in blue, orange, and green
+respectively.  The brightness of neighborhood stars is given on the
+far right.  Note the slight coordinate rotation difference between DSS
+and TESS images; DSS images are aligned north-up, east-left; TESS
+images are oriented as closely as possible to this system without
+actually performing the rotation.
+
+\section{Neighborhood plots}
+
+The standard vetting report's neighborhood
+analysis is helpful, but insufficient for determination of
+cluster membership.
+A more thorough approach is to query Gaia-DR2 for
+nearby stars in position, parallax, and proper motion space, and
+let the data speak for itself regarding {\it (a)} the existence of
+the group, and {\it (b)} the target star's membership within the group.
+
+For these plots, the ``neighborhood'' is defined as a group of at
+most $10^4$ randomly selected stars within:
+\begin{align}
+\langle \alpha \rangle \pm 5\sigma_\alpha, \\
+\langle \delta \rangle \pm 5\sigma_\delta, \\
+\langle \pi \rangle \pm 5\sigma_\pi,
+\end{align}
+where $(\alpha, \delta, \pi)$ are the right ascension,
+declination, and parallax.
+$\langle x \rangle$ denotes the mean over all stars within
+the claimed cluster, $\sigma_x$ denotes the standard deviation.
+The limiting $G$ magnitude for the ``neighborhood'' is set
+to 18 for \citet{cantat-gaudin_gaia_2018} groups, and 16
+for \cite{Kharchenko_et_al_2013} groups.
+
+For the 2019-09-18 through 2019-11-25 deliveries,
+these plots were made with code available online\footnote{
+\url{https://github.com/lgbouma/cdips_followup/tree/e4d9d}}.
+
+\subsection{Neighborhood diagnostic}
+\label{sec:nbhd}
+Figure~\ref{fig:nbhd} shows the labelled quantities from
+the target star, the neighborhood, and the ``cluster members'' reported by either
+\citet{cantat-gaudin_gaia_2018} or \citet{Kharchenko_et_al_2013}.
+The top three subplots intentionally omit the labelled
+cluster members, in order to give the user their own by-eye
+assessment of whether they see clusters in the neighborhood, and
+whether the target star is within those clusters.
+
+\subsection{Neighborhood diagnostic, with overplot}
+\label{sec:nbdh_extra}
+Figure~\ref{fig:nbhd_extra}.
+Same as Figure~\ref{fig:nbhd}, but with overplotted cluster members
+on the upper three subplots.
+
+\begin{figure*}[!h]
+	\begin{center}
+		\leavevmode
+		\includegraphics[width=0.8\textwidth]{gaiatwo0005599752663752776192-0007_page01.pdf}
+	\end{center}
+	\vspace{-0.5cm}
+	\caption{
+    {\bf Transit search summary.} See \S~\ref{sec:pg1}.
+		\label{fig:pg1}
+	}
+\end{figure*}
+
+\begin{figure*}[!h]
+	\begin{center}
+		\leavevmode
+		\includegraphics[width=0.8\textwidth]{gaiatwo0005599752663752776192-0007_page02.pdf}
+	\end{center}
+	\vspace{-0.5cm}
+	\caption{
+		{\bf Light-curve diagnostics.} See \S~\ref{sec:pg2}.
+		\label{fig:pg2}
+	}
+\end{figure*}
+
+\begin{figure*}[!h]
+	\begin{center}
+		\leavevmode
+		\includegraphics[width=0.8\textwidth]{gaiatwo0005599752663752776192-0007_page03.pdf}
+	\end{center}
+	\vspace{-0.5cm}
+	\caption{
+    {\bf Transit diagnostics.}  See \S~\ref{sec:pg3}.
+		\label{fig:pg3}
+	}
+\end{figure*}
+
+\begin{figure*}[!h]
+	\begin{center}
+		\leavevmode
+		\includegraphics[width=0.8\textwidth]{gaiatwo0005599752663752776192-0007_page04.pdf}
+	\end{center}
+	\vspace{-0.5cm}
+	\caption{
+		{\bf Light-curves for increasing aperture sizes.}  See
+    \S~\ref{sec:pg4}.
+		\label{fig:pg4}
+	}
+\end{figure*}
+
+\begin{figure*}[!h]
+	\begin{center}
+		\leavevmode
+		\includegraphics[width=0.8\textwidth]{gaiatwo0005599752663752776192-0007_page05.pdf}
+	\end{center}
+	\vspace{-0.5cm}
+	\caption{
+		{\bf Cluster membership assessment diagnostics.} See
+    \S~\ref{sec:pg5}.
+		\label{fig:pg5}
+	}
+\end{figure*}
+
+\begin{figure*}[!h]
+	\begin{center}
+		\leavevmode
+		\includegraphics[width=0.8\textwidth]{gaiatwo0005599752663752776192-0007_page06.pdf}
+	\end{center}
+	\vspace{-0.5cm}
+	\caption{
+		{\bf Imaging variability diagnostics.} See \S~\ref{sec:pg6}.
 		\label{fig:pg6}
@@
 
-% \begin{figure*}[!h]
-% 	\begin{center}
-% 		\leavevmode
-% 		\includegraphics[width=0.98\textwidth]{gaiatwo0005541111035713815552-0007_page01.pdf}
-% 	\end{center}
-% 	\vspace{-0.5cm}
-% 	\caption{
-% 		{\bf Transit search summary.} Periodograms from TLS and 
-% 		phase-dispersion minimization, as calculated 
-% 		with \texttt{astrobase.periodbase}, are shown in the top left and top center 
-% 		\citep{bhatti_astrobase_2018,hippke_TLS_2019,stellingwerf_period_1978}.
-% 		The top three peaks from each 
-% 		method are shown in the second and third rows; the raw light curve is in the 
-% 		top-right. A small finder chart from DSS is inset to the top left, with
-% 		the 1.5-pixel radius aperture used to extract the light curve in orange.
-% 		\label{fig:pg1}
-% 	}
-% \end{figure*}
-% 
-% \begin{figure*}[!h]
-% 	\begin{center}
-% 		\leavevmode
-% 		\includegraphics[width=0.98\textwidth]{gaiatwo0005541111035713815552-0007_page02.pdf}
-% 	\end{center}
-% 	\vspace{-0.5cm}
-% 	\caption{
-% 		{\bf Light curve diagnostics.} 
-% 		Time-series of raw flux (\texttt{IRM2}),  TFA-detrended flux (\texttt{TF2}), stellar-variability
-% 		detrended flux, and the background are shown as a function of
-% 		barycentric Julian date.
-% 		The overplotted dashed vertical lines are the ephemeris of the highest-power
-% 		TLS peak from Figure~\ref{fig:pg1}.
-% 		An important check is whether the flux dips are correlated with changes in the 
-% 		background level -- in this case, they are not.
-% 		The standard deviation and TESS magnitude are quoted in the upper right.
-% 		The red line in the second from the top plot is the windowed 
-% 		spline described in Section~\ref{subsec:ctois} -- in this case it is near its maximal
-% 		frequency.
-% 		\label{fig:pg2}
-% 	}
-% \end{figure*}
-% 
-% \begin{figure*}[!h]
-% 	\begin{center}
-% 		\leavevmode
-% 		\includegraphics[width=0.98\textwidth]{gaiatwo0005541111035713815552-0007_page03.pdf}
-% 	\end{center}
-% 	\vspace{-0.5cm}
-% 	\caption{
-%     {\bf Transit diagnostics.} The plots show the
-%     maximally-detrended light curve (top); the phase-folded light
-%     curve centered over $\pm3$ transit durations of the primary
-%     transit (middle left); the secondary eclipse (middle right); the
-%     odd-numbered transits (lower left); and the even-numbered transits
-%     (lower right).
-%     The stellar parameters ($T_{\rm eff}, R_\star, M_\star$) are taken from
-%     TICv8 when available \citep{stassun_TIC8_2019}.
-%     %Gaia-DR2 Apsis pipeline results when available
-%     %\citep{andrae_apsis_2018}.
-%     The first eight lines of text are parameters determined from the
-%     best-fitting TLS model.
-%     The one exception is the planet radius, which uses the stellar
-%     radius as noted above.
-%     The ``flux contamination'' (\texttt{TICCONT}) from neighboring
-%     stars is {\it never} taken into account, because transit depth
-%     dilution does not affect image subtraction analyses in the same
-%     manner as aperture-photometry reductions.
-%     To estimate the transit to occulation depth ratio, the
-%     phase-folded light curve is also coarsely fit via maximum
-%     likelihood by a sum of two gaussians.
-%     ``AstExc'' refers to the Gaia-DR2 astrometric excess, which can
-%     indicate hints of astrometric binarity in the system.
-%     ``$d_{\rm geom}$'' is the geometric distance from
-%     \citet{bailer-jones_distances_2018}.
-%     ``$R_\star + M_\star \rightarrow T_{b0}$'' gives the duration of a
-%     zero-eccentricity central transit based on the TICv8 stellar
-%     radius and mass if available. If the mass is not available, a
-%     stellar mass is interpolated from the
-%     \citet{pecaut_intrinsic_2013} table, under the assumption that the
-%     star is a dwarf.
-%     %\footnote{\url{http://www.pas.rochester.edu/~emamajek/EEM_dwarf_UBVIJHK_colors_Teff.txt}}.
-% 		\label{fig:pg3}
-% 	}
-% \end{figure*}
-% 
-% \begin{figure*}[!h]
-% 	\begin{center}
-% 		\leavevmode
-% 		\includegraphics[width=0.98\textwidth]{gaiatwo0005541111035713815552-0007_page04.pdf}
-% 	\end{center}
-% 	\vspace{-0.5cm}
-% 	\caption{
-% 		{\bf Light curves for increasing aperture sizes.} 
-% 		Apertures of radius 1, 1.5, and 2.25 pixels are shown from top to bottom.
-% 		The blue line is the reference transit depth from the best-fitting TLS model.
-% 		Any changes in depth with aperture size might indicate the need for a 
-% 		detailed pixel-level analysis.
-% 		\label{fig:pg4}
-% 	}
-% \end{figure*}
-% 
-% \begin{figure*}[!h]
-% 	\begin{center}
-% 		\leavevmode
-% 		\includegraphics[width=0.98\textwidth]{gaiatwo0005541111035713815552-0007_page05.pdf}
-% 	\end{center}
-% 	\vspace{-0.5cm}
-% 	\caption{
-% 		{\bf Cluster membership assessment diagnostics.}
-% 		The star was considered a candidate cluster member by the source(s) listed under
-% 		``Reference'', in this case \citet{dias_proper_2014}.
-% 		The name used in the Dias catalog in this case was \texttt{264-025831}, a
-% 		UCAC-4 identifier, which can be back-referenced to find that \citet{dias_proper_2014}
-% 		assigned this star a
-% 		membership probability in NGC 2546 of 98\%.
-% 		The base catalog for the plots is chiefly that of \citet{Kharchenko_et_al_2013},
-% 		due to its homogeneous parameter determination procedure (particularly for age).
-% 		If a match to the \citet{Kharchenko_et_al_2013} catalog is found, then the remaining
-% 		plots are populated.
-% 		Top-left shows the parallax, with orange points sampled from the Gaia-DR2
-% 		posterior, black points the other cluster members in the Kharchenko catalog,
-% 		and the blue line the claimed Kharchenko parallax for the cluster.
-% 		A large number of field contaminants are visible in this case.
-% 		Top-right are the Gaia proper motions, where against black points are cluster
-% 		members from Kharchenko, and the orange is the target star.
-%     Bottom-left is the color-magnitude diagram, and bottom-right are
-%     the on-sky positions.  In the text,
-% 		\texttt{N1sr2} is the number of $1\sigma$ cluster members reported
-% 		by \citet{Kharchenko_et_al_2013} within the cluster angular radius;
-% 		$\log t$ is the base-10 logarithm of the age in years;
-% 		\texttt{type} matches the type codes provided by
-%     \citet{Kharchenko_et_al_2013};
-%     \texttt{K13Note} gives the description of the cluster from
-%     \citet{Kharchenko_et_al_2013}, if available.
-% 		\label{fig:pg5}
-% 	}
-% \end{figure*}
-% 
-% \begin{figure*}[!h]
-% 	\begin{center}
-% 		\leavevmode
-% 		\includegraphics[width=0.98\textwidth]{gaiatwo0005541111035713815552-0007_page06.pdf}
-% 	\end{center}
-% 	\vspace{-0.5cm}
-% 	\caption{
-% 		{\bf Imaging variability diagnostics.} 
-% 		This page is intended to help diagnose which stars are producing the observed
-% 		variability.
-% 		Top-left and top-center are the mean out-of-transit (OOT) and mean in-transit 
-% 		calibrated images (separate from any of our image-subtraction analysis).
-% 		The OOT images are based on the same number of exposures as the in-transit images
-% 		and split evenly before and after each transit \citep[following][]{bryson_identification_2013,kostov_l9859_2019}.
-% 		The yellow star is the target; cyan dots are the flux-weighted centroid of the entire
-% 		image for each transit event; small red crosses are WCS-projected locations of neighbor stars.
-% 		Middle-left is the most important sub-panel: the difference between
-% 		the OOT and in-transit mean images.
-% 		If the variability shown in background map (units: ADU) is off-target, the
-% 		transit is typically not from the target star.
-% 		Middle-center is the same, normalized by the uncertainty map.
-% 		Lower left and lower center show the DSS field in linear and log scales
-% 		at roughly the same pixel scale as the TESS image,
-% 		with the 1, 1.5, and 2.25 pixel-radius apertures in blue, orange, and green respectively.
-% 		The brightness of neighborhood stars is given on the far right.
-% 		Note the slight rotation difference between DSS and TESS images;
-% 		DSS images are aligned north-up, east-left; TESS images are oriented as closely as
-% 		possible to this system without actually performing the rotation.
-% 		\label{fig:pg6}
-% 	}
-% \end{figure*}
+\begin{figure*}[!h]
+	\begin{center}
+		\leavevmode
+		\includegraphics[width=0.85\textwidth]{TIC125192758O-lb20190918_NGC_2323_neighborhood.png}
+	\end{center}
+	\vspace{-0.5cm}
+	\caption{
+		{\bf Neighborhood diagnostic.} See \S~\ref{sec:nbhd}.
+		\label{fig:nbhd}
+	}
+\end{figure*}
+
+\begin{figure*}[!h]
+	\begin{center}
+		\leavevmode
+		\includegraphics[width=0.85\textwidth]{TIC125192758O-lb20190918_NGC_2323_neighborhood_extra.png}
+	\end{center}
+	\vspace{-0.5cm}
+	\caption{
+		{\bf Neighborhood diagnostic with additional overplotted points.} See \S~\ref{sec:nbhd_extra}.
+		\label{fig:nbhd_extra}
+	}
+\end{figure*}
+
+%%%%%%%%%%%
+% BIBLIOGRAPHY %
+%%%%%%%%%%%
+\clearpage
+\newpage
+\bibliographystyle{yahapj}                            
+\bibliography{bibliography}
 

### 2019-12-12 cdips/plotting/vetting_pdf.py
minor

@@ -468,11 +468,6 @@ def _get_full_infodict(tlsp, hdr, mdf):
     if h['TICCONT'] != 'nan':
         h['TICCONT'] = '{:.2f}'.format(h['TICCONT'])
 
-    # if you have Gaia Rstar, use that to estimate stellar mass, and the
-    # circular transit duration timescale
-    mamadf = pd.read_csv('../data/Mamajek_Rstar_Mstar_Teff_SpT.txt',
-                         delim_whitespace=True)
-
     if h['rstar'] != 'nan' and h['mstar'] != 'nan':
         mstar = float(h['mstar'])
         rstar = float(h['rstar'])*u.Rsun
@@ -481,6 +476,11 @@ def _get_full_infodict(tlsp, hdr, mdf):
         h['circduration'] = '{:.1f}'.format(tdur_circ)
 
     elif h['rstar'] != 'nan' and h['mstar'] == 'nan':
+
+        # if you have only Rstar, use that to estimate stellar mass (assuming
+        # it's a dwarf), and therefore the circular transit duration timescale
+        mamadf = pd.read_csv('../data/Mamajek_Rstar_Mstar_Teff_SpT.txt',
+                             delim_whitespace=True)
 
         #
         # mass monotonically decreases, but radius does not (in Mamajek's

### 2019-12-12 doc/vetting_report_documentation/doc_TeX/ms.tex
update vetting report docs for s8-s11 release

@@
 This document describes the CDIPS planet candidate vetting reports
-uploaded by \texttt{lbouma} to ExoFOP-TESS 2019-09-18 through 2019-11-25.
+uploaded by \texttt{lbouma} to ExoFOP-TESS 2019-12-15 through present.
+Earlier version of this document are available at
+  \url{lgbouma.com/cdips_documentation/}.
 \\
@@
 {\it (b)} whether the reported age is correct.
-The code used to make these reports for the 2019-09-18 through
-2019-11-25 planet candidates is available online\footnote{ 
-\url{https://github.com/lgbouma/cdips/tree/a83a30}}.
+The code used to make these reports is available online\footnote{
+  \url{https://github.com/lgbouma/cdips/tree/57274b}}.
 
-Figures~\ref{fig:pg1} to~\ref{fig:pg6} summarize the document
+Figures~\ref{fig:pg1} to~\ref{fig:pg7} summarize the document
 construed for these purposes.  The planet candidate chosen for these
-figures (Gaia-DR2 \texttt{5541111035713815552} = TIC
-\texttt{110718787}) was chosen in part because it passed all the
-tests.  It was reported\footnote{\url{https://exofop.ipac.caltech.edu/tess/view_ctoi.php}}
-as a giant planet candidate in an open cluster
-on Sep 9, 2019.  Higher
-resolution HATSouth photometry revealed about a month afterward that
-the dip signal comes from a neighboring eclipsing binary.
+figures (Gaia-DR2 \texttt{532542547468722176} = TIC
+\texttt{401153825}) was chosen because it showcases many of the
+vetting report features, while also being a likely eclipsing binary.
 
@@
 
-Figure~\ref{fig:pg1}.
-Periodograms from TLS and phase-dispersion minimization, calculated
-with \texttt{astrobase.periodbase}, are shown in the top left and top
-center
+Figure~\ref{fig:pg1}.  Periodograms from TLS and phase-dispersion
+minimization, calculated with \texttt{astrobase.periodbase}, are shown
+in the top left and top center
 \citep{bhatti_astrobase_2018,hippke_TLS_2019,stellingwerf_period_1978}.
 The top three peaks from each method are shown in the second and third
-rows; the raw light-curve is in the top-right. A small finder chart
-from DSS is inset to the top left, with the 1.5-pixel radius aperture
+rows; the raw light-curve is in the top-right. A finder chart
+is inset to the top left, with the 1.5-pixel radius aperture
 used to extract the light-curve in orange.
+The finder charts are from The Second Digitized Sky Survey (Red); they
+are pulled from NASA's \texttt{skyview} service\footnote{See
+\url{https://skyview.gsfc.nasa.gov/current/cgi/survey.pl} and
+\url{http://archive.stsci.edu/dss/acknowledging.html}}.
 
@@
 quoted in the upper right.  The red line in the second from the top
-plot is a spline fit, which in this case an essential step for finding
-the eclipse signal.
+plot is a spline fit, which in this case was not an essential step for
+finding the eclipse signal.
 
-The windowed spline is an optional feature: it is only fitted and
-removed if the star is found to be ``variable'' (the Lomb-Scargle peak
-period is found with false alarm probability below $10^{-5}$). The
-spline is a robust penalized B-spline, which is a B-spline with
-knot-length automatically determined via cross-validation
+The spline is an optional feature: it is only fitted and removed if
+the star is found to be ``variable'' (the Lomb-Scargle peak period is
+found with false alarm probability below $10^{-5}$). The spline is a
+robust penalized B-spline, which is a B-spline with knot-length
+automatically determined via cross-validation
 \citep{eilers_flexible_1996}. The idea behind the cross-validation is
@@
 the odd-numbered transits (lower left); and the even-numbered transits
-(lower right).  The stellar parameters ($T_{\rm eff}, R_\star,
-M_\star$) are taken from TICv8 when available
-\citep{stassun_TIC8_2019}.
-%FIXME: if not, what happens?!?!
-%Gaia-DR2 Apsis pipeline results when available
-%\citep{andrae_apsis_2018}.
+(lower right).
+Also shown is the best-fit TLS template model --- by default, this
+assumes a non-grazing geometry (see \citealt{hippke_TLS_2019}).
+
+The stellar parameters ($T_{\rm eff}, R_\star, M_\star$) are taken
+from TICv8 when available \citep{stassun_TIC8_2019}.  For the stellar
+radius, if TICv8 does not quote a radius, neither will the vetting
+report.  If TICv8 gives a stellar radius, but does not give
+a stellar mass, we interpolate the mass using the radius and the 
+\citet{pecaut_intrinsic_2013}
+table, under the assumption that the star is a dwarf.
+%\footnote{\url{http://www.pas.rochester.edu/~emamajek/EEM_dwarf_UBVIJHK_colors_Teff.txt}}.
+The effective temperatures calculated by TICv8 were estimated from an empirical
+color relation involving Gaia $G_{\rm Bp}$ and $G_{\rm Rp}$ magnitudes.  These
+observed colors were dereddened first, using Pan-STARRS dust maps
+\citep{green_galactic_2018} for declinations above $-30^\circ$, and the
+\citet{schlegel_maps_1998} maps otherwise.
+
 The first eight lines of text are parameters determined from the
@@
 T_{b0}$'' gives the duration of a zero-eccentricity central transit
-based on the TICv8 stellar radius and mass if available. If the mass
-is not available, a stellar mass is interpolated from the
-\citet{pecaut_intrinsic_2013} table, under the assumption that the
-star is a dwarf.
-%\footnote{\url{http://www.pas.rochester.edu/~emamajek/EEM_dwarf_UBVIJHK_colors_Teff.txt}}.
+based on the TICv8 stellar radius and masses discussed above.
 
@@
 listed under ``Reference'', in this case
-\citet{cantat-gaudin_gaia_2018}.  The name used in their catalog in
-this case was \texttt{5599752663752776192}, a Gaia-DR2 identifier,
-which can be back-referenced to find that
-\citet{cantat-gaudin_gaia_2018} assigned this star a membership
-probability in Haffner 13 of just 10\%.  The base catalog for the
-plots is chiefly that of \citet{Kharchenko_et_al_2013}, due to its
-homogeneous parameter determination procedure (particularly for age).
-If a match to the \citet{Kharchenko_et_al_2013} catalog is found, then
-the remaining plots are populated.  Top-left shows the parallax, with
-orange points sampled from the Gaia-DR2 posterior, black points the
-other cluster members in the Kharchenko catalog, and the blue line the
-claimed Kharchenko parallax for the cluster.  A number of field
-contaminants in the Kharchenko catalog are visible in this case.
-Top-right are the Gaia proper motions, where against black points are
-cluster members from Kharchenko, and the orange is the target star.
-Bottom-left is the color-magnitude diagram, and bottom-right are the
-on-sky positions.  In the text, \texttt{N1sr2} is the number of
-$1\sigma$ cluster members reported by \citet{Kharchenko_et_al_2013}
-within the cluster angular radius; $\log t$ is the base-10 logarithm
-of the age in years; \texttt{type} matches the type codes provided by
-\citet{Kharchenko_et_al_2013}; \texttt{K13Note} gives the description
-of the cluster from \citet{Kharchenko_et_al_2013}, if available.
+\citet{cantat-gaudin_gaia_2018}.  The name used in their catalog was
+\texttt{5325425474687221760}, a Gaia-DR2 identifier, which can be
+back-referenced to find the membership probability they assigned this
+star for being in Collinder 205.  The base catalog however for this page
+of plots is \citet{Kharchenko_et_al_2013}, due to its homogeneous
+parameter determination procedure (particularly for age).  If a match to
+the \citet{Kharchenko_et_al_2013} catalog is found, then the subplots on
+this page are populated; otherwise, they are not.  Top-left shows the
+parallax, with orange points sampled from the Gaia-DR2 posterior, black
+points the other cluster members in the {\it Kharchenko catalog} (not
+the catalog claiming membership), and the blue line the claimed
+Kharchenko parallax for the cluster.  A number of field contaminants in
+the Kharchenko catalog are visible in this case.  Top-right are the Gaia
+proper motions, where against black points are cluster members from
+Kharchenko, and the orange is the target star.  Bottom-left is the
+color-magnitude diagram, and bottom-right are the on-sky positions.  In
+the text, \texttt{N1sr2} is the number of $1\sigma$ cluster members
+reported by \citet{Kharchenko_et_al_2013} within the cluster angular
+radius; $\log t$ is the base-10 logarithm of the age in years;
+\texttt{type} matches the type codes provided by
+\citet{Kharchenko_et_al_2013}; ``\texttt{Note}'' gives the description
+of the cluster from \citet{Kharchenko_et_al_2013}, if any is available.
 Extra caution must be taken when interpreting this set of plots, since
@@
 and those of the listed Kharchenko members (and the latter may be
-biased).
+incomplete or otherwise biased).
 
@@
 variability.  Top-left and top-center are the mean out-of-transit
-(OOT) and mean in-transit calibrated images (separate from any of our
-image-subtraction analysis).  The OOT images are based on the same
+(OOT) and mean in-transit calibrated images (created separately from our
+image-subtraction analysis, using \texttt{TESScut},
+\citealt{brasseur_astrocut_2019}).  The OOT images are based on the same
 number of exposures as the in-transit images and split evenly before
@@
 \citep[following][]{bryson_identification_2013,kostov_l9859_2019}.
-The yellow star is the target; cyan dots are the flux-weighted
-centroid of the entire image for each transit event; small red crosses
-are WCS-projected locations of neighbor stars.  Middle-left is the
-most important sub-panel: the difference between the OOT and
-in-transit mean images.  If the variability shown in background map
-(units: ADU) is off-target, the transit is typically not from the
-target star.  Middle-center is the same, normalized by the uncertainty
-map.  Lower left and lower center show the DSS field in linear and log
-scales at roughly the same pixel scale as the TESS image, with the 1,
-1.5, and 2.25 pixel-radius apertures in blue, orange, and green
-respectively.  The brightness of neighborhood stars is given on the
-far right.  Note the slight coordinate rotation difference between DSS
-and TESS images; DSS images are aligned north-up, east-left; TESS
-images are oriented as closely as possible to this system without
-actually performing the rotation.
+The yellow star is the target's position from TICv8; 
+small red crosses are WCS-projected locations of neighbor stars.
 
-\section{Neighborhood plots}
+Middle-left is the most important sub-panel: the difference between
+the OOT and in-transit mean images.
+If the variability shown in the background map (units: ADU) is off-target,
+the signal is not from the target star.  
+A two dimensional gaussian is fit to the inner 8x8 pixels to estimate
+the centroid position --- the resulting best-fit location is shown as
+a white star, and the separation to the catalog star's position
+(yellow star) is labelled \texttt{ctlg - gauss(OOT-intra)} on the
+right.
+A different approach, simply taking the first moment of the middle-left
+image, gives the \texttt{ctlg - <OOT-intra>} line.
 
-The standard vetting report's neighborhood
-analysis is helpful, but insufficient for determination of
-cluster membership.
+Middle-center is the same as middle-left, but normalized by the
+uncertainty map.  Lower left and lower center show the DSS2-Red field
+in linear and log scales at roughly the same pixel scale as the TESS
+image, with the 1, 1.5, and 2.25 pixel-radius apertures in blue,
+orange, and green respectively.  The brightness of neighborhood stars
+is given on the far right.  Note the slight coordinate rotation
+difference between DSS and TESS images; DSS images are aligned
+north-up, east-left; TESS images are oriented as closely as possible
+to this system without actually performing the rotation.
+
+\subsection{Neighborhood plots}
+\label{sec:pg7}
+
+Figure~\ref{fig:pg7}.
+The analysis in Figure~\ref{fig:pg5} is helpful but insufficient for
+determination of cluster membership.
 A more thorough approach is to query Gaia-DR2 for
@@
 
-For the 2019-09-18 through 2019-11-25 deliveries,
-these plots were made with code available online\footnote{
-\url{https://github.com/lgbouma/cdips_followup/tree/e4d9d}}.
-
-\subsection{Neighborhood diagnostic}
-\label{sec:nbhd}
-Figure~\ref{fig:nbhd} shows the labelled quantities from
-the target star, the neighborhood, and the ``cluster members'' reported by either
-\citet{cantat-gaudin_gaia_2018} or \citet{Kharchenko_et_al_2013}.
-The top three subplots intentionally omit the labelled
-cluster members, in order to give the user their own by-eye
-assessment of whether they see clusters in the neighborhood, and
-whether the target star is within those clusters.
-
-\subsection{Neighborhood diagnostic, with overplot}
-\label{sec:nbdh_extra}
-Figure~\ref{fig:nbhd_extra}.
-Same as Figure~\ref{fig:nbhd}, but with overplotted cluster members
-on the upper three subplots.
+Figure~\ref{fig:pg7} shows the labeled quantities from the target
+star, the neighborhood, and the ``cluster members'' reported by
+\citet{cantat-gaudin_gaia_2018}, \cite{kounkel_untangling_2019}, or
+\citet{Kharchenko_et_al_2013}.  The top three subplots intentionally
+omit the labelled cluster members, in order to give the user their own
+by-eye assessment of whether they see clusters in the neighborhood,
+and whether the target star is within those clusters.
+The middle three subplots overplot cluster members from the reference
+noted in the legend.
 
@@
 		\leavevmode
-		\includegraphics[width=0.8\textwidth]{gaiatwo0005599752663752776192-0007_page01.pdf}
+		\includegraphics[width=0.8\textwidth]{pg_0001.pdf}
 	\end{center}
@@
 		\leavevmode
-		\includegraphics[width=0.8\textwidth]{gaiatwo0005599752663752776192-0007_page02.pdf}
+		\includegraphics[width=0.8\textwidth]{pg_0002.pdf}
 	\end{center}
@@
 		\leavevmode
-		\includegraphics[width=0.8\textwidth]{gaiatwo0005599752663752776192-0007_page03.pdf}
+		\includegraphics[width=0.8\textwidth]{pg_0003.pdf}
 	\end{center}
@@
 		\leavevmode
-		\includegraphics[width=0.8\textwidth]{gaiatwo0005599752663752776192-0007_page04.pdf}
+		\includegraphics[width=0.8\textwidth]{pg_0004.pdf}
 	\end{center}
@@
 		\leavevmode
-		\includegraphics[width=0.8\textwidth]{gaiatwo0005599752663752776192-0007_page05.pdf}
+		\includegraphics[width=0.8\textwidth]{pg_0005.pdf}
 	\end{center}
@@
 		\leavevmode
-		\includegraphics[width=0.8\textwidth]{gaiatwo0005599752663752776192-0007_page06.pdf}
+		\includegraphics[width=0.8\textwidth]{pg_0006.pdf}
 	\end{center}
@@
 		\leavevmode
-		\includegraphics[width=0.85\textwidth]{TIC125192758O-lb20190918_NGC_2323_neighborhood.png}
+		\includegraphics[width=0.85\textwidth]{pg_0007.pdf}
 	\end{center}
@@
 	\caption{
-		{\bf Neighborhood diagnostic.} See \S~\ref{sec:nbhd}.
-		\label{fig:nbhd}
-	}
-\end{figure*}
-
-\begin{figure*}[!h]
-	\begin{center}
-		\leavevmode
-		\includegraphics[width=0.85\textwidth]{TIC125192758O-lb20190918_NGC_2323_neighborhood_extra.png}
-	\end{center}
-	\vspace{-0.5cm}
-	\caption{
-		{\bf Neighborhood diagnostic with additional overplotted points.} See \S~\ref{sec:nbhd_extra}.
-		\label{fig:nbhd_extra}
+		{\bf Neighborhood diagnostic.} See \S~\ref{sec:pg7}.
+		\label{fig:pg7}
 	}

### 2019-12-13 drivers/classification_postprocessing.py
classification postproc: clarify organization

@@ -9,18 +9,18 @@ if host != 'brik':
 
 def main():
     isfull = 0
-    iscollabsubclass = 1
-    getgold = 0
+    iscollabsubclass = 0
+    organize_PCs = 1
 
-    sector = 8
-    today = '20191121'
+    sector = 11
+    today = '20191205'
 
     if isfull:
         given_full_classifications_organize(sector=sector, today=today)
     if iscollabsubclass:
         given_collab_subclassifications_merge(sector=sector)
-    if getgold:
-        given_merged_gold_organize_PCs(sector=sector)
+    if organize_PCs:
+        given_merged_organize_PCs(sector=sector)
 
 
 def ls_to_df(classfile, classifier='LGB'):
@@ -115,12 +115,12 @@ def given_collab_subclassifications_merge(sector=6):
     print('wrote {}'.format(outpath))
 
 
-def given_merged_gold_organize_PCs(sector=None):
+def given_merged_organize_PCs(sector=None):
     """
     Using output from given_collab_subclassifications_merge, assign gold=2,
-    maybe=1, junk, and look closer at anything with average rating >=1. The one
-    exception: things classified as "not_cdips_still_good", which go in their
-    own pile.
+    maybe=1, junk, and look closer at anything with average rating >1 (note:
+    not >=). The one exception: things classified as "not_cdips_still_good",
+    which go in their own pile.
     """
 
     datadir = '/home/luke/Dropbox/proj/cdips/results/vetting_classifications/'
@@ -131,41 +131,131 @@ def given_merged_gold_organize_PCs(sector=None):
 
     tag_colnames = [c for c in df.columns if 'Tags' in c]
 
-    allisgold = np.ones_like(df['Name'])
+    # iterate over ["LGB_tags", "JH_tags", "JNW_tags"] to get scores assigned
+    # by each
     for tag_colname in tag_colnames:
-        newcol = tag_colname.split('_')[0]+'_isgold'
+
+        newcol = tag_colname.split('_')[0]+'_score'
 
         classifier_isgold = np.array(
             df[tag_colname].str.lower().str.contains('gold')
         )
+        classifier_ismaybe = np.array(
+            df[tag_colname].str.lower().str.contains('maybe')
+        )
+        classifier_isjunk = np.array(
+            df[tag_colname].str.lower().str.contains('junk')
+        )
 
[…]

### 2020-01-11 doc/vetting_report_documentation/doc_TeX/ms.tex
vetting report docs
doc: clarify "neighborhood" definition

@@
 uploaded by \texttt{lbouma} to ExoFOP-TESS 2019-12-15 through present.
-Earlier version of this document are available at
-  \url{lgbouma.com/cdips_documentation/}.
+Earlier versions of this document are available at
+  \url{lgbouma.com}.
 \\
@@
 
+The cluster members (black points) and the neighborhood members (gray
+points) are {\it mutually exclusive sets}. After the stars are
+randomly selected from the volume described above, any overlapping
+stars between the group and the neighborhood samples are removed from
+the neighborhood sample.
+
 Figure~\ref{fig:pg7} shows the labeled quantities from the target
@@
 omit the labelled cluster members, in order to give the user their own
-by-eye assessment of whether they see clusters in the neighborhood,
+by-eye assessment of whether they see clusters in the neighborhood (as
+might happen if the membership labelling is {\it incomplete}),
 and whether the target star is within those clusters.

### 2020-03-04 cdips/lcproc/detrend.py
detrending: cosmetic addition

@@ -22,22 +22,26 @@ assert int(wotanversiontuple[0]) >= 1
 assert int(wotanversiontuple[1]) >= 4
 
 
-def detrend_flux(time, flux, break_tolerance=0.5):
+def detrend_flux(time, flux, break_tolerance=0.5, method='pspline'):
 
-    # matched detrending to do_initial_period_finding
-    flat_flux, trend_flux = flatten(time, flux,
-                                    method='pspline',
-                                    return_trend=True,
-                                    break_tolerance=break_tolerance)
+    if method == 'pspline':
+        # matched detrending to do_initial_period_finding
+        flat_flux, trend_flux = flatten(time, flux,
+                                        method='pspline',
+                                        return_trend=True,
+                                        break_tolerance=break_tolerance)
 
-    # # another option:
-    # flat_flux, trend_flux = flatten(time, flux,
-    #                                 method='biweight',
-    #                                 return_trend=True,
-    #                                 break_tolerance=0.5,
-    #                                 window_length=0.3,
-    #                                 cval=6)
+    elif method == 'biweight':
+        # another option:
+        flat_flux, trend_flux = flatten(time, flux,
+                                        method='biweight',
+                                        return_trend=True,
+                                        break_tolerance=0.5,
+                                        window_length=0.3,
+                                        cval=6)
 
+    else:
+        raise NotImplementedError
 
     return flat_flux, trend_flux
 

### 2020-03-04 cdips/utils/lcutils.py
planet search: alter search logic per 0a42054
to go from detrended RAW LCs, in the case of a variable TFA LC, rather
than noisy detrended TFA LCs.

this is a shift from previous sectors, but should help for variable
stars.

@@ -1,10 +1,11 @@
 from astropy.io import fits
 
-def get_lc_data(lcpath, tfa_aperture='TFA2'):
+def get_lc_data(lcpath, mag_aperture='TFA2', tfa_aperture='TFA2'):
 
     hdul = fits.open(lcpath)
 
     tfa_time = hdul[1].data['TMID_BJD']
+    ap_mag = hdul[1].data[mag_aperture]
     tfa_mag = hdul[1].data[tfa_aperture]
 
     xcc, ycc = hdul[0].header['XCC'], hdul[0].header['YCC']
@@ -18,4 +19,4 @@ def get_lc_data(lcpath, tfa_aperture='TFA2'):
     # */cam2_ccd1/hlsp_cdips_tess_ffi_gaiatwo0002916360554371119104-0006_tess_v01_llc.fits
     source_id = lcpath.split('gaiatwo')[1].split('-')[0].lstrip('0')
 
-    return source_id, tfa_time, tfa_mag, xcc, ycc, ra, dec, tmag
+    return source_id, tfa_time, ap_mag, xcc, ycc, ra, dec, tmag, tfa_mag

### 2020-03-04 drivers/do_initial_period_finding.py

@@ -45,10 +45,11 @@ def main():
     )
 
 
-def run_periodograms_and_detrend(source_id, tfa_time, tfa_mag, period_min=0.5,
+def run_periodograms_and_detrend(source_id, time, mag, period_min=0.5,
                                  period_max=27, orbitgap=1, expected_norbits=2,
                                  orbitpadding=6/(24), detrend_if_variable=True,
-                                 ls_fap_cutoff=1e-5):
+                                 ls_fap_cutoff=1e-5, tfa_time=None,
+                                 tfa_mag=None):
     """
     kwargs:
 
@@ -68,7 +69,6 @@ def run_periodograms_and_detrend(source_id, tfa_time, tfa_mag, period_min=0.5,
         is 50, which for TESS data (total time ~=25 days) is commensurate with
         0.5 day periodic signal.
 
-
         In injection-recovery tests (/tests/detrend_checks.py),  the result was
         that the additional trending was only helpful in detecting planets
         whenever substantial non-gaussian variability existed in the TFA light
@@ -83,18 +83,27 @@ def run_periodograms_and_detrend(source_id, tfa_time, tfa_mag, period_min=0.5,
     ls_fap = ls.false_alarm_probability(power.max())
     ls_period = 1/freq[np.argmax(power)]
 
+    # If the light-curve is still variable in TFA-form, then default to just
+    # running wotan on the raw light-curve. If it's not variable in TFA form,
+    # then don't run wotan, just search the TFA light-curve.
+    if detrend_if_variable and ls_fap > ls_fap_cutoff:
+        flux = tfa_flux
+        time = tfa_time
+    else:
+        pass
+
     #
     # prepare flux for transit least squares.
     #
     f_x0 = 1e4
     m_x0 = 10
-    tfa_flux = f_x0 * 10**( -0.4 * (tfa_mag - m_x0) )
-    tfa_flux /= np.nanmedian(tfa_flux)
+    flux = f_x0 * 10**( -0.4 * (mag - m_x0) )
+    flux /= np.nanmedian(flux)
 
     #
     # ignore the times near the edges of orbits for TLS.
     #
-    bls_time, bls_flux = moe.mask_orbit_start_and_end(tfa_time, tfa_flux)
+    bls_time, bls_flux = moe.mask_orbit_start_and_end(time, flux)
 
     #
[…]

### 2020-03-04 drivers/do_initial_period_finding.py
minor

@@ -377,7 +377,7 @@ def do_initial_period_finding(
 
     plot_initial_period_finding_results(df, resultsdir)
 
-    if sectornum not in [6,7,8,9,10]:
+    if sectornum not in [6,7,8,9,10,11]:
         raise NotImplementedError(
             'you need to manually set SNR limits for this sector!'
         )

### 2020-03-04 doc/vetting_report_documentation/doc_TeX/ms.tex
update vetting report description document
I now understand why changing anything in these vetting reports is a big
hassle for NASA. You need to rewrite the documentation too! And it's
never backwards-compatible!

@@
 \begin{abstract}
-To find planet candidates in clusters,
-we make vetting reports using our light-curves \citep{bouma_cdips_2019} and
-auxiliary data.
-This document describes the CDIPS planet candidate vetting reports
-uploaded by \texttt{lbouma} to ExoFOP-TESS 2019-12-15 through present.
-Earlier versions of this document are available at
-  \url{lgbouma.com}.
+To find planet candidates in clusters, we make vetting reports using
+our light-curves \citep{bouma_cdips_2019} and auxiliary data.  This
+document describes the CDIPS planet candidate vetting reports
+uploaded by \texttt{bouma} to ExoFOP-TESS 2020-01-20 through
+2020-05-01.  Earlier versions of this document are available at
+\url{lgbouma.com/notes}.
 \\
@@
 construed for these purposes.  The planet candidate chosen for these
-figures (Gaia-DR2 \texttt{532542547468722176} = TIC
-\texttt{401153825}) was chosen because it showcases many of the
-vetting report features, while also being a likely eclipsing binary.
+figures (Gaia-DR2 \texttt{3050033749239975552} = TIC
+\texttt{125192758}) was chosen because it showcases many of the
+vetting report features, in this case for a neighboring eclipsing binary.
 
@@
 Time-series of raw flux (\texttt{IRM2}),  TFA-detrended flux
-(\texttt{TF2}), stellar-variability detrended flux, and the background
+(\texttt{TF2}), stellar-variability ``detrended flux'', and the background
 are shown as a function of barycentric Julian date.  The overplotted
@@
 case, they are not.  The standard deviation and TESS magnitude are
-quoted in the upper right.  The red line in the second from the top
-plot is a spline fit, which in this case was not an essential step for
+quoted in the upper right.  The red line in the top
+plot is a spline fit, which in this case helped in
 finding the eclipse signal.
@@
 the star is found to be ``variable'' (the Lomb-Scargle peak period is
-found with false alarm probability below $10^{-5}$). The spline is a
+found with false alarm probability below $10^{-5}$, within the TFA light-curves). The spline is a
 robust penalized B-spline, which is a B-spline with knot-length
@@
 larger errors when tested on the entire dataset.  We used the
-\texttt{wotan} implementation, which is a wrapper to the
+\texttt{wotan} implementation\footnote{
+We use \texttt{wotan} versions greater than \texttt{1.4}. Before \texttt{2020-03-01}, an earlier version
+was used, which led to qualitatively worse detrending performance for a subset
+of light-curves due to a floating point truncation error. See \texttt{\url{https://github.com/hippke/wotan/issues/51}}.
+}, which is a wrapper to the
 \texttt{pyGAM} spline fitter, with $2\sigma$ clipping of outliers from
@@
 day}$ window.
+
+Whenever the TFA light-curve is found to be variable, the ``stellar variability detrended flux'' is
+the result of dividing the raw \texttt{IRM2} flux by the best-fit spline\footnote{
+Before \texttt{2020-03-01}, this definition was different. For the initial
+single-sector processing of S6-S11, it was the result of dividing the \texttt{TFA2} flux
+by the best-fit spline.
+}.
+This is the light-curve that is then searched for transiting planets, and used
+in {\it e.g.}, Figure~\ref{fig:pg1} and Figure~\ref{fig:pg3}.
+If the TFA light-curve is not found to be variable, then the \texttt{TFA2} light-curve is used for
+this purpose.
 
@@
 Figure~\ref{fig:pg4}.
-Apertures of radius 1, 1.5, and 2.25 pixels are shown from top to
+Apertures of radius 1, 1.5, and 2.25 pixels are shown in maximally detrended
+light-curves from top to
 bottom.  The blue line is the reference transit depth from the
@@
 \citet{cantat-gaudin_gaia_2018}.  The name used in their catalog was
-\texttt{5325425474687221760}, a Gaia-DR2 identifier, which can be
+in this case a Gaia-DR2 identifier, which can be
 back-referenced to find the membership probability they assigned this
-star for being in Collinder 205.  The base catalog however for this page
+star for being in NGC 2323.  The base catalog however for this page
 of plots is \citet{Kharchenko_et_al_2013}, due to its homogeneous
@@
 they can only show disagreement between the observed star's properties
-and those of the listed Kharchenko members (and the latter may be
+and those of the listed Kharchenko members (and the latter is in some cases
 incomplete or otherwise biased).
@@
 noted in the legend.
+The radial velocity plots (bottom row) use radial velocities from Gaia-DR2,
+and so are limited to roughly 3500-7000$\,$K, for $G\lesssim 12.5$ \citep{katz_gaia_2019}.
 

### 2020-03-04 cdips/plotting/__init__.py
minor tweaks

@@ -1,6 +1,10 @@
 from datetime import datetime
 
 def savefig(fig, figpath):
+
+    if not figpath.endswith('.png'):
+        raise ValueError('figpath must end with .png')
+
     fig.savefig(figpath, dpi=450, bbox_inches='tight')
     print('{}: made {}'.format(datetime.utcnow().isoformat(), figpath))
 

### 2020-03-04 cdips/plotting/visualize_survey_designs.py

@@ -568,8 +568,9 @@ if __name__=="__main__":
 
     # END OPTIONS
 
-    only_extended_only_primary(overplot_galactic_plane=overplot_galactic_plane,
-                               for_proposal=for_proposal,
-                               overplot_k2_fields=overplot_k2_fields,
-                               plot_tess=plot_tess,
-                               overplot_cdips=overplot_cdips)
+    for overplot_cdips in [0,1]:
+        only_extended_only_primary(overplot_galactic_plane=overplot_galactic_plane,
+                                   for_proposal=for_proposal,
+                                   overplot_k2_fields=overplot_k2_fields,
+                                   plot_tess=plot_tess,
+                                   overplot_cdips=overplot_cdips)
